### 2014-07-13 doc/manual/overview.tex
Initial commit

\chapter{Overview}

The prevalent uses of JavaScript in web programming have revealed
security vulnerability issues of JavaScript applications,
which emphasizes the need for JavaScript analyzers to detect such issues.
Recently, researchers have proposed several analyzers of JavaScript programs
and some web service companies have developed various JavaScript engines.
However, unfortunately, most of the tools are not documented well,
thus it is very hard to understand and modify them.
Or, such tools are often not open to the public.

In this specification, we present formal specification and implementation
of \safe, a scalable analysis framework for ECMAScript, developed for the JavaScript research community.
This is the very first attempt to provide both formal specification and
its open-source implementation for JavaScript,
compared to the existing approaches focused on only one of them.
To make it more amenable for other researchers to use our framework,
we formally define three kinds of intermediate representations for JavaScript
used in the framework,
and we provide formal specifications of translations between them.
To be adaptable for adventurous future research including modifications
in the original JavaScript syntax,
we actively use open-source tools to automatically generate parsers and some intermediate
representations.
To support a variety of program analyses in various compilation phases,
we design the framework to be as flexible, scalable, and pluggable as possible.
Finally, our framework is publicly available,
and some collaborative research using the framework are in progress.

### 2014-07-13 benchmarks/v8_v1/units/permute.js

@@ -1,0 +1,76 @@
+// Benchpress: A collection of micro-benchmarks.
+
+var allResults = [ ];
+
+
+// -----------------------------------------------------------------------------
+// F r a m e w o r k
+// -----------------------------------------------------------------------------
+function Benchmark(string, run) {
+  this.string = string;
+  this.run = run;
+}
+
+// Run each benchmark for two seconds and count number of iterations.
+function time(benchmark) {
+  var elapsed = 0;
+  var start = new Date();
+  for (var n = 0; elapsed < 2000; n++) {
+    benchmark.run();
+    elapsed = new Date() - start;
+  }
+  var usec = (elapsed * 1000) / n;
+  allResults.push(usec);
+  //print('Time (' + benchmark.string + '): ' + Math.floor(usec) + ' us.');
+}
+
+function error(string) {
+  //print(string);
+}
+
+
+// -----------------------------------------------------------------------------
+// P e r m u t e
+// -----------------------------------------------------------------------------
+var permuteCount;
+ 
+function swap(n, k, array) {
+  var tmp = array[n];
+  array[n] = array[k];
+  array[k] = tmp;
+}
+
+function doPermute(n, array) {
+  permuteCount++;
+  if (n != 1) {
+    doPermute(n - 1, array);
+    for (var k = n - 1; k >= 1; k--) {
+      swap(n, k, array);
+      doPermute(n - 1, array);
+      swap(n, k, array);
+    }
+  }
+}
+
+function permute() {
+  var array = new Array(8);
+  for (var i = 1; i <= 7; i++) array[i] = i - 1;
+  permuteCount = 0;
+  doPermute(7, array);
+  if (permuteCount != 8660) error("Wrong result: " + permuteCount + " should be: 8660");
+}
+
+var Permute = new Benchmark("Permute", permute);
+
+
+// -----------------------------------------------------------------------------
+// M a i n 
+// -----------------------------------------------------------------------------
+time(Permute);
+
+var logMean = 0;
+for (var i = 0; i < allResults.length; i++)
+  logMean += Math.log(allResults[i]);
+logMean /= allResults.length;
+
+//print("Geometric mean: " + Math.round(Math.pow(Math.E, logMean)) + " us.");

### 2014-07-13 benchmarks/v8_v1/units/takl.js

@@ -1,0 +1,83 @@
+// Benchpress: A collection of micro-benchmarks.
+
+var allResults = [ ];
+
+
+// -----------------------------------------------------------------------------
+// F r a m e w o r k
+// -----------------------------------------------------------------------------
+function Benchmark(string, run) {
+  this.string = string;
+  this.run = run;
+}
+
+// Run each benchmark for two seconds and count number of iterations.
+function time(benchmark) {
+  var elapsed = 0;
+  var start = new Date();
+  for (var n = 0; elapsed < 2000; n++) {
+    benchmark.run();
+    elapsed = new Date() - start;
+  }
+  var usec = (elapsed * 1000) / n;
+  allResults.push(usec);
+  //print('Time (' + benchmark.string + '): ' + Math.floor(usec) + ' us.');
+}
+
+function error(string) {
+  //print(string);
+}
+
+// -----------------------------------------------------------------------------
+//  T a k l
+// -----------------------------------------------------------------------------
+function ListElement(length, next) {
+  this.length = length;
+  this.next = next;
+}
+
+function makeList(length) {
+  if (length == 0) return null;
+  return new ListElement(length, makeList(length - 1));
+}
+
+function isShorter(x, y) {
+  var xTail = x, yTail = y;
+  while (yTail != null) {
+    if (xTail == null) return true;
+    xTail = xTail.next;
+    yTail = yTail.next;
+  }
+  return false;
+}
+
+function doTakl(x, y, z) {
+  if (isShorter(y, x)) {
+    return doTakl(doTakl(x.next, y, z), 
+                  doTakl(y.next, z, x), 
+                  doTakl(z.next, x, y));
+  } else {
+    return z;
+  }
+}
+
+function takl() {
+  var result = doTakl(makeList(15), makeList(10), makeList(6));
+  if (result.length != 10) 
+    error("Wrong result: " + result.length + " should be: 10");
+}
+
+var Takl = new Benchmark("Takl", takl);
+
+
+// -----------------------------------------------------------------------------
+// M a i n 
+// -----------------------------------------------------------------------------
+time(Takl);
+
+var logMean = 0;
+for (var i = 0; i < allResults.length; i++)
+  logMean += Math.log(allResults[i]);
+logMean /= allResults.length;
+
+//print("Geometric mean: " + Math.round(Math.pow(Math.E, logMean)) + " us.");

### 2014-07-13 bin/models/dom/__dom__.js

@@ -1,0 +1,1 @@
+// DOM object models

### 2014-07-13 src/main/java/kr/ac/kaist/jsaf/useful/MagicNumbers.java

@@ -1,0 +1,235 @@
+/*******************************************************************************
+    Copyright 2008,2010, Oracle and/or its affiliates.
+    All rights reserved.
+
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+package kr.ac.kaist.jsaf.useful;
+
+import java.util.Collection;
+
+/**
+ * Magic numbers chosen to be:
+ * <ul>
+ * <li> prime </li>
+ * <li> 16 set bits </li>
+ * <li> good for 32-bit LFSR (irreducible in GF(2^32) if 2^32 added) </li>
+ * <li> positive </li>
+ * <li> inverses modulo 0x7fffffffL, 0x80000000L, 0x100000000L also prime
+ * </li>
+ * </ul>
+ */
+public final class MagicNumbers {
+    public final static int A = 0x56dfa013;
+    public final static int B = 0x5c1e0d2f;
+    public final static int C = 0x3aab43c9;
+    public final static int D = 0x03a19fe9;
+    public final static int E = 0x0c3679d3;
+    public final static int F = 0x6cc54e71;
+    public final static int G = 0x258f951d;
+    public final static int H = 0x21ed7817;
+    public final static int I = 0x1bb6c345;
+    public final static int J = 0x689b8d8d;
+    public final static int K = 0x48d51cb7;
+    public final static int L = 0x46ad91cd;
+    public final static int M = 0x52db2a55;
+    public final static int N = 0x1095aef5;
+    public final static int O = 0x1196e735;
+    public final static int P = 0x164dd83d;
+    public final static int Q = 0x78ba8693;
+    public final static int R = 0x45b701af;
+    public final static int S = 0x2f0e039f;
+    public final static int T = 0x547a88bb;
+    public final static int U = 0x403bf571;
+    public final static int V = 0x06b5ea1b;
+    public final static int W = 0x0f5e60ab;
+    public final static int X = 0x799988b3;
+    public final static int Y = 0x2e7a950b;
+    public final static int Z = 0x72438977;
+    public final static int a = 0x2b5d129d;
+    public final static int b = 0x34d4d32b;
+    public final static int c = 0x674f07c1;
+    public final static int d = 0x56ab29a5;
[…]

### 2014-07-13 src/main/scala/kr/ac/kaist/jsaf/analysis/typing/WorklistFIFO.scala

@@ -1,0 +1,39 @@
+/*******************************************************************************
+    Copyright (c) 2012-2013, KAIST.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+package kr.ac.kaist.jsaf.analysis.typing
+
+import scala.collection.mutable.{ LinkedHashSet => MLinkedHashSet }
+import kr.ac.kaist.jsaf.analysis.lib.WorkTreeSet
+
+class WorklistFIFO extends Worklist {
+  private val worklist = new MLinkedHashSet[ControlPoint]
+
+  def head: ControlPoint = this.synchronized { worklist.last }
+
+  def isEmpty: Boolean = this.synchronized { worklist.isEmpty }
+
+  def getSize: Int = this.synchronized { worklist.size }
+
+  def getWorkList: WorkTreeSet = WorkTreeSet.Empty // TODO: return type does not match
+
+  override def toString: String = {
+    val str = new StringBuilder
+    for(w <- worklist.toList.reverse) str.append(w + "\n")
+    str.toString()
+  }
+
+  protected def insertWork(work: OrderEntry): Unit = worklist.add(work._2)
+
+  protected def removeHead: ControlPoint = {
+    val cp = worklist.last
+    worklist.remove(cp)
+    cp
+  }
+}

### 2014-07-13 src/main/scala/kr/ac/kaist/jsaf/analysis/typing/debug/commands/CmdPrint.scala

@@ -1,0 +1,213 @@
+/*******************************************************************************
+    Copyright (c) 2013, KAIST.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+  ******************************************************************************/
+
+package kr.ac.kaist.jsaf.analysis.typing.debug.commands
+
+import kr.ac.kaist.jsaf.analysis.typing.debug.DebugConsole
+import kr.ac.kaist.jsaf.analysis.typing.domain.DomainPrinter
+import kr.ac.kaist.jsaf.analysis.cfg.{CFGInst, LEntry, Block}
+import kr.ac.kaist.jsaf.analysis.typing.AddressManager._
+import kr.ac.kaist.jsaf.analysis.typing.ControlPoint
+import scala.collection.mutable.{HashMap => MHashMap, HashSet => MHashSet, Stack => MStack}
+
+class CmdPrint extends Command {
+  override val name = "print"
+  override val info: String = "Print out various information."
+
+  override def help(): Unit = {
+    System.out.println("usage: print allstate ({keyword})")
+    System.out.println("       print state ({keyword})")
+    System.out.println("       print loc {LocName} ({keyword})")
+    System.out.println("       print fid {functionID}")
+    System.out.println("       print worklist")
+    System.out.println("       print ipsucc")
+    System.out.println("       print trace")
+    System.out.println("       print (cmd|command)")
+  }
+
+  def grep(key: String, txt: String): String = {
+    val list = txt.split("\n")
+    list.foldLeft("")((txt, line) => {
+      if (line.contains(key)) txt + line + "\n"
+      else txt
+    })
+  }
+
+  override def run(c: DebugConsole, args: Array[String]): Unit = {
+    try {
+      val subcmd = args(0)
+      subcmd.toLowerCase match {
+        case "allstate" => {
+          val key =
+            if (args.length > 1) Some(args(1))
+            else None
+
+          val inS = c.readTable(c.current)
+          val heap_1 = DomainPrinter.printHeap(0, inS._1, c.getCFG, 3)
+          val heap_2 = key match {
+            case Some(k) => grep(k, heap_1)
+            case None => heap_1
+          }
+          System.out.println(heap_2)
+          System.out.println(DomainPrinter.printContext(0, inS._2))
+        }
+        case "state" => {
+          val key =
+            if (args.length > 1) Some(args(1))
+            else None
+
+          val inS = c.readTable(c.current)
[…]

### 2014-07-13 src/main/scala/kr/ac/kaist/jsaf/analysis/typing/domain/AbsUndef.scala

@@ -1,0 +1,81 @@
+/*******************************************************************************
+    Copyright (c) 2012-2013, S-Core, KAIST.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+package kr.ac.kaist.jsaf.analysis.typing.domain
+
+object AbsUndef {
+  sealed abstract class AbsUndefCase
+  case object UndefTopCase extends AbsUndefCase
+  case object UndefBotCase extends AbsUndefCase
+
+  val UndefTop: AbsUndef = new AbsUndef(UndefTopCase)
+  val UndefBot: AbsUndef = new AbsUndef(UndefBotCase)
+
+  def alpha: AbsUndef = UndefTop
+}
+
+class AbsUndef(_kind: AbsUndef.AbsUndefCase) extends AbsDomain {
+  val kind: AbsUndef.AbsUndefCase = _kind
+
+  override def getAbsCase: AbsCase =
+    this.kind match {
+      case AbsUndef.UndefBotCase => AbsBot
+      case AbsUndef.UndefTopCase => AbsTop
+    }
+
+  /* partial order */
+  def <= (that: AbsUndef) = {
+    (this == UndefBot) || (that == UndefTop)
+  }
+
+  /* not a partial order */
+  def </ (that: AbsUndef) = {
+    (this == UndefTop) && (that == UndefBot)
+  }
+
+  /* join */
+  def + (that: AbsUndef) = {
+    if (this == UndefTop || that == UndefTop) UndefTop
+    else UndefBot
+  }
+
+  /* meet */
+  def <> (that: AbsUndef) = {
+    if (this == UndefTop && that == UndefTop) UndefTop
+    else UndefBot
+  }
+  
+  /* abstract operator 'equal to' */
+  def === (that: AbsUndef): AbsBool = {
+    (this.kind, that.kind) match {
+      case (AbsUndef.UndefBotCase, _) => BoolBot
+      case (_, AbsUndef.UndefBotCase) => BoolBot
+      case _ => BoolTrue
+    }
+  }
+  
+  override def toString: String = {
+    this.kind match {
+      case AbsUndef.UndefTopCase => "undefined"
+      case AbsUndef.UndefBotCase => "Bot"
+    }
+  }
+
+  override def isTop: Boolean = {this == UndefTop}
+
+  override def isBottom: Boolean = {this == UndefBot}
+
[…]

### 2014-07-13 src/main/scala/kr/ac/kaist/jsaf/analysis/typing/models/DOMEvent/EventTarget.scala

@@ -1,0 +1,227 @@
+/*******************************************************************************
+    Copyright (c) 2013-2014, S-Core, KAIST.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+  ******************************************************************************/
+
+package kr.ac.kaist.jsaf.analysis.typing.models.DOMEvent
+
+import kr.ac.kaist.jsaf.analysis.typing.domain._
+import kr.ac.kaist.jsaf.analysis.typing.domain.{BoolFalse => F, BoolTrue => T}
+import kr.ac.kaist.jsaf.analysis.typing.models.DOMCore.DOMNode
+import kr.ac.kaist.jsaf.analysis.typing.models.DOMObject.XMLHttpRequest
+import kr.ac.kaist.jsaf.analysis.typing.models._
+import kr.ac.kaist.jsaf.analysis.typing._
+import kr.ac.kaist.jsaf.analysis.cfg.{CFG, CFGExpr, FunctionId}
+import kr.ac.kaist.jsaf.analysis.typing.{ControlPoint, Helper, PreHelper}
+import kr.ac.kaist.jsaf.analysis.typing.domain.Heap
+import kr.ac.kaist.jsaf.analysis.typing.domain.Context
+import kr.ac.kaist.jsaf.analysis.typing.models.AbsBuiltinFunc
+
+object EventTarget extends DOM {
+  private val name = "EventTarget"
+
+  /* predefined locatoins */
+  val loc_proto = ObjProtoLoc
+  // no locations
+
+  /* initial property list */
+  override def getInitList(): List[(Loc, List[(String, AbsProperty)])] = List(
+    // Node interface should implements EventTarget
+    (DOMNode.loc_proto, prop_node_proto),
+    // window interface should implements EventTarget
+    (DOMWindow.WindowLoc, prop_window),
+    // XMLHttpRequest
+    (XMLHttpRequest.loc_proto, prop_ajax)
+  )
+
+  def getPropList = prop_node_proto
+  /* prorotype */
+  private val prop_node_proto: List[(String, AbsProperty)] = List(
+    ("addEventListener",    AbsBuiltinFunc("EventTarget.addEventListener", 3)),
+    ("removeEventListener", AbsBuiltinFunc("EventTarget.removeEventListener", 3)),
+    ("dispatchEvent",       AbsBuiltinFunc("EventTarget.dispatchEvent", 1))
[…]

### 2014-07-13 src/main/scala/kr/ac/kaist/jsaf/analysis/typing/models/DOMObject/ClientRect.scala

@@ -1,0 +1,73 @@
+/*******************************************************************************
+    Copyright (c) 2013, KAIST, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+package kr.ac.kaist.jsaf.analysis.typing.models.DOMObject
+
+import kr.ac.kaist.jsaf.analysis.typing.domain._
+import kr.ac.kaist.jsaf.analysis.typing.domain.{BoolFalse => F, BoolTrue => T}
+import kr.ac.kaist.jsaf.analysis.typing.models._
+import kr.ac.kaist.jsaf.analysis.typing.models.AbsConstValue
+import scala.Some
+import kr.ac.kaist.jsaf.analysis.typing.AddressManager._
+
+// Modeled based on W3C CSSOM View Module
+// Section 10.2 The ClientRect Interface
+object ClientRect extends DOM {
+  private val name = "ClientRect"
+
+  /* predefined locations */
+  val loc_ins = newSystemRecentLoc(name + "Ins")
+  val loc_proto = newSystemRecentLoc(name + "Proto")
+  
+  /* prorotype */
+  private val prop_proto: List[(String, AbsProperty)] = List(
+    ("@class", AbsConstValue(PropValue(AbsString.alpha("Object")))),
+    ("@proto", AbsConstValue(PropValue(ObjectValue(Value(ObjProtoLoc), F, F, F)))),
+    ("@extensible", AbsConstValue(PropValue(BoolTrue)))
+  )
+  /* instance */
+  private val prop_ins: List[(String, AbsProperty)] = List(
+    ("@class",    AbsConstValue(PropValue(AbsString.alpha("Object")))),
+    ("@proto",    AbsConstValue(PropValue(ObjectValue(loc_proto, F, F, F)))),
+    ("@extensible", AbsConstValue(PropValue(BoolTrue))),
+    ("top", AbsConstValue(PropValue(ObjectValue(NumTop, F, T, T)))),
+    ("right", AbsConstValue(PropValue(ObjectValue(NumTop, F, T, T)))),
+    ("bottom", AbsConstValue(PropValue(ObjectValue(NumTop, F, T, T)))),
+    ("left", AbsConstValue(PropValue(ObjectValue(NumTop, F, T, T)))),
[…]

### 2014-07-13 src/main/scala/kr/ac/kaist/jsaf/analysis/typing/models/Tizen/TIZENNDEFRecordURI.scala

@@ -1,0 +1,91 @@
+/*******************************************************************************
+    Copyright (c) 2013-2014, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+  ******************************************************************************/
+
+package kr.ac.kaist.jsaf.analysis.typing.models.Tizen
+
+import kr.ac.kaist.jsaf.analysis.typing.AddressManager._
+
+
+import kr.ac.kaist.jsaf.analysis.cfg.{CFG, CFGExpr, InternalError}
+import kr.ac.kaist.jsaf.analysis.typing.domain._
+import kr.ac.kaist.jsaf.analysis.typing.models._
+import kr.ac.kaist.jsaf.analysis.typing.domain.{BoolFalse => F, BoolTrue => T}
+import kr.ac.kaist.jsaf.analysis.typing._
+
+
+object TIZENNDEFRecordURI extends Tizen {
+  private val name = "NDEFRecordURI"
+  /* predefined locations */
+  val loc_cons = newSystemRecentLoc(name + "Cons")
+  val loc_proto = newSystemRecentLoc(name + "Proto")
+  val loc_parent = TIZENNDEFRecord.loc_proto
+  /* constructor or object*/
+  private val prop_cons: List[(String, AbsProperty)] = List(
+    ("@class", AbsConstValue(PropValue(AbsString.alpha("Function")))),
+    ("@proto", AbsConstValue(PropValue(ObjectValue(Value(ObjProtoLoc), F, F, F)))),
+    ("@extensible",                 AbsConstValue(PropValue(T))),
+    ("@scope",                      AbsConstValue(PropValueNullTop)),
+    ("@construct",               AbsInternalFunc("tizen.NDEFRecordURI.constructor")),
+    ("@hasinstance", AbsConstValue(PropValueNullTop)),
+    ("prototype", AbsConstValue(PropValue(ObjectValue(Value(loc_proto), F, F, F))))
+  )
+
+  /* prototype */
+  private val prop_proto: List[(String, AbsProperty)] = List(
+    ("@class", AbsConstValue(PropValue(AbsString.alpha("CallbackObject")))),
+    ("@proto", AbsConstValue(PropValue(ObjectValue(Value(loc_parent), F, F, F)))),
+    ("@extensible", AbsConstValue(PropValue(BoolTrue)))
+  )
+
[…]

### 2014-07-13 src/main/scala/kr/ac/kaist/jsaf/concolic/FunctionInfo.scala

@@ -1,0 +1,69 @@
+/*******************************************************************************
+    Copyright (c) 2012-2014, KAIST, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+package kr.ac.kaist.jsaf.concolic
+
+import _root_.edu.rice.cs.plt.tuple.{Pair => JPair}
+import _root_.java.lang.{Integer => JInteger}
+import _root_.java.util.{List => JList}
+import _root_.java.util.{Map => JavaMap}
+import _root_.java.util.{HashMap => JavaHashMap}
+import _root_.edu.rice.cs.plt.tuple.{Option => JavaOption}
+import kr.ac.kaist.jsaf.nodes._
+import kr.ac.kaist.jsaf.nodes_util.EJSOp
+import kr.ac.kaist.jsaf.scala_src.nodes._
+import kr.ac.kaist.jsaf.scala_src.useful.Lists._
+import kr.ac.kaist.jsaf.scala_src.useful.Maps._
+import kr.ac.kaist.jsaf.scala_src.useful.Options._
+import kr.ac.kaist.jsaf.scala_src.useful.Pairs._
+import kr.ac.kaist.jsaf.scala_src.useful.Sets._
+import scala.collection.mutable.Map
+
+class FunctionInfo() {
+  var isTarget: Boolean = false
+  var isCandidate: Boolean = false
+  var isProcess: Boolean = false
+  var params: Map[Int, List[String]] = Map[Int, List[String]]()
+  var objects: Map[Int, (String, List[(String, String)])] = Map[Int, (String, List[(String, String)])]() 
+  var thisObject: List[(String, String)] = List[(String, String)]() 
+  var thisName: String = null
+  
+  def toJavaObjects: JavaMap[JInteger, JPair[String, JList[JPair[String, String]]]] = {
+    var jobjects = new JavaHashMap[JInteger, JPair[String, JList[JPair[String, String]]]]()
+    for (key <- objects.keysIterator) {
+      jobjects.put(key, JPair.make(objects(key)._1, toJavaList(objects(key)._2.map(toJavaPair(_)))))
+    }
+    jobjects
+  }
+  def toJavaThisObject: JList[JPair[String, String]] = toJavaList(thisObject.map(toJavaPair(_)))
+
+  def isNewType(p: Int, t: String) = params.get(p) match { case Some(types) => !types.contains(t); case None => true }
+
[…]

### 2014-07-13 src/main/scala/kr/ac/kaist/jsaf/interpreter/InterpreterState.scala

@@ -1,0 +1,318 @@
+/*******************************************************************************
+    Copyright (c) 2012-2013, KAIST, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+package kr.ac.kaist.jsaf.interpreter
+
+import edu.rice.cs.plt.tuple.{Option => JOption}
+import kr.ac.kaist.jsaf.ShellParameters
+import kr.ac.kaist.jsaf.compiler.Predefined
+import kr.ac.kaist.jsaf.nodes_util.{Coverage, NodeUtil => NU}
+import kr.ac.kaist.jsaf.interpreter.{InterpreterPredefine => IP}
+import kr.ac.kaist.jsaf.interpreter.objects._
+import kr.ac.kaist.jsaf.nodes.{IRRoot, IRSpanInfo, IRFunctional}
+import kr.ac.kaist.jsaf.nodes_util.{Span, IRFactory => IF}
+import kr.ac.kaist.jsaf.scala_src.useful.Sets
+import kr.ac.kaist.jsaf.Shell
+import java.util.HashMap
+
+class InterpreterState(val I: Interpreter) {
+  var env: Env = new EmptyEnv()
+  var strict: Boolean = false
+  var comp: Completion = new Completion()
+  var lastComp: Completion = new Completion()
+  var eval: Boolean = false
+  var span: Span = IP.defSpan
+  var coverage: Option[Coverage] = None
+  var objectProps = Set[String]()
+
+  def init() {
+    // Set properties
+    GlobalObject.init()
+    ObjectConstructor.init()
+    ObjectPrototype.init()
+    objectProps = Sets.toSet(ObjectPrototype.property.map.keySet)
+    FunctionConstructor.init()
+    FunctionPrototype.init()
+    ArrayConstructor.init()
+    ArrayPrototype.init()
+    StringConstructor.init()
+    StringPrototype.init()
+    BooleanConstructor.init()
+    BooleanPrototype.init()
+    NumberConstructor.init()
+    NumberPrototype.init()
+    MathObject.init()
+    DateConstructor.init()
+    DatePrototype.init()
+    RegExpConstructor.init()
[…]

### 2014-07-13 src/main/scala/kr/ac/kaist/jsaf/interpreter/objects/JSSyntaxErrorConstructor.scala

@@ -1,0 +1,46 @@
+/*******************************************************************************
+    Copyright (c) 2012-2013, KAIST, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+package kr.ac.kaist.jsaf.interpreter.objects
+
+import kr.ac.kaist.jsaf.scala_src.nodes._
+import kr.ac.kaist.jsaf.scala_src.useful.Lists._
+import kr.ac.kaist.jsaf.scala_src.useful.Options._
+import kr.ac.kaist.jsaf.interpreter.{InterpreterPredefine => IP, _}
+
+class JSSyntaxErrorConstructor(_I: Interpreter, _proto: JSObject)
+  extends JSFunction13(_I, _proto, "Function", true,
+                       propTable, _I.IH.dummyFtn(1), EmptyEnv(), true) {
+  def init(): Unit = {
+    /*
+     * 15.11.7.5 Properties of the NativeError Constructors
+     */
+    property.put("prototype", I.IH.mkDataProp(I.IS.SyntaxErrorPrototype))
+  }
+
+  /*
+   * 15.11.7.4 new NativeError (message)
+   */
+  def construct(message: Val): JSErrorObject =
+    new JSErrorObject(I, I.IS.SyntaxErrorPrototype, "Error", true,
+                      if (I.IH.isUndef(message)) propTable
+                      else I.IH.strPropTable(I.IH.toString(message)))
+
+  /*
+   * 15.11.7.3 The NativeError Constructors
+   */
+  override def _construct(argsObj: JSObject): JSErrorObject =
+    construct(argsObj._get("0"))
+
+  /*
+   * 15.11.7.1 NativeError Constructors Called as Functions
+   */
+  override def _call(tb: Val, argsObj: JSObject): Unit =
+    I.IS.comp.setReturn(_construct(argsObj))
+}

### 2014-07-13 src/main/scala/kr/ac/kaist/jsaf/scala_src/useful/Sets.scala

@@ -1,0 +1,30 @@
+/*******************************************************************************
+    Copyright 2009,2011, Oracle and/or its affiliates.
+    All rights reserved.
+
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+package kr.ac.kaist.jsaf.scala_src.useful
+
+import _root_.java.util.{HashSet => JHashSet}
+import _root_.java.util.{Set => JavaSet}
+import scala.collection.JavaConversions
+
+object Sets {
+
+  /** Takes in any kind of collection. */
+  def toJavaSet[T](elts: Iterable[T]): JavaSet[T] = {
+    val temp = new JHashSet[T]()
+    elts.foreach(temp.add)
+    temp
+  }
+
+  /** Creates an immutable set. */
+  def toSet[T](jset: JavaSet[T]): Set[T] =
+    Set(JavaConversions.asScalaSet(jset).toSeq: _*)
+
+}

### 2014-07-13 src/main/scala/kr/ac/kaist/jsaf/tests/ParserJUTest.scala

@@ -1,0 +1,122 @@
+/*******************************************************************************
+    Copyright (c) 2012-2013, KAIST, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+package kr.ac.kaist.jsaf.tests
+
+import _root_.java.util.{List => JList}
+import _root_.java.io.BufferedReader
+import _root_.java.io.InputStreamReader
+import _root_.java.io.InputStream
+import _root_.java.io.File
+import _root_.java.io.FileFilter
+import _root_.java.io.FilenameFilter
+import _root_.java.io.IOException
+import _root_.java.io.PrintStream
+import _root_.java.util.Arrays
+import _root_.java.util.Collections
+import _root_.java.util.Random
+
+import kr.ac.kaist.jsaf.ProjectProperties
+import kr.ac.kaist.jsaf.compiler.Parser
+import kr.ac.kaist.jsaf.exceptions.SyntaxError
+import kr.ac.kaist.jsaf.scala_src.useful.Arrays._
+import kr.ac.kaist.jsaf.useful.Files
+import kr.ac.kaist.jsaf.useful.TestCaseWrapper
+import kr.ac.kaist.jsaf.useful.WireTappedPrintStream
+
+import junit.framework.Assert
+import junit.framework.TestCase
+import junit.framework.TestSuite
+
+object ParserJUTest extends TestCaseWrapper {
+
+  val SEP = File.separator
+  val PARSER_FAIL_TESTS_DIR = ProjectProperties.BASEDIR + SEP + "tests/parser_tests" + SEP
+
+  def suite(): TestSuite =
+    new ParserTestSuite("ParserJUTest", PARSER_FAIL_TESTS_DIR)
+
+  class ParserTestSuite(_name: String,  _failTestDir: String) extends TestSuite(_name) {
+    val VERBOSE = true
+
+    // relative to the top directory
+    var failTestDir = _failTestDir
+    val _ = addParserTests(failTestDir)
+
+    def addParserTests(_dir: String): Unit = {
+      var dir = _dir
+      if (!dir.endsWith(SEP)) dir += SEP
+      val jsFilter = new FilenameFilter() {
+                       def accept(dir: File, name: String) = name.endsWith(".js")
+                     }
+      // Permute filenames for randomness
+      for (filename <- shuffle(new File(dir).list(jsFilter)))
[…]

### 2014-07-13 tests/clone_detector_tests/cappuccino/Tools/NativeHost/AppController.h

@@ -1,0 +1,54 @@
+//
+//  AppController.h
+//  NativeHost
+//
+//  Created by Francisco Tolmasky on 6/4/09.
+//  Copyright 2009 280 North, Inc. All rights reserved.
+//
+
+#import <Cocoa/Cocoa.h>
+
+extern int SERVER_PORT;
+extern NSString *SERVER_PASSWORD;
+extern NSString *SERVER_USER;
+
+@class Server;
+@class WebScriptObject;
+
+@interface AppController : NSObject
+{
+    NSWindow                        * webViewWindow;
+    WebView                         * webView;
+
+    NSMutableArray                  * openingFilenames;
+    NSMutableArray                  * openingURLStrings;
+
+    Server                          * server;
+    NSFileHandle                    * stdinFileHandle;
+
+    NSMutableAttributedString       * loggedOutput;
+
+    NSURL                           * baseURL;
+}
+
+- (void)configureLocalStorage;
+- (NSURL *)baseURL;
+
+- (void)startServer;
+- (void)startCappuccinoApplication;
+
+- (NSArray *)openingURLStrings;
+
+- (NSView *)keyView;
+- (WebView *)webView;
+- (WebScriptObject *)windowScriptObject;
+
+@end
+
+@interface AppController (MainMenu)
+
+- (void)setMainMenuObject:(WebScriptObject *)aMenuObject;
+
+@end
+
+void NHLog(NSString *type, NSString *message);

### 2014-07-13 tests/clone_detector_tests/closure-library-read-only/closure/goog/events/browserevent.js

@@ -1,0 +1,415 @@
+// Copyright 2005 The Closure Library Authors. All Rights Reserved.
+//
+// Licensed under the Apache License, Version 2.0 (the "License");
+// you may not use this file except in compliance with the License.
+// You may obtain a copy of the License at
+//
+//      http://www.apache.org/licenses/LICENSE-2.0
+//
+// Unless required by applicable law or agreed to in writing, software
+// distributed under the License is distributed on an "AS-IS" BASIS,
+// WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+// See the License for the specific language governing permissions and
+// limitations under the License.
+
+/**
+ * @fileoverview A patched, standardized event object for browser events.
+ *
+ * <pre>
+ * The patched event object contains the following members:
+ * - type           {string}    Event type, e.g. 'click'
+ * - timestamp      {Date}      A date object for when the event was fired
+ * - target         {Object}    The element that actually triggered the event
+ * - currentTarget  {Object}    The element the listener is attached to
+ * - relatedTarget  {Object}    For mouseover and mouseout, the previous object
+ * - offsetX        {number}    X-coordinate relative to target
+ * - offsetY        {number}    Y-coordinate relative to target
+ * - clientX        {number}    X-coordinate relative to viewport
+ * - clientY        {number}    Y-coordinate relative to viewport
+ * - screenX        {number}    X-coordinate relative to the edge of the screen
+ * - screenY        {number}    Y-coordinate relative to the edge of the screen
+ * - button         {number}    Mouse button. Use isButton() to test.
+ * - keyCode        {number}    Key-code
+ * - ctrlKey        {boolean}   Was ctrl key depressed
+ * - altKey         {boolean}   Was alt key depressed
+ * - shiftKey       {boolean}   Was shift key depressed
+ * - metaKey        {boolean}   Was meta key depressed
+ * - defaultPrevented {boolean} Whether the default action has been prevented
+ * - state          {Object}    History state object
+ *
[…]

### 2014-07-13 tests/clone_detector_tests/closure-library-read-only/closure/goog/iter/iter.js

@@ -1,0 +1,686 @@
+// Copyright 2007 The Closure Library Authors. All Rights Reserved.
+//
+// Licensed under the Apache License, Version 2.0 (the "License");
+// you may not use this file except in compliance with the License.
+// You may obtain a copy of the License at
+//
+//      http://www.apache.org/licenses/LICENSE-2.0
+//
+// Unless required by applicable law or agreed to in writing, software
+// distributed under the License is distributed on an "AS-IS" BASIS,
+// WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+// See the License for the specific language governing permissions and
+// limitations under the License.
+
+/**
+ * @fileoverview Python style iteration utilities.
+ * @author arv@google.com (Erik Arvidsson)
+ */
+
+
+goog.provide('goog.iter');
+goog.provide('goog.iter.Iterator');
+goog.provide('goog.iter.StopIteration');
+
+goog.require('goog.array');
+goog.require('goog.asserts');
+
+
+// TODO(nnaze): Add more functions from Python's itertools.
+// http://docs.python.org/library/itertools.html
+
+
+/**
+ * @typedef {goog.iter.Iterator|{length:number}|{__iterator__}}
+ */
+goog.iter.Iterable;
+
+
+// For script engines that already support iterators.
+if ('StopIteration' in goog.global) {
+  /**
+   * Singleton Error object that is used to terminate iterations.
+   * @type {Error}
+   */
+  goog.iter.StopIteration = goog.global['StopIteration'];
+} else {
+  /**
+   * Singleton Error object that is used to terminate iterations.
+   * @type {Error}
+   * @suppress {duplicate}
+   */
+  goog.iter.StopIteration = Error('StopIteration');
+}
+
+
+
+/**
+ * Class/interface for iterators.  An iterator needs to implement a {@code next}
+ * method and it needs to throw a {@code goog.iter.StopIteration} when the
+ * iteration passes beyond the end.  Iterators have no {@code hasNext} method.
+ * It is recommended to always use the helper functions to iterate over the
+ * iterator or in case you are only targeting JavaScript 1.7 for in loops.
+ * @constructor
+ */
+goog.iter.Iterator = function() {};
+
+
+/**
+ * Returns the next value of the iteration.  This will throw the object
+ * {@see goog.iter#StopIteration} when the iteration passes the end.
+ * @return {*} Any object or value.
+ */
[…]

### 2014-07-13 tests/clone_detector_tests/sproutcore/frameworks/datastore/tests/models/single_attribute.js

@@ -1,0 +1,357 @@
+// ==========================================================================
+// Project:   SproutCore - JavaScript Application Framework
+// Copyright: ©2006-2011 Apple Inc. and contributors.
+// License:   Licensed under MIT license (see license.js)
+// ==========================================================================
+/*globals module ok equals same test MyApp */
+
+// test core array-mapping methods for RecordArray with RecordAttribute
+var storeKeys, rec, rec2, bar, bar2 ;
+
+module("SC.RecordAttribute core methods", {
+  setup: function() {
+
+    MyApp = SC.Object.create({
+      store: SC.Store.create()
+    });
+
+    MyApp.Foo = SC.Record.extend({
+
+      // test toOne relationships
+      relatedTo: SC.Record.toOne('MyApp.Foo'),
+
+      // test non-isEditable toOne relationships
+      readOnlyRelatedTo: SC.Record.toOne('MyApp.Bar', {
+        isEditable: NO
+      }),
+
+      // test toOne relationship with computed type
+      relatedToComputed: SC.Record.toOne(function() {
+        // not using .get() to avoid another transform which will
+        // trigger an infinite loop
+        return (this.readAttribute('relatedToComputed').indexOf("foo")===0) ? MyApp.Foo : MyApp.Bar;
+      }),
+
+      bar: SC.Record.toOne('MyApp.Bar', { inverse: 'foo' }),
+
+      barKeyed: SC.Record.toOne('MyApp.Bar', { key: 'barId' })
+
+    });
+
+    MyApp.Bar = SC.Record.extend({
+      foo: SC.Record.toOne('MyApp.Foo', { inverse: 'bar', isMaster: NO })
+    });
+
+    SC.RunLoop.begin();
+    storeKeys = MyApp.store.loadRecords(MyApp.Foo, [
+      {
+        guid: 'foo1',
+        firstName: "John",
+        lastName: "Doe",
+        date: "2009-03-01T20:30-08:00",
+        anArray: ['one', 'two', 'three'],
+        anObject: { 'key1': 'value1', 'key2': 'value2' },
+        bar: "bar1"
+      },
+
+      {
+        guid: 'foo2',
+        firstName: "Jane",
+        lastName: "Doe",
+        relatedTo: 'foo1',
[…]

### 2014-07-13 tests/clone_detector_tests/sproutcore/frameworks/datastore/tests/system/store/pushChanges.js

@@ -1,0 +1,77 @@
+// ==========================================================================
+// Project:   SproutCore - JavaScript Application Framework
+// Copyright: ©2006-2011 Apple Inc. and contributors.
+// License:   Licensed under MIT license (see license.js)
+// ==========================================================================
+/*globals module ok equals same test MyApp */
+
+var store, storeKey, json;
+module("SC.Store#pushChanges", {
+  setup: function() {
+    SC.RunLoop.begin();
+    store = SC.Store.create();
+    
+    json = {
+      string: "string",
+      number: 23,
+      bool:   YES
+    };
+    
+    storeKey1 = SC.Store.generateStoreKey();
+    store.writeDataHash(storeKey1, json, SC.Record.EMPTY);
+
+    storeKey2 = SC.Store.generateStoreKey();
+    store.writeDataHash(storeKey2, json, SC.Record.EMPTY);
+
+    storeKey3 = SC.Store.generateStoreKey();
+    store.writeDataHash(storeKey3, json, SC.Record.EMPTY);
+
+    storeKey4 = SC.Store.generateStoreKey();
+    store.writeDataHash(storeKey4, json, SC.Record.BUSY_LOADING);
+
+    storeKey5 = SC.Store.generateStoreKey();
+    store.writeDataHash(storeKey5, json, SC.Record.BUSY_LOADING);
+
+    storeKey6 = SC.Store.generateStoreKey();
+    store.writeDataHash(storeKey6, json, SC.Record.BUSY_LOADING);
+    SC.RunLoop.end();
+  }
+});
+
+test("Do a pushRetrieve and check if there is conflicts", function() {
+  var res = store.pushRetrieve(SC.Record, undefined, undefined, storeKey1);
+  equals(res, storeKey1, "There is no conflict, pushRetrieve was succesful.");
+  res = store.pushRetrieve(SC.Record, undefined, undefined, storeKey4);
+  ok(!res, "There is a conflict, because of the state, this is expected.");
+});
+
+test("Do a pushDestroy and check if there is conflicts", function() {
+  var res = store.pushDestroy(SC.Record, undefined, storeKey2);
+  equals(res, storeKey2, "There is no conflict, pushDestroy was succesful.");
+  res = store.pushRetrieve(SC.Record, undefined, undefined, storeKey5);
+  ok(!res, "There is a conflict, because of the state, this is expected.");
+});
+
[…]

### 2014-07-13 tests/clone_detector_tests/sproutcore/frameworks/experimental/apps/greenhouse/states/inspector.js

@@ -1,0 +1,152 @@
+// ==========================================================================
+// Project:   Greenhouse
+// Copyright: ©2010 Mike Ball
+// ==========================================================================
+/*globals Greenhouse */
+/*jslint evil: true */
+
+/** @mixin
+  @extends Greenhouse
+  @author Mike Ball
+  @author Evin Grano
+  @version RC1
+  @since RC1
+*/
+Greenhouse.mixin( /** @scope Greenhouse */{
+  
+  inspectorStates: SC.State.design({
+    initialSubstate: 'inspectorClosed',
+    
+    inspectorClosed: SC.State.design({
+
+      parallelStatechart: 'inspector',
+
+      // ..........................................................
+      // Events
+      //
+      openInspector: function(anchor){
+        if(anchor) Greenhouse.setPath('inspectorStates.openInspectorPicker.anchor', anchor);
+        this.gotoState('openInspectorPicker');
+      },
+
+      toggleDockedInspector: function(){
+        this.gotoState('dockedInspector');
+      },
+
+      floatInspector: function(){
+        this.gotoState('inspectorPalette');
+      }
+    }),
+
+    openInspectorPicker: SC.State.design({
+      parallelStatechart: 'inspector',
+
+      enterState: function(){
+        var ap = Greenhouse.appPage;
+        var picker = ap.get('inspectorPicker'),
+            pickerContentView = ap.get('inspectorPickerContentView');
+        var anchor = this.get('anchor') || ap.getPath('mainView.toolBar.inspector');
+
+        pickerContentView.setIfChanged('nowShowing', 'Greenhouse.appPage.inspectorContentView');
+        picker.popup(anchor, SC.PICKER_POINTER);
+        picker.becomeFirstResponder();
+      },
+      exitState: function(){
+        var ap = Greenhouse.appPage; 
+        var picker = ap.get('inspectorPicker'),
+            pickerContentView = ap.get('inspectorPickerContentView');
+        pickerContentView.setIfChanged('nowShowing', null);
+        picker.remove();
+        this.set('anchor', null);
+      },
+
+      // ..........................................................
+      // Events
+      //
+      cancel: function(){
+        this.gotoState('inspectorClosed');
+      },
+
+      floatInspector: function(){
+        this.gotoState('inspectorPalette');
+      },
+
+      toggleDockedInspector: function(){
+        this.gotoState('dockedInspector');
+      }
+    }),
+
[…]

### 2014-07-13 tests/clone_detector_tests/sproutcore/frameworks/experimental/frameworks/designer/controllers/page_design.js

@@ -1,0 +1,172 @@
+// ==========================================================================
+// Project:   SproutCore - JavaScript Application Framework
+// Copyright: ©2006-2011 Strobe Inc. and contributors.
+//            Portions ©2008-2011 Apple Inc. All rights reserved.
+// License:   Licensed under MIT license (see license.js)
+// ==========================================================================
+
+
+/** @class
+  An instance of this controller is created for every page where designers 
+  are involved.  The Designer's themselves will register with the 
+  controller so that you can hook to the controller to manage the views and
+  their editors.
+  
+  Among other things, this controller implements global selection support for
+  the designers.
+  
+  @extends SC.Object
+  @since SproutCore 1.0
+*/
+SC.PageDesignController = SC.Object.extend({
+  
+  isPageDesignController: YES,
+  
+  // ..........................................................
+  // SELECTION
+  // 
+  
+  /** The current view builder selection. */
+  selection: null,
+  
+  /** 
+    Updates the selection either by adding the item or by resetting the 
+    selection.  Calling this method with no parameters will reset the 
+    selection.
+    
+    The passed selection must be a Designer object.
+  */
+  select: function(sel, extend) {
+    var base = this.get('selection');
+    if (!base || !extend || !base.contains(sel)) {
+      base = (!extend || !base) ? SC.CoreSet.create() : base.copy();
+      base.add(sel);
+      this.set('selection', base.freeze()) ;
+      //make the designPane the firstResponder
+      SC.designPage.getPath('designMainPane.container').becomeFirstResponder();
+    }
+    return this ;
+  },
+  
+  /**
+    Removes the passed items from the current selection.
+    
+    The passed selection must be a Designer object.
+  */
+  deselect: function(sel) {
+    
+    var base = this.get('selection');
+    if (base && base.contains(sel)) {
+      base = base.copy();
+      base.remove(sel);
+      this.set('selection', base.freeze());
+    }
+    return this;
+  },
+  /**
+    Invoked whenever the selection changes.  Updates the selection states 
+    on the old and new views.
+  */
+  selectionDidChange: function() {
+    var sel = this.get('selection'),
+        oldSel = this._selection ;
+
+    // save old selection for next time
+    this._selection = sel ;
+    
+    // set the isSelected state on new selection.
+    if (sel) sel.setEach('designIsSelected', YES);
+    
[…]

### 2014-07-13 tests/clone_detector_tests/sproutcore/frameworks/experimental/frameworks/scroll_view/tests/scroll/ui.js

@@ -1,0 +1,258 @@
+// ==========================================================================
+// Project:   SproutCore - JavaScript Application Framework
+// Copyright: ©2006-2011 Strobe Inc. and contributors.
+//            portions copyright @2011 Apple Inc.
+// License:   Licensed under MIT license (see license.js)
+// ==========================================================================
+
+/*global module test ok equals same stop start */
+
+(function() {
+    var appleURL="http://photos4.meetupstatic.com/photos/event/4/6/9/9/600_4518073.jpeg";
+    var iv=SC.ImageView.design({value: appleURL, layout: {height:400, width:400}});
+    var pane = SC.ControlTestPane.design({ height: 100 })
+    .add("basic", SC.ScrollView, {
+  
+    })
+
+    .add("basic2", SC.ScrollView, {
+        contentView: iv
+    })
+    
+    .add("basic3", SC.ScrollView, {
+      contentView: iv,
+      isHorizontalScrollerVisible: NO,
+      autohidesHorizontalScroller: NO,
+      autohidesVerticalScroller: NO
+    })
+    
+    .add("nestedHoriz", SC.ScrollView, {
+      layout: { width: 100, height: 440 },
+        
+      contentView: SC.ScrollView.design({
+        layout: { width: 200, height: 420 },
+        contentView: iv
+      })
+    })
+    
+    .add("nestedVert", SC.ScrollView, {
+      layout: { width: 440, height: 100 },
+        
+      contentView: SC.ScrollView.design({
+        layout: { width: 420, height: 200 },
+        contentView: iv
+      })
+    })
+    
+    .add("nestedVertInHoriz", SC.ScrollView, {
+      layout: { width: 100, height: 220 },
+        
+      contentView: SC.ScrollView.design({
+        layout: { width: 420, height: 200 },
+        contentView: iv
+      })
+    })
+    
+    .add("nestedHorizInVert", SC.ScrollView, {
+      layout: { width: 220, height: 100 },
+        
+      contentView: SC.ScrollView.design({
+        layout: { width: 200, height: 420 },
+        contentView: iv
+      })
+    })
+    
+    .add("disabled", SC.ScrollView, {
+      isEnabled: NO
+    })
+    
+    .add("verticalScrollerBottom",SC.ScrollView, {
+      contentView: iv,
+      hasHorizontalScroller : NO,
+      verticalScrollerBottom: 16,
[…]

### 2014-07-13 tests/clone_detector_tests/sproutcore/frameworks/runtime/tests/mixins/array.js

@@ -1,0 +1,81 @@
+// ==========================================================================
+// Project:   SproutCore Costello - Property Observing Library
+// Copyright: ©2006-2011 Strobe Inc. and contributors.
+//            Portions ©2008-2011 Apple Inc. All rights reserved.
+// License:   Licensed under MIT license (see license.js)
+// ==========================================================================
+
+// Unit test some standard SC.Array implementations.
+
+// ..........................................................
+// BUILT-IN ARRAY
+//
+
+sc_require('debug/test_suites/array');
+
+SC.ArraySuite.generate("built-in Array");
+
+// ..........................................................
+// DUMMY ARRAY (BASIC FAKE IMPLEMENTATION)
+//
+
+// Test that illustrates how to build a SproutCore Array-like
+// that correctly participates in KVO.
+var DummyArray = SC.Object.extend(SC.Array, {
+
+  // The SC.Array Interface requires a length property
+  length: 0,
+
+  content: null,
+
+  // The SC.Array mixin sends all mutations through replace.
+  // As a result, we can implement KVO notification in
+  // replace.
+  replace: function(idx, amt, objects) {
+    if (!this.content) { this.content = [] ; }
+
+    var len = objects ? objects.get('length') : 0;
+
+    // SC.Array implementations must call arrayContentWillChange
+    // before making mutations. This allows observers to perform
+    // operations based on the state of the Array before the
+    // change, such as reflecting removals.
+    this.arrayContentWillChange(idx, amt, len);
+    this.beginPropertyChanges() ;
+
+    // Mutate the underlying Array
+    this.content.replace(idx,amt,objects) ;
+
+    // Update the length property
+    this.set('length', this.content.length) ;
+
+    // Call the general-purpose enumerableContentDidChange
+    // Enumerable method.
+    this.enumerableContentDidChange(idx, amt, len - amt) ;
+    this.endPropertyChanges() ;
+
+    // SC.Array implementations must call arrayContentDidChange
+    // after making mutations. This allows observers to perform
+    // operations based on the mutation. For instance, a listener
+    // might want to reflect additions onto itself.
+    this.arrayContentDidChange(idx, amt, len);
+  },
+
+  // SC.Arrays must implement objectAt, which returns an object
+  // for a given index.
+  objectAt: function(idx) {
+    if (!this.content) { this.content = [] ; }
+    return this.content[idx] ;
+  }
+
+});
+
[…]

### 2014-07-13 tests/clone_detector_tests/sproutcore/frameworks/runtime/tests/mixins/enumerable/enumerable.js

@@ -1,0 +1,623 @@
+// ==========================================================================
+// Project:   SproutCore Costello - Property Observing Library
+// Copyright: ©2006-2011 Strobe Inc. and contributors.
+//            Portions ©2008-2011 Apple Inc. All rights reserved.
+// License:   Licensed under MIT license (see license.js)
+// ==========================================================================
+
+/*globals module test ok isObj equals expects */
+
+var enumerables ; // global variables
+
+var DummyEnumerable = SC.Object.extend( SC.Enumerable, {
+  
+  content: [],
+  
+  length: function() { return this.content.length; }.property(),
+  
+  objectAt: function(idx) { return this.content[idx]; },
+  
+  nextObject: function(idx) { return this.content[idx]; },
+  
+  // add support for reduced properties.
+  unknownProperty: function(key, value) {
+    var ret = this.reducedProperty(key, value) ;
+    if (ret === undefined) {
+      if (value !== undefined) this[key] = value ;
+      ret = value ;
+    }
+    return ret ;
+  },
+  
+  pushObject: function(object) {
+    this.content.push(object) ;
+    this.enumerableContentDidChange() ;
+  }
+  
+});
+
+var runFunc = function(a,b) { return ['DONE', a, b]; } ;
+var invokeWhileOK = function() { return "OK"; } ;
+var invokeWhileNotOK = function() { return "FAIL"; };
+var reduceTestFunc = function(prev, item, idx, e, pname) { return pname||'TEST'; } ;
+
+var CommonArray = [
+  {
+    first: "Charles", 
+    gender: "male", 
+    californian: NO, 
+    ready: YES, 
+    visited: "Prague", 
+    doneTravelling: NO, 
+    run: runFunc,
+    invokeWhileTest: invokeWhileOK,
+    balance: 1
+  },
+  
+  {
+    first: "Jenna", 
+    gender: "female", 
+    californian: YES, 
+    ready: YES, 
+    visited: "Prague", 
+    doneTravelling: NO, 
+    run: runFunc,
+    invokeWhileTest: invokeWhileOK,
+    balance: 2 
+  },
+  
+  {
+    first: "Peter", 
+    gender: "male", 
+    californian: NO, 
+    ready: YES, 
+    visited: "Prague", 
+    doneTravelling: NO, 
+    run: runFunc,
[…]

### 2014-07-13 tests/clone_detector_tests/sproutcore/frameworks/runtime/tests/mixins/observable/observable.js

@@ -1,0 +1,989 @@
+// ==========================================================================
+// Project:   SproutCore - JavaScript Application Framework
+// Copyright: ©2006-2011 Strobe Inc. and contributors.
+//            ©2008-2011 Apple Inc. All rights reserved.
+// License:   Licensed under MIT license (see license.js)
+// ==========================================================================
+// ========================================================================
+// SC.Observable Tests
+// ========================================================================
+/*globals module test ok isObj equals expects Namespace */
+
+var object, ObjectC, ObjectD, objectA, objectB ;
+
+// ..........................................................
+// GET()
+//
+
+module("object.get()", {
+
+  setup: function() {
+    object = SC.Object.create({
+
+      normal: 'value',
+      numberVal: 24,
+      toggleVal: true,
+
+      computed: function() { return 'value'; }.property(),
+
+      method: function() { return "value"; },
+
+      nullProperty: null,
+
+      unknownProperty: function(key, value) {
+        this.lastUnknownProperty = key ;
+        return "unknown" ;
+      }
+
+    });
+  }
+
+});
+
+test("should get normal properties", function() {
+  equals(object.get('normal'), 'value') ;
+});
+
+test("should call computed properties and return their result", function() {
+  equals(object.get("computed"), "value") ;
+});
+
+test("should return the function for a non-computed property", function() {
+  var value = object.get("method") ;
+  equals(SC.typeOf(value), SC.T_FUNCTION) ;
+});
+
+test("should return null when property value is null", function() {
+  equals(object.get("nullProperty"), null) ;
+});
+
+test("should call unknownProperty when value is undefined", function() {
+  equals(object.get("unknown"), "unknown") ;
+  equals(object.lastUnknownProperty, "unknown") ;
+});
+
+// ..........................................................
+// SC.GET()
+//
+module("SC.get()", {
+  setup: function() {
+    objectA = SC.Object.create({
+
+      normal: 'value',
+      numberVal: 24,
+      toggleVal: true,
+
+      computed: function() { return 'value'; }.property(),
+
+      method: function() { return "value"; },
+
+      nullProperty: null,
+
+      unknownProperty: function(key, value) {
+        this.lastUnknownProperty = key ;
+        return "unknown" ;
+      }
+
+    });
+
+    objectB = {
[…]

### 2014-07-13 tests/interpreter_mozilla_tests/safe.js

@@ -1,0 +1,10 @@
+/*******************************************************************************
+    Copyright (c) 2012, KAIST.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+function print(x) { _<>_print(x); }

### 2014-07-13 tests/interpreter_nightly_tests/sunspider_v0.9.1/access-fannkuch.js

@@ -1,0 +1,80 @@
+//function record(time) {
+//    document.getElementById("console").innerHTML = time + "ms";
+//    if (window.parent) {
+//        parent.recordResult(time);
+//    }
+//}
+
+//var _sunSpiderStartDate = new Date();
+
+/* The Great Computer Language Shootout
+   http://shootout.alioth.debian.org/
+   contributed by Isaac Gouy */
+
+function fannkuch(n) {
+   var check = 0;
+   var perm = Array(n);
+   var perm1 = Array(n);
+   var count = Array(n);
+   var maxPerm = Array(n);
+   var maxFlipsCount = 0;
+   var m = n - 1;
+
+   for (var i = 0; i < n; i++) perm1[i] = i;
+   var r = n;
+
+   while (true) {
+      // write-out the first 30 permutations
+      if (check < 30){
+         var s = "";
+         for(var i=0; i<n; i++) s += (perm1[i]+1).toString();
+         check++;
+      }
+
+      while (r != 1) { count[r - 1] = r; r--; }
+      if (!(perm1[0] == 0 || perm1[m] == m)) {
+         for (var i = 0; i < n; i++) perm[i] = perm1[i];
+
+         var flipsCount = 0;
+         var k;
+
+         while (!((k = perm[0]) == 0)) {
+            var k2 = (k + 1) >> 1;
+            for (var i = 0; i < k2; i++) {
+               var temp = perm[i]; perm[i] = perm[k - i]; perm[k - i] = temp;
+            }
+            flipsCount++;
+         }
+
+         if (flipsCount > maxFlipsCount) {
+            maxFlipsCount = flipsCount;
+            for (var i = 0; i < n; i++) maxPerm[i] = perm1[i];
+         }
+      }
+
+      while (true) {
+         if (r == n) return maxFlipsCount;
+         var perm0 = perm1[0];
+         var i = 0;
+         while (i < r) {
+            var j = i + 1;
+            perm1[i] = perm1[j];
+            i = j;
+         }
+         perm1[r] = perm0;
+
+         count[r] = count[r] - 1;
+         if (count[r] > 0) break;
+         r++;
+      }
+   }
+}
+
+var n = 7;
+var ret = fannkuch(n);
+
+ret
+
+//var _sunSpiderInterval = new Date() - _sunSpiderStartDate;
+
+//record(_sunSpiderInterval);

### 2014-07-13 tests/interpreter_nightly_tests/sunspider_v0.9.1/bitops-bits-in-byte.js

@@ -1,0 +1,35 @@
+//function record(time) {
+//    document.getElementById("console").innerHTML = time + "ms";
+//    if (window.parent) {
+//        parent.recordResult(time);
+//    }
+//}
+
+//var _sunSpiderStartDate = new Date();
+
+// Copyright (c) 2004 by Arthur Langereis (arthur_ext at domain xfinitegames, tld com)
+
+
+// 1 op = 2 assigns, 16 compare/branches, 8 ANDs, (0-8) ADDs, 8 SHLs
+// O(n)
+function bitsinbyte(b) {
+  var m = 1, c = 0;
+  while(m<0x100) {
+    if(b & m) c++;
+    m <<= 1;
+  }
+  return c;
+}
+
+function TimeFunc(func) {
+  var x, y, t;
+  //for(var x=0; x<350; x++)
+  for(var y=0; y<256; y++) _<>_print(func(y));
+}
+
+TimeFunc(bitsinbyte);
+
+
+//var _sunSpiderInterval = new Date() - _sunSpiderStartDate;
+
+//record(_sunSpiderInterval);

### 2014-07-13 tests/interpreter_tests/compare.js

@@ -1,0 +1,31 @@
+var arr1 = [1, 2, 3], arr1_pt = arr1;
+var arr2 = [1, 2, 3];
+
+_<>_print(1 < 2);
+_<>_print(1 <= 2);
+_<>_print(1 > 2);
+_<>_print(1 >= 2);
+_<>_print(1 == 2);
+_<>_print(1 != 2);
+_<>_print("123" < "456");
+_<>_print("123" >= "456");
+_<>_print("123" == "123");
+_<>_print("123" != "123");
+_<>_print(" ");
+
+_<>_print(1 == "1");
+_<>_print(1 != "1");
+_<>_print(1 === "1");
+_<>_print(1 !== "1");
+_<>_print("123" === "123");
+_<>_print("123" !== "123");
+_<>_print(" ");
+
+_<>_print(arr1 == arr1_pt);
+_<>_print(arr1 == arr2);
+_<>_print(arr2 == arr1_pt);
+_<>_print(arr1 === arr1_pt);
+_<>_print(arr1 === arr2);
+_<>_print(arr2 === arr1_pt);
+
+"PASS"

### 2014-07-13 tests/interpreter_tests/continue.js

@@ -1,0 +1,9 @@
+var x,y;
+var out = 123;
+lab1: for(x=0; x<10; x++) {
+    lab2: for(y=0; y<10; y++) {
+        continue lab1;
+    }
+    out = 456;
+}
+out;

### 2014-07-13 tests/interpreter_tests/defaultValue1.js

@@ -1,0 +1,3 @@
+a = { toString: function() { return "ABC"; }, substring: String.prototype.substring }
+_<>_print(a.substring(0))
+"PASS"

### 2014-07-13 tests/interpreter_tests/eval-2.js

@@ -1,0 +1,5 @@
+var x = 'global';
+_<>_print('x in '+x);
+f = function() { var x = 'function'; _<>_print('x in '+x); eval("_<>_print('x in '+x)"); }
+f();
+"PASS"

### 2014-07-13 tests/interpreter_tests/function3.js

@@ -1,0 +1,18 @@
+function func1()
+{
+	_<>_print("func1");
+	return "func1";
+}
+
+function func2()
+{
+	_<>_print("func2");
+	return "func2";
+}
+
+func1();
+// This program is terminated right after that the func1() returns.
+// The codes below are not executed.
+func2();
+
+"PASS";

### 2014-07-13 tests/interpreter_tests/object-freeze.js

@@ -1,0 +1,19 @@
+a = { x: 0 }
+_<>_print(a.x)
+_<>_print(a.y)
+a.x = 1
+a.y = 2
+_<>_print(a.x)
+_<>_print(a.y)
+delete a.y
+_<>_print(a.x)
+_<>_print(a.y)
+Object.freeze(a)
+a.x = 3
+a.y = 4
+_<>_print(a.x)
+_<>_print(a.y)
+delete a.x
+_<>_print(a.x)
+_<>_print(a.y)
+"PASS"

### 2014-07-13 tests/interpreter_tests/object-hasOwnProperty.js

@@ -1,0 +1,9 @@
+p = { a: 42 }
+f = function() { this.b = 42; }
+f.prototype = p
+o = new f()
+_<>_print("a: "+o.a)
+_<>_print(o.hasOwnProperty("a"))
+_<>_print("b: "+o.b)
+_<>_print(o.hasOwnProperty("b"))
+"PASS"

### 2014-07-13 tests/interpreter_tests/with7.js

@@ -1,0 +1,12 @@
+z = 8
+function f() {
+  var x = 5
+  var y = 42
+  with ({y : 3}) {
+    z = 38
+    _<>_print(x)
+    _<>_print(y)
+    _<>_print(z)
+  }
+}
+f()

### 2014-07-13 tests/tizen_tests/AddrBook_find1.js

@@ -1,0 +1,31 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+var __result1, __result2;
+
+var addressbook;
+
+// Define the error callback for all the asynchronous calls
+function errorCB(err) {
+  __result2 = err.name;
+}
+
+
+function contactsFoundCB(contacts) {
+  __result1 = contacts[0].name.firstName;
+}
+
+// Get default address book.
+addressbook = tizen.contact.getDefaultAddressBook();
+
+var filter = new tizen.AttributeFilter('name.firstName', 'CONTAINS', 'Chris');
+addressbook.find(contactsFoundCB, errorCB, filter);
+
+var __expect1 = "Chris";
+var __expect2 = "NotFoundError";

### 2014-07-13 tests/tizen_tests/BTAdapter_getDevice1.js

@@ -1,0 +1,29 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+var __result1, __result2;
+var adapter = tizen.bluetooth.getDefaultAdapter();
+function onBluetoothsetPowered() {
+   adapter.getDevice("35:F4:59:D1:7A:03", gotDeviceInfo, onError);
+}
+
+function gotDeviceInfo(device) {
+   __result1 = device.name;
+}
+
+function onError(e) {
+    __result2 = e.name;
+}
+
+adapter.setPowered(true, onBluetoothsetPowered);
+
+
+
+
+var __expect1 = "bluetooth";
+var __expect2 = "UnknownError";

### 2014-07-13 tests/tizen_tests/NFCAdapter_unsetTagListener1.js

@@ -1,0 +1,12 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+var adapt = tizen.nfc.getDefaultAdapter();
+
+var __result1 = adapt.unsetTagListener();
+var __expect1 = undefined;

### 2014-07-13 tests/tizen_tests/SQLDataCtrlConsum_update1.js

@@ -1,0 +1,27 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+var __result1, __result2, __result3;
+function successcb(id){
+  __result1 = id;
+}
+function errorcb(id, error){
+  __result2 = id;
+  __result3 = error.name;
+}
+var rowData = {
+     columns : ["WORD", "WORD_DESC"] ,
+     values  : ["'tizen1'", "'samsung platform'"]
+};
+var globalSQLConsumer = tizen.datacontrol.getDataControlConsumer("http://tizen.org/datacontrol/provider/DictionaryDataControlProvider", "Dictionary", "SQL");
+globalSQLConsumer.update(1, rowData, "WORD='tizen1'", successcb, errorcb);
+
+
+var __expect1 = 1;
+var __expect2 = 1;
+var __expect3 = "InvalidValuesError"

### 2014-07-13 tests/tizen_tests/SimpleCoordi_new1.js

@@ -1,0 +1,14 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+var coordi = new tizen.SimpleCoordinates(1.4, 2.3);
+
+var __result1 = coordi.latitude;
+var __expect1 = 1.4;
+var __result2 = coordi.longitude;
+var __expect2 = 2.3;

### 2014-07-13 tests/tizen_tests/SyncProfInfo_new1.js

@@ -1,0 +1,36 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+// Creates a sync info
+var syncInfo = new tizen.SyncInfo("http://example.com/sync", "myId", "myPassword", "MANUAL", "TWO_WAY");
+// Syncs both contacts and events
+var contactInfo = new tizen.SyncServiceInfo(true, "CONTACT", "serverContact");
+var eventInfo = new tizen.SyncServiceInfo(true, "EVENT", "serverEvent");
+var serviceInfo = [contactInfo, eventInfo];
+var profile = new tizen.SyncProfileInfo("MyProfile", syncInfo, serviceInfo);
+
+var __result1 = profile.profileId;
+var __expect1 = null
+var __result2 = profile.profileName;
+var __expect2 = "MyProfile"
+var __result3 = profile.syncInfo.url;
+var __expect3 = "http://example.com/sync"
+var __result4 = profile.syncInfo.id;
+var __expect4 = "myId"
+var __result5 = profile.syncInfo.password;
+var __expect5 = "myPassword"
+var __result6 = profile.syncInfo.mode;
+var __expect6 = "MANUAL"
+var __result7 = profile.syncInfo.type;
+var __expect7 = "TWO_WAY"
+var __result8 = profile.syncInfo.interval;
+var __expect8 = null
+var __result9 = profile.serviceInfo[0].serviceType;
+var __expect9 = "CONTACT"
+var __result10 = profile.serviceInfo[1].serviceType;
+var __expect10 = "EVENT"

### 2014-07-13 tests/tizen_tests/TZDate_getTimezoneAbbreviation1.js

@@ -1,0 +1,12 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+var a = new tizen.TZDate(2013, 6, 27, 16, 32, 22, 10, "GMT");
+var __result1 = a.getTimezoneAbbreviation();
+var __expect1 = "a";

### 2014-07-13 tests/tizen_tests/TZDate_setDate1.js

@@ -1,0 +1,12 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+var a = new tizen.TZDate(2013, 6, 27, 16, 32, 22, 10, "GMT");
+var __result1 = a.setDate(3);
+var __expect1 = undefined;

### 2014-07-13 tests/tizen_tests/TZDate_toLocaleString1.js

@@ -1,0 +1,12 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+var a = new tizen.TZDate(2013, 6, 27, 16, 32, 22, 10, "GMT");
+var __result1 = a.toLocaleString();
+var __expect1 = "a";

### 2014-07-13 tests/tizen_tests/TZDate_toTimezone1.js

@@ -1,0 +1,12 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+var a = new tizen.TZDate(2013, 6, 27, 16, 32, 22, 10, "GMT");
+var __result1 = typeof a.toTimezone("a");
+var __expect1 = "object";

### 2014-07-13 tests/tizen_tests/bookmark_get1.js

@@ -1,0 +1,18 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+ var bmitem = new tizen.BookmarkItem("tizen", "https://www.tizen.org");
+ tizen.bookmark.add(bmitem);
+ var allBookmarks = tizen.bookmark.get(null);
+
+ var __result1 = allBookmarks[0].parent;
+ var __expect1 = null
+ var __result2 = allBookmarks[0].title;
+ var __expect2 = "tizen"
+ var __result3 = allBookmarks[0].url;
+ var __expect3 = "https://www.tizen.org"

### 2014-07-13 tests/tizen_tests/bookmark_remove1.js

@@ -1,0 +1,12 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+ var bmitem = new tizen.BookmarkItem("tizen", "https://www.tizen.org");
+ tizen.bookmark.add(bmitem);
+ var __result1 = tizen.bookmark.remove();
+ var __expect1 = undefined;

### 2014-07-13 tests/tizen_tests/contact_getUnifiedAddressBook1.js

@@ -1,0 +1,16 @@
+/*******************************************************************************
+    Copyright (c) 2013, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+var addrbook = tizen.contact.getUnifiedAddressBook();
+
+var __result1 = addrbook.id;
+var __expect1 = null
+var __result2 = addrbook.name;
+var __expect2 = "aa"
+var __result3 = addrbook.readOnly;
+var __expect3 = false

### 2014-07-13 tests/ts_tests/jasmine.d.ts

@@ -1,0 +1,392 @@
+﻿// Type definitions for Jasmine 1.2
+// Project: http://pivotal.github.com/jasmine/
+// Definitions by: Boris Yankov <https://github.com/borisyankov/>
+// DefinitelyTyped: https://github.com/borisyankov/DefinitelyTyped
+
+
+declare function describe(description: string, specDefinitions: () => void): void;
+declare function xdescribe(description: string, specDefinitions: () => void): void;
+
+declare function it(expectation: string, assertion: () => void): void;
+declare function it(expectation: string, assertion: (done: (err?: any) => void) => void): void;
+declare function xit(expectation: string, assertion: () => void): void;
+
+declare function beforeEach(action: () => void): void;
+declare function afterEach(action: () => void): void;
+
+declare function expect(spy: Function): jasmine.Matchers;
+//declare function expect(spy: jasmine.Spy): jasmine.Matchers;
+declare function expect(actual: any): jasmine.Matchers;
+
+declare function spyOn(object: any, method: string): jasmine.Spy;
+
+declare function runs(asyncMethod: Function): void;
+declare function waitsFor(latchMethod: () => boolean, failureMessage?: string, timeout?: number): void;
+declare function waits(timeout?: number): void;
+
+declare module jasmine {
+
+    var Clock: Clock;
+
+    function any(aclass: any): Any;
+    function objectContaining(sample: any): ObjectContaining;
+    function createSpy(name: string, originalFn?: Function): Spy;
+    function createSpyObj(baseName: string, methodNames: any[]): any;
+    function createSpyObj<T>(baseName: string, methodNames: any[]): T;
+    function pp(value: any): string;
+    function getEnv(): Env;
+
+    interface Any {
+
+        new (expectedClass: any): any;
+
+        jasmineMatches(other: any): boolean;
+        jasmineToString(): string;
+    }
+
+    interface ObjectContaining {
+        new (sample: any): any;
+
+        jasmineMatches(other: any, mismatchKeys: any[], mismatchValues: any[]): boolean;
+        jasmineToString(): string;
+    }
+
+    interface Block {
+
+        new (env: Env, func: SpecFunction, spec: Spec): any;
+
+        execute(onComplete: () => void): void;
+    }
+
+    interface WaitsBlock extends Block {
+        new (env: Env, timeout: number, spec: Spec): any;
+    }
+
+    interface WaitsForBlock extends Block {
[…]

### 2014-07-13 tests/ts_tests/jqrangeslider.d.ts

@@ -1,0 +1,74 @@
+// Type definitions for jQRangeSlider 4.2.8
+// Project: http://ghusse.github.com/jQRangeSlider
+// Definitions by: Dániel Tar https://github.com/qcz
+// Definitions: https://github.com/borisyankov/DefinitelyTyped
+
+/// <reference path="../jquery/jquery.d.ts"/>
+/// <reference path="../jqueryui/jqueryui.d.ts"/>
+
+interface JQRangeSliderNumericRange {
+    min?: number;
+    max?: number;
+}
+
+interface JQRangeSliderDateRange {
+    min?: Date;
+    max?: Date;
+}
+
+interface JQRangeSliderRangeLength {
+    min?: any;
+    max?: any;
+}
+
+interface JQRangeSliderDateSteps {
+    years?: number;
+    months?: number;
+    weeks?: number;
+    days?: number;
+    hours?: number;
+    minutes?: number;
+    seconds?: number;
+}
+
+interface JQRangeSliderOptions {
+    wheelMode?: string; // function of the wheel, "zoom", "scroll" or null
+    wheelSpeed?: number; // speed of the wheel scrolling
+    arrows?: boolean; // hide the arrows or not
+    valueLabels?: string; // when to show value labels: "show" (always), "hide" (never) and "change" (only if slider changed)
+    durationIn?: number; // fade in length when displaying value labels (only when valueLabels = "change")
+    durationOut?: number; // fade out length when displaying value labels (only when valueLabels = "change")
+    delayOut?: number; // duration labels are shown after the user changed its values (only when valueLabels = "change")
+    range?: JQRangeSliderRangeLength; // lets you specify minimum and/or maximum range length
+}
+
+interface JQNumericRangeSliderOptions extends JQRangeSliderOptions {
+    bounds?: JQRangeSliderNumericRange; // min and max values of the slider
+    defaultValues?: JQRangeSliderNumericRange; // values selected by default on construction
+    formatter?: (integer) => string; // customize displayed label text
+    step?: number; // allows to customize values rounding, and graphically render this rounding
+}
+
+interface JQDateRangeSliderOptions extends JQRangeSliderOptions {
+    bounds?: JQRangeSliderDateRange; // min and max values of the slider
+    defaultValues?: JQRangeSliderDateRange; // values selected by default on construction
+    formatter?: (Date) => string; // customize displayed label text
[…]

### 2014-07-13 tests/ts_tests/select2.d.ts

@@ -1,0 +1,147 @@
+// Type definitions for Select2 3.2
+// Project: http://ivaynberg.github.com/select2/
+// Definitions by: Boris Yankov <https://github.com/borisyankov/>
+// Definitions: https://github.com/borisyankov/DefinitelyTyped
+
+
+/// <reference path="../jquery/jquery.d.ts"/>
+
+interface Select2QueryOptions {
+    term?: string;
+    page?: number;
+    context?: any;
+    callback?: (result: { results: any; more?: boolean; context?: any; }) => void;
+}
+
+interface AjaxFunction {
+    (settings: JQueryAjaxSettings): JQueryXHR;
+    (url: string, settings?: JQueryAjaxSettings): JQueryXHR;
+}
+
+interface Select2AjaxOptions {
+    transport?: AjaxFunction;
+    /**
+    * Url to make request to, Can be string or a function returning a string.
+    */
+    url?: any;
+    dataType?: string;
+    quietMillis?: number;
+    data?: (term: string, page: number, context: any) => any;
+    results?: (term: any, page: number, context: any) => any;
+}
+
+interface IdTextPair {
+    id: any;
+    text: string;
+}
+
+interface Select2Options {
+    width?: string;
+    dropdownAutoWidth?: boolean;
+    minimumInputLength?: number;
+    minimumResultsForSearch?: number;
+    maximumSelectionSize?: number;
+    placeholder?: string;
+    separator?: string;
+    allowClear?: boolean;
+    multiple?: boolean;
+    closeOnSelect?: boolean;
+    openOnEnter?: boolean;
+    id?: (object: any) => string;
+    matcher?: (term: string, text: string, option: any) => boolean;
+    formatSelection?: (object: any, container: JQuery, escapeMarkup:(markup: string) => string) => string;
+    formatResult?: (object: any, container: JQuery, query: any, escapeMarkup: (markup: string) => string) => string;
+    formatResultCssClass?: (object: any) => string;
+    formatNoMatches?: (term: string) => string;
+    formatSearching?: () => string;
+    formatInputTooShort?: (term: string, minLength: number) => string;
+    formatSelectionTooBig?: (maxSize: number) => string;
+    formatLoadMore?: (pageNumber: number) => string;
+    createSearchChoice?: (term: string, data: any) => any;
+    initSelection?: (element: JQuery, callback: (data: any) => void ) => void;
+    tokenizer?: (input: string, selection: any[], selectCallback: () => void , options: Select2Options) => string;
+    tokenSeparators?: string[];
[…]

### 2014-07-13 tests/typing_tests/TAJS_micro/test05.js

@@ -1,0 +1,9 @@
+function foo(x) {
+	return x + 777;
+}
+
+var q = foo(1234) * 5678;
+
+//assert (q === 11418458);
+var __result1 = q;  // for SAFE
+var __expect1 = 11418458;  // for SAFE

### 2014-07-13 tests/typing_tests/TAJS_micro/test103.js

@@ -1,0 +1,21 @@
+var x = {c:42}
+var y1 = x.a;
+var y2 = x["b"]
+var y3 = x.c
+var y4 = x["c"]
+
+//dumpValue(y1)
+var __result1 = y1;  // for SAFE
+var __expect1 = undefined;  // for SAFE
+
+//dumpValue(y2)
+var __result2 = y2;  // for SAFE
+var __expect2 = undefined;  // for SAFE
+
+//dumpValue(y3)
+var __result3 = y3;  // for SAFE
+var __expect3 = 42.0;  // for SAFE
+
+//dumpValue(y4)
+var __result4 = y4;  // for SAFE
+var __expect4 = 42.0;  // for SAFE

### 2014-07-13 tests/typing_tests/TAJS_micro/test59.js

@@ -1,0 +1,41 @@
+function f(x) {
+	if (x)
+	  return "a";
+	else
+	  return "b";
+}
+
+var a = f(true) + f(false);
+//dumpValue(a);
+//assert(a === "ab");
+var __result1 = a;  // for SAFE
+var __expect1 = "ab";  // for SAFE
+
+var x = {};
+x[a] = "hello";
+
+//dumpObject(x);
+
+//dumpValue(x.dfg);
+var __result2 = x.dfg;  // for SAFE
+var __expect2 = undefined;  // for SAFE
+
+//dumpValue(x[1]);
+var __result3 = x[1];  // for SAFE
+var __expect3 = undefined;  // for SAFE
+
+//dumpValue(x[2]);
+var __result4 = x[2];  // for SAFE
+var __expect4 = undefined;  // for SAFE
+
+//dumpValue(x.ab);
+var __result5 = x.ab;  // for SAFE
+var __expect5 = "hello";  // for SAFE
+
+//assert(x.dfg === undefined);
+//assert(x[1] === undefined);
+//assert(x[2] === undefined);
+//assert(x.ab === "hello");
+
+
+

### 2014-07-13 tests/typing_tests/semantics/alloc2.js

@@ -1,0 +1,22 @@
+/*******************************************************************************
+    Copyright (c) 2012, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ***************************************************************************** */
+
+function Class(n) {
+	this.p = n;
+}
+
+var x = new Class(123);
+
+var y = new Class([456]);
+
+var __result1 = x.p;
+var __expect1 = 123;
+
+var __result2 = (y.p)[0];
+var __expect2 = 456;

### 2014-07-13 tests/typing_tests/semantics/builtin_Math_cos1.js

@@ -1,0 +1,11 @@
+/*******************************************************************************
+    Copyright (c) 2012, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ***************************************************************************** */
+
+var __result1 = Math.cos(NaN);
+var __expect1 = NaN;

### 2014-07-13 tests/typing_tests/semantics/builtin_array16.js

@@ -1,0 +1,19 @@
+/*******************************************************************************
+    Copyright (c) 2012, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+var x = [1,2,3,4,5];
+
+var __result1 = x.slice(2,4).toString();
+var __expect1 = "3,4";
+
+var __result2 = x.slice(4,2).toString();
+var __expect2 = "";
+
+var __result3 = x.slice(-3,-1).toString();
+var __expect3 = "3,4";

### 2014-07-13 tests/typing_tests/semantics/exprStmt3.js

@@ -1,0 +1,13 @@
+/*******************************************************************************
+    Copyright (c) 2012, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+NaN = 3;
+
+var __result1 = NaN;
+var __expect1 = NaN;

### 2014-07-13 tests/typing_tests/semantics/objEquals3.js

@@ -1,0 +1,39 @@
+/*******************************************************************************
+    Copyright (c) 2012, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+var o1 = {a:1};
+var o2;
+
+
+if (__TOP) o2 = o1; else o2 = {a:2};
+
+var __result1 = o1 == o2;
+var __expect1 = true;
+
+var __result2 = o1 == o2;
+var __expect2 = false;
+
+var __result3 = o1 === o2;
+var __expect3 = true;
+
+var __result4 = o1 === o2;
+var __expect4 = false;
+
+
+var __result5 = o1 != o2;
+var __expect5 = false;
+
+var __result6 = o1 != o2;
+var __expect6 = true;
+
+var __result7 = o1 !== o2;
+var __expect7 = false;
+
+var __result8 = o1 !== o2;
+var __expect8 = true;

### 2014-07-13 tests/typing_tests/semantics/store8.js

@@ -1,0 +1,27 @@
+/*******************************************************************************
+    Copyright (c) 2012, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ***************************************************************************** */
+
+var o1 = { };
+var p1;
+if (__TOP) {
+    p1 = "A";
+} else {
+    p1 = "B";
+}
+
+o1[p1] = 123;
+
+var __result1 = o1["A"];
+var __expect1 = 123;
+
+var __result2 = o1["B"];
+var __expect2 = 123;
+
+var __result3 = o1[__TOP];
+var __expect3 = 123;

### 2014-07-13 tests/typing_tests/semantics/toNumber2.js

@@ -1,0 +1,15 @@
+/*******************************************************************************
+    Copyright (c) 2012, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ***************************************************************************** */
+var x = true;
+
+var __result1 = x--;
+var __expect1 = 1;
+
+var __result2 = x;
+var __expect2 = 0;

### 2014-07-13 tests/typing_tests/semantics/while1.js

@@ -1,0 +1,22 @@
+/*******************************************************************************
+    Copyright (c) 2012, S-Core.
+    All rights reserved.
+
+    Use is subject to license terms.
+
+    This distribution may include materials developed by third parties.
+ ******************************************************************************/
+
+var x = 123;
+
+while(__TOP) {
+	x = 456;
+	break;
+	x = 789;
+}
+
+var __result1 = x;
+var __expect1 = 123;
+
+var __result2 = x;
+var __expect2 = 456;

### 2016-05-05 doc/overview.tex
Add the SAFE document till AST2IR

\chapter{Overview}

The prevalent uses of JavaScript in web programming have revealed
security vulnerability issues of JavaScript applications,
which emphasizes the need for JavaScript analyzers to detect such issues.
Recently, researchers have proposed several analyzers of JavaScript programs
and some web service companies have developed various JavaScript engines.
However, unfortunately, most of the tools are not documented well,
thus it is very hard to understand and modify them.
Or, such tools are often not open to the public.

In this specification, we present formal specifications and implementation
of \safe, a scalable analysis framework for ECMAScript, developed for the JavaScript research community.
To make it more amenable for other researchers to use our framework,
we formally define three kinds of intermediate representations for JavaScript
used in the framework,
and we provide formal specifications of translation between them.
To support a variety of program analyses in various compilation phases,
we design the framework to be as flexible, scalable, and pluggable as possible.
Finally, our framework is publicly available:
\begin{center}
\url{http://safe.kaist.ac.kr}
\end{center}
Our project has been supported by
Korea Ministry of Education, Science and Technology (MEST),
National Research Foundation of Korea (NRF),
Samsung Electronics,
S-Core,
Microsoft Research Asia, and
Google.

Projects and colleagues using \safe\ include:
\begin{itemize}
\item K Framework @ University of Illinois at Urbana-Champaign
\item Ken Cheung @ HKUST
\item ROSAEC @ Seoul National University
\item Tizen @ Linux Foundation
\item Web-based Vulnerability Detection @ Oracle Labs
\end{itemize}
Publications related to \safe\ include:
\begin{itemize}
\item Battles with false positives in static analysis of JavaScript web applications in the wild (ICSE SEIP 2016)
\item Static analysis of JavaScript web applications in the wild via practical DOM modeling (ASE 2015)
\item Practically tunable static analysis framework for large-scale JavaScript applications (ASE 2015)
\item Development nature matters: An empirical study of code clones in JavaScript applications (EMSE 2015)
\item Scalable and precise static analysis of JavaScript applications via loop-sensitivity (ECOOP 2015)
\item {\sf SAFE$_{\mbox{\sf\scriptsize WAPI}}$}: Web API misuse detector for web applications (FSE 2014)
\item All about the \texttt{with} statement in JavaScript: Removing \texttt{with} statements in JavaScript applications (DLS 2013)
\item Formal specification of a JavaScript module system (OOPSLA 2012)
\item \safe: Formal specification and implementation of a scalable analysis framework for ECMAScript (FOOL 2012)
\end{itemize}

### 2016-05-05 doc/safe-ir.tex
Add the SAFE document till AST2IR

\chapter{IR}
\small
\[
\begin{array}{llll}
\ir\pgm & ::= & \ir\stmt^* & \mtt{IRRoot(val fds:~List[IRFunDecl], val vds:~List[IRVarStmt],}\\
&&&\mtt{\phantom{IRRoot(}val irs:~List[IRStmt])}\\

\ir\stmt & ::= & \irid \ \verb+=+ \ \ir\expr &
 \mtt{IRExprStmt(val lhs:~IRId, val right:~IRExpr, val ref:~Boolean)}\\

&\mid& \irid \ \verb+=+ \ {\sf delete}\ \irid
& \mtt{IRDelete(val lhs:~IRId, val id:~IRId)}\\

 &\mid& \irid \ \verb+=+ \ {\sf delete}\ \irid\verb+[+\irid\verb+]+
 & \mtt{IRDeleteProp(val lhs:~IRId, val obj:~IRId, val index:~IRExpr)}\\

 &\mid& \irid\verb+[+\irid\verb+] =+ \ \irexpr & \mtt{IRStore(val obj:~IRId, val index:~IRExpr, val rhs:~IRExpr)}\\
 &\mid& \irid \ \verb+=+ \ \verb+{+ (\ir\member\verb+,+)^* \verb+}+
 & \mtt{IRObject(val lhs:~IRId, val members:~List[IRMember],}\\
&&&\mtt{\phantom{IRObject(}val proto:~Option[IRId])}\\
 &\mid& \irid \ \verb+=+ \ \verb+[+ (\irexpr\verb+,+)^* \verb+]+ & \mtt{IRArray(val lhs:~IRId, val elements:~List[Option[IRExpr]])}\\
&&&\mtt{IRArgs(val lhs:~IRId, val elements:~List[Option[IRExpr]])}\\

 &\mid& \irid \ \verb+=+ \ \irid\verb+(+\irid\verb+,+\irid\verb+)+
& \mtt{IRCall(val lhs:~IRId, val fun:~IRId, val thisB:~IRId,}\\
&&&\mtt{\phantom{IRCall(}val args:~IRId)}\\
 &\mid& \irid \ \verb+=+ \ \irid\verb+(+\irid(\verb+,+\irid)^?\verb+)+
& \mtt{IRInternalCall(val lhs:~IRId, val fun:~IRId, val first:~IRExpr,}\\
&&&\mtt{\phantom{IRInternalCall(}val second:~Option[IRId])}\\
&&&{\inblue \mtt{toObject}, \mtt{toNumber}, \mtt{isObject},
\mtt{getBase}, \mtt{iteratorInit},}\\
&&&{\inblue \mtt{iteratorHasNext}, \mtt{iteratorKey}}\\

 &\mid& \irid \ \verb+=+ \ {\sf new}\ \irid\verb+(+(\irid\verb+,+)^*\verb+)+
 & \mtt{IRNew(val lhs:~IRId, val fun:~IRId, val args:~List[IRId])}\\
 &\mid& \irid \ \verb+=+ \ {\sf function} \ \ir{f} \verb+(+\irid\verb+,+\irid\verb+) {+ \ir\stmt^* \verb+}+
& \mtt{IRFunExpr(val lhs:~IRId, val fun:~IRFunctional)}\\
&&&\mtt{IRFunctional(val fromSource:~Boolean, val name:~IRId,}\\
&&&\mtt{\phantom{IRFunctional(}val params:~List[IRId], val args:~List[IRStmt],}\\
&&&\mtt{\phantom{IRFunctional(}val fds:~List[IRFunDecl],}\\
&&&\mtt{\phantom{IRFunctional(}val vds:~List[IRVarStmt], val body:~List[IRStmt])}\\

 &\mid& {\sf function} \ \ir{f} \verb+(+\irid\verb+,+\irid\verb+) {+ \ir\stmt^* \verb+}+
 & \mtt{IRFunDecl(val ftn:~IRFunctional)}\\

 &\mid& \irid \ \verb+=+ \ {\sf eval}\verb+(+\ir\expr\verb+)+ & \mtt{IREval(val lhs:~IRId, val arg:~IRExpr)}\\
 &\mid& {\sf break} \ \irid & \mtt{IRBreak(val label:~IRId)}\\
 &\mid& {\sf return} \ \irexpr^?& \mtt{IRReturn(val expr:~Option[IRExpr])}\\
 &\mid& {\sf with} \ \verb+(+\irid\verb+)+ \ \ir\stmt & \mtt{IRWith(val id:~IRId, val stmt:~IRStmt)}\\
 & \mid & \ir{l} \; \verb+: {+ \; \ir\stmt \; \verb+}+
 & \mtt{IRLabelStmt(val label:~IRId, val stmt:~IRStmt)}\\
 &\mid& {\sf var} \ \irid& \mtt{IRVarStmt(val lhs:~IRId, val fromParam:~Boolean)}\\

 &\mid& {\sf throw} \ \irexpr& \mtt{IRThrow(val expr:~IRExpr)}\\
 &\mid& {\ir\stmt}^*& \mtt{IRSeq(val stmts:~List[IRStmt])}\\
 &\mid& {\sf if} \ \verb+(+\irexpr\verb+)+\ {\sf then} \ \ir\stmt \ ({\sf else} \ \ir\stmt)^?
& \mtt{IRIf(val expr:~IRExpr, val trueB:~IRStmt,}\\
&&&\mtt{\phantom{IRIf(}val falseb:~Option[IRStmt])}\\

 &\mid& {\sf while} \ \verb+(+\irexpr\verb+)+\ \ir\stmt& \mtt{IRWhile(val cond:~IRExpr, val body:~IRStmt)}\\
 &\mid& {\sf try} \ \verb+{+ \ir\stmt \verb+}+ \
({\sf catch} \ \verb+(+\irid\verb+){+ \ir\stmt \verb+}+)^?
& \mtt{IRTry(val body:~IRStmt, val name:~Option[IRId],}\\
&& \phantom{{\sf try} \{ \ir\stmt \}\ \ \ }
({\sf finally} \ \verb+{+ \ir\stmt \verb+}+)^?
&\mtt{\phantom{IRTry(}val catchB:~Option[IRStmt], finallyB:~Option[IRStmt])}\\
&\mid& \open {\ir\stmt}^* \close & \mtt{IRStmtUnit(List[IRStmt] stmts)}\\
\end{array}
\]

\[
\begin{array}{llll}
\ir\expr &::=&
 \irexpr \ \inop \irexpr & \mtt{IRBin(val first:~IRExpr, val op:~IROp, val second:~IRExpr)}\\
 &\mid& \preop \irexpr & \mtt{IRUn(val op:~IROp, val expr:~IRExpr)}\\
 &\mid& \irid\verb+[+\ir\expr\verb+]+ & \mtt{IRLoad(val obj:~IRId, val index:~IRExpr)}\\
 &\mid& \irid& \mtt{IRUserId(val global:~Boolean, val isWith:~Boolean)}\\
 &\mid& \newvar{x}& \mtt{IRTmpId(val global:~Boolean)}\\
 &\mid& \ir\num & \mtt{IRNumber(val text:~String, val num:~Double)}\\
 &\mid& \ir\str & \mtt{IRString(val str:~String)}\\
 &\mid& {\sf true} & \mtt{IRBool(val bool:~Boolean)}\\
 &\mid& {\sf false} & \mtt{IRBool(val bool:~Boolean)}\\
 &\mid& {\sf undefined} & \mtt{IRUndef()}\\
 &\mid& {\sf null} & \mtt{IRNull()}\\
 &\mid& {\sf this} & \mtt{IRThis()}\\\\

\ir\member &::=& \irid \ \verb+:+ \ \irexpr & \mtt{IRField(val prop:~IRId, val expr:~IRExpr)}\\
 &\mid& {\tt get}\ \ir{f} \verb+(+\irid\verb+,+\irid\verb+) {+ \ir\stmt^* \verb+}+
 &\mtt{IRGetProp(val ftn:~IRFunctional)}\\
 &\mid& {\tt set}\ \ir{f} \verb+(+\irid\verb+,+\irid\verb+) {+ \ir\stmt^* \verb+}+
 &\mtt{IRSetProp(val ftn:~IRFunctional)}\\

\end{array}
\]

Assumptions and notations:
\begin{itemize}
\item Functions and variables are hoisted to their closest enclosing functions
or the top level via {\tt Hoister}.
\item Identifiers and labels that exist in the source program,
except when they appear at top level or within the {\tt with} statement,
are already disambiguated via {\tt Disambiguator},
so that they have unique names.
\item We use $\env$ to disambiguate the generated labels and temporary variables in the AST to IR translation.
For the presentation brevity, we simply add the newly generated names to $\env$.
\begin{itemize}
\item In the actual implementation, we need to create a unique id for each generated name and
add the binding information from the general name to the unique id to $\env$.
For example, when we say ``$\env; \newvar{break}$'',
we actually create a unique id for $\newvar{break}$, say $\newvar{break}_{42}$, and add it to $\env$ as $\env; \newvar{break} \mapsto \newvar{break}_{42}$.
When we look up the environment by $\env(\newvar{break})$, the unique $\newvar{break}_{42}$ is returned.
\item In the scope when the generated name is created, we don't add it to the environment but use the unique id instead of the general name.
For example, when we say ``$\newvar{eq}\ \verb+=+\ \env(\newvar{val}) \verb+===+ \newvar{break};$'',
we create a unique id for \newvar{eq}, say $\newvar{eq}_{910157}$, and it is acually
``$\newvar{eq}_{910157}\ \verb+=+\ \env(\newvar{val}) \verb+===+ \newvar{break}_{42};$''.
\item To be clear, we use blue for the binding sites of such names and red for the use sites of such names.
\end{itemize}
\item We denote a list as a possibly empty, semicolon-separated sequence, enclosed by $\langle$ and $\rangle$.
\item We denote a series of list appends as superscripted $*$ such as $\stmt^*$.
\item We denote a fresh variable name as $\newvar{}$ and its variants.
\item We abuse our notations by mixing semicolon-separated sequences and lists.
\item We use the following:\\
\verb+===+, {\sf \ensuremath{\diamond}toObject}, {\sf \ensuremath{\diamond}toNumber}, {\sf \ensuremath{\diamond}isObject},
{\sf \ensuremath{\diamond}iteratorInit}, {\sf \ensuremath{\diamond}iteratorHasNext}, {\sf \ensuremath{\diamond}iteratorNext},
% {\sf startsWith},
{\sf \ensuremath{\diamond}global}, {\sf \ensuremath{\diamond}getBase}
\item To denote an AST-level statement granularity in the translated IR statements,
we use {\tt IRStmtUnit} which is represented as green angle brackets {\ingreen $\open\ \close$} in this document.
To reduce the number of temporary variables, we use global variables to denote constants such as {\sf 1} and
{\sf true} which is represented in green {\ingreen\sf 1} and  {\ingreen\sf true} in this document.
\item We wrap a possibly identical assignment with a box so that the actual implementation, {\tt Translator}, can eliminate identical assignments.
\end{itemize}

### 2016-10-09 doc/chap-1-foreword.tex
Added LaTeX sources for the user manual

%--------------------------------------------------------------------
% Foreword: audience, authors, license, installation
%--------------------------------------------------------------------
\chapter{Foreword}
\label{c:1:foreword}

\section{Audience}
This document is for users of \safe (Scalable Analysis Framework for ECMAScript)
2.0, a scalable and pluggable analysis framework for JavaScript web applications.
General information on the \safe project is available at an invited talk at ICFP 2016~\cite{safeicfp16}:
\begin{center}
  \url{https://www.youtube.com/watch?v=gEU9utf0sxE}
\end{center}
and the source code and publications are available at:
\begin{center}
  \url{https://github.com/sukyoung/safe}
\end{center}
For more information, please contact the main developers of \safe
at \texttt{safe [at] plrg.kaist.ac.kr}.

SAFE has been used by:
\begin{itemize}
\itemsep-.2em
\item JSAI~\cite{jsai} @ UCSB
\item ROSAEC~\cite{rosaec} @ Seoul National University
\item K framework~\cite{kjs} @ UIUC
\item Ken Cheung~\cite{emse16} @ HKUST
\item Web-based vulnerability detection~\cite{oracle} @ Oracle
\item Tizen~\cite{tizen} @ Linux Foundation
\end{itemize}

\section{Contributors}
The main developers of SAFE 2.0 are as follows:
\begin{itemize}
\itemsep-.2em
\item Jihyeok Park
\item Yeonhee Ryou
\item Sukyoung Ryu
\end{itemize}
and the following have contributed to the source code:
\begin{itemize}
\itemsep-.1em
\item Minsoo Kim (Built-in function modeling)
\item PLRG @ KAIST and our colleagues in S-Core and Samsung Electronics (SAFE 1.0)
\end{itemize}

\section{License}
The \safe source code is released under the BSD license:
\begin{center}
\url{github.com/sukyoung/safe/blob/master/LICENSE}
\end{center}

\section{Installation}
We assume you are using an operating system with a Unix-style shell
(for example, Mac OS X, Linux, or Cygwin on Windows).
Assuming \verb!SAFE_HOME! points to the SAFE directory,
you will need to have access to the following:
\begin{itemize}
\item J2SDK 1.8.  See
\url{http://java.sun.com/javase/downloads/index.jsp}
\item Scala 2.12.  See
\url{http://scala-lang.org/download}
\item sbt version 0.13.  See
\url{http://www.scala-sbt.org}
\item Bash version 2.5, installed at \verb!/bin/bash!.  See
\url{http://www.gnu.org/software/bash/}
\end{itemize}

In your shell startup script, add \verb!$SAFE_HOME/bin! to your path.
The shell scripts in this directory are Bash scripts.
To run them, you must have Bash accessible in \verb!/bin/bash!.

Type \verb!sbt compile! and then \verb!sbt test! to make sure that
your installation successfully finishes the tests.
Two regression test suites are provided with \safe and can be
analyzed automatically:
\begin{verbatim}
$ sbt test
$ sbt test262Test
\end{verbatim}
In addition to the \safe-specific test suite,
\safe 2.0 has been tested using Test262, the official ECMAScript (ECMA-262) conformance suite:
\begin{center}
\url{https://github.com/tc39/test262}
\end{center}
Not a single test should end in a failure.

Once you have built the framework, you can call it from any directory,
on any JavaScript file, simply by typing one of available commands at a command line
as explained in \cref{3:refman}.

\subsection{IntelliJ configuration}
IntelliJ users can use IntelliJ 2016.2.4 with the latest Scala plugin as follows:
\begin{enumerate}
\item Create a new project from existing sources (aka. \verb!Import project!).
\item Choose \verb!build.sbt! in the SAFE 2.0 root to import.
\item Choose JDK 1.8 as the project JDK.
\item Manually download \verb!xtc.jar! in to \verb!lib/!
\item Goto \verb!Project Settings! $\rightarrow$ \verb!Modules! $\rightarrow$
\verb!root (module)! $\rightarrow$ \verb!Dependencies!
\item Open \verb!SBT:unmanaged-jars! dependencies.
\item Remove broken entries for \verb!spray-json! and \verb!xtc!.
\item Add \verb!(+) .jars! for the two libraries above.
\item Run the \verb!buildParsers! task in SBT.
\end{enumerate}

### 2016-10-09 doc/chap-3-refman.tex
Added LaTeX sources for the user manual

%--------------------------------------------------------------------
% Reference manual, with description of the options
%--------------------------------------------------------------------
\chapter{Reference manual}
\label{c:3:refman}

We describe \safe commands and their basic usage.

\section{\safe commands}
One can run a \safe command as follows:
\begin{verbatim}
safe {command} [-{option}]*
     [-{phase}:{option}[={input}]]* {filename}+
\end{verbatim}
For example, the following command analyzes JavaScript code stored in a file name
``{sample.js}'' located in the current directory without showing detailed information
from the \verb!astRewriter! phase but printing the result of the \verb!cfgBuilder!
phase into a file name ``{out}'':
\begin{verbatim}
safe analyze -astRewriter:silent
             -cfgBuilder:out=out sample.js
\end{verbatim}

Each command has its own available options.  The most common options are as follows:
\begin{itemize}
\item \verb!-{phase}:silent!

\safe does not show messages during the phase.

\item \verb!-{phase}:out={out}!

\safe writes the result of the phase to a file \verb!out!.
% \item[\doption{-{phase}:out={out}}]: \\
%   \safe writes the result of the phase to a file name \verb!out!.
\end{itemize}

The currently supported commands and their options are as follows:
\begin{itemize}
\item \verb!parse -parser:out={out}!

parses the JavaScript code in a given file.
\item \verb!astRewrite -astRewriter:silent!\\
\hspace*{5.8em}\verb!-astRewriter:out={out}!

generates a simplified Abstract Syntax Tree (AST)
of the  JavaScript code in a given file.
\item \verb!compile -compiler:silent!\\
\hspace*{4.2em}\verb!-compiler:out={out}!

generates an Intermediate Representation (IR)
of the  JavaScript code in a given file.
\item \verb!cfgBuild -cfgBuilder:silent!\\
\hspace*{4.8em}\verb!-cfgBuilder:out={out}!\\
\hspace*{4.8em}\verb!-cfgBuilder:dot={dot}!

generates a Control Flow Graph (CFG) of the  JavaScript code in a given file.

If \verb!-cfgBuilder:dot=dot! is given,
\safe writes the resulting CFG in a graph visualization format
to file names \verb!dot.gv! and \verb!dot.pdf!.

\item \verb!analyze -analyzer:silent!\\
\hspace*{4.4em}\verb!-analyzer:out={out}!\\
\hspace*{4.4em}\verb!-analyzer:console!

analyzes the  JavaScript code in a given file.

If \verb!-analyzer:console! is given,
\safe enables a user to debug analysis results by navigating the intermediate
status of the analysis.
We describe this facility in the next section.

\item \verb!help! shows the usage of \safe commands to the standard output.
\end{itemize}

\medskip
The \verb!parse! command parses the JavaScript code in a given file and
rewrites obvious dynamic code generation into other statements without using
dynamic code generation but with the same semantics.  For example, the following
JavaScript code
\begin{verbatim}
function f() { return 3; }
eval("f()")
\end{verbatim}
is rewritten as follows:
\begin{verbatim}
function f() { return 3; }
f();
\end{verbatim}

\medskip
The \verb!astRewrite! command parses the JavaScript code in a given file and
rewrites its AST representation into a simpler AST.
The \verb!astRewriter! phase performs three kinds of AST transformations:
\begin{itemize}
\item \verb!Hoister! lifts the declarations of functions and variables inside
programs and functions up to the beginning of them.
\item \verb!Disambiguator! checks some static restrictions and renames identifiers
to unique names.
\item \verb!WithRewriter! rewrites the \verb!with! statements that do not include
any dynamic code generation such as \verb!eval! into other statements without using
the \verb!with! statement but with the same semantics.
\end{itemize}

Note that building a graph visualization format of CFGs requires the \verb!dot! program
from Graphviz~\cite{graphviz} be in your path.
For example, the following command:
\begin{verbatim}
safe cfgBuild -cfgBuilder:dot=dot sample.js
\end{verbatim}
runs the following command:
\begin{verbatim}
dot -Tpdf dot.gv -o dot.pdf
\end{verbatim}
to produce something like the following:
\begin{figure}[H]
\includegraphics[width=8.75cm]{cfg.png}
\end{figure}

\section{\safe analyzer debugging}
When the \verb!-analyzer:console! option is given to the \texttt{analyze} command,
\safe provides a REPL-style console debugger.
For example, the following command:
\begin{verbatim}
safe analyze -analyzer:console test.js
\end{verbatim}
shows the list of available commands for debugging and
the starting point of the analysis:
{\small
\begin{verbatim}
Command list:
- help           
- next       jump to the next iteration. (same as "")
- jump       Continue to analyze until the given
             iteration.
- print      Print out various information.
- result     Print out various information.
- run_insts  Run instruction by instruction.
- move       Change a current position.
- home       Reset the current position.
- run        Run until meet some break point.
- break      Add a break point.
- break-list Show the list of break points.
- break-rm   Remove a break point.
For more information, see 'help <command>'.

<function[0] top-level: Entry[-1], ()> @test.js:1:1
Iter[0] > 
\end{verbatim}
}

The current status is denoted as follows:
{\small
\begin{verbatim}
<function [{fid}] {fun-name}: {block-kind}[{bid}],
 {call-context}> @{filename}:{span}
Iter[{#iteration}] >
\end{verbatim}
}
\noindent
where \verb!fid! and \verb!fun-name! are the id and the name of the current function,
respectively, \verb!block-kind! and \verb!bid!
are the kind and the id of the current block, respectively,
\verb!call-context! is the call context of the current analysis,
\verb!filename! is the name of the file being analyzed,
\verb!span! is the location of the current analysis, and
\verb!#iteration! is the iteration number of the current analysis.

A block is one of the following kinds:
\begin{itemize}
\itemsep-.1em
\item Entry: the entry block of a function
\item Block: a normal block with instructions
\item Exit: the exit block of a function
\item ExitExc: a block denoting uncaught exceptions in a function
\item Call: a block denoting a function call
\item AfterCall: a block receiving a return value of a function call
\item AfterCatch: a block receiving uncaught exceptions after a function call
\item ModelBlock: a block denoting a modeled function
\end{itemize}

The \verb!help! command displays a list of available commands and
the \verb!help <command>! command displays the usage of the \verb!<command>!.
For example:
{\small
\begin{verbatim}
<function[0] top-level: Entry[-1], ()> @test.js:1:1
Iter[0] > help print
usage: print state(-all) ({keyword})
       print block
       print loc {LocName} ({keyword})
       print fid {functionID}
       print worklist
       print ipsucc
       print trace
       print cfg
\end{verbatim}
}
\noindent
shows the usage of the \verb!print! command.

\medskip
The \verb!next! command proceeds the analysis of the current block,
which is the default command.  For example:
{\small
\begin{verbatim}
<function[0] top-level: Entry[-1], ()> @test.js:1:1
Iter[0] >

<function[0] top-level: Block[0], ()> @test.js:1:1-7:18
Iter[1] >
\end{verbatim}
}

\medskip
The \verb!jump {#iteration}! command proceeds the analysis until the given
number of iterations.  For example:
{\small
\begin{verbatim}
<function[0] top-level: Entry[-1], ()> @test.js:1:1
Iter[0] > jump 10

<function[0] top-level: Block[4], ()> @test.js:7:5-21:1
Iter[10] >
\end{verbatim}
}

\medskip
The \verb!print! command displays the status just before
analyzing the current block.  We describe it in Section~\ref{s:3:2:1:refman}.

\medskip
The \verb!result! command displays the status after analyzing
the current block:
\begin{itemize}
\item \verb!result (exc-)state(-all) ({keyword})!

It displays the state in the same way as the \verb!print! command does,
and it can additionally show the exception state generated after the analysis.
\item \verb!result (exc-)loc {LocName}!

It finds and displays the location in the same way as the \verb!print! command does,
and it can additionally find and display the location from
the exception state generated after the analysis.
\end{itemize}

\medskip
The \verb!run_insts! command shows the list of instructions in the current block,
and it enables to analyze each instruction.  It opens a sub-console, which provides 3 kinds
of commands:
\begin{itemize}
\itemsep-.1em
\item \verb!s! shows the state
\item \verb!q! quits the analysis
\item \verb!n! analyzes the next instruction; the default command
\end{itemize}
For example:
{\small
\begin{verbatim}
<function[0] top-level: Block[4], ()> @test.js:8:5-26:1
Iter[10] > run_insts 
Block[4] -> Exit, ExitExc
  [0] shift := <>Global<>ignore6
  [1] __result1 := shift !== "x"
  [2] __expect1 := false
  [3] <>obj<>10 := <>Global<>toObject(obj) @ #13
  [4] __result2 := <>obj<>10["length"] !== 1
  [5] __expect2 := false
  [6] <>obj<>11 := <>Global<>toObject(obj) @ #14
  [7] __result3 := <>obj<>11[0] !== "y"
  [8] __expect3 := false
  [9] <>obj<>12 := <>Global<>toObject(obj) @ #15
  [10] __result4 := <>obj<>12[1] !== undefined
  [11] __expect4 := false
  [12] noop(EndOfFile)

inst: [0] shift := <>Global<>ignore6
('s': state / 'q': stop / 'n','': next)
>

inst: [1] __result1 := shift !== "x"
('s': state / 'q': stop / 'n','': next)
> 
\end{verbatim}
}

\medskip
The \verb!move {fid}:{{bid}|entry|exit|exitExc}! command
moves the current block to the given block denoted by the id of a function,
the id of a block, and the kind of the block.  For example:
{\small
\begin{verbatim}
<function[0] top-level: ExitExc[-3], ()> @test.js:26:1
Iter[12] > move 0:exit
* current control point changed.

<function[0] top-level: Exit[-2], ()> @test.js:26:1
Iter[12] >
\end{verbatim}
}

\medskip
The \verb!home! command moves the current block back to the original
block to be analyzed.  For example:
{\small
\begin{verbatim}
<function[0] top-level: Exit[-2], ()> @test.js:26:1
Iter[12] > home
* reset the current control point.

<function[0] top-level: ExitExc[-3], ()> @test.js:26:1
Iter[12] >
\end{verbatim}
}

\medskip
The \verb!run! command proceeds the analysis until encountering a break
point.  A short-key for this command is Ctrl-d.  For example:
{\small
\begin{verbatim}
<function[0] top-level: Entry[-1], ()> @test.js:1:1
Iter[0] > break 0:exit

<function[0] top-level: Entry[-1], ()> @test.js:1:1
Iter[0] > run

<function[0] top-level: Exit[-2], ()> @test.js:26:1
Iter[11] >
\end{verbatim}
}

\medskip
The \verb!break! command sets up a break point at the given block.
For example:
{\small
\begin{verbatim}
<function[0] top-level: Entry[-1], ()> @test.js:1:1
Iter[0] > break 0:exit

<function[0] top-level: Entry[-1], ()> @test.js:1:1
Iter[0] > run

<function[0] top-level: Exit[-2], ()> @test.js:26:1
Iter[11] >
\end{verbatim}
}

\medskip
The \verb!break-list! command shows a list of blocks with
break points.  For example:
{\small
\begin{verbatim}
<function[0] top-level: Exit[-2], ()> @test.js:26:1
Iter[11] > break-list
* 2 break point(s).
  [0] function[0] Exit[-2]
  [1] function[0] Entry[-1]
\end{verbatim}
}

\medskip
The \verb!break-rm {break-order}! command
removes the break point of a given block
denoted by the order in the result of \verb!break-list!.
For example:
{\small
\begin{verbatim}
<function[0] top-level: Exit[-2], ()> @test.js:26:1
Iter[11] > break-list
* 2 break point(s).
  [0] function[0] Exit[-2]
  [1] function[0] Entry[-1]

<function[0] top-level: Exit[-2], ()> @test.js:26:1
Iter[11] > break-rm 0
* break-point[0] removed.
[0] function[0] Exit[-2]

<function[0] top-level: Exit[-2], ()> @test.js:26:1
Iter[11] > break-list
* 1 break point(s).
  [0] function[0] Entry[-1]
\end{verbatim}
}

\subsection{Analyzer debugging with printing}
\label{s:3:2:1:refman}
The \verb!print! command displays the status just before
analyzing the current block.

\medskip\noindent
\fbox{\texttt{print state(-all) (\{keyword\})}}\\[.2em]
The \verb!print state! command displays the current state,
and the \verb!print state-all! command
displays the current state including all system addresses.
When a keyword is given, it displays only the parts that include the keyword.
For example:
{\small
\begin{verbatim}
<function[0] top-level: Exit[-2], ()> @test.js:21:1
Iter[12] > print state result
           "__result1" -> [ttf] false
           "__result2" -> [ttf] false
           "__result3" -> [ttf] false
           Set(NaN, __result3, Function,
__EvalErrLoc, URIError, pop, JSON, Error, Number,
decodeURIComponent, __SyntaxErrProtoLoc, RangeError,
__RangeErrLoc, __ArrayConstLoc, __EvalErrProtoLoc,
Boolean, ReferenceError, __RefErrLoc, obj, __BOT,
encodeURIComponent, __TypeErrProtoLoc, Array,
EvalError, __expect1, encodeURI, eval, __expect3,
isFinite, __ErrProtoLoc, Object, __TOP, Math,
__TypeErrLoc, __URIErrProtoLoc, __result1,
parseFloat, __RangeErrProtoLoc, TypeError,
<>Global<>global, __ObjConstLoc, isNaN, __URIErrLoc,
Date, __NumTop, __expect2, decodeURI, RegExp,
__BoolTop, __UInt, parseInt, __result2, __StrTop,
Infinity, SyntaxError, __RefErrProtoLoc, __Global,
<>Global<>true, __SyntaxErrLoc, undefined, String)
\end{verbatim}
}

\medskip\noindent
\fbox{\texttt{print block}}\\[.2em]
The \verb!print block! command displays the information of
a given block.  For example:
{\small
\begin{verbatim}
<function[0] top-level: Block[0], ()> @test.js:1:1-7:18
Iter[1] > print block
Block[0] -> [1], ExitExc
  [0] noop(StartOfFile)
  [1] <>Global<>ignore1 := alloc() @ #1
  [2] obj := <>Global<>ignore1
  [3] <>obj<>1 := <>Global<>toObject(obj) @ #2
  [4] <>obj<>2 := <>Global<>toObject(Array) @ #3
  [5] <>obj<>3 :=
      <>Global<>toObject(<>obj<>2["prototype"]) @ #4
  [6] <>obj<>1["pop"] := <>obj<>3["pop"]
  [7] <>obj<>4 := <>Global<>toObject(obj) @ #5
  [8] <>obj<>4[4294967294] := "x"
  [9] <>obj<>5 := <>Global<>toObject(obj) @ #6
  [10] <>obj<>5["length"] := - 1
  [11] <>obj<>6 := <>Global<>toObject(obj) @ #7
  [12] <>arguments<>7 := allocArg(0) @ #8
  [13] <>fun<>8 :=
       <>Global<>toObject(<>obj<>6["pop"]) @ #9
\end{verbatim}
}

\medskip\noindent
\fbox{\texttt{print loc \{LocName\} (\{keyword\})}}\\[.2em]
The \verb!print loc {LocName}! command shows the object
bound at a given location in the current state.
When a keyword is given, it displays only the parts that include the keyword
in the object.  For example:
{\small
\begin{verbatim}
<function[0] top-level: ExitExc[-3], ()> @test.js:21:1
Iter[12] > print loc #1
#1 -> [[Class]] : "Object"
      [[Extensible]] : true
      [[Prototype]] : #Object.prototype
      "4294967294" -> [ttt] "x"
      "length" -> [ttt] -1
      "pop" -> [ttt] #Array.prototype.pop
      Set(pop, length, 4294967294)
\end{verbatim}
}

\medskip\noindent
\fbox{\texttt{print fid \{functionID\}}}\\[.2em]
It displays the name and the span information of
a given function id.  For example:
{\small
\begin{verbatim}
<function[0] top-level: ExitExc[-3], ()> @test.js:21:1
Iter[12] > print fid 0
* function name: top-level
* span info.   : test.js:1:1-21:1
\end{verbatim}
}

\medskip\noindent
\fbox{\texttt{print worklist}}\\[.2em]
It shows the work in the current worklist.  For example:
{\small
\begin{verbatim}
<function[42] []Array.prototype.pop: ExitExc[-3],
 (10)> @[]Array.prototype.pop:0:0
Iter[6] > print worklist
* Worklist set
(42:ExitExc[-3], (10)), (42:Exit[-2], (10)),
(0:AfterCall[2], ()), (0:ExitExc[-3], ())
\end{verbatim}
}

\medskip\noindent
\fbox{\texttt{print ipsucc}}\\[.2em]
It displays the information of the current inter-procedural successor.
For example:
{\small
\begin{verbatim}
<function[42] []Array.prototype.pop: ExitExc[-3],
 (10)> @[]Array.prototype.pop:0:0
Iter[6] > print ipsucc
* successor map
- src: FlowSensitiveCP(ExitExc[-3],(10))
- dst: FlowSensitiveCP(AfterCatch[3],()),
 mayOld: (10, 1, 8)
mustOld: (10, 1, 8)
\end{verbatim}
}

\medskip\noindent
\fbox{\texttt{print trace}}\\[.2em]
It shows the current call trace.  For example:
{\small
\begin{verbatim}
<function[42] []Array.prototype.pop: Entry[-1],
 (10)> @[]Array.prototype.pop:0:0
Iter[3] > print trace
* Call-Context Trace
Entry[-1] of function[42] []Array.prototype.pop with (10)
 1>  [0] call(<>fun<>8, <>obj<>6, <>arguments<>7) @ #10
test.js:7:11-20 @Call[1] of function[0] top-level with ()
\end{verbatim}
}

\medskip\noindent
\fbox{\texttt{print cfg}}\\[.2em]
It prints the current CFG as an input file to the \verb!dot! program.

### 2016-10-10 doc/chap-2-intro.tex

%--------------------------------------------------------------------
% Brief general description of the structure of the analyzer
%--------------------------------------------------------------------
\chapter{\safe}

\section{Introduction to \safe 1.0}
\label{s:2:1:safe1}
Analyzing real-world JavaScript web applications is a challenging task.
On top of understanding the semantics of JavaScript~\cite{ecma5},
it requires modeling of web documents~\cite{W3C}, platform objects~\cite{tizen},
and interactions between them.
Not only JavaScript itself but also its usage patterns are extremely dynamic~\cite{dynamic,eval}.
Most of web applications load JavaScript code dynamically,
which makes pure static analysis approaches inapplicable.

To analyze JavaScript web applications in the wild mostly statically,
we have developed \safe and extended it with various approaches.
We first described quirky language features and semantics of JavaScript
that make static analysis difficult and designed \safe to analyze pure JavaScript
benchmarks~\cite{fool12}.  It provides a default static analyzer based on
the abstract interpretation framework~\cite{ai77},
and it supports flow-sensitive and context-sensitive analyses of stand-alone JavaScript programs.
It performs several preprocessing steps on JavaScript code
to address some quirky semantics of JavaScript such as
the \texttt{with} statement~\cite{dls13}.
The pluggable and scalable design of the framework allowed experiments with JavaScript variants
like adding a module system~\cite{oopsla12,modularity14}
and detecting code clones~\cite{emse16}.

We then extended \safe
to model web application execution environments of various browsers~\cite{ase15a} and
platform-specific library functions~\cite{fse14,safets}.  To provide a faithful (partial) model of browsers,
we support the configurability of HTML/DOM tree abstraction levels 
so that users can adjust a trade-off between analysis performance and precision 
depending on their applications.  To analyze interactions between applications
and platform-specific libraries specified in Web APIs written in Web IDLs,
we developed automatic modeling
of library functions from Web APIs and detect possible misuses of Web APIs
by web applications.  The same technique can support analysis of libraries specified
in TypeScript~\cite{ts}.  Analyzing real-world web applications requires
more scalable analysis than analyzing stand-alone JavaScript programs~\cite{ase15b,ecoop15}.

The baseline analysis is designed to be sound, which means that the properties it
computes should over-approximate the concrete behaviors of the analyzed program.
However, \safe may contain implementation bugs leading to unsound analysis results.
Moreover, some components of \safe may be intentionally unsound, or soundy~\cite{soundy}.
To lessen the burden of analyzing the entire concrete behaviors of programs,
we may use approximate call graphs~\cite{icse13}
from WALA~\cite{wala} to analyze a fraction of them,
or utilize dynamic information statically~\cite{safehybrid}
to prune relatively unrelated code.

\section{Introduction to \safe 2.0}
\label{s:2:2:safe2}
Based on our experiments and experiences with \safe 1.0,
we now release \safe 2.0, which is aimed to be a playground for
advanced research in JavaScript web applications.
Thus, we intentionally designed it to be light-weight, highly parametric, and modular.

The important changes from \safe 1.0 include the following:
\begin{itemize}
\item \safe 2.0 has been tested using Test262, the official ECMAScript (ECMA-262) conformance suite.
\item \safe 2.0 now uses sbt instead of ant to build the framework.
\item \safe 2.0 provides a library of abstract domains that supports
parameterization and high-level specification of abstract semantics on them.
\item Most Java source files are replaced by Scala code and the only Java source code remained is the generated parser code.
\item Several components from \safe 1.0 may not be integrated into \safe 2.0. Such components include interpreter, concolic testing, clone detector, clone refactoring, TypeScript support, Web API misuse detector, and several abstract domains like the string automata domain.
\end{itemize}

We have the following roadmap for \safe 2.0:
\begin{itemize}
\item \safe 2.0 will make monthly updates.
\item The next update will include a \safe document, browser benchmarks, and more Test262 tests.
\item We plan to support some missing features from \safe 1.0 incrementally such as a bug detector, DOM modeling, and jQuery analysis.
\item Future versions of \safe 2.0 will address various analysis techniques, dynamic features of web applications, event handling, modeling framework, compositional analysis, and selective sensitivity among others.
\end{itemize}

\section{A sample use of \safe}
\label{sec:usage-example}
Let us consider a very simple JavaScript program stored in a file name ``{sample.js}'' located
in the current directory:
\begin{verbatim}
with({a: 1}) {a = 2;}
\end{verbatim}
Then, one can see how \safe desugars the \texttt{with} statement by the command below:
\begin{verbatim}
safe astRewrite sample.js
\end{verbatim}
which shows an output like the following:
{\small
\begin{verbatim}
The command 'astRewrite' took 178 ms.
  {
    <>alpha<>1 = <>Global<>toObject({
      a : 1
    });
    ("a" in <>alpha<>1 ? <>alpha<>1.a = 2 : a = 2);
  }
\end{verbatim}
}
\noindent
where the names prefixed by \verb!<>! are generated by \safe.
\safe translates the rewritten JavaScript source code to its intermediate representation
format, and one can see the result by the command below:
\begin{verbatim}
safe compile sample.js
\end{verbatim}
which shows an output like the following:
{\small
\begin{verbatim}
The command 'compile' took 382 ms.
{
  {
    <>new1<>1 = {
      a : 1
    }
    <>Global<>ignore1 = <>Global<>toObject(<>new1<>1)
    <>alpha<>2 = <>Global<>ignore1
  }
  if("a" in <>alpha<>2)
  {
    <>obj<>3 = <>Global<>toObject(<>alpha<>2)
    <>obj<>3["a"] = 2
    <>Global<>ignore2 = <>obj<>3["a"]
  }
  else
  {
    a = 2
    <>Global<>ignore2 = 2
  }
}
\end{verbatim}
}
\noindent
The \safe analysis is performed on control flow graphs of programs,
which can be built by the command below:
\begin{verbatim}
safe cfgBuild sample.js
\end{verbatim}
\noindent
resulting an output as follows:
{\small
\begin{verbatim}
The command 'cfgBuild' took 492 ms.
function[0] top-level {
  Entry[-1] -> [0]

  Block[0] -> [2], [1], ExitExc
    [0] noop(StartOfFile)
    [1] <>new1<>1 := alloc() @ #1
    [2] <>new1<>1["a"] := 1
    [3] <>Global<>ignore1 :=
          <>Global<>toObject(<>new1<>1) @ #2
    [4] <>alpha<>2 := <>Global<>ignore1

  Block[1] -> [3], ExitExc
    [0] assert("a" in <>alpha<>2)
    [1] <>obj<>3 := <>Global<>toObject(<>alpha<>2) @ #3
    [2] <>obj<>3["a"] := 2
    [3] <>Global<>ignore2 := <>obj<>3["a"]

  Block[2] -> [3], ExitExc
    [0] assert(! "a" in <>alpha<>2)
    [1] a := 2
    [2] <>Global<>ignore2 := 2

  Block[3] -> Exit
    [0] noop(EndOfFile)

  Exit[-2]

  ExitExc[-3]
}
\end{verbatim}
}
\noindent
Finally, the following command:
\begin{verbatim}
safe analyze sample.js
\end{verbatim}
analyzes the JavaScript program in the file and shows the analysis results:
{\small
\begin{verbatim}
The command 'analyze' took 1002 ms.
** heap **
#Global -> [[Class]] : "Object"
...
#1 -> [[Class]] : "Object"
      [[Extensible]] : true
      [[Prototype]] : #Object.prototype
      "a" -> [ttt] 2
      Set(a)

** context **
\end{verbatim}
\vspace*{-.6em}
\verb!##Collapsed -> [[Default]] @->! $\bot$\verb!(value)!
\vspace*{-.6em}
\begin{verbatim}
               * Outer: null
#GlobalEnv -> Top(global environment record)
              * Outer: null
              ...
this: #Global

** old address set **
mayOld: (1)
mustOld: (1)

- # of iteration: 6
- # of user functions: 1
- # of touched blocks: 6
    user blocks: 6
    modeling blocks: 0
- # of instructions: 13
\end{verbatim}
}

### 2016-10-10 doc/chap-3-refman.tex
Added the HTML debugger

@@
 
-If \verb!-cfgBuilder:dot=dot! is given,
+If \verb!-cfgBuilder:dot=name! is given,
 \safe writes the resulting CFG in a graph visualization format
-to file names \verb!dot.gv! and \verb!dot.pdf!.
+to file names \verb!name.gv! and \verb!name.pdf!.
 
@@
 \hspace*{4.4em}\verb!-analyzer:out={out}!\\
-\hspace*{4.4em}\verb!-analyzer:console!
+\hspace*{4.4em}\verb!-analyzer:console!\\
+\hspace*{4.4em}\verb!-analyzer:html={html}!
 
@@
 If \verb!-analyzer:console! is given,
-\safe enables a user to debug analysis results by navigating the intermediate
+\safe enables a user to debug analysis results by investigating the intermediate
 status of the analysis.
-We describe this facility in the next section.
+
+If \verb!-analyzer:html=name! is given,
+\safe writes the resulting CFG with states that can be investigated to
+file name \verb!name.html!.
+
+We describe these facilities in the next section.
 
@@
 \fbox{\texttt{print cfg}}\\[.2em]
-It prints the current CFG as an input file to the \verb!dot! program.
+It prints the current CFG to files \verb!cfg.gv! and \verb!cfg.pdf!.
+
+\medskip\noindent
+\fbox{\texttt{print html}}\\[.2em]
+It prints the current CFG and its state to the \verb!cfg.html! file.
+We describe this facility in the next section.
+
+\subsection{Analyzer debugging with browsing}
+\label{s:3:2:2:refman}
+The \verb!print html! command writes the current status into an HTML file
+so that a user can investigate the analysis status from a browser.
+Consider the following snapshot:
+\begin{figure}[H]
+\includegraphics[width=8.75cm]{htmldebugger.png}
+\end{figure}
+\noindent
+which shows the current CFG in the middle.
+Nodes in black lines denote the blocks that are analyzed,
+those in gray lines denote the blocks not yet being analyzed, and
+colored nodes denote the blocks that are currently in the worklist of the analyzer.
+One can toggle whether to show the nodes in the worklist by the menu button on the top right.
+When a user selects a block from the CFG, the list of the instructions in the block
+and the state just before analyzing the block are displayed on the left.

### 2016-10-10 tests/test262/11.1/11.1.5/11.1.5-3-s.js
SAFE 2.0 official release

@@ -1,0 +1,11 @@
+// TODO strict
+// function testcase() {
+
+//         try {
+//             eval("var obj = {set _11_1_5_3_fun(eval) { \"use strict\"; }};");
+//             return false;
+//         } catch (e) {
+//             return (e instanceof SyntaxError);
+//         }
+//     }
+// runTestCase(testcase);

### 2016-10-10 tests/test262/11.13/11.13.2/11.13.2-29-s.js

@@ -1,0 +1,24 @@
+// TODO strict
+//   function testcase() 
+//   {
+//   "use strict";
+//     var obj = {
+      
+//     };
+//     Object.defineProperty(obj, "prop", {
+//       value : 10,
+//       writable : false,
+//       enumerable : true,
+//       configurable : true
+//     });
+//     try
+// {      obj.prop >>= 20;
+//       return false;}
+//     catch (e)
+// {      return e instanceof TypeError && obj.prop === 10;}
+
+//   }
+//   {
+//     var __result1 = testcase();
+//     var __expect1 = true;
+//   }

### 2016-10-10 tests/test262/11.13/11.13.2/S11.13.2_A2.1_T1.5.js

@@ -1,0 +1,14 @@
+  var x = 1;
+  var z = (x -= 1);
+  {
+    var __result1 = z !== 0;
+    var __expect1 = false;
+  }
+  var x = 1;
+  var y = 1;
+  var z = (x -= y);
+  {
+    var __result2 = z !== 0;
+    var __expect2 = false;
+  }
+  

### 2016-10-10 tests/test262/11.13/11.13.2/S11.13.2_A3.1_T10.js

@@ -1,0 +1,13 @@
+  var x = 0;
+  x ^= 1;
+  {
+    var __result1 = x !== 1;
+    var __expect1 = false;
+  }
+  y = 1;
+  y ^= 0;
+  {
+    var __result2 = y !== 1;
+    var __expect2 = false;
+  }
+  

### 2016-10-10 tests/test262/11.13/11.13.2/S11.13.2_A4.1_T2.4.js

@@ -1,0 +1,25 @@
+  x = 1;
+  x *= undefined;
+  {
+    var __result1 = isNaN(x) !== true;
+    var __expect1 = false;
+  }
+  x = undefined;
+  x *= 1;
+  {
+    var __result2 = isNaN(x) !== true;
+    var __expect2 = false;
+  }
+  x = new Number(1);
+  x *= undefined;
+  {
+    var __result3 = isNaN(x) !== true;
+    var __expect3 = false;
+  }
+  x = undefined;
+  x *= new Number(1);
+  {
+    var __result4 = isNaN(x) !== true;
+    var __expect4 = false;
+  }
+  

### 2016-10-10 tests/test262/11.13/11.13.2/S11.13.2_A4.5_T1.4.js

@@ -1,0 +1,25 @@
+  x = null;
+  x -= undefined;
+  {
+    var __result1 = isNaN(x) !== true;
+    var __expect1 = false;
+  }
+  x = undefined;
+  x -= null;
+  {
+    var __result2 = isNaN(x) !== true;
+    var __expect2 = false;
+  }
+  x = undefined;
+  x -= undefined;
+  {
+    var __result3 = isNaN(x) !== true;
+    var __expect3 = false;
+  }
+  x = null;
+  x -= null;
+  {
+    var __result4 = x !== 0;
+    var __expect4 = false;
+  }
+  

### 2016-10-10 tests/test262/11.4/11.4.1/11.4.1-4-a-3-s.js

@@ -1,0 +1,19 @@
+// TODO strict
+  // function testcase() 
+  // {
+  // "use strict";
+  //   var obj = {
+      
+  //   };
+  //   Object.defineProperty(obj, "prop", {
+  //     value : "abc",
+  //     configurable : true
+  //   });
+  //   delete obj.prop;
+  //   return ! obj.hasOwnProperty("prop");
+  // }
+  // {
+  //   var __result1 = testcase();
+  //   var __expect1 = true;
+  // }
+  

### 2016-10-10 tests/test262/11.5/11.5.2/S11.5.2_A3_T1.3.js

@@ -1,0 +1,25 @@
+  {
+    var __result1 = "1" / "1" !== 1;
+    var __expect1 = false;
+  }
+  {
+    var __result2 = new String("1") / "1" !== 1;
+    var __expect2 = false;
+  }
+  {
+    var __result3 = "1" / new String("1") !== 1;
+    var __expect3 = false;
+  }
+  {
+    var __result4 = new String("1") / new String("1") !== 1;
+    var __expect4 = false;
+  }
+  {
+    var __result5 = isNaN("x" / "1") !== true;
+    var __expect5 = false;
+  }
+  {
+    var __result6 = isNaN("1" / "x") !== true;
+    var __expect6 = false;
+  }
+  

### 2016-10-10 tests/test262/11.5/11.5.3/S11.5.3_A2.3_T1.js

@@ -1,0 +1,30 @@
+// TODO [[DefaultValue]]
+//   var x = {
+//     valueOf : (function () 
+//     {
+//       throw "x";
+//     })
+//   };
+//   var y = {
+//     valueOf : (function () 
+//     {
+//       throw "y";
+//     })
+//   };
+//   try
+// {    x % y;
+//     $ERROR('#1.1: var x = { valueOf: function () { throw "x"; } }; var y = { valueOf: function () { throw "y"; } }; x % y throw "x". Actual: ' + (x % y));}
+//   catch (e)
+// {    if (e === "y")
+//     {
+//       $ERROR('#1.2: ToNumber(first expression) is called first, and then ToNumber(second expression)');
+//     }
+//     else
+//     {
+//       {
+//         var __result1 = e !== "x";
+//         var __expect1 = false;
+//       }
+//     }}
+
+  

### 2016-10-10 tests/test262/11.8/11.8.2/S11.8.2_A3.2_T1.1.js

@@ -1,0 +1,25 @@
+  {
+    var __result1 = "1" > "1" !== false;
+    var __expect1 = false;
+  }
+  {
+    var __result2 = new String("1") > "1" !== false;
+    var __expect2 = false;
+  }
+  {
+    var __result3 = "1" > new String("1") !== false;
+    var __expect3 = false;
+  }
+  {
+    var __result4 = new String("1") > new String("1") !== false;
+    var __expect4 = false;
+  }
+  {
+    var __result5 = "x" > "1" !== true;
+    var __expect5 = false;
+  }
+  {
+    var __result6 = "1" > "x" !== false;
+    var __expect6 = false;
+  }
+  

### 2016-10-10 tests/test262/11.8/11.8.4/S11.8.4_A4.12_T1.js

@@ -1,0 +1,29 @@
+  {
+    var __result1 = ("xy" >= "xx") !== true;
+    var __expect1 = false;
+  }
+  {
+    var __result2 = ("xx" >= "xy") !== false;
+    var __expect2 = false;
+  }
+  {
+    var __result3 = ("y" >= "x") !== true;
+    var __expect3 = false;
+  }
+  {
+    var __result4 = ("aba" >= "aab") !== true;
+    var __expect4 = false;
+  }
+  {
+    var __result5 = ("\u0061\u0061\u0061\u0061" >= "\u0061\u0061\u0061\u0062") !== false;
+    var __expect5 = false;
+  }
+  {
+    var __result6 = ("a\u0000b" >= "a\u0000a") !== true;
+    var __expect6 = false;
+  }
+  {
+    var __result7 = ("aa" >= "aB") !== true;
+    var __expect7 = false;
+  }
+  

### 2016-10-10 tests/test262/12.10/S12.10_A1.5_T2.js

@@ -1,0 +1,155 @@
+  this.p1 = 1;
+  this.p2 = 2;
+  this.p3 = 3;
+  var result = "result";
+  var myObj = {
+    p1 : 'a',
+    p2 : 'b',
+    p3 : 'c',
+    value : 'myObj_value',
+    valueOf : (function () 
+    {
+      return 'obj_valueOf';
+    }),
+    parseInt : (function () 
+    {
+      return 'obj_parseInt';
+    }),
+    NaN : 'obj_NaN',
+    Infinity : 'obj_Infinity',
+    eval : (function () 
+    {
+      return 'obj_eval';
+    }),
+    parseFloat : (function () 
+    {
+      return 'obj_parseFloat';
+    }),
+    isNaN : (function () 
+    {
+      return 'obj_isNaN';
+    }),
+    isFinite : (function () 
+    {
+      return 'obj_isFinite';
+    })
+  };
+  var del;
+  var st_p1 = "p1";
+  var st_p2 = "p2";
+  var st_p3 = "p3";
+  var st_parseInt = "parseInt";
+  var st_NaN = "NaN";
+  var st_Infinity = "Infinity";
+  var st_eval = "eval";
+  var st_parseFloat = "parseFloat";
+  var st_isNaN = "isNaN";
+  var st_isFinite = "isFinite";
+  try
+{    for(var prop in myObj)
+    {
+      with (myObj)
+      {
+        st_p1 = p1;
+        p1 = 'x1';
+        st_p2 = p2;
+        this.p2 = 'x2';
+        st_p3 = p3;
+        del = delete p3;
+        st_parseInt = parseInt;
+        st_NaN = NaN;
+        st_Infinity = Infinity;
+        st_eval = eval;
+        st_parseFloat = parseFloat;
+        st_isNaN = isNaN;
+        st_isFinite = isFinite;
+        var p4 = 'x4';
+        p5 = 'x5';
+        var value = 'value';
+        throw value;
+      }
+    }}
+  catch (e)
+{    result = e;}
+
+  {
+    var __result1 = ! (result === "value");
+    var __expect1 = false;
+  }
+  {
+    var __result2 = ! (p1 === 1);
+    var __expect2 = false;
+  }
+  {
+    var __result3 = ! (p2 === "x2");
+    var __expect3 = false;
+  }
+  {
+    var __result4 = ! (p3 === 3);
+    var __expect4 = false;
+  }
+  {
+    var __result5 = ! (p4 === "x4");
[…]

### 2016-10-10 tests/test262/12.10/S12.10_A1.5_T3.js

@@ -1,0 +1,173 @@
+  this.p1 = 1;
+  this.p2 = 2;
+  this.p3 = 3;
+  var result = "result";
+  var myObj = {
+    p1 : 'a',
+    p2 : 'b',
+    p3 : 'c',
+    value : 'myObj_value',
+    valueOf : (function () 
+    {
+      return 'obj_valueOf';
+    }),
+    parseInt : (function () 
+    {
+      return 'obj_parseInt';
+    }),
+    NaN : 'obj_NaN',
+    Infinity : 'obj_Infinity',
+    eval : (function () 
+    {
+      return 'obj_eval';
+    }),
+    parseFloat : (function () 
+    {
+      return 'obj_parseFloat';
+    }),
+    isNaN : (function () 
+    {
+      return 'obj_isNaN';
+    }),
+    isFinite : (function () 
+    {
+      return 'obj_isFinite';
+    })
+  };
+  var del;
+  var st_p1 = "p1";
+  var st_p2 = "p2";
+  var st_p3 = "p3";
+  var st_parseInt = "parseInt";
+  var st_NaN = "NaN";
+  var st_Infinity = "Infinity";
+  var st_eval = "eval";
+  var st_parseFloat = "parseFloat";
+  var st_isNaN = "isNaN";
+  var st_isFinite = "isFinite";
+  try
+{    for(var prop in myObj)
+    {
+      with (myObj)
+      {
+        throw value;
+        if (prop === 'p1')
+        {
+          st_p1 = p1;
+          p1 = 'x1';
+        }
+        if (prop === 'p2')
+        {
+          st_p2 = p2;
+          this.p2 = 'x2';
+        }
+        if (prop === 'p3')
+        {
+          st_p3 = p3;
+          del = delete p3;
+        }
+        if (prop === 'parseInt')
+          st_parseInt = parseInt;
+        if (prop === 'NaN')
+          st_NaN = NaN;
+        if (prop === 'Infinity')
+          st_Infinity = Infinity;
+        if (prop === 'eval')
+          st_eval = eval;
+        if (prop === 'parseFloat')
+          st_parseFloat = parseFloat;
+        if (prop === 'isNaN')
+          st_isNaN = isNaN;
+        if (prop === 'isFinite')
+          st_isFinite = isFinite;
+        var p4 = 'x4';
+        p5 = 'x5';
+        var value = 'value';
+      }
+    }}
+  catch (e)
[…]

### 2016-10-10 tests/test262/12.10/S12.10_A1.8_T4.js

@@ -1,0 +1,160 @@
+   this.p1 = 1;
+   this.p2 = 2;
+   this.p3 = 3;
+   var result = "result";
+   var myObj = {
+     p1 : 'a',
+     p2 : 'b',
+     p3 : 'c',
+     value : 'myObj_value',
+     valueOf : (function () 
+     {
+       return 'obj_valueOf';
+     }),
+     parseInt : (function () 
+     {
+       return 'obj_parseInt';
+     }),
+     NaN : 'obj_NaN',
+     Infinity : 'obj_Infinity',
+     eval : (function () 
+     {
+       return 'obj_eval';
+     }),
+     parseFloat : (function () 
+     {
+       return 'obj_parseFloat';
+     }),
+     isNaN : (function () 
+     {
+       return 'obj_isNaN';
+     }),
+     isFinite : (function () 
+     {
+       return 'obj_isFinite';
+     })
+   };
+   var del;
+   var st_p1 = "p1";
+   var st_p2 = "p2";
+   var st_p3 = "p3";
+   var st_parseInt = "parseInt";
+   var st_NaN = "NaN";
+   var st_Infinity = "Infinity";
+   var st_eval = "eval";
+   var st_parseFloat = "parseFloat";
+   var st_isNaN = "isNaN";
+   var st_isFinite = "isFinite";
+   try
+ {    with (myObj)
+     {
+       var f = (function () 
+       {
+         st_p1 = p1;
+         st_p2 = p2;
+         st_p3 = p3;
+         st_parseInt = parseInt;
+         st_NaN = NaN;
+         st_Infinity = Infinity;
+         st_eval = eval;
+         st_parseFloat = parseFloat;
+         st_isNaN = isNaN;
+         st_isFinite = isFinite;
+         p1 = 'x1';
+         this.p2 = 'x2';
+         del = delete p3;
+         var p4 = 'x4';
+         p5 = 'x5';
+         var value = 'value';
+         throw value;
+       });
+       var obj = new f();
+     }}
+   catch (e)
+ {    result = e;}
+
+   {
+     var __result1 = ! (result === "value");
+     var __expect1 = false;
+   }
+   {
+     var __result2 = ! (p1 === 1);
+     var __expect2 = false;
+   }
+   {
+     var __result3 = ! (p2 === 2);
+     var __expect3 = false;
+   }
+   {
+     var __result4 = ! (p3 === 3);
+     var __expect4 = false;
+   }
+   try
[…]

### 2016-10-10 tests/test262/12.10/S12.10_A1.9_T3.js

@@ -1,0 +1,165 @@
+  this.p1 = 1;
+  this.p2 = 2;
+  this.p3 = 3;
+  var result = "result";
+  var myObj = {
+    p1 : 'a',
+    p2 : 'b',
+    p3 : 'c',
+    value : 'myObj_value',
+    valueOf : (function () 
+    {
+      return 'obj_valueOf';
+    }),
+    parseInt : (function () 
+    {
+      return 'obj_parseInt';
+    }),
+    NaN : 'obj_NaN',
+    Infinity : 'obj_Infinity',
+    eval : (function () 
+    {
+      return 'obj_eval';
+    }),
+    parseFloat : (function () 
+    {
+      return 'obj_parseFloat';
+    }),
+    isNaN : (function () 
+    {
+      return 'obj_isNaN';
+    }),
+    isFinite : (function () 
+    {
+      return 'obj_isFinite';
+    })
+  };
+  var del;
+  var st_p1 = "p1";
+  var st_p2 = "p2";
+  var st_p3 = "p3";
+  var st_parseInt = "parseInt";
+  var st_NaN = "NaN";
+  var st_Infinity = "Infinity";
+  var st_eval = "eval";
+  var st_parseFloat = "parseFloat";
+  var st_isNaN = "isNaN";
+  var st_isFinite = "isFinite";
+  with (myObj)
+  {
+    for(var prop in myObj)
+    {
+      break;
+      if (prop === 'p1')
+      {
+        st_p1 = p1;
+        p1 = 'x1';
+      }
+      if (prop === 'p2')
+      {
+        st_p2 = p2;
+        this.p2 = 'x2';
+      }
+      if (prop === 'p3')
+      {
+        st_p3 = p3;
+        del = delete p3;
+      }
+      if (prop === 'parseInt')
+        st_parseInt = parseInt;
+      if (prop === 'NaN')
+        st_NaN = NaN;
+      if (prop === 'Infinity')
+        st_Infinity = Infinity;
+      if (prop === 'eval')
+        st_eval = eval;
+      if (prop === 'parseFloat')
+        st_parseFloat = parseFloat;
+      if (prop === 'isNaN')
+        st_isNaN = isNaN;
+      if (prop === 'isFinite')
+        st_isFinite = isFinite;
+      var p4 = 'x4';
+      p5 = 'x5';
+      var value = 'value';
+    }
+  }
+  {
+    var __result1 = ! (p1 === 1);
+    var __expect1 = false;
+  }
[…]

### 2016-10-10 tests/test262/12.14/S12.14_A16_T13.js

@@ -1,0 +1,11 @@
+// Syntax error
+// try
+// {
+// }
+// catch("22")
+// {
+// }
+
+
+
+

### 2016-10-10 tests/test262/15.2/15.2.3/15.2.3.7/15.2.3.7-6-a-41.js

@@ -1,19 +1,88 @@
-//   TODO dataPropertyAttributesAreCorrect
-//   function testcase() 
-//   {
-//     var obj = {
-//       
-//     };
-//     obj.foo = 101;
-//     Object.defineProperties(obj, {
-//       foo : {
-//         value : "102"
-//       }
-//     });
-//     return dataPropertyAttributesAreCorrect(obj, "foo", "102", true, true, true);
-//   }
-//   {
-//     var __result1 = testcase();
-//     var __expect1 = true;
-//   }
-//   
+  function testcase() 
+  {
+    var obj = {
+      
+    };
+    obj.foo = 101;
+    Object.defineProperties(obj, {
+      foo : {
+        value : "102"
+      }
+    });
+    return dataPropertyAttributesAreCorrect(obj, "foo", "102", true, true, true);
+  }
+  {
+    var __result1 = testcase();
+    var __expect1 = true;
+  }
+  
+function dataPropertyAttributesAreCorrect(obj,
+                                          name,
+                                          value,
+                                          writable,
+                                          enumerable,
+                                          configurable) {
+    var attributesCorrect = true;
+
+    if (obj[name] !== value) {
+        if (typeof obj[name] === "number" &&
+            isNaN(obj[name]) &&
+            typeof value === "number" &&
+            isNaN(value)) {
+            // keep empty
+        } else {
+            attributesCorrect = false;
+        }
+    }
+
+    try {
+        if (obj[name] === "oldValue") {
+            obj[name] = "newValue";
+        } else {
+            obj[name] = "OldValue";
+        }
+    } catch (we) {
+    }
+
+    var overwrited = false;
+    if (obj[name] !== value) {
+        if (typeof obj[name] === "number" &&
+            isNaN(obj[name]) &&
+            typeof value === "number" &&
+            isNaN(value)) {
+            // keep empty
+        } else {
+            overwrited = true;
+        }
+    }
+    if (overwrited !== writable) {
+        attributesCorrect = false;
+    }
+
+    var enumerated = false;
+    for (var prop in obj) {
+        if (obj.hasOwnProperty(prop) && prop === name) {
+            enumerated = true;
+        }
+    }
+
+    if (enumerated !== enumerable) {
+        attributesCorrect = false;
+    }
+
+
+    var deleted = false;
+
+    try {
+        delete obj[name];
+    } catch (de) {
+    }
+    if (!obj.hasOwnProperty(name)) {
[…]

### 2016-10-10 tests/test262/15.2/15.2.3/15.2.3.7/15.2.3.7-6-a-95.js

@@ -1,24 +1,93 @@
-//   TODO dataPropertyAttributesAreCorrect
-//   function testcase() 
-//   {
-//     var obj = {
-//       
-//     };
-//     Object.defineProperty(obj, "foo", {
-//       value : 200,
-//       enumerable : true,
-//       writable : true,
-//       configurable : true
-//     });
-//     Object.defineProperties(obj, {
-//       foo : {
-//         value : undefined
-//       }
-//     });
-//     return dataPropertyAttributesAreCorrect(obj, "foo", undefined, true, true, true);
-//   }
-//   {
-//     var __result1 = testcase();
-//     var __expect1 = true;
-//   }
-//   
+  function testcase() 
+  {
+    var obj = {
+      
+    };
+    Object.defineProperty(obj, "foo", {
+      value : 200,
+      enumerable : true,
+      writable : true,
+      configurable : true
+    });
+    Object.defineProperties(obj, {
+      foo : {
+        value : undefined
+      }
+    });
+    return dataPropertyAttributesAreCorrect(obj, "foo", undefined, true, true, true);
+  }
+  {
+    var __result1 = testcase();
+    var __expect1 = true;
+  }
+  
+function dataPropertyAttributesAreCorrect(obj,
+                                          name,
+                                          value,
+                                          writable,
+                                          enumerable,
+                                          configurable) {
+    var attributesCorrect = true;
+
+    if (obj[name] !== value) {
+        if (typeof obj[name] === "number" &&
+            isNaN(obj[name]) &&
+            typeof value === "number" &&
+            isNaN(value)) {
+            // keep empty
+        } else {
+            attributesCorrect = false;
+        }
+    }
+
+    try {
+        if (obj[name] === "oldValue") {
+            obj[name] = "newValue";
+        } else {
+            obj[name] = "OldValue";
+        }
+    } catch (we) {
+    }
+
+    var overwrited = false;
+    if (obj[name] !== value) {
+        if (typeof obj[name] === "number" &&
+            isNaN(obj[name]) &&
+            typeof value === "number" &&
+            isNaN(value)) {
+            // keep empty
+        } else {
+            overwrited = true;
+        }
+    }
+    if (overwrited !== writable) {
+        attributesCorrect = false;
+    }
+
+    var enumerated = false;
+    for (var prop in obj) {
+        if (obj.hasOwnProperty(prop) && prop === name) {
[…]

### 2016-10-10 tests/test262/15.4/15.4.4/15.4.4.14/15.4.4.14-5-27.js

@@ -1,0 +1,44 @@
+// XXX
+//  function testcase() 
+//  {
+//    var stepThreeOccurs = false;
+//    var stepFiveOccurs = false;
+//    var obj = {
+//      
+//    };
+//    Object.defineProperty(obj, "length", {
+//      get : (function () 
+//      {
+//        return {
+//          valueOf : (function () 
+//          {
+//            stepThreeOccurs = true;
+//            if (stepFiveOccurs)
+//            {
+//              throw new Error("Step 5 occurred out of order");
+//            }
+//            return 20;
+//          })
+//        };
+//      }),
+//      configurable : true
+//    });
+//    var fromIndex = {
+//      valueOf : (function () 
+//      {
+//        stepFiveOccurs = true;
+//        return 0;
+//      })
+//    };
+//    try
+//{      Array.prototype.indexOf.call(obj, undefined, fromIndex);
+//      return stepThreeOccurs && stepFiveOccurs;}
+//    catch (ex)
+//{      return false;}
+//
+//  }
+//  {
+//    var __result1 = testcase();
+//    var __expect1 = true;
+//  }
+//  

### 2016-10-12 doc/chap-3-refman.tex
Fixed a typo
Fixed a typo in the manual
show all function list and fid -> func in print command of console

@@
 \hspace*{4.8em}\verb!-cfgBuilder:out={out}!\\
-\hspace*{4.8em}\verb!-cfgBuilder:dot={dot}!
+\hspace*{4.8em}\verb!-cfgBuilder:dot={name}!
 
@@
 \hspace*{4.4em}\verb!-analyzer:console!\\
-\hspace*{4.4em}\verb!-analyzer:html={html}!
+\hspace*{4.4em}\verb!-analyzer:html={name}!
 
@@
        print loc {LocName} ({keyword})
-       print fid {functionID}
+       print func {functionID}
        print worklist
@@
 \medskip\noindent
-\fbox{\texttt{print fid \{functionID\}}}\\[.2em]
-It displays the name and the span information of
-a given function id.  For example:
+\fbox{\texttt{print func (\{functionID\})}}\\[.2em]
+It displays the list of functions.
+If a function id is given, it displays the name and the span of it.
+For example:
 {\small
@@
 <function[0] top-level: ExitExc[-3], ()> @test.js:21:1
-Iter[12] > print fid 0
+Iter[12] > print func 0
 * function name: top-level

### 2016-10-21 src/main/scala/kr/ac/kaist/safe/analyzer/models/Code.scala
edit CFG document

@@ -29,7 +29,7 @@ abstract class Code {
     val argsName: String = s"<>arguments<>$funName"
     val ir: IRModelFunc = IRModelFunc(ModelFunc(ASTNodeInfo(Span(funName))))
     val func: CFGFunction =
-      cfg.createFunction(argsName, Nil, Nil, funName, ir, "", false)
+      cfg.createFunction(argsName, Nil, Nil, funName, ir, false)
     (funName, argsName, func)
   }
 }

### 2016-10-28 doc/safe-ir.tex

@@
 \chapter{IR}
+This section describes each construct of the \safe IR
+in both the BNF notation and its corresponding implementation.
+The implementation of IR nodes is available at:
+\begin{verbatim}
+$SAFE_HOME/src/main/scala/kr/ac/kaist/safe/nodes/ir/
+\end{verbatim}
 \small
@@
 \begin{array}{llll}
-\ir\pgm & ::= & \ir\stmt^* & \mtt{IRRoot(val fds:~List[IRFunDecl], val vds:~List[IRVarStmt],}\\
-&&&\mtt{\phantom{IRRoot(}val irs:~List[IRStmt])}\\
+\ir\pgm & ::= & \ir\stmt^* \\
+&& \mtt{IRRoot(val fds:~List[IRFunDecl],}\\
+&&\mtt{\phantom{IRRoot(}val vds:~List[IRVarStmt],}\\
+&&\mtt{\phantom{IRRoot(}val irs:~List[IRStmt])}\\\\
 
-\ir\stmt & ::= & \irid \ \verb+=+ \ \ir\expr &
- \mtt{IRExprStmt(val lhs:~IRId, val right:~IRExpr, val ref:~Boolean)}\\
+\ir\stmt & ::= & \irid \ \verb+=+ \ \ir\expr \\
+&& \mtt{IRExprStmt(val lhs:~IRId, val right:~IRExpr,}\\
+&&\mtt{\phantom{IRExprStmt(}val ref:~Boolean)}\\
+&\mid& \irid \ \verb+=+ \ {\sf delete}\ \irid\\
+&& \mtt{IRDelete(val lhs:~IRId, val id:~IRId)}\\
+&\mid& \irid \ \verb+=+ \ {\sf delete}\ \irid\verb+[+\irid\verb+]+\\
+&& \mtt{IRDeleteProp(val lhs:~IRId, val obj:~IRId,}\\
+&&\mtt{\phantom{IRDeleteProp(}val index:~IRExpr)}\\
+&\mid& \irid\verb+[+\irid\verb+] =+ \ \irexpr \\
+&& \mtt{IRStore(val obj:~IRId, val index:~IRExpr,}\\
+&&\mtt{\phantom{IRStore(}val rhs:~IRExpr)}\\
+ &\mid& \irid \ \verb+=+ \ \verb+{+ (\ir\member\verb+,+)^* \verb+}+\\
+&& \mtt{IRObject(val lhs:~IRId, val members:~List[IRMember],}\\
+&&\mtt{\phantom{IRObject(}val proto:~Option[IRId])}\\
+ &\mid& \irid \ \verb+=+ \ \verb+[+ (\irexpr\verb+,+)^* \verb+]+ \\
+&& \mtt{IRArray(val lhs:~IRId,}\\
+&&\mtt{\phantom{IRArray(}val elements:~List[Option[IRExpr]])}\\
+&&\mtt{IRArgs(val lhs:~IRId,}\\
+&&\mtt{\phantom{IRArray(}val elements:~List[Option[IRExpr]])}\\
+ &\mid& \irid \ \verb+=+ \ \irid\verb+(+\irid\verb+,+\irid\verb+)+\\
+&& \mtt{IRCall(val lhs:~IRId, val fun:~IRId,}\\
+&&\mtt{\phantom{IRCall(}val thisB:~IRId, val args:~IRId)}\\
+ &\mid& \irid \ \verb+=+ \ \irid\verb+(+\irid(\verb+,+\irid)^?\verb+)+\\
+&& \mtt{IRInternalCall(val lhs:~IRId, val fun:~IRId,}\\
+&&\mtt{\phantom{IRInternalCall(}val first:~IRExpr,}\\
+&&\mtt{\phantom{IRInternalCall(}val second:~Option[IRId])}\\
+&&{\inblue \mtt{toObject}, \mtt{toNumber}, \mtt{isObject},
+\mtt{getBase}, \mtt{iteratorInit},}\\
+&&{\inblue \mtt{iteratorHasNext}, \mtt{iteratorKey}}\\
 
-&\mid& \irid \ \verb+=+ \ {\sf delete}\ \irid
-& \mtt{IRDelete(val lhs:~IRId, val id:~IRId)}\\
-
- &\mid& \irid \ \verb+=+ \ {\sf delete}\ \irid\verb+[+\irid\verb+]+
- & \mtt{IRDeleteProp(val lhs:~IRId, val obj:~IRId, val index:~IRExpr)}\\
-
- &\mid& \irid\verb+[+\irid\verb+] =+ \ \irexpr & \mtt{IRStore(val obj:~IRId, val index:~IRExpr, val rhs:~IRExpr)}\\
- &\mid& \irid \ \verb+=+ \ \verb+{+ (\ir\member\verb+,+)^* \verb+}+
- & \mtt{IRObject(val lhs:~IRId, val members:~List[IRMember],}\\
-&&&\mtt{\phantom{IRObject(}val proto:~Option[IRId])}\\
- &\mid& \irid \ \verb+=+ \ \verb+[+ (\irexpr\verb+,+)^* \verb+]+ & \mtt{IRArray(val lhs:~IRId, val elements:~List[Option[IRExpr]])}\\
-&&&\mtt{IRArgs(val lhs:~IRId, val elements:~List[Option[IRExpr]])}\\
-
- &\mid& \irid \ \verb+=+ \ \irid\verb+(+\irid\verb+,+\irid\verb+)+
-& \mtt{IRCall(val lhs:~IRId, val fun:~IRId, val thisB:~IRId,}\\
-&&&\mtt{\phantom{IRCall(}val args:~IRId)}\\
- &\mid& \irid \ \verb+=+ \ \irid\verb+(+\irid(\verb+,+\irid)^?\verb+)+
-& \mtt{IRInternalCall(val lhs:~IRId, val fun:~IRId, val first:~IRExpr,}\\
-&&&\mtt{\phantom{IRInternalCall(}val second:~Option[IRId])}\\
-&&&{\inblue \mtt{toObject}, \mtt{toNumber}, \mtt{isObject},
-\mtt{getBase}, \mtt{iteratorInit},}\\
-&&&{\inblue \mtt{iteratorHasNext}, \mtt{iteratorKey}}\\
-
- &\mid& \irid \ \verb+=+ \ {\sf new}\ \irid\verb+(+(\irid\verb+,+)^*\verb+)+
- & \mtt{IRNew(val lhs:~IRId, val fun:~IRId, val args:~List[IRId])}\\
- &\mid& \irid \ \verb+=+ \ {\sf function} \ \ir{f} \verb+(+\irid\verb+,+\irid\verb+) {+ \ir\stmt^* \verb+}+
-& \mtt{IRFunExpr(val lhs:~IRId, val fun:~IRFunctional)}\\
-&&&\mtt{IRFunctional(val fromSource:~Boolean, val name:~IRId,}\\
-&&&\mtt{\phantom{IRFunctional(}val params:~List[IRId], val args:~List[IRStmt],}\\
-&&&\mtt{\phantom{IRFunctional(}val fds:~List[IRFunDecl],}\\
-&&&\mtt{\phantom{IRFunctional(}val vds:~List[IRVarStmt], val body:~List[IRStmt])}\\
-
- &\mid& {\sf function} \ \ir{f} \verb+(+\irid\verb+,+\irid\verb+) {+ \ir\stmt^* \verb+}+
- & \mtt{IRFunDecl(val ftn:~IRFunctional)}\\
-
- &\mid& \irid \ \verb+=+ \ {\sf eval}\verb+(+\ir\expr\verb+)+ & \mtt{IREval(val lhs:~IRId, val arg:~IRExpr)}\\
- &\mid& {\sf break} \ \irid & \mtt{IRBreak(val label:~IRId)}\\
- &\mid& {\sf return} \ \irexpr^?& \mtt{IRReturn(val expr:~Option[IRExpr])}\\
- &\mid& {\sf with} \ \verb+(+\irid\verb+)+ \ \ir\stmt & \mtt{IRWith(val id:~IRId, val stmt:~IRStmt)}\\
- & \mid & \ir{l} \; \verb+: {+ \; \ir\stmt \; \verb+}+
- & \mtt{IRLabelStmt(val label:~IRId, val stmt:~IRStmt)}\\
- &\mid& {\sf var} \ \irid& \mtt{IRVarStmt(val lhs:~IRId, val fromParam:~Boolean)}\\
-
- &\mid& {\sf throw} \ \irexpr& \mtt{IRThrow(val expr:~IRExpr)}\\
- &\mid& {\ir\stmt}^*& \mtt{IRSeq(val stmts:~List[IRStmt])}\\
- &\mid& {\sf if} \ \verb+(+\irexpr\verb+)+\ {\sf then} \ \ir\stmt \ ({\sf else} \ \ir\stmt)^?
-& \mtt{IRIf(val expr:~IRExpr, val trueB:~IRStmt,}\\
-&&&\mtt{\phantom{IRIf(}val falseb:~Option[IRStmt])}\\
-
- &\mid& {\sf while} \ \verb+(+\irexpr\verb+)+\ \ir\stmt& \mtt{IRWhile(val cond:~IRExpr, val body:~IRStmt)}\\
- &\mid& {\sf try} \ \verb+{+ \ir\stmt \verb+}+ \
-({\sf catch} \ \verb+(+\irid\verb+){+ \ir\stmt \verb+}+)^?
-& \mtt{IRTry(val body:~IRStmt, val name:~Option[IRId],}\\
-&& \phantom{{\sf try} \{ \ir\stmt \}\ \ \ }
-({\sf finally} \ \verb+{+ \ir\stmt \verb+}+)^?
-&\mtt{\phantom{IRTry(}val catchB:~Option[IRStmt], finallyB:~Option[IRStmt])}\\
-&\mid& \open {\ir\stmt}^* \close & \mtt{IRStmtUnit(List[IRStmt] stmts)}\\
+ &\mid& \irid \ \verb+=+ \ {\sf new}\ \irid\verb+(+(\irid\verb+,+)^*\verb+)+\\
+&& \mtt{IRNew(val lhs:~IRId, val fun:~IRId,}\\
+&&\mtt{\phantom{IRNew(}val args:~List[IRId])}\\
 \end{array}
@@
 \begin{array}{llll}
+ &\mid& \irid \ \verb+=+ \ {\sf function} \ \ir{f} \verb+(+\irid\verb+,+\irid\verb+) {+ \ir\stmt^* \verb+}+\\
+&& \mtt{IRFunExpr(val lhs:~IRId, val fun:~IRFunctional)}\\
+&&\mtt{IRFunctional(val fromSource:~Boolean,}\\
+&&\mtt{\phantom{IRFunctional(}val name:~IRId,}\\
+&&\mtt{\phantom{IRFunctional(}val params:~List[IRId],}\\
+&&\mtt{\phantom{IRFunctional(}val args:~List[IRStmt],}\\
+&&\mtt{\phantom{IRFunctional(}val fds:~List[IRFunDecl],}\\
+&&\mtt{\phantom{IRFunctional(}val vds:~List[IRVarStmt],}\\
+&&\mtt{\phantom{IRFunctional(}val body:~List[IRStmt])}\\
+ &\mid& {\sf function} \ \ir{f} \verb+(+\irid\verb+,+\irid\verb+) {+ \ir\stmt^* \verb+}+\\
+&& \mtt{IRFunDecl(val ftn:~IRFunctional)}\\
+ &\mid& \irid \ \verb+=+ \ {\sf eval}\verb+(+\ir\expr\verb+)+ \\
+&& \mtt{IREval(val lhs:~IRId, val arg:~IRExpr)}\\
+ &\mid& {\sf break} \ \irid \\
+&& \mtt{IRBreak(val label:~IRId)}\\
+ &\mid& {\sf return} \ \irexpr^?\\
+&& \mtt{IRReturn(val expr:~Option[IRExpr])}\\
+ &\mid& {\sf with} \ \verb+(+\irid\verb+)+ \ \ir\stmt\\
+&& \mtt{IRWith(val id:~IRId, val stmt:~IRStmt)}\\
+ & \mid & \ir{l} \; \verb+: {+ \; \ir\stmt \; \verb+}+\\
+ && \mtt{IRLabelStmt(val label:~IRId, val stmt:~IRStmt)}\\
+ &\mid& {\sf var} \ \irid\\
+&& \mtt{IRVarStmt(val lhs:~IRId, val fromParam:~Boolean)}\\
+ &\mid& {\sf throw} \ \irexpr\\
+&& \mtt{IRThrow(val expr:~IRExpr)}\\
+ &\mid& {\ir\stmt}^*\\
+&& \mtt{IRSeq(val stmts:~List[IRStmt])}\\
+ &\mid& {\sf if} \ \verb+(+\irexpr\verb+)+\ {\sf then} \ \ir\stmt \ ({\sf else} \ \ir\stmt)^?\\
+&& \mtt{IRIf(val expr:~IRExpr, val trueB:~IRStmt,}\\
+&&\mtt{\phantom{IRIf(}val falseb:~Option[IRStmt])}\\
+ &\mid& {\sf while} \ \verb+(+\irexpr\verb+)+\ \ir\stmt\\
+&& \mtt{IRWhile(val cond:~IRExpr, val body:~IRStmt)}\\
+%
+ &\mid& {\sf try} \ \verb+{+ \ir\stmt \verb+}+ \
+({\sf catch} \ \verb+(+\irid\verb+){+ \ir\stmt \verb+}+)^? ({\sf finally} \ \verb+{+ \ir\stmt \verb+}+)^?\\
+&& \mtt{IRTry(val body:~IRStmt, val name:~Option[IRId],}\\
+&&\mtt{\phantom{IRTry(}val catchB:~Option[IRStmt],}\\
+&&\mtt{\phantom{IRTry(}finallyB:~Option[IRStmt])}\\
+&\mid& \open {\ir\stmt}^* \close\\
+&& \mtt{IRStmtUnit(List[IRStmt] stmts)}\\\\
 \ir\expr &::=&
- \irexpr \ \inop \irexpr & \mtt{IRBin(val first:~IRExpr, val op:~IROp, val second:~IRExpr)}\\
- &\mid& \preop \irexpr & \mtt{IRUn(val op:~IROp, val expr:~IRExpr)}\\
- &\mid& \irid\verb+[+\ir\expr\verb+]+ & \mtt{IRLoad(val obj:~IRId, val index:~IRExpr)}\\
- &\mid& \irid& \mtt{IRUserId(val global:~Boolean, val isWith:~Boolean)}\\
- &\mid& \newvar{x}& \mtt{IRTmpId(val global:~Boolean)}\\
- &\mid& \ir\num & \mtt{IRNumber(val text:~String, val num:~Double)}\\
- &\mid& \ir\str & \mtt{IRString(val str:~String)}\\
- &\mid& {\sf true} & \mtt{IRBool(val bool:~Boolean)}\\
- &\mid& {\sf false} & \mtt{IRBool(val bool:~Boolean)}\\
- &\mid& {\sf undefined} & \mtt{IRUndef()}\\
- &\mid& {\sf null} & \mtt{IRNull()}\\
- &\mid& {\sf this} & \mtt{IRThis()}\\\\
-
-\ir\member &::=& \irid \ \verb+:+ \ \irexpr & \mtt{IRField(val prop:~IRId, val expr:~IRExpr)}\\
- &\mid& {\tt get}\ \ir{f} \verb+(+\irid\verb+,+\irid\verb+) {+ \ir\stmt^* \verb+}+
- &\mtt{IRGetProp(val ftn:~IRFunctional)}\\
- &\mid& {\tt set}\ \ir{f} \verb+(+\irid\verb+,+\irid\verb+) {+ \ir\stmt^* \verb+}+
- &\mtt{IRSetProp(val ftn:~IRFunctional)}\\
-
+ \irexpr \ \inop \irexpr \\
+&& \mtt{IRBin(val first:~IRExpr, val op:~IROp,}\\
+&& \mtt{\phantom{IRBin(}val second:~IRExpr)}\\
+ &\mid& \preop \irexpr \\
+&& \mtt{IRUn(val op:~IROp, val expr:~IRExpr)}\\
+ &\mid& \irid\verb+[+\ir\expr\verb+]+ \\
+&& \mtt{IRLoad(val obj:~IRId, val index:~IRExpr)}\\
+ &\mid& \irid\\
+&& \mtt{IRUserId(val global:~Boolean, val isWith:~Boolean)}\\
+ &\mid& \newvar{x}\\
+&& \mtt{IRTmpId(val global:~Boolean)}\\
+ &\mid& \ir\num \\
+&& \mtt{IRNumber(val text:~String, val num:~Double)}\\
+ &\mid& \ir\str \\
+&& \mtt{IRString(val str:~String)}\\
+ &\mid& {\sf true} \\
+&& \mtt{IRBool(val bool:~Boolean)}\\
+ &\mid& {\sf false} \\
+&& \mtt{IRBool(val bool:~Boolean)}\\
 \end{array}
@@
 
-Assumptions and notations:
+\[
+\begin{array}{llll}
+ &\mid& {\sf undefined} \\
+&& \mtt{IRUndef()}\\
+ &\mid& {\sf null} \\
+&& \mtt{IRNull()}\\
+ &\mid& {\sf this} \\
+&& \mtt{IRThis()}\\\\
+
+\ir\member &::=& \irid \ \verb+:+ \ \irexpr\\
+&& \mtt{IRField(val prop:~IRId, val expr:~IRExpr)}\\
+ &\mid& {\tt get}\ \ir{f} \verb+(+\irid\verb+,+\irid\verb+) {+ \ir\stmt^* \verb+}+\\
+&&\mtt{IRGetProp(val ftn:~IRFunctional)}\\
+ &\mid& {\tt set}\ \ir{f} \verb+(+\irid\verb+,+\irid\verb+) {+ \ir\stmt^* \verb+}+\\
+&&\mtt{IRSetProp(val ftn:~IRFunctional)}\\
+\end{array}
+\]
+
+The \safe IR has the following assumptions and notations:
 \begin{itemize}
-\item Functions and variables are hoisted to their closest enclosing functions
-or the top level via {\tt Hoister}.
+\item We denote a list as a possibly empty, semicolon-separated sequence, enclosed by $\langle$ and $\rangle$.
+\item We denote a series of list appends as superscripted $*$ such as $\stmt^*$.
+\item We abuse our notations by interchanging semicolon-separated sequences and lists.
+\item To denote an AST-level statement granularity in the translated IR statements,
+we use {\tt IRStmtUnit} which is represented as green angle brackets {\ingreen $\open\ \close$} in this document.
+\item Declarations of functions and variables are hoisted to their closest enclosing functions
+or the top level via the \verb!Hoister! transformation of the \verb!astRewriter! phase.
 \item Identifiers and labels that exist in the source program,
 except when they appear at top level or within the {\tt with} statement,
-are already disambiguated via {\tt Disambiguator},
+are already disambiguated via the \verb!Disambiguator! transformation of the \verb!astRewriter! phase
 so that they have unique names.
-\item We use $\env$ to disambiguate the generated labels and temporary variables in the AST to IR translation.
-For the presentation brevity, we simply add the newly generated names to $\env$.
-\begin{itemize}
-\item In the actual implementation, we need to create a unique id for each generated name and
-add the binding information from the general name to the unique id to $\env$.
-For example, when we say ``$\env; \newvar{break}$'',
-we actually create a unique id for $\newvar{break}$, say $\newvar{break}_{42}$, and add it to $\env$ as $\env; \newvar{break} \mapsto \newvar{break}_{42}$.
-When we look up the environment by $\env(\newvar{break})$, the unique $\newvar{break}_{42}$ is returned.
-\item In the scope when the generated name is created, we don't add it to the environment but use the unique id instead of the general name.
-For example, when we say ``$\newvar{eq}\ \verb+=+\ \env(\newvar{val}) \verb+===+ \newvar{break};$'',
-we create a unique id for \newvar{eq}, say $\newvar{eq}_{910157}$, and it is acually
-``$\newvar{eq}_{910157}\ \verb+=+\ \env(\newvar{val}) \verb+===+ \newvar{break}_{42};$''.
-\item To be clear, we use blue for the binding sites of such names and red for the use sites of such names.
 \end{itemize}
-\item We denote a list as a possibly empty, semicolon-separated sequence, enclosed by $\langle$ and $\rangle$.
-\item We denote a series of list appends as superscripted $*$ such as $\stmt^*$.
-\item We denote a fresh variable name as $\newvar{}$ and its variants.
-\item We abuse our notations by mixing semicolon-separated sequences and lists.
-\item We use the following:\\
-\verb+===+, {\sf \ensuremath{\diamond}toObject}, {\sf \ensuremath{\diamond}toNumber}, {\sf \ensuremath{\diamond}isObject},
-{\sf \ensuremath{\diamond}iteratorInit}, {\sf \ensuremath{\diamond}iteratorHasNext}, {\sf \ensuremath{\diamond}iteratorNext},
-% {\sf startsWith},
-{\sf \ensuremath{\diamond}global}, {\sf \ensuremath{\diamond}getBase}
-\item To denote an AST-level statement granularity in the translated IR statements,
-we use {\tt IRStmtUnit} which is represented as green angle brackets {\ingreen $\open\ \close$} in this document.
-To reduce the number of temporary variables, we use global variables to denote constants such as {\sf 1} and
-{\sf true} which is represented in green {\ingreen\sf 1} and  {\ingreen\sf true} in this document.
-\item We wrap a possibly identical assignment with a box so that the actual implementation, {\tt Translator}, can eliminate identical assignments.
-\end{itemize}

### 2016-10-29 doc/chap-3-refman.tex
Made the console debugger take names for printing CFGs and HTMLs

@@
 \begin{verbatim}
-safe analyze -astRewriter:silent
+safe analyze -silent
              -cfgBuilder:out=out sample.js
@@
 \end{itemize}
+and the global options are \verb!-silent! and \verb!-testMode!.
 
@@
 \medskip\noindent
-\fbox{\texttt{print cfg}}\\[.2em]
-It prints the current CFG to files \verb!cfg.gv! and \verb!cfg.pdf!.
+\fbox{\texttt{print cfg \{name\}}}\\[.2em]
+It prints the current CFG to files \verb!name.gv! and \verb!name.pdf!.
 
 \medskip\noindent
-\fbox{\texttt{print html}}\\[.2em]
-It prints the current CFG and its state to the \verb!cfg.html! file.
+\fbox{\texttt{print html \{name\}}}\\[.2em]
+It prints the current CFG and its state to the \verb!name.html! file.
 We describe this facility in the next section.

### 2016-10-29 doc/safe-overview.tex
Renamed overview.tex as safe-overview.tex

--- 2016-10-10 doc/chap-2-intro.tex
@@
-%--------------------------------------------------------------------
-% Brief general description of the structure of the analyzer
-%--------------------------------------------------------------------
-\chapter{\safe}
+\chapter{Overview}\label{c:1:overview}
 
@@
 
+\section{Audience}
+This document is for users of \safe (Scalable Analysis Framework for ECMAScript)
+2.0, a scalable and pluggable analysis framework for JavaScript web applications.
+General information on the \safe project is available at an invited talk at ICFP 2016~\cite{safeicfp16}:
+\begin{center}
+  \url{https://www.youtube.com/watch?v=gEU9utf0sxE}
+\end{center}
+and the source code and publications are available at:
+\begin{center}
+  \url{https://github.com/sukyoung/safe}
+\end{center}
+For more information, please contact the main developers of \safe
+at \texttt{safe [at] plrg.kaist.ac.kr}.
+
+SAFE has been used by:
+\begin{itemize}
+\itemsep-.2em
+\item JSAI~\cite{jsai} @ UCSB
+\item ROSAEC~\cite{rosaec} @ Seoul National University
+\item K framework~\cite{kjs} @ UIUC
+\item Ken Cheung~\cite{emse16} @ HKUST
+\item Web-based vulnerability detection~\cite{oracle} @ Oracle
+\item Tizen~\cite{tizen} @ Linux Foundation
+\end{itemize}
+
+\section{Contributors}
+The main developers of SAFE 2.0 are as follows:
+\begin{itemize}
+\itemsep-.2em
+\item Jihyeok Park
+\item Yeonhee Ryou
+\item Sukyoung Ryu
+\end{itemize}
+and the following have contributed to the source code:
+\begin{itemize}
+\itemsep-.1em
+\item Minsoo Kim (Built-in function modeling)
+\item PLRG @ KAIST and our colleagues in S-Core and Samsung Electronics (SAFE 1.0)
+\end{itemize}
+
+\section{License}
+The \safe source code is released under the BSD license:
+\begin{center}
+\url{github.com/sukyoung/safe/blob/master/LICENSE}
+\end{center}
+
 \section{A sample use of \safe}
@@
 where the names prefixed by \verb!<>! are generated by \safe.
-\safe translates the rewritten JavaScript source code to its intermediate representation
-format, and one can see the result by the command below:
-\begin{verbatim}
-safe compile sample.js
-\end{verbatim}
-which shows an output like the following:
-{\small
-\begin{verbatim}
-The command 'compile' took 382 ms.
-{
-  {
-    <>new1<>1 = {
-      a : 1
-    }
-    <>Global<>ignore1 = <>Global<>toObject(<>new1<>1)
-    <>alpha<>2 = <>Global<>ignore1
-  }
-  if("a" in <>alpha<>2)
-  {
-    <>obj<>3 = <>Global<>toObject(<>alpha<>2)
-    <>obj<>3["a"] = 2
-    <>Global<>ignore2 = <>obj<>3["a"]
-  }
-  else
-  {
-    a = 2
-    <>Global<>ignore2 = 2
-  }
-}
-\end{verbatim}
-}
-\noindent
 The \safe analysis is performed on control flow graphs of programs,
@@
   Entry[-1] -> [0]
-
   Block[0] -> [2], [1], ExitExc
@@
     [4] <>alpha<>2 := <>Global<>ignore1
-
   Block[1] -> [3], ExitExc
@@
     [3] <>Global<>ignore2 := <>obj<>3["a"]
-
   Block[2] -> [3], ExitExc
@@
     [2] <>Global<>ignore2 := 2
-
   Block[3] -> Exit
     [0] noop(EndOfFile)
-
   Exit[-2]
-
   ExitExc[-3]
@@
 \begin{verbatim}
-The command 'analyze' took 1002 ms.
 ** heap **
-#Global -> [[Class]] : "Object"
 ...
@@
       Set(a)
-
-** context **
-\end{verbatim}
-\vspace*{-.6em}
-\verb!##Collapsed -> [[Default]] @->! $\bot$\verb!(value)!
-\vspace*{-.6em}
-\begin{verbatim}
-               * Outer: null
-#GlobalEnv -> Top(global environment record)
-              * Outer: null
 ...
-this: #Global
-
-** old address set **
-mayOld: (1)
-mustOld: (1)
 

### 2016-10-29 tests/test262/10.6/S10.6_A5_T2.js
1. Added Test262 for ECMAScript chapters 6~10. 2. Added benchmarks: sunspider, v8, and jsai. 3. Added CFG and IR2CFG translation rules to the user manual. 4. Added a SAFE specification. 5. Made states, heaps, and objects as abstract domains.

@@ -1,0 +1,39 @@
+  function f1() 
+  {
+    for(var x in arguments)
+    {
+      if (x === "length")
+      {
+        return false;
+      }
+    }
+    return true;
+  }
+  try
+{    {
+      var __result1 = ! f1();
+      var __expect1 = false;
+    }}
+  catch (e)
+{    $ERROR("#1: arguments object don't exists");}
+
+  var f2 = (function () 
+  {
+    for(var x in arguments)
+    {
+      if (x === "length")
+      {
+        return false;
+      }
+    }
+    return true;
+  });
+  try
+{    {
+      var __result2 = ! f2();
+      var __expect2 = false;
+    }}
+  catch (e)
+{    $ERROR("#2: arguments object don't exists");}
+
+  

### 2016-10-29 tests/test262/7.6/7.6.1/7.6.1-5-11.js

@@ -1,0 +1,23 @@
+  function testcase() 
+  {
+    var tokenCodes = {
+      enum : 0,
+      extends : 1,
+      super : 2
+    };
+    var arr = ['enum', 'extends', 'super', ];
+    for(var i = 0;i < arr.length;i++)
+    {
+      if (tokenCodes[arr[i]] !== i)
+      {
+        return false;
+      }
+      ;
+    }
+    return true;
+  }
+  {
+    var __result1 = testcase();
+    var __expect1 = true;
+  }
+  

### 2016-10-29 tests/test262/8.12/8.12.1/8.12.1-1_1.js

@@ -1,0 +1,12 @@
+  function testcase() 
+  {
+    var o = {
+      
+    };
+    return o.hasOwnProperty("foo") === false;
+  }
+  {
+    var __result1 = testcase();
+    var __expect1 = true;
+  }
+  

### 2016-10-29 tests/test262/8.12/8.12.1/8.12.1-1_4.js

@@ -1,0 +1,15 @@
+  function testcase() 
+  {
+    var o = {
+      
+    };
+    Object.defineProperty(o, "foo", {
+      value : 42
+    });
+    return o.hasOwnProperty("foo");
+  }
+  {
+    var __result1 = testcase();
+    var __expect1 = true;
+  }
+  

### 2016-10-29 tests/test262/8.3/S8.3_A1_T1.js

@@ -1,0 +1,15 @@
+  {
+    var __result1 = x !== undefined;
+    var __expect1 = false;
+  }
+  var x = true;
+  var y = false;
+  {
+    var __result2 = x !== true;
+    var __expect2 = false;
+  }
+  {
+    var __result3 = y !== false;
+    var __expect3 = false;
+  }
+  

### 2016-11-07 doc/icse-demo/main.tex
ICSE demonstrations track submission: first draft

\documentclass[10pt, conference]{IEEEtran}
\usepackage[pdftex]{graphicx}

\usepackage[ruled,lined]{algorithm2e}
\usepackage{amsfonts,amssymb,amsmath, tikz,kotex,mathtools}
\usepackage{microtype,xspace}
\usepackage{url,color,multirow}
\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
\usepackage{stmaryrd}
\newcommand{\mtt}[1]{\texttt{\small #1}}
\newcommand{\msf}[1]{{\sf\small #1}}
\newcommand{\oldsafe}{{SAFE 1.0}\xspace}
\newcommand{\safe}{{SAFE 2.0}\xspace}
\newcommand{\htmldebug}{{\sf\small HTML Debugger}\xspace}

\hyphenation{op-tical net-works semi-conduc-tor}
\begin{document}
\title{\hspace*{-.7em}
Analysis of JavaScript Web Applications\\ Using \safe}

\author{\IEEEauthorblockN{Jihyeok Park}
\IEEEauthorblockA{KAIST\\
{ jhpark0223@kaist.ac.kr}}
\and
\IEEEauthorblockN{Yeonhee Ryou}
\IEEEauthorblockA{KAIST\\
{ ryou770@kaist.ac.kr}}
\and
\IEEEauthorblockN{Joonyoung Park}
\IEEEauthorblockA{KAIST\\
{ gmb55@kaist.ac.kr}}
\and
\IEEEauthorblockN{Sukyoung Ryu}
\IEEEauthorblockA{KAIST\\
{ sryu.cs@kaist.ac.kr}}}
\maketitle

\begin{abstract}
JavaScript has been the language for web applications, and
the growing prevalence of web environments in various devices
makes JavaScript web applications even more ubiquitous.
However, because JavaScript and web environments are
extremely dynamic, JavaScript web applications are often
vulnerable to type-related errors and security attacks.
To lessen the problem, researchers have developed various analysis
techniques in different analyzers, but they are not especially
aimed for usability.  In this paper, we present \safe, a scalable
analysis framework for ECMAScript especially aimed to be a playground
for advanced research in JavaScript web applications.  \safe is designed
to be light-weight, which supports configurability, extensibility, and
debuggability.
\end{abstract}

\section{Introduction}
JavaScript has become the language for web applications, but
JavaScript web applications are often vulnerable to programmer
errors and security attacks.  Because JavaScript provides
extremely functional and dynamic features and high portability
with web environments, web developers build web applications
mostly in JavaScript these days.  However, the characteristics
that brought the prevalent uses of JavaScript web applications
also introduce difficulties in building correct web applications.
The extremely functional and dynamic features make programs
hard to write correctly and hard to reason about.
Also, the dynamism and portability of web environments make
web applications vulnerable to security attacks.

To help JavaScript developers build correct programs, researchers
have developed analyzers that support various analysis techniques,
but they are not especially designed for usability.
SAFE\footnote{\url{http://plrg.kaist.ac.kr/redmine/projects/jsf/repository}}~\cite{Lee12}
is a scalable analysis framework for ECMAScript, and it has adopted recent research results incrementally.
While more analysis techniques make SAFE more featureful,
they make the code base of SAFE large and complex, which makes it
difficult for new users to understand the code base.
TAJS\footnote{\url{https://github.com/cs-au-dk/TAJS}}~\cite{TAJSDETER})
is a dataflow analysis for JavaScript that infers type information and call graphs.
It also provides analysis techniques published by the TAJS team with options;
for example, the {\tt -determinacy} option enables the techniques described in~\cite{TAJSDETER}.
WALA\footnote{\url{http://wala.sourceforge.net/wiki/index.php}}~\cite{Schafer13}
was originally developed for pointer analysis of Java programs, and it
also supports flow-insensitive pointer analysis of JavaScript programs.
Because WALA aims to support analysis of multiple programming languages,
the source code repository is huge with many packages.
While SAFE, TAJS, and WALA are mainly static analyzers possibly using dynamic information,
Jalangi\footnote{\url{https://github.com/SRA-SiliconValley/jalangi}}~\cite{Sen13}
is a dynamic analysis framework for JavaScript, which provides simple
traditional dynamic analyzers like a taint analyzer as example uses of the framework.

Let us consider SAFE more closely.  It was first designed to analyze pure
JavaScript benchmarks~\cite{Lee12}.  It provides a default static analyzer
based on the abstract interpretation framework, and it supports
flow-sensitive and context-sensitive analyses of stand-alone JavaScript
programs.  It performs several preprocessing steps on JavaScript code to
address some quirky semantics of JavaScript such as the {\tt with}
statement~\cite{dls13}.
%, and that part has been used by other researchers~\cite{jsai,kjs}.
It was then extended to model web application execution environments
of various browsers~\cite{safewapp} with HTML/DOM tree abstraction,
and it supports analysis of interactions between JavaScript applications
and native functions in platform-specific libraries by using automatic
modeling of library functions from API specifications~\cite{SAFEWAPI}.
Recent extensions of SAFE include aggressive integration of
soundy~\cite{soundy} analysis.  Instead of analyzing the entire concrete
behaviors of programs, it supports an analysis of partial
programs by using approximate call graphs from WALA~\cite{asewala}.
It also utilizes dynamic information statically to focus on specific
environments like specific browser versions~\cite{safehybrid}.
The more advanced analysis techniques SAFE integrates,
the more difficult it is for SAFE users to understand the SAFE code base.

\setcounter{figure}{1}
\begin{figure*}[t]
\centering
\begin{tabular}{c}
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
val commands: List[Command] = List(CmdParse, CmdASTRewrite, CmdCompile, CmdCFGBuild, CmdAnalyze,
                                   CmdBugDetect, CmdHelp)
var phases: List[Phase] = List(Parse, ASTRewrite, Compile, CFGBuild, Analyze, BugDetect, Help)
\end{verbatim}
\end{minipage}
\\[1.5em]
{\small (a) Add a new command and a new phase to the lists of available
commands and phases, respectively, in {\tt Safe.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object CmdBugDetect extends CommandObj("bugDetect", CmdAnalyze >> BugDetect) {
  override def display(cfg: CFG): Unit = println(cfg.toString(0))
}
\end{verbatim}
\end{minipage}
\\[1em]
{\small (b) Add the new command by specifying its name and phases in {\tt Command.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object BugDetect extends PhaseObj[(CFG, Int, CallContext), BugDetectConfig, CFG] {
  val name: String = "bugDetector"
  val help: String = "Detect possible bugs in JavaScript source files."
  def apply(in: (CFG, Int, CallContext), safeConfig: SafeConfig, config: BugDetectConfig): Try[CFG] = {
    val (cfg, _, _) = in
    // Bug detector implementation here.
    Success(cfg)
  }
  def defaultConfig: BugDetectConfig = BugDetectConfig()
  val options: List[PhaseOption[BugDetectConfig]] = List(
    ("silent", BoolOption(c => c.silent = true), "messages during analysis are muted.")
  )
}

case class BugDetectConfig(var silent: Boolean = false) extends Config

\end{verbatim}
\end{minipage}
\\
{\small (c) Implement the new phase in \mtt{phase/BugDetect.scala}}
\end{tabular}
\caption{\small Extension of \safe with a bug detector~\cite{safewapp}}
\label{fig:extensibility}
\end{figure*}

\setcounter{figure}{0}
\begin{figure}[t]
\centering
\begin{tabular}{|c|}\hline
\begin{minipage}{.3\textwidth}
\footnotesize
\begin{verbatim}
Some JSON code
that specifies
the configuration
(phases/options)
of selecting
analysis sensitivity
\end{verbatim}
\end{minipage}
\\\hline
\multicolumn{1}{c}{~}\\[-.7em]
\multicolumn{1}{c}{\small (a) Specifies selected analysis sensitivity}\\
\multicolumn{1}{c}{~}\\[-.7em]
\hline
\begin{minipage}{.3\textwidth}
\footnotesize
\begin{verbatim}
Some JSON code
that specifies
the configuration
(phases/options)
of selecting
abstract domains
\end{verbatim}
\end{minipage}\\\hline
\multicolumn{1}{c}{~}\\[-.7em]
\multicolumn{1}{c}{\small (b) Specifies selected abstract domains}\\
\multicolumn{1}{c}{~}\\[-.7em]
\end{tabular}
\caption{\small \safe analysis configuration files in JSON format}
\label{fig:configurability}
\end{figure}

In this paper, we present \safe, which is aimed to be a playground
for advanced research in JavaScript web applications.  Thus, we
intentionally designed it to be light-weight, highly parametric,
and modular.  The main features of \safe are as follows:
\begin{itemize}
\item Configurability: Because \safe supports various phases
like parsing, compilation, and analysis with many options like
verbosity, pretty printing, and analysis sensitivity, it provides
a declarative way to describe them concisely.

\item Extensibility: In order for researchers to experiment with their
new ideas easily or to reproduce research achievements from the
literature quickly, \safe supports well-designed APIs for adding new
phases or options.

\item Debuggability: To aid \safe users to understand and reason about
analysis results easily, it now supports \htmldebug, which lets users
investigate analysis status from browsers.  \safe has been tested using
Test262, the official ECMAScript conformance suite, and it allows users
to test their experimental analysis techniques with Test262.
\end{itemize}

\section{SAFE 2.0 Features}

\subsection{Configurability}
\safe supports various phases, options, and their combinations.
In order to support them, it provides APIs for \safe users to get results
from any phases, and each phase may perform differently depending on
given options.  For example, one may want to compare analysis precision
and scalability with different $n$ for $n$-depth loop unrolling or
different $k$ for $k$-CFA, which distinguishes the same function body
from its different call sites using $k$ call history.  Moreover, \safe even
allows users to experiment with different abstract domains via analysis
options.  For example, while the default abstract domain for strings in
\safe is a string set domain, one may want to try a regular expression
domain~\cite{dls16} or a string automata domain~\cite{aplas14}.

Because specifying various options for different commands as
command-line options multiple times is tedious and error-prone,
we provide an easy way to specify them in a configuration file in
JSON format.  Figure~\ref{fig:configurability}(a) shows an example
configuration file that specifies which analysis sensitivities are to be
used, and the configuration files shown in
Figure~\ref{fig:configurability}(b) specifies which abstract domains
are to be used.  Unlike command-line options,
configuration files enable users to specify the selected options
in a declarative manner.

\subsection{Extensibility}
\setcounter{figure}{2}
\begin{figure*}[t]
\begin{tabular}{c|c|}\cline{2-2}
\begin{minipage}{.52\textwidth}
\includegraphics[width=\textwidth]{seip}
\end{minipage}
&
\begin{minipage}{.44\textwidth}
\small
\begin{verbatim}
sample snapshot
\end{verbatim}
\end{minipage}
\\\cline{2-2}
\end{tabular}
\vspace*{.5em}
\caption{\small Extension of \safe with dynamic heap information~\cite{safehybrid}}
\label{fig:seip}
\end{figure*}

Researchers may devise new analysis techniques or they may want to
reproduce analysis results reported in the literature.  In either way,
depending on which analysis technique is being implemented, one may
have to add a new phase or it may suffice to add one option to an
existing phase.  For example, when a researcher wanted to add
a simple symbolic executor to \oldsafe, the researcher had to modify
many functions in different files without much help from API functions.
In order to add a command, a phase, an option, a help message, and an
implementation of the new functionality, the researcher had to understand
many low-level details of \oldsafe.

Based on our own painful experiences, we revamped the structures of
the main \safe driver, commands, phases, options, and configurations,
and provide well-designed APIs for adding new commands, phases, and
options.  For example, when we extended \safe with a bug
detector~\cite{safewapp}, all we had to do was to make small
modifications in two files and to implement the bug detector.
Figure~\ref{fig:extensibility}(a) shows how we added a new command
\mtt{CmdBugDetect} and a new phase \mtt{BugDetect} in the main
driver file \mtt{Safe.scala}.  Figure~\ref{fig:extensibility}(b) presents
that we added the new command \mtt{CmdBugDetect} with a name
\mtt{bugDetect} and its phases \mtt{CmdAnalyze >> BugDetect},
which denotes that the new phase \mtt{BugDetect} is added to the end
of the phases of the command \mtt{CmdAnalyze}.  Then,
Figure~\ref{fig:extensibility}(c) shows the implementation of the
bug detector.  While the actual implementation is omitted at line 6,
simply providing its name, help message, configuration, and possible
options all in one single file is enough for \safe to plug the
information into appropriate places.  In this way, users do not
need to understand how \safe handles commands, phases, options, and
help messages, but they can simply specify what they are for the new
command.

Figure~\ref{fig:seip} illustrates another example that we extended \safe
with dynamic heap information as specified in the
literature~\cite{safehybrid}.  The technique is to capture the initial
concrete heap for each browser called \emph{snapshot}, to transform
it to its corresponding abstract heap, to merge the resulting
abstract heap with the default initial heap, and to use the merged heap
for the analysis.  Thus, the implementation of the technique consists
of two parts: a capturing app of concrete heaps, and code that
transforms a concrete heap to an abstract heap and merges it with another
abstract heap.  By using a browser-specific concrete heap
instead of a sound approximation that covers concrete heaps from
all the possible browsers, the technique reduces many false positives
from analysis results.  When applying the technique to \safe, we could
reuse the capturing app in tact, and we had to implement only 
\msf{heap construction} that parses a snapshot and constructs a concrete
heap in \safe, and we could reuse existing APIs for the remaining tasks.
As Figure~\ref{fig:seip} shows, for a given snapshot from the capturing
app, \msf{heap construction} constructs a concrete heap from the
snapshot.  Then, we can use the existing abstraction function for heaps
and the join operation on heaps in \safe.

\subsection{Debuggability}
While many programming language environments provide debugging
facilities, most static analysis frameworks do not provide such utilities
for analysis developers.  Because understanding and reasoning about
analysis status are extremely difficult, tracking the causes of analysis
imprecision is one of the active research topics.  However, existing
JavaScript analyzers are still in pre-mature stages.  \oldsafe provides
a console debugger, which allows users to investigte the analysis status
during analysis with stepwise exeuction of the underlying analyzer.
It indeed helps \oldsafe users debug the analyzer behaviors, but it lacks
documentation and it requires knowledge of the underlying analyzer.

To help \safe users to easily understand and reason about
analysis results, it now supports \htmldebug, which enables users
to investigate analysis status from browsers.  During analysis,
a user can write the current analysis status into an HTML file and
investigate it from a browser as illustrated in
Figure~\ref{fig:htmldebug}.  It shows the current CFG in the middle.
Nodes in black lines denote the blocks that are analyzed, those in
gray lines denote the blocks not yet being analyzed, and colored nodes
denote the blocks that are currently in the worklist of the analyzer.
One can toggle whether to show the nodes in the worklist by the menu
button on the top right.
When a user selects a block from the CFG, the list of the instructions in
the block and the state just before analyzing the block are displayed
on the left.

\safe has been tested using Test262, the official ECMAScript
conformance suite:
\begin{center}
\url{https://github.com/tc39/test262}
\end{center}
which helped us find and fix bugs in our modeling of builtin
functions specified in chapter 15 of the ECMAScript
specification~\cite{ECMA}.  Our regression test suite checks
whether the analysis results soundly approximate their corresponding
concrete values.  It also measures how many tests are being analyzed
precisely.  This test infrastructure with Test262 will aid \safe users
who build new analysis techniques to ``test'' the soundness of their
new analysis implementation.

\begin{figure*}[t]
\centering
\includegraphics[width=.7\textwidth]{htmldebugger.png}
\caption{\htmldebug}\label{fig:htmldebug}
\end{figure*}

\section{Future Directions}
Since the release of \safe in early October 2016~\cite{saferelease},
we have been extending \safe with various features.
Among others, the following features will be supported in near future:
\begin{itemize}
\item Easier addition of sensitivities 
\item More support for abstract domain APIs
\item Improvements in \htmldebug

We are working on integration of the \safe analyzer and \htmldebug,
which would allow stepwise execution and more interactive debugging from browsers.
We plan to use a database for analysis results for scalability.
\end{itemize}
In addition, we plan to provide basic modeling supports for HTML/DOM
tree abstraction and the jQuery library, which has more than 90\% of
market share.  We believe \safe will let us explore more easily
the remaining challenges in analysis of JavaScript web applications
like event handling, modeling framework, and compositional analysis.

\section{Conclusion}
We present \safe, a tool that analyzes JavaScript web applications with
supports for analyzer users in mind.  On top of the well-tested core
features of \safe based on the prior experiences from building \oldsafe,
it also provides mechanisms for analysis developers to experiment with
their novel ideas without too much implementation burden.
It allows users to specify target phases and options in a declarative
manner, which can configure even abstract domains and analysis
sensitivities.  Analyzer developers can add new analysis techniques
into \safe without too much understanding of the implementation details
of \safe via its extensible APIs.  Finally, \safe provides a debugging
support for analysis developers with visualization and interactive
investigation of the analysis status.  The tool was motivated by the pain
the authors themselves experienced with \oldsafe, which was greatly
relieved by the \htmldebug.  Also, analysis developers can test their
new analysis techniques with extensive Test262, the official ECMAScript
conformance suite.

\bibliographystyle{abbrv}
\bibliography{ref}
\end{document}

### 2016-11-08 doc/icse-demo/main.tex

@@
 \newcommand{\oldsafe}{{SAFE 1.0}\xspace}
-\newcommand{\safe}{{SAFE 2.0}\xspace}
+\newcommand{\safe}{{SAFE~2.0}\xspace}
 \newcommand{\htmldebug}{{\sf\small HTML Debugger}\xspace}
@@
 To lessen the problem, researchers have developed various analysis
-techniques in different analyzers, but they are not especially
-aimed for usability.  In this paper, we present \safe, a scalable
-analysis framework for ECMAScript especially aimed to be a playground
-for advanced research in JavaScript web applications.  \safe is designed
-to be light-weight, which supports configurability, extensibility, and
+techniques in different analyzers, but such analyzers are not especially
+aimed for ease of use by analysis developers.  In this paper, we present \safe, a scalable
+analysis framework for ECMAScript especially designed as a playground
+for advanced research in JavaScript web applications.  \safe is
+light-weight, which supports configurability, extensibility, and
 debuggability.
@@
 difficult for new users to understand the code base.
-TAJS\footnote{\url{https://github.com/cs-au-dk/TAJS}}~\cite{TAJSDETER})
+TAJS\footnote{\url{https://github.com/cs-au-dk/TAJS}}~\cite{TAJSDETER}
 is a dataflow analysis for JavaScript that infers type information and call graphs.
-It also provides analysis techniques published by the TAJS team with options;
-for example, the {\tt -determinacy} option enables the techniques described in~\cite{TAJSDETER}.
+It provides an analysis technique as a whole with an option instead of as
+configurable components;
+for example, the \mtt{-determinacy} option enables the techniques described in~\cite{TAJSDETER}.
 WALA\footnote{\url{http://wala.sourceforge.net/wiki/index.php}}~\cite{Schafer13}
@@
 Jalangi\footnote{\url{https://github.com/SRA-SiliconValley/jalangi}}~\cite{Sen13}
-is a dynamic analysis framework for JavaScript, which provides simple
-traditional dynamic analyzers like a taint analyzer as example uses of the framework.
+is a dynamic analysis framework for JavaScript, which may miss many execution flows.
+It provides simple dynamic analyzers like a taint analyzer as example uses of the framework.
 
@@
 programs.  It performs several preprocessing steps on JavaScript code to
-address some quirky semantics of JavaScript such as the {\tt with}
+address some quirky semantics of JavaScript such as the \mtt{with}
 statement~\cite{dls13}.
@@
 {\small (a) Add a new command and a new phase to the lists of available
-commands and phases, respectively, in {\tt Safe.scala}}
+commands and phases, respectively, in \mtt{Safe.scala}}
 \\[1em]
@@
 \\[1em]
-{\small (b) Add the new command by specifying its name and phases in {\tt Command.scala}}
+{\small (b) Add the new command by specifying its name and phases in \mtt{Command.scala}}
 \\[1em]
@@
 precisely.  This test infrastructure with Test262 will aid \safe users
-who build new analysis techniques to ``test'' the soundness of their
+who build new analysis techniques to ``test'' the soundness and precision of their
 new analysis implementation.

### 2016-11-08 doc/icse-demo/main.tex

@@
 
-Let us consider SAFE more closely.  It was first designed to analyze pure
+Let us consider SAFE more closely\footnote{
+Note that one of the authors is a main developer of SAFE.}.  It was first designed to analyze pure
 JavaScript benchmarks~\cite{Lee12}.  It provides a default static analyzer
 based on the abstract interpretation framework, and it supports
-flow-sensitive and context-sensitive analyses of stand-alone JavaScript
+flow-sensitive and context-sensitive analyses of JavaScript
 programs.  It performs several preprocessing steps on JavaScript code to
-address some quirky semantics of JavaScript such as the \mtt{with}
+address quirky semantics of JavaScript such as the \mtt{with}
 statement~\cite{dls13}.
@@
 of various browsers~\cite{safewapp} with HTML/DOM tree abstraction,
-and it supports analysis of interactions between JavaScript applications
+and it supports analysis of interactions between JavaScript code
 and native functions in platform-specific libraries by using automatic

### 2016-11-12 doc/icse-demo/main.tex
Revised the demo paper.

--- 2016-11-08 doc/icse-demo/main.tex
@@
 for advanced research in JavaScript web applications.  \safe is
-light-weight, which supports configurability, extensibility, and
+light-weight, which supports pluggability, extensibility, and
 debuggability.
@@
 but they are not especially designed for usability.
-SAFE\footnote{\url{http://plrg.kaist.ac.kr/redmine/projects/jsf/repository}}~\cite{Lee12}
+SAFE\footnote{\url{https://github.com/sukyoung/safe/tree/SAFE1.0}}~\cite{Lee12}
 is a scalable analysis framework for ECMAScript, and it has adopted recent research results incrementally.
@@
 is a dataflow analysis for JavaScript that infers type information and call graphs.
-It provides an analysis technique as a whole with an option instead of as
-configurable components;
-for example, the \mtt{-determinacy} option enables the techniques described in~\cite{TAJSDETER}.
+Even though it provides a large collection of analysis techniques like SAFE,
+it does not provide a facility to understand the analysis status during analysis.
+Similarly for SAFE, it is not easy for a novice user to extend TAJS to
+experiment with new analysis techniques.
+%{\color{red}{
+%It provides an analysis technique as a whole with an option instead of as
+%configurable components.  For example, because the \mtt{-determinacy} option
+% enables the techniques described in~\cite{TAJSDETER} altogether,
+% it does not provide a way to experiment with each technique separately.}}
+%
 WALA\footnote{\url{http://wala.sourceforge.net/wiki/index.php}}~\cite{Schafer13}
@@
 Because WALA aims to support analysis of multiple programming languages,
-the source code repository is huge with many packages.
-While SAFE, TAJS, and WALA are mainly static analyzers possibly using dynamic information,
-Jalangi\footnote{\url{https://github.com/SRA-SiliconValley/jalangi}}~\cite{Sen13}
-is a dynamic analysis framework for JavaScript, which may miss many execution flows.
-It provides simple dynamic analyzers like a taint analyzer as example uses of the framework.
+the source code repository is gigantic with many packages,
+which incurs a huge learning curve.
+% While SAFE, TAJS, and WALA are mainly static analyzers possibly using dynamic information,
+% Jalangi\footnote{\url{https://github.com/SRA-SiliconValley/jalangi}}~\cite{Sen13}
+% is a dynamic analysis framework for JavaScript, which may miss many execution flows.
+% It provides simple dynamic analyzers like a taint analyzer as example uses of the framework.
 
-Let us consider SAFE more closely.  It was first designed to analyze pure
+The more advanced analysis techniques are integrated,
+the more difficult it is for analyzer users to understand the code base.
+For example, SAFE was first designed to analyze pure
 JavaScript benchmarks~\cite{Lee12}.  It provides a default static analyzer
-based on the abstract interpretation framework, and it supports
-flow-sensitive and context-sensitive analyses of stand-alone JavaScript
-programs.  It performs several preprocessing steps on JavaScript code to
-address some quirky semantics of JavaScript such as the \mtt{with}
+based on the abstract interpretation framework, and it 
+performs several preprocessing steps on JavaScript code to
+address quirky semantics of JavaScript such as the \mtt{with}
 statement~\cite{dls13}.
@@
 It was then extended to model web application execution environments
-of various browsers~\cite{safewapp} with HTML/DOM tree abstraction,
-and it supports analysis of interactions between JavaScript applications
+of various browsers~\cite{jswapp} with HTML/DOM tree abstraction,
+and it supports analysis of interactions between JavaScript code
 and native functions in platform-specific libraries by using automatic
@@
 environments like specific browser versions~\cite{safehybrid}.
-The more advanced analysis techniques SAFE integrates,
-the more difficult it is for SAFE users to understand the SAFE code base.
+The more features are integrated, the more complicated the SAFE code base gets.
 
@@
     val (cfg, _, _) = in
-    // Bug detector implementation here.
+\end{verbatim}
+\vspace*{-.6em}
+\textbf{~~~~~~~// Bug detector implementation here.}
+\vspace*{-.8em}
+\begin{verbatim}
     Success(cfg)
@@
 \end{tabular}
-\caption{\small Extension of \safe with a bug detector~\cite{safewapp}}
+\caption{\small Extension of \safe with a bug detector~\cite{jswapp}}
 \label{fig:extensibility}
@@
 \footnotesize
+\vspace*{.3em}
 \begin{verbatim}
-Some JSON code
-that specifies
-the configuration
-(phases/options)
-of selecting
-analysis sensitivity
+{
+  "analyzer": {
+    "callsiteSensitivity": 1
+  },
+  "file": ["wikipedia.org.htm"]
+}
 \end{verbatim}
+\vspace*{.05em}
 \end{minipage}
@@
 \footnotesize
+\vspace*{.3em}
 \begin{verbatim}
-Some JSON code
-that specifies
-the configuration
-(phases/options)
-of selecting
-abstract domains
+{
+  "analyzer": {
+    "number": "flat",
+    "maxStrSetSize": 10
+  },
+  "file": ["wikipedia.org.htm"]
+}
 \end{verbatim}
+\vspace*{.05em}
 \end{minipage}\\\hline
@@
 \caption{\small \safe analysis configuration files in JSON format}
-\label{fig:configurability}
+\label{fig:pluggability}
 \end{figure}
 
-In this paper, we present \safe, which is aimed to be a playground
-for advanced research in JavaScript web applications.  Thus, we
-intentionally designed it to be light-weight, highly parametric,
-and modular.  The main features of \safe are as follows:
+In this paper, we present \safe\footnote{
+\url{https://github.com/sukyoung/safe}}, a playground
+for advanced research in JavaScript web applications\footnote{
+We call SAFE ``\oldsafe'' from now on to distinguish it from \safe.
+}.  We designed it to be light-weight, highly parametric,
+and modular.  \safe has the following main features:
 \begin{itemize}
-\item Configurability: Because \safe supports various phases
-like parsing, compilation, and analysis with many options like
-verbosity, pretty printing, and analysis sensitivity, it provides
-a declarative way to describe them concisely.
+\item Pluggability: To help analysis developers experiment with
+various analysis techniques easily, \safe enables analysis sensitivities
+and even abstract domains to be selected at run time.
 
-\item Extensibility: In order for researchers to experiment with their
+\item Extensibility: In order for researchers to implement their
 new ideas easily or to reproduce research achievements from the
@@
 \item Debuggability: To aid \safe users to understand and reason about
-analysis results easily, it now supports \htmldebug, which lets users
-investigate analysis status from browsers.  \safe has been tested using
-Test262, the official ECMAScript conformance suite, and it allows users
-to test their experimental analysis techniques with Test262.
+analysis results easily, it supports \htmldebug, which lets users
+investigate analysis status from browsers.  Users can also
+test their analysis implementation with Test262,
+the official ECMAScript conformance suite.
 \end{itemize}
@@
 
-\subsection{Configurability}
-\safe supports various phases, options, and their combinations.
-In order to support them, it provides APIs for \safe users to get results
-from any phases, and each phase may perform differently depending on
-given options.  For example, one may want to compare analysis precision
+\subsection{Pluggability}
+\safe is designed to support selection of analysis sensitivities and
+abstract domains at run time.  A large body of research on program
+analysis has been designing, developing, and evaluating various
+analysis techniques like analysis sensitivities and abstract domains.
+For example, researchers have evaluated the analysis precision
 and scalability with different $n$ for $n$-depth loop unrolling or
 different $k$ for $k$-CFA, which distinguishes the same function body
-from its different call sites using $k$ call history.  Moreover, \safe even
-allows users to experiment with different abstract domains via analysis
-options.  For example, while the default abstract domain for strings in
-\safe is a string set domain, one may want to try a regular expression
-domain~\cite{dls16} or a string automata domain~\cite{aplas14}.
+from its different call sites using $k$ call history~\cite{SAFELSA}.
+Moreover, various abstract domains for JavaScript string analysis
+have been proposed such as a regular expression
+domain~\cite{dls16} and a string automata domain~\cite{aplas14}.
+However, with existing analyzers, it is not easy to configure analysis
+sensitivities and abstract domains without recompilation of the analyzers.
 
-Because specifying various options for different commands as
-command-line options multiple times is tedious and error-prone,
-we provide an easy way to specify them in a configuration file in
-JSON format.  Figure~\ref{fig:configurability}(a) shows an example
-configuration file that specifies which analysis sensitivities are to be
-used, and the configuration files shown in
-Figure~\ref{fig:configurability}(b) specifies which abstract domains
-are to be used.  Unlike command-line options,
-configuration files enable users to specify the selected options
-in a declarative manner.
+In order to help analysis researchers experiment with different analysis
+techniques easily, \safe provides APIs that support pluggable analysis
+sensitivities and abstract domains.  The APIs enable \safe users
+to select specific analysis techniques.  For example, while the default
+abstract domain for strings in \safe is a string set domain, one can use
+a regular expression domain or a string automata domain.
+Because specifying various selection as command-line options multiple
+times is tedious and error-prone, we provide an easy way to specify them
+in a configuration file in JSON format.
+The configuration file shown in Figure~\ref{fig:pluggability}(a)
+specifies that it uses the 1-CFA analysis sensitivity, and the one in
+Figure~\ref{fig:pluggability}(b) specifies that it uses a flat number
+domain and a string set domain of maximum size 10.
+
+% \safe supports various phases, options, and their combinations.
+% In order to support them, it provides APIs for \safe users to get results
+% from any phases, and each phase may perform differently depending on
+% given options.  For example, one may want to compare analysis precision
+% and scalability with different $n$ for $n$-depth loop unrolling or
+% different $k$ for $k$-CFA, which distinguishes the same function body
+% from its different call sites using $k$ call history.  Moreover, \safe even
+% allows users to experiment with different abstract domains via analysis
+% options.  For example, while the default abstract domain for strings in
+% \safe is a string set domain, one may want to try a regular expression
+% domain~\cite{dls16} or a string automata domain~\cite{aplas14}.
+
+% Because specifying various options for different commands as
+% command-line options multiple times is tedious and error-prone,
+% we provide an easy way to specify them in a configuration file in
+% JSON format.  Figure~\ref{fig:pluggability}(a) shows an example
+% configuration file that specifies which analysis sensitivities are to be
+% used, and the configuration files shown in
+% Figure~\ref{fig:pluggability}(b) specifies which abstract domains
+% are to be used.  Unlike command-line options,
+% configuration files enable users to specify the selected options
+% in a declarative manner.
 
@@
 \begin{figure*}[t]
-\begin{tabular}{c|c|}\cline{2-2}
-\begin{minipage}{.52\textwidth}
+\hspace*{-1em}
+\begin{tabular}{cc}
+\begin{tabular}{c}
+\begin{minipage}{.5\textwidth}
 \includegraphics[width=\textwidth]{seip}
 \end{minipage}
+\\\\[-.5em]
+\multicolumn{1}{c}{\small (a) Use of dynamic heap information to reduce false positives~\cite{safehybrid}}\\
+\end{tabular}
 &
-\begin{minipage}{.44\textwidth}
-\small
+\begin{tabular}{c}
+\begin{minipage}{.45\textwidth}
+\footnotesize
 \begin{verbatim}
-sample snapshot
+def addSnapshot(st: AbsState,
+                snapshot: String): AbsState = {
+  val concreteHeap = Heap.parse(snapshot)
+  val abstractHeap = AbsHeap.alpha(concreteHeap)
+  AbsState(st.heap + abstractHeap, st.context)
+}
 \end{verbatim}
 \end{minipage}
-\\\cline{2-2}
+\\[1.5em]
+{\small (b) Implement the new technique}
+\\[1em]
+\begin{minipage}{.45\textwidth}
+\footnotesize
+\begin{verbatim}
+("snapshot",
+ StrOption((c, s) => c.snapshot = Some(s)),
+ "analysis with an initial heap generated \
+  from a dynamic snapshot(*.json)."),
+
+config.snapshot.map(str =>
+  initSt = Initialize.addSnapshot(initSt, str))
+\end{verbatim}
+\end{minipage}
+\\\\[-.5em]
+{\small (c) Add a new option in \mtt{Analyze.scala}}
+\\[.5em]
 \end{tabular}
-\vspace*{.5em}
+%\begin{minipage}{.4\textwidth}
+%\footnotesize
+%\vspace*{.3em}
+% \begin{verbatim}
+% {
+%   "#Global": {
+%     "chrome": {
+%       "value": "#Chrome",
+%       "writable": true,
+%       "enumerable": true,
+%       "configurable": false
+%     }
+%   },
+%   "#Chrome": {
+%     "[[Extensible]]": true,
+%     "[[Prototype]]": "#Object.prototype",
+%     "[[Class]]": "Object"
+%   }
+% }
+% \end{verbatim}
+%\vspace*{.1em}
+%\end{minipage}
+\end{tabular}
 \caption{\small Extension of \safe with dynamic heap information~\cite{safehybrid}}
@@
 options.  For example, when we extended \safe with a bug
-detector~\cite{safewapp}, all we had to do was to make small
+detector~\cite{jswapp}, all we had to do was to make small
 modifications in two files and to implement the bug detector.
@@
 Figure~\ref{fig:extensibility}(c) shows the implementation of the
-bug detector.  While the actual implementation is omitted at line 6,
+bug detector.  While the actual implementation is omitted,
 simply providing its name, help message, configuration, and possible
@@
 
-Figure~\ref{fig:seip} illustrates another example that we extended \safe
+Figure~\ref{fig:seip} illustrates another example extending \safe
 with dynamic heap information as specified in the
@@
 for the analysis.  Thus, the implementation of the technique consists
-of two parts: a capturing app of concrete heaps, and code that
-transforms a concrete heap to an abstract heap and merges it with another
-abstract heap.  By using a browser-specific concrete heap
-instead of a sound approximation that covers concrete heaps from
-all the possible browsers, the technique reduces many false positives
-from analysis results.  When applying the technique to \safe, we could
-reuse the capturing app in tact, and we had to implement only 
-\msf{heap construction} that parses a snapshot and constructs a concrete
-heap in \safe, and we could reuse existing APIs for the remaining tasks.
-As Figure~\ref{fig:seip} shows, for a given snapshot from the capturing
-app, \msf{heap construction} constructs a concrete heap from the
+of two parts: a capturing app of dynamic heap, and code that
+transforms the captured dynamic heap to an abstract heap and merges it
+with another abstract heap.  By using a browser-specific information
+instead of a sound approximation of all browsers, the technique reduces many false positives
+from analysis results.  When applying the technique to \safe,
+we had to implement only \mtt{Heap.parse} that parses a snapshot and
+constructs a concrete heap in \safe, and we could reuse the capturing app in tact
+and existing \safe APIs for the remaining tasks.
+As Figure~\ref{fig:seip}(b) shows, for a given snapshot from the capturing
+app, \mtt{Heap.parse} constructs a concrete heap from the
 snapshot.  Then, we can use the existing abstraction function for heaps
-and the join operation on heaps in \safe.
+\mtt{AbsHeap.alpha} and the join operation on heaps \mtt{+} in \safe.
+As Figure~\ref{fig:seip}(c) shows, one can add a new technique
+to the existing analysis by simply adding one option.
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=.7\textwidth]{htmldebugger.png}
+\caption{\htmldebug}\label{fig:htmldebug}
+\end{figure*}
 
@@
 JavaScript analyzers are still in pre-mature stages.  \oldsafe provides
-a console debugger, which allows users to investigte the analysis status
-during analysis with stepwise exeuction of the underlying analyzer.
+a console debugger, which allows users to investigate the analysis status
+during analysis with stepwise execution of the underlying analyzer.
 It indeed helps \oldsafe users debug the analyzer behaviors, but it lacks
@@
 \safe has been tested using Test262, the official ECMAScript
-conformance suite:
-\begin{center}
-\url{https://github.com/tc39/test262}
-\end{center}
+conformance suite\footnote{\url{https://github.com/tc39/test262}},
 which helped us find and fix bugs in our modeling of builtin
@@
 new analysis implementation.
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=.7\textwidth]{htmldebugger.png}
-\caption{\htmldebug}\label{fig:htmldebug}
-\end{figure*}
 

### 2016-11-18 doc/icse-demo/main.tex
Demo paper

@@
 debuggability.
+
+Demo video: \url{http://youtu.be/x7Jr_gyyHD0}
 \end{abstract}
@@
 \begin{verbatim}
-case object CmdBugDetect extends CommandObj("bugDetect", CmdAnalyze >> BugDetect) {
-  override def display(cfg: CFG): Unit = println(cfg.toString(0))
-}
+case object CmdBugDetect extends CommandObj("bugDetect", CmdAnalyze >> BugDetect)
 \end{verbatim}
@@
   val help: String = "Detect possible bugs in JavaScript source files."
+  def defaultConfig: BugDetectConfig = BugDetectConfig()
+  val options: List[PhaseOption[BugDetectConfig]] = List(
+    ("silent", BoolOption(c => c.silent = true), "messages during analysis are muted.")
+  )
+
   def apply(in: (CFG, Int, CallContext), safeConfig: SafeConfig, config: BugDetectConfig): Try[CFG] = {
@@
   }
-  def defaultConfig: BugDetectConfig = BugDetectConfig()
-  val options: List[PhaseOption[BugDetectConfig]] = List(
-    ("silent", BoolOption(c => c.silent = true), "messages during analysis are muted.")
-  )
 }
@@
 case class BugDetectConfig(var silent: Boolean = false) extends Config
-
 \end{verbatim}
@@
 \begin{itemize}
-\item Pluggability: To help analysis developers experiment with
-various analysis techniques easily, \safe enables analysis sensitivities
+\item Pluggability: To help developers experiment with
+analysis techniques easily, \safe enables analysis sensitivities
 and even abstract domains to be selected at run time.
@@
 \centering
-\includegraphics[width=.7\textwidth]{htmldebugger.png}
+\includegraphics[width=.68\textwidth]{htmldebugger.png}
 \caption{\htmldebug}\label{fig:htmldebug}

### 2016-12-23 doc/chap-1-foreword.tex

@@
 \end{enumerate}
+
+For debugging purpose, you can first add a configuration like this:
+
+\begin{enumerate}
+\item Go to \verb!Run -> Edit Configurations!
+\item Click the ``+'' button on the left to add a new configuration, select ``Remote'' in the drop-down menu
+\item Name the configuration something like ``remote-debugging'', then it should work out of box (you can check that the port is 5005 though)
+\item Save the configuration by clicking ``OK''
+\end{enumerate}
+
+Now you can debug by first launching SAFE with a \verb!-debug!
+flag as the first argument, then following your other options.
+For example, \verb!./bin/safe -debug analyze something.js!.
+Your application is supposed to wait for connection from debugger once started, then you can start the debugging configuration we just created in IntelliJ.

### 2016-12-31 doc/chap-1-foreword.tex
1. Changed the current developers in the manual. 2. Debugging support for IntelliJ by Zhen Zhang.

--- 2016-10-09 doc/chap-1-foreword.tex
@@
 \begin{itemize}
-\itemsep-.2em
+\itemsep-.1em
 \item JSAI~\cite{jsai} @ UCSB
@@
 \section{Contributors}
-The main developers of SAFE 2.0 are as follows:
+The current developers of SAFE 2.0 are as follows:
 \begin{itemize}
-\itemsep-.2em
+\itemsep-.1em
 \item Jihyeok Park
-\item Yeonhee Ryou
+\item Joonyoung Park
 \item Sukyoung Ryu
@@
 \itemsep-.1em
+\item Yeonhee Ryou (SAFE 2.0 core)
 \item Minsoo Kim (Built-in function modeling)
@@
 \subsection{IntelliJ configuration}
+[\emph{Thanks to Alexander Jordan @ Oracle Labs in Australia}]
+\smallskip
+
 IntelliJ users can use IntelliJ 2016.2.4 with the latest Scala plugin as follows:
@@
 \item Choose JDK 1.8 as the project JDK.
-\item Manually download \verb!xtc.jar! in to \verb!lib/!
+\item Manually download \verb!xtc.jar! in to \verb!lib/!.
 \item Goto \verb!Project Settings! $\rightarrow$ \verb!Modules! $\rightarrow$
-\verb!root (module)! $\rightarrow$ \verb!Dependencies!
+\verb!root (module)! $\rightarrow$ \verb!Dependencies!.
 \item Open \verb!SBT:unmanaged-jars! dependencies.
@@
 \end{enumerate}
+
+\noindent
+[\emph{Thanks to Zhen Zhang @ USTC in China}]
+\smallskip
+
+For debugging purpose, one can first add a configuration as follows:
+
+\begin{enumerate}
+\item Go to \verb!Run! $\rightarrow$ \verb!Edit Configurations!.
+\item Click the \verb!+! button on the left to add a new configuration.
+\item Choose \verb!Remote! in the drop-down menu.
+\item Name the configuration something like \verb!remote-debugging!.
+(It should work out of box and the port should be 5005.)
+\item Save the configuration by clicking \verb!OK!.
+\end{enumerate}
+
+In order to debug \verb!something.js! for example,
+launch \safe first with the \verb!-debug! flag as the first argument:
+\verb!safe -debug analyze something.js!.
+The application waits for a connection from the debugger once started,
+and users can start the debugging configuration created in IntelliJ.

### 2017-09-03 doc/chap-3-refman.tex
1. Added a two-step heap abstraction (global/local) for optimization. 2. Removed Concrete Abstraction (implementation of the Singleton Abstraction) 3. Upgraded the console debugger. 4. Added simple modeling: window.navigator and RegExp.prototype.test 5. Added README files for the third-party liceses thanks to Alexander Jordan. 6. Added a list of ignored tests when JS modeling is not used.

@@
 any dynamic code generation such as \verb!eval! into other statements without using
-the \verb!with! statement but with the same semantics.
+the \verb!with! statement but with the same semantics~\cite{dls13,withtr}.
 \end{itemize}
@@
 usage: print state(-all) ({keyword})
-       print block
+       print block ({fid}:{bid})
        print loc {LocName} ({keyword})
@@
 \medskip\noindent
-\fbox{\texttt{print block}}\\[.2em]
+\fbox{\texttt{print block ({}{})}}\\[.2em]
+\fbox{\texttt{print block (\{fid\}\{bid\})}}\\[.2em]
 The \verb!print block! command displays the information of
-a given block.  For example:
+the current block. For example:
 {\small
@@
        <>Global<>toObject(<>obj<>6["pop"]) @ #9
+\end{verbatim}
+}
+
+Moreover, it displays the information of the given block denoted
+by the id of a function, the id of a block, and the kind of the block.
+For example:
+
+{\small
+\begin{verbatim}
+<function[0] top-level: Block[0], ()> @test.js:1:1-7:18
+Iter[1] > print block 0:4
+Block[4] -> Exit, ExitExc
+  [0] shift := <>Global<>ignore6
+  [1] __result1 := shift !== "x"
+  [2] __expect1 := false
+  [3] <>obj<>10 := <>Global<>toObject(obj) @ #13
+  [4] __result2 := <>obj<>10["length"] !== 1
+  [5] __expect2 := false
+  [6] <>obj<>11 := <>Global<>toObject(obj) @ #14
+  [7] __result3 := <>obj<>11[0] !== "y"
+  [8] __expect3 := false
+  [9] <>obj<>12 := <>Global<>toObject(obj) @ #15
+  [10] __result4 := <>obj<>12[1] !== undefined
+  [11] __expect4 := false
+  [12] noop(EndOfFile)
 \end{verbatim}

### 2018-02-06 doc/chap-2-intro.tex
Updated documentation

@@
 \begin{verbatim}
-The command 'astRewrite' took 178 ms.
   {
-    <>alpha<>1 = <>Global<>toObject({
+    <>alpha<>1 = @ToObject({
       a : 1
@@
   }
+The command 'astRewrite' took 100 ms.
 \end{verbatim}
@@
 \begin{verbatim}
-The command 'compile' took 382 ms.
 {
   {
-    <>new1<>1 = {
+    <>new0<>1 = {
       a : 1
     }
-    <>Global<>ignore1 = <>Global<>toObject(<>new1<>1)
+    <>Global<>ignore1 = @ToObject(<>new0<>1)
     <>alpha<>2 = <>Global<>ignore1
@@
   {
-    <>obj<>3 = <>Global<>toObject(<>alpha<>2)
+    <>obj<>3 = @ToObject(<>alpha<>2)
     <>obj<>3["a"] = 2
@@
 }
+The command 'compile' took 123 ms.
 \end{verbatim}
@@
 \begin{verbatim}
-The command 'cfgBuild' took 492 ms.
 function[0] top-level {
@@
     [0] noop(StartOfFile)
-    [1] <>new1<>1 := alloc() @ #1
-    [2] <>new1<>1["a"] := 1
-    [3] <>Global<>ignore1 :=
-          <>Global<>toObject(<>new1<>1) @ #2
+    [1] <>new0<>1 := alloc() @ #1
+    [2] <>new0<>1["a"] := 1
+    [3] <>Global<>ignore1 := @ToObject(<>new0<>1) @ #2
     [4] <>alpha<>2 := <>Global<>ignore1
@@
     [0] assert("a" in <>alpha<>2)
-    [1] <>obj<>3 := <>Global<>toObject(<>alpha<>2) @ #3
+    [1] <>obj<>3 := @ToObject(<>alpha<>2) @ #3
     [2] <>obj<>3["a"] := 2
@@
   ExitExc[-3]
+
 }
+The command 'cfgBuild' took 160 ms.
 \end{verbatim}
@@
 \begin{verbatim}
-safe analyze sample.js
+safe analyze sample.js -analyzer:exitDump
 \end{verbatim}
@@
 \begin{verbatim}
-The command 'analyze' took 1002 ms.
 ** heap **
-#Global -> [[Class]] : "Object"
+R#1 -> Internal Properties:
+       [[Class]] -!> "Object"
+       [[Extensible]] -!> true
+       [[Prototype]] -!> R#Object.prototype
+       DEFAULT: (⊥Elem, Top(absent))
+       Normal Properties:
+       a -!> [ttt] 2
+       DEFAULT: (⊥DataProp, Top(absent))
 ...
-#1 -> [[Class]] : "Object"
-      [[Extensible]] : true
-      [[Prototype]] : #Object.prototype
-      "a" -> [ttt] 2
-      Set(a)
 
 ** context **
-\end{verbatim}
-\vspace*{-.6em}
-\verb!##Collapsed -> [[Default]] @->! $\bot$\verb!(value)!
-\vspace*{-.6em}
-\begin{verbatim}
-               * Outer: null
-#GlobalEnv -> Top(global environment record)
-              * Outer: null
 ...
-this: #Global
+#PureLocal -> ...
+              <>obj<>3 |-> [t]R#1
+              ...
+this: R#Global
 
-** old address set **
-mayOld: (1)
-mustOld: (1)
-
+** old allocation site set **
+mayOld: (#1)
+mustOld: (#1)
 - # of iteration: 6
@@
 - # of instructions: 13
+The command 'analyze' took 406 ms.
 \end{verbatim}

### 2018-02-06 doc/chap-3-refman.tex
1. Refactored abstract domains based on Scala dependent object type (DOT). 2. Updated Scala version from 2.12.0-M5 to 2.12.3. 3. Supported website-based debugger instead of html-based debugger. 4. Supported loop sensitivity analysis (LSA) using loop iterations and inner-loop depths. 5. Updated the manual documentation for users. 6. Implemented more modeling for HTML DOM elements

--- 2016-10-29 doc/chap-3-refman.tex
@@
 \section{\safe commands}
-One can run a \safe command as follows:
+Each command consists of phases and one can run a \safe command as follows:
 \begin{verbatim}
@@
 \end{verbatim}
-For example, the following command analyzes JavaScript code stored in a file name
-``{sample.js}'' located in the current directory without showing detailed information
-from the \verb!astRewriter! phase but printing the result of the \verb!cfgBuilder!
+For example, The command \verb!compile! consists of six phases; 
+\verb!parser!, \verb!astRewriter!, and \verb!compiler!.
+The following command compiles JavaScript code stored in a file name
+``{sample.js}'' located in the current directory without showing detailed
+information but printing the result of the \verb!cfgBuilder!
 phase into a file name ``{out}'':
@@
 
-Each command has its own available options.  The most common options are as follows:
+Each phase has its own available options.
+The most common options are as follows:
 \begin{itemize}
@@
 
-\item \verb!-{phase}:out={out}!
+\item \verb!-{phase}:out={string}!
 
-\safe writes the result of the phase to a file \verb!out!.
-% \item[\doption{-{phase}:out={out}}]: \\
-%   \safe writes the result of the phase to a file name \verb!out!.
+\safe writes the result of the phase to a file \verb!{string}!.
 \end{itemize}
@@
 
-The currently supported commands and their options are as follows:
+The currently supported commands and their phases are as follows:
+\begin{verbatim}
+parse          parser
+astRewrite     parse >> astRewriter
+compile        astRewrite >> compiler
+cfgBuild       compile >> cfgBuilder
+heapBuild      cfgBuild >> heapBuilder
+analyze        heapBuild >> analyzer
+bugDetect      analyze >> bugDetector
+web            web
+help           helper
+\end{verbatim}
+
+and phases and their options are as follows:
 \begin{itemize}
-\item \verb!parse -parser:out={out}!
+\item \verb!parser -out={string}!
 
-parses the JavaScript code in a given file.
-\item \verb!astRewrite -astRewriter:silent!\\
-\hspace*{5.8em}\verb!-astRewriter:out={out}!
+parses the JavaScript code and generates an Abstract Syntax Tree (AST)
+in given files. If multiple files are given, they are concatenated
+in the given order before being parsed.
 
-generates a simplified Abstract Syntax Tree (AST)
-of the  JavaScript code in a given file.
-\item \verb!compile -compiler:silent!\\
-\hspace*{4.2em}\verb!-compiler:out={out}!
+\item \verb!astRewriter -silent!\\
+\hspace*{6.3em}\verb!-out={string}!
 
-generates an Intermediate Representation (IR)
-of the  JavaScript code in a given file.
-\item \verb!cfgBuild -cfgBuilder:silent!\\
-\hspace*{4.8em}\verb!-cfgBuilder:out={out}!\\
-\hspace*{4.8em}\verb!-cfgBuilder:dot={name}!
+rewrites a given AST into a simplified AST.
 
-generates a Control Flow Graph (CFG) of the  JavaScript code in a given file.
+\item \verb!compiler -silent!\\
+\hspace*{4.7em}\verb!-out={string}!
 
-If \verb!-cfgBuilder:dot=name! is given,
-\safe writes the resulting CFG in a graph visualization format
-to file names \verb!name.gv! and \verb!name.pdf!.
+generates an Intermediate Representation (IR) from a given AST.
 
-\item \verb!analyze -analyzer:silent!\\
-\hspace*{4.4em}\verb!-analyzer:out={out}!\\
-\hspace*{4.4em}\verb!-analyzer:console!\\
-\hspace*{4.4em}\verb!-analyzer:html={name}!
+\item \verb!cfgBuilder -silent!\\
+\hspace*{5.8em}\verb!-out={string}!
 
-analyzes the  JavaScript code in a given file.
+generates a Control Flow Graph (CFG) from a given IR.
 
-If \verb!-analyzer:console! is given,
-\safe enables a user to debug analysis results by investigating the intermediate
+\item \verb!heapBuilder -silent!\\
+\hspace*{6.3em}\verb!-maxStrSetSize={number}!\\
+\hspace*{6.3em}\verb!-aaddrType={string}!\\
+\hspace*{6.3em}\verb!-callsiteSensitivity={number}!\\
+\hspace*{6.3em}\verb!-loopIter={number}!\\
+\hspace*{6.3em}\verb!-loopDepth={number}!\\
+\hspace*{6.3em}\verb!-snapshot={string}!\\
+\hspace*{6.3em}\verb!-number={string}!\\
+\hspace*{6.3em}\verb!-jsModel!
+
+builds initial abstract heap used in the \verb!analyzer! phase
+and attaches it into a given CFG.
+
+If \verb!-maxStrSetSize={number}! is given,
+the analyzer will use the string set domain with given size limit n.
+
+If \verb!-aaddrType={string}! is given,
+the analyzer will use a given address abstraction type;
+\verb!"normal"!: allocation-site abstraction and
+\verb!"recency"!: recency abstraction with allocation-site abstraction.
+
+If \verb!-callsiteSensitivity={number}! is given,
+{number}-depth callsite-sensitive analysis will be executed.
+
+If \verb!-loopIter={number}! is given,
+{number}-iteration loop-sensitive analysis will be executed.
+
+If \verb!-loopDepth={number}! is given,
+{number}-depth loop-sensitive analysis will be executed.
+
+If \verb!-snapshot={string}! is given,
+analysis with an initial heap generated from a dynamic snapshot(*.json)
+will be executed.
+
+If \verb!-jsModel! is given,
+analysis with JavaScript models will be executed.
+
+\item \verb!analyzer -silent!\\
+\hspace*{4.7em}\verb!-console!\\
+\hspace*{4.7em}\verb!-exitDump!\\
+\hspace*{4.7em}\verb!-out={string}!
+
+analyzes the given CFG with the given initial abstract heap.
+
+If \verb!-console! is given,
+a user can debug analysis results by investigating the intermediate
 status of the analysis.
 
-If \verb!-analyzer:html=name! is given,
-\safe writes the resulting CFG with states that can be investigated to
-file name \verb!name.html!.
+If \verb!-exitDump! is given,
+it shows the abstract state of the top-level exit node.
 
-We describe these facilities in the next section.
+\item \verb!bugDetector -silent!
 
-\item \verb!help! shows the usage of \safe commands to the standard output.
+detects possible bugs in a given analysis result.
+
+\item \verb!web -port={number}!
+
+allows a user to investigate the analysis status from a browser
+based on network connection. It starts web server with the given
+port number (default: 8080). We describe this in Section~\ref{s:3:2:2:refman}
+
+\item \verb!help!
+
+shows the usage of \safe commands to the standard output.
 \end{itemize}
@@
 \medskip
-The \verb!parse! command parses the JavaScript code in a given file and
+The \verb!parser! phase parses the JavaScript code in a given file and
 rewrites obvious dynamic code generation into other statements without using
@@
 \medskip
-The \verb!astRewrite! command parses the JavaScript code in a given file and
-rewrites its AST representation into a simpler AST.
-The \verb!astRewriter! phase performs three kinds of AST transformations:
+The \verb!astRewriter! phase rewrites its AST representation into a simpler AST
+using three kinds of AST transformations:
 \begin{itemize}
@@
 any dynamic code generation such as \verb!eval! into other statements without using
-the \verb!with! statement but with the same semantics.
+the \verb!with! statement but with the same semantics~\cite{dls13,withtr}.
 \end{itemize}
 
-Note that building a graph visualization format of CFGs requires the \verb!dot! program
-from Graphviz~\cite{graphviz} be in your path.
-For example, the following command:
-\begin{verbatim}
-safe cfgBuild -cfgBuilder:dot=dot sample.js
-\end{verbatim}
-runs the following command:
-\begin{verbatim}
-dot -Tpdf dot.gv -o dot.pdf
-\end{verbatim}
-to produce something like the following:
-\begin{figure}[H]
-\includegraphics[width=8.75cm]{cfg.png}
-\end{figure}
+% Note that building a graph visualization format of CFGs requires the \verb!dot! program
+% from Graphviz~\cite{graphviz} be in your path.
+% For example, the following command:
+% \begin{verbatim}
+% safe cfgBuild -cfgBuilder:dot=dot sample.js
+% \end{verbatim}
+% runs the following command:
+% \begin{verbatim}
+% dot -Tpdf dot.gv -o dot.pdf
+% \end{verbatim}
+% to produce something like the following:
+% \begin{figure}[H]
+% \includegraphics[width=8.75cm]{cfg.png}
+% \end{figure}
 
@@
 - break-rm       Remove a break point.
+- find-bot       Find the instruction whose result is
+                 bottom.
+- restart        Restart the analysis.
 For more information, see 'help <command>'.
 
-<function[0] top-level: Entry[-1], ()> @test.js:1:1
+<top-level[0]: Entry[-1], NoLoop> @sample.js:1:1
  Iter[0] >
@@
 \begin{verbatim}
-<function [{fid}] {fun-name}: {block-kind}[{bid}],
- {call-context}> @{filename}:{span}
+<{fun-name}[{fid}]: {block-kind}[{bid}],
+ {sensitivity}> @{filename}:{span}
 Iter[{#iteration}] >
@@
 \noindent
-where \verb!fid! and \verb!fun-name! are the id and the name of the current function,
+where \verb!fun-name! and \verb!fid! are the name and the id of the current function,
 respectively, \verb!block-kind! and \verb!bid!
 are the kind and the id of the current block, respectively,
-\verb!call-context! is the call context of the current analysis,
+\verb!sensitivity! is the sensitivity of the current analysis,
 \verb!filename! is the name of the file being analyzed,
@@
 \verb!#iteration! is the iteration number of the current analysis.
+We support call-context sensitivity based on call-sites
+and loop sensitivity based on loop iterations and inner-loop depths
+as analysis sensitivities.
 
@@
 \item Entry: the entry block of a function
-\item Block: a normal block with instructions
 \item Exit: the exit block of a function
@@
 \item AfterCatch: a block receiving uncaught exceptions after a function call
+\item Block: a normal block with instructions
+\item LoopHead: a block denoting a loop head
+\item LBreak: a block right after the \verb!break! statement
+\item LCont: a block right after the \verb!continue! statement
+\item Branch: a block denoting a branch
+\item Switch: a block denoting a head of \verb!switch! statement
+\item Case: a block denoting a \verb!case! clause in a \verb!switch! statement
+\item Default: a block denoting the \verb!default! clause
+  in a \verb!switch! statement
+\item Try: a block denoting a head of \verb!try! block
+\item Finally: a block denoting a \verb!finally! block
+\item Catch: a block denoting a \verb!catch! block
+\item Label({string}): a block denoting a user label \verb!{string}!
 \item ModelBlock: a block denoting a modeled function
@@
 usage: print state(-all) ({keyword})
-       print block
+       print heap(-all) ({keyword})
+       print context ({keyword})
+       print block ({fid}:{bid})
        print loc {LocName} ({keyword})
-       print func {functionID}
+       print func ({fid})
+       print function ({fid})
        print worklist
@@
        print trace
-       print cfg
 \end{verbatim}
@@
 \begin{verbatim}
-<function[0] top-level: Entry[-1], ()> @test.js:1:1
+<top-level[0]: Entry[-1], NoLoop> @test.js:1:1
  Iter[0] >
 
-<function[0] top-level: Block[0], ()> @test.js:1:1-7:18
-Iter[1] >
+<top-level[0]: Block[0], NoLoop> @test.js:2:1-8:20
 \end{verbatim}
@@
 \begin{verbatim}
-<function[0] top-level: Entry[-1], ()> @test.js:1:1
+<top-level[0]: Entry[-1], NoLoop> @test.js:1:1
  Iter[0] > jump 10
 
-<function[0] top-level: Block[4], ()> @test.js:7:5-21:1
+<f[1]: Block[4], NoLoop> @test.js:5:8-19
  Iter[10] >
@@
 \begin{verbatim}
-<function[0] top-level: Block[4], ()> @test.js:8:5-26:1
-Iter[10] > run_insts 
-Block[4] -> Exit, ExitExc
-  [0] shift := <>Global<>ignore6
-  [1] __result1 := shift !== "x"
-  [2] __expect1 := false
-  [3] <>obj<>10 := <>Global<>toObject(obj) @ #13
-  [4] __result2 := <>obj<>10["length"] !== 1
-  [5] __expect2 := false
-  [6] <>obj<>11 := <>Global<>toObject(obj) @ #14
-  [7] __result3 := <>obj<>11[0] !== "y"
-  [8] __expect3 := false
-  [9] <>obj<>12 := <>Global<>toObject(obj) @ #15
-  [10] __result4 := <>obj<>12[1] !== undefined
-  [11] __expect4 := false
-  [12] noop(EndOfFile)
+<top-level[0]: Block[0], NoLoop> @test.js:2:1-8:20
+ Iter[1] > run_insts
+Block[0] -> [1], ExitExc
+  [0] f := function (1) @ #6, #7
+  [1] noop(StartOfFile)
+  [2] x := 1
+  [3] <>obj<>9 := @ToObject(f) @ #8
+  [4] <>arguments<>10 := allocArg(0) @ #9
+  [5] <>fun<>11 := @GetBase(f)
+  [6] <>this<> := enterCode(<>fun<>11)
 
-inst: [0] shift := <>Global<>ignore6
+inst: [0] f := function (1) @ #6, #7
 ('s': state / 'q': stop / 'n','': next)
@@
 
-inst: [1] __result1 := shift !== "x"
+inst: [1] noop(StartOfFile)
 ('s': state / 'q': stop / 'n','': next)
@@
 \begin{verbatim}
-<function[0] top-level: ExitExc[-3], ()> @test.js:26:1
-Iter[12] > move 0:exit
+<top-level[0]: Block[0], NoLoop> @test.js:2:1-8:20
+ Iter[1] > move 0:entry
 * current control point changed.
 
-<function[0] top-level: Exit[-2], ()> @test.js:26:1
-Iter[12] >
+<top-level[0]: Entry[-1], NoLoop> @test.js:1:1
+ Iter[1] >
 \end{verbatim}
@@
 \begin{verbatim}
-<function[0] top-level: Exit[-2], ()> @test.js:26:1
-Iter[12] > home
+<top-level[0]: Entry[-1], NoLoop> @test.js:1:1
+ Iter[1] > home
 * reset the current control point.
 
-<function[0] top-level: ExitExc[-3], ()> @test.js:26:1
-Iter[12] >
+<top-level[0]: Block[0], NoLoop> @test.js:2:1-8:20
+ Iter[1] >
 \end{verbatim}
@@
 \begin{verbatim}
-<function[0] top-level: Entry[-1], ()> @test.js:1:1
+<top-level[0]: Entry[-1], NoLoop> @test.js:1:1
  Iter[0] > break 0:exit
 
-<function[0] top-level: Entry[-1], ()> @test.js:1:1
+<top-level[0]: Entry[-1], NoLoop> @test.js:1:1
  Iter[0] > run
 
-<function[0] top-level: Exit[-2], ()> @test.js:26:1
-Iter[11] >
+<top-level[0]: Exit[-2], NoLoop> @test.js:10:1
+ Iter[14] >
 \end{verbatim}
@@
 \begin{verbatim}
-<function[0] top-level: Exit[-2], ()> @test.js:26:1
-Iter[11] > break-list
-* 2 break point(s).
+top-level[0]: Exit[-2], NoLoop> @test.js:10:1
+ Iter[14] > break-list
+* 1 break point(s).
   [0] function[0] Exit[-2]
-  [1] function[0] Entry[-1]
+
+<top-level[0]: Exit[-2], NoLoop> @test.js:10:1
+ Iter[14] >
 \end{verbatim}
@@
 \begin{verbatim}
-<function[0] top-level: Exit[-2], ()> @test.js:26:1
-Iter[11] > break-list
-* 2 break point(s).
+<top-level[0]: Exit[-2], NoLoop> @test.js:10:1
+ Iter[14] > break-list
+* 1 break point(s).
   [0] function[0] Exit[-2]
-  [1] function[0] Entry[-1]
 
-<function[0] top-level: Exit[-2], ()> @test.js:26:1
-Iter[11] > break-rm 0
+<top-level[0]: Exit[-2], NoLoop> @test.js:10:1
+ Iter[14] > break-rm 0
 * break-point[0] removed.
@@
 
-<function[0] top-level: Exit[-2], ()> @test.js:26:1
-Iter[11] > break-list
-* 1 break point(s).
-  [0] function[0] Entry[-1]
+<top-level[0]: Exit[-2], NoLoop> @test.js:10:1
+ Iter[14] > break-list
+* no break point.
+
+<top-level[0]: Exit[-2], NoLoop> @test.js:10:1
+ Iter[14] >
+\end{verbatim}
+}
+
+\medskip
+The \verb!find-bot! command finds the instruction
+that generates the bottom abstract state.  For example:
+{\small
+\begin{verbatim}
+<top-level[0]: Block[2], NoLoop> @branch.js:2:5-12
+ Iter[3] > find-bot
+The result of the following instruction is bottom:
+  [0] assert(x !== 0)
+
+<top-level[0]: Block[2], NoLoop> @branch.js:2:5-12
+ Iter[3] >
+\end{verbatim}
+}
+
+\medskip
+The \verb!restart! command restarts the analysis.  For example:
+{\small
+\begin{verbatim}
+<top-level[0]: Exit[-2], NoLoop> @test.js:10:1
+ Iter[14] > restart
+
+<top-level[0]: Entry[-1], NoLoop> @test.js:1:1
+ Iter[0] >
 \end{verbatim}
@@
 \begin{verbatim}
-<function[0] top-level: Exit[-2], ()> @test.js:21:1
-Iter[12] > print state result
-           "__result1" -> [ttf] false
-           "__result2" -> [ttf] false
-           "__result3" -> [ttf] false
-           Set(NaN, __result3, Function,
-__EvalErrLoc, URIError, pop, JSON, Error, Number,
-decodeURIComponent, __SyntaxErrProtoLoc, RangeError,
-__RangeErrLoc, __ArrayConstLoc, __EvalErrProtoLoc,
-Boolean, ReferenceError, __RefErrLoc, obj, __BOT,
-encodeURIComponent, __TypeErrProtoLoc, Array,
-EvalError, __expect1, encodeURI, eval, __expect3,
-isFinite, __ErrProtoLoc, Object, __TOP, Math,
-__TypeErrLoc, __URIErrProtoLoc, __result1,
-parseFloat, __RangeErrProtoLoc, TypeError,
-<>Global<>global, __ObjConstLoc, isNaN, __URIErrLoc,
-Date, __NumTop, __expect2, decodeURI, RegExp,
-__BoolTop, __UInt, parseInt, __result2, __StrTop,
-Infinity, SyntaxError, __RefErrProtoLoc, __Global,
-<>Global<>true, __SyntaxErrLoc, undefined, String)
+<top-level[0]: Exit[-2], NoLoop> @test.js:31:1
+ Iter[15] > print state result
+            __result1 -!> [ttf] UInt
+            __result2 -!> [ttf] UInt
+            __result3 -!> [ttf] UInt
 \end{verbatim}
@@
 \medskip\noindent
-\fbox{\texttt{print block}}\\[.2em]
+\fbox{\texttt{print heap(-all) (\{keyword\})}}\\[.2em]
+The \verb!print heap! command displays the heap of the current state
+in the same way as \verb!print state!.
+
+\medskip\noindent
+\fbox{\texttt{print context(-all) (\{keyword\})}}\\[.2em]
+The \verb!print heap! command displays the context of the current state
+in the same way as \verb!print state!.
+
+\medskip\noindent
+\fbox{\texttt{print block (\{fid\}\{bid\})}}\\[.2em]
 The \verb!print block! command displays the information of
-a given block.  For example:
+the current block. For example:
 {\small
 \begin{verbatim}
-<function[0] top-level: Block[0], ()> @test.js:1:1-7:18
+<top-level[0]: Block[0], NoLoop> @test.js:2:1-10:20
  Iter[1] > print block
+span: test.js:2:1-10:20
 Block[0] -> [1], ExitExc
-  [0] noop(StartOfFile)
-  [1] <>Global<>ignore1 := alloc() @ #1
-  [2] obj := <>Global<>ignore1
-  [3] <>obj<>1 := <>Global<>toObject(obj) @ #2
-  [4] <>obj<>2 := <>Global<>toObject(Array) @ #3
-  [5] <>obj<>3 :=
-      <>Global<>toObject(<>obj<>2["prototype"]) @ #4
-  [6] <>obj<>1["pop"] := <>obj<>3["pop"]
-  [7] <>obj<>4 := <>Global<>toObject(obj) @ #5
-  [8] <>obj<>4[4294967294] := "x"
-  [9] <>obj<>5 := <>Global<>toObject(obj) @ #6
-  [10] <>obj<>5["length"] := - 1
-  [11] <>obj<>6 := <>Global<>toObject(obj) @ #7
-  [12] <>arguments<>7 := allocArg(0) @ #8
-  [13] <>fun<>8 :=
-       <>Global<>toObject(<>obj<>6["pop"]) @ #9
+  [0] f := function (1) @ #6, #7
+  [1] noop(StartOfFile)
+  [2] x := 1
+  [3] <>obj<>9 := @ToObject(f) @ #8
+  [4] <>arguments<>10 := allocArg(0) @ #9
+  [5] <>fun<>11 := @GetBase(f)
+  [6] <>this<> := enterCode(<>fun<>11)
+\end{verbatim}
+}
+
+Moreover, it displays the information of the given block denoted
+by the id of a function, and the id or the kind of the block.
+For example:
+
+{\small
+\begin{verbatim}
+<top-level[0]: Block[0], NoLoop> @test.js:2:1-10:20
+ Iter[1] > print block 1:0
+span: test.js:4:8-5:19
+Block[0] -> [1], ExitExc
+  [0] <>ff<>1 := function (2) @ #1, #2
+  [1] <>x<>2 := 2
+  [2] <>obj<>5 := @ToObject(<>ff<>1) @ #3
+  [3] <>arguments<>6 := allocArg(0) @ #4
+  [4] <>fun<>7 := @GetBase(<>ff<>1)
+  [5] <>this<> := enterCode(<>fun<>7)
 \end{verbatim}
@@
 \begin{verbatim}
-<function[0] top-level: ExitExc[-3], ()> @test.js:21:1
-Iter[12] > print loc #1
-#1 -> [[Class]] : "Object"
-      [[Extensible]] : true
-      [[Prototype]] : #Object.prototype
-      "4294967294" -> [ttt] "x"
-      "length" -> [ttt] -1
-      "pop" -> [ttt] #Array.prototype.pop
-      Set(pop, length, 4294967294)
+<top-level[0]: Exit[-2], NoLoop> @test.js:2:1
+ Iter[2] > print loc R#1
+R#1 -> Internal Properties:
+       [[Class]] -!> "Object"
+       [[Extensible]] -!> true
+       [[Prototype]] -!> R#Object.prototype
+       DEFAULT: (⊥Elem, Top(absent))
+       Normal Properties:
+       DEFAULT: (⊥DataProp, Top(absent))
 \end{verbatim}
@@
 \medskip\noindent
-\fbox{\texttt{print func (\{functionID\})}}\\[.2em]
+\fbox{\texttt{print func (\{fid\})}}\\[.2em]
 It displays the list of functions.
@@
 \begin{verbatim}
-<function[0] top-level: ExitExc[-3], ()> @test.js:21:1
-Iter[12] > print func 0
-* function name: top-level
-* span info.   : test.js:1:1-21:1
+<top-level[0]: Entry[-1], NoLoop> @test.js:1:1
+ Iter[0] > print func 1
+* function name: f
+* span info.   : test.js:1:1-15
+\end{verbatim}
+}
+
+\medskip\noindent
+\fbox{\texttt{print function (\{fid\})}}\\[.2em]
+It displays the detailed control flows in the current function.
+If a function id is given, it displays that of the corresponding function.
+For example:
+{\small
+\begin{verbatim}
+<top-level[0]: Entry[-1], NoLoop> @test.js:1:1
+ Iter[0] > print function 1
+function[1] f {
+  Entry[-1] -> [0]
+
+  Block[0] -> Exit, ExitExc
+    [0] x := 1
+
+  Exit[-2]
+
+  ExitExc[-3]
+
+}
 \end{verbatim}
@@
 \begin{verbatim}
-<function[42] []Array.prototype.pop: ExitExc[-3],
- (10)> @[]Array.prototype.pop:0:0
-Iter[6] > print worklist
+<top-level[0]: Block[1], NoCall x NoLoop> @test.js:0:0
+ Iter[2] > print worklist
 * Worklist set
-(42:ExitExc[-3], (10)), (42:Exit[-2], (10)),
-(0:AfterCall[2], ()), (0:ExitExc[-3], ())
+(0:Block[1], NoCall x NoLoop)
+(0:Block[2], NoCall x NoLoop)
 \end{verbatim}
@@
 \begin{verbatim}
-<function[42] []Array.prototype.pop: ExitExc[-3],
- (10)> @[]Array.prototype.pop:0:0
-Iter[6] > print ipsucc
+<f[1]: Exit[-2], NoLoop> @test.js:1:15
+ Iter[17] > print ipsucc
 * successor map
-- src: FlowSensitiveCP(ExitExc[-3],(10))
-- dst: FlowSensitiveCP(AfterCatch[3],()),
- mayOld: (10, 1, 8)
-mustOld: (10, 1, 8)
+- src: (1:Exit[-2], NoLoop)
+- dst:
+  (0:AfterCall[2], NoLoop), mayOld: (#4, #1, #5, #2),
+    mustOld: (#4, #1, #5, #2)
+  (0:AfterCall[6], NoLoop), mayOld: (#4, #7, #1, #5,
+    #8, #2), mustOld: (#4, #7, #1, #5, #8, #2)
 \end{verbatim}
@@
 
-\medskip\noindent
-\fbox{\texttt{print trace}}\\[.2em]
-It shows the current call trace.  For example:
-{\small
-\begin{verbatim}
-<function[42] []Array.prototype.pop: Entry[-1],
- (10)> @[]Array.prototype.pop:0:0
-Iter[3] > print trace
-* Call-Context Trace
-Entry[-1] of function[42] []Array.prototype.pop with (10)
- 1>  [0] call(<>fun<>8, <>obj<>6, <>arguments<>7) @ #10
-test.js:7:11-20 @Call[1] of function[0] top-level with ()
-\end{verbatim}
-}
-
-\medskip\noindent
-\fbox{\texttt{print cfg \{name\}}}\\[.2em]
-It prints the current CFG to files \verb!name.gv! and \verb!name.pdf!.
-
-\medskip\noindent
-\fbox{\texttt{print html \{name\}}}\\[.2em]
-It prints the current CFG and its state to the \verb!name.html! file.
-We describe this facility in the next section.
-
 \subsection{Analyzer debugging with browsing}
 \label{s:3:2:2:refman}
-The \verb!print html! command writes the current status into an HTML file
-so that a user can investigate the analysis status from a browser.
+The \verb!safe web! command starts a web server to allows
+users to investigate the analysis status from a browser.
 Consider the following snapshot:
@@
 and the state just before analyzing the block are displayed on the left.
+Moreover, users can use all functionalities of the console debugger
+through the console screen in the right side.

### 2018-02-06 src/main/scala/kr/ac/kaist/safe/analyzer/console/command/CmdPrint.scala

@@ -18,81 +18,82 @@ import kr.ac.kaist.safe.analyzer.html_debugger._
 import kr.ac.kaist.safe.analyzer.domain._
 import kr.ac.kaist.safe.errors.error.IllFormedBlockStr
 import kr.ac.kaist.safe.nodes.cfg._
-import kr.ac.kaist.safe.cfg_builder.DotWriter
 
 // print
 case object CmdPrint extends Command("print", "Print out various information.") {
-  def help: Unit = {
-    println("usage: " + name + " state(-all) ({keyword})")
-    println("       " + name + " heap(-all) ({keyword})")
-    println("       " + name + " context ({keyword})")
-    println("       " + name + " block ({fid}:{bid})")
-    println("       " + name + " loc {LocName} ({keyword})")
-    println("       " + name + " func ({functionID})")
-    println("       " + name + " worklist")
-    println("       " + name + " ipsucc")
-    println("       " + name + " trace")
-    println("       " + name + " function ({fid})")
-    println("       " + name + " cfg {name}")
-    println("       " + name + " html {name}")
-  }
+  override val help: String = s"""usage: $name state(-all) ({keyword})
+       $name heap(-all) ({keyword})
+       $name context ({keyword})
+       $name block ({fid}:{bid})
+       $name loc {LocName} ({keyword})
+       $name func ({fid})
+       $name function ({fid})
+       $name worklist
+       $name ipsucc"""
 
-  def run(c: Console, args: List[String]): Option[Target] = {
+  def run(c: Interactive, args: List[String]): Option[Target] = {
     val idPattern = "(-?\\d+):(\\d+)".r
     val spPattern = "(-?\\d+):(entry|exit|exit-exc)".r
     args match {
-      case Nil => help
+      case Nil => printResult(help)
       case subcmd :: rest => subcmd match {
         case "state" =>
           val res = c.sem.getState(c.getCurCP).toString
           rest match {
-            case Nil => println(res)
-            case key :: Nil => println(grep(key, res))
-            case _ => help
+            case Nil => printResult(res)
+            case key :: Nil => printResult(grep(key, res))
+            case _ => printResult(help)
           }
         case "state-all" =>
           val res = c.sem.getState(c.getCurCP).toStringAll
           rest match {
-            case Nil => println(res)
-            case key :: Nil => println(grep(key, res))
-            case _ => help
+            case Nil => printResult(res)
+            case key :: Nil => printResult(grep(key, res))
+            case _ => printResult(help)
           }
[…]

### 2018-02-06 src/main/scala/kr/ac/kaist/safe/analyzer/domain/AbsEnvRec.scala

@@ -1,184 +1,0 @@
-/**
- * *****************************************************************************
- * Copyright (c) 2016-2017, KAIST.
- * All rights reserved.
- *
- * Use is subject to license terms.
- *
- * This distribution may include materials developed by third parties.
- * ****************************************************************************
- */
-
-package kr.ac.kaist.safe.analyzer.domain
-
-import kr.ac.kaist.safe.analyzer.domain.Utils._
-import kr.ac.kaist.safe.LINE_SEP
-import kr.ac.kaist.safe.util._
-
-/* 10.2.1 Environment Records */
-
-////////////////////////////////////////////////////////////////////////////////
-// concrete environment record type
-////////////////////////////////////////////////////////////////////////////////
-trait EnvRec
-
-////////////////////////////////////////////////////////////////////////////////
-// environment record abstract domain
-////////////////////////////////////////////////////////////////////////////////
-trait AbsEnvRec extends AbsDomain[EnvRec, AbsEnvRec] {
-  val decEnvRec: AbsDecEnvRec
-  val globalEnvRec: AbsGlobalEnvRec
-
-  // 10.2.1.2.1 HasBinding(N)
-  def HasBinding(name: String)(heap: AbsHeap): AbsBool
-
-  // 10.2.1.2.2 CreateMutableBinding(N, D)
-  def CreateMutableBinding(
-    name: String,
-    del: Boolean
-  )(heap: AbsHeap): (AbsEnvRec, AbsHeap, Set[Exception])
-
-  // 10.2.1.2.3 SetMutableBinding(N, V, S)
-  def SetMutableBinding(
-    name: String,
-    v: AbsValue,
-    strict: Boolean
-  )(heap: AbsHeap): (AbsEnvRec, AbsHeap, Set[Exception])
-
-  // 10.2.1.2.4 GetBindingValue(N, S)
-  def GetBindingValue(
-    name: String,
-    strict: Boolean
-  )(heap: AbsHeap): (AbsValue, Set[Exception])
-
-  // 10.2.1.2.5 DeleteBinding(N)
-  def DeleteBinding(
-    name: String
-  )(heap: AbsHeap): (AbsEnvRec, AbsHeap, AbsBool)
-
[…]

### 2018-02-06 src/main/scala/kr/ac/kaist/safe/analyzer/domain/binding/BindingDomain.scala

@@ -1,0 +1,39 @@
+/**
+ * *****************************************************************************
+ * Copyright (c) 2016-2017, KAIST.
+ * All rights reserved.
+ *
+ * Use is subject to license terms.
+ *
+ * This distribution may include materials developed by third parties.
+ * ****************************************************************************
+ */
+
+package kr.ac.kaist.safe.analyzer.domain
+
+import scala.collection.immutable.HashSet
+
+// binding abstract domain
+trait BindingDomain extends AbsDomain[Binding] {
+  def apply(
+    value: AbsValue,
+    uninit: AbsAbsent = AbsAbsent.Bot,
+    mutable: AbsBool = AbsBool.True
+  ): Elem
+
+  // abstract binding element
+  type Elem <: ElemTrait
+
+  // abstract binding element traits
+  trait ElemTrait extends super.ElemTrait { this: Elem =>
+    val value: AbsValue
+    val uninit: AbsAbsent
+    val mutable: AbsBool
+
+    def copy(
+      value: AbsValue = this.value,
+      uninit: AbsAbsent = this.uninit,
+      mutable: AbsBool = this.mutable
+    ): Elem
+  }
+}

### 2018-02-06 src/main/scala/kr/ac/kaist/safe/nodes/cfg/CFGFunction.scala

@@ -14,19 +14,19 @@ package kr.ac.kaist.safe.nodes.cfg
 import scala.collection.mutable.{ HashMap => MHashMap, Map => MMap }
 import kr.ac.kaist.safe.{ LINE_SEP, SIGNIFICANT_BITS }
 import kr.ac.kaist.safe.nodes.ir.IRNode
-import kr.ac.kaist.safe.util.NodeUtil
+import kr.ac.kaist.safe.util._
 import kr.ac.kaist.safe.analyzer.models.SemanticFun
 
 import spray.json._
 
 case class CFGFunction(
-    override val ir: IRNode,
+    ir: IRNode,
     argumentsName: String,
     argVars: List[CFGId],
     localVars: List[CFGId],
     name: String,
     isUser: Boolean
-) extends CFGNode(ir) {
+) extends CFGNode {
   var id: FunctionId = 0 // XXX should be a value but for JS model for a while.
 
   val entry = Entry(this)
@@ -50,6 +50,9 @@ case class CFGFunction(
   var blockData: Vector[JsValue] = _
   var capturedData: Vector[JsValue] = _
 
+  // out blocks
+  var outBlocks: List[CFGBlock] = List(exit, exitExc)
+
   // append block
   private def addBlock(block: CFGBlock): CFGBlock = {
     bidCount += 1
@@ -59,10 +62,13 @@ case class CFGFunction(
   }
 
   // create call
-  def createCall(callInstCons: Call => CFGCallInst, retVar: CFGId): Call = {
+  def createCall(callInstCons: Call => CFGCallInst, retVar: CFGId, outer: Option[LoopHead]): Call = {
     val call = Call(this, callInstCons, retVar)
     val afterCall = call.afterCall
     val afterCatch = call.afterCatch
+    call.outerLoop = outer
+    afterCall.outerLoop = outer
+    afterCatch.outerLoop = outer
     addBlock(call)
     addBlock(afterCall)
     addBlock(afterCatch)
@@ -70,14 +76,16 @@ case class CFGFunction(
   }
 
   // create block
-  def createBlock: NormalBlock = createBlock(NoLabel)
-  def createBlock(label: LabelKind): NormalBlock = {
+  def createBlock(outer: Option[LoopHead]): NormalBlock = createBlock(NoLabel, outer)
+  def createBlock(label: LabelKind, outer: Option[LoopHead]): NormalBlock = {
     val block = NormalBlock(this, label)
[…]

### 2018-02-06 tests/test262/7.4/S7.4_A5.js

@@ -1,47 +1,0 @@
-  var errorCount = 0;
-  var count = 0;
-  var hex = ["0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "A", "B", "C", "D", "E", "F", ];
-  for(var i1 = 0;i1 < 16;i1++)
-  {
-    for(var i2 = 0;i2 < 16;i2++)
-    {
-      for(var i3 = 0;i3 < 16;i3++)
-      {
-        for(var i4 = 0;i4 < 16;i4++)
-        {
-          try
-{            var uu = hex[i1] + hex[i2] + hex[i3] + hex[i4];
-            var xx = String.fromCharCode("0x" + uu);
-            var LineTerminators = ((uu === "000A") || (uu === "000D") || (uu === "2028") || (uu === "2029"));
-            var yy = 0;
-            eval("//var " + xx + "yy = -1");
-            if (LineTerminators !== true)
-            {
-              if (yy !== 0)
-              {
-                $ERROR('#' + uu + ' ');
-                errorCount++;
-              }
-            }
-            else
-            {
-              if (yy !== - 1)
-              {
-                $ERROR('#' + uu + ' ');
-                errorCount++;
-              }
-            }}
-          catch (e)
-{            $ERROR('#' + uu + ' ');
-            errorCount++;}
-
-          count++;
-        }
-      }
-    }
-  }
-  {
-    var __result1 = errorCount > 0;
-    var __expect1 = false;
-  }
-  

### 2019-03-25 bin/checkCopyrights.sh
1. Updated Scala 2.12.3. -> 2.12.6. 2. Re-organized tests. 3. Supported only JS modelings (Removed Scala modelings). 4. Added .jvmopts file to manage the JVM memory usage for sbt. 5. Added stop-exit-exc and stop-already-visited command into the console. 6. Added fast merge instructions for Scala HashMap. 7. Updated jline 2.12 -> 3.10.0. 8. Fixed the xtc jar URL

@@ -1,7 +1,7 @@
 #!/bin/sh
 
 ################################################################################
-#    Copyright (c) 2016-2017, KAIST.
+#    Copyright (c) 2016-2018, KAIST.
 #    All rights reserved.
 #
 #    Use is subject to license terms.
@@ -22,14 +22,15 @@ strdiff() {
 for dir in $WKSPACE/src $WKSPACE/tests
 do
   cd $dir
-  files_2017_java=`find $dir -name "*.java" -newer ../timestamp -print`
-  files_2017_rats=`find $dir -name "*.rats" -newer ../timestamp -print`
-  files_2017_scala=`find $dir -name "*.scala" -newer ../timestamp -print`
+  files_2018_java=`find $dir -name "*.java" -newer ../timestamp -print`
+  files_2018_rats=`find $dir -name "*.rats" -newer ../timestamp -print`
+  files_2018_scala=`find $dir -name "*.scala" -newer ../timestamp -print`
+  files_2018_scala=`find $dir -name "*.sh" -newer ../timestamp -print`
 
-  for fil in $files_2017_java $files_2017_rats $files_2017_scala
+  for fil in $files_2018_java $files_2018_rats $files_2018_scala
   do
-    res=`grep "2017, KAIST" $fil`
-    if strdiff "$res" "2017, KAIST" ; then
+    res=`grep "2018, KAIST" $fil`
+    if strdiff "$res" "2018, KAIST" ; then
       if (strdiff "$fil" "main/java/kr/ac/kaist/safe/parser/JS.java") ; then
         echo "  $fil"
       fi

### 2019-03-25 src/main/scala/kr/ac/kaist/safe/analyzer/domain/package.scala

@@ -1,6 +1,6 @@
 /**
  * *****************************************************************************
- * Copyright (c) 2016-2017, KAIST.
+ * Copyright (c) 2016-2018, KAIST.
  * All rights reserved.
  *
  * Use is subject to license terms.
@@ -13,8 +13,7 @@ package kr.ac.kaist.safe.analyzer
 
 import kr.ac.kaist.safe.nodes.cfg.{ CFG, FunctionId }
 import kr.ac.kaist.safe.errors.error._
-import scala.collection.immutable.{ HashMap, HashSet }
-import spray.json._
+import kr.ac.kaist.safe.util.{ PredAllocSite, HashMap }
 
 package object domain {
   ////////////////////////////////////////////////////////////////
@@ -28,10 +27,10 @@ package object domain {
   ////////////////////////////////////////////////////////////////
   // value constructors
   ////////////////////////////////////////////////////////////////
-  val ExcSetEmpty: Set[Exception] = HashSet[Exception]()
+  val ExcSetEmpty: Set[Exception] = Set[Exception]()
   val ExcSetTop: Set[Exception] = null // TODO refactoring
 
-  val FidSetEmpty: Set[FunctionId] = HashSet[FunctionId]()
+  val FidSetEmpty: Set[FunctionId] = Set[FunctionId]()
 
   ////////////////////////////////////////////////////////////////
   // constant values
@@ -86,11 +85,14 @@ package object domain {
   implicit def num2pv(num: AbsNum): AbsPValue = AbsPValue(numval = num)
   implicit def str2pv(str: AbsStr): AbsPValue = AbsPValue(strval = str)
 
+  // location -> LocSet
+  implicit def loc2locset(loc: Loc): LocSet = LocSet(loc)
+
   // AbsPValue -> AbsValue
   implicit def pv2v[T <% AbsPValue](pv: T): AbsValue = AbsValue(pv)
 
-  // AbsLoc -> AbsValue
-  implicit def loc2v[T <% AbsLoc](loc: T): AbsValue = AbsValue(loc)
+  // LocSet -> AbsValue
+  implicit def locset2v[T <% LocSet](loc: T): AbsValue = AbsValue(loc)
 
   // AbsValue -> AbsIValue
   implicit def v2iv[T <% AbsValue](v: T): AbsIValue = AbsIValue(v)
[…]

### 2019-03-25 src/main/scala/kr/ac/kaist/safe/analyzer/models/SelfModel.scala

@@ -1,19 +1,0 @@
-/**
- * *****************************************************************************
- * Copyright (c) 2016-2017, KAIST.
- * All rights reserved.
- *
- * Use is subject to license terms.
- *
- * This distribution may include materials developed by third parties.
- * ****************************************************************************
- */
-
-package kr.ac.kaist.safe.analyzer.models
-
-import kr.ac.kaist.safe.analyzer.domain._
-import kr.ac.kaist.safe.nodes.cfg.CFG
-
-object SelfModel extends Model {
-  def init(h: AbsHeap, cfg: CFG): (AbsHeap, AbsValue) = (h, AbsValue.Bot)
-}

### 2019-03-25 src/main/scala/kr/ac/kaist/safe/errors/error/CompileError.scala

@@ -1,40 +1,0 @@
-/**
- * *****************************************************************************
- * Copyright (c) 2016-2017, KAIST.
- * All rights reserved.
- *
- * Use is subject to license terms.
- *
- * This distribution may include materials developed by third parties.
- * ****************************************************************************
- */
-
-package kr.ac.kaist.safe.errors.error
-
-import kr.ac.kaist.safe.nodes.ast._
-
-sealed abstract class CompileError(msg: String, ast: ASTNode) extends SafeError({
-  s"${ast.info.span}: $msg"
-})
-
-case class IRIdNotBoundError(name: String, ast: ASTNode) extends CompileError({
-  s"Identifier $name is not bound."
-}, ast)
-case class NotUniqueIdError(id: Id) extends CompileError({
-  s"Identifiers should have a unique name after the disambiguation phase: ${id.text}."
-}, id)
-case class NotUniqueLabelError(l: Label) extends CompileError({
-  s"Labels should have a unique name after the disambiguation phase: ${l.id.text}."
-}, l)
-case class VarDeclNotHaveInitExprError(vd: VarDecl) extends CompileError({
-  "Variable declarations should not have any initialization expressions after the disambiguation phase."
-}, vd)
-case class InvalidUnAssignOpError(u: UnaryAssignOpApp) extends CompileError({
-  s"Invalid UnaryAssignOpApp operator: ${u.op.text}."
-}, u)
-case class InvalidInfixOpAppError(infix: InfixOpApp) extends CompileError({
-  s"Infix operator ${infix.op.text} should have at least two arguments."
-}, infix)
-case class InvalidStringError(str: StringLiteral) extends CompileError({
-  s"Incomplete escape sequence ${str.escaped}."
-}, str)

### 2019-03-25 src/main/scala/kr/ac/kaist/safe/util/FileKind.scala

@@ -1,6 +1,6 @@
 /**
  * *****************************************************************************
- * Copyright (c) 2016-2017, KAIST.
+ * Copyright (c) 2016-2018, KAIST.
  * All rights reserved.
  *
  * Use is subject to license terms.
@@ -17,7 +17,6 @@ object FileKind {
     if (fileName.endsWith(".js")) JSFile
     else if (fileName.endsWith(".js.err")) JSErrFile
     else if (fileName.endsWith(".js.todo")) JSTodoFile
-    else if (fileName.endsWith(".json")) JSONFile
     else if (fileName.endsWith(".html") ||
       fileName.endsWith(".xhtml") ||
       fileName.endsWith(".htm")) HTMLFile
@@ -29,5 +28,4 @@ case object JSFile extends FileKind
 case object JSErrFile extends FileKind
 case object JSTodoFile extends FileKind
 case object HTMLFile extends FileKind
-case object JSONFile extends FileKind
 case object NormalFile extends FileKind

### 2020-08-31 paper/pldi21/conclusion.tex
Added the PLDI latex template.

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

### 2020-08-31 paper/pldi21/detail.tex
Added the PLDI latex template.

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

### 2020-08-31 paper/pldi21/eval.tex
Added the PLDI latex template.

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

### 2020-08-31 paper/pldi21/formal.tex
Added the PLDI latex template.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

### 2020-08-31 paper/pldi21/intro.tex
Added the PLDI latex template.

\section{Introduction}
ACM's consolidated article template~\cite{Lamport:LaTeX}, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

### 2020-08-31 paper/pldi21/overview.tex
Added the PLDI latex template.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[sigplan,screen]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

### 2020-08-31 paper/pldi21/related.tex
Added the PLDI latex template.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

### 2020-08-31 paper/pldi21/sample/sample-sigconf.tex
Added the PLDI latex template.

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{The Name of the Title is Hope}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{\institution{The Kumquat Consortium}}
\email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{sampleteaser}
  \caption{Seattle Mariners at Spring Training, 2010.}
  \Description{Enjoying the baseball game from the third-base
  seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[sigconf]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

Always use midrule to separate table header rows from data rows, and
use it only for this purpose. This enables assistive technologies to
recognise table headers and support their users in navigating tables
more easily.

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader.

Figure captions are placed {\itshape below} the figure.

Every figure should also have a figure description unless it is purely
decorative. These descriptions convey what’s in the image to someone
who cannot see it. They are also used by search engine crawlers for
indexing images, and when images cannot be loaded.

A figure description must be unformatted plain text less than 2000
characters long (including spaces).  {\bfseries Figure descriptions
  should not repeat the figure caption – their purpose is to capture
  important information that is not already provided in the caption or
  the main text of the paper.} For figures that convey important and
complex new information, a short text description may not be
adequate. More complex alternative descriptions can be placed in an
appendix and referenced in a short figure description. For example,
provide a data table capturing the information in a bar chart, or a
structured list representing a graph.  For additional information
regarding how best to write figure descriptions and why doing this is
so important, please see
\url{https://www.acm.org/publications/taps/describing-figures/}.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before the command
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, a couple of articles in a proceedings (of a
  conference, symposium, workshop for example) (paginated proceedings
  article) \cite{Andler79, Hagerup1993}, a proceedings article with
  all possible elements \cite{Smith10}, an example of an enumerated
  proceedings article \cite{VanGundy07}, an informally published work
  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
  master's thesis: \cite{anisi03}, an online document / world wide web
  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
  \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

### 2020-08-31 paper/pldi21/abstract.tex
Wrote the draft of abstract.

\begin{abstract}
Static analyses based on abstract interpretation can be integrated into developer workflow and help developers to find bugs.
However, the dynamic features of JavaScript degrade the scalability and precision of the pure static bug detection.
Combining static and dynamic analyses is one of the breakthroughs in JavaScript bug detection.
Existing combined analyses have clear boundaries that apply which analysis to which part.
Such boundaries are intuitive but limit chances to optimize transitions between two analyses.
We formally present dynamic shortcuts, a more flexible compound of static and dynamic analyses.
We implement a proof of concept bug detector by extending the existing JavaScript static analyzer for a subset of ECMAScript 5.1.
Our experimental results show that adding dynamic shortcuts indeed speeds up the detection and provides more precise bug reports.
\end{abstract}

### 2020-09-01 paper/pldi21/abstract.tex
Updated the title and abstract.

@@
 Static analyses based on abstract interpretation can be integrated into developer workflow and help developers to find bugs.
-However, the dynamic features of JavaScript degrade the scalability and precision of the pure static bug detection.
+However, the dynamic features of JavaScript degrade the scalability and precision of the pure static analyses.
 Combining static and dynamic analyses is one of the breakthroughs in JavaScript bug detection.
-Existing combined analyses have clear boundaries that apply which analysis to which part.
+Existing combined analyses have static boundaries that distinguish which analysis used for which part of a program.
 Such boundaries are intuitive but limit chances to optimize transitions between two analyses.
 We formally present dynamic shortcuts, a more flexible compound of static and dynamic analyses.
-We implement a proof of concept bug detector by extending the existing JavaScript static analyzer for a subset of ECMAScript 5.1.
+We implement a proof of concept bug detector by extending the existing static analyzer supporting a subset of ECMAScript 5.1.
 Our experimental results show that adding dynamic shortcuts indeed speeds up the detection and provides more precise bug reports.

### 2020-09-01 paper/pldi21/abstract.tex
Revised the abstract

@@
 Such boundaries are intuitive but limit chances to optimize transitions between two analyses.
-We formally present dynamic shortcuts, a more flexible compound of static and dynamic analyses.
+We formally present the alloyed analysis, a more flexible compound of static and dynamic analyses.
 We implement a proof of concept bug detector by extending the existing static analyzer supporting a subset of ECMAScript 5.1.
-Our experimental results show that adding dynamic shortcuts indeed speeds up the detection and provides more precise bug reports.
+Our experimental results show that the alloyed analysis indeed speeds up the detection and reports bugs more precisely.
 \end{abstract}

### 2020-09-07 paper/pldi21/formal.tex
Till Abstract Interpretation

@@
-\section{Title Information}
+\section{Formalization}
 
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
+In this section, we formally define the dynamic shortcut over the abstract
+interpretation.
 
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
+\subsection{Notation}
+\[
+  \begin{array}{ll@{~}c@{~}l}
+    \text{Programs} & \prog &::=& (\lab: \inst)^*\\
+    \text{Labels} & \lab &\in& \labset\\
+    \text{Instructions} & \inst &::=& x = \expr \mid \kwif \; \expr \; \lab \;
+    \lab \mid \cdots\\
+    \text{Expressions} & \expr &::=& \const \mid x \mid \lambda x. \lab \mid \op(\expr, \cdots, \expr)
+    \mid \cdots\\
+  \end{array}
+\]
+
+\subsection{Concrete Semantics}
+
+We represent the semantics of a program $\prog$ as a state transition system
+$(\stset, \trans, \istset)$.  A state $\st \in \stset$ represents a status of the
+program $\prog$ and $\istset$ denotes the initial state set.  The transition
+relation $\trans \subseteq \stset \times \stset$ describes how states are
+transformed to other states.
+
+A \textit{collecting semantics} $\sem{\prog} = \{ \st \in \stset \mid \ist \in
+\istset \wedge \ist \trans^* \st \}$ consists of reachable states from initial
+states of the program $\prog$.  We could calculate it using the \textit{transfer
+function} $\transfer: \dom \rightarrow \dom$ as follows:
+\[
+  \begin{array}{r@{~}c@{~}l}
+    \sem{\prog} &=& \underset{n \rightarrow \infty}{\lim}{\transfer^n(\ielem)}\\
+    \transfer(\elem) &=& \elem \join \step(\elem)\\
+  \end{array}
+\]
+The \textit{concrete domain} $\dom = \powerset{\stset}$ is a complete lattice
+with $\cup$, $\cap$, and $\subseteq$ as its join($\join$), meet($\meet$), and
+partial order($\order$) operators.  The initial states are $\ielem = \istset$.
+The \textit{one-step execution} $\step: \dom \rightarrow \dom$ transforms states
+using the transition relation $\trans$: $\step(\elem) = \{ \st' \mid \st \in
+\elem \wedge \st \trans \st' \}$.
+
+\subsection{Abstract Interpretation}
+The abstract interpretation over-approximate the transfer $\transfer$ to the
+\textit{abstract transfer function} $\abstransfer: \absdom \rightarrow \absdom$
+to get the \textit{abstract semantics} $\abssem{\prog}$ in finite iterations as
+follows:
+\[
+    \abssem{\prog} = \underset{n \rightarrow
+    \infty}{\lim}{(\abstransfer)^n(\iabselem)}\\
+\]
+We define a \textit{state abstraction} $\dom \galois{\alpha}{\gamma} \absdom$ as
+a Galois connection between the concrete domain $\dom$ and an abstract domain
+$\absdom$ with a \textit{concretization function} $\gamma$ and a
+\textit{abstraction function} $\alpha$.  The initial abstract state $\iabselem
+\in \absdom$ represents an abstraction of the initial state set; $\ielem
+\subseteq \gamma(\iabselem)$.  The abstract transfer function $\abstransfer:
+\absdom \rightarrow \absdom$ is defined as $\abstransfer(\abselem) = \abselem
+\join \absstep(\abselem)$ with an \textit{abstract one-step execution}
+$\absstep: \abselem \rightarrow \abselem$.  For the sound state abstraction, the
+join operator and the abstract one-step execution should satisfy the following
+conditions:
+\begin{itemize}
+  \item $\forall \abselem_0, \abselem_1 \in \absdom. \; \gamma(\abselem_0) \cup
+    \gamma(\abselem_1) \subseteq \gamma(\abselem_0 \join \abselem_1)$
+  \item $\forall \abselem \in \absdom. \; \absstep \circ \gamma(\abselem) \subseteq
+    \gamma \circ \absstep(\abselem)$
+\end{itemize}

### 2020-09-09 paper/pldi21/detail.tex
[PLDI21] Removed unnecessary files / Updated formalization

@@
-\section{Typefaces}
+\section{Application: JavaScript}
 
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
+\todo
+
+% \subsection{Core Language}
+% \[
+%   \begin{array}{ll@{~}c@{~}l}
+%     \text{Programs} & \prog &::=& (\lab: \inst)^*\\
+%     \text{Labels} & \lab &\in& \labset\\
+%     \text{Instructions} & \inst &::=& x = \expr \mid \kwif \; \expr \; \lab \;
+%     \lab\\
+%     \text{Expressions} & \expr &::=& \const \mid x \mid \op(\expr, \cdots,
+%     \expr)\\
+%   \end{array}
+% \]
+% 
+% In a core language, we define a program as a sequence of labelled instructions
+% and instructions are variable assignments and branches.  An expression is a
+% constant $\const$, a variable $x$, and $n$-ary operations.  We define states
+% $\stset = \labset \times \memset$ as pairs of labels and memories mapping from
+% variables to values.  We define the transition relation $\trans$ between states
+% as follows:
+% 
+% \begin{prooftree}
+%   \AxiomC{$\prog = \cdots, \lab: x = \expr, \lab': \inst, \cdots$}
+%   \AxiomC{$\sem{e}(\mem) = v$}
+%   \BinaryInfC{$(\lab, \mem) \trans (\lab', \mem[x \mapsto v])$}
+% \end{prooftree}

### 2020-09-09 paper/pldi21/formal.tex
[PLDI21] Removed unnecessary files / Updated formalization

@@
 
-\subsection{Notation}
+\subsection{Concrete Semantics}
 \[
-  \begin{array}{ll@{~}c@{~}l}
-    \text{Programs} & \prog &::=& (\lab: \inst)^*\\
-    \text{Labels} & \lab &\in& \labset\\
-    \text{Instructions} & \inst &::=& x = \expr \mid \kwif \; \expr \; \lab \;
-    \lab \mid \cdots\\
-    \text{Expressions} & \expr &::=& \const \mid x \mid \lambda x. \lab \mid \op(\expr, \cdots, \expr)
-    \mid \cdots\\
-  \end{array}
+  \prog ::= (\lab: \inst)^*\\
 \]
-
-\subsection{Concrete Semantics}
-
-We represent the semantics of a program $\prog$ as a state transition system
-$(\stset, \trans, \istset)$.  A state $\st \in \stset$ represents a status of the
-program $\prog$ and $\istset$ denotes the initial state set.  The transition
+A program $\prog$ is a sequence of labelled instructions.  We represent the
+semantics of a program $\prog$ as a state transition system $(\stset, \trans,
+\istset)$.  A state $\st \in \stset = \labset \times \memset$ is a pair of a
+label and a memory and represents a status of the program $\prog$.  A memory
+$\mem \in \memset = \locset \finmap \valset$ is a finite mapping from locations
+to values. A program starts with an initial state in $\istset$.  The transition
 relation $\trans \subseteq \stset \times \stset$ describes how states are
@@
 \[
-  \begin{array}{r@{~}c@{~}l}
-    \sem{\prog} &=& \underset{n \rightarrow \infty}{\lim}{\transfer^n(\ielem)}\\
-    \transfer(\elem) &=& \elem \join \step(\elem)\\
-  \end{array}
+  \sem{\prog} = \underset{n \rightarrow \infty}{\lim}{\transfer^n(\ielem)}\\
+  \qquad
+  \transfer(\elem) = \elem \join \step(\elem)\\
 \]
@@
 \join \absstep(\abselem)$ with an \textit{abstract one-step execution}
-$\absstep: \abselem \rightarrow \abselem$.  For the sound state abstraction, the
+$\absstep: \absdom \rightarrow \absdom$.  For the sound state abstraction, the
 join operator and the abstract one-step execution should satisfy the following
@@
 \end{itemize}
+
+\subsection{Analysis Sensitivity}
+
+Abstract interpretation is often defined with \textit{analysis sensitivity} to
+increase the precision of static analysis.  A sensitive abstract domain
+$\sabsdom: \viewset \rightarrow \absdom$ is defined with a \textit{view
+abstraction} $\viewmap: \viewset \rightarrow \dom$ that provides multiple points
+of views for reachable states during static analysis.  It maps a finite number
+of views $\viewset$ to sets of states $\dom$. Each view $\view \in \viewset$
+represents a set of states $\viewmap(\view)$.
+A \textit{sensitive state abstraction} $\dom
+\galois{\alpha_\viewmap}{\gamma_\viewmap} \sabsdom$ is a Galois connection between
+the concrete domain $\dom$ and the sensitive abstract domain $\sabsdom$ with the
+following concretization function:
+\[
+  \gamma_\viewmap(\abselem) = \{ \st \in \stset \mid \forall \view \in \viewset.
+  \; \st \in \viewmap(\view) \Rightarrow \st \in \gamma \circ \sabselem(\view) \}
+\]
+
+With analysis sensitivities, the abstract one-step execution $\sabsstep:
+\sabsdom \rightarrow \sabsdom$ is defined as follows:
+\[
+  \sabsstep(\sabselem) = \lambda \view \in \viewset. \; \underset{\view' \in
+  \viewset}{\bigjoin}{\viewtrans{\view'}{\view} \circ \sabselem(\view')}
+\]
+where $\viewtrans{\view'}{\view}: \absdom \rightarrow \absdom$ is the abstract
+semantics of a \textit{view transition} from a view $\view'$ to another view
+$\view$.  It should satsify the following condition for the soundness of the
+analysis:
+\[
+  \forall \abselem \in \absdom. \; \step(\gamma(\abselem) \cap \viewmap(\view'))
+  \cap \viewmap(\view) \subseteq \gamma \circ
+  \viewtrans{\view'}{\view}(\abselem)
+\]
+
+One of the most widely-used sensitivity techniques is \textit{flow sensitivity}
+using a flow sensitive view abstraction $\fsviewmap: \labset \rightarrow \dom$.
+It discriminates states using their labels as follows:
+\[
+  \forall \lab \in \labset. \; \fsviewmap(\lab) = \{ \st \in \stset \mid \st =
+  (\lab, \_) \}
+\]
+
+\subsection{Abstract Counting}
+
+We define a \textit{memory abstraction} $\powerset{\memset}
+\galois{\alpha_\memset}{\gamma_\memset} \absmemset$ as a Galois connection
+between sets of concrete memories and abstract memories.  An abstract memory
+$\absmem \in \absmemset: \abslocset \finmap \absvalset$ is a finite mapping from
+abstract locations to abstract values.  The \textit{strong update} in memory
+abstraction is important to increase the precision of static analysis.  For
+sound analysis, a memory update for a specific abstract location should join old
+abstract values with new abstract values, which calls a \textit{weak update}.
+It degrades the analysis precision because of the sprious values.  To overcome
+such degradation, researchers proposed the abstract
+counting~\cite{abstract-gc-counting, revisit-recency} to track how many times an
+abstract location has been allocated and to apply strong updates to singleton
+abstract locations.
+
+We extended abstract states with an abstract counting operator $\abscount{-}:
+\abslocset \rightarrow \abscountset = \{ \abszero, \absone, \absmany \}$, which
+is a function that takes an abstract location and returns its abstract count;
+$\abszero$ denotes that it have never been allocated, $\absone$ once, and
+$\absmany$ more than equals to twice.
+
+\subsection{On-Demand Access Aanlysis}

### 2020-09-09 paper/pldi21/related.tex
[PLDI21] Removed unnecessary files / Updated formalization

@@
-\section{Rights Information}
+\section{Related Work}
 
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
+\todo
 
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
+\subsection{Combined Analysis}
+
 \begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
+  \item Concerto: a framework for combined concrete and abstract
+    interpretation~\cite{concerto}
+  \item Battles with false positives in static analysis of JavaScript web
+    applications in the wild~\cite{battles}
+  \item EventHandler-Based Analysis Framework for Web Apps Using Dynamically
+    Collected States~\cite{eha}
+  \item Automatic Modeling of Opaque Code for JavaScript Static
+    Analysis~\cite{opaque-model}
+  \item Mimic: Computing models for opaque code~\cite{mimic}
 \end{itemize}
 
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
+\subsection{Abstract Counting}
 
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
+\begin{itemize}
+  \item Improving flow analyses via $\Gamma$CFA: Abstract garbage collection and
+    counting~\cite{abstract-gc-counting}
+  \item Revisiting recency abstraction for JavaScript: towards an intuitive,
+    compositional, and efficient heap abstraction~\cite{revisit-recency}
+\end{itemize}
+
+\subsection{Access Analysis}
+
+\begin{itemize}
+  \item Access Analysis-Based Tight Localization of Abstract
+    Memories~\cite{func-local}
+  \item Design and implementation of sparse global analyses for C-like
+    languages~\cite{sparse}
+\end{itemize}

### 2020-09-11 paper/pldi21/formal.tex
[PLDI21] Lazy Concrete Interpretation / Combined Analysis

@@
 sound analysis, a memory update for a specific abstract location should join old
-abstract values with new abstract values, which calls a \textit{weak update}.
+abstract values with new abstract values, called as a \textit{weak update}.
 It degrades the analysis precision because of the sprious values.  To overcome
@@
 
-We extended abstract states with an abstract counting operator $\abscount{-}:
+We extend abstract states with an abstract counting operator $\abscount{-}:
 \abslocset \rightarrow \abscountset = \{ \abszero, \absone, \absmany \}$, which
@@
 $\abszero$ denotes that it have never been allocated, $\absone$ once, and
-$\absmany$ more than equals to twice.
+$\absmany$ more than or equals to twice.
 
-\subsection{On-Demand Access Aanlysis}
+\subsection{Lazy Concrete Interpretation}
+
+We define a \textit{lazy concrete interpretation} by extending the transition
+relation $\trans$ as a symbolic transition relation $\symbtrans$ on abstract
+states. First, we extends the concrete states $\stset$ to \textit{symbolic
+states} $\symbstset = (\labset \times \symbmemset) \cup \{ \excst \}$ with
+symbolic memories $\symbmemset$ consisting of symbolic values $\symb \in
+\symbset$ and a special exception state $\excst$. Each symbolic value denotes an
+abstract value cannot be concretized to a singleton value.  A symbolic state
+\textit{alwyas} has a symbolic transition relation with a single symbolic state.
+When a symbolic state has a non-determinism or accesses symbolic values, it has
+the relation with the exception state: $\symbst \symbtrans \excst$.  Thus, the lazy
+concrete interpretation does not care about the non-deterministic semantics or
+symbolic values.
+
+We define a Galois connection $\symbstset
+\galois{\alpha_\symbset}{\gamma_\symbset} \absdom$ to freely convert an abstract
+state to the corresponding symbolic state and vice versa.  In the concretization
+function $\gamma_\symbset$, if an abstract value $\absval$ represents a
+singleton value, the function transforms the abstract value to the
+corresponding concrete value.  Otherwise, it keeps the abstract value as a
+symbolic value in the result symbolic state.
+
+\subsection{Combined Analysis}
+
+We define the \textit{combined analysis} of the abstract interpretation and the
+lazy concrete interpretation by extending the view transition as follows:
+\[
+  \viewtrans{\view'}{\view}_\symbset(\abselem) = \left\{
+    \begin{array}{ll}
+      \abselem_0 & \text{if} \; \symbst' \symbtrans \excst\\
+      \alpha_\symbset(\symbst) & \text{if} \; \symbst' \symbtrans \symbst
+      \wedge\\
+      & \phantom{\text{if}} \; \gamma \circ \alpha_\symbset(\symbst)
+      \cap \viewmap(\view) \neq \varnothing\\ \bot & \text{otherwise}\\
+    \end{array}
+  \right.
+\]
+where $\symbst' = \gamma_\symbset \circ \abselem(\view')$ and $\abselem_0 =
+\viewtrans{\view'}{\view}(\abselem)$.  The combined analysis first tries to
+convert the current abstract state $\abselem(\view')$ to the corresponding
+symbolic state $\symbst'$ and performs the lazy concrete evaluation.  When the
+evaluation produces the exception state $\excst$, it utilizes the abstract
+interpretation instead of the lazy concrete interpretation.  Otherwise, the lazy
+concrete interpretation successfully produces a new symbolic state $\symbst$.
+If the symbolic state $\symbst$ is related to the target view $\view$, the
+result is the corresponding abstract state $\alpha_\symbset(\symbst)$ of the
+symbolic state $\symbst$. Otherwise, the result becomes the bottom $\bot$.

### 2020-09-11 paper/pldi21/detail.tex
[PLDI21] Core langage of JavaScript and its concrete semantics

--- 2020-08-31 paper/pldi21/detail.tex
@@
-\section{Typefaces}
+\section{Application: JavaScript}
 
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
+In this section, we introduce the core language of JavaScript that supports
+first-class functions, open objects, and first-class property names, and define
+combined analysis of the core language.
+
+\subsection{Core Language of JavaScript}
+
+\begin{figure*}[t]
+  \centering
+
+  \fbox{$\st \trans \st$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \refer = \expr\\
+      \referrule{\st}{\refer}{\loc}\\
+      \exprrule{\st}{\expr}{\val}\\
+    }
+    {
+      \st = (\lab, \mem, \ctxtstack, \addr)
+      \trans
+      (\labnext(\lab), \mem[\loc \mapsto \val], \ctxtstack, \addr)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \refer = \kwobj\\
+      \referrule{\st}{\refer}{\loc}\\
+      \addr' = \text{(a fresh object address)}
+    }
+    {
+      \st = (\lab, \mem, \ctxtstack, \addr)
+      \trans
+      (\labnext(\lab), \mem[\loc \mapsto \addr'], \ctxtstack, \addr)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \refer = \expr_f ( \expr_a )\\
+      \referrule{\st}{\refer}{\loc}\\
+      \exprrule{\st}{\expr_f}{\fval{x}{\lab_b}}\\
+      \exprrule{\st}{\expr_a}{\val_a}\\
+      \addr' = \text{(a fresh environment address)}
+    }
+    {
+      \st = (\lab, \mem, \ctxtstack, \addr)
+      \trans
+      (\lab_b, \mem[(\addr', x) \mapsto \val_a], (\addr, \labnext(\lab), \loc)
+      :: \ctxtstack, \addr')
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwret \; \expr\\
+      \exprrule{\st}{\expr}{\val}\\
+    }
+    {
+      \st = (\lab, \mem, (\addr', \lab', \loc) :: \ctxtstack, \addr)
+      \trans
+      (\lab', \mem[\loc \mapsto \val], \ctxtstack, \addr')
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwif \; \expr \; \lab'\\
+      \exprrule{\st}{\expr}{\kwtrue}\\
+    }
+    {
+      \st = (\lab, \mem, \ctxtstack, \addr)
+      \trans
+      (\lab', \mem, \ctxtstack, \addr)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwif \; \expr \; \lab'\\
+      \exprrule{\st}{\expr}{\kwfalse}\\
+    }
+    {
+      \st = (\lab, \mem, \ctxtstack, \addr)
+      \trans
+      (\labnext(\lab), \mem, \ctxtstack, \addr)
+    }
+  \end{mathpar}
+
+  \fbox{$\referrule{\st}{\refer}{\loc}$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {}
+    {
+      \referrule{\st = (\lab, \mem, \ctxtstack, \addr)}{x}{(\addr, x)}\\
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \exprrule{\st}{\expr_0}{\addr_0}\\
+      \exprrule{\st}{\expr_1}{\val_1}\\
+      \val_1 \in \strset\\
+    }
+    {
+      \referrule{\st = (\lab, \mem, \ctxtstack, \addr)}{\expr_0 [ \expr_1
+      ]}{(\addr_0, \val_1)}
+    }
+  \end{mathpar}
+
+  \fbox{$\exprrule{\st}{\expr}{\val}$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {
+    }
+    {
+      \exprrule{\st = (\lab, \mem, \ctxtstack, \addr)}{\pval}{\pval}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+    }
+    {
+      \exprrule{\st = (\lab, \mem, \ctxtstack,
+      \addr)}{\fval{x}{\lab'}}{\fval{x}{\lab'}}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \referrule{\st}{\refer}{\loc}\\
+      \loc \in \mem\\
+    }
+    {
+      \exprrule{\st = (\lab, \mem, \ctxtstack, \addr)}{\refer}{\mem(\loc)}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \referrule{\st}{\refer}{\loc}\\
+      \loc \not\in \mem\\
+    }
+    {
+      \exprrule{\st = (\lab, \mem, \ctxtstack, \addr)}{\refer}{\kwundef}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \exprrule{\st}{\expr_1}{\val_1}\\
+      \cdots\\
+      \exprrule{\st}{\expr_n}{\val_n}\\
+    }
+    {
+      \exprrule{\st = (\lab, \mem, \ctxtstack, \addr)}
+      {\op(\expr_1, \cdots, \expr_n)}{\op(\val_1, \cdots, \val_n)}
+    }
+  \end{mathpar}
+
+  \caption{The transition relation for the core language of JavaScript}
+  \label{fig:core-trans-rel}
+\end{figure*}
+
+\[
+  \begin{array}{ll@{~}c@{~}l}
+    \text{Programs} & \prog &::=& (\lab: \inst)^*\\
+
+    \text{Labels} & \lab &\in& \labset\\
+
+    \text{Instructions} & \inst &::=&
+    \refer = \expr \mid
+    \refer = \kwobj \mid
+    \refer = \expr ( \expr ) \mid
+    \kwret \; \expr \mid
+    \kwif \; \expr \; \lab\\
+
+    \text{References} & \refer &::=&
+    x \mid
+    \expr [ \expr ]\\
+
+    \text{Expressions} & \expr &::=&
+    \pval \mid
+    \lambda x. \; \lab \mid
+    \refer \mid
+    \op(\expr^*)\\
+  \end{array}
+\]
+
+A program $\prog$ is a sequence of labelled instructions. An instruction $\inst$
+is an expression assignment, an object creation, a function call, a return
+instruction, or a branch.  An expression $\expr$ is a primitive, a lambda
+function, a reference, or an operation between other expressions.  A reference
+$\refer$ is a variable or a property access of an object.
+
+\[
+  \begin{array}{lr@{~}c@{~}l@{~}c@{~}l}
+    \text{States} & \st &\in& \stset &=& \labset \times \memset \times
+    \ctxtset^* \times \eaddrset\\
+    \text{Memories} & \mem &\in& \memset &=& \locset \rightarrow \valset\\
+    \text{Contexts} & \ctxt &\in& \ctxtset &=& \eaddrset \times \labset \times
+    \locset\\
+    \text{Locations} & \loc &\in& \locset &=& (\eaddrset \times \varset) \uplus
+    (\oaddrset \times \strset)\\
+    \text{Values} & \val &\in& \valset &=& \pvalset \uplus \oaddrset \uplus
+    \fvalset\\
+    \text{Primitives} & \pval &\in& \pvalset &=& \strset \uplus \cdots\\
+    \text{Addresses} & \addr &\in& \addrset &=& \eaddrset \uplus \oaddrset\\
+    \text{Functions} & \fval{x}{\lab} &\in& \fvalset &=& \varset \times
+    \labset\\
+  \end{array}
+\]
+
+States $\stset$ consist of labels $\labset$, memories $\memset$, context stacks
+$\ctxtset^*$, and environment addresses.  A memory $\mem \in \memset$ is a
+mapping from locations to values.  Context stacks is sequences of contexts
+$\ctxtset$ and a context $\ctxt \in \ctxtset$ is a tuple of an environment
+address, a return label, and a left-hand side location.  A location $\loc \in
+\locset$ is a variable or an object property; a variable location consists of an
+environment address and its name, and an object property location consists of an
+object address and a string value.  A value $\val \in \valset$ is a primitive,
+an address, or a function value.  An address $\addr \in \addrset$ is an
+environment address or an object address.  A function value
+$\fval{x}{\lab}{\addr} \in \fvalset$ consists a parameter and a body label.  In
+the core language, the closed scoping is used for functions for brevity thus
+only parameters and local variables are accessible in the function body.
+
+We formulate the concrete semantics of the core language as described in
+Figure~\ref{fig:core-trans-rel}.  The transition relation between concrete
+states is defined with the semantics of references and expressions using two
+different forms \fbox{$\referrule{\st}{\refer}{\loc}$} and
+\fbox{$\exprrule{\st}{\expr}{\val}$}, respectively.  The special value
+$\kwundef$ denotes an undefined value and it is produced when the program access
+an unknown location.
+
+\subsection{Abstract Semantics}
+
+\todo

### 2020-09-22 paper/pldi21/detail.tex
Updated formalization of combined analysis

@@
 \todo
+
+\subsection{Abstract Counting}
+
+We define a \textit{memory abstraction} $\powerset{\memset}
+\galois{\alpha_\memset}{\gamma_\memset} \absmemset$ as a Galois connection
+between sets of concrete memories and abstract memories.  An abstract memory
+$\absmem \in \absmemset: \abslocset \finmap \absvalset$ is a finite mapping from
+abstract locations to abstract values.  The \textit{strong update} in memory
+abstraction is important to increase the precision of static analysis.  For
+sound analysis, a memory update for a specific abstract location should join old
+abstract values with new abstract values, called as a \textit{weak update}.
+It degrades the analysis precision because of the sprious values.  To overcome
+such degradation, researchers proposed the abstract
+counting~\cite{abstract-gc-counting, revisit-recency} to track how many times an
+abstract location has been allocated and to apply strong updates to singleton
+abstract locations.
+
+We extend abstract states with an abstract counting operator $\abscount{-}:
+\abslocset \rightarrow \abscountset = \{ \abszero, \absone, \absmany \}$, which
+is a function that takes an abstract location and returns its abstract count;
+$\abszero$ denotes that it have never been allocated, $\absone$ once, and
+$\absmany$ more than or equals to twice.

### 2020-09-22 paper/pldi21/formal.tex
Updated formalization of combined analysis

--- 2020-09-09 paper/pldi21/formal.tex
@@
 \subsection{Concrete Semantics}
-\[
-  \prog ::= (\lab: \inst)^*\\
-\]
-A program $\prog$ is a sequence of labelled instructions.  We represent the
-semantics of a program $\prog$ as a state transition system $(\stset, \trans,
-\istset)$.  A state $\st \in \stset = \labset \times \memset$ is a pair of a
-label and a memory and represents a status of the program $\prog$.  A memory
-$\mem \in \memset = \locset \finmap \valset$ is a finite mapping from locations
-to values. A program starts with an initial state in $\istset$.  The transition
-relation $\trans \subseteq \stset \times \stset$ describes how states are
-transformed to other states.
 
-A \textit{collecting semantics} $\sem{\prog} = \{ \st \in \stset \mid \ist \in
-\istset \wedge \ist \trans^* \st \}$ consists of reachable states from initial
-states of the program $\prog$.  We could calculate it using the \textit{transfer
-function} $\transfer: \dom \rightarrow \dom$ as follows:
+% \[
+%   \prog ::= (\lab: \inst)^*\\
+% \]
+% A program $\prog$ is a sequence of labelled instructions.  We represent the
+% semantics of a program $\prog$ as a state transition system $(\stset, \trans,
+% \istset)$.  A state $\st \in \stset = \labset \times \memset$ is a pair of a
+% label and a memory and represents a status of the program $\prog$.  A memory
+% $\mem \in \memset = \locset \finmap \valset$ is a finite mapping from locations
+% to values. A program starts with an initial state in $\istset$.  The transition
+% relation $\trans \subseteq \stset \times \stset$ describes how states are
+% transformed to other states.  It is defined with the \textit{concrete semantics}
+% $\sem{\inst}: \stset \rightarrow \powerset{\stset}$ of instructions as follows:
+% \[
+%   \st \trans \st' \iff \st = (\lab, \_) \wedge \st' \in \sem{\prog(\lab)}(\st)
+% \]
+
+We define a program $\prog$ as a state transition system $(\stset, \trans,
+\istset)$.  A program starts with an initial state in $\istset$ and the
+transition relation $\trans \subseteq \stset \times \stset$ describes how states
+are transformed to other states.  A \textit{collecting semantics} $\sem{\prog} =
+\{ \st \in \stset \mid \ist \in \istset \wedge \ist \trans^* \st \}$ consists of
+reachable states from initial states of the program $\prog$.  We could calculate
+it using the \textit{transfer function} $\transfer: \dom \rightarrow \dom$ as
+follows:
 \[
@@
 with $\cup$, $\cap$, and $\subseteq$ as its join($\join$), meet($\meet$), and
-partial order($\order$) operators.  The initial states are $\ielem = \istset$.
-The \textit{one-step execution} $\step: \dom \rightarrow \dom$ transforms states
-using the transition relation $\trans$: $\step(\elem) = \{ \st' \mid \st \in
-\elem \wedge \st \trans \st' \}$.
+partial order($\order$) operators.  The element $\ielem$ denotes the initial
+states $\istset$.  The \textit{one-step execution} $\step: \dom \rightarrow
+\dom$ transforms states using the transition relation $\trans$: $\step(\elem) =
+\{ \st' \mid \st \in \elem \wedge \st \trans \st' \}$.
 
 \subsection{Abstract Interpretation}
-The abstract interpretation over-approximate the transfer $\transfer$ to the
-\textit{abstract transfer function} $\abstransfer: \absdom \rightarrow \absdom$
-to get the \textit{abstract semantics} $\abssem{\prog}$ in finite iterations as
-follows:
+The abstract interpretation~\cite{abs-interp-1977, abs-interp-1992}
+over-approximate the transfer $\transfer$ to the \textit{abstract transfer
+function} $\abstransfer: \absdom \rightarrow \absdom$ to get the
+\textit{abstract semantics} $\abssem{\prog}$ in finite iterations as follows:
 \[
@@
 \[
-  \gamma_\viewmap(\abselem) = \{ \st \in \stset \mid \forall \view \in \viewset.
+  \gamma_\viewmap(\sabselem) = \{ \st \in \stset \mid \forall \view \in \viewset.
   \; \st \in \viewmap(\view) \Rightarrow \st \in \gamma \circ \sabselem(\view) \}
@@
 
-One of the most widely-used sensitivity techniques is \textit{flow sensitivity}
-using a flow sensitive view abstraction $\fsviewmap: \labset \rightarrow \dom$.
-It discriminates states using their labels as follows:
+% One of the most widely-used sensitivity techniques is \textit{flow sensitivity}
+% using a flow sensitive view abstraction $\fsviewmap: \labset \rightarrow \dom$.
+% It discriminates states using their labels as follows:
+% \[
+%   \forall \lab \in \labset. \; \fsviewmap(\lab) = \{ \st \in \stset \mid \st =
+%   (\lab, \_) \}
+% \]
+
+\subsection{Lazy Concrete Interpretation}
+
+We define a \textit{lazy concrete interpretation} by extending the transition
+relation $\trans$ as a symbolic transition relation $\symbtrans$ on symbolic
+states. First, we extends the concrete states $\stset$ to \textit{symbolic
+states} with symbolic values $\symbset$ that denote abstract values cannot be
+concretized to singleton values. A symbolic transition relation $\symbtrans
+\subseteq \symbstset \times (\symbstset \uplus \{ \excst \})$ is exactly same
+with the original transition relation $\trans$ except when the relation requires
+the exact value of symbolic values.  In this case, the symbolic state has the
+relation a special exception state $\excst$ to represent that it is impossible
+to interpret in a concrete way.  Thus, a symbolic state \textit{always} has a
+symbolic transition relation with a single symbolic state, and the lazy concrete
+interpret is linear execution until reaching the exception state.
+
+To freely convert a pair of view and an abstract state to the corresponding
+symbolic state and vice versa, we define two domain converters $\symbstset
+\galois{\saconverter}{\asconverter} (\viewset \times \absdom)$.  In the
+converter $\asconverter$ from abstract states to symbolic states, if an abstract
+value $\absval$ represents a singleton value, the function transforms the
+abstract value to the corresponding concrete value.  Otherwise, it converts the
+abstract value as a symbolic value in the result symbolic state.  Two converters
+convert given elements wihtout loss of information:
 \[
-  \forall \lab \in \labset. \; \fsviewmap(\lab) = \{ \st \in \stset \mid \st =
-  (\lab, \_) \}
+  \saconverter \circ \asconverter = \asconverter \circ \saconverter = \identity
 \]
+where $\identity$ denotes the identity function.
 
-\subsection{Abstract Counting}
+\subsection{Combined Analysis}
 
-We define a \textit{memory abstraction} $\powerset{\memset}
-\galois{\alpha_\memset}{\gamma_\memset} \absmemset$ as a Galois connection
-between sets of concrete memories and abstract memories.  An abstract memory
-$\absmem \in \absmemset: \abslocset \finmap \absvalset$ is a finite mapping from
-abstract locations to abstract values.  The \textit{strong update} in memory
-abstraction is important to increase the precision of static analysis.  For
-sound analysis, a memory update for a specific abstract location should join old
-abstract values with new abstract values, which calls a \textit{weak update}.
-It degrades the analysis precision because of the sprious values.  To overcome
-such degradation, researchers proposed the abstract
-counting~\cite{abstract-gc-counting, revisit-recency} to track how many times an
-abstract location has been allocated and to apply strong updates to singleton
-abstract locations.
+We define the \textit{combined analysis} of the abstract interpretation and the
+lazy concrete interpretation.  In the combined analysis, we use the powerset of
+symbolic states as the domain $\combdom = \powerset{\symbstset}$, and extend the
+view transition as follows:
+\[
+  \begin{array}{l}
+    \combviewtrans{\view}{\view'}(\combelem) =\\
+    \qquad \{
+      \symbst' \mid \symbst \in S \wedge
+      \symbst \symbtrans \symbst' \wedge
+      \saconverter(\symbst') = (\view', \_)
+    \}\\
+    \qquad \cup \left\{
+    \begin{array}{ll}
+      \{ \asconverter \circ \viewtrans{\view}{\view'}(\bigjoin D) \}
+      & \text{if} \; D \neq \varnothing\\
+      \varnothing & \text{otherwise}\\
+    \end{array}
+    \right.
+  \end{array}
+\]
+where $S = \combelem\mid_{\checker}$ and $D =
+\dot{\saconverter}(\combelem\mid_{\neg\checker})$.  The dot notation $\dot{f}$
+denotes the element-wise extended function of a function $f$.  We could
+configure when the lazy concrete interpretation or the abstract interpretation
+is performed based on the definition of the $\checker$ function and its negation
+$\neg\checker$.  It should satisfy the following condition for the soundness and
+the termination of the combined analysis:
+\[
+  \checker(\symbst) \Rightarrow \symbst \symbtrans^k \excst \wedge
+  1 \leq k \leq N
+\]
+where $N$ is the pre-defined maximum length of the lazy concrete interpretation.
+The combined analysis just performs one-step symbolic transition for each
+symbolic state that passes the filter $\checker$. On the other hand, it converts
+remaining symbolic states to the corresponding abstract states, merges them into
+a single abstract state, and performs the abstract one-step execution for the
+abstract state.
 
-We extended abstract states with an abstract counting operator $\abscount{-}:
-\abslocset \rightarrow \abscountset = \{ \abszero, \absone, \absmany \}$, which
-is a function that takes an abstract location and returns its abstract count;
-$\abszero$ denotes that it have never been allocated, $\absone$ once, and
-$\absmany$ more than equals to twice.
-
-\subsection{On-Demand Access Aanlysis}
+% The abstract sensitivity should be defined with a view
+% abstraction $\viewmap: \viewset \rightarrow \dom$ more find-grained than the
+% flow sensitive view abstraction $\fsviewmap$:
+% \[
+%   \forall \view \in \viewset. \; \exists \lab \in \labset. \;
+%   \viewmap(\view) \subseteq \fsviewmap(\lab)
+% \]

### 2020-09-22 paper/pldi21/detail.tex
Abstract semantics of core language

--- 2020-09-11 paper/pldi21/detail.tex
@@
     \inferrule*[width=0.48\textwidth]
-    {
-    }
+    {}
     {
@@
       \referrule{\st}{\refer}{\loc}\\
-      \loc \in \mem\\
+      \loc \in \Dom(\mem)
     }
@@
     {
-      \referrule{\st}{\refer}{\loc}\\
-      \loc \not\in \mem\\
-    }
-    {
-      \exprrule{\st = (\lab, \mem, \ctxtstack, \addr)}{\refer}{\kwundef}
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
       \exprrule{\st}{\expr_1}{\val_1}\\
       \cdots\\
-      \exprrule{\st}{\expr_n}{\val_n}\\
+      \exprrule{\st}{\expr_n}{\val_n}
     }
@@
 is an expression assignment, an object creation, a function call, a return
-instruction, or a branch.  An expression $\expr$ is a primitive, a lambda
-function, a reference, or an operation between other expressions.  A reference
-$\refer$ is a variable or a property access of an object.
+instruction, or a branch.  A reference $\refer$ is a variable or a property
+access of an object.  An expression $\expr$ is a primitive, a lambda function, a
+reference, or an operation between other expressions.
 
@@
     \ctxtset^* \times \eaddrset\\
-    \text{Memories} & \mem &\in& \memset &=& \locset \rightarrow \valset\\
+    \text{Memories} & \mem &\in& \memset &=& \locset \finmap \valset\\
     \text{Contexts} & \ctxt &\in& \ctxtset &=& \eaddrset \times \labset \times
@@
 States $\stset$ consist of labels $\labset$, memories $\memset$, context stacks
-$\ctxtset^*$, and environment addresses.  A memory $\mem \in \memset$ is a
-mapping from locations to values.  Context stacks is sequences of contexts
-$\ctxtset$ and a context $\ctxt \in \ctxtset$ is a tuple of an environment
-address, a return label, and a left-hand side location.  A location $\loc \in
-\locset$ is a variable or an object property; a variable location consists of an
-environment address and its name, and an object property location consists of an
-object address and a string value.  A value $\val \in \valset$ is a primitive,
-an address, or a function value.  An address $\addr \in \addrset$ is an
-environment address or an object address.  A function value
-$\fval{x}{\lab}{\addr} \in \fvalset$ consists a parameter and a body label.  In
-the core language, the closed scoping is used for functions for brevity thus
-only parameters and local variables are accessible in the function body.
+$\ctxtset^*$, and environment addresses $\eaddrset$.  A memory $\mem \in
+\memset$ is a finite mapping from locations to values.  Context stacks is
+sequences of contexts $\ctxtset$ and a context $\ctxt \in \ctxtset$ is a tuple
+of an environment address, a return label, and a left-hand side location.  A
+location $\loc \in \locset$ is a variable or an object property; a variable
+location consists of an environment address and its name, and an object property
+location consists of an object address and a string value.  A value $\val \in
+\valset$ is a primitive, an address, or a function value.  An address $\addr \in
+\addrset$ is an environment address or an object address.  A function value
+$\fval{x}{\lab} \in \fvalset$ consists of a parameter and a body label.  In the
+core language, the closed scoping is used for functions for brevity thus only
+parameters and local variables are accessible in the function body.
 
@@
 different forms \fbox{$\referrule{\st}{\refer}{\loc}$} and
-\fbox{$\exprrule{\st}{\expr}{\val}$}, respectively.  The special value
-$\kwundef$ denotes an undefined value and it is produced when the program access
-an unknown location.
+\fbox{$\exprrule{\st}{\expr}{\val}$}, respectively.  The initial states are
+$\istset = \{ (\ilab, \varnothing, \epsilon, \tladdr) \}$ where $\ilab$ denotes
+the initial label, $\epsilon$ empty list, and $\tladdr$ the top-level
+environment address.  The function $\labnext$ returns the next lable of the
+given lable in the current program $\prog$.
 
@@
 
-\todo
+\begin{figure*}[t]
+  \centering
+
+  \fbox{$\viewtrans{\view}{\view'}: \absdom \rightarrow \absdom$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
+      \prog(\lab) = \refer = \expr\\
+      \referabssem{\refer}(\abselem) = L\\
+      \exprabssem{\expr}(\abselem) = \absval
+    }
+    {
+      \viewtrans{\lab}{\labnext(\lab)}(\abselem) =
+      (\absmem[L \mapstos \absval], \absctxt, \absaddr, \abscount)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
+      \prog(\lab) = \refer = \kwobj\\
+      \referabssem{\refer}(\abselem) = L\\
+      \oabsaddr = \lab
+    }
+    {
+      \viewtrans{\lab}{\labnext(\lab)}(\abselem) = (\absmem[L \mapstos \{
+      \oabsaddr \}], \absctxt, \absaddr, \inc(\abscount, \oabsaddr))
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
+      \prog(\lab) = \refer = \expr_f ( \expr_a )\\
+      \referabssem{\refer}(\abselem) = L\\
+      \fval{x}{\lab_b} \in \exprabssem{\expr_f}(\abselem)\\
+      \exprabssem{\expr_a}(\abselem) = \absval_a\\
+      \eabsaddr = \lab_b\\
+      \eabsctxt = \absctxt[\eabsaddr \mapsto \absctxt(\eabsaddr) \cup \{
+      (\absaddr, \lab, L) \} ]
+    }
+    {
+      \viewtrans{\lab}{\lab_b}(\abselem) = (\absmem[(\eabsaddr, x) \mapsto
+      \absval_a], \eabsctxt, \eabsaddr, \inc(\abscount, \eabsaddr))
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
+      \prog(\lab) = \kwret \; \expr\\
+      \exprabssem{\expr}(\abselem) = \absval\\
+      (\rabsaddr, \lab', L) \in \absctxt(\absaddr)
+    }
+    {
+      \viewtrans{\lab}{\lab'}(\abselem) = (\absmem[L \mapstos \absval],
+      \absctxt, \rabsaddr, \abscount)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwif \; \expr \; \lab'\\
+      \kwtrue \in \exprabssem{\expr}(\abselem)
+    }
+    {
+      \viewtrans{\lab}{\lab'}(\abselem) = \abselem
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwif \; \expr \; \lab'\\
+      \kwfalse \in \exprabssem{\expr}(\abselem)
+    }
+    {
+      \viewtrans{\lab}{\labnext(\lab)}(\abselem) = \abselem
+    }
+  \end{mathpar}
+
+  \fbox{$\referabssem{\refer}: \absdom \rightarrow \powerset{\abslocset}$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)
+    }
+    {
+      \referabssem{x}(\abselem) = \{ (\absaddr, x) \}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
+      A = \exprabssem{\expr_0}(\abselem) \cap \absaddrset\\
+      S = \exprabssem{\expr_1}(\abselem) \cap \strset\\
+    }
+    {
+      \referabssem{\expr_0 [ \expr_1 ]} = A \times S
+    }
+  \end{mathpar}
+
+  \fbox{$\exprabssem{\expr}: \absdom \rightarrow \absvalset$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {}
+    {
+      \exprabssem{\pval}(\abselem) = \{ \pval \}
+    }
+
+    {}
+    {
+      \exprabssem{\fval{x}{\lab}}(\abselem) = \{ \fval{x}{\lab} \}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
+      \absval = \bigjoin \{ \absmem(\absloc) \mid \absloc \in
+      \referabssem{\refer}(\abselem) \}
+    }
+    {
+      \exprabssem{\refer}(\abselem) = \absval
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \exprabssem{\expr_1}(\abselem) = \absval_1\\
+      \cdots\\
+      \exprabssem{\expr_n}(\abselem) = \absval_n
+    }
+    {
+      \exprabssem{\op(\expr_1, \cdots, \expr_n)}(\abselem) = \ops(\absval_1,
+      \cdots, \absval_n)
+    }
+  \end{mathpar}
+
+  \caption{The semantics of view transition for the core language of JavaScript}
+  \label{fig:core-view-trans}
+\end{figure*}
+
+In abstract semantics of the core language, we use the flow sensitivity with a
+flow sensitive view abstraction $\fsviewmap: \labset \rightarrow \dom$ that
+discriminates states using their labels: $\forall \lab \in \labset. \;
+\fsviewmap(\lab) = \{ \st \in \stset \mid \st = (\lab, \_, \_, \_) \}$ Thus, the
+sensitive abstract domain is defined as $\sabsdom = \labset \rightarrow
+\absdom$.  We define an abstract state $\abselem \in \absdom$ as a tuple of an
+abstract memory, an abstract context, an abstract address, and set of singleton
+abstract addresses as follows:
+
+\[
+  \begin{array}{lr@{~}c@{~}l@{~}c@{~}l}
+    \text{Abstract States} & \abselem &\in& \absdom &=& \absmemset \times \absctxtset
+    \times \absaddrset \times \abscountset\\
+    \text{Abstract Memories} & \absmem &\in& \absmemset &=& \abslocset \finmap
+    \absvalset\\
+    \text{Abstract Contexts} & \absctxt &\in& \absctxtset &=& \absaddrset \finmap
+    \powerset{\absaddrset \times \viewset \times \powerset{\abslocset}}\\
+    \text{Abstract Locations} & \absloc &\in& \abslocset &=& (\absaddrset \times
+    \varset) \uplus (\absaddrset \times \strset)\\
+    \text{Abstract Values} & \absval &\in& \absvalset &=& \powerset{\pvalset
+    \uplus \absaddrset \uplus \fvalset}\\
+    \text{Abstract Addresses} & \absaddr &\in& \absaddrset &=& \labset\\
+    \text{Abstract Counters} & \abscount &\in& \abscountset &=& \absaddrset
+    \rightarrow \{ \abszero, \absone, \absmany \}\\
+  \end{array}
+\]
+
+An abstract memory $\absmem \in \absmemset$ is a finite mapping from abstract
+locations $\abslocset$ to abstract values $\absvalset$.  Abstract locations
+$\abslocset$ are pairs of abstract addresses with variable names or string
+values. Abstract addresses $\absaddrset$ are defined with the
+\textit{allocation-site abstraction} that partitions concrete addresses
+$\addrset$ based on their allocation sites $\labset$.  Abstract contexts
+$\absctxtset$ are finite maps from abstract addresses to powersets of triples of
+abstract addresses, views, and powerset of abstract locations.  For abstract
+counting~\cite{abstract-gc-counting, revisit-recency} in static analysis, we
+define abstract counters $\abscountset$ that maps from abstract addresses to
+their abstract counts representing how many times each abstract address has been
+allocated; $\abszero$ denotes that it have never been allocated, $\absone$ once,
+and $\absmany$ more than or equals to twice.
+
+We define the semantics of view transition for the core language in
+Figure~\ref{fig:core-view-trans}.  For abstract memories, we use the notation
+$\absmem[L \mapstos \absval]$ to represent the update of multiple abstract
+locations in $L$ with the abstract value $\absval$.  It performs the strong
+update if the abstract address for an abstract location $(\absaddr, \_) \in L$
+is singleton: $\abscount(\absaddr) = \absone$.  Otherwise, it performs the weak
+update for the soundness.  Moreover, we define the increment function $\inc:
+\abscountset \times \absaddr \rightarrow \abscountset$ of the abstract counter
+defined as follows:
+\[
+  \inc(\abscount)(\absaddr_0) = \lambda \absaddr \in \absaddrset. \; \left\{
+    \begin{array}{ll}
+      \absone & \text{if} \; \absaddr = \absaddr_0 \wedge
+      \abscount(\absaddr_0) = \abszero\\
+      \absmany & \text{if} \; \absaddr = \absaddr_0 \wedge
+      \abscount(\absaddr_0) = \absone\\
+      \abscount(\absaddr) & \text{otherwise}
+    \end{array}
+  \right.
+\]

### 2020-09-28 paper/pldi21/detail.tex
Combined analysis of the core language

@@
     {
-      \st = (\lab, \mem, \ctxtstack, \addr)
+      \st = (\lab, \mem, \ctxt, \addr)
       \trans
-      (\labnext(\lab), \mem[\loc \mapsto \val], \ctxtstack, \addr)
+      (\labnext(\lab), \mem[\loc \mapsto \val], \ctxt, \addr)
     }
@@
     {
-      \st = (\lab, \mem, \ctxtstack, \addr)
+      \st = (\lab, \mem, \ctxt, \addr)
       \trans
-      (\labnext(\lab), \mem[\loc \mapsto \addr'], \ctxtstack, \addr)
+      (\labnext(\lab), \mem[\loc \mapsto \addr'], \ctxt, \addr)
     }
@@
     {
-      \st = (\lab, \mem, \ctxtstack, \addr)
+      \st = (\lab, \mem, \ctxt, \addr)
       \trans
-      (\lab_b, \mem[(\addr', x) \mapsto \val_a], (\addr, \labnext(\lab), \loc)
-      :: \ctxtstack, \addr')
+      (\lab_b, \mem[(\addr', x) \mapsto \val_a], \ctxt[\addr' \mapsto (\addr,
+      \labnext(\lab), \loc)], \addr')
     }
@@
       \exprrule{\st}{\expr}{\val}\\
+      \ctxt(\addr) = (\addr', \lab', \loc)
     }
     {
-      \st = (\lab, \mem, (\addr', \lab', \loc) :: \ctxtstack, \addr)
+      \st = (\lab, \mem, \ctxt, \addr)
       \trans
-      (\lab', \mem[\loc \mapsto \val], \ctxtstack, \addr')
+      (\lab', \mem[\loc \mapsto \val], \ctxt, \addr')
     }
@@
     {
-      \st = (\lab, \mem, \ctxtstack, \addr)
+      \st = (\lab, \mem, \ctxt, \addr)
       \trans
-      (\lab', \mem, \ctxtstack, \addr)
+      (\lab', \mem, \ctxt, \addr)
     }
@@
     {
-      \st = (\lab, \mem, \ctxtstack, \addr)
+      \st = (\lab, \mem, \ctxt, \addr)
       \trans
-      (\labnext(\lab), \mem, \ctxtstack, \addr)
+      (\labnext(\lab), \mem, \ctxt, \addr)
     }
@@
     {
-      \referrule{\st = (\lab, \mem, \ctxtstack, \addr)}{x}{(\addr, x)}\\
+      \referrule{\st = (\lab, \mem, \ctxt, \addr)}{x}{(\addr, x)}\\
     }
@@
     {
-      \referrule{\st = (\lab, \mem, \ctxtstack, \addr)}{\expr_0 [ \expr_1
+      \referrule{\st = (\lab, \mem, \ctxt, \addr)}{\expr_0 [ \expr_1
       ]}{(\addr_0, \val_1)}
@@
     {
-      \exprrule{\st = (\lab, \mem, \ctxtstack, \addr)}{\pval}{\pval}
+      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}{\pval}{\pval}
     }
@@
     {
-      \exprrule{\st = (\lab, \mem, \ctxtstack,
+      \exprrule{\st = (\lab, \mem, \ctxt,
       \addr)}{\fval{x}{\lab'}}{\fval{x}{\lab'}}
@@
     {
-      \exprrule{\st = (\lab, \mem, \ctxtstack, \addr)}{\refer}{\mem(\loc)}
+      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}{\refer}{\mem(\loc)}
     }
@@
     {
-      \exprrule{\st = (\lab, \mem, \ctxtstack, \addr)}
+      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}
       {\op(\expr_1, \cdots, \expr_n)}{\op(\val_1, \cdots, \val_n)}
@@
     \text{States} & \st &\in& \stset &=& \labset \times \memset \times
-    \ctxtset^* \times \eaddrset\\
+    \ctxtset \times \eaddrset\\
     \text{Memories} & \mem &\in& \memset &=& \locset \finmap \valset\\
-    \text{Contexts} & \ctxt &\in& \ctxtset &=& \eaddrset \times \labset \times
-    \locset\\
+    \text{Contexts} & \ctxt &\in& \ctxtset &=& \eaddrset \finmap (\eaddrset
+    \times \labset \times \locset)\\
     \text{Locations} & \loc &\in& \locset &=& (\eaddrset \times \varset) \uplus
@@
 
-States $\stset$ consist of labels $\labset$, memories $\memset$, context stacks
-$\ctxtset^*$, and environment addresses $\eaddrset$.  A memory $\mem \in
-\memset$ is a finite mapping from locations to values.  Context stacks is
-sequences of contexts $\ctxtset$ and a context $\ctxt \in \ctxtset$ is a tuple
-of an environment address, a return label, and a left-hand side location.  A
-location $\loc \in \locset$ is a variable or an object property; a variable
-location consists of an environment address and its name, and an object property
-location consists of an object address and a string value.  A value $\val \in
-\valset$ is a primitive, an address, or a function value.  An address $\addr \in
-\addrset$ is an environment address or an object address.  A function value
-$\fval{x}{\lab} \in \fvalset$ consists of a parameter and a body label.  In the
-core language, the closed scoping is used for functions for brevity thus only
-parameters and local variables are accessible in the function body.
+States $\stset$ consist of labels $\labset$, memories $\memset$, contexts
+$\ctxtset$, and environment addresses $\eaddrset$.  A memory $\mem \in \memset$
+is a finite mapping from locations to values.  A context $\ctxt \in \ctxtset$ is
+a finite mapping from environment addresses to tuple of environment addresses,
+return labels, and left-hand side locations.  A location $\loc \in \locset$ is a
+variable or an object property; a variable location consists of an environment
+address and its name, and an object property location consists of an object
+address and a string value.  A value $\val \in \valset$ is a primitive, an
+address, or a function value.  An address $\addr \in \addrset$ is an environment
+address or an object address.  A function value $\fval{x}{\lab} \in \fvalset$
+consists of a parameter and a body label.  In the core language, the closed
+scoping is used for functions for brevity thus only parameters and local
+variables are accessible in the function body.
 
@@
 update for the soundness.  Moreover, we define the increment function $\inc:
-\abscountset \times \absaddr \rightarrow \abscountset$ of the abstract counter
+\abscountset \times \absaddrset \rightarrow \abscountset$ of the abstract counter
 defined as follows:
@@
 \]
+
+\subsection{Combined Analysis}
+
+We define the symbolic states with the extended concrete values and the abstract
+counters for addresses as follows:
+\[
+  \begin{array}{r@{~}c@{~}l}
+    \symbstset &=& \labset \times \memset \times \ctxtset \times \eaddrset
+    \times \abscountset\\
+    \ctxtset &=& \addrset \finmap ((\addrset \times \labset \times \locset)
+    \uplus \symbset)\\
+    \valset &=& \pvalset \uplus \oaddrset \uplus \fvalset \uplus \symbset\\
+    \abscountset &=& \addrset \rightarrow \{ \abszero, \absone, \absmany \}\\
+  \end{array}
+\]
+We define the converter $\asconverter: \absdom \rightarrow \symbstset$ from
+abstract states to corresponding symbolic states as follows:
+\[
+  \asconverter((\lab, (\absmem, \absctxt, \absaddr, \abscount))) = (\lab,
+  \asconverter^\memset(\absmem), \asconverter^\ctxtset(\absctxt),
+  \asconverter^\addrset(\absaddr), \abscount)\\
+\]
+The converter for memories $\asconverter^\memset$ is defined with the converter
+for values $\asconverter^\valset$ where:
+\[
+  \asconverter^\valset(\absval) = \left\{
+    \begin{array}{ll}
+      \val & \text{if} \; \absval = \{ \val \}\\
+      \absval & \text{otherwise}\\
+    \end{array}
+  \right.
+\]
+In a similar way, the converter for contexts $\asconverter^\ctxtset$ is defined
+as follows:
+\[
+  \asconverter^\ctxtset(\absctxt)(\absaddr) = \left\{
+    \begin{array}{ll}
+      (\absaddr, \lab, \loc) & \text{if} \; \absctxt(\absaddr) = \{ (\absaddr,
+      \lab, \{ \loc \}) \}\\
+      \absctxt(\absaddr) & \text{otherwise}\\
+    \end{array}
+  \right.
+\]
+The opposite converter $\saconverter: \symbstset \rightarrow \absdom$ from
+symbolic states to abstract states is defined as the inverse function of
+$\asconverter$: $\saconverter = \asconverter^{-1}$.
+The symbolic transition relation $\symbtrans$ is an extension of the original
+concrete transition relation $\trans$.  When the exact values of symbolic values
+are required, symbolic states have the symbolic transition relation with the
+exception state $\excst$.  For example, we add the following rule for $\kwret$
+statements:
+\begin{mathpar}
+  \inferrule
+  {
+    \prog(\lab) = \kwret \; \expr\\
+    \exprrule{\st}{\expr}{\val}\\
+    \ctxt(\addr) \in \symbset
+  }
+  {
+    \st = (\lab, \mem, \ctxt, \addr)
+    \trans \excst
+  }
+\end{mathpar}
+We extend each rule of concrete semantics to support such behaviors of symbolic
+values.

### 2020-10-12 paper/pldi21/detail.tex
Applied review

@@
 $\istset = \{ (\ilab, \varnothing, \epsilon, \tladdr) \}$ where $\ilab$ denotes
-the initial label, $\epsilon$ empty list, and $\tladdr$ the top-level
-environment address.  The function $\labnext$ returns the next lable of the
+the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level
+environment address.  The function $\labnext$ returns the next lable of a
 given lable in the current program $\prog$.
@@
       \eabsctxt = \absctxt[\eabsaddr \mapsto \absctxt(\eabsaddr) \cup \{
-      (\absaddr, \lab, L) \} ]
+      (\absaddr, \labnext(\lab), L) \} ]
     }
@@
     {
-      \referabssem{\expr_0 [ \expr_1 ]} = A \times S
+      \referabssem{\expr_0 [ \expr_1 ]}(\abselem) = A \times S
     }
@@
 discriminates states using their labels: $\forall \lab \in \labset. \;
-\fsviewmap(\lab) = \{ \st \in \stset \mid \st = (\lab, \_, \_, \_) \}$ Thus, the
+\fsviewmap(\lab) = \{ \st \in \stset \mid \st = (\lab, \_, \_, \_) \}$. Thus, the
 sensitive abstract domain is defined as $\sabsdom = \labset \rightarrow
@@
 their abstract counts representing how many times each abstract address has been
-allocated; $\abszero$ denotes that it have never been allocated, $\absone$ once,
+allocated; $\abszero$ denotes that it has never been allocated, $\absone$ once,
 and $\absmany$ more than or equals to twice.
@@
 
-\subsection{Combined Analysis}
+\subsection{Lazy Concrete Interpretation}
 
@@
     \times \abscountset\\
-    \ctxtset &=& \addrset \finmap ((\addrset \times \labset \times \locset)
+    \ctxtset &=& \eaddrset \finmap ((\eaddrset \times \labset \times \locset)
     \uplus \symbset)\\
     \valset &=& \pvalset \uplus \oaddrset \uplus \fvalset \uplus \symbset\\
-    \abscountset &=& \addrset \rightarrow \{ \abszero, \absone, \absmany \}\\
+    \abscountset &=& \oaddrset \rightarrow \{ \abszero, \absone, \absmany \}\\
   \end{array}
 \]
-We define the converter $\asconverter: \absdom \rightarrow \symbstset$ from
-abstract states to corresponding symbolic states as follows:
+We define the converter $\asconverter: (\viewset \times \absdom) \rightarrow
+\symbstset$ from abstract states to corresponding symbolic states as follows:
 \[
@@
 \]
-The opposite converter $\saconverter: \symbstset \rightarrow \absdom$ from
-symbolic states to abstract states is defined as the inverse function of
-$\asconverter$: $\saconverter = \asconverter^{-1}$.
+The opposite converter $\saconverter: \symbstset \rightarrow (\viewset \times
+\absdom)$ from symbolic states to abstract states is defined as the inverse
+function of $\asconverter$: $\saconverter = \asconverter^{-1}$.
 The symbolic transition relation $\symbtrans$ is an extension of the original

### 2020-10-12 paper/pldi21/formal.tex
Abstract semantics of core language
Fixed minor typo in formalization
Applied review

@@
 The abstract interpretation~\cite{abs-interp-1977, abs-interp-1992}
-over-approximate the transfer $\transfer$ to the \textit{abstract transfer
+over-approximates the transfer $\transfer$ to the \textit{abstract transfer
 function} $\abstransfer: \absdom \rightarrow \absdom$ to get the
@@
 a Galois connection between the concrete domain $\dom$ and an abstract domain
-$\absdom$ with a \textit{concretization function} $\gamma$ and a
+$\absdom$ with a \textit{concretization function} $\gamma$ and an
 \textit{abstraction function} $\alpha$.  The initial abstract state $\iabselem
@@
 
-% One of the most widely-used sensitivity techniques is \textit{flow sensitivity}
-% using a flow sensitive view abstraction $\fsviewmap: \labset \rightarrow \dom$.
-% It discriminates states using their labels as follows:
-% \[
-%   \forall \lab \in \labset. \; \fsviewmap(\lab) = \{ \st \in \stset \mid \st =
-%   (\lab, \_) \}
-% \]
-
 \subsection{Lazy Concrete Interpretation}
@@
 states. First, we extends the concrete states $\stset$ to \textit{symbolic
-states} with symbolic values $\symbset$ that denote abstract values cannot be
+states} with symbolic values $\symbset$ that denote abstract values that cannot be
 concretized to singleton values. A symbolic transition relation $\symbtrans
-\subseteq \symbstset \times (\symbstset \uplus \{ \excst \})$ is exactly same
+\subseteq \symbstset \times (\symbstset \uplus \{ \excst \})$ is exactly the same
 with the original transition relation $\trans$ except when the relation requires
@@
 
-To freely convert a pair of view and an abstract state to the corresponding
+To freely convert a pair of view and an abstract state to its corresponding
 symbolic state and vice versa, we define two domain converters $\symbstset
@@
   \checker(\symbst) \Rightarrow \symbst \symbtrans^k \excst \wedge
-  1 \leq k \leq N
+  1 < k \leq N
 \]
-where $N$ is the pre-defined maximum length of the lazy concrete interpretation.
+where $N$ is a pre-defined maximum length of the lazy concrete interpretation.
 The combined analysis just performs one-step symbolic transition for each

### 2020-10-23 paper/pldi21/conclusion.tex
Added labels for each section

@@
-\section{CCS Concepts and User-Defined Keywords}
+\section{Conclusion}\label{sec:conclusion}
 
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
+\todo

### 2020-10-23 paper/pldi21/motivation.tex
Added labels for each section

\section{Motivation}\label{sec:motivation}

\todo

### 2020-10-26 paper/pldi21/motivation.tex
Motivating example - Figure 1

@@
 
+\begin{figure}[t]
+  \centering
+  \begin{subfigure}[t]{0.5\textwidth}
+    \begin{lstlisting}[style=myJSstyle]
+function concat() {
+  var length = arguments.length;
+  if (!length) return [];
+  var args = Array(length - 1),
+      array = arguments[0],
+      index = length;
+  while (index--)
+    args[index-1] = arguments[index];
+  return arrayPush(isArray(array) ?
+    copyArray(array) :
+    [array], baseFlatten(args, 1));
+}
+    \end{lstlisting}
+    \label{fig:example-concat}
+    \vspace*{-1em}
+    \caption{Lodash's \code{concat} function.}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \begin{lstlisting}[style=myJSstyle,firstnumber=13]
+function getData(e) {
+  var option = ... // option of server connection
+  post(option).then(function(e) {
+    if (e.total_records && e.total_records > 0) {
+      // non-deterministic arguments of `concat`
+      this.pastEvents =
+        _.concat(this.pastEvents, e.events);
+      this.total = e.total_records;
+    } else this.noPastData = !0
+  })
+}
+    \end{lstlisting}
+    \label{fig:example-concat}
+    \vspace*{-1em}
+    \caption{The \code{getData} function to load more events from the server.}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \begin{lstlisting}[style=myJSstyle,firstnumber=24]
+function changeCountry(G) {
+  ...
+  if (G.selectedVal === "US" && state) {
+    // deterministic arguments of `concat`
+    state.items = _.concat([["Other", "Other"]],
+      WebinarBase.questions.state.items);
+    state.selectedVal = _.head(_.head(C.items));
+  }
+}
+    \end{lstlisting}
+    \label{fig:example-concat}
+    \vspace*{-1em}
+    \caption{The \code{changeCountry} function to update state information.}
+  \end{subfigure}
+  \label{fig:example}
+  \vspace*{-1em}
+  \caption{Motivating Example: Excerpts from Lodash library and JavaScript codes
+  in \code{zoom.us} site.}
+\end{figure}
+
+\begin{lstlisting}[style=myJSstyle]
+WebinarBase.questions = { ...
+  state: { ...
+    items: [["AL","Alabama"], ["AK","Alaska"], ...]
+  }
+};
+\end{lstlisting}
+
 \todo

### 2020-10-27 paper/pldi21/intro.tex
Added first draft of introduction.

@@
-\section{Introduction}
-ACM's consolidated article template~\cite{Lamport:LaTeX}, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
+\section{Introduction}\label{sec:intro}
+JavaScript is the de facto programming language in web development and,
+moreover, blossoming beyond the web.
+JavaScript has dominated client-side scripting of the web for over a decade.
+JavaScript takes the unique position as the universal language operating in both
+the browser and on a server in the form of Node.js.
+The client-side frameworks such as React, Vue.js, and Angular have accelerated
+the universal use of JavaScript.
+The cross-platform frameworks like React Native and Electron have spread
+JavaScript to the new domains of mobile and desktop beyond the web.
+This is only possible thanks to JavaScript's easy operation in development and
+deployment with scripting language characteristics such as dynamic and
+interpreted language features~\cite{weakly}.
 
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
+However, such features make it difficult to support developer tools that require
+statically reasoning about semantics of JavaScript programs such as call graph
+construction, type checking, optimization, and bug detection.
+For example, the combination of the JavaScript features: dynamically-computed
+property name, prototype chain, and first-class function, makes call graph
+construction challenging.
+Even a minor precision loss at property name can cause reading all methods in
+the object and its prototype chain, including hundreds of built-ins, that
+results in useless analysis results.
+In static analyses of Java, the benchmark results clearly show the trade-off
+between precision and performance~\cite{}, a low degree of context sensitivity
+shows a high performance but low precision.
+In the case of JavaScript, the relationship between precision and performance is
+more complex due to the spurious callee explosion.
+Low precision tends to cause the large number of spurious callees, which
+significantly degrades the performance~\cite{}.
 
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
+For this reason, recent studies on JavaScript static analysis have proposed
+techniques to improve analysis precision against this challenge.
+Madsen et al.~\cite{} presented sophisticated abstract domains for strings.
+Park and Ryu proposed high degrees of context sensitivity for loop~\cite{}.
+Relations between object properties aid to analysis precision~\cite{}.
+Demand-driven value refinement~\cite{} and lightweight variants of trace
+partitioning~\cite{} showed promising results.
+
+Unfortunately, it does not mean that high precision leads to "good" performance
+but "better" than the "bad" performance.
+Computation costs of high degree of sensitivity remains as it is but the
+snowball of low precision is much larger than that.
+We alleviate computation costs of high degrees of sensitivity through a combined
+approach of static and dynamic analyses.
+
+Existing combined approaches derive three kinds of benefits of dynamic analysis.
+Dynamic analysis can run on a highly-optimized JavaScript engine like V8, so
+it boosts up analysis performance.
+There is no precision loss coming from limitations of abstract domains and
+sensitivities if the dynamic analysis terminates.
+Dynamic analysis can pass by opaque codes that require extra handling for static
+analysis.
+
+However, the existing combined analyses are limited to maximize benefits of
+dynamic analysis.
+Staged analyses first collect particular information by dynamic analysis and
+apply static analysis augmented with dynamic information.
+Dynamic information can be argument length, object creation site, entire heap at
+specific program points.
+Once static analysis starts, it does not utilize more dynamic information.
+The other design of combined analysis is divide whole program into two parts.
+One for the dynamic analysis (framework code) and the other for the static analysis (user code).
+The policy to divde a program is predefined and syntactic.
+Each analysis always take on each part of code.
+
+We present a much more fine-grained method to combine two analyses to maximize
+benefits.
+Our approach extend dynamic analysis to work with the presence of abstract
+values, named lazy concrete execution.
+The analysis goes on the dynamic side as much as possible until non-determinism
+is actually introduced by abstract values or analysis sensitivity that dynamic
+analysis cannot handle.
+When the lazy concrete exeuction meets non-determinism, the analysis switches to
+the traditional static analysis and its abstract semantics to handle that.
+As soon as analysis sensitivity is deterministic, it switches to lazy concrete
+execution again.
+
+\begin{figure}[h]
+  \centering
+  \label{intro:fig:performance}
+  \includegraphics[width=\linewidth]{benchmark_performance}
+  \caption{The performances of static and dynamic analyses on deterministic benchmarks}
+  \
+  \Description{}
+\end{figure}
+
+Our key observation is that high degrees of sensitivity increase the use of
+concrete semantics during analysis and utilizing an optimzied engine like V8 is
+the fast way to apply concrete semantics.
+As shown in ~\ref{intro:fig:performance}.
+Our design is not limited to any predefined features including program point and
+does not harmful to the soundness of the original static analysis.
+
+%We have demonstrated how dynamic shortcut maximize benefits of dynamic analysis.
+%We have implemetned our method by extending the existing JavaScript static
+%analyzer.
+%We found that using dynamic shortcut significantly increased performance for
+%benchmark programs enhanced with abstracted input.
+
+In summary, the contributions of this paper are as follows.
+\begin{itemize}
+\item We formally describe the high-level idea of adding dynamic shortcuts, a
+  technique for combining static and dynamic analyses into fine-grained level on
+  the general abstract interpretation framework (Section 3).
+  We explain JavaScript related details formalized with core language of JavaScript as well (Section 4).
+\item We actualize our method by extending the existing JavaScript static analyzer SAFE 2.0.
+  We explain key techniques to synchronize two analyses (Section 5).
+\item We empirically evaluate our technique using the implementation (Section 6).
+  We find that using dynamic shortcut significantly increased performance for
+  benchmark programs enhanced with abstracted input that existing combined
+  analysis designs cannot handle.
+\end{itemize}
+
+%There are almost 200 million active websites out of over 1.8 billion sites on the entire web.
+%https://www.internetlivestats.com/total-number-of-websites/
+%JavaScript is used as client-side programming language by 96.9\% of all the websites.
+%https://w3techs.com/technologies/history_overview/client_side_language/all/y

### 2020-10-27 paper/pldi21/abstract.tex
Adding citations on introduction.

@@
 Such boundaries are intuitive but limit chances to optimize transitions between two analyses.
-We formally present the alloyed analysis, a more flexible compound of static and dynamic analyses.
+We formally present the dynamic shortcut, a more flexible compound of static and dynamic analyses.
 We implement a proof of concept bug detector by extending the existing static analyzer supporting a subset of ECMAScript 5.1.
-Our experimental results show that the alloyed analysis indeed speeds up the detection and reports bugs more precisely.
+Our experimental results show that the combined analysis indeed speeds up and produces more precise results.
 \end{abstract}

### 2020-10-27 paper/pldi21/intro.tex
Adding citations on introduction.

@@
 deployment with scripting language characteristics such as dynamic and
-interpreted language features~\cite{weakly}.
+interpreted language features~\cite{weaklySPE}.
 
@@
 In static analyses of Java, the benchmark results clearly show the trade-off
-between precision and performance~\cite{}, a low degree of context sensitivity
-shows a high performance but low precision.
+between precision and performance~\cite{data-driven} \todo, a low degree of
+context sensitivity shows a high performance but low precision.
 In the case of JavaScript, the relationship between precision and performance is
@@
 Low precision tends to cause the large number of spurious callees, which
-significantly degrades the performance~\cite{}.
+significantly degrades the performance~\cite{correlation, determinacy-jQuery, weaklySPE, value-refinement}.
 
-For this reason, recent studies on JavaScript static analysis have proposed
-techniques to improve analysis precision against this challenge.
-Madsen et al.~\cite{} presented sophisticated abstract domains for strings.
-Park and Ryu proposed high degrees of context sensitivity for loop~\cite{}.
-Relations between object properties aid to analysis precision~\cite{}.
-Demand-driven value refinement~\cite{} and lightweight variants of trace
-partitioning~\cite{} showed promising results.
+For this reason, recent studies on JavaScript static analysis have developed
+to improve analysis precision against this challenge.
+Madsen et al.~\cite{string, regex, combining-string} presented sophisticated abstract domains for strings.
+Park et al. proposed high degrees of context sensitivity for loop~\cite{lsaECOOP, lsaSPE}.
+Relations between object properties have aided to analysis precision~\cite{correlation, weaklyAPLAS, weaklySPE}.
+The idea stretches from property name to non-local variables and types for predicate functions~\cite{value-partitioning}.
+The on-demand backward analyses~\cite{value-refinement} refines imprecise values for property writes.
 
@@
 Existing combined approaches derive three kinds of benefits of dynamic analysis.
-Dynamic analysis can run on a highly-optimized JavaScript engine like V8, so
-it boosts up analysis performance.
+Dynamic analyses~\cite{jalangi, jalangi2, dlint} can run on a highly-optimized
+JavaScript engine like V8, so it boosts up analysis performance.
 There is no precision loss coming from limitations of abstract domains and
-sensitivities if the dynamic analysis terminates.
+sensitivities if the dynamic analysis terminates~\cite{concerto}.
 Dynamic analysis can pass by opaque codes that require extra handling for static
-analysis.
+analysis~\cite{battles, sra}.
 
@@
 Staged analyses first collect particular information by dynamic analysis and
-apply static analysis augmented with dynamic information.
-Dynamic information can be argument length, object creation site, entire heap at
-specific program points.
+apply static analysis augmented with dynamic information~\cite{staged, blendedJava, eha} \todo.
+Dynamic information can be argument length, object creation site~\cite{blended}, entire heap at
+specific program points~\cite{battles}.
 Once static analysis starts, it does not utilize more dynamic information.
-The other design of combined analysis is divide whole program into two parts.
+The other design of combined analysis is divide whole program into two parts~\cite{concerto}.
 One for the dynamic analysis (framework code) and the other for the static analysis (user code).

### 2020-10-27 paper/pldi21/intro.tex
Added citations in introduction.

@@
 In static analyses of Java, the benchmark results clearly show the trade-off
-between precision and performance~\cite{data-driven} \todo, a low degree of
+between precision and performance~\cite{introspective, data-driven}, a low degree of
 context sensitivity shows a high performance but low precision.
@@
 Madsen et al.~\cite{string, regex, combining-string} presented sophisticated abstract domains for strings.
-Park et al. proposed high degrees of context sensitivity for loop~\cite{lsaECOOP, lsaSPE}.
+Park et al. proposed higher degrees of context sensitivity for loops~\cite{lsaECOOP, lsaSPE}.
 Relations between object properties have aided to analysis precision~\cite{correlation, weaklyAPLAS, weaklySPE}.
@@
 Existing combined approaches derive three kinds of benefits of dynamic analysis.
-Dynamic analyses~\cite{jalangi, jalangi2, dlint} can run on a highly-optimized
-JavaScript engine like V8, so it boosts up analysis performance.
+Dynamic analyses~\cite{jalangi, dlint} can run on a highly-optimized
+JavaScript engine like V8, so it can boost up analysis performance.
 There is no precision loss coming from limitations of abstract domains and
-sensitivities if the dynamic analysis terminates~\cite{concerto}.
+sensitivities if the dynamic analysis terminates~\cite{determinacy, concerto}.
 Dynamic analysis can pass by opaque codes that require extra handling for static
@@
 Staged analyses first collect particular information by dynamic analysis and
-apply static analysis augmented with dynamic information~\cite{staged, blendedJava, eha} \todo.
-Dynamic information can be argument length, object creation site~\cite{blended}, entire heap at
-specific program points~\cite{battles}.
+apply static analysis augmented with dynamic information~\cite{blendedJava, eha}.
+Dynamic information can be determinacy facts~\cite{determinacy}, call graphs~\cite{tunable}
+object creation site~\cite{blendedJS}, or entire heap at specific program points~\cite{battles}.
 Once static analysis starts, it does not utilize more dynamic information.
 The other design of combined analysis is divide whole program into two parts~\cite{concerto}.
-One for the dynamic analysis (framework code) and the other for the static analysis (user code).
-The policy to divde a program is predefined and syntactic.
-Each analysis always take on each part of code.
+One (framework code) for the dynamic analysis  and the other (user code) for the
+static analysis.
+The policy to divde a program is predefined and syntactic and never changes
+during analysis.
 
-We present a much more fine-grained method to combine two analyses to maximize
-benefits.
+We present a more flexible and fine-grained method to combine two analyses to
+maximize benefits.
 Our approach extend dynamic analysis to work with the presence of abstract
 values, named lazy concrete execution.
-The analysis goes on the dynamic side as much as possible until non-determinism
-is actually introduced by abstract values or analysis sensitivity that dynamic
-analysis cannot handle.
+The analysis goes on a concrete engine side as much as possible until
+non-determinism is actually introduced by abstract values or analysis
+sensitivity that the lazy concrete execution cannot handle.
 When the lazy concrete exeuction meets non-determinism, the analysis switches to
-the traditional static analysis and its abstract semantics to handle that.
-As soon as analysis sensitivity is deterministic, it switches to lazy concrete
-execution again.
+the traditional static analysis and uses its abstract semantics to handle that.
+As soon as analysis sensitivity is deterministic, it switches to the lazy
+concrete execution again.
 
-\begin{figure}[h]
+\begin{figure}
   \centering
-  \label{intro:fig:performance}
   \includegraphics[width=\linewidth]{benchmark_performance}
   \caption{The performances of static and dynamic analyses on deterministic benchmarks}
-  \
-  \Description{}
+  \label{fig:performance}
 \end{figure}
@@
 the fast way to apply concrete semantics.
-As shown in ~\ref{intro:fig:performance}.
+As shown in Figure~\ref{fig:performance}.
 Our design is not limited to any predefined features including program point and

### 2020-10-28 paper/pldi21/intro.tex
Revised the introduction.

@@
 The cross-platform frameworks like React Native and Electron have spread
-JavaScript to the new domains of mobile and desktop beyond the web.
+JavaScript to the new domains like mobile and desktop beyond the web.
 This is only possible thanks to JavaScript's easy operation in development and
@@
 property name, prototype chain, and first-class function, makes call graph
-construction challenging.
+construction extremely challenging.
 Even a minor precision loss at property name can cause reading all methods in
@@
 In static analyses of Java, the benchmark results clearly show the trade-off
-between precision and performance~\cite{introspective, data-driven}, a low degree of
-context sensitivity shows a high performance but low precision.
+between precision and performance~\cite{introspective, data-driven}, a low
+degree of context sensitivity shows a high performance but low precision.
 In the case of JavaScript, the relationship between precision and performance is
 more complex due to the spurious callee explosion.
-Low precision tends to cause the large number of spurious callees, which
+Low precision tends to cause the large number of spurious callees that
 significantly degrades the performance~\cite{correlation, determinacy-jQuery, weaklySPE, value-refinement}.
@@
 to improve analysis precision against this challenge.
-Madsen et al.~\cite{string, regex, combining-string} presented sophisticated abstract domains for strings.
+Madsen et al.~\cite{string, regex, combining-string} presented sophisticated
+abstract domains for strings.
 Park et al. proposed higher degrees of context sensitivity for loops~\cite{lsaECOOP, lsaSPE}.
 Relations between object properties have aided to analysis precision~\cite{correlation, weaklyAPLAS, weaklySPE}.
-The idea stretches from property name to non-local variables and types for predicate functions~\cite{value-partitioning}.
-The on-demand backward analyses~\cite{value-refinement} refines imprecise values for property writes.
+The idea stretches from property name to non-local variables and types for
+predicate functions~\cite{value-partitioning}.
+The on-demand backward analyses~\cite{value-refinement} refines imprecise values
+for property writes.
 
-Unfortunately, it does not mean that high precision leads to "good" performance
-but "better" than the "bad" performance.
-Computation costs of high degree of sensitivity remains as it is but the
-snowball of low precision is much larger than that.
-We alleviate computation costs of high degrees of sensitivity through a combined
-approach of static and dynamic analyses.
+Unfortunately, computation cost of high degrees of sensitivity remains as it is
+but the snowball cost of low precision is much larger than that.
+So it is difficult to scale up JavaScript static analysis even though we give up
+analysis precision.
+We address the scalability issue of high degrees of sensitivity through a
+combined approach of static and dynamic analyses.
 
-Existing combined approaches derive three kinds of benefits of dynamic analysis.
+Existing combined approaches derive three kinds of benefits by dynamic analysis.
 Dynamic analyses~\cite{jalangi, dlint} can run on a highly-optimized
@@
 sensitivities if the dynamic analysis terminates~\cite{determinacy, concerto}.
+Note that in this case of combined analyses does not sacrifice soundness.
 Dynamic analysis can pass by opaque codes that require extra handling for static
@@
 Staged analyses first collect particular information by dynamic analysis and
-apply static analysis augmented with dynamic information~\cite{blendedJava, eha}.
+augment static analysis with the information~\cite{blendedJava, eha}.
 Dynamic information can be determinacy facts~\cite{determinacy}, call graphs~\cite{tunable}
-object creation site~\cite{blendedJS}, or entire heap at specific program points~\cite{battles}.
-Once static analysis starts, it does not utilize more dynamic information.
-The other design of combined analysis is divide whole program into two parts~\cite{concerto}.
+object creations~\cite{blendedJS}, or entire heaps at specific program points~\cite{battles}.
+Once static analysis starts, staged analyses does not utilize more dynamic information.
+The other design of combined analysis divides a whole program into two parts~\cite{concerto}.
 One (framework code) for the dynamic analysis  and the other (user code) for the
 static analysis.
-The policy to divde a program is predefined and syntactic and never changes
+The policy to divde a program is predefined and syntactic, so never changes
 during analysis.
@@
 We present a more flexible and fine-grained method to combine two analyses to
-maximize benefits.
-Our approach extend dynamic analysis to work with the presence of abstract
-values, named lazy concrete execution.
-The analysis goes on a concrete engine side as much as possible until
-non-determinism is actually introduced by abstract values or analysis
-sensitivity that the lazy concrete execution cannot handle.
-When the lazy concrete exeuction meets non-determinism, the analysis switches to
+maximize the benefits.
+Our idea enables abstract interpretation to use the dynamic analysis on demand
+to speed up the analysis while preserving soundness, so we call that adding
+dynamic shortcuts.
+We extend a dynamic analysis to work as long as possible despite of the presence
+of abstract values by laziness.
+The analysis goes on the concrete engine as much as possible until it meets
+operations with non-deterministic values by abstract values or analysis
+sensitivity that the concrete engine cannot handle.
+When the dynamic shortcut meets non-determinism, the analysis switches to
 the traditional static analysis and uses its abstract semantics to handle that.
-As soon as analysis sensitivity is deterministic, it switches to the lazy
-concrete execution again.
+As soon as analysis sensitivity is deterministic, it continues to take the
+dynamic shortcut again.
 
@@
 the fast way to apply concrete semantics.
-As shown in Figure~\ref{fig:performance}.
+\inred{As shown in Figure~\ref{fig:performance}. dynamic analyses on V8 engine show
+25x fatster on average than the fastest static analyzer.}
 Our design is not limited to any predefined features including program point and
@@
   technique for combining static and dynamic analyses into fine-grained level on
-  the general abstract interpretation framework (Section 3).
-  We explain JavaScript related details formalized with core language of JavaScript as well (Section 4).
+  the general abstract interpretation framework.
 \item We actualize our method by extending the existing JavaScript static analyzer SAFE 2.0.
-  We explain key techniques to synchronize two analyses (Section 5).
-\item We empirically evaluate our technique using the implementation (Section 6).
+\item We empirically evaluate our technique using the implementation.
   We find that using dynamic shortcut significantly increased performance for
@@
 \end{itemize}
+The remainder of this paper is organized as follows.
+In Section~\ref{sec:motivation}, we explain more details about limitations of
+existing techniques and our solution with the real-world JavaScript programs.
+Section~\ref{sec:formal} formalizes adding dynamic shortucts on abstract
+interpretation.
+We explain JavaScript related features formalized with core language of
+JavaScript in Section~\ref{sec:javascript}.
+We explain key implementation techniques like the synchronizetion of two analyses.
+We evaluate our idea using real-world benchmarks in Section~\ref{sec:eval}.
+We organize related work in Section~\ref{sec:related}, and we conclude in Section~\ref{sec:conclusion}.
 

### 2020-10-28 paper/pldi21/motivation.tex
Motivation

--- 2020-10-23 paper/pldi21/motivation.tex
@@
 
-\todo
+\begin{figure}[t]
+  \centering
+  \begin{subfigure}[t]{0.5\textwidth}
+    \begin{lstlisting}[style=myJSstyle]
+function concat() {
+  var length = arguments.length;
+  if (!length) return [];
+  var args = Array(length - 1),
+      array = arguments[0],
+      index = length;
+  while (index--)
+    args[index-1] = arguments[index];
+  return arrayPush(
+    isArray(array) ? copyArray(array) : [array],
+    baseFlatten(args, 1));
+}
+    \end{lstlisting}
+    \vspace*{-1em}
+    \caption{Lodash's \jscode{concat} function.}
+    \label{fig:concat}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \begin{lstlisting}[style=myJSstyle,firstnumber=13]
+function changeCountry(G) {
+  ...
+  if (G.selectedVal === "US" && state) {
+    // deterministic arguments of `concat`
+    state.items = _.concat([["Other", "Other"]],
+      WebinarBase.questions.state.items);
+    state.selectedVal = _.head(_.head(C.items));
+  }
+}
+    \end{lstlisting}
+    \vspace*{-1em}
+    \caption{Load the list of states of the United States.}
+    \label{fig:changeCountry}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.5\textwidth}
+    \begin{lstlisting}[style=myJSstyle,firstnumber=22]
+function getData(e) {
+  var option = ... // option of server connection
+  post(option).then(function(e) {
+    if (e.total_records && e.total_records > 0) {
+      // non-deterministic arguments of `concat`
+      this.pastEvents =
+        _.concat(this.pastEvents, e.events);
+      this.total = e.total_records;
+    } else this.noPastData = !0
+  })
+}
+    \end{lstlisting}
+    \vspace*{-1em}
+    \caption{Load more Zoom events from the server.}
+    \label{fig:getData}
+  \end{subfigure}
+  \vspace*{-1em}
+  \caption{Motivating Example: Excerpts from Lodash library and JavaScript codes
+  \label{fig:example}
+  in \code{zoom.us} site.}
+\end{figure}
+
+In this section, we will explain the motivation of the combined analysis for
+JavaScript programs with a simple motivating example described in
+Figure~\ref{fig:example}.  It shows how to utilize dynamic analysis during
+static analysis using lazy concrete execution to increase performance and
+precision of static analysis.
+
+For a motivating example, we excerpt the \jscode{concat} function in
+Figure~\ref{fig:concat} from Lodash library~\cite{lodash} (v4.17.20), which is
+the most popular npm package~\footnote{https://www.npmjs.com/browse/depended}
+and \inred{124,562} npm packages have dependency with it.  The \jscode{concat}
+function creates a new array concatenating given arrays or values.  It first
+checks the length of arguments in line 2-3. Then, it stores the first argument
+to \jscode{array} in line 5 and copies the remaining arguments to \jscode{args} in
+line 7-8.  Finally, it creates a new array by copying the given array via
+\jscode{copyArray} or initializing with a single value in line 10, and pushes
+each element of \jscode{args} after flattening it via \jscode{baseFlatten} in
+line 11.
+
+For applications of Lodash, we excerpt two functions \jscode{changeCountry} in
+Figure~\ref{fig:changeCountry} and \jscode{getData} in Figure~\ref{fig:getData}
+from the \code{zoom.us}~\cite{zoom} site.  The website \code{zoom.us} is
+homepage of Zoom, which is a videotelephony software program developed by Zooom
+Video Communications and it is ranked as \inred{16th} popular web site accroding
+to Alexa~\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.
+
+When the given arguments of a function invokation are concrete values, we can
+perform dynamic analysis instead of static analysis. For example, The
+\jscode{changeCountry} function is invoked when a country different with the
+current one is selected in registration of Zoom meetings.  When the ``United
+States of America'' (USA) is selected, it calls the \jscode{concat} function
+with two pre-defined concrete values as arguments to load USA state information
+in line 17-18.  The first argument is an array literal \jscode{[["Other",
+"Other"]]} and the second one is an array of pairs of abbreviations and names of
+USA states defined as follows:
+\begin{lstlisting}[style=myJSstyle,numbers=none]
+WebinarBase.questions.state.items =
+  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
+\end{lstlisting}
+Moreover, \jscode{this} value is also a concrete value, the Lodash top-level
+object \jscode{\_}.  Thus, we could perform dynamic analysis by invoking the
+\jscode{concat} funciton with \jscode{\_} as \jscode{this} value and above two
+concrete values as arguments.  It increases performance of static analysis by
+skipping the analysis of function call in line 17-18 and utilizing the result of
+dynamic analysis.
+
+Dynamic analysis is still applicable using lazy concrete execution even if the
+arguments are not concrete values.  The \jscode{getData} function is another
+part to use \jscode{concat} function but we can only partially apply dynamic
+analysis in this case.  It is invoked when loading more Zoom events in
+``Webinars \& Events'' page.  At the first time, initial eight events are stored
+in \jscode{this.pastEvents}.  For each click of the ``Load More'' button, the
+\jscode{getData} sends a POST request to the server and receives additional
+event information \jscode{e} in line 24.  Then, eight events in
+\jscode{e.events} are appended to \jscode{this.pastEvents} using the
+\jscode{concat} function in line 27-28.  In this case, arguments are not
+deterministic but dependent on the given data from the server.  However, we know
+that the number of arguments are still deterministically defined as \jscode{2}
+and they are array objects.  Thus, we just invoke the funciton \jscode{concat}
+with \jscode{\_} as \jscode{this} value and two abstract arrays as arguments for
+dynamic analysis.  Then, dynamic analysis is successfully performed in line 2-8
+because it just checks the length of \jscode{arguments} and passes its elements
+to \jscode{array} and \jscode{args}.  Moreover, \jscode{isArray(array)} is also
+able to be evaluated using concrete semantics because we know that \code{array}
+is an abstract array.  Only copying via \jscode{copyArray}, flattening via
+\jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize the abstract
+semantics.  This is the core idea of lazy concrete execution to maximize the
+part of dynamic analysis during static analysis.
+
+In the remaining section we formally define the combined analysis with lazy
+concrete execution in Section~\ref{sec:formal}.  Then, we explain how to define
+the combined analysis for JavaScript programs in Section~\ref{sec:javascript}.

### 2020-10-28 paper/pldi21/implementation.tex
Added the missing file, implementation.tex.

\section{Implementation}\label{sec:implementation}

\todo

### 2020-10-29 paper/pldi21/motivation.tex
Fixed error in motivation
Revising Section 2. motivation.

@@
   \caption{Motivating Example: Excerpts from Lodash library and JavaScript codes
+  in \code{zoom.us} site.}
   \label{fig:example}
-  in \code{zoom.us} site.}
 \end{figure}
 
-In this section, we will explain the motivation of the combined analysis for
-JavaScript programs with a simple motivating example described in
-Figure~\ref{fig:example}.  It shows how to utilize dynamic analysis during
-static analysis using lazy concrete execution to increase performance and
-precision of static analysis.
+In this section, we first point out limitations that existing techniques face to
+analyze the real-world example described in Figure~\ref{fig:example}.
+We then show how our combined analysis increase the analysis scalability and
+precision through lazy concrete execution, seamlessly combined with the original
+static analysis.
 
-For a motivating example, we excerpt the \jscode{concat} function in
-Figure~\ref{fig:concat} from Lodash library~\cite{lodash} (v4.17.20), which is
-the most popular npm package~\footnote{https://www.npmjs.com/browse/depended}
-and \inred{124,562} npm packages have dependency with it.  The \jscode{concat}
-function creates a new array concatenating given arrays or values.  It first
-checks the length of arguments in line 2-3. Then, it stores the first argument
-to \jscode{array} in line 5 and copies the remaining arguments to \jscode{args} in
-line 7-8.  Finally, it creates a new array by copying the given array via
-\jscode{copyArray} or initializing with a single value in line 10, and pushes
-each element of \jscode{args} after flattening it via \jscode{baseFlatten} in
-line 11.
+We excerpt the \jscode{concat} function in Figure~\ref{fig:concat} from Lodash
+library~\cite{lodash} (v4.17.20), which is the most popular npm package~\footnote{https://www.npmjs.com/browse/depended}
+that \inred{124,562} npm packages depend on.
+The \jscode{concat} function creates a new array concatenating given arrays or
+values.
+It first checks the length of arguments in line 2-3. Then, it stores the first
+argument to \jscode{array} in line 5 and copies the remaining arguments to
+\jscode{args} in line 7-8.
+Finally, it creates a new array by copying the given array via \jscode{copyArray}
+or initializing with a single value in line 10, and pushes each element of
+\jscode{args} after flattening it via \jscode{baseFlatten} in line 11.
 
-For applications of Lodash, we excerpt two functions \jscode{changeCountry} in
-Figure~\ref{fig:changeCountry} and \jscode{getData} in Figure~\ref{fig:getData}
-from the \code{zoom.us}~\cite{zoom} site.  The website \code{zoom.us} is
-homepage of Zoom, which is a videotelephony software program developed by Zooom
-Video Communications and it is ranked as \inred{16th} popular web site accroding
+A low degree of context sensitivity tends to face spurious callee explosion
+during analyzing \jscode{concat} function.
+The analysis is not supposed to lose precision for the loop in line 7-8.
+Moreover, \jscode{baseFlatten} has a recursive call in a loop that is a
+traditional challenge for static analysis.
+
+We excerpt two functions \jscode{changeCountry} in Figure~\ref{fig:changeCountry}
+and \jscode{getData} in Figure~\ref{fig:getData} from the \code{zoom.us}~\cite{zoom}
+site.
+The website \code{zoom.us} is ranked at \inred{16th} popular web site accroding
 to Alexa~\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.

### 2020-10-29 paper/pldi21/combined.tex
Added labels for each section
Added running example / Citation for TOPLAS'18

--- 2020-10-12 paper/pldi21/formal.tex
@@
-\section{Formalization}
+\section{Combined Analysis}\label{sec:formal}
 
-In this section, we formally define the dynamic shortcut over the abstract
-interpretation.
+In this section, we formally define the combined analysis with lazy concrete
+execution.  We extend the formalization of abstract interpretation and analysis
+sensitivity proposed by \citet{sens-toplas}.
 
 \subsection{Concrete Semantics}
-
-% \[
-%   \prog ::= (\lab: \inst)^*\\
-% \]
-% A program $\prog$ is a sequence of labelled instructions.  We represent the
-% semantics of a program $\prog$ as a state transition system $(\stset, \trans,
-% \istset)$.  A state $\st \in \stset = \labset \times \memset$ is a pair of a
-% label and a memory and represents a status of the program $\prog$.  A memory
-% $\mem \in \memset = \locset \finmap \valset$ is a finite mapping from locations
-% to values. A program starts with an initial state in $\istset$.  The transition
-% relation $\trans \subseteq \stset \times \stset$ describes how states are
-% transformed to other states.  It is defined with the \textit{concrete semantics}
-% $\sem{\inst}: \stset \rightarrow \powerset{\stset}$ of instructions as follows:
-% \[
-%   \st \trans \st' \iff \st = (\lab, \_) \wedge \st' \in \sem{\prog(\lab)}(\st)
-% \]
 
@@
 \{ \st' \mid \st \in \elem \wedge \st \trans \st' \}$.
+
+\begin{figure}[H]
+  \[
+    \begin{array}{l}
+      \enspace \labdot{0} \; \varx = \;? \; ;  \; \labdot{1}\\
+      \enspace \kwif \; (\; \varx \geq 0 \;) \; \labdot{2} \; \varx = \varx ;\\
+      \enspace \kwelse \; \labdot{3} \; \varx = -\varx ;  \; \labdot{4}\\
+    \end{array}
+  \]
+\vspace*{-1em}
+\caption{Conditional branch}
+\label{fig:running-example}
+\end{figure}
+
+For example, the code in Figure~\ref{fig:running-example} is a simple program
+that applies the mathematical absolute value function to the variable $\varx$.
+The question mark $?$ denotes the user input that returns an integer.  States
+are pairs of labels and integers $\varx$: $\stset = \labset \times \mathbb{N}$.
+The initial states are $\istset = \{ (\lab_0, 0) \}$ which means the program
+starts with the varible $\varx$ that stores 0 at $\lab_0$.  If the user input is
+$-42$, the program is executed with the following trace:
+\[
+  (\lab_0, 0) \trans (\lab_1, -42) \trans (\lab_3, -42) \trans (\lab_4, 42)
+\]
 
@@
 \end{itemize}
+
+A simple example abstract domain is $\absdom_\pm = \powerset{\{ -, +, 0 \}}$ with
+set operators as domain operators; $-$ denotes negative integers, $+$ positive
+integers, and $0$ zero.  If we use it for the code in
+Figure~\ref{fig:running-example}, the analysis result becomes $\{ -, +, 0 \}$
+because $\varx$ can have any integers at $\lab_1$.
 
@@
 
-\subsection{Lazy Concrete Interpretation}
+One of the most widely-used analysis sensitivity is \textit{flow sensitivity}
+defined with the flow-sensitive view abstraction $\fsviewmap: \labset
+\rightarrow \dom$ where
+\[
+  \forall \lab\in\labset. \; \fsviewmap(\lab) = \{ \st \mid \st = (\lab, \_) \}
+\]
+If we apply the flow sensitivity for the above example, the analysis result
+becomes as follows:
+\[
+  \begin{array}{|c||c|c|c|c|c|}\hline
+    \labset & \lab_0 & \lab_1 & \lab_2 & \lab_3 & \lab_4\\\hline
+    \absdom_\pm & 0 & -, +, 0 & +, 0 & - & +, 0\\\hline
+  \end{array}
+\]
 
-We define a \textit{lazy concrete interpretation} by extending the transition
+\subsection{Lazy Concrete Execution}
+
+We define a \textit{lazy concrete execution} by extending the transition
 relation $\trans$ as a symbolic transition relation $\symbtrans$ on symbolic
@@
 symbolic transition relation with a single symbolic state, and the lazy concrete
-interpret is linear execution until reaching the exception state.
+execution is linear until reaching the exception state.
 
@@
 abstract value to the corresponding concrete value.  Otherwise, it converts the
-abstract value as a symbolic value in the result symbolic state.  Two converters
+abstract value as a symbolic value in a result symbolic state.  Two converters
 convert given elements wihtout loss of information:
@@
 We define the \textit{combined analysis} of the abstract interpretation and the
-lazy concrete interpretation.  In the combined analysis, we use the powerset of
+lazy concrete execution.  In the combined analysis, we use the powerset of
 symbolic states as the domain $\combdom = \powerset{\symbstset}$, and extend the
@@
 denotes the element-wise extended function of a function $f$.  We could
-configure when the lazy concrete interpretation or the abstract interpretation
+configure when the lazy concrete execution or the abstract interpretation
 is performed based on the definition of the $\checker$ function and its negation
@@
 \]
-where $N$ is a pre-defined maximum length of the lazy concrete interpretation.
+where $N$ is a pre-defined maximum length of the lazy concrete execution.
 The combined analysis just performs one-step symbolic transition for each
@@
 abstract state.
-
-% The abstract sensitivity should be defined with a view
-% abstraction $\viewmap: \viewset \rightarrow \dom$ more find-grained than the
-% flow sensitive view abstraction $\fsviewmap$:
-% \[
-%   \forall \view \in \viewset. \; \exists \lab \in \labset. \;
-%   \viewmap(\view) \subseteq \fsviewmap(\lab)
-% \]

### 2020-10-29 paper/pldi21/combined.tex
Changed: lazy concrete execution -> sealed symbolic execution

@@
 
-In this section, we formally define the combined analysis with lazy concrete
+In this section, we formally define the combined analysis with sealed symbolic
 execution.  We extend the formalization of abstract interpretation and analysis
@@
 
-\subsection{Lazy Concrete Execution}
+\subsection{Sealed Symbolic Execution}
 
-We define a \textit{lazy concrete execution} by extending the transition
+We define a \textit{sealed symbolic execution} by extending the transition
 relation $\trans$ as a symbolic transition relation $\symbtrans$ on symbolic
@@
 to interpret in a concrete way.  Thus, a symbolic state \textit{always} has a
-symbolic transition relation with a single symbolic state, and the lazy concrete
-execution is linear until reaching the exception state.
+symbolic transition relation with a single symbolic state, and the sealed
+symbolic execution is linear until reaching the exception state.
 
@@
 We define the \textit{combined analysis} of the abstract interpretation and the
-lazy concrete execution.  In the combined analysis, we use the powerset of
+sealed symbolic execution.  In the combined analysis, we use the powerset of
 symbolic states as the domain $\combdom = \powerset{\symbstset}$, and extend the
@@
 denotes the element-wise extended function of a function $f$.  We could
-configure when the lazy concrete execution or the abstract interpretation
+configure when the sealed symbolic execution or the abstract interpretation
 is performed based on the definition of the $\checker$ function and its negation
@@
 \]
-where $N$ is a pre-defined maximum length of the lazy concrete execution.
+where $N$ is a pre-defined maximum length of the sealed symbolic execution.
 The combined analysis just performs one-step symbolic transition for each

### 2020-10-29 paper/pldi21/motivation.tex
Changed: lazy concrete execution -> sealed symbolic execution

@@
 We then show how our combined analysis increase the analysis scalability and
-precision through lazy concrete execution, seamlessly combined with the original
+precision through sealed symbolic execution, seamlessly combined with the original
 static analysis.
@@
 
-Dynamic analysis is still applicable using lazy concrete execution even if the
+Dynamic analysis is still applicable using sealed symbolic concrete execution even if the
 arguments are not concrete values.  The \jscode{getData} function is another
@@
 \jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize the abstract
-semantics.  This is the core idea of lazy concrete execution to maximize the
+semantics.  This is the core idea of sealed symbolic execution to maximize the
 part of dynamic analysis during static analysis.
 
-In the remaining section we formally define the combined analysis with lazy
-concrete execution in Section~\ref{sec:formal}.  Then, we explain how to define
+In the remaining section we formally define the combined analysis with sealed
+symbolic execution in Section~\ref{sec:formal}.  Then, we explain how to define
 the combined analysis for JavaScript programs in Section~\ref{sec:javascript}.

### 2020-10-29 paper/pldi21/intro.tex
Added the implementation section.
Revising motivation.

@@
 dynamic shortcuts.
-We extend a dynamic analysis to work as long as possible despite of the presence
-of abstract values by laziness.
+We use a linear symbolic execution as dynamic analysis to analyze program on the
+concrete engine as long as possible despite of the presence of abstract values.
 The analysis goes on the concrete engine as much as possible until it meets
@@
 JavaScript in Section~\ref{sec:javascript}.
-We explain key implementation techniques like the synchronizetion of two analyses.
+Section~\ref{sec:implementation} describes key implementation techniques like the synchronizetion of two analyses.
 We evaluate our idea using real-world benchmarks in Section~\ref{sec:eval}.

### 2020-10-29 paper/pldi21/motivation.tex
Revising motivation.

@@
 
-A low degree of context sensitivity tends to face spurious callee explosion
-during analyzing \jscode{concat} function.
-The analysis is not supposed to lose precision for the loop in line 7-8.
-Moreover, \jscode{baseFlatten} has a recursive call in a loop that is a
-traditional challenge for static analysis.
-
+The functions in Lodash are popular to implement common functionalities for
+websites as well.
 We excerpt two functions \jscode{changeCountry} in Figure~\ref{fig:changeCountry}
-and \jscode{getData} in Figure~\ref{fig:getData} from the \code{zoom.us}~\cite{zoom}
-site.
+and \jscode{getData} in Figure~\ref{fig:getData} from the \code{zoom.us}~\cite{zoom} site.
 The website \code{zoom.us} is ranked at \inred{16th} popular web site accroding
 to Alexa~\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.
-
-When the given arguments of a function invokation are concrete values, we can
-perform dynamic analysis instead of static analysis. For example, The
-\jscode{changeCountry} function is invoked when a country different with the
-current one is selected in registration of Zoom meetings.  When the ``United
-States of America'' (USA) is selected, it calls the \jscode{concat} function
-with two pre-defined concrete values as arguments to load USA state information
-in line 17-18.  The first argument is an array literal \jscode{[["Other",
+The \jscode{changeCountry} is the example of using \jscode{concat} only with
+concrete values.
+The \jscode{changeCountry} function is invoked when a user selects his/her
+country on the dropdown list in the register page.
+When the user selects ``United States of America'', \jscode{changeCountry} calls
+the \jscode{concat} function in line 17-18 to prepare the array for
+``State/Province'' dropdown list.
+The first argument of \jscode{concat} is an array literal \jscode{[["Other",
 "Other"]]} and the second one is an array of pairs of abbreviations and names of
-USA states defined as follows:
+the states defined as follows:
 \begin{lstlisting}[style=myJSstyle,numbers=none]
@@
 \end{lstlisting}
-Moreover, \jscode{this} value is also a concrete value, the Lodash top-level
-object \jscode{\_}.  Thus, we could perform dynamic analysis by invoking the
-\jscode{concat} funciton with \jscode{\_} as \jscode{this} value and above two
-concrete values as arguments.  It increases performance of static analysis by
-skipping the analysis of function call in line 17-18 and utilizing the result of
-dynamic analysis.
+Thus, \jscode{changeCountry} always invokes \jscode{concat} with concrete values.
+In the case of \jscode{getData}, \jscode{concat} works with unknown values.
+The \jscode{getData} function is invoked when loading more Zoom events in
+``Webinars \& Events'' page.
+At the first time, initial eight events appear on the page.
+For each click of the ``Load More'' button, the \jscode{getData} sends a POST
+request to the server and receives data of 8 more events by calling \jscode{concat} in line 28.
+As a result, the events list on the page keeps growing by 8.
+Both functions, selecting an option of dropdown list and loading more contents
+from server-side, are familiar to users.
 
-Dynamic analysis is still applicable using sealed symbolic concrete execution even if the
-arguments are not concrete values.  The \jscode{getData} function is another
-part to use \jscode{concat} function but we can only partially apply dynamic
-analysis in this case.  It is invoked when loading more Zoom events in
-``Webinars \& Events'' page.  At the first time, initial eight events are stored
-in \jscode{this.pastEvents}.  For each click of the ``Load More'' button, the
-\jscode{getData} sends a POST request to the server and receives additional
-event information \jscode{e} in line 24.  Then, eight events in
-\jscode{e.events} are appended to \jscode{this.pastEvents} using the
-\jscode{concat} function in line 27-28.  In this case, arguments are not
-deterministic but dependent on the given data from the server.  However, we know
-that the number of arguments are still deterministically defined as \jscode{2}
-and they are array objects.  Thus, we just invoke the funciton \jscode{concat}
-with \jscode{\_} as \jscode{this} value and two abstract arrays as arguments for
-dynamic analysis.  Then, dynamic analysis is successfully performed in line 2-8
-because it just checks the length of \jscode{arguments} and passes its elements
-to \jscode{array} and \jscode{args}.  Moreover, \jscode{isArray(array)} is also
-able to be evaluated using concrete semantics because we know that \code{array}
-is an abstract array.  Only copying via \jscode{copyArray}, flattening via
-\jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize the abstract
-semantics.  This is the core idea of sealed symbolic execution to maximize the
-part of dynamic analysis during static analysis.
+Existing techniques: static analysis, dynamic analysis, and combined analysis
+have limitations to deal with the program containing \jscode{changeCountry} and
+\jscode{getData}.
+Static analyses of low degrees of context sensitivity tend to cause the
+precision loss during analyzing \jscode{concat} function.
+The loop in line 7-8 can lead to messing up every property value of args object.
+Moreover, \jscode{baseFlatten} has a recursive call that is another challenge
+for static analysis.
+High degrees of context sensitivity is the promising way, but its computaion
+cost is the burden.
+Dynamic analyses can show much higher performance for the \jscode{concat} call
+by \jscode{changeCountry} than static analyses without any unsoundness and
+precision loss.
+However, they cannot cover all possible behavior of the \jscode{concat} call
+by \jscode{getData} originated by unknown server-side data.
+A promising form of combined analysis is dynamically analyzing the call by \jscode{changeCountry}
+and statically analyzing the call by \jscode{getData} that is not possible by
+existing combined analyses.
+User events trigger both functions, the order of function calls is
+non-deterministic, so the proper point to divide stages for combined analyses
+does not exist.
+The syntactic division of the program imposes to choose only one kind of analysis
+for the \jscode{concat} function that restricts the benefits of combined analysis.
+
+We present a more flexible and fine-grained method to combine two analyses to
+maximize the benefits.
+
+Our observation is
+
+%When the given arguments of a function invokation are concrete values, we can
+%perform dynamic analysis instead of static analysis. For example, The
+%\jscode{changeCountry} function is invoked when a country different with the
+%current one is selected in registration of Zoom meetings.  When the ``United
+%States of America'' (USA) is selected, it calls the \jscode{concat} function
+%with two pre-defined concrete values as arguments to load USA state information
+%in line 17-18.  The first argument is an array literal \jscode{[["Other",
+%"Other"]]} and the second one is an array of pairs of abbreviations and names of
+%USA states defined as follows:
+%\begin{lstlisting}[style=myJSstyle,numbers=none]
+%WebinarBase.questions.state.items =
+%  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
+%\end{lstlisting}
+%Moreover, \jscode{this} value is also a concrete value, the Lodash top-level
+%object \jscode{\_}.  Thus, we could perform dynamic analysis by invoking the
+%\jscode{concat} funciton with \jscode{\_} as \jscode{this} value and above two
+%concrete values as arguments.  It increases performance of static analysis by
+%skipping the analysis of function call in line 17-18 and utilizing the result of
+%dynamic analysis.
+%
+%Dynamic analysis is still applicable using lazy concrete execution even if the
+%arguments are not concrete values.  The \jscode{getData} function is another
+%part to use \jscode{concat} function but we can only partially apply dynamic
+%analysis in this case.  It is invoked when loading more Zoom events in
+%``Webinars \& Events'' page.  At the first time, initial eight events are stored
+%in \jscode{this.pastEvents}.  For each click of the ``Load More'' button, the
+%\jscode{getData} sends a POST request to the server and receives additional
+%event information \jscode{e} in line 24.  Then, eight events in
+%\jscode{e.events} are appended to \jscode{this.pastEvents} using the
+%\jscode{concat} function in line 27-28.  In this case, arguments are not
+%deterministic but dependent on the given data from the server.  However, we know
+%that the number of arguments are still deterministically defined as \jscode{2}
+%and they are array objects.  Thus, we just invoke the funciton \jscode{concat}
+%with \jscode{\_} as \jscode{this} value and two abstract arrays as arguments for
+%dynamic analysis.  Then, dynamic analysis is successfully performed in line 2-8
+%because it just checks the length of \jscode{arguments} and passes its elements
+%to \jscode{array} and \jscode{args}.  Moreover, \jscode{isArray(array)} is also
+%able to be evaluated using concrete semantics because we know that \code{array}
+%is an abstract array.  Only copying via \jscode{copyArray}, flattening via
+%\jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize the abstract
+%semantics.  This is the core idea of lazy concrete execution to maximize the
+%part of dynamic analysis during static analysis.
 

### 2020-10-29 paper/pldi21/combined.tex
More explanation with traditional symbolic execution

@@
 
-We define a \textit{sealed symbolic execution} by extending the transition
-relation $\trans$ as a symbolic transition relation $\symbtrans$ on symbolic
-states. First, we extends the concrete states $\stset$ to \textit{symbolic
-states} with symbolic values $\symbset$ that denote abstract values that cannot be
-concretized to singleton values. A symbolic transition relation $\symbtrans
-\subseteq \symbstset \times (\symbstset \uplus \{ \excst \})$ is exactly the same
-with the original transition relation $\trans$ except when the relation requires
-the exact value of symbolic values.  In this case, the symbolic state has the
-relation a special exception state $\excst$ to represent that it is impossible
-to interpret in a concrete way.  Thus, a symbolic state \textit{always} has a
-symbolic transition relation with a single symbolic state, and the sealed
-symbolic execution is linear until reaching the exception state.
+To handle abstract values in concrete semantics, we define \textit{sealed
+symbolic execution} by extending the transition relation $\trans$ as a symbolic
+transition relation $\symbtrans$ on symbolic states.  First, we extends the
+concrete states $\stset$ to symbolic states with \textit{sealed symbolic values}
+$\symbset$.  A symbolic transition relation $\symbtrans \subseteq \symbstset
+\times (\symbstset \uplus \{ \excst \})$ is exactly the same with the original
+transition relation $\trans$ except when the relation requires the exact value
+of sealed symbolic values.  In this case, the symbolic state has the relation a
+special exception state $\excst$ to represent that it is impossible to interpret
+in a concrete way.  Thus, a symbolic state \textit{always} has a symbolic
+transition relation with a single symbolic state, and the sealed symbolic
+execution is linear until being terminated or reaching the exception state
+$\excst$.
+
+The main difference of sealed symbolic execution with the traditional symbolic
+execution~\cite{symbolic} is that it only supports sealed symbolic values
+instead of symbolic expressions and path constraints.  For example, the
+following trace represents the traditional symbolic execution of the running
+example in Figure~\ref{fig:running-example}:
+\[
+  \begin{array}{r@{~}c@{~}l}
+    &&(\lab_2, \symb)[\symb \geq 0] \trans (\lab_4, \symb)[\symb \geq 0]
+    \vspace*{-0.5em}\\
+    &\rutrans&
+    \vspace*{-0.5em}\\
+    (\lab_0, 0)[] \trans (\lab_1, \symb)[]&&
+    \vspace*{-0.5em}\\
+    &\rdtrans&
+    \vspace*{-0.5em}\\
+    &&(\lab_3, \symb)[\symb < 0] \trans (\lab_4, -\symb)[\symb < 0]\\
+  \end{array}
+\]
+It first assigns a symbolic value $\symb$ to the variable $\varx$ at $\lab_1$.
+For the conditional branch, it is forked by creating two symbolic states with
+different path conditions $\symb \geq 0$ and $\symb < 0$ for true and false
+branches, respectively.  After executing statements $\varx = \varx$ and $\varx =
+-\varx$, the variable $\varx$ stores symblic expressions $\symb$ and $-\symb$ at
+$\lab_4$.  However, the sealed symbolic execution stops at $\lab_1$ as follows:
+\[
+  (\lab_0, 0) \; \symbtrans \; (\lab_1, \symb) \; \symbtrans \; \excst
+\]
+because the branch requires the actual value of the symbolic value $\symb$.
 

### 2020-10-29 paper/pldi21/combined.tex
Added diagram for combined analysis and more explanation

@@
 
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\linewidth]{img/combined-analysis}
+  \vspace*{-2em}
+  \caption{The diagram for the extended view transition in the combined analysis.}
+  \vspace*{-1em}
+  \label{fig:combined-analysis}
+\end{figure}
+
 We define the \textit{combined analysis} of the abstract interpretation and the
@@
 denotes the element-wise extended function of a function $f$.  We could
-configure when the sealed symbolic execution or the abstract interpretation
-is performed based on the definition of the $\checker$ function and its negation
-$\neg\checker$.  It should satisfy the following condition for the soundness and
-the termination of the combined analysis:
+configure when the sealed symbolic execution or the abstract interpretation is
+performed based on the definition of the $\checker$ function and its negation
+$\neg\checker$.  The combined analysis performs one-step symbolic transition for
+each symbolic state that passes the filter $\checker$. On the other hand, it
+converts remaining symbolic states to the corresponding abstract states, merges
+them into a single abstract state, and performs the abstract one-step execution
+for the abstract state.
+
+For example, Figure~\ref{fig:combined-analysis} depicts the
+diagram of the view transition from $\view$ to $\view'$ in the combined
+analysis.  The element $\combelem$ in $\view$ consists of five symbolic states
+from $\nsymbst{1}$ to $\nsymbst{5}$.  The solid box denotes that the corresponding
+symbolic state passes the filter $\checker$ and the dotted box denotes that it
+does not.  For each symbolic state that passes the filter ($\nsymbst{1}$,
+$\nsymbst{2}$, and $\nsymbst{4}$), it applies the symbolic transition $\symbtrans$.
+For failed symbolic states ($\nsymbst{3}$ and $\nsymbst{5}$), it applies the
+converter $\saconverter$ to convert each of them to the corresponding abstract
+state and merges results using the join operator ($\join$).  Then, it utilizes
+the abstract semantics via the original view transition
+$\viewtrans{\view}{\view'}$ and the converter $\asconverter$ to convert the
+result to the corresponding symbolic state.
+
+For the soundness and the termination of the combined analysis, the filter
+$\checker$ in the extended view transition should satisfy the following
+condition:
+\begin{theorem}
+  The combined analysis has sound analysis result and terminates in a finite
+  time if its abstract semantics is sound and $\checker$ satisfies the following
+  condition:
   \[
@@
   where $N$ is a pre-defined maximum length of the sealed symbolic execution.
-The combined analysis just performs one-step symbolic transition for each
-symbolic state that passes the filter $\checker$. On the other hand, it converts
-remaining symbolic states to the corresponding abstract states, merges them into
-a single abstract state, and performs the abstract one-step execution for the
-abstract state.
+\end{theorem}
+\inred{We prove that any combined analysis defined with the extended view
+transition satisfying the above condition always has sound analysis result and
+terminates in a finite time. Because of the page limitation, we omit the
+proof in this paper and include it in a companion report.}

### 2020-10-29 paper/pldi21/combined.tex
Added example for checker

@@
 \dot{\saconverter}(\combelem\mid_{\neg\checker})$.  The dot notation $\dot{f}$
-denotes the element-wise extended function of a function $f$.  We could
-configure when the sealed symbolic execution or the abstract interpretation is
-performed based on the definition of the $\checker$ function and its negation
-$\neg\checker$.  The combined analysis performs one-step symbolic transition for
-each symbolic state that passes the filter $\checker$. On the other hand, it
-converts remaining symbolic states to the corresponding abstract states, merges
-them into a single abstract state, and performs the abstract one-step execution
-for the abstract state.
+denotes the element-wise extended function of a function $f$.  The combined
+analysis performs one-step symbolic transition for each symbolic state that
+passes the filter $\checker$. On the other hand, it converts remaining symbolic
+states to the corresponding abstract states, merges them into a single abstract
+state, and performs the abstract one-step execution for the abstract state.
 
@@
 
-For the soundness and the termination of the combined analysis, the filter
-$\checker$ in the extended view transition should satisfy the following
-condition:
+We could configure when the sealed symbolic execution or the abstract
+interpretation is performed based on the definition of the $\checker$ function
+and its negation $\neg\checker$.  For example, we could define the $\checker$
+that passes only function entry, call, and exit points to perform conversions in
+a function level.  However, for the soundness and the termination of the
+combined analysis, it should satisfy the following condition:
 \begin{theorem}

### 2020-11-02 paper/pldi21/abstract.tex
Revised abstract

@@
 \begin{abstract}
-Static analyses based on abstract interpretation can be integrated into developer workflow and help developers to find bugs.
-However, the dynamic features of JavaScript degrade the scalability and precision of the pure static analyses.
-Combining static and dynamic analyses is one of the breakthroughs in JavaScript bug detection.
-Existing combined analyses have static boundaries that distinguish which analysis used for which part of a program.
-Such boundaries are intuitive but limit chances to optimize transitions between two analyses.
-We formally present the dynamic shortcut, a more flexible compound of static and dynamic analyses.
-We implement a proof of concept bug detector by extending the existing static analyzer supporting a subset of ECMAScript 5.1.
-Our experimental results show that the combined analysis indeed speeds up and produces more precise results.
+  JavaScript becomes one of the most widely used programming languages for web
+  development, server-side programming, and embedded systems.  However, its
+  dynamic language features degrade the scalability and precision of the static
+  analysis.  Moreover, the variety of built-in functions and host environments
+  requires excessive manual modeling of their behaviors for the static analysis
+  of real-world JavaScript applications.  To alleviate this problem, several
+  researchers utilize the dynamic analysis to take its advantage during
+  JavaScript static analysis.  However, most of them sacrifice the soundness
+  and focus on only reducing the effort of manual modeling.
+
+  In this paper, we propose a novel \textit{dynamic shortcut} technique to
+  leverage high performance of dynamic analysis for static analysis in a sound
+  way.  It could significantly accelerate the JavaScript static analysis by
+  using the highly-optimized commercial JavaScript engines for the concretely
+  executable program parts.  Moreover, it might improve the precision and lessen
+  the modeling effort by performing dynamic analysis for opaque codes.  To
+  maximize the usage of dynamic analysis, we propose \textit{sealed symbolic
+  execution}, which is an augmented concrete execution that represents abstract
+  values as sealed symbolic values.  We formally define the static analysis with
+  dynamic shortcut using sealed symbolic execution.  We actualize our method via
+  $\tool$, which is an extension of the existing JavaScript static analyzer
+  $\safe$ with dynamic shortcut.  For evaluation of $\tool$, we analyzed
+  abstracted versions of \inred{77} official tests of \inred{Lodash 4} library.
+  Our tool is \inred{X.X}x faster than the original static analysis on average.
+  Moreover, it improves \inred{XX.XX}\% of analysis precision by using dynamic
+  analysis instead of static analysis for \inred{XX.X} opaque functions on
+  average.
 \end{abstract}

### 2020-11-02 paper/pldi21/abstract.tex
Revised intro

@@
   JavaScript becomes one of the most widely used programming languages for web
-  development, server-side programming, and embedded systems.  However, its
-  dynamic language features degrade the scalability and precision of the static
-  analysis.  Moreover, the variety of built-in functions and host environments
-  requires excessive manual modeling of their behaviors for the static analysis
-  of real-world JavaScript applications.  To alleviate this problem, several
-  researchers utilize the dynamic analysis to take its advantage during
-  JavaScript static analysis.  However, most of them sacrifice the soundness
-  and focus on only reducing the effort of manual modeling.
+  development, server-side programming, and even micro-controllers for IoT.
+  However, its dynamic language features degrade the scalability and precision
+  of the static analysis.  Moreover, the variety of built-in functions and host
+  environments requires excessive manual modeling of their behaviors.  To
+  alleviate this problem, several researchers utilize dynamic analysis to take
+  its advantage during JavaScript static analysis.  However, most of them cannot
+  fully utilize high performance of dynamic analysis and sacrifice the soundness
+  of static analysis.
 
   In this paper, we propose a novel \textit{dynamic shortcut} technique to
-  leverage high performance of dynamic analysis for static analysis in a sound
-  way.  It could significantly accelerate the JavaScript static analysis by
-  using the highly-optimized commercial JavaScript engines for the concretely
-  executable program parts.  Moreover, it might improve the precision and lessen
-  the modeling effort by performing dynamic analysis for opaque codes.  To
-  maximize the usage of dynamic analysis, we propose \textit{sealed symbolic
-  execution}, which is an augmented concrete execution that represents abstract
-  values as sealed symbolic values.  We formally define the static analysis with
-  dynamic shortcut using sealed symbolic execution.  We actualize our method via
-  $\tool$, which is an extension of the existing JavaScript static analyzer
-  $\safe$ with dynamic shortcut.  For evaluation of $\tool$, we analyzed
-  abstracted versions of \inred{77} official tests of \inred{Lodash 4} library.
-  Our tool is \inred{X.X}x faster than the original static analysis on average.
-  Moreover, it improves \inred{XX.XX}\% of analysis precision by using dynamic
-  analysis instead of static analysis for \inred{XX.X} opaque functions on
-  average.
+  leverage high performance of dynamic analysis for static analysis by freely
+  switching between them in a sound way.  It could significantly accelerate the
+  JavaScript static analysis by using the highly-optimized commercial JavaScript
+  engines for the concretely executable program parts.  Moreover, it might
+  improve the precision and lessen the modeling effort by performing dynamic
+  analysis for opaque codes.  To maximize the usage of dynamic analysis, we
+  propose \textit{sealed symbolic execution}, which is an augmented concrete
+  execution that represents abstract values as sealed symbolic values.  We
+  formally define the static analysis with dynamic shortcut using sealed
+  symbolic execution.  We actualize our method via $\tool$, which is an
+  extension of the existing JavaScript static analyzer SAFE with dynamic
+  shortcut.  For evaluation of $\tool$, we analyzed abstracted versions of
+  \inred{77} official tests of \inred{Lodash 4} library.  Our tool is
+  \inred{X.X}x faster than the original static analysis on average.  Moreover,
+  it improves \inred{XX.XX}\% of analysis precision by using dynamic analysis
+  instead of static analysis for \inred{XX.X} opaque functions on average.
 \end{abstract}

### 2020-11-02 paper/pldi21/eval.tex
Revised intro

@@
-\section{Authors and Affiliations}
+\section{Evaluation}\label{sec:eval}
 
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-Note that authors' addresses are mandatory for journal articles.
+\begin{itemize}
+  \item \textbf{RQ1) Analysis Speed-up:} How much analysis time is reduced by
+    adding dynamic shortcut to static analysis?
+  \item \textbf{RQ2) Precision Improvement:} How much analysis precision is
+    improved by replacing the manual modeling with dynamic shortcut?
+  \item \textbf{RQ3) Opaque Function Coverage:} How many opaque functions are
+    covered by dynamic shortcut without using manual modeling?
+\end{itemize}

### 2020-11-02 paper/pldi21/intro.tex
Added img/ directory
Revised intro

--- 2020-10-27 paper/pldi21/intro.tex
@@
 \section{Introduction}\label{sec:intro}
-JavaScript is the de facto programming language in web development and,
-moreover, blossoming beyond the web.
-JavaScript has dominated client-side scripting of the web for over a decade.
-JavaScript takes the unique position as the universal language operating in both
-the browser and on a server in the form of Node.js.
-The client-side frameworks such as React, Vue.js, and Angular have accelerated
-the universal use of JavaScript.
-The cross-platform frameworks like React Native and Electron have spread
-JavaScript to the new domains of mobile and desktop beyond the web.
-This is only possible thanks to JavaScript's easy operation in development and
-deployment with scripting language characteristics such as dynamic and
-interpreted language features~\cite{weaklySPE}.
 
-However, such features make it difficult to support developer tools that require
-statically reasoning about semantics of JavaScript programs such as call graph
-construction, type checking, optimization, and bug detection.
-For example, the combination of the JavaScript features: dynamically-computed
-property name, prototype chain, and first-class function, makes call graph
-construction challenging.
-Even a minor precision loss at property name can cause reading all methods in
-the object and its prototype chain, including hundreds of built-ins, that
-results in useless analysis results.
-In static analyses of Java, the benchmark results clearly show the trade-off
-between precision and performance~\cite{introspective, data-driven}, a low degree of
-context sensitivity shows a high performance but low precision.
-In the case of JavaScript, the relationship between precision and performance is
-more complex due to the spurious callee explosion.
-Low precision tends to cause the large number of spurious callees, which
-significantly degrades the performance~\cite{correlation, determinacy-jQuery, weaklySPE, value-refinement}.
+Over the past decade, the rise of JavaScript as the de facto programming
+language in web development has expanded its reach to diverse fields.
+Node.js~\cite{nodejs} supports server-side programming, React
+Native~\cite{react-native} and Electron~\cite{electron} produce cross-platform
+applications.  Moreover, Moddable~\cite{moddable} and Espruino~\cite{espruino}
+provide JavaScript environments in micro-controllers for IoT.  Such wide prevalent
+usage places JavaScript at \#7 in TIOBE Programming Community
+index\footnote{https://www.tiobe.com/tiobe-index/}.  Thus, researchers have
+developed static analyzers such as JSAI~\cite{jsai}, TAJS~\cite{tajs},
+WALA~\cite{wala}, and SAFE~\cite{safe,safe2} to understand behaviors of
+JavaScript programs and to detect their bugs in a sound way.
 
-For this reason, recent studies on JavaScript static analysis have developed
-to improve analysis precision against this challenge.
-Madsen et al.~\cite{string, regex, combining-string} presented sophisticated abstract domains for strings.
-Park et al. proposed higher degrees of context sensitivity for loops~\cite{lsaECOOP, lsaSPE}.
-Relations between object properties have aided to analysis precision~\cite{correlation, weaklyAPLAS, weaklySPE}.
-The idea stretches from property name to non-local variables and types for predicate functions~\cite{value-partitioning}.
-The on-demand backward analyses~\cite{value-refinement} refines imprecise values for property writes.
+However, static analysis of real-world JavaScript programs suffers from its
+dynamic language features.  JavaScript supports various \textit{dynamic language
+features} such as high-order functions, first-class property names, and dynamic
+code generations.  While they provide great flexibility in development but it is
+challenging to statically analyze such features.  To overcome this problem,
+researchers have proposed several analysis techniques: advanced string
+domains~\cite{string, regex, combining-string}, loop sensitivity~\cite{lsaECOOP,
+lsaSPE}, property relation based analysis~\cite{correlation, weaklyAPLAS,
+weaklySPE, value-partitioning}, and on-demand backward
+analysis~\cite{value-refinement}.
 
-Unfortunately, it does not mean that high precision leads to "good" performance
-but "better" than the "bad" performance.
-Computation costs of high degree of sensitivity remains as it is but the
-snowball of low precision is much larger than that.
-We alleviate computation costs of high degrees of sensitivity through a combined
-approach of static and dynamic analyses.
-
-Existing combined approaches derive three kinds of benefits of dynamic analysis.
-Dynamic analyses~\cite{jalangi, dlint} can run on a highly-optimized
-JavaScript engine like V8, so it can boost up analysis performance.
-There is no precision loss coming from limitations of abstract domains and
-sensitivities if the dynamic analysis terminates~\cite{determinacy, concerto}.
-Dynamic analysis can pass by opaque codes that require extra handling for static
-analysis~\cite{battles, sra}.
-
-However, the existing combined analyses are limited to maximize benefits of
-dynamic analysis.
-Staged analyses first collect particular information by dynamic analysis and
-apply static analysis augmented with dynamic information~\cite{blendedJava, eha}.
-Dynamic information can be determinacy facts~\cite{determinacy}, call graphs~\cite{tunable}
-object creation site~\cite{blendedJS}, or entire heap at specific program points~\cite{battles}.
-Once static analysis starts, it does not utilize more dynamic information.
-The other design of combined analysis is divide whole program into two parts~\cite{concerto}.
-One (framework code) for the dynamic analysis  and the other (user code) for the
-static analysis.
-The policy to divde a program is predefined and syntactic and never changes
-during analysis.
-
-We present a more flexible and fine-grained method to combine two analyses to
-maximize benefits.
-Our approach extend dynamic analysis to work with the presence of abstract
-values, named lazy concrete execution.
-The analysis goes on a concrete engine side as much as possible until
-non-determinism is actually introduced by abstract values or analysis
-sensitivity that the lazy concrete execution cannot handle.
-When the lazy concrete exeuction meets non-determinism, the analysis switches to
-the traditional static analysis and uses its abstract semantics to handle that.
-As soon as analysis sensitivity is deterministic, it switches to the lazy
-concrete execution again.
+At the same time, various JavaScript host environments require excessively
+manual modeling of their behaviors for static analysis.  Built-in functions and
+host-dependent functions are implemented in another native language like C++
+instead of JavaScript thus their codes are \textit{opaque} during static
+analysis.  Thus, we need to manually model their behaviors but it is
+error-prone, tedious, and labor-intensive.  While several automatic modeling
+techniques~\cite{safewapi, model-ts} have been proposed, they utilize only type
+information thus they generate imprecise modeling compared to the manual
+approach.
 
@@
   \centering
-  \includegraphics[width=\linewidth]{benchmark_performance}
-  \caption{The performances of static and dynamic analyses on deterministic benchmarks}
+  \includegraphics[width=\linewidth]{img/performance_v8v7}
+  \vspace*{-2em}
+  \caption{The performances of dynamic analysis and static analysis for V8
+  benchmarks (version 7)}
   \label{fig:performance}
+  \vspace*{-1em}
 \end{figure}
 
-Our key observation is that high degrees of sensitivity increase the use of
-concrete semantics during analysis and utilizing an optimzied engine like V8 is
-the fast way to apply concrete semantics.
-As shown in Figure~\ref{fig:performance}.
-Our design is not limited to any predefined features including program point and
-does not harmful to the soundness of the original static analysis.
+Instead of advancing static analysis techniques, several researchers leverage
+dynamic analysis to resolve such obstacles in static analysis.  Dynamic
+analyzers such as Jalangi~\cite{jalangi} and DLint~\cite{dlint} run on a
+highly-optimized commercial JavaScript engine thus they are much faster than
+static analysis.  Figure~\ref{fig:performance} shows that the dynamic analysis
+(Jalangi) is \inred{X.X}x faster than static analysis (SAFE) for V8 benchmarks
+(version 7).  Using high performance dynamic analysis, several researchers
+reduce the scope of static analysis~\cite{determinacy, blendedJS}, construct
+initial abstract state~\cite{battles, eha}, and automatic modeling of opaque
+codes~\cite{sra}.
 
-%We have demonstrated how dynamic shortcut maximize benefits of dynamic analysis.
-%We have implemetned our method by extending the existing JavaScript static
-%analyzer.
-%We found that using dynamic shortcut significantly increased performance for
-%benchmark programs enhanced with abstracted input.
+Unfortunately, existing techniques using dynamic analysis for static analysis
+have two limitations: 1) it cannot fully utilize the high performance of dynamic
+analysis, and 2) it sacrifices the soundness of static analysis.  Most of
+existing techniques are \textit{staged analyses} that first extract specific
+information via dynamic analysis and utilize it in static analysis;
+\citet{determinacy} identifies determinate expressions that always have the same
+value at given program point, \citet{blendedJS} extract the dynamic values to
+change expressions as certain literals, and Park et al.~\cite{battles,eha} dump
+initial states in a certain host environment or the entry of an event handler.
+However, they cannot utilize dynamic analysis any more after starting static
+analysis thus they disturb to maximize the performance advantage.  Moreover,
+they sacrifice the soundness of static analysis to perform dynamic analysis.
+For example, \citet{sra} utilize dynamic analysis for opaque codes with given
+abstract arguments during static analysis.  However, they randomly sample finite
+concrete values for given abstract arguments when they represent infinite number
+of values.  Thus, the analysis result becomes unsound because of the missing
+concrete values.
 
-In summary, the contributions of this paper are as follows.
+In this paper, we propose a novel \textit{dynamic shortcut} technique to
+leverage high performance of dynamic analysis for static analysis by freely
+switching between them in a sound way.  Our key observation is that we can
+use concrete semantics for specific program parts while preserving the soundness
+if they are not dependent with meaning of abstract values.  For example, the
+third line of the following program passes the abstract value \jscode{absval}
+stored in \jscode{obj.p1} to the variable \jscode{x}:
+\begin{lstlisting}[style=myJSstyle,numbers=none]
+var absval = ... // an abstract value
+var obj = { p1: absval }, y = "p";
+x = obj[y + 1];
+\end{lstlisting}
+Even though \jscode{obj} contains an abstract value \jscode{absval}, the
+semantics of the third line does not dependent with the meaning of
+\jscode{absval}.  To utilize this observation in dynamic shortcut, we introduce
+\textit{sealed symbolic execution}, which is an augmented concrete execution
+with sealed symbolic values.  We represent each abstract value as a sealed
+symbolic value, which is a symbolic value that throws an error when trying to
+access its actual meaning.  To evaluate our approach, we implemented $\tool$ by
+extending the existing JavaScript static analyzer SAFE with dynamic shortcut.
+For evaluation of $\tool$, we analyzed abstracted versions of \inred{77}
+official tests of \inred{Lodash 4} library.
+
+Our contributions in this paper include the following:
 \begin{itemize}
-\item We formally describe the high-level idea of adding dynamic shortcuts, a
-  technique for combining static and dynamic analyses into fine-grained level on
-  the general abstract interpretation framework (Section 3).
-  We explain JavaScript related details formalized with core language of JavaScript as well (Section 4).
-\item We actualize our method by extending the existing JavaScript static analyzer SAFE 2.0.
-  We explain key techniques to synchronize two analyses (Section 5).
-\item We empirically evaluate our technique using the implementation (Section 6).
-  We find that using dynamic shortcut significantly increased performance for
-  benchmark programs enhanced with abstracted input that existing combined
-  analysis designs cannot handle.
+  \item We present a novel \textit{dynamic shortcut} for JavaScript static
+    analysis to leverage the high performance of dynamic analysis.  We also
+    formally define it with sealed symbolic execution and prove the soundness of
+    static analysis using dynamic shortcut.
+  \item We actualize dynamic shortcut technique in $\tool$, which is an
+    extension of an existing JavaScript static analyzer SAFE with a dynamic
+    analyzer Jalangi.
+  \item For empirical evaluation, we analyzed \inred{77} official tests of
+    \inred{Lodash 4} library with randomly abstracted values.  Our tool
+    accelerates \inred{X.X}x the static analysis on average.  Moreover, it
+    improves \inred{XX.XX}\% of analysis precision by using dynamic shortcut
+    instead of manual modeling for \inred{XX.X} opaque functions on average.
 \end{itemize}
 
-%There are almost 200 million active websites out of over 1.8 billion sites on the entire web.
-%https://www.internetlivestats.com/total-number-of-websites/
-%JavaScript is used as client-side programming language by 96.9\% of all the websites.
-%https://w3techs.com/technologies/history_overview/client_side_language/all/y
+In the remainder of this paper, Section~\ref{sec:motivation} explains the
+motivation of this work with a simple example.  Section~\ref{sec:formal}
+formalizes adding dynamic shortcuts on abstract interpretation.  We extended the
+formalization with JavaScript specific language features with a core language in
+Section~\ref{sec:javascript}.  Section~\ref{sec:implementation} describes
+key techniques to implement dynamic shortcuts for JavaScript static analysis.
+We describes evaluation result of our techniques with real-world benchmarks in
+Section~\ref{sec:eval}.  Section~\ref{sec:related} explains related works and
+Section~\ref{sec:conclusion} concludes.

### 2020-11-03 paper/pldi21/intro.tex
Minor change in intro
Revised motivation

@@
 if they are not dependent with meaning of abstract values.  For example, the
-third line of the following program passes the abstract value \jscode{absval}
-stored in \jscode{obj.p1} to the variable \jscode{x}:
+third line of the following program passes the abstract value \jscode{v} stored
+in \jscode{obj.p1} to the variable \jscode{x}:
 \begin{lstlisting}[style=myJSstyle,numbers=none]
-var absval = ... // an abstract value
-var obj = { p1: absval }, y = "p";
+var v = ... // an abstract value
+var obj = { p1: v }, y = "p";
 x = obj[y + 1];
 \end{lstlisting}
-Even though \jscode{obj} contains an abstract value \jscode{absval}, the
-semantics of the third line does not dependent with the meaning of
-\jscode{absval}.  To utilize this observation in dynamic shortcut, we introduce
-\textit{sealed symbolic execution}, which is an augmented concrete execution
-with sealed symbolic values.  We represent each abstract value as a sealed
-symbolic value, which is a symbolic value that throws an error when trying to
-access its actual meaning.  To evaluate our approach, we implemented $\tool$ by
-extending the existing JavaScript static analyzer SAFE with dynamic shortcut.
-For evaluation of $\tool$, we analyzed abstracted versions of \inred{77}
-official tests of \inred{Lodash 4} library.
+Even though \jscode{obj} contains an abstract value \jscode{v}, the semantics of
+the third line does not dependent with the meaning of \jscode{v}.  To utilize
+this observation in dynamic shortcut, we introduce \textit{sealed symbolic
+execution}, which is an augmented concrete execution with sealed symbolic
+values.  We represent each abstract value as a sealed symbolic value, which is a
+symbolic value that detects when trying to access its actual meaning.  To
+evaluate our approach, we implemented $\tool$ by extending the existing
+JavaScript static analyzer SAFE with dynamic shortcut.  For evaluation of
+$\tool$, we analyzed abstracted versions of \inred{77} official tests of
+\inred{Lodash 4} library.
 

### 2020-11-03 paper/pldi21/motivation.tex
Revised motivation

--- 2020-10-29 paper/pldi21/motivation.tex
@@
   if (!length) return [];
-  var args = Array(length - 1),
-      array = arguments[0],
+  var array = arguments[0],
+      args  = Array(length - 1),
       index = length;
@@
     args[index-1] = arguments[index];
-  return arrayPush(
-    isArray(array) ? copyArray(array) : [array],
+  return arrayPush(isArray(array) ?
+    copyArray(array) : [array],
     baseFlatten(args, 1));
@@
   \label{fig:example}
+  \vspace*{-1em}
 \end{figure}
 
-In this section, we first point out limitations that existing techniques face to
-analyze the real-world example described in Figure~\ref{fig:example}.
-We then show how our combined analysis increase the analysis scalability and
-precision through lazy concrete execution, seamlessly combined with the original
-static analysis.
+In this section, we will explain the motivation of the dynamic shortcut for
+JavaScript static analysis with real-world examples described in
+Figure~\ref{fig:example}.  We first describe their program behaviors and then
+explain how to utilize dynamic analysis during static analysis of them.
 
-We excerpt the \jscode{concat} function in Figure~\ref{fig:concat} from Lodash
-library~\cite{lodash} (v4.17.20), which is the most popular npm package~\footnote{https://www.npmjs.com/browse/depended}
-that \inred{124,562} npm packages depend on.
-The \jscode{concat} function creates a new array concatenating given arrays or
-values.
-It first checks the length of arguments in line 2-3. Then, it stores the first
-argument to \jscode{array} in line 5 and copies the remaining arguments to
-\jscode{args} in line 7-8.
-Finally, it creates a new array by copying the given array via \jscode{copyArray}
-or initializing with a single value in line 10, and pushes each element of
-\jscode{args} after flattening it via \jscode{baseFlatten} in line 11.
+For motivating examples, we excerpt the \jscode{concat} function in
+Figure~\ref{fig:concat} from Lodash library~\cite{lodash} (v4.17.20), which is
+the most popular npm package\footnote{https://www.npmjs.com/browse/depended}
+and \inred{124,562} npm packages have dependency with it.  The \jscode{concat}
+function creates a new array concatenating given arrays or values.  It first
+checks the length of arguments in line 1-3. Then, it stores the first argument
+to \jscode{array} in line 4 and copies the remaining arguments to \jscode{args} in
+line 5-8.  In line 9, it checks whether \jscode{array} is an array object with
+the built-in function \jscode{isArray}.  If so, it creates a new array by
+copying the given array via or initializing with a single value in line 10.
+Finally, it flattens \jscode{args} via \jscode{baseFlatten} and pushes the
+result to the new array in line 11.
 
-A low degree of context sensitivity tends to face spurious callee explosion
-during analyzing \jscode{concat} function.
-The analysis is not supposed to lose precision for the loop in line 7-8.
-Moreover, \jscode{baseFlatten} has a recursive call in a loop that is a
-traditional challenge for static analysis.
+For applications of Lodash, we excerpt two functions \jscode{changeCountry} in
+Figure~\ref{fig:changeCountry} and \jscode{getData} in Figure~\ref{fig:getData}
+from the \code{zoom.us}~\cite{zoom} site.  The website \code{zoom.us} is
+homepage of Zoom, which is a videotelephony software program developed by Zooom
+Video Communications and it is ranked as \inred{16th} popular web site according
+to Alexa\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.
 
-We excerpt two functions \jscode{changeCountry} in Figure~\ref{fig:changeCountry}
-and \jscode{getData} in Figure~\ref{fig:getData} from the \code{zoom.us}~\cite{zoom}
-site.
-The website \code{zoom.us} is ranked at \inred{16th} popular web site accroding
-to Alexa~\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.
-
-When the given arguments of a function invokation are concrete values, we can
-perform dynamic analysis instead of static analysis. For example, The
-\jscode{changeCountry} function is invoked when a country different with the
-current one is selected in registration of Zoom meetings.  When the ``United
-States of America'' (USA) is selected, it calls the \jscode{concat} function
-with two pre-defined concrete values as arguments to load USA state information
-in line 17-18.  The first argument is an array literal \jscode{[["Other",
-"Other"]]} and the second one is an array of pairs of abbreviations and names of
-USA states defined as follows:
+\paragraph{Dynamic shortcut with concrete values.}
+When the given arguments of a function are concrete values, we can perform
+dynamic analysis instead of static analysis. For example, the
+\jscode{changeCountry} function is invoked when a user selects another country
+on the drop-down list in the registration page.  It calls the \jscode{concat}
+function to update the drop-down list of states or provinces in 17-18.  However,
+when the user selects ``United States of America'' (USA), two arguments are
+pre-defined with deterministic values; the first one is an array literal
+\jscode{[["Other", "Other"]]} and the second one is an array of pairs of
+abbreviations and names of the states defined as follows:
 \begin{lstlisting}[style=myJSstyle,numbers=none]
@@
 object \jscode{\_}.  Thus, we could perform dynamic analysis by invoking the
-\jscode{concat} funciton with \jscode{\_} as \jscode{this} value and above two
+\jscode{concat} function with \jscode{\_} as \jscode{this} value and above two
 concrete values as arguments.  It increases performance of static analysis by
@@
 
-Dynamic analysis is still applicable using lazy concrete execution even if the
-arguments are not concrete values.  The \jscode{getData} function is another
-part to use \jscode{concat} function but we can only partially apply dynamic
-analysis in this case.  It is invoked when loading more Zoom events in
-``Webinars \& Events'' page.  At the first time, initial eight events are stored
-in \jscode{this.pastEvents}.  For each click of the ``Load More'' button, the
-\jscode{getData} sends a POST request to the server and receives additional
-event information \jscode{e} in line 24.  Then, eight events in
-\jscode{e.events} are appended to \jscode{this.pastEvents} using the
-\jscode{concat} function in line 27-28.  In this case, arguments are not
-deterministic but dependent on the given data from the server.  However, we know
-that the number of arguments are still deterministically defined as \jscode{2}
-and they are array objects.  Thus, we just invoke the funciton \jscode{concat}
-with \jscode{\_} as \jscode{this} value and two abstract arrays as arguments for
-dynamic analysis.  Then, dynamic analysis is successfully performed in line 2-8
-because it just checks the length of \jscode{arguments} and passes its elements
-to \jscode{array} and \jscode{args}.  Moreover, \jscode{isArray(array)} is also
-able to be evaluated using concrete semantics because we know that \code{array}
-is an abstract array.  Only copying via \jscode{copyArray}, flattening via
-\jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize the abstract
-semantics.  This is the core idea of lazy concrete execution to maximize the
-part of dynamic analysis during static analysis.
+\begin{figure}[t]
+  \begin{subfigure}{0.23\textwidth}
+    \[
+      \begin{array}{|c|c|}\hline
+        \text{Property} & \text{Value}\\\hline
+        \top & \symb_\jscode{evt}\\\hline
+        \jscode{"length"} & \symb_\jscode{int}\\\hline
+      \end{array}
+    \]
+    \vspace*{-1em}
+    \caption{\jscode{this.pastEvents}}
+    \label{fig:pastEvents}
+  \end{subfigure}
+  \begin{subfigure}{0.23\textwidth}
+    \[
+      \begin{array}{|c|c|}\hline
+        \text{Property} & \text{Value}\\\hline
+        \jscode{0} & \symb_\jscode{evt}\\\hline
+        \cdots & \cdots\\\hline
+        \jscode{7} & \symb_\jscode{evt}\\\hline
+        \jscode{"length"} & \jscode{8}\\\hline
+      \end{array}
+    \]
+    \vspace*{-1em}
+    \caption{\jscode{e.events}}
+    \label{fig:events}
+  \end{subfigure}
+  \vspace*{-1em}
+  \caption{Concrete objects for arguments with sealed symbolic values.}
+  \label{fig:sealed}
+  \vspace*{-1em}
+\end{figure}
 
-In the remaining section we formally define the combined analysis with lazy
-concrete execution in Section~\ref{sec:formal}.  Then, we explain how to define
-the combined analysis for JavaScript programs in Section~\ref{sec:javascript}.
+\paragraph{Dynamic shortcut with abstract values.}
+Dynamic analysis is still applicable using \textit{sealed symbolic execution}
+even if the arguments are not concrete values.  The \jscode{getData} function is
+invoked when clicking the ``Load More'' button to load more Zoom events in
+``Webinars \& Events'' page.  For each click, the \jscode{getData} sends a POST
+request to the server and receives additional event information \jscode{e} in
+line 24.  Then, eight events in \jscode{e.events} are appended to
+\jscode{this.pastEvents} using the \jscode{concat} function in line 27-28.
+However, the arguments of \jscode{concat} are not deterministic because 1) the
+event list stored in \jscode{this.pastEvents} is continuously grown for each
+load and 2) also each event stored in \jscode{e.events} are dependent on the
+data given from the server.
+
+To perform dynamic analysis with abstract values, we sealed the abstract values
+of arguments with symbolic values as described in Figure~\ref{fig:sealed}.  It
+contains two symbolic values $\symbevt$ and $\symbint$ that represent any event
+objects and integer values, respectively.  Then, dynamic analysis is
+successfully performed before copying \jscode{array} via \jscode{copyArray} in
+line 10.  First, \jscode{length} stores \jscode{2} and passes the length check
+in line 1-2. Then, \jscode{array} points to the same object of
+\jscode{this.pastEvents} in line 4, \jscode{args} stores an array with a
+single object stored in \jscode{e.events} in 5-8, and the \jscode{isArray}
+function returns \jscode{true} for \jscode{array} in line 9.  However, it fails
+to perform dynamic analysis for \jscode{copyArray} because the \jscode{length}
+property of \jscode{array} is the symbolic value $\symbint$.  Thus, the dynamic
+shortcut returns the analysis result and the static analyzer continues to
+analyze the program from line 10.  Then, only copying via \jscode{copyArray},
+flattening via \jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize
+the abstract semantics.  This is how to utilize sealed symbolic execution to
+maximize the part of dynamic analysis during static analysis.
+
+\paragraph{Dynamic shortcut for opaque functions.}
+
+The previous two examples also show that dynamic shortcut can improve the
+analysis precision and lessen the effort of modeling the opaque functions.
+In line 9, the \jscode{isArray} function is a JavaScript built-in library thus
+it is written in a native language of the host environment.  Thus, we need to
+manually model its behavior to statically analyze it.  Assume that we model the
+\jscode{isArray} function to return the top boolean value that denotes both of
+\jscode{true} and \jscode{false}.  If we perform static analysis with this
+modeling, both of true branch \jscode{copyArray(array)} and false branch
+\jscode{[array]} in line 10 are always analyzed while \jscode{[array]} is never
+reachable in the motivating examples.  However, with the dynamic shortcut, the
+analyzer utilizes the concrete semantics of \jscode{isArray}.  It returns more
+precise result \jscode{true} instead of the top boolean value and it is not
+necessary to model the \jscode{isArray} function for static analysis of
+motivating examples.

### 2020-11-03 paper/pldi21/javascript.tex
Added labels for each section
Added running example / Citation for TOPLAS'18
Changed: lazy concrete execution -> sealed symbolic execution
Revised Section 3,4

--- 2020-10-12 paper/pldi21/detail.tex
@@
-\section{Application: JavaScript}
+\section{Dynamic Shortcut for JavaScript}\label{sec:javascript}
 
@@
 first-class functions, open objects, and first-class property names, and define
-combined analysis of the core language.
+sealed symbolic execution of the core language for dynamic shortcut.
 
@@
 
-A program $\prog$ is a sequence of labelled instructions. An instruction $\inst$
+A program $\prog$ is a sequence of labeled instructions. An instruction $\inst$
 is an expression assignment, an object creation, a function call, a return
@@
 the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level
-environment address.  The function $\labnext$ returns the next lable of a
-given lable in the current program $\prog$.
+environment address.  The function $\labnext$ returns the next label of a
+given label in the current program $\prog$.
 
@@
 
-\subsection{Lazy Concrete Interpretation}
+\subsection{Sealed Symbolic Execution}
 

### 2020-11-03 paper/pldi21/shortcut.tex
Revised Section 3,4

--- 2020-10-29 paper/pldi21/combined.tex
@@
-\section{Combined Analysis}\label{sec:formal}
+\section{Dynamic Shortcut}\label{sec:formal}
 
-In this section, we formally define the combined analysis with sealed symbolic
-execution.  We extend the formalization of abstract interpretation and analysis
-sensitivity proposed by \citet{sens-toplas}.
+In this section, we formally define the dynamic shortcut with sealed symbolic
+execution.  We extend the formalization of abstract interpretation of
+\citet{abs-interp-1977, abs-interp-1992} and views-based analysis sensitivity of
+\citet{sens-toplas}.
 
@@
 The initial states are $\istset = \{ (\lab_0, 0) \}$ which means the program
-starts with the varible $\varx$ that stores 0 at $\lab_0$.  If the user input is
+starts with the variable $\varx$ that stores 0 at $\lab_0$.  If the user input is
 $-42$, the program is executed with the following trace:
@@
 semantics of a \textit{view transition} from a view $\view'$ to another view
-$\view$.  It should satsify the following condition for the soundness of the
+$\view$.  It should satisfy the following condition for the soundness of the
 analysis:
@@
 branches, respectively.  After executing statements $\varx = \varx$ and $\varx =
--\varx$, the variable $\varx$ stores symblic expressions $\symb$ and $-\symb$ at
+-\varx$, the variable $\varx$ stores symbolic expressions $\symb$ and $-\symb$ at
 $\lab_4$.  However, the sealed symbolic execution stops at $\lab_1$ as follows:
@@
 abstract value as a symbolic value in a result symbolic state.  Two converters
-convert given elements wihtout loss of information:
+convert given elements without loss of information:
 \[
@@
 
-\subsection{Combined Analysis}
+\subsection{Dynamic Shortcut}
 
@@
   \centering
-  \includegraphics[width=\linewidth]{img/combined-analysis}
+  \includegraphics[width=\linewidth]{img/dynamic-shortcut}
   \vspace*{-2em}
-  \caption{The diagram for the extended view transition in the combined analysis.}
+  \caption{The diagram for the extended view transition for dynamic shortcut.}
   \vspace*{-1em}
-  \label{fig:combined-analysis}
+  \label{fig:dynamic-shortcut}
 \end{figure}
 
-We define the \textit{combined analysis} of the abstract interpretation and the
-sealed symbolic execution.  In the combined analysis, we use the powerset of
-symbolic states as the domain $\combdom = \powerset{\symbstset}$, and extend the
-view transition as follows:
+We define the the abstract interpretation with \textit{dynamic shortcut}, which
+is a concrete semantics on sealed symbolic execution.  With dynamic shortcut,
+we use the powerset of symbolic states as the domain $\combdom =
+\powerset{\symbstset}$, and extend the view transition as follows:
 \[
@@
 \dot{\saconverter}(\combelem\mid_{\neg\checker})$.  The dot notation $\dot{f}$
-denotes the element-wise extended function of a function $f$.  The combined
-analysis performs one-step symbolic transition for each symbolic state that
-passes the filter $\checker$. On the other hand, it converts remaining symbolic
-states to the corresponding abstract states, merges them into a single abstract
-state, and performs the abstract one-step execution for the abstract state.
+denotes the element-wise extended function of a function $f$.  The abstract
+interpretation with dynamic shortcut performs one-step symbolic transition for
+each symbolic state that passes the filter $\checker$. On the other hand, it
+converts remaining symbolic states to the corresponding abstract states, merges
+them into a single abstract state, and performs the abstract one-step execution
+for the abstract state.
 
-For example, Figure~\ref{fig:combined-analysis} depicts the
-diagram of the view transition from $\view$ to $\view'$ in the combined
-analysis.  The element $\combelem$ in $\view$ consists of five symbolic states
+For example, Figure~\ref{fig:dynamic-shortcut} depicts the
+diagram of the extended view transition from $\view$ to $\view'$ for dynamic
+shortcut.  The element $\combelem$ in $\view$ consists of five symbolic states
 from $\nsymbst{1}$ to $\nsymbst{5}$.  The solid box denotes that the corresponding
@@
 a function level.  However, for the soundness and the termination of the
-combined analysis, it should satisfy the following condition:
-\begin{theorem}
-  The combined analysis has sound analysis result and terminates in a finite
-  time if its abstract semantics is sound and $\checker$ satisfies the following
-  condition:
+the abstract interpretation with dynamic shortcut, it should satisfy the
+following condition:
+\begin{theorem}\label{theorem:shortcut}
+  The abstract interpretation with dynamic shortcut is sound and terminates in a
+  finite time if its abstract semantics is sound and $\checker$ satisfies the
+  following condition:
   \[
@@
 \end{theorem}
-\inred{We prove that any combined analysis defined with the extended view
-transition satisfying the above condition always has sound analysis result and
-terminates in a finite time. Because of the page limitation, we omit the
-proof in this paper and include it in a companion report.}
+\inred{We proved Theorem~\ref{theorem:shortcut} using the Kleene's fixed-point
+theorem~\cite{kleene} with the finite height of abstract domains. Because of the
+page limitation, we omit the proof in this paper and include it in a companion
+report~\cite{report}.}

### 2020-11-09 paper/pldi21/eval.tex
Little writing for Evaluation

@@
 
+We developed $\tool$ to implement dynamic shortcut technique for JavaScript
+static analysis (Section~\ref{sec:javascript}).  Our tool is an extension of
+a state-of-the-art JavaScript static analyzer SAFE 2.0~\cite{safe2} with the
+dynamic analyzer Jalangi 2~\cite{jalangi}.
+
+\todo - Explain the detail of implementation
+
+We evaluated our tool based on the following research questions:
 \begin{itemize}
@@
 \end{itemize}
+We performed our experiments on an Ubuntu machine equipped with 4.2GHz Quad-Core
+Intel Core i7 and 64GB of RAM.
+
+\subsection{Analysis Speed-up}
+
+\begin{table}
+  \caption{Analysis of 306 tests of Lodash 4.}
+  \label{table:conc-test}
+  \vspace*{-1em}
+  \centering
+  \[
+    \begin{array}{c?r|r|r}
+      &
+      \multicolumn{1}{c|}{\text{SAFE (ms)}} &
+      \multicolumn{1}{c|}{\tool \text{ (ms)}} &
+      \multicolumn{1}{c}{\text{Speed Up}}\\\hline\hline
+      \text{avg.}       & \inred{168,399} & \inred{1,811} & \inred{116.38}\\\hline
+      \text{min.}       & \inred{ 37,095} & \inred{  514} & \inred{ 12.81}\\\hline
+      \text{max.}       & \inred{299,375} & \inred{2,986} & \inred{489.67}\\\hline\hline
+      \text{\# success} & \inred{    274} & \inred{  306} &
+    \end{array}
+  \]
+  \vspace*{-1em}
+\end{table}
+
+We targeted official 306 tests of Lodash 4\cite{lodash} used in motivating
+examples (Section~\ref{sec:motivation}).  Recent papers for JavaScript static
+analysis techniques~\cite{value-refinement, value-partitioning} also evaluated
+their techniques based on them.  Table~\ref{table:conc-test} shows that our tool
+successfully analyzes \inred{all 306} tests in \inred{514 ms} on average while
+SAFE only analyzes \inred{274} out of 306 tests within 5 minute timeout.  For
+\inred{274} tests analyzable by SAFE, our tool is at least \inred{12.81x}, at
+most \inred{489.67x}, and \inred{116.38x} on average faster than SAFE.
+
+However, all tests do not contain any non-deterministic values thus they could
+be analyzed via only dynamic analysis without static analysis.  In fact, our
+tool covers all program parts via only one dynamic shortcut without using
+abstract semantics of static analysis.  Thus, we modified 306 official tests to
+include abstract values by lifting each literal to the corresponding typed
+value.  For example, the numerical literal \jscode{42} will be lifted to the
+abstract value $\top_{\code{num}}$, which represents the whole numerical values.
+
+% abstract versions
+% of official 
+% 
+% performs only dynamic shortcut
+% 
+% by only performing dynamic shortcut for
+% whole program points.  Moreover, they analyzed 
+% 
+% , which is a modern JavaScript library
+% delivering modularity, performance, and extras.  It is the first 
+% 
+% 
+% For motivating examples, we excerpt the \jscode{concat} function in
+% Figure~\ref{fig:concat} from Lodash library~\cite{lodash} (v4.17.20), which is
+% the most popular npm package\footnote{https://www.npmjs.com/browse/depended}
+% and \inred{124,562} npm packages have dependency with it.  The \jscode{concat}
+%

### 2020-11-14 paper/pldi21/implementation.tex
Section Implementation

@@
 
-\todo
+We have implemented the dynamic shortcut for JavaScript static analysis
+presented in Section~\ref{sec:javascript} in a prototype implementation called
+$\tool$.  The tool is an extension of an existing state-of-the-art JavaScript
+static analyzer SAFE~\cite{safe, safe2} with a dynamic analyzer
+Jalangi~\cite{jalangi}, and it is open source and available online~\footnote{The
+URL of the tool is anonymized due to a double-blind review process.}.  In this
+section, we introduce challenges and solutions when implementing dynamic
+shortcut on existing JavaScript analyzers.
+
+\paragraph{Sealed Symbolic Values.}
+The main challenge of implementing dynamic shortcut is to support the sealed
+symbolic execution on the existing JavaScript engine.  We leverage the \jscode{Proxy}
+object introduced in ECMAScript 6 (2015, ES6)~\cite{es6}, which allows
+developers to handle the internal behaviors of specific objects (such as
+property reads and writes, implicit conversions, etc.).  When the dynamic
+analyzer constructs the execution environments at the start of the dynamic
+shortcut, it creates revoked \jscode{Proxy} objects to represent abstract values
+via the following \jscode{generateSymbol} function:
+\begin{lstlisting}[style=myJSstyle]
+function generateSymbol() {
+  const r = Proxy.revocable(function() {}, {});
+  r.revoke();
+  return r.proxy;
+}
+var x = generateSymbol();
+var y = x;
+var z = x + 1;
+\end{lstlisting}
+The function creates a sealed symbol as a revocable proxy object with a dummy
+function object without any handlers and revokes it by
+\jscode{revocable.revoke()} to not allow any access of the symbol.  Thus, the
+variable \jscode{y} successfully points to the same symbol stored in \jscode{x}
+but the program throws a \jscode{TypeError} in line 8 because \jscode{x + 1}
+requires the actual value of the symbol.  Using this idea, we successfully
+extend the JavaScript engine to support a sealed symbolic execution.
+
+\paragraph{Abstract Locations for Objects.}
+During dynamic analysis, each JavaScript object should be designated by the
+corresponding abstract location used in the static analysis.  In this paper, we
+define abstract locations using the allocation site
+abstraction~\cite{allocation-site} with heap cloning~\cite{heap-cloning} for
+each abstract context in the static analyzer.  Thus, we instrument the given
+JavaScript program to annotate each object created during dynamic analysis with
+its allocation site and context information.  After the sealed symbolic
+execution, the dynamic analyzer collects the objects based on their annotated
+information for each abstract location.
+
+\paragraph{Optimizations.}
+To perform dynamic shortcut, the static analyzer should communicate with the
+dynamic analyzer by passing the current abstract state and receiving the final
+result of the sealed symbolic execution.  When abstract states are massive, it
+is burden to send them as they stand.  Thus, we perform mark-and-sweep garbage
+collection to remove unreachable information in the current abstract state.
+Moreover, the abstract values are converted to the sealed symbolic values and
+their contents are not necessary in the dynamic analysis.  Thus, we replace
+abstract values with their unique identifiers and stores the table from
+identifiers to abstract values before sending the abstract state
+from the static analyzer.  Thus, the dynamic analyzer only receives identifiers
+of abstract values and wrap them as \jscode{Proxy} objects.  After finishing the
+sealed symbolic execution, the static analyzer recovers the abstract values in
+the result abstract state using the table.
+
+\paragraph{Termination.}
+To guarantee the termination of static analysis with dynamic shortcut, the
+filter $\checker$ should pass the state $\symbst$ only when it terminates in a
+bound time $N$.  Since it is difficult to statically check its termination,
+we just performs the sealed symbolic execution with a time limit.  When it runs
+over the time limit, we treat it fails to pass $\checker$, otherwise we utilizes
+the result of the execution.  In the experiments, we set the time limit as
+\inred{5 seconds} for each sealed symbolic execution.
+
+% \paragraph{Function-Level Dynamic Shortcut.}
+% The dynamic shortcut is activated when the current abstract state passes the
+% filter $\checker$.  If the filter tolerantly admits the dynamic shortcut, the
+% analysis suffers from the frequent communication between static and dynamic
+% analyzers.  To diminish the burden of communication, we only activate new
+% dynamic shortcut in function entries thus $\tool$ supports only
+% \textit{function-level} dynamic shortcut.  Moreover, the filter $\checker$
+% should pass only when the given abstract state terminates in a bound time.
+% Since it is difficult to staticaly check its termination, we just performs the
+% sealed symbolic exeuction with a time limit and we use \inred{5} minutes time
+% limit for experiments.  Thus, a sealed symbolic execution introduced by a
+% function \jscode{f} terminates when it 1) meets the exit of the function
+% \jscode{f}, 2) accesses the inside of sealed symbolic values, or 3) runs over
+% the time limit.
+
+% \paragraph{Communication between Analyzers.}
+% To perform dynamic shortcut, the static analyzer should communicate with the the
+% dynamic analyzer by passing the current abstract state and receiving the final
+% result of the sealed symbolic execution.  However, The static analyzer SAFE and
+% the dynamic analyzer Jalangi are implemented in different languages Scala and
+% JavaScript, respectively.  To overcome the difference, we represent abstract
+% states as JSON objects and communicate between analyzers by passing them.  For
+% each dynamic shortcut, Jalangi constructs the execution environments based on
+% the given JSON object and executes the dynamic analysis from the target program
+% points.  After finishing the sealed symbolic execution, it sends a newly
+% constructed JSON object to SAFE to update the abstract states in the function
+% exit point.

### 2020-11-15 paper/pldi21/related.tex
Added labels for each section
Related Work

@@
-\section{Related Work}
+\section{Related Work}\label{sec:related}
 
-\todo
+Several researchers have introduced analysis technique to utilize dynamic
+analysis for static analysis in three different ways: combined analysis,
+automatic modeling, and pruning states.
 
-\subsection{Combined Analysis}
+\paragraph{Combined Analysis}
 
-\begin{itemize}
-  \item Concerto: a framework for combined concrete and abstract
-    interpretation~\cite{concerto}
-  \item Battles with false positives in static analysis of JavaScript web
-    applications in the wild~\cite{battles}
-  \item EventHandler-Based Analysis Framework for Web Apps Using Dynamically
-    Collected States~\cite{eha}
-  \item Automatic Modeling of Opaque Code for JavaScript Static
-    Analysis~\cite{opaque-model}
-  \item Mimic: Computing models for opaque code~\cite{mimic}
-\end{itemize}
+The most related previous work is the combined analysis that utilizes dynamic
+analysis during Java static analysis introduced by \citet{concerto}.  They
+proved that their combined analysis is sound and showed that it could
+significantly improve the precision and performance of Java static analysis by
+evaluating their tool, \concerto.  However, their approach have several
+limitations compared to the dynamic shortcut.  First, they syntactically divides
+a given program to \textit{applications} parts for static analysis and
+\textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
+freely switching between static and dynamic and even impossible to perform both
+of static and dynamic analysis to the same program part in different contexts.
+Besides, they introduced \textit{mostly-concrete interpretation} similar with
+our sealed symbolic execution.  However, it supports only a special
+\textit{unknown} value that represents any possible value.  Thus, it cannot
+preserves the precision of complex abstract domains~\cite{safe, tajs, regex,
+weaklySPE} frequently used in JavaScript static analysis.  In the other hand,
+the sealed symbolic execution automatically detects whether the abstract
+semantics for abstract values.  Finally, \concerto preserves the soundness when
+the program satisfies the \textit{state separation hypothesis}.  They assume
+that states of application and framework parts do not interrogated or
+manipulated by each other.  While it is reasonable for static analysis of Java
+applications using external libraries, the assumption is not satisfied for
+JavaScript programs in general.  Unlike their approach, our approach does not
+have any assumption between static and dynamic analysis parts.
 
-\subsection{Abstract Counting}
+\paragraph{Automatic Modeling}
+For static analysis of JavaScript programs, modeling behaviors of built-in
+libraries or host-dependent functions is required because they are opaque
+codes.  Since manual modeling is error-prone, tedious, and labor-intensive,
+several researchers~\cite{safewapi, safets} utilize type information to
+automatically model their behaviors.  However, type information is too imprecise
+to reflect the detailed semantics and is difficult to represent the
+side-effects.  To alleviate the problem, \citet{mimic} introduced the technique
+to infer JavaScript codes for opaque codes using concrete execution.  They
+captured the effects of opaque codes on user objects by collecting partial
+execution traces and synthesized JavaScript codes based on the extracted
+behaviors.  They also leveraged ES6 \jscode{Proxy} objects to capture the
+effects on user objects.  Instead of synthesizing JavaScript codes,
+\citet{opaque-model} presented a \textit{Sample-Run-Abstract (SRA)} approach for
+on-demand modeling thus they focused on the current abstract state during static
+analysis.  It first \textit{samples} concrete states in a well-distributed way,
+\textit{runs} each sampled state on a JavaScript engine, and \textit{abstract}
+executions results.  However, all of previous works sacrifice the soundness of
+static analysis.  On the other hand, while the dynamic shortcut is not
+applicable for all invocation of opaque functions, it is sound if it is
+applicable.
 
-\begin{itemize}
-  \item Improving flow analyses via $\Gamma$CFA: Abstract garbage collection and
-    counting~\cite{abstract-gc-counting}
-  \item Revisiting recency abstraction for JavaScript: towards an intuitive,
-    compositional, and efficient heap abstraction~\cite{revisit-recency}
-\end{itemize}
+\paragraph{Pruning Analysis Scopes}
+Another approach to utilize dynamic analysis for JavaScript static analysis is
+to prune the scope of analysis.  \citet{blended} introduced \textit{blended
+taint analysis} that specializes JavaScript dynamic language features such as
+dynamic code generation (e.g. \jscode{eval}) or variadic function calls.  They
+first performs dynamic analysis to collect traces with concrete values used in
+dynamic language features and restrict the semantics of features based on the
+collected traces during static analysis.  \citet{battles, eha} utilizes three
+different points to reduce analysis scopes: initial states, dynamically loaded
+files, and event handlers.  They dumped the initial states from a specific web
+browser to focus on analyzing the behaviors of web browsers running on the
+browser.  Then, they collected paths of dynamically loaded files via concrete
+executions and utilized the path information in static analysis.  For event
+handlers, they intentionally analyzed partial execution flows using concrete
+user events.  They collected concrete states for each entry of event handler
+during dynamic analysis, merged them to a single abstract state, and analyzed
+the event handler with the abstract state.  Unfortunately, all of them does not
+preserve soundness of static analysis unlike the dynamic shortcut.
 
-\subsection{Access Analysis}
+% \subsection{Abstract Counting}
+% 
+% \begin{itemize}
+%   \item Improving flow analyses via $\Gamma$CFA: Abstract garbage collection and
+%     counting~\cite{abstract-gc-counting}
+%   \item Revisiting recency abstraction for JavaScript: towards an intuitive,
+%     compositional, and efficient heap abstraction~\cite{revisit-recency}
+% \end{itemize}
 
-\begin{itemize}
-  \item Access Analysis-Based Tight Localization of Abstract
-    Memories~\cite{func-local}
-  \item Design and implementation of sparse global analyses for C-like
-    languages~\cite{sparse}
-\end{itemize}
+% \subsection{Access Analysis}
+% 
+% \begin{itemize}
+%   \item Access Analysis-Based Tight Localization of Abstract
+%     Memories~\cite{func-local}
+%   \item Design and implementation of sparse global analyses for C-like
+%     languages~\cite{sparse}
+% \end{itemize}

### 2020-11-15 paper/pldi21/related.tex
Slightly updated Relate Work

@@
 \textit{unknown} value that represents any possible value.  Thus, it cannot
-preserves the precision of complex abstract domains~\cite{safe, tajs, regex,
-weaklySPE} frequently used in JavaScript static analysis.  In the other hand,
-the sealed symbolic execution automatically detects whether the abstract
+preserves the precision of complex abstract domains~\cite{revisit-recency,
+regex, weaklySPE} frequently used in JavaScript static analysis.  On the other
+hand, the sealed symbolic execution automatically detects whether the abstract
 semantics for abstract values.  Finally, \concerto preserves the soundness when

### 2020-11-15 paper/pldi21/conclusion.tex
Conclusion

@@
 
-\todo
+We have presented a novel technique \textit{dynamic shortcut} for JavaScript
+static analysis.  It could significantly accelerate the JavaScript static
+analysis by freely leveraging high performance of dynamic analysis for the
+concretely executable program parts.  To maximize the usage of dynamic analysis,
+we augmented the concrete execution to \textit{sealed symbolic execution} with
+symbolic values for abstract values required abstract semantics.  We formally
+defined the static analysis with dynamic shortcut using sealed symbolic execution
+and proved its soundness on the formalization.  We developed $\tool$ as a
+prototype implementation of the dynamic shortcut by combining state-of-the-art
+static and dynamic analyzers SAFE and Jalangi.  Our tool accelerates the speed
+of static analysis \inred{X.X}x for original tests and \inred{X.X}x for
+abstracted tests of Lodash 4 library.  Moreover, it improves \inred{XX.XX}\% of
+analysis precision by using dynamic analysis instead of static analysis for
+\inred{XX.X} opaque functions on average.

### 2020-11-16 paper/pldi21/eval.tex
Writing eval.tex...

--- 2020-11-02 paper/pldi21/eval.tex
@@
 
+We evaluated our tool based on the following research questions:
 \begin{itemize}
@@
 \end{itemize}
+We targeted the official 306 tests of Lodash 4
+(v.4.17.20)\footnote{https://github.com/lodash/lodash/blob/4.17.20/test/test.js}
+used in motivating examples (Section~\ref{sec:motivation}).  The most recent
+papers for JavaScript static analysis techniques~\cite{value-refinement,
+value-partitioning} also evaluated their techniques based on them.
+Among them, we filtered out \inred{37} tests including JavaScript language
+features SAFE does not support, such as dynamic code generation using
+\jscode{Function}, getter/setter, and browser specific features
+(e.g. $\jscode{__proto__}$).  Thus, we only targeted \inred{269} out of 306
+tests for the evaluation.  We performed our experiments on an Ubuntu machine
+equipped with 4.2GHz Quad-Core Intel Core i7 and 64GB of RAM.
+
+\subsection{Analysis Speed-up}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{img/conc-analysis-speed}
+  \vspace*{-1.5em}
+  \caption{Analysis time for Lodash 4 tests with (DS) and without the dynamic
+  shortcut (no-DS) with 5 minutes time limit}
+  \label{fig:conc-analysis-speed}
+  \vspace*{-1.5em}
+\end{figure}
+
+To evaluate the effectiveness of the dynamic shortcut, we performed static
+analysis for \inred{269} Lodash 4 tests with and without dynamic shortcut.
+Figure~\ref{fig:conc-analysis-speed} depicts the box plot chart for their
+analysis time and for speed up after applying the dynamic shortcut.  While the
+base analysis (no-DS) finished \inred{199} out of \inred{269} tests within 5
+minutes, our tool finished all tests with the dynamic shortcut (DS).  For
+\inred{199} tests analyzable by both analyses, the analysis (no-DS) took
+\inred{168.4} seconds and \inred{12.2} seconds on average without dynamic
+shortcut (no-DS) and with dynamic shortcut (DS), and the dynamic shortcut
+accelerates \inred{20.16}\textsf{x} the static analysis on average.
+
+Unfortunately, since most of Lodash 4 tests use concrete values instead of
+non-deterministic user inputs, they could be analyzed via a few number of
+dynamic shortcut.  In fact, among \inred{269} tests, \inred{230} tests analyzed
+via a single usage of dynamic shortcut without using abstract semantics.
+However, the arguments of library functions might include non-deterministic user
+inputs in the real-world JavaScript programs.  Thus, we modified Lodash 4
+official tests with abstract values to mimic the use patterns of library
+functions.  We randomly selected literals and replace subset of them to their
+corresponding typed abstract values.  For example, if we pick a numerical
+literal \jscode{42}, we modified it to the abstract numeric value
+$\top_{\code{num}}$, which represents the all numerical values.  For the
+remaining section, we evaluated our tool based on the randomly abstracted tests
+of Lodash 4.
+
+\subsection{Precision Improvement}
+
+\subsection{Opaque Function Coverage}

### 2020-11-16 paper/pldi21/eval.tex
Dummy images

@@
 \section{Evaluation}\label{sec:eval}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{img/conc-analysis-time}
+  \vspace*{-1.5em}
+  \caption{Analysis time for Lodash 4 tests with (DS) and without (no-DS) the
+  dynamic shortcut within 5 minutes.}
+  \label{fig:conc-analysis-time}
+  \vspace*{-1.5em}
+\end{figure}
 
@@
   \centering
-  \includegraphics[width=\linewidth]{img/conc-analysis-speed}
-  \vspace*{-1.5em}
-  \caption{Analysis time for Lodash 4 tests with (DS) and without the dynamic
-  shortcut (no-DS) with 5 minutes time limit}
-  \label{fig:conc-analysis-speed}
+  \begin{subfigure}[t]{0.48\textwidth}
+    \vspace*{-1em}
+    \includegraphics[width=\linewidth]{img/abs-analysis-time}
+    \caption{Analysis time and speed up.}
+    \label{fig:abs-time-speed}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.48\textwidth}
+    \includegraphics[width=\linewidth]{img/abs-analysis-ratio}
+    \caption{Analysis time ratio.}
+    \label{fig:abs-analysis-ratio}
+  \end{subfigure}
+  \caption{Analysis time for abstracted Lodash 4 tests with (DS) and without
+  (no-DS) the dynamic shortcut within 5 minutes.}
+  \label{fig:abs-analysis-time}
   \vspace*{-1.5em}
@@
 analysis for \inred{269} Lodash 4 tests with and without dynamic shortcut.
-Figure~\ref{fig:conc-analysis-speed} depicts the box plot chart for their
+Figure~\ref{fig:conc-analysis-time} depicts the box plot chart for their
 analysis time and for speed up after applying the dynamic shortcut.  While the
@@
 shortcut (no-DS) and with dynamic shortcut (DS), and the dynamic shortcut
-accelerates \inred{20.16}\textsf{x} the static analysis on average.
+accelerates \inred{20.16}\textsf{x} the static analysis on average.  Only for
+one test using $\jscode{_.sample}$ (a Lodash 4 library that randomly samples a
+value from a given array), the static analysis using dynamic shortcut had
+\inred{0.81}\textsf{x} speed of the base analysis because of the frequent use of
+dynamic shortcut (\inred{24} times).
 
@@
 non-deterministic user inputs, they could be analyzed via a few number of
-dynamic shortcut.  In fact, among \inred{269} tests, \inred{230} tests analyzed
+dynamic shortcut.  In fact, among \inred{269} tests, \inred{262} tests analyzed
 via a single usage of dynamic shortcut without using abstract semantics.
@@
 literal \jscode{42}, we modified it to the abstract numeric value
-$\top_{\code{num}}$, which represents the all numerical values.  For the
+$\top_{\code{num}}$, which represents the all numerical values.  In the
 remaining section, we evaluated our tool based on the randomly abstracted tests
@@
 
+\todo
+
 \subsection{Precision Improvement}
 
+\begin{figure}
+  \centering
+  \begin{subfigure}[t]{0.48\textwidth}
+    \vspace*{-1em}
+    \includegraphics[width=\linewidth]{img/precision-func}
+    \caption{Reachable functions.}
+    \label{fig:precision-func}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.48\textwidth}
+    \includegraphics[width=\linewidth]{img/precision-branch}
+    \caption{Reachable branches.}
+    \label{fig:abs-analysis-ratio}
+  \end{subfigure}
+  \caption{The comparison of analysis precision with (DS) and without (no-DS)
+  dynamic shortcut}
+  \label{fig:precision}
+  \vspace*{-1.5em}
+\end{figure}
+
+\todo
+
 \subsection{Opaque Function Coverage}
+
+\todo

### 2020-11-17 paper/pldi21/related.tex
Minor change in related.tex
Added dynamic determinacy analysis in related work.

@@
 hand, the sealed symbolic execution automatically detects whether the abstract
-semantics for abstract values.  Finally, \concerto preserves the soundness when
-the program satisfies the \textit{state separation hypothesis}.  They assume
-that states of application and framework parts do not interrogated or
-manipulated by each other.  While it is reasonable for static analysis of Java
-applications using external libraries, the assumption is not satisfied for
+semantics are required for abstract values.  Finally, \concerto preserves the
+soundness when the program satisfies the \textit{state separation hypothesis}.
+They assume that states of application and framework parts do not interrogated
+or manipulated by each other.  While it is reasonable for static analysis of
+Java applications using external libraries, the assumption is not satisfied for
 JavaScript programs in general.  Unlike their approach, our approach does not
@@
 Another approach to utilize dynamic analysis for JavaScript static analysis is
-to prune the scope of analysis.  \citet{blended} introduced \textit{blended
-taint analysis} that specializes JavaScript dynamic language features such as
-dynamic code generation (e.g. \jscode{eval}) or variadic function calls.  They
-first performs dynamic analysis to collect traces with concrete values used in
-dynamic language features and restrict the semantics of features based on the
+to prune the scope of analysis.  \citet{determinacy} proposed dynamic
+determinacy analysis that infer determinacy facts via concrete executions that a
+variable or expression at a given location holds the same value in all possible
+execution of the program.  They specialized target source codes with determinacy
+facts so that static analyses could benefit from eliminations of dynamic code
+generation (e.g. \jscode{eval}) and constant property names.  \citet{blended}
+introduced \textit{blended taint analysis} that specializes JavaScript dynamic
+language features such as dynamic code generation or variadic function calls.
+They first performs dynamic analysis to collect traces with concrete values used
+in dynamic language features and restrict the semantics of features based on the
 collected traces during static analysis.  \citet{battles, eha} utilizes three

### 2020-11-17 paper/pldi21/implementation.tex
Added some more descriptions on Proxy objects.

@@
 The main challenge of implementing dynamic shortcut is to support the sealed
-symbolic execution on the existing JavaScript engine.  We leverage the \jscode{Proxy}
-object introduced in ECMAScript 6 (2015, ES6)~\cite{es6}, which allows
-developers to handle the internal behaviors of specific objects (such as
-property reads and writes, implicit conversions, etc.).  When the dynamic
-analyzer constructs the execution environments at the start of the dynamic
-shortcut, it creates revoked \jscode{Proxy} objects to represent abstract values
-via the following \jscode{generateSymbol} function:
+symbolic execution on the existing JavaScript engine.  To represent an abstract
+value, we leverage the \jscode{Proxy} object introduced in ECMAScript 6
+(2015, ES6)~\cite{es6}, which allows developers to handle the internal behaviors
+of specific objects (such as property reads and writes, implicit conversions,
+etc.).  We are inspired by \textsc{Mimic}~\cite{mimic} using \jscode{Proxy} to
+capture accesses from the inside of opaque functions.  When the dynamic analyzer
+constructs the execution environments at the start of the dynamic shortcut, it
+creates revoked \jscode{Proxy} objects to represent each abstract values via the
+following \jscode{generateSymbol} function:
 \begin{lstlisting}[style=myJSstyle]
@@
 function object without any handlers and revokes it by
-\jscode{revocable.revoke()} to not allow any access of the symbol.  Thus, the
-variable \jscode{y} successfully points to the same symbol stored in \jscode{x}
-but the program throws a \jscode{TypeError} in line 8 because \jscode{x + 1}
-requires the actual value of the symbol.  Using this idea, we successfully
-extend the JavaScript engine to support a sealed symbolic execution.
+\jscode{revocable.revoke()} to not allow any access of the symbol.  The revoked
+object throws a \jscode{TypeError} when the object faces 13 kinds of operations
+so we can determine whether or not the seal is open.  For example, the variable
+\jscode{y} successfully points to the same symbol stored in \jscode{x} but the
+program throws the \jscode{TypeError} in line 8 because \jscode{x + 1} requires
+the actual value of the symbol.  Moreover, we instrument unary and binary
+operations on Jalangi to fully cover accesses on the symbol beyond 13 traps
+provided by \jscode{Proxy}.  Using this idea, we successfully extend the
+JavaScript engine to support a sealed symbolic execution.
 

### 2020-11-17 paper/pldi21/eval.tex
Prepared the excel file for figures
Writing Evaluation / Table 1

@@
   \vspace*{-1.5em}
-  \caption{Analysis time for Lodash 4 tests with (DS) and without (no-DS) the
-  dynamic shortcut within 5 minutes.}
+  \caption{Analysis time for Lodash 4 \textit{original} tests without (no-DS)
+  and with (DS) the dynamic shortcut within 5 minutes.}
   \label{fig:conc-analysis-time}
@@
   \centering
-  \begin{subfigure}[t]{0.48\textwidth}
-    \vspace*{-1em}
   \includegraphics[width=\linewidth]{img/abs-analysis-time}
-    \caption{Analysis time and speed up.}
-    \label{fig:abs-time-speed}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.48\textwidth}
-    \includegraphics[width=\linewidth]{img/abs-analysis-ratio}
-    \caption{Analysis time ratio.}
-    \label{fig:abs-analysis-ratio}
-  \end{subfigure}
-  \caption{Analysis time for abstracted Lodash 4 tests with (DS) and without
-  (no-DS) the dynamic shortcut within 5 minutes.}
+  \vspace*{-1.5em}
+  \caption{Analysis time for Lodash 4 \textit{abstracted} tests without (no-DS)
+  and with (DS) the dynamic shortcut within 5 minutes.}
   \label{fig:abs-analysis-time}
@@
 Figure~\ref{fig:conc-analysis-time} depicts the box plot chart for their
-analysis time and for speed up after applying the dynamic shortcut.  While the
-base analysis (no-DS) finished \inred{199} out of \inred{269} tests within 5
-minutes, our tool finished all tests with the dynamic shortcut (DS).  For
-\inred{199} tests analyzable by both analyses, the analysis (no-DS) took
-\inred{168.4} seconds and \inred{12.2} seconds on average without dynamic
+analysis time and for speed up after applying the dynamic shortcut in a
+logarithmic scale.  While the base analysis (no-DS) finished \inred{199} out of
+\inred{269} tests within 5 minutes, our tool finished all tests with the dynamic
+shortcut (DS).  For \inred{199} tests analyzable by both analyses, the analysis
+took \inred{168.4} seconds and \inred{12.2} seconds on average without dynamic
 shortcut (no-DS) and with dynamic shortcut (DS), and the dynamic shortcut
@@
 
-\todo
+For abstracted tests, the dynamic shortcut successfully accelerates the static
+analysis.  Figure~\ref{fig:abs-analysis-time} shows the analysis time for the
+abstracted tests in a logarithmic scale.  Among \inred{269} abstracted tests,
+the base analysis (no-DS) finished \inred{82} tests within 5 minutes.  On the
+other hand, the analysis using dynamic shortcut (DS) finished \inred{219} tests.
+For \inred{82} tests analyzable by both analyses, the analyses took
+\inred{168.4} seconds and \inred{12.2} seconds on average without dynamic
+shortcut (no-DS) and with dynamic shortcut (DS), and the dynamic shortcut
+accelerates \inred{20.16}\textsf{x} the static analysis on average.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{img/abs-analysis-ratio}
+  \vspace*{-1.5em}
+  \caption{Time ratio of the finished analysis with dynamic shortcut for
+  \inred{219} Lodash 4 \textit{abstracted} tests.}
+  \label{fig:abs-analysis-ratio}
+  \vspace*{-1.5em}
+\end{figure}
+
+For \inred{219} abstracted tests successfully analyzed with the dynamic
+shortcut, communication costs between static and dynamic analysis grew
+relatively to the number of dynamic shortcuts.  To communicate with the
+dynamic analyzer, the static analysis should dump the current abstract state,
+send it to the dynamic analyzer, receive the result from the dynamic analysis,
+and apply the given update information to the abstract state.  Thus, the
+communication costs will increase dependent on the number of dynamic shortcuts.
+Figure~\ref{fig:abs-analysis-ratio} shows the time ratio of dynamic and static
+analysis parts with communication costs in total analysis time.  On average, the
+dynamic analysis occupied \inred{63.30}\%, communication \inred{9.52}\%, and
+static analysis \inred{27.17}\% in total analysis time.  If the dynamic
+shortcuts are performed less than 10 times, the ratio of communication in total
+analysis time is \inred{9.50\%} on average.  The more dynamic shortcuts
+performed, the more communication cost is required.  When the number is
+between 41 and 50, the ratio of average communication cost is rised to
+\inred{10.65\%} in the total analysis time.
 
 \subsection{Precision Improvement}
+
+To evaluate the precision improvement of dynamic shortcut, we used two different
+metrics to measure the precision of the analysis results: 1) the number of false
+alarms for assertions in tests and 2) the number of branch covered by analysis.
+Figure~\ref{fig:precision} depicts the comparison of analysis precision without
+(no-DS) and with (DS) dynamic shortcut using two different metrics.
+
+Lodash 4 official tests check the assertions based on
+QUnit\footnote{https://qunitjs.com/}, which is a powerful, easy-to-use
+JavaScript testing framework.  Since all assertions in each test are passed in
+the concrete execution, any assertion failures during static analysis should be
+false alarms.  Although we analyzed \textit{abstracted} Lodash 4 tests, the
+number of assertion failures during static anlysis could be a metric of
+imprecision of the analysis.  Figure~\ref{fig:precision-fail} shows the number
+of assertion failures in each test analyzable by both analysis with and
+without dynamic shortcut.  The $x$- and $y$-axis denote the analysis without
+(no-DS) and with (DS) dynamic shortcut and each $\times$ mark denotes each test.
+The top and bottom dotted lines denote the worst and best precision improvement,
+and the middle solid line denotes the average improvement.  Thus, dynamic
+shortcut reduces assertion failures to at least \inred{1.00}\textsc{x}, at most
+\inred{0.54}\textsc{x}, and \inred{0.92}x on average.
+
+Another metric to measure the precision of static analysis is the number of
+branches covered during analysis.  If the static analysis is sound, the more
+precise analysis covers the less number of branches.  In the similar way with
+the number of assertion failures, Figure~\ref{fig:precision-branch} depicts the
+the comparison of the number of branches during static analysis without (no-DS)
+and with (DS) dynamic shortcut.  In the view point of the branch coverage,
+dynamic shortcut successfully cut down the number of covered branches at least
+\inred{0.81}\textsc{x}, at most \inred{0.51}\textsc{x}, and
+\inred{0.68}\textsc{x} on average.
 
@@
   \begin{subfigure}[t]{0.48\textwidth}
-    \vspace*{-1em}
-    \includegraphics[width=\linewidth]{img/precision-func}
-    \caption{Reachable functions.}
-    \label{fig:precision-func}
+    \includegraphics[width=\linewidth]{img/precision-fail}
+    \vspace*{-1.5em}
+    \caption{\# Failed Assertions.}
+    \label{fig:precision-fail}
   \end{subfigure}
@@
     \includegraphics[width=\linewidth]{img/precision-branch}
-    \caption{Reachable branches.}
-    \label{fig:abs-analysis-ratio}
+    \vspace*{-1.5em}
+    \caption{\# Covered Branches.}
+    \label{fig:precision-branch}
   \end{subfigure}
-  \caption{The comparison of analysis precision with (DS) and without (no-DS)
-  dynamic shortcut}
+  \vspace*{-1em}
+  \caption{The comparison of analysis precision without (no-DS) and with (DS)
+  dynamic shortcut for \inred{82} \textit{abstracted} tests analyzable by both
+  analyses}
   \label{fig:precision}
@@
 
-\todo
-
 \subsection{Opaque Function Coverage}
 
+\begin{table*}
+  \centering
+  \scriptsize
+  \[
+    \begin{array}{c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}}
+      \myhead
+      \mysucc{2}{Boolean}   {Boolean}         {214}{214}{100} & \mydata{1}{}            {new Object}        {214}{214}{100} & \mymult{2}{Number}      {valueOf}       {214}{214}{100} \mylineff
+      \mydata{1}{}          {new Boolean}     {214}{214}{100} & \mydata{1}{}            {getPrototypeOf}    {214}{214}{100} & \myname{1}{.prototype}                                  \mylinetft
+      \mydata{1}{Array}     {isArray}         {214}{214}{100} & \mydata{1}{}            {create}            {214}{214}{100} & \mymult{2}{RegExp}      {toString}      {214}{214}{100} \mylinetf
+      \mydata{1}{}          {toString}        {214}{214}{100} & \mydata{1}{Object}      {preventExtensions} {214}{214}{100} & \myname{1}{.prototype}                                  \mylinefft
+      \mydata{1}{}          {toLocaleString}  {214}{214}{ 90} & \mydata{1}{}            {isFrozen}          {214}{214}{100} & \mydata{2}{String}      {String}        {214}{214}{100} \mylinefff
+      \mydata{1}{}          {concat}          {214}{214}{100} & \mydata{1}{}            {isExtensible}      {214}{214}{100} & \mydata{1}{}            {fromCharCode}  {214}{214}{100} \mylinefft
+      \mydata{1}{}          {join}            {214}{214}{100} & \mydata{1}{}            {keys}              {214}{214}{100} & \mydata{1}{}            {charAt}        {214}{214}{100} \mylineftf
+      \mysucc{1}{Array}     {pop}             {214}{214}{100} & \mydata{1}{Object}      {valueOf}           {214}{214}{100} & \mydata{1}{}            {charCodeAt}    {214}{214}{100} \mylinefff
+      \mydata{1}{.prototype}{push}            {214}{214}{100} & \mydata{1}{.prototype}  {isPrototypeOf}     {214}{214}{100} & \mydata{1}{}            {indexOf}       {214}{214}{100} \mylineftf
+      \mydata{1}{}          {slice}           {214}{214}{100} & \mydata{1}{}            {acos}              {214}{214}{100} & \mysucc{1}{}            {match}         {214}{214}{100} \mylinefff
+      \mydata{1}{}          {splice}          {214}{214}{100} & \mysucc{1}{}            {atan2}             {214}{214}{100} & \mydata{1}{String}      {replace}       {214}{214}{100} \mylinefff
+      \mydata{1}{}          {map}             {214}{214}{100} & \mydata{1}{}            {cos}               {214}{214}{100} & \mydata{1}{.prototype}  {splice}        {214}{214}{100} \mylinefff
+      \mydata{1}{}          {reduce}          {214}{214}{100} & \mydata{1}{Math}        {exp}               {214}{214}{100} & \mydata{1}{}            {split}         {214}{214}{100} \mylinetff
+      \mysucc{1}{global}    {eval}            {214}{214}{100} & \mydata{1}{}            {floor}             {214}{214}{100} & \mysucc{1}{}            {substring}     {214}{214}{100} \mylinetff
+      \mydata{1}{}          {new Date}        {214}{214}{100} & \mydata{1}{}            {max}               {214}{214}{100} & \mydata{1}{}            {toLowerCase}   {214}{214}{100} \mylinefff
+      \mydata{1}{Date}      {parse}           {214}{214}{100} & \mydata{1}{}            {min}               {214}{214}{100} & \mydata{1}{}            {toUpperCase}   {214}{214}{100} \mylinef
+      \mydata{1}{}          {now}             {214}{214}{100}
+    \end{array}
+  \]
+  \caption{\todo}
+  \label{fig:abs-analysis-ratio}
+  \vspace*{-1.5em}
+\end{table*}
+
 \todo

### 2020-11-17 paper/pldi21/eval.tex
First draft

@@
 
+\begin{figure}
+  \centering
+  \begin{subfigure}[t]{0.48\textwidth}
+    \includegraphics[width=\linewidth]{img/precision-fail}
+    \vspace*{-1.5em}
+    \caption{\# Failed Assertions.}
+    \label{fig:precision-fail}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.48\textwidth}
+    \includegraphics[width=\linewidth]{img/precision-branch}
+    \vspace*{-1.5em}
+    \caption{\# Covered Branches.}
+    \label{fig:precision-branch}
+  \end{subfigure}
+  \vspace*{-1em}
+  \caption{The comparison of analysis precision without (no-DS) and with (DS)
+  dynamic shortcut for \inred{82} \textit{abstracted} tests analyzable by both
+  analyses}
+  \label{fig:precision}
+  \vspace*{-1.5em}
+\end{figure}
+
+\begin{table*}
+  \centering
+  \caption{The number of \textit{abstracted} tests using dynamic shortcut
+  instead of manual modeling for each JavaScript built-in library.}
+  \label{table:func-replace}
+  \vspace*{-1em}
+  \scriptsize
+  \[
+    \begin{array}{c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}}
+
+      \myhead{Object}       {Function}        {\# Replaced}
+
+      \mysucc{2}{Boolean}   {Boolean}         {214}{214}{100} & \mydata{1}{}            {new Object}        {214}{214}{100} & \mymult{2}{Number}      {valueOf}       {214}{214}{100} \mylineff
+      \mydata{1}{}          {new Boolean}     {214}{214}{100} & \mydata{1}{}            {getPrototypeOf}    {214}{214}{100} & \myname{1}{.prototype}                                  \mylinetft
+      \mydata{1}{Array}     {isArray}         {214}{214}{100} & \mydata{1}{}            {create}            {214}{214}{100} & \mymult{2}{RegExp}      {toString}      {214}{214}{100} \mylinetf
+      \mydata{1}{}          {toString}        { 92}{139}{ 66} & \mydata{1}{Object}      {preventExtensions} {214}{214}{100} & \myname{1}{.prototype}                                  \mylinefft
+      \mydata{1}{}          {toLocaleString}  {193}{214}{ 90} & \mydata{1}{}            {isFrozen}          {214}{214}{100} & \mydata{2}{String}      {String}        {214}{214}{100} \mylinefff
+      \mydata{1}{}          {concat}          {214}{214}{100} & \mydata{1}{}            {isExtensible}      {214}{214}{100} & \mydata{1}{}            {fromCharCode}  {214}{214}{100} \mylinefft
+      \mydata{1}{}          {join}            {214}{214}{100} & \mydata{1}{}            {keys}              {214}{214}{100} & \mydata{1}{}            {charAt}        {214}{214}{100} \mylineftf
+      \mysucc{1}{Array}     {pop}             {214}{214}{100} & \mydata{1}{Object}      {valueOf}           {214}{214}{100} & \mydata{1}{}            {charCodeAt}    {214}{214}{100} \mylinefff
+      \mydata{1}{.prototype}{push}            {214}{214}{100} & \mydata{1}{.prototype}  {isPrototypeOf}     {214}{214}{100} & \mydata{1}{}            {indexOf}       {214}{214}{100} \mylineftf
+      \mydata{1}{}          {slice}           {214}{214}{100} & \mydata{1}{}            {acos}              {214}{214}{100} & \mysucc{1}{}            {match}         {214}{214}{100} \mylinefff
+      \mydata{1}{}          {splice}          {214}{214}{100} & \mysucc{1}{}            {atan2}             {214}{214}{100} & \mydata{1}{String}      {replace}       {214}{214}{100} \mylinefff
+      \mydata{1}{}          {map}             {214}{214}{100} & \mydata{1}{}            {cos}               {214}{214}{100} & \mydata{1}{.prototype}  {splice}        {214}{214}{100} \mylinefff
+      \mydata{1}{}          {reduce}          {214}{214}{100} & \mydata{1}{Math}        {exp}               {214}{214}{100} & \mydata{1}{}            {split}         {214}{214}{100} \mylinetff
+      \mysucc{1}{global}    {eval}            {214}{214}{100} & \mydata{1}{}            {floor}             {214}{214}{100} & \mysucc{1}{}            {substring}     {214}{214}{100} \mylinetff
+      \mydata{1}{}          {new Date}        {214}{214}{100} & \mydata{1}{}            {max}               {214}{214}{100} & \mydata{1}{}            {toLowerCase}   {214}{214}{100} \mylinefff
+      \mydata{1}{Date}      {parse}           {214}{214}{100} & \mydata{1}{}            {min}               {214}{214}{100} & \mydata{1}{}            {toUpperCase}   {214}{214}{100} \mylinef
+      \mydata{1}{}          {now}             {214}{214}{100}
+    \end{array}
+  \]
+  \vspace*{-1em}
+\end{table*}
+
 To evaluate the precision improvement of dynamic shortcut, we used two different
@@
 
-\begin{figure}
-  \centering
-  \begin{subfigure}[t]{0.48\textwidth}
-    \includegraphics[width=\linewidth]{img/precision-fail}
-    \vspace*{-1.5em}
-    \caption{\# Failed Assertions.}
-    \label{fig:precision-fail}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.48\textwidth}
-    \includegraphics[width=\linewidth]{img/precision-branch}
-    \vspace*{-1.5em}
-    \caption{\# Covered Branches.}
-    \label{fig:precision-branch}
-  \end{subfigure}
-  \vspace*{-1em}
-  \caption{The comparison of analysis precision without (no-DS) and with (DS)
-  dynamic shortcut for \inred{82} \textit{abstracted} tests analyzable by both
-  analyses}
-  \label{fig:precision}
-  \vspace*{-1.5em}
-\end{figure}
+\inred{TODO - Case Study.}
 
@@
 
-\begin{table*}
-  \centering
-  \scriptsize
-  \[
-    \begin{array}{c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}}
-      \myhead
-      \mysucc{2}{Boolean}   {Boolean}         {214}{214}{100} & \mydata{1}{}            {new Object}        {214}{214}{100} & \mymult{2}{Number}      {valueOf}       {214}{214}{100} \mylineff
-      \mydata{1}{}          {new Boolean}     {214}{214}{100} & \mydata{1}{}            {getPrototypeOf}    {214}{214}{100} & \myname{1}{.prototype}                                  \mylinetft
-      \mydata{1}{Array}     {isArray}         {214}{214}{100} & \mydata{1}{}            {create}            {214}{214}{100} & \mymult{2}{RegExp}      {toString}      {214}{214}{100} \mylinetf
-      \mydata{1}{}          {toString}        {214}{214}{100} & \mydata{1}{Object}      {preventExtensions} {214}{214}{100} & \myname{1}{.prototype}                                  \mylinefft
-      \mydata{1}{}          {toLocaleString}  {214}{214}{ 90} & \mydata{1}{}            {isFrozen}          {214}{214}{100} & \mydata{2}{String}      {String}        {214}{214}{100} \mylinefff
-      \mydata{1}{}          {concat}          {214}{214}{100} & \mydata{1}{}            {isExtensible}      {214}{214}{100} & \mydata{1}{}            {fromCharCode}  {214}{214}{100} \mylinefft
-      \mydata{1}{}          {join}            {214}{214}{100} & \mydata{1}{}            {keys}              {214}{214}{100} & \mydata{1}{}            {charAt}        {214}{214}{100} \mylineftf
-      \mysucc{1}{Array}     {pop}             {214}{214}{100} & \mydata{1}{Object}      {valueOf}           {214}{214}{100} & \mydata{1}{}            {charCodeAt}    {214}{214}{100} \mylinefff
-      \mydata{1}{.prototype}{push}            {214}{214}{100} & \mydata{1}{.prototype}  {isPrototypeOf}     {214}{214}{100} & \mydata{1}{}            {indexOf}       {214}{214}{100} \mylineftf
-      \mydata{1}{}          {slice}           {214}{214}{100} & \mydata{1}{}            {acos}              {214}{214}{100} & \mysucc{1}{}            {match}         {214}{214}{100} \mylinefff
-      \mydata{1}{}          {splice}          {214}{214}{100} & \mysucc{1}{}            {atan2}             {214}{214}{100} & \mydata{1}{String}      {replace}       {214}{214}{100} \mylinefff
-      \mydata{1}{}          {map}             {214}{214}{100} & \mydata{1}{}            {cos}               {214}{214}{100} & \mydata{1}{.prototype}  {splice}        {214}{214}{100} \mylinefff
-      \mydata{1}{}          {reduce}          {214}{214}{100} & \mydata{1}{Math}        {exp}               {214}{214}{100} & \mydata{1}{}            {split}         {214}{214}{100} \mylinetff
-      \mysucc{1}{global}    {eval}            {214}{214}{100} & \mydata{1}{}            {floor}             {214}{214}{100} & \mysucc{1}{}            {substring}     {214}{214}{100} \mylinetff
-      \mydata{1}{}          {new Date}        {214}{214}{100} & \mydata{1}{}            {max}               {214}{214}{100} & \mydata{1}{}            {toLowerCase}   {214}{214}{100} \mylinefff
-      \mydata{1}{Date}      {parse}           {214}{214}{100} & \mydata{1}{}            {min}               {214}{214}{100} & \mydata{1}{}            {toUpperCase}   {214}{214}{100} \mylinef
-      \mydata{1}{}          {now}             {214}{214}{100}
-    \end{array}
-  \]
-  \caption{\todo}
-  \label{fig:abs-analysis-ratio}
-  \vspace*{-1.5em}
-\end{table*}
+The dynamic shortcut does not only improve performance or precision of analysis
+but also reduce the effort to model the behavior of opaque functions.
+JavaScript programs often use JavaScript built-in libraries or host-dependent
+functions but they are opaque codes; it means that they are executable but
+written in a different programming languages.  A typical solution is to
+manually model their behaviors to statically analyze for JavaScript programs
+using such functions.  The dynamic shortcut can reduce such efforts if some
+opaque functions are analyzed by only dynamic analysis instead of static
+analysis.
 
-\todo
+Table~\ref{table:func-replace} describes the dynamic shortcut effectively lessen
+the burden of manual modeling for JavaScript built-in functions.  Among Lodash 4
+\inred{219} abstracted tests analyzable with dynamic shortcut, we measured the
+number of tests using only dynamic shortcut instead of manual modeling for each
+JavaScript built-in library.  For each raw, \textbf{Object} column denotes the
+built-in object, \textbf{Function} function name, \textbf{\# Replaced} the
+number of tests successfully replacing the modeling via dynamic shortcut with
+the total number of tests using the target function.  For example, the fourth
+row in the left side describes that \jscode{Array.prototype.toString} is used in
+\inred{139} Lodash 4 abstracted tests and the static analysis with dynamic
+shortcut successfully analyze \inred{92} tests among them.  It means that
+\inred{66}\% of tests using \jscode{Array.prototype.toString} could be analyzed
+without the manual modeling of the built-in function.
+
+Moreover, \inred{6} functions out of \inred{49} JavaScript built-in functions
+are analyzed by only dynamic shortcut instead of manual modeling for all Lodash
+4 tests.  Each raw colored colored with \inred{yellow} describes such case in
+Table~\ref{table:func-replace}.  It means that the manual modeling of \inred{6} 
+JavaScript built-in functions is does not required to analyze all Lodash 4
+abstracted tests. \inred{TODO - Explain the detail for each case.}

### 2020-11-18 paper/pldi21/implementation.tex
Replaced a paragraph in implementation.

@@
 
-\paragraph{Abstract Locations for Objects.}
-During dynamic analysis, each JavaScript object should be designated by the
-corresponding abstract location used in the static analysis.  In this paper, we
-define abstract locations using the allocation site
-abstraction~\cite{allocation-site} with heap cloning~\cite{heap-cloning} for
-each abstract context in the static analyzer.  Thus, we instrument the given
-JavaScript program to annotate each object created during dynamic analysis with
-its allocation site and context information.  After the sealed symbolic
-execution, the dynamic analyzer collects the objects based on their annotated
-information for each abstract location.
+\paragraph{Synchronization of Control Points.}
+For seamless interactions between the static analyzer and dynamic shortcuts,
+the synchronization of control points is a prerequisite.
+The static analyzer compiles a target JavaScript program to intermediate
+representation and builds a control flow graph.  It produces annotations for
+control points on the CFG including functions, call sites, and object allocation
+sites.  During the sealed symbolic execution, the dynamic analyzer requires
+those annotations to calculate sensitive location names of newly created object
+and lexical environments.  The key to place annotations on the instrumented code
+is the span information of the original AST node.  Both the CFG of SAFE and
+instrumented code of Jalangi maintain the span information, but they use
+different parsers resulting mismatches for some corner cases.  Thus, we
+preprocess to synchronize control points of two analyzers by the closest match
+of the span information rather than the exact match.
 
@@
 % exit point.
+
+%\paragraph{Abstract Locations for Objects.}
+%During dynamic analysis, each JavaScript object should be designated by the
+%corresponding abstract location used in the static analysis.  In this paper, we
+%define abstract locations using the allocation site
+%abstraction~\cite{allocation-site} with heap cloning~\cite{heap-cloning} for
+%each abstract context in the static analyzer.  Thus, we instrument the given
+%JavaScript program to annotate each object created during dynamic analysis with
+%its allocation site and context information.  After the sealed symbolic
+%execution, the dynamic analyzer collects the objects based on their annotated
+%information for each abstract location.

### 2020-11-18 paper/pldi21/report/report.tex
Write soundness proof

\documentclass[11pt]{article}
\usepackage[a4paper,left=20mm,right=20mm,top=30mm,bottom=25mm]{geometry}

\usepackage{mathtools}
\usepackage[T1]{fontenc}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathpartir}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{stmaryrd}
\usepackage{tikz}
\usepackage{dirtree}
\usepackage{multicol}
\usepackage{array}
\usepackage{galois}
\usepackage{amsthm}

\usetikzlibrary{arrows}
\tikzset{
  treenode/.style = {align=center, inner sep=0pt, text centered},
  arn_n/.style = {treenode, circle, black, draw=black, text width=1.5em},
}

\begin{document}

\input{macros}

\title{Dynamic Shortcut Soundness Proof}

\author{Dongjun Youn$^*$ \and Jihyeok Park$^*$ \and Sukyoung Ryu$^*$}

\date{$^*$KAIST, South Korea}
\maketitle

\input{proof}

\end{document}

### 2020-11-19 paper/pldi21/intro.tex
Updated intro.tex with the explanation of dynamic shortcut
Updated intro

@@
 leverage high performance of dynamic analysis for static analysis by freely
-switching between them in a sound way.  Our key observation is that we can
-use concrete semantics for specific program parts while preserving the soundness
-if they are not dependent with meaning of abstract values.  For example, the
-third line of the following program passes the abstract value \jscode{v} stored
-in \jscode{obj.p1} to the variable \jscode{x}:
+switching between them in a sound way.  A dynamic shortcut consists of three
+parts that 1) dumps the current abstract state to the corresponding sealed
+symbolic state, 2) performs dynamic analysis on the sealed symbolic state, and
+3) updates the abstract state with the result of dynamic analysis.  Our key
+observation is that we can use concrete semantics for specific program parts
+while preserving the soundness if they are not dependent with meaning of
+abstract values.  For example, the third line of the following program passes
+the abstract value \jscode{v} stored in \jscode{obj.p1} to the variable
+\jscode{x}:
 \begin{lstlisting}[style=myJSstyle,numbers=none]

### 2020-11-19 paper/pldi21/ds.tex
Separated ds.tex from shortcut.tex

--- 2020-11-03 paper/pldi21/shortcut.tex
@@
-\section{Dynamic Shortcut}\label{sec:formal}
-
-In this section, we formally define the dynamic shortcut with sealed symbolic
-execution.  We extend the formalization of abstract interpretation of
-\citet{abs-interp-1977, abs-interp-1992} and views-based analysis sensitivity of
-\citet{sens-toplas}.
-
-\subsection{Concrete Semantics}
-
-We define a program $\prog$ as a state transition system $(\stset, \trans,
-\istset)$.  A program starts with an initial state in $\istset$ and the
-transition relation $\trans \subseteq \stset \times \stset$ describes how states
-are transformed to other states.  A \textit{collecting semantics} $\sem{\prog} =
-\{ \st \in \stset \mid \ist \in \istset \wedge \ist \trans^* \st \}$ consists of
-reachable states from initial states of the program $\prog$.  We could calculate
-it using the \textit{transfer function} $\transfer: \dom \rightarrow \dom$ as
-follows:
-\[
-  \sem{\prog} = \underset{n \rightarrow \infty}{\lim}{\transfer^n(\ielem)}\\
-  \qquad
-  \transfer(\elem) = \elem \join \step(\elem)\\
-\]
-The \textit{concrete domain} $\dom = \powerset{\stset}$ is a complete lattice
-with $\cup$, $\cap$, and $\subseteq$ as its join($\join$), meet($\meet$), and
-partial order($\order$) operators.  The element $\ielem$ denotes the initial
-states $\istset$.  The \textit{one-step execution} $\step: \dom \rightarrow
-\dom$ transforms states using the transition relation $\trans$: $\step(\elem) =
-\{ \st' \mid \st \in \elem \wedge \st \trans \st' \}$.
-
-\begin{figure}[H]
-  \[
-    \begin{array}{l}
-      \enspace \labdot{0} \; \varx = \;? \; ;  \; \labdot{1}\\
-      \enspace \kwif \; (\; \varx \geq 0 \;) \; \labdot{2} \; \varx = \varx ;\\
-      \enspace \kwelse \; \labdot{3} \; \varx = -\varx ;  \; \labdot{4}\\
-    \end{array}
-  \]
-  \vspace*{-1em}
-  \caption{Conditional branch}
-  \label{fig:running-example}
-\end{figure}
-
-For example, the code in Figure~\ref{fig:running-example} is a simple program
-that applies the mathematical absolute value function to the variable $\varx$.
-The question mark $?$ denotes the user input that returns an integer.  States
-are pairs of labels and integers $\varx$: $\stset = \labset \times \mathbb{N}$.
-The initial states are $\istset = \{ (\lab_0, 0) \}$ which means the program
-starts with the variable $\varx$ that stores 0 at $\lab_0$.  If the user input is
-$-42$, the program is executed with the following trace:
-\[
-  (\lab_0, 0) \trans (\lab_1, -42) \trans (\lab_3, -42) \trans (\lab_4, 42)
-\]
-
-\subsection{Abstract Interpretation}
-The abstract interpretation~\cite{abs-interp-1977, abs-interp-1992}
-over-approximates the transfer $\transfer$ to the \textit{abstract transfer
-function} $\abstransfer: \absdom \rightarrow \absdom$ to get the
-\textit{abstract semantics} $\abssem{\prog}$ in finite iterations as follows:
-\[
-    \abssem{\prog} = \underset{n \rightarrow
-    \infty}{\lim}{(\abstransfer)^n(\iabselem)}\\
-\]
-We define a \textit{state abstraction} $\dom \galois{\alpha}{\gamma} \absdom$ as
-a Galois connection between the concrete domain $\dom$ and an abstract domain
-$\absdom$ with a \textit{concretization function} $\gamma$ and an
-\textit{abstraction function} $\alpha$.  The initial abstract state $\iabselem
-\in \absdom$ represents an abstraction of the initial state set; $\ielem
-\subseteq \gamma(\iabselem)$.  The abstract transfer function $\abstransfer:
-\absdom \rightarrow \absdom$ is defined as $\abstransfer(\abselem) = \abselem
-\join \absstep(\abselem)$ with an \textit{abstract one-step execution}
-$\absstep: \absdom \rightarrow \absdom$.  For the sound state abstraction, the
-join operator and the abstract one-step execution should satisfy the following
-conditions:
-\begin{itemize}
-  \item $\forall \abselem_0, \abselem_1 \in \absdom. \; \gamma(\abselem_0) \cup
-    \gamma(\abselem_1) \subseteq \gamma(\abselem_0 \join \abselem_1)$
-  \item $\forall \abselem \in \absdom. \; \absstep \circ \gamma(\abselem) \subseteq
-    \gamma \circ \absstep(\abselem)$
-\end{itemize}
-
-A simple example abstract domain is $\absdom_\pm = \powerset{\{ -, +, 0 \}}$ with
-set operators as domain operators; $-$ denotes negative integers, $+$ positive
-integers, and $0$ zero.  If we use it for the code in
-Figure~\ref{fig:running-example}, the analysis result becomes $\{ -, +, 0 \}$
-because $\varx$ can have any integers at $\lab_1$.
-
-\subsection{Analysis Sensitivity}
-
-Abstract interpretation is often defined with \textit{analysis sensitivity} to
-increase the precision of static analysis.  A sensitive abstract domain
-$\sabsdom: \viewset \rightarrow \absdom$ is defined with a \textit{view
-abstraction} $\viewmap: \viewset \rightarrow \dom$ that provides multiple points
-of views for reachable states during static analysis.  It maps a finite number
-of views $\viewset$ to sets of states $\dom$. Each view $\view \in \viewset$
-represents a set of states $\viewmap(\view)$.
-A \textit{sensitive state abstraction} $\dom
-\galois{\alpha_\viewmap}{\gamma_\viewmap} \sabsdom$ is a Galois connection between
-the concrete domain $\dom$ and the sensitive abstract domain $\sabsdom$ with the
-following concretization function:
-\[
-  \gamma_\viewmap(\sabselem) = \{ \st \in \stset \mid \forall \view \in \viewset.
-  \; \st \in \viewmap(\view) \Rightarrow \st \in \gamma \circ \sabselem(\view) \}
-\]
-
-With analysis sensitivities, the abstract one-step execution $\sabsstep:
-\sabsdom \rightarrow \sabsdom$ is defined as follows:
-\[
-  \sabsstep(\sabselem) = \lambda \view \in \viewset. \; \underset{\view' \in
-  \viewset}{\bigjoin}{\viewtrans{\view'}{\view} \circ \sabselem(\view')}
-\]
-where $\viewtrans{\view'}{\view}: \absdom \rightarrow \absdom$ is the abstract
-semantics of a \textit{view transition} from a view $\view'$ to another view
-$\view$.  It should satisfy the following condition for the soundness of the
-analysis:
-\[
-  \forall \abselem \in \absdom. \; \step(\gamma(\abselem) \cap \viewmap(\view'))
-  \cap \viewmap(\view) \subseteq \gamma \circ
-  \viewtrans{\view'}{\view}(\abselem)
-\]
-
-One of the most widely-used analysis sensitivity is \textit{flow sensitivity}
-defined with the flow-sensitive view abstraction $\fsviewmap: \labset
-\rightarrow \dom$ where
-\[
-  \forall \lab\in\labset. \; \fsviewmap(\lab) = \{ \st \mid \st = (\lab, \_) \}
-\]
-If we apply the flow sensitivity for the above example, the analysis result
-becomes as follows:
-\[
-  \begin{array}{|c||c|c|c|c|c|}\hline
-    \labset & \lab_0 & \lab_1 & \lab_2 & \lab_3 & \lab_4\\\hline
-    \absdom_\pm & 0 & -, +, 0 & +, 0 & - & +, 0\\\hline
-  \end{array}
-\]
-
-\subsection{Sealed Symbolic Execution}
-
-To handle abstract values in concrete semantics, we define \textit{sealed
-symbolic execution} by extending the transition relation $\trans$ as a symbolic
-transition relation $\symbtrans$ on symbolic states.  First, we extends the
-concrete states $\stset$ to symbolic states with \textit{sealed symbolic values}
-$\symbset$.  A symbolic transition relation $\symbtrans \subseteq \symbstset
-\times (\symbstset \uplus \{ \excst \})$ is exactly the same with the original
-transition relation $\trans$ except when the relation requires the exact value
-of sealed symbolic values.  In this case, the symbolic state has the relation a
-special exception state $\excst$ to represent that it is impossible to interpret
-in a concrete way.  Thus, a symbolic state \textit{always} has a symbolic
-transition relation with a single symbolic state, and the sealed symbolic
-execution is linear until being terminated or reaching the exception state
-$\excst$.
-
-The main difference of sealed symbolic execution with the traditional symbolic
-execution~\cite{symbolic} is that it only supports sealed symbolic values
-instead of symbolic expressions and path constraints.  For example, the
-following trace represents the traditional symbolic execution of the running
-example in Figure~\ref{fig:running-example}:
-\[
-  \begin{array}{r@{~}c@{~}l}
-    &&(\lab_2, \symb)[\symb \geq 0] \trans (\lab_4, \symb)[\symb \geq 0]
-    \vspace*{-0.5em}\\
-    &\rutrans&
-    \vspace*{-0.5em}\\
-    (\lab_0, 0)[] \trans (\lab_1, \symb)[]&&
-    \vspace*{-0.5em}\\
-    &\rdtrans&
-    \vspace*{-0.5em}\\
-    &&(\lab_3, \symb)[\symb < 0] \trans (\lab_4, -\symb)[\symb < 0]\\
-  \end{array}
-\]
-It first assigns a symbolic value $\symb$ to the variable $\varx$ at $\lab_1$.
-For the conditional branch, it is forked by creating two symbolic states with
-different path conditions $\symb \geq 0$ and $\symb < 0$ for true and false
-branches, respectively.  After executing statements $\varx = \varx$ and $\varx =
--\varx$, the variable $\varx$ stores symbolic expressions $\symb$ and $-\symb$ at
-$\lab_4$.  However, the sealed symbolic execution stops at $\lab_1$ as follows:
-\[
-  (\lab_0, 0) \; \symbtrans \; (\lab_1, \symb) \; \symbtrans \; \excst
-\]
-because the branch requires the actual value of the symbolic value $\symb$.
-
-To freely convert a pair of view and an abstract state to its corresponding
-symbolic state and vice versa, we define two domain converters $\symbstset
-\galois{\saconverter}{\asconverter} (\viewset \times \absdom)$.  In the
-converter $\asconverter$ from abstract states to symbolic states, if an abstract
-value $\absval$ represents a singleton value, the function transforms the
-abstract value to the corresponding concrete value.  Otherwise, it converts the
-abstract value as a symbolic value in a result symbolic state.  Two converters
-convert given elements without loss of information:
-\[
-  \saconverter \circ \asconverter = \asconverter \circ \saconverter = \identity
-\]
-where $\identity$ denotes the identity function.
-
 \subsection{Dynamic Shortcut}
@@
 \end{figure}
+
+\begin{figure*}[t]
+  \centering
+
+  \fbox{$\st \trans \st$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \refer = \expr\\
+      \referrule{\st}{\refer}{\loc}\\
+      \exprrule{\st}{\expr}{\val}\\
+    }
+    {
+      \st = (\lab, \mem, \ctxt, \addr)
+      \trans
+      (\labnext(\lab), \mem[\loc \mapsto \val], \ctxt, \addr)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \refer = \kwobj\\
+      \referrule{\st}{\refer}{\loc}\\
+      \addr' = \text{(a fresh object address)}
+    }
+    {
+      \st = (\lab, \mem, \ctxt, \addr)
+      \trans
+      (\labnext(\lab), \mem[\loc \mapsto \addr'], \ctxt, \addr)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \refer = \expr_f ( \expr_a )\\
+      \referrule{\st}{\refer}{\loc}\\
+      \exprrule{\st}{\expr_f}{\fval{x}{\lab_b}}\\
+      \exprrule{\st}{\expr_a}{\val_a}\\
+      \addr' = \text{(a fresh environment address)}
+    }
+    {
+      \st = (\lab, \mem, \ctxt, \addr)
+      \trans
+      (\lab_b, \mem[(\addr', x) \mapsto \val_a], \ctxt[\addr' \mapsto (\addr,
+      \labnext(\lab), \loc)], \addr')
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwret \; \expr\\
+      \exprrule{\st}{\expr}{\val}\\
+      \ctxt(\addr) = (\addr', \lab', \loc)
+    }
+    {
+      \st = (\lab, \mem, \ctxt, \addr)
+      \trans
+      (\lab', \mem[\loc \mapsto \val], \ctxt, \addr')
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwif \; \expr \; \lab'\\
+      \exprrule{\st}{\expr}{\kwtrue}\\
+    }
+    {
+      \st = (\lab, \mem, \ctxt, \addr)
+      \trans
+      (\lab', \mem, \ctxt, \addr)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwif \; \expr \; \lab'\\
+      \exprrule{\st}{\expr}{\kwfalse}\\
+    }
+    {
+      \st = (\lab, \mem, \ctxt, \addr)
+      \trans
+      (\labnext(\lab), \mem, \ctxt, \addr)
+    }
+  \end{mathpar}
+
+  \fbox{$\referrule{\st}{\refer}{\loc}$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {}
+    {
+      \referrule{\st = (\lab, \mem, \ctxt, \addr)}{x}{(\addr, x)}\\
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \exprrule{\st}{\expr_0}{\addr_0}\\
+      \exprrule{\st}{\expr_1}{\val_1}\\
+      \val_1 \in \strset\\
+    }
+    {
+      \referrule{\st = (\lab, \mem, \ctxt, \addr)}{\expr_0 [ \expr_1
+      ]}{(\addr_0, \val_1)}
+    }
+  \end{mathpar}
+
+  \fbox{$\exprrule{\st}{\expr}{\val}$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {}
+    {
+      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}{\pval}{\pval}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {}
+    {
+      \exprrule{\st = (\lab, \mem, \ctxt,
+      \addr)}{\fval{x}{\lab'}}{\fval{x}{\lab'}}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \referrule{\st}{\refer}{\loc}\\
+      \loc \in \Dom(\mem)
+    }
+    {
+      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}{\refer}{\mem(\loc)}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \exprrule{\st}{\expr_1}{\val_1}\\
+      \cdots\\
+      \exprrule{\st}{\expr_n}{\val_n}
+    }
+    {
+      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}
+      {\op(\expr_1, \cdots, \expr_n)}{\op(\val_1, \cdots, \val_n)}
+    }
+  \end{mathpar}
+
+  \caption{The transition relation for the core language of JavaScript}
+  \label{fig:core-trans-rel}
+\end{figure*}
 

### 2020-11-19 paper/pldi21/shortcut.tex
Move Figure 6 to the right position
Separated ds.tex from shortcut.tex

@@
 where $\identity$ denotes the identity function.
-
-\subsection{Dynamic Shortcut}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=\linewidth]{img/dynamic-shortcut}
-  \vspace*{-2em}
-  \caption{The diagram for the extended view transition for dynamic shortcut.}
-  \vspace*{-1em}
-  \label{fig:dynamic-shortcut}
-\end{figure}
-
-We define the the abstract interpretation with \textit{dynamic shortcut}, which
-is a concrete semantics on sealed symbolic execution.  With dynamic shortcut,
-we use the powerset of symbolic states as the domain $\combdom =
-\powerset{\symbstset}$, and extend the view transition as follows:
-\[
-  \begin{array}{l}
-    \combviewtrans{\view}{\view'}(\combelem) =\\
-    \qquad \{
-      \symbst' \mid \symbst \in S \wedge
-      \symbst \symbtrans \symbst' \wedge
-      \saconverter(\symbst') = (\view', \_)
-    \}\\
-    \qquad \cup \left\{
-    \begin{array}{ll}
-      \{ \asconverter \circ \viewtrans{\view}{\view'}(\bigjoin D) \}
-      & \text{if} \; D \neq \varnothing\\
-      \varnothing & \text{otherwise}\\
-    \end{array}
-    \right.
-  \end{array}
-\]
-where $S = \combelem\mid_{\checker}$ and $D =
-\dot{\saconverter}(\combelem\mid_{\neg\checker})$.  The dot notation $\dot{f}$
-denotes the element-wise extended function of a function $f$.  The abstract
-interpretation with dynamic shortcut performs one-step symbolic transition for
-each symbolic state that passes the filter $\checker$. On the other hand, it
-converts remaining symbolic states to the corresponding abstract states, merges
-them into a single abstract state, and performs the abstract one-step execution
-for the abstract state.
-
-For example, Figure~\ref{fig:dynamic-shortcut} depicts the
-diagram of the extended view transition from $\view$ to $\view'$ for dynamic
-shortcut.  The element $\combelem$ in $\view$ consists of five symbolic states
-from $\nsymbst{1}$ to $\nsymbst{5}$.  The solid box denotes that the corresponding
-symbolic state passes the filter $\checker$ and the dotted box denotes that it
-does not.  For each symbolic state that passes the filter ($\nsymbst{1}$,
-$\nsymbst{2}$, and $\nsymbst{4}$), it applies the symbolic transition $\symbtrans$.
-For failed symbolic states ($\nsymbst{3}$ and $\nsymbst{5}$), it applies the
-converter $\saconverter$ to convert each of them to the corresponding abstract
-state and merges results using the join operator ($\join$).  Then, it utilizes
-the abstract semantics via the original view transition
-$\viewtrans{\view}{\view'}$ and the converter $\asconverter$ to convert the
-result to the corresponding symbolic state.
-
-We could configure when the sealed symbolic execution or the abstract
-interpretation is performed based on the definition of the $\checker$ function
-and its negation $\neg\checker$.  For example, we could define the $\checker$
-that passes only function entry, call, and exit points to perform conversions in
-a function level.  However, for the soundness and the termination of the
-the abstract interpretation with dynamic shortcut, it should satisfy the
-following condition:
-\begin{theorem}\label{theorem:shortcut}
-  The abstract interpretation with dynamic shortcut is sound and terminates in a
-  finite time if its abstract semantics is sound and $\checker$ satisfies the
-  following condition:
-  \[
-    \checker(\symbst) \Rightarrow \symbst \symbtrans^k \excst \wedge
-    1 < k \leq N
-  \]
-  where $N$ is a pre-defined maximum length of the sealed symbolic execution.
-\end{theorem}
-\inred{We proved Theorem~\ref{theorem:shortcut} using the Kleene's fixed-point
-theorem~\cite{kleene} with the finite height of abstract domains. Because of the
-page limitation, we omit the proof in this paper and include it in a companion
-report~\cite{report}.}

### 2020-11-19 paper/pldi21/abstract.tex
Till Abstract

--- 2020-10-27 paper/pldi21/abstract.tex
@@
 \begin{abstract}
-Static analyses based on abstract interpretation can be integrated into developer workflow and help developers to find bugs.
-However, the dynamic features of JavaScript degrade the scalability and precision of the pure static analyses.
-Combining static and dynamic analyses is one of the breakthroughs in JavaScript bug detection.
-Existing combined analyses have static boundaries that distinguish which analysis used for which part of a program.
-Such boundaries are intuitive but limit chances to optimize transitions between two analyses.
-We formally present the dynamic shortcut, a more flexible compound of static and dynamic analyses.
-We implement a proof of concept bug detector by extending the existing static analyzer supporting a subset of ECMAScript 5.1.
-Our experimental results show that the combined analysis indeed speeds up and produces more precise results.
+JavaScript becomes one of the most widely used programming languages for web
+development, server-side programming, and even micro-controllers for IoT.
+However, its extremely functional and dynamic features degrade the scalability and precision
+of static analysis.  Moreover, the variety of built-in functions and host
+environments requires excessive manual modeling of their behaviors.  To
+alleviate these problems, researchers have proposed various ways to
+leverage dynamic analysis during JavaScript static analysis.  However,
+they do not fully utilize the high performance of dynamic analysis and
+often sacrifice the soundness of static analysis.
+
+In this paper, we propose a novel technique to take advantage of the
+high performance of dynamic analysis for JavaScript static analysis
+in a sound way by using \textit{dynamic shortcuts}.  A dynamic shortcut
+consists of three parts: 1) converting an abstract state to its corresponding
+\textit{sealed symbolic state}, 2) performing \textit{sealed symbolic execution}
+on the sealed symbolic state, and 3) converting a sealed symbolic state
+to its corresponding abstract state. By taking dynamic shortcuts
+during static analysis, we can significantly improve the analysis
+scalability and precision by using highly-optimized commercial JavaScript engines
+and lessen the modeling efforts by performing sealed symbolic execution for opaque code.
+We formally define static analysis using dynamic shortcuts in the abstract
+interpretation framework.  We actualize the technique via $\tool$, an
+extended combination of SAFE and Jalangi, a static analyzer and a
+dynamic analyzer, respectively.  We evaluated $\tool$ using
+\inred{77} official tests of Lodash 4 library.
+Our experiment shows that $\tool$ is \inred{X.X}x faster than the
+baseline static analyzer on average, and it improves \inred{XX.XX}\%
+of the analysis precision on average by using sealed symbolic
+execution for \inred{XX.X} opaque functions.
 \end{abstract}

### 2020-11-19 paper/pldi21/abstract.tex
Till Sec. 1

@@
 \begin{abstract}
-JavaScript becomes one of the most widely used programming languages for web
+JavaScript has become one of the most widely used programming languages for web
 development, server-side programming, and even micro-controllers for IoT.

### 2020-11-19 paper/pldi21/intro.tex
Till Sec. 1

--- 2020-11-03 paper/pldi21/intro.tex
@@
 \section{Introduction}\label{sec:intro}
-
-Over the past decade, the rise of JavaScript as the de facto programming
-language in web development has expanded its reach to diverse fields.
+Over the past decades, the rise of JavaScript as the de facto programming
+language for web development has expanded its reach to diverse fields.
 Node.js~\cite{nodejs} supports server-side programming, React
 Native~\cite{react-native} and Electron~\cite{electron} produce cross-platform
-applications.  Moreover, Moddable~\cite{moddable} and Espruino~\cite{espruino}
+applications, and Moddable~\cite{moddable} and Espruino~\cite{espruino}
 provide JavaScript environments in micro-controllers for IoT.  Such wide prevalent
-usage places JavaScript at \#7 in TIOBE Programming Community
+uses place JavaScript at \#7 in the TIOBE Programming Community
 index\footnote{https://www.tiobe.com/tiobe-index/}.  Thus, researchers have
@@
 WALA~\cite{wala}, and SAFE~\cite{safe,safe2} to understand behaviors of
-JavaScript programs and to detect their bugs in a sound way.
+JavaScript programs and to detect their bugs in a sound manner.
 
-However, static analysis of real-world JavaScript programs suffers from its
-dynamic language features.  JavaScript supports various \textit{dynamic language
-features} such as high-order functions, first-class property names, and dynamic
-code generations.  While they provide great flexibility in development but it is
-challenging to statically analyze such features.  To overcome this problem,
+However, static analysis of real-world JavaScript programs suffers from immensely
+functional and dynamic features of JavaScript such as callback
+functions, first-class property names, and dynamic code generation.
+While they provide flexibility in software development, it is
+challenging to statically analyze such features.  To overcome these problems,
 researchers have proposed several analysis techniques: advanced string
 domains~\cite{string, regex, combining-string}, loop sensitivity~\cite{lsaECOOP,
-lsaSPE}, property relation based analysis~\cite{correlation, weaklyAPLAS,
+lsaSPE}, analysis based on property relations~\cite{correlation, weaklyAPLAS,
 weaklySPE, value-partitioning}, and on-demand backward
@@
 
-At the same time, various JavaScript host environments require excessively
-manual modeling of their behaviors for static analysis.  Built-in functions and
-host-dependent functions are implemented in another native language like C++
-instead of JavaScript thus their codes are \textit{opaque} during static
-analysis.  Thus, we need to manually model their behaviors but it is
-error-prone, tedious, and labor-intensive.  While several automatic modeling
-techniques~\cite{safewapi, model-ts} have been proposed, they utilize only type
-information thus they generate imprecise modeling compared to the manual
-approach.
+At the same time, various JavaScript host environments require excessive
+manual modeling of their behaviors for static analysis.  Because built-in functions and
+host-dependent functions are implemented in native language like C and
+C++ instead of JavaScript, their code is \textit{opaque} during static
+analysis.  Thus, static analyzers often model their behaviors
+manually, which is error-prone, tedious, and labor-intensive.
+While several researchers have proposed automatic modeling
+techniques~\cite{safewapi, model-ts}, since they utilize only type
+information, they generate imprecise modeling compared with the manual approach.
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
   \vspace*{-2em}
-  \caption{The performances of dynamic analysis and static analysis for V8
-  benchmarks (version 7)}
+  \caption{Performance of a dynamic analyzer and a static analyzer for V8
+  benchmarks version 7}
   \label{fig:performance}
@@
 
-Instead of advancing static analysis techniques, several researchers leverage
-dynamic analysis to resolve such obstacles in static analysis.  Dynamic
-analyzers such as Jalangi~\cite{jalangi} and DLint~\cite{dlint} run on a
-highly-optimized commercial JavaScript engine thus they are much faster than
-static analysis.  Figure~\ref{fig:performance} shows that the dynamic analysis
-(Jalangi) is \inred{X.X}x faster than static analysis (SAFE) for V8 benchmarks
-(version 7).  Using high performance dynamic analysis, several researchers
-reduce the scope of static analysis~\cite{determinacy, blendedJS}, construct
-initial abstract state~\cite{battles, eha}, and automatic modeling of opaque
-codes~\cite{sra}.
+To alleviate these problems, researchers have leveraged
+dynamic analysis during static analysis.  Because dynamic
+analyzers such as Jalangi~\cite{jalangi} and DLint~\cite{dlint} run on
+highly-optimized commercial JavaScript engines, they are much faster than
+static analyzers.  Figure~\ref{fig:performance} shows that the dynamic analyzer
+Jalangi is \inred{X.X}x faster than the static analyzer SAFE for V8 benchmarks
+version 7.  Using high performance dynamic analysis, researchers have
+reduced the scope of static analysis~\cite{determinacy, blendedJS} and constructed
+initial abstract states~\cite{battles, eha} and automatic modeling of opaque
+code~\cite{sra}.
 
 Unfortunately, existing techniques using dynamic analysis for static analysis
-have two limitations: 1) it cannot fully utilize the high performance of dynamic
-analysis, and 2) it sacrifices the soundness of static analysis.  Most of
-existing techniques are \textit{staged analyses} that first extract specific
-information via dynamic analysis and utilize it in static analysis;
-\citet{determinacy} identifies determinate expressions that always have the same
-value at given program point, \citet{blendedJS} extract the dynamic values to
-change expressions as certain literals, and Park et al.~\cite{battles,eha} dump
-initial states in a certain host environment or the entry of an event handler.
-However, they cannot utilize dynamic analysis any more after starting static
-analysis thus they disturb to maximize the performance advantage.  Moreover,
-they sacrifice the soundness of static analysis to perform dynamic analysis.
-For example, \citet{sra} utilize dynamic analysis for opaque codes with given
-abstract arguments during static analysis.  However, they randomly sample finite
-concrete values for given abstract arguments when they represent infinite number
-of values.  Thus, the analysis result becomes unsound because of the missing
-concrete values.
+have two limitations: 1) they do not fully utilize the high performance of dynamic
+analysis, and 2) they sacrifice the soundness of static analysis.  Most of
+them are \textit{staged analyses}, which first extract specific
+information via dynamic analysis and utilize it in static analysis.
+\citet{determinacy} identify determinate expressions that always have the same
+values at given program points, \citet{blendedJS} extract dynamic values to
+change expressions to certain literals, and Park et al.~\cite{battles,eha} dump
+the initial states of a certain host environment or the entry of an event handler.
+However, because they do not utilize dynamic analysis as soon as static
+analysis begins, they do not get performance benefits since then.  Moreover,
+they sacrifice the soundness of static analysis by performing dynamic analysis.
+For example, the SRA model~\cite{sra} uses dynamic analysis for opaque code
+with abstract arguments during static analysis.  When the abstract arguments
+represent an infinite number of values, it randomly samples finite
+concrete values for the abstract arguments, which makes the analysis
+result unsound due to missing concrete values.
 
-In this paper, we propose a novel \textit{dynamic shortcut} technique to
-leverage high performance of dynamic analysis for static analysis by freely
-switching between them in a sound way.  Our key observation is that we can
-use concrete semantics for specific program parts while preserving the soundness
-if they are not dependent with meaning of abstract values.  For example, the
-third line of the following program passes the abstract value \jscode{v} stored
-in \jscode{obj.p1} to the variable \jscode{x}:
+In this paper, we propose a novel technique to fully utilize
+the high performance of dynamic analysis for JavaScript static
+analysis in a sound manner by using \textit{dynamic shortcuts}.
+During static analysis, one can take a dynamic shortcut, which
+consists of three parts: 1) converting the current abstract state to
+its corresponding \textit{sealed symbolic state}, 2) performing
+\textit{sealed symbolic execution} on the sealed symbolic state, and
+3) converting the result of the sealed symbolic execution to its
+corresponding abstract state.  Our key observation is that we can use
+the fast concrete execution for specific program parts while
+preserving the soundness if they do not use abstract values.
+For example, consider static analysis of the following code:
 \begin{lstlisting}[style=myJSstyle,numbers=none]
@@
 \end{lstlisting}
-Even though \jscode{obj} contains an abstract value \jscode{v}, the semantics of
-the third line does not dependent with the meaning of \jscode{v}.  To utilize
-this observation in dynamic shortcut, we introduce \textit{sealed symbolic
-execution}, which is an augmented concrete execution with sealed symbolic
-values.  We represent each abstract value as a sealed symbolic value, which is a
-symbolic value that detects when trying to access its actual meaning.  To
-evaluate our approach, we implemented $\tool$ by extending the existing
-JavaScript static analyzer SAFE with dynamic shortcut.  For evaluation of
-$\tool$, we analyzed abstracted versions of \inred{77} official tests of
-\inred{Lodash 4} library.
+Because \jscode{y + 1} evaluates to \jscode{"p1"},
+the third line assigns the abstract value of \jscode{v} stored in
+\jscode{obj.p1} to the variable \jscode{x}.
+Note that even though \jscode{obj} contains an abstract value \jscode{v},
+because the third line does not ``use'' the value of \jscode{v},
+we can concretely execute the code.  Based on this observation,
+we introduce sealed symbolic execution, which is concrete execution
+using \textit{sealed symbolic values}.  A sealed symbolic value is a
+representation of an abstract value in symbolic execution; it signals
+the end of the current dynamic shortcut when the sealed symbolic
+execution tries to access its value.
+To evaluate our technique, we implemented $\tool$ using both SAFE
+and Jalangi and analyzed \inred{77} official tests of Lodash 4 library.
 
-Our contributions in this paper include the following:
+The contributions of this paper include the following:
 \begin{itemize}
-  \item We present a novel \textit{dynamic shortcut} for JavaScript static
-    analysis to leverage the high performance of dynamic analysis.  We also
-    formally define it with sealed symbolic execution and prove the soundness of
-    static analysis using dynamic shortcut.
-  \item We actualize dynamic shortcut technique in $\tool$, which is an
-    extension of an existing JavaScript static analyzer SAFE with a dynamic
-    analyzer Jalangi.
+\item We present a novel technique for JavaScript static
+analysis to leverage the high performance of dynamic analysis by taking
+multiple dynamic shortcuts.  We formally define the technique and prove
+its soundness and termination.
+\item We actualize the proposed technique in $\tool$, an
+extended combination of existing analyzers SAFE and Jalangi.
 \item For empirical evaluation, we analyzed \inred{77} official tests of
-    \inred{Lodash 4} library with randomly abstracted values.  Our tool
-    accelerates \inred{X.X}x the static analysis on average.  Moreover, it
-    improves \inred{XX.XX}\% of analysis precision by using dynamic shortcut
-    instead of manual modeling for \inred{XX.X} opaque functions on average.
+\inred{Lodash 4} library.  The experiment shows that $\tool$ outperforms
+SAFE \inred{X.X}x on average.  Moreover, by using dynamic shortcuts
+instead of manual modeling for \inred{XX.X} opaque functions,
+$\tool$ improves \inred{XX.XX}\% of the analysis precision on average.
 \end{itemize}
@@
 motivation of this work with a simple example.  Section~\ref{sec:formal}
-formalizes adding dynamic shortcuts on abstract interpretation.  We extended the
-formalization with JavaScript specific language features with a core language in
-Section~\ref{sec:javascript}.  Section~\ref{sec:implementation} describes
-key techniques to implement dynamic shortcuts for JavaScript static analysis.
-We describes evaluation result of our techniques with real-world benchmarks in
-Section~\ref{sec:eval}.  Section~\ref{sec:related} explains related works and
+formalizes the language-agnostic part of the technique in the abstract
+interpretation framework.  Then, we extend the formalization with
+JavaScript specific features in Section~\ref{sec:javascript}.
+Section~\ref{sec:implementation} describes important details of the
+$\tool$ implementation.  We explain the evaluation results of $\tool$
+with real-world benchmarks in Section~\ref{sec:eval}.
+Section~\ref{sec:related} discusses related work and
 Section~\ref{sec:conclusion} concludes.

### 2020-11-19 paper/pldi21/report/def.tex
Changed the formal definition

--- 2020-10-29 paper/pldi21/combined.tex
@@
-\section{Combined Analysis}\label{sec:formal}
+\section{Definition of Dynamic Shortcut}\label{sec:def}
 
-In this section, we formally define the combined analysis with sealed symbolic
-execution.  We extend the formalization of abstract interpretation and analysis
-sensitivity proposed by \citet{sens-toplas}.
+In this section, we introduce the formal definition of dynamic shortcut based on
+sealed symbolic execution in abstract interpretation.
 
-\subsection{Concrete Semantics}
+\subsection{Abstract Interpretation}
+
+We first define the traditional abstract interpretation.
+
+\subsubsection{Concrete Semantics}
 
@@
 
-\begin{figure}[H]
-  \[
-    \begin{array}{l}
-      \enspace \labdot{0} \; \varx = \;? \; ;  \; \labdot{1}\\
-      \enspace \kwif \; (\; \varx \geq 0 \;) \; \labdot{2} \; \varx = \varx ;\\
-      \enspace \kwelse \; \labdot{3} \; \varx = -\varx ;  \; \labdot{4}\\
-    \end{array}
-  \]
-\vspace*{-1em}
-\caption{Conditional branch}
-\label{fig:running-example}
-\end{figure}
+\subsubsection{Abstract Interpretation}
 
-For example, the code in Figure~\ref{fig:running-example} is a simple program
-that applies the mathematical absolute value function to the variable $\varx$.
-The question mark $?$ denotes the user input that returns an integer.  States
-are pairs of labels and integers $\varx$: $\stset = \labset \times \mathbb{N}$.
-The initial states are $\istset = \{ (\lab_0, 0) \}$ which means the program
-starts with the varible $\varx$ that stores 0 at $\lab_0$.  If the user input is
-$-42$, the program is executed with the following trace:
-\[
-  (\lab_0, 0) \trans (\lab_1, -42) \trans (\lab_3, -42) \trans (\lab_4, 42)
-\]
-
-\subsection{Abstract Interpretation}
-The abstract interpretation~\cite{abs-interp-1977, abs-interp-1992}
-over-approximates the transfer $\transfer$ to the \textit{abstract transfer
-function} $\abstransfer: \absdom \rightarrow \absdom$ to get the
-\textit{abstract semantics} $\abssem{\prog}$ in finite iterations as follows:
+The abstract interpretation over-approximates the transfer $\transfer$ to the
+\textit{abstract transfer function} $\abstransfer: \absdom \rightarrow \absdom$
+to get the \textit{abstract semantics} $\abssem{\prog}$ in finite iterations as
+follows:
 \[
@@
 
-A simple example abstract domain is $\absdom_\pm = \powerset{\{ -, +, 0 \}}$ with
-set operators as domain operators; $-$ denotes negative integers, $+$ positive
-integers, and $0$ zero.  If we use it for the code in
-Figure~\ref{fig:running-example}, the analysis result becomes $\{ -, +, 0 \}$
-because $\varx$ can have any integers at $\lab_1$.
-
-\subsection{Analysis Sensitivity}
+\subsubsection{Analysis Sensitivity}
 
@@
 
-One of the most widely-used analysis sensitivity is \textit{flow sensitivity}
-defined with the flow-sensitive view abstraction $\fsviewmap: \labset
-\rightarrow \dom$ where
+\subsection{Dynamic Shortcut}
+
+We define dynamic shortcut by combining the sensitive abstract interpretation
+with sealed symbolic execution.
+
+\subsubsection{Sealed Symbolic Execution}
+
+We define \textit{sealed symbolic execution} by extending the transition
+relation $\trans$ as a symbolic transition relation $\symbtrans$ on symbolic
+states.  First, we augment concrete states $\stset$ to symbolic states
+$\symbstset$ by extending values $\valset$ with \textit{sealed symbolic values}
+$\symbset$.  We also define the symbolic transition relation $\symbtrans
+\subseteq \symbstset \times \symbstset$. We use the notation $\symbtrans^k$
+for $k$ repetition of $\symbtrans$, and  $\symbst \symbtrans \excst$ when
+$\symbst$ does not have symbolic transitions with any other symbolic states.  We
+also define the soundness of sealed symbolic execution as follows:
+\begin{definition}{(Soundness)}
+  The symbolic transition relation is \textit{sound} when the following
+  condition is satisfied:
   \[
-  \forall \lab\in\labset. \; \fsviewmap(\lab) = \{ \st \mid \st = (\lab, \_) \}
-\]
-If we apply the flow sensitivity for the above example, the analysis result
-becomes as follows:
-\[
-  \begin{array}{|c||c|c|c|c|c|}\hline
-    \labset & \lab_0 & \lab_1 & \lab_2 & \lab_3 & \lab_4\\\hline
-    \absdom_\pm & 0 & -, +, 0 & +, 0 & - & +, 0\\\hline
+    \begin{array}{l}
+      \forall \imap \in \imapset. \; \forall \symbst, \symbst' \in \symbstset.\\
+      \symbst \symbtrans \symbst' \Rightarrow \instant{\symbst}{\imap} \trans
+      \instant{\symbst'}{\imap}
     \end{array}
   \]
+  where $\imapset: \symbset \rightarrow \valset$ is instantiation maps from
+  symblic values to real values, and $\instant{\symbst}{\imap}$ denotes a state
+  produced by replacing each symbolic value $\symb$ to the corresponding value
+  $\imap(\symb)$ using the instantiation map $\imap \in \imapset$.
+\end{definition}
 
-\subsection{Sealed Symbolic Execution}
+Note that the main difference of sealed symbolic execution with the traditional
+symbolic execution is that it only supports sealed symbolic values instead of
+symbolic expressions and path constraints.
 
-To handle abstract values in concrete semantics, we define \textit{sealed
-symbolic execution} by extending the transition relation $\trans$ as a symbolic
-transition relation $\symbtrans$ on symbolic states.  First, we extends the
-concrete states $\stset$ to symbolic states with \textit{sealed symbolic values}
-$\symbset$.  A symbolic transition relation $\symbtrans \subseteq \symbstset
-\times (\symbstset \uplus \{ \excst \})$ is exactly the same with the original
-transition relation $\trans$ except when the relation requires the exact value
-of sealed symbolic values.  In this case, the symbolic state has the relation a
-special exception state $\excst$ to represent that it is impossible to interpret
-in a concrete way.  Thus, a symbolic state \textit{always} has a symbolic
-transition relation with a single symbolic state, and the sealed symbolic
-execution is linear until being terminated or reaching the exception state
-$\excst$.
+\subsubsection{Combined Domain}
 
-The main difference of sealed symbolic execution with the traditional symbolic
-execution~\cite{symbolic} is that it only supports sealed symbolic values
-instead of symbolic expressions and path constraints.  For example, the
-following trace represents the traditional symbolic execution of the running
-example in Figure~\ref{fig:running-example}:
+We define a \textit{combined domain} $\combdom = \sabsdom \times
+\powerset{\symbstset}$ as a pair of a sensitive abstract domain and a set of
+sealed symbolic states.   The join operator of combined states is defined in an
+element-wise manner:
 \[
-  \begin{array}{r@{~}c@{~}l}
-    &&(\lab_2, \symb)[\symb \geq 0] \trans (\lab_4, \symb)[\symb \geq 0]
-    \vspace*{-0.5em}\\
-    &\rutrans&
-    \vspace*{-0.5em}\\
-    (\lab_0, 0)[] \trans (\lab_1, \symb)[]&&
-    \vspace*{-0.5em}\\
-    &\rdtrans&
-    \vspace*{-0.5em}\\
-    &&(\lab_3, \symb)[\symb < 0] \trans (\lab_4, -\symb)[\symb < 0]\\
-  \end{array}
+  \forall (\sabselem, S), ({\sabselem}', S') \in \combdom. \;
+  (\sabselem, S) \join ({\sabselem}', S') = (\sabselem \join {\sabselem}', S \cup S')
 \]
-It first assigns a symbolic value $\symb$ to the variable $\varx$ at $\lab_1$.
-For the conditional branch, it is forked by creating two symbolic states with
-different path conditions $\symb \geq 0$ and $\symb < 0$ for true and false
-branches, respectively.  After executing statements $\varx = \varx$ and $\varx =
--\varx$, the variable $\varx$ stores symblic expressions $\symb$ and $-\symb$ at
-$\lab_4$.  However, the sealed symbolic execution stops at $\lab_1$ as follows:
-\[
-  (\lab_0, 0) \; \symbtrans \; (\lab_1, \symb) \; \symbtrans \; \excst
-\]
-because the branch requires the actual value of the symbolic value $\symb$.
 
-To freely convert a pair of view and an abstract state to its corresponding
-symbolic state and vice versa, we define two domain converters $\symbstset
-\galois{\saconverter}{\asconverter} (\viewset \times \absdom)$.  In the
-converter $\asconverter$ from abstract states to symbolic states, if an abstract
-value $\absval$ represents a singleton value, the function transforms the
-abstract value to the corresponding concrete value.  Otherwise, it converts the
-abstract value as a symbolic value in a result symbolic state.  Two converters
-convert given elements wihtout loss of information:
+To freely convert a pair of view and an abstract state to its
+corresponding symbolic state and vice versa, we define two domain converters
+$\symbstset \galois{\saconverter}{\asconverter} (\viewset \times \absdom)$.  In
+the converter $\asconverter$ from abstract states to symbolic states, if an
+abstract value $\absval$ represents a singleton value, the function transforms
+the abstract value to the corresponding concrete value.  Otherwise, it converts
+the abstract value as a symbolic value in a result symbolic state.  Two
+converters convert given elements without loss of information:
 \[
@@
 
-\subsection{Combined Analysis}
-
-We define the \textit{combined analysis} of the abstract interpretation and the
-sealed symbolic execution.  In the combined analysis, we use the powerset of
-symbolic states as the domain $\combdom = \powerset{\symbstset}$, and extend the
-view transition as follows:
+An analysis element $\aelem \in \aelemset = (\viewset \times \absdom) \uplus
+\symbstset$ is either a pair of a view and an abstract state or a sealed
+symbolic state.  We define a $\atriage$ function using two converters between
+analysis elements as follows:
+\begin{definition}[$\atriage$]
+  The triage function $\atriage: \aelemset \rightarrow \aelemset$ for analysis
+  elements is defined as
   \[
-  \begin{array}{l}
-    \combviewtrans{\view}{\view'}(\combelem) =\\
-    \qquad \{
-      \symbst' \mid \symbst \in S \wedge
-      \symbst \symbtrans \symbst' \wedge
-      \saconverter(\symbst') = (\view', \_)
-    \}\\
-    \qquad \cup \left\{
+    \atriage(\aelem) = \left\{
       \begin{array}{ll}
-      \{ \asconverter \circ \viewtrans{\view}{\view'}(\bigjoin D) \}
-      & \text{if} \; D \neq \varnothing\\
-      \varnothing & \text{otherwise}\\
+        \asconverter(\aelem)
+        & \text{if} \; \aelem = (\view, \abselem) \wedge \checker(\aelem)\\
+        \saconverter(\aelem)
+        & \text{if} \; \aelem = \symbst \wedge \symbst \symbtrans \symbst'\\
+        \aelem
+        & \text{Otherwise}
       \end{array}
     \right.
-  \end{array}
   \]
-where $S = \combelem\mid_{\checker}$ and $D =
-\dot{\saconverter}(\combelem\mid_{\neg\checker})$.  The dot notation $\dot{f}$
-denotes the element-wise extended function of a function $f$.  We could
-configure when the sealed symbolic execution or the abstract interpretation
-is performed based on the definition of the $\checker$ function and its negation
-$\neg\checker$.  It should satisfy the following condition for the soundness and
-the termination of the combined analysis:
+  where the function $\checker$ decides whether to perform sealed symbolic
+  execution instead of abstract interpretation.
+\end{definition}
+Using the $\atriage$ function for analysis elements, we defined the $\triage$
+function for combined states:
+\begin{definition}[$\triage$]
+  The triage function $\triage: \combdom \rightarrow \combdom$ for combined
+  states is defined as
   \[
-  \checker(\symbst) \Rightarrow \symbst \symbtrans^k \excst \wedge
-  1 < k \leq N
+    \triage((\sabselem, S)) = \left(
+      \lambda \view. \;  \bigjoin \{ \abselem \mid (\view, \abselem) \in E \},
+      E \cap \symbstset
+    \right)
+  \]
+  where
+  \[
+    E = \dot{\atriage}(\{ (\view, \abselem) \mid \view \in \viewset \wedge
+    \sabselem(\view) = \abselem \} \cup S)
+  \]
+\end{definition}
+The dot notation $\dot{f}$ denotes the element-wise extended function of a
+function $f$.
+
+We could configure when the sealed symbolic execution or the abstract
+interpretation is performed based on the definition of the $\checker$ function.
+For example, we could define the $\checker$ that passes only function entry,
+call, and exit points to perform conversions in a function level.  For the
+soundness and the termination of the the abstract interpretation with dynamic
+shortcuts, it should satisfy the following condition:
+\begin{theorem}\label{theorem:shortcut}
+  The abstract interpretation with dynamic shortcut is sound and terminates in a
+  finite time if its abstract semantics is sound and $\checker$ satisfies the
+  following condition:
+  \[
+    \checker((\view, \abselem)) \Rightarrow \asconverter((\view, \abselem))
+    \symbtrans^k \excst \wedge 1 < k \leq N
   \]
   where $N$ is a pre-defined maximum length of the sealed symbolic execution.
-The combined analysis just performs one-step symbolic transition for each
-symbolic state that passes the filter $\checker$. On the other hand, it converts
-remaining symbolic states to the corresponding abstract states, merges them into
-a single abstract state, and performs the abstract one-step execution for the
-abstract state.
+\end{theorem}
+
+In the remaining section, we will prove this theorem using the Kleene's
+fixed-point theorem with the finite height of abstract domains.

### 2020-11-19 paper/pldi21/report/def.tex
Modified definition

@@
 A \textit{sensitive state abstraction} $\dom
-\galois{\alpha_\viewmap}{\gamma_\viewmap} \sabsdom$ is a Galois connection between
+\galois{\alpha_\viewmap}{\sgamma} \sabsdom$ is a Galois connection between
 the concrete domain $\dom$ and the sensitive abstract domain $\sabsdom$ with the
@@
 \[
-  \gamma_\viewmap(\sabselem) = \{ \st \in \stset \mid \forall \view \in \viewset.
+  \sgamma(\sabselem) = \{ \st \in \stset \mid \forall \view \in \viewset.
   \; \st \in \viewmap(\view) \Rightarrow \st \in \gamma \circ \sabselem(\view) \}
@@
 
+We also define an \textit{abstract instantiation map} $\absimap \in \absimapset:
+\symbset \rightarrow \absvalset$ with abstract values $\absvalset$.  Its
+concretization function $\imapgamma: \absimapset \rightarrow
+\powerset{\imapset}$ is defined with the concretization function $\valgamma:
+\absvalset \rightarrow \powerset{\valset}$ for values as follows:
+\[
+  \imapgamma(\absimap) = \{
+    \imap \mid \forall \symb \in \symbset. \;
+    \imap(\symb) \in \gamma \circ \absimap(\symb)
+  \}
+\]
+We define the instantiation of a given sealed symbolic state $\symbst \in
+\symbstset$ with an abstract instantiation map $\absimap \in \absimapset$ as
+follows:
+\[
+  \instant{\symbst}{\absimap} = \{ \instant{\symbst}{\imap} \mid \imap \in
+  \imapgamma(\absimap) \}
+\]
+
+\begin{definition}[Sealed Symbolic Domain]
+  We define \textit{sealed symbolic domain} $\symbdom: \powerset{\absimapset
+  \times \symbstset}$ with the following concretization function $\symbgamma:
+  \symbdom \rightarrow \dom$ and sealed symbolic one-step execution $\symbstep:
+  \symbdom \rightarrow \symbdom$ as follows:
+  \begin{itemize}
+    \item \(
+      \symbgamma(\symbelem) = 
+      \bigcup \{ \instant{\symbst}{\absimap} \mid (\absimap, \symbst) \in
+      \symbelem\}
+    \)
+    \item \(
+      \symbstep(\symbelem) = \{ (\absimap, \symbst') \mid (\absimap, \symbst)
+      \in \symbelem \wedge \symbst \symbtrans \symbst' \}
+    \)
+  \end{itemize}
+\end{definition}
+
 \subsubsection{Combined Domain}
 
-We define a \textit{combined domain} $\combdom = \sabsdom \times
-\powerset{\symbstset}$ as a pair of a sensitive abstract domain and a set of
-sealed symbolic states.   The join operator of combined states is defined in an
-element-wise manner:
+\begin{definition}[Combined Domain]
+  We define a \textit{combined domain} as $\combdom = \sabsdom \times \symbdom$
+  with the following concretization function and join operator:
+  \begin{itemize}
+    \item \(
+      \combgamma((\sabselem, \symbelem)) = \sgamma(\sabselem) \cup
+      \symbgamma(\symbelem)
+    \)
+    \item \(
+      (\sabselem, \symbelem) \join ({\sabselem}', \symbelem') = (\sabselem \join
+      {\sabselem}', \symbelem \cup \symbelem')
+    \)
+  \end{itemize}
+\end{definition}
+
+An analysis element $\aelem \in \aelemset = (\viewset \times \absdom) \uplus
+(\absimapset \times \symbstset)$ is either a pair of a view and an abstract
+state or a sealed symbolic state.  To freely convert a pair of a view and an
+abstract state to its corresponding pair of an abstract instantiation map and a
+sealed symbolic state, we define two domain converters: \begin{itemize} \item
+$\asconverter: (\viewset \times \absdom) \hookrightarrow (\absimapset \times
+\symbstset)$ \item $\saconverter: (\viewset \times \absdom) \leftarrow
+(\absimapset \times \symbstset)$ \end{itemize} The converter $\asconverter$ is a
+\textit{partial function} and it is applicable when it is possible to represent
+a given abstract state in a specific view as a pair of abstract instantiation
+map and a sealed symbolic state.  Two converters should convert given elements
+without loss of information:
 \[
-  \forall (\sabselem, S), ({\sabselem}', S') \in \combdom. \;
-  (\sabselem, S) \join ({\sabselem}', S') = (\sabselem \join {\sabselem}', S \cup S')
+  \forall \view \in \viewset, \abselem \in \absdom.
 \]
-
-To freely convert a pair of view and an abstract state to its
-corresponding symbolic state and vice versa, we define two domain converters
-$\symbstset \galois{\saconverter}{\asconverter} (\viewset \times \absdom)$.  In
-the converter $\asconverter$ from abstract states to symbolic states, if an
-abstract value $\absval$ represents a singleton value, the function transforms
-the abstract value to the corresponding concrete value.  Otherwise, it converts
-the abstract value as a symbolic value in a result symbolic state.  Two
-converters convert given elements without loss of information:
 \[
-  \saconverter \circ \asconverter = \asconverter \circ \saconverter = \identity
+  \asconverter((\view, \abselem)) = (\absimap, \symbst)
+  \Rightarrow \left\{
+  \begin{array}{l}
+    (\view, \abselem) = \saconverter((\absimap, \symbst))\\\
+    \viewmap(\view) \cap \gamma(\abselem) = \instant{\symbst}{\absimap}\\
+  \end{array}
+  \right.
 \]
@@
 
-An analysis element $\aelem \in \aelemset = (\viewset \times \absdom) \uplus
-\symbstset$ is either a pair of a view and an abstract state or a sealed
-symbolic state.  We define a $\atriage$ function using two converters between
-analysis elements as follows:
+We define a $\atriage$ function using two converters between analysis elements
+as follows:
 \begin{definition}[$\atriage$]
@@
         \asconverter(\aelem)
-        & \text{if} \; \aelem = (\view, \abselem) \wedge \checker(\aelem)\\
+        & \text{if} \; \aelem = (\view, \abselem) \wedge \aelem \in
+        \Dom(\asconverter)\\
         \saconverter(\aelem)
-        & \text{if} \; \aelem = \symbst \wedge \symbst \symbtrans \symbst'\\
+        & \text{if} \; \aelem = (\absimap, \symbst) \wedge \symbst \symbtrans \symbst'\\
         \aelem
@@
   \]
-  where the function $\checker$ decides whether to perform sealed symbolic
-  execution instead of abstract interpretation.
 \end{definition}
@@
   \[
-    \triage((\sabselem, S)) = \left(
-      \lambda \view. \;  \bigjoin \{ \abselem \mid (\view, \abselem) \in E \},
-      E \cap \symbstset
+    \triage((\sabselem, \symbelem)) = \left(
+      \lambda \view. \bigjoin \{ \abselem \!\mid\! (\view, \abselem) \in E \},
+      E \cap (\absimapset \times \symbstset)
     \right)
@@
     E = \dot{\atriage}(\{ (\view, \abselem) \mid \view \in \viewset \wedge
-    \sabselem(\view) = \abselem \} \cup S)
+    \sabselem(\view) = \abselem \} \cup \symbelem)
   \]
@@
 
+\begin{definition}[Combined One-Step Execution]
+  We define the combined one-step execution $\combstep: \combdom \rightarrow
+  \combdom$ is define as follows:
+  \[
+    \combstep(\combelem) = (
+      \sabsstep(\sabselem),
+      \symbstep(\symbelem)
+    )
+  \]
+  where $(\sabselem, \symbelem) = \triage(\combelem)$.
+\end{definition}
+
 We could configure when the sealed symbolic execution or the abstract
-interpretation is performed based on the definition of the $\checker$ function.
-For example, we could define the $\checker$ that passes only function entry,
-call, and exit points to perform conversions in a function level.  For the
-soundness and the termination of the the abstract interpretation with dynamic
-shortcuts, it should satisfy the following condition:
+interpretation is performed based on the definition of the converter
+$\asconverter$.  For example, we could define the $\asconverter$ for analysis
+elements related to only function entry, call, and exit points to perform
+conversions in a function level.  For the soundness and the termination of the
+the abstract interpretation with dynamic shortcuts, it should satisfy the
+following condition:
 \begin{theorem}\label{theorem:shortcut}
   The abstract interpretation with dynamic shortcut is sound and terminates in a
-  finite time if its abstract semantics is sound and $\checker$ satisfies the
+  finite time if its abstract semantics is sound and $\saconverter$ satisfies the
   following condition:
   \[
-    \checker((\view, \abselem)) \Rightarrow \asconverter((\view, \abselem))
-    \symbtrans^k \excst \wedge 1 < k \leq N
+    \asconverter((\view, \abselem)) = (\absimap, \symbst) \Rightarrow
+    \symbst \symbtrans^k \excst \wedge 1 < k \leq N
   \]

### 2020-11-20 paper/pldi21/intro.tex
Till Sec. 2

@@
 \section{Introduction}\label{sec:intro}
-Over the past decades, the rise of JavaScript as the de facto programming
+Over the past decades, the rise of JavaScript as the de facto
 language for web development has expanded its reach to diverse fields.
@@
 \item We present a novel technique for JavaScript static
-analysis to leverage the high performance of dynamic analysis by taking
-multiple dynamic shortcuts.  We formally define the technique and prove
+analysis to leverage the high performance of dynamic analysis using
+dynamic shortcuts.  We formally define the technique and prove
 its soundness and termination.
 \item We actualize the proposed technique in $\tool$, an
-extended combination of existing analyzers SAFE and Jalangi.
+extended combination of SAFE and Jalangi.
 \item For empirical evaluation, we analyzed \inred{77} official tests of

### 2020-11-20 paper/pldi21/motivation.tex
Till Sec. 2

@@
     \vspace*{-1em}
-    \caption{Lodash's \jscode{concat} function.}
+    \caption{Lodash's \jscode{concat} function}
     \label{fig:concat}
@@
     \begin{lstlisting}[style=myJSstyle,firstnumber=13]
-function changeCountry(G) {
-  ...
+function changeCountry(G) { ...
   if (G.selectedVal === "US" && state) {
@@
     \vspace*{-1em}
-    \caption{Load the list of states of the United States.}
+    \caption{Call of \jscode{concat} with concrete values}
     \label{fig:changeCountry}
@@
 function getData(e) {
-  var option = ... // option of server connection
+  var option = ... // option for server connection
   post(option).then(function(e) {
@@
     \vspace*{-1em}
-    \caption{Load more Zoom events from the server.}
+    \caption{Call of \jscode{concat} with abstract values}
     \label{fig:getData}
@@
   \vspace*{-1em}
-  \caption{Motivating Example: Excerpts from Lodash library and JavaScript codes
-  in \code{zoom.us} site.}
+  \caption{Lodash library function and its uses in \code{zoom.us}}
   \label{fig:example}
@@
 
-In this section, we will explain the motivation of the dynamic shortcut for
-JavaScript static analysis with real-world examples described in
-Figure~\ref{fig:example}.  We first describe their program behaviors and then
-explain how to utilize dynamic analysis during static analysis of them.
+In this section, we explain the motivation of dynamic shortcuts
+using real-world examples shown in Figure~\ref{fig:example}.
+We first describe their behaviors and then explain how we can utilize
+dynamic shortcuts during their static analysis.
 
-For motivating examples, we excerpt the \jscode{concat} function in
-Figure~\ref{fig:concat} from Lodash library~\cite{lodash} (v4.17.20), which is
+Figure~\ref{fig:example}(a) shows the \jscode{concat} function defined
+in Lodash library~\cite{lodash} (v4.17.20); it is
 the most popular npm package\footnote{https://www.npmjs.com/browse/depended}
-and \inred{124,562} npm packages have dependency with it.  The \jscode{concat}
-function creates a new array concatenating given arrays or values.  It first
-checks the length of arguments in line 1-3. Then, it stores the first argument
-to \jscode{array} in line 4 and copies the remaining arguments to \jscode{args} in
-line 5-8.  In line 9, it checks whether \jscode{array} is an array object with
-the built-in function \jscode{isArray}.  If so, it creates a new array by
-copying the given array via or initializing with a single value in line 10.
-Finally, it flattens \jscode{args} via \jscode{baseFlatten} and pushes the
-result to the new array in line 11.
+and \inred{124,562} npm packages have a dependency on it.
+The \jscode{concat} function creates a new array concatenating given arrays or values.
+It first checks the length of \jscode{arguments} on lines 1--3.
+Then, it stores the first argument to \jscode{array} on line 4 and
+copies the remaining arguments to \jscode{args} on lines 5--8.
+On line 9, it checks whether \jscode{array} is an array object using
+the built-in function \jscode{isArray}.  If so, it creates a new array
+by copying the given array via \jscode{copyArray}; otherwise,
+it creates a singleton array \jscode{[array]}.  Finally, it flattens
+\jscode{args} via \jscode{baseFlatten} and pushes the result to the
+new array on line 11.
 
-For applications of Lodash, we excerpt two functions \jscode{changeCountry} in
-Figure~\ref{fig:changeCountry} and \jscode{getData} in Figure~\ref{fig:getData}
-from the \code{zoom.us}~\cite{zoom} site.  The website \code{zoom.us} is
-homepage of Zoom, which is a videotelephony software program developed by Zooom
-Video Communications and it is ranked as \inred{16th} popular web site according
+Figure~\ref{fig:example}(b) and Figure~\ref{fig:example}(c) show use
+cases of the \jscode{concat} function in the \code{zoom.us}~\cite{zoom} site.
+It is the homepage of Zoom, which is a videotelephony software program developed by Zoom
+Video Communications and it is ranked as the \inred{16th} popular web site according
 to Alexa\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.
 
-\paragraph{Dynamic shortcut with concrete values.}
-When the given arguments of a function are concrete values, we can perform
-dynamic analysis instead of static analysis. For example, the
-\jscode{changeCountry} function is invoked when a user selects another country
-on the drop-down list in the registration page.  It calls the \jscode{concat}
-function to update the drop-down list of states or provinces in 17-18.  However,
-when the user selects ``United States of America'' (USA), two arguments are
-pre-defined with deterministic values; the first one is an array literal
-\jscode{[["Other", "Other"]]} and the second one is an array of pairs of
-abbreviations and names of the states defined as follows:
+\paragraph{Dynamic shortcuts with concrete values.}
+When a function is called with concrete values, we can perform
+dynamic analysis instead of static analysis.
+For example, \jscode{changeCountry} in Figure~\ref{fig:example}(b)
+is invoked when a user selects a country from a drop-down list in the registration page.
+It calls the \jscode{concat} function to update the drop-down list of
+states or provinces on lines 17--18.  However, when the user selects ``United States of America,''
+which is \jscode{"US"}, two arguments are pre-defined with
+deterministic values; the first one is an array literal
+\jscode{[["Other", "Other"]]} and the second one is an array of pairs
+of abbreviations and names of the states defined as follows:
 \begin{lstlisting}[style=myJSstyle,numbers=none]
@@
 \end{lstlisting}
-Moreover, \jscode{this} value is also a concrete value, the Lodash top-level
-object \jscode{\_}.  Thus, we could perform dynamic analysis by invoking the
-\jscode{concat} function with \jscode{\_} as \jscode{this} value and above two
-concrete values as arguments.  It increases performance of static analysis by
-skipping the analysis of function call in line 17-18 and utilizing the result of
-dynamic analysis.
+Moreover, \jscode{this} also has a concrete value, the Lodash top-level object \jscode{\_}.
+Thus, we can perform dynamic analysis by invoking \jscode{concat} with
+\jscode{\_} as its \jscode{this} value and the above concrete values as arguments. 
+By skipping the analysis of the function call on lines 17--18 and
+utilizing the result of dynamic analysis, it improved the analysis performance.
 
@@
   \vspace*{-1em}
-  \caption{Concrete objects for arguments with sealed symbolic values.}
+  \caption{Concrete objects with sealed symbolic values}
   \label{fig:sealed}
@@
 
-\paragraph{Dynamic shortcut with abstract values.}
-Dynamic analysis is still applicable using \textit{sealed symbolic execution}
-even if the arguments are not concrete values.  The \jscode{getData} function is
-invoked when clicking the ``Load More'' button to load more Zoom events in
-``Webinars \& Events'' page.  For each click, the \jscode{getData} sends a POST
-request to the server and receives additional event information \jscode{e} in
+\paragraph{Dynamic shortcuts with abstract values.}
+Even when a function is called with abstract values, we can still
+perform dynamic analysis using sealed symbolic execution.
+For example, \jscode{getData} in Figure~\ref{fig:example}(c) is invoked
+when a user clicks the ``Load More'' button to load more Zoom events in
+the ``Webinars \& Events'' page.  It sends a POST
+request to a server and receives additional events \jscode{e} on
 line 24.  Then, eight events in \jscode{e.events} are appended to
-\jscode{this.pastEvents} using the \jscode{concat} function in line 27-28.
+\jscode{this.pastEvents} using \jscode{concat} on lines 27--28.
 However, the arguments of \jscode{concat} are not deterministic because 1) the
 event list stored in \jscode{this.pastEvents} is continuously grown for each
-load and 2) also each event stored in \jscode{e.events} are dependent on the
+load and 2) the events stored in \jscode{e.events} are dependent on the
 data given from the server.
 
-To perform dynamic analysis with abstract values, we sealed the abstract values
-of arguments with symbolic values as described in Figure~\ref{fig:sealed}.  It
-contains two symbolic values $\symbevt$ and $\symbint$ that represent any event
-objects and integer values, respectively.  Then, dynamic analysis is
-successfully performed before copying \jscode{array} via \jscode{copyArray} in
-line 10.  First, \jscode{length} stores \jscode{2} and passes the length check
-in line 1-2. Then, \jscode{array} points to the same object of
-\jscode{this.pastEvents} in line 4, \jscode{args} stores an array with a
-single object stored in \jscode{e.events} in 5-8, and the \jscode{isArray}
-function returns \jscode{true} for \jscode{array} in line 9.  However, it fails
-to perform dynamic analysis for \jscode{copyArray} because the \jscode{length}
-property of \jscode{array} is the symbolic value $\symbint$.  Thus, the dynamic
-shortcut returns the analysis result and the static analyzer continues to
-analyze the program from line 10.  Then, only copying via \jscode{copyArray},
-flattening via \jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize
-the abstract semantics.  This is how to utilize sealed symbolic execution to
-maximize the part of dynamic analysis during static analysis.
+To perform dynamic analysis with abstract values, we seal abstract values
+with symbolic values as in Figure~\ref{fig:sealed}.  Two symbolic
+values $\symbevt$ and $\symbint$ represent an event
+object and an integer, respectively.  Then, we can perform dynamic analysis
+successfully until line 9.  On line 2, \jscode{length} is \jscode{2};
+on line 4, \jscode{array} points to \jscode{this.pastEvents};
+on lines 5--8, \jscode{args} stores an array with a single object stored in \jscode{e.events};
+and on line 9, \jscode{isArray(array)} is \jscode{true}.
+However, dynamic analysis fails for \jscode{copyArray(array)} on line 10
+because the value of the \jscode{length} property of \jscode{array} is the symbolic value $\symbint$.
+Then, we stop the sealed symbolic execution, convert the current
+sealed symbolic state to its corresponding abstract state, and resume
+the static analysis from line 10.  Because sealed symbolic execution
+leverages fast dynamic analysis as long as possible, the overall
+analysis becomes more scalable.
 
-\paragraph{Dynamic shortcut for opaque functions.}
-
-The previous two examples also show that dynamic shortcut can improve the
-analysis precision and lessen the effort of modeling the opaque functions.
-In line 9, the \jscode{isArray} function is a JavaScript built-in library thus
-it is written in a native language of the host environment.  Thus, we need to
-manually model its behavior to statically analyze it.  Assume that we model the
-\jscode{isArray} function to return the top boolean value that denotes both of
-\jscode{true} and \jscode{false}.  If we perform static analysis with this
-modeling, both of true branch \jscode{copyArray(array)} and false branch
-\jscode{[array]} in line 10 are always analyzed while \jscode{[array]} is never
-reachable in the motivating examples.  However, with the dynamic shortcut, the
-analyzer utilizes the concrete semantics of \jscode{isArray}.  It returns more
-precise result \jscode{true} instead of the top boolean value and it is not
-necessary to model the \jscode{isArray} function for static analysis of
-motivating examples.
+\paragraph{Dynamic shortcuts for opaque functions.}
+As the previous two examples additionally show, using dynamic shortcuts 
+lessens the burden of modeling opaque functions from static analysis, and
+it can even improve the analysis precision.
+On line 9, since the \jscode{isArray} function is a JavaScript built-in library function,
+it is implemented in a native language of the host environment, which
+often requires manual modeling of its behaviors for JavaScript static analysis.
+Assuming that a static analyzer models \jscode{isArray} to return the
+boolean top value $\top_b$ that encompasses both \jscode{true} and \jscode{false},
+static analysis of the ternary conditional expression on lines 9--10 analyzes
+both branches \jscode{copyArray(array)} and \jscode{[array]}, even though
+\jscode{[array]} is never reachable in the example code.  On the contrary,
+using dynamic shortcuts, static analysis does not need to model \jscode{isArray}.
+It can perform sealed symbolic execution for \jscode{isArray}, which
+returns a more precise result \jscode{true} than $\top_b$.

### 2020-11-20 paper/pldi21/report/def.tex
Minor change in report

@@
 following condition:
-\begin{theorem}\label{theorem:shortcut}
+\begin{theorem}[Soundness and Termination]\label{theorem:shortcut}
   The abstract interpretation with dynamic shortcut is sound and terminates in a
@@
   following condition:
-  \[
+  \begin{equation}\label{expr:condition}
     \asconverter((\view, \abselem)) = (\absimap, \symbst) \Rightarrow
     \symbst \symbtrans^k \excst \wedge 1 < k \leq N
-  \]
+  \end{equation}
   where $N$ is a pre-defined maximum length of the sealed symbolic execution.

### 2020-11-20 paper/pldi21/implementation.tex
Revised Sec. 5

@@
 \section{Implementation}\label{sec:implementation}
-
-We have implemented the dynamic shortcut for JavaScript static analysis
-presented in Section~\ref{sec:javascript} in a prototype implementation called
+We implemented JavaScript static analysis using dynamic shortcuts
+presented in Section~\ref{sec:javascript} in a prototype implementation dubbed
 $\tool$.  The tool is an extension of an existing state-of-the-art JavaScript
 static analyzer SAFE~\cite{safe, safe2} with a dynamic analyzer
-Jalangi~\cite{jalangi}, and it is open source and available online~\footnote{The
+Jalangi~\cite{jalangi}, and it is an open-source project and available online~\footnote{The
 URL of the tool is anonymized due to a double-blind review process.}.  In this
-section, we introduce challenges and solutions when implementing dynamic
-shortcut on existing JavaScript analyzers.
+section, we introduce challenges and solutions in implementing dynamic
+shortcuts on existing JavaScript analyzers.
 
 \paragraph{Sealed Symbolic Values.}
-The main challenge of implementing dynamic shortcut is to support the sealed
-symbolic execution on the existing JavaScript engine.  To represent an abstract
+The main challenge of implementing dynamic shortcuts is to support sealed
+symbolic execution on an existing JavaScript engine.  To represent an abstract
 value, we leverage the \jscode{Proxy} object introduced in ECMAScript 6
-(2015, ES6)~\cite{es6}, which allows developers to handle the internal behaviors
-of specific objects (such as property reads and writes, implicit conversions,
-etc.).  We are inspired by \textsc{Mimic}~\cite{mimic} using \jscode{Proxy} to
-capture accesses from the inside of opaque functions.  When the dynamic analyzer
-constructs the execution environments at the start of the dynamic shortcut, it
-creates revoked \jscode{Proxy} objects to represent each abstract values via the
+(2015, ES6)~\cite{es6}, which allows developers to handle internal behaviors
+of specific objects such as property reads and writes and implicit conversions.
+We are inspired by \textsc{Mimic}~\cite{mimic}, which used \jscode{Proxy} to
+capture accesses from internals of opaque functions.  When the dynamic analyzer
+constructs an execution environment at the start of a dynamic shortcut, it
+creates revoked \jscode{Proxy} objects to represent abstract values via the
 following \jscode{generateSymbol} function:
@@
 \end{lstlisting}
-The function creates a sealed symbol as a revocable proxy object with a dummy
-function object without any handlers and revokes it by
-\jscode{revocable.revoke()} to not allow any access of the symbol.  The revoked
-object throws a \jscode{TypeError} when the object faces 13 kinds of operations
-so we can determine whether or not the seal is open.  For example, the variable
-\jscode{y} successfully points to the same symbol stored in \jscode{x} but the
-program throws the \jscode{TypeError} in line 8 because \jscode{x + 1} requires
-the actual value of the symbol.  Moreover, we instrument unary and binary
-operations on Jalangi to fully cover accesses on the symbol beyond 13 traps
-provided by \jscode{Proxy}.  Using this idea, we successfully extend the
-JavaScript engine to support a sealed symbolic execution.
+The function creates a sealed symbol \jscode{r} as a revocable proxy object with a dummy
+function object without any handlers. It then revokes the symbol by
+\jscode{r.revoke()} not to allow any accesses of the symbol.  A revoked
+object throws a \jscode{TypeError} exception when any of 13 pre-defined operations
+are applied to the object, which enables us to determine whether an
+object is sealed or not.  For example, the variable
+\jscode{y} successfully points to the same symbol stored in \jscode{x}, but the
+program throws \jscode{TypeError} on line 8 because \jscode{x + 1} requires
+the actual value of the symbol.  In addition, we instrument unary and binary
+operations in Jalangi so that we can detect all the accesses on the
+symbol beyond the 13 operations provided by \jscode{Proxy}.
+Using this idea, we successfully extended the
+JavaScript engine to support sealed symbolic execution.
 
 \paragraph{Synchronization of Control Points.}
-For seamless interactions between the static analyzer and dynamic shortcuts,
-the synchronization of control points is a prerequisite.
-The static analyzer compiles a target JavaScript program to intermediate
-representation and builds a control flow graph.  It produces annotations for
-control points on the CFG including functions, call sites, and object allocation
-sites.  During the sealed symbolic execution, the dynamic analyzer requires
-those annotations to calculate sensitive location names of newly created object
-and lexical environments.  The key to place annotations on the instrumented code
-is the span information of the original AST node.  Both the CFG of SAFE and
-instrumented code of Jalangi maintain the span information, but they use
-different parsers resulting mismatches for some corner cases.  Thus, we
-preprocess to synchronize control points of two analyzers by the closest match
-of the span information rather than the exact match.
+For seamless interaction between static analysis and sealed symbolic execution,
+synchronization of control points in both worlds is a prerequisite.
+The SAFE static analyzer parses a JavaScript program to an Abstract
+Syntax Tree (AST), compiles it to its intermediate representation, and
+builds a Control Flow Graph (CFG).  It produces annotations for
+control points on the CFG including functions, call sites, and object allocation sites.
+On the contrary, the Jalangi dynamic analyzer instruments a JavaScript program 
+to keep track of necessary information at run time.  Therefore, during
+sealed symbolic execution, Jalangi requires the annotations from SAFE to compute
+abstract locations of newly created concrete objects and lexical environments.
+The key to put annotations on the instrumented code is the source-code
+location of the original AST node.  While both CFG of SAFE and
+instrumented code of Jalangi maintain the source-code location information,
+because they use different parsers we found various location mismatches for corner cases.
+Therefore, we synchronize control points of two analyzers by using the closest match
+of their source-code locations rather than using their exact match.
 
 \paragraph{Optimizations.}
-To perform dynamic shortcut, the static analyzer should communicate with the
-dynamic analyzer by passing the current abstract state and receiving the final
-result of the sealed symbolic execution.  When abstract states are massive, it
-is burden to send them as they stand.  Thus, we perform mark-and-sweep garbage
-collection to remove unreachable information in the current abstract state.
-Moreover, the abstract values are converted to the sealed symbolic values and
-their contents are not necessary in the dynamic analysis.  Thus, we replace
-abstract values with their unique identifiers and stores the table from
-identifiers to abstract values before sending the abstract state
-from the static analyzer.  Thus, the dynamic analyzer only receives identifiers
-of abstract values and wrap them as \jscode{Proxy} objects.  After finishing the
-sealed symbolic execution, the static analyzer recovers the abstract values in
-the result abstract state using the table.
+To use dynamic shortcuts, the static analyzer should communicate with the
+dynamic analyzer by passing abstract states and receiving results of sealed
+symbolic execution.  When abstract states are massive, sending
+abstract states and receiving sealed symbolic values as they are could
+incur large performance overhead.  Thus, we
+implemented mark-and-sweep garbage collection to remove unreachable
+information in abstract states.  In addition, because abstract values
+themselves are not used in sealed symbolic execution, we make a map
+from unique identifiers to abstract values and replace
+abstract values with their unique identifiers when we convert abstract
+values to sealed symbolic values.  Therefore, the dynamic analyzer
+receives only identifiers of abstract values and wraps them as
+\jscode{Proxy} objects.  After finishing sealed symbolic execution,
+the static analyzer recovers the abstract values in the results of
+sealed symbolic execution by replacing unique identifiers with their
+corresponding abstract values.
 
 \paragraph{Termination.}
-To guarantee the termination of static analysis with dynamic shortcut, the
-filter $\checker$ should pass the state $\symbst$ only when it terminates in a
-bound time $N$.  Since it is difficult to statically check its termination,
-we just performs the sealed symbolic execution with a time limit.  When it runs
-over the time limit, we treat it fails to pass $\checker$, otherwise we utilizes
-the result of the execution.  In the experiments, we set the time limit as
+To guarantee the termination of static analysis using dynamic shortcuts, the
+filter $\checker$ should pass a state $\symbst$ only when it terminates in a
+bound time $N$.  Since statically checking the termination property is a difficult task,
+we simply perform sealed symbolic execution with a pre-determined time limit.  When it runs
+over the time limit, we treat it as a failure to pass $\checker$; otherwise, we utilize
+the result of the sealed symbolic execution.  In our experiments, we set the time limit as
 \inred{5 seconds} for each sealed symbolic execution.

### 2020-11-20 paper/pldi21/shortcut.tex
Revised Sec. 5

@@
 that applies the mathematical absolute value function to the variable $\varx$.
-The question mark $?$ denotes the user input that returns an integer.  States
+The question mark $?$ denotes a user input that returns an integer.  States
 are pairs of labels and integers $\varx$: $\stset = \labset \times \mathbb{N}$.
@@
 defined with the flow-sensitive view abstraction $\fsviewmap: \labset
-\rightarrow \dom$ where
+\rightarrow \dom$ where:
 \[
@@
 symbolic execution} by extending the transition relation $\trans$ as a symbolic
-transition relation $\symbtrans$ on symbolic states.  First, we extends the
+transition relation $\symbtrans$ on symbolic states.  First, we extend the
 concrete states $\stset$ to symbolic states with \textit{sealed symbolic values}

### 2020-11-20 paper/pldi21/report/def.tex
Till Soundness in report

@@
 with $\cup$, $\cap$, and $\subseteq$ as its join($\join$), meet($\meet$), and
-partial order($\order$) operators.  The element $\ielem$ denotes the initial
-states $\istset$.  The \textit{one-step execution} $\step: \dom \rightarrow
-\dom$ transforms states using the transition relation $\trans$: $\step(\elem) =
-\{ \st' \mid \st \in \elem \wedge \st \trans \st' \}$.
+partial order($\order$) operators.  The set of states $\ielem$ denotes the
+initial states $\istset$.  The \textit{one-step execution} $\step: \dom
+\rightarrow \dom$ transforms states using the transition relation $\trans$:
+$\step(\elem) = \{ \st' \mid \st \in \elem \wedge \st \trans \st' \}$.
 
@@
 conditions:
-\begin{itemize}
-  \item $\forall \abselem_0, \abselem_1 \in \absdom. \; \gamma(\abselem_0) \cup
-    \gamma(\abselem_1) \subseteq \gamma(\abselem_0 \join \abselem_1)$
-  \item $\forall \abselem \in \absdom. \; \absstep \circ \gamma(\abselem) \subseteq
-    \gamma \circ \absstep(\abselem)$
-\end{itemize}
+\begin{equation}\label{equ:sound}
+  \begin{array}{l}
+  - \; \forall \abselem_0, \abselem_1 \in \absdom. \; \gamma(\abselem_0) \cup
+    \gamma(\abselem_1) \subseteq \gamma(\abselem_0 \join \abselem_1)\\
+  - \; \forall \abselem \in \absdom. \; \step \circ \gamma(\abselem) \subseteq
+    \gamma \circ \absstep(\abselem)\\
+  \end{array}
+\end{equation}
 
@@
 of views $\viewset$ to sets of states $\dom$. Each view $\view \in \viewset$
-represents a set of states $\viewmap(\view)$.
-A \textit{sensitive state abstraction} $\dom
-\galois{\alpha_\viewmap}{\sgamma} \sabsdom$ is a Galois connection between
-the concrete domain $\dom$ and the sensitive abstract domain $\sabsdom$ with the
-following concretization function:
+represents a set of states $\viewmap(\view)$ and also a state is always
+included in a unique view: $\forall \st \in \stset. \; \exists! \view \in
+\viewset.$ s.t. $\st \in \viewmap(\view)$.  A \textit{sensitive state
+abstraction} $\dom \galois{\alpha_\viewmap}{\sgamma} \sabsdom$ is a Galois
+connection between the concrete domain $\dom$ and the sensitive abstract domain
+$\sabsdom$ with the following concretization function:
 \[
-  \sgamma(\sabselem) = \{ \st \in \stset \mid \forall \view \in \viewset.
-  \; \st \in \viewmap(\view) \Rightarrow \st \in \gamma \circ \sabselem(\view) \}
+  \sgamma(\sabselem) = \underset{\view \in \viewset}{\bigcup}
+  {\viewmap(\view) \cap \gamma \circ \sabselem(\view)}
 \]
@@
 also define the soundness of sealed symbolic execution as follows:
-\begin{definition}{(Soundness)}
-  The symbolic transition relation is \textit{sound} when the following
+\begin{definition}{(Validity)}
+  The symbolic transition relation is \textit{valid} when the following
   condition is satisfied:
   \[
-    \begin{array}{l}
-      \forall \imap \in \imapset. \; \forall \symbst, \symbst' \in \symbstset.\\
-      \symbst \symbtrans \symbst' \Rightarrow \instant{\symbst}{\imap} \trans
-      \instant{\symbst'}{\imap}
-    \end{array}
+      \forall \symbst, \symbst' \in \symbstset.\\
+  \]
+  \[
+    \symbst \symbtrans \symbst' \Leftrightarrow
+    \forall \imap \in \imapset. \;
+    \{ \st' \mid \instant{\symbst}{\imap} \trans \st' \}
+    = \{ \instant{\symbst'}{\imap} \}
   \]
@@
 a given abstract state in a specific view as a pair of abstract instantiation
-map and a sealed symbolic state.  Two converters should convert given elements
-without loss of information:
+map and a sealed symbolic state.  We define the concretization function
+$\aelemgamma: \aelemset \rightarrow \dom$ for analysis elements as follows:
+\[
+  \aelemgamma(\aelem) = \left\{
+    \begin{array}{ll}
+      \viewmap(\view) \cap \gamma(\abselem) & \text{if} \; (\view, \abselem) = \aelem\\
+      \instant{\symbst}{\absimap} & \text{if} \; (\absimap, \symbst) = \aelem\\
+    \end{array}
+  \right.
+\]
+Moreover, two converters should convert given elements without loss of
+information:
 \[
@@
 \[
-  \asconverter((\view, \abselem)) = (\absimap, \symbst)
-  \Rightarrow \left\{
+  \asconverter(\aelem) = \aelem' \Rightarrow \left\{
   \begin{array}{l}
-    (\view, \abselem) = \saconverter((\absimap, \symbst))\\\
-    \viewmap(\view) \cap \gamma(\abselem) = \instant{\symbst}{\absimap}\\
+    \aelem = \saconverter(\aelem')\\
+    \aelemgamma(\aelem) = \aelemgamma(\aelem')\\
   \end{array}
@@
 \]
-where $\identity$ denotes the identity function.
 
@@
 as follows:
-\begin{definition}[$\atriage$]
+\begin{definition}[$\atriage$]\label{def:atriage}
   The triage function $\atriage: \aelemset \rightarrow \aelemset$ for analysis
@@
         \saconverter(\aelem)
-        & \text{if} \; \aelem = (\absimap, \symbst) \wedge \symbst \symbtrans \symbst'\\
+        & \text{if} \; \aelem = (\absimap, \symbst) \wedge \symbst \symbtrans
+        \bot\\
         \aelem
@@
 function for combined states:
-\begin{definition}[$\triage$]
+\begin{definition}[$\triage$]\label{def:triage}
   The triage function $\triage: \combdom \rightarrow \combdom$ for combined
@@
   \[
-    E = \dot{\atriage}(\{ (\view, \abselem) \mid \view \in \viewset \wedge
-    \sabselem(\view) = \abselem \} \cup \symbelem)
+    E = \dot{\atriage}(\{ (\view, \sabselem(\view)) \mid \view \in \viewset \} \cup \symbelem)
   \]
@@
   following condition:
-  \begin{equation}\label{expr:condition}
+  \begin{equation}\label{equ:cond}
     \asconverter((\view, \abselem)) = (\absimap, \symbst) \Rightarrow

### 2020-11-20 paper/pldi21/related.tex
Revised Sec. 7

--- 2020-11-15 paper/pldi21/related.tex
@@
 \section{Related Work}\label{sec:related}
-
-Several researchers have introduced analysis technique to utilize dynamic
-analysis for static analysis in three different ways: combined analysis,
-automatic modeling, and pruning states.
+Researchers have introduced various analysis technique to utilize dynamic
+analysis for static analysis in three ways: combined analysis,
+automatic modeling, and pruning analysis scope.
 
 \paragraph{Combined Analysis}
-
-The most related previous work is the combined analysis that utilizes dynamic
-analysis during Java static analysis introduced by \citet{concerto}.  They
-proved that their combined analysis is sound and showed that it could
+The most related previous work is combined analysis that utilizes dynamic
+analysis during Java static analysis introduced by \citet{concerto}.
+They proved that their combined analysis is sound and showed that it could
 significantly improve the precision and performance of Java static analysis by
-evaluating their tool, \concerto.  However, their approach have several
-limitations compared to the dynamic shortcut.  First, they syntactically divides
-a given program to \textit{applications} parts for static analysis and
-\textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
-freely switching between static and dynamic and even impossible to perform both
-of static and dynamic analysis to the same program part in different contexts.
-Besides, they introduced \textit{mostly-concrete interpretation} similar with
-our sealed symbolic execution.  However, it supports only a special
-\textit{unknown} value that represents any possible value.  Thus, it cannot
-preserves the precision of complex abstract domains~\cite{safe, tajs, regex,
-weaklySPE} frequently used in JavaScript static analysis.  In the other hand,
-the sealed symbolic execution automatically detects whether the abstract
-semantics for abstract values.  Finally, \concerto preserves the soundness when
-the program satisfies the \textit{state separation hypothesis}.  They assume
-that states of application and framework parts do not interrogated or
-manipulated by each other.  While it is reasonable for static analysis of Java
-applications using external libraries, the assumption is not satisfied for
-JavaScript programs in general.  Unlike their approach, our approach does not
-have any assumption between static and dynamic analysis parts.
+evaluating their tool, \concerto.  However, their approach has several
+limitations compared with dynamic shortcuts.  First, it syntactically
+divides a given program to \textit{applications} parts for static
+analysis and \textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
+freely switch between static analysis and dynamic analysis.  It is
+even impossible to perform both static and dynamic analysis of 
+the same program part in different contexts.  In addition, while they
+introduced \textit{mostly-concrete interpretation} similar to our
+sealed symbolic execution, it supports only a special \textit{unknown}
+value that represents any possible value.  Thus, it cannot preserve
+the precision of complex abstract domains~\cite{revisit-recency,
+  regex, weaklySPE} frequently used in JavaScript static analysis.
+On the contrary, sealed symbolic execution automatically detects when
+to switch to static analysis to use abstract semantics for abstract values.
+Finally, \concerto preserves the soundness when a program satisfies
+the \textit{state separation hypothesis}.  It assumes that the states
+of application parts and framework parts are not interrogated
+or manipulated by each other.  While the assumption may be reasonable
+for static analysis of Java applications using external libraries, it
+is not satisfied for JavaScript programs in general.  Unlike their
+approach, our approach does not have any assumptions between static and
+dynamic analysis parts.
 
@@
 For static analysis of JavaScript programs, modeling behaviors of built-in
-libraries or host-dependent functions is required because they are opaque
-codes.  Since manual modeling is error-prone, tedious, and labor-intensive,
-several researchers~\cite{safewapi, safets} utilize type information to
+libraries or host-dependent functions is necessary because they are opaque code.
+Since manual modeling is error-prone, tedious, and labor-intensive,
+researchers~\cite{safewapi, safets} have utilized type information to
 automatically model their behaviors.  However, type information is too imprecise
-to reflect the detailed semantics and is difficult to represent the
-side-effects.  To alleviate the problem, \citet{mimic} introduced the technique
-to infer JavaScript codes for opaque codes using concrete execution.  They
-captured the effects of opaque codes on user objects by collecting partial
-execution traces and synthesized JavaScript codes based on the extracted
-behaviors.  They also leveraged ES6 \jscode{Proxy} objects to capture the
-effects on user objects.  Instead of synthesizing JavaScript codes,
+to reflect complex semantics and is difficult to represent the side-effects.
+To alleviate the problem, \citet{mimic} introduced a technique
+to infer JavaScript code for opaque code using concrete execution.
+They captured the effects of opaque code on user objects by collecting partial
+execution traces and synthesized JavaScript code using the extracted behaviors.
+They also leveraged ES6 \jscode{Proxy} objects to capture the effects on user objects.
+Instead of synthesizing JavaScript code,
 \citet{opaque-model} presented a \textit{Sample-Run-Abstract (SRA)} approach for
-on-demand modeling thus they focused on the current abstract state during static
-analysis.  It first \textit{samples} concrete states in a well-distributed way,
-\textit{runs} each sampled state on a JavaScript engine, and \textit{abstract}
-executions results.  However, all of previous works sacrifice the soundness of
-static analysis.  On the other hand, while the dynamic shortcut is not
-applicable for all invocation of opaque functions, it is sound if it is
-applicable.
+on-demand modeling focusing on the current abstract states during static analysis.
+It first \textit{samples} concrete states in a well-distributed manner,
+\textit{runs} each sampled state on a JavaScript engine, and \textit{abstracts} execution results.
+However, all the previous work sacrifice the soundness of static analysis.
+On the contrary, while dynamic shortcuts may not be applicable to some
+invocations of opaque functions, it is sound if it is applicable.
 
-\paragraph{Pruning Analysis Scopes}
+\paragraph{Pruning Analysis Scope}
 Another approach to utilize dynamic analysis for JavaScript static analysis is
-to prune the scope of analysis.  \citet{blended} introduced \textit{blended
-taint analysis} that specializes JavaScript dynamic language features such as
-dynamic code generation (e.g. \jscode{eval}) or variadic function calls.  They
-first performs dynamic analysis to collect traces with concrete values used in
-dynamic language features and restrict the semantics of features based on the
-collected traces during static analysis.  \citet{battles, eha} utilizes three
-different points to reduce analysis scopes: initial states, dynamically loaded
-files, and event handlers.  They dumped the initial states from a specific web
-browser to focus on analyzing the behaviors of web browsers running on the
-browser.  Then, they collected paths of dynamically loaded files via concrete
-executions and utilized the path information in static analysis.  For event
-handlers, they intentionally analyzed partial execution flows using concrete
-user events.  They collected concrete states for each entry of event handler
+to prune the scope of analysis.  \citet{determinacy} proposed dynamic
+determinacy analysis, which infers determinacy facts like whether a
+variable or an expression at a given location holds the same value in
+all possible execution of a program via concrete execution.
+They specialized target source code with determinacy
+facts so that static analysis can get benefits from elimination of dynamic code
+generation such as \jscode{eval} and constant property names.
+\citet{blended} introduced \textit{blended taint analysis}, which specializes JavaScript dynamic
+language features such as dynamic code generation or variadic function calls.
+It first performs dynamic analysis to collect traces with concrete values used
+in dynamic language features and restricts the semantics of features based on the
+collected traces during static analysis.  \citet{battles, eha} utilize three different points to reduce
+analysis scope: initial states, dynamically loaded files, and event handlers.
+They dumped the initial states from a specific web browser to focus on
+analysis of the behaviors of web applications running on the browser.
+Then, they collected paths of dynamically loaded files via concrete
+execution and utilized the path information in static analysis.
+For event handlers, they intentionally analyzed partial execution flows using concrete user events.
+They collected concrete states for each entry of an event handler
 during dynamic analysis, merged them to a single abstract state, and analyzed
-the event handler with the abstract state.  Unfortunately, all of them does not
-preserve soundness of static analysis unlike the dynamic shortcut.
+the event handler with the abstract state.
+Unfortunately, all the above mentioned approaches do not preserve
+soundness of static analysis unlike our approach using dynamic shortcuts.
 

### 2020-11-20 paper/pldi21/conclusion.tex
Revised Sec. 8

--- 2020-10-23 paper/pldi21/conclusion.tex
@@
 \section{Conclusion}\label{sec:conclusion}
-
-\todo
+We presented a novel technique for JavaScript static analysis using \textit{dynamic shortcuts}.
+It can significantly accelerate the JavaScript static
+analysis by freely leveraging high performance of dynamic analysis for
+concretely executable program parts.  To maximally use dynamic analysis during static analysis,
+we proposed \textit{sealed symbolic execution}, which performs
+concrete execution using sealed symbolic values for abstract values.
+We formally defined static analysis using dynamic shortcuts in the
+abstract interpretation framework and proved its soundness and termination.
+We developed $\tool$ as a prototype implementation of the proposed approach
+by extending a combination of the state-of-the-art static and dynamic
+analyzers SAFE and Jalangi.  Our tool accelerates the speed
+of static analysis \inred{X.X}x for original tests and \inred{X.X}x for
+abstracted tests of Lodash 4 library.  Moreover, it improves \inred{XX.XX}\% of
+the analysis precision by using sealed symbolic execution instead of
+manual modeling for \inred{XX.X} opaque functions on average.

### 2020-11-20 paper/pldi21/eval.tex
Revised Section 6

@@
 analysis for \inred{269} Lodash 4 tests with and without dynamic shortcut.
-Figure~\ref{fig:conc-analysis-time} depicts the box plot chart for their
-analysis time and for speed up after applying the dynamic shortcut in a
-logarithmic scale.  While the base analysis (no-DS) finished \inred{199} out of
-\inred{269} tests within 5 minutes, our tool finished all tests with the dynamic
-shortcut (DS).  For \inred{199} tests analyzable by both analyses, the analysis
-took \inred{168.4} seconds and \inred{12.2} seconds on average without dynamic
-shortcut (no-DS) and with dynamic shortcut (DS), and the dynamic shortcut
-accelerates \inred{20.16}\textsf{x} the static analysis on average.  Only for
-one test using $\jscode{_.sample}$ (a Lodash 4 library that randomly samples a
-value from a given array), the static analysis using dynamic shortcut had
+Figure~\ref{fig:conc-analysis-time} depicts the histogram for their analysis
+time and the box plot for speed up after applying the dynamic shortcut.  While
+the base analysis (no-DS) finished \inred{199} out of \inred{269} tests within 5
+minutes, our tool finished all tests with the dynamic shortcut (DS).  For
+\inred{199} tests analyzable by both analyses, the analysis took \inred{168.4}
+seconds and \inred{12.2} seconds on average without dynamic shortcut (no-DS) and
+with dynamic shortcut (DS), and the dynamic shortcut accelerates
+\inred{20.16}\textsf{x} the static analysis on average.  Only for one test using
+$\jscode{_.sample}$ (a Lodash 4 library that randomly samples a value from a
+given array), the static analysis using dynamic shortcut had
 \inred{0.81}\textsf{x} speed of the base analysis because of the frequent use of
@@
 official tests with abstract values to mimic the use patterns of library
-functions.  We randomly selected literals and replace subset of them to their
+functions.  We randomly selected literals and replace one of them to their
 corresponding typed abstract values.  For example, if we pick a numerical
@@
 $\top_{\code{num}}$, which represents the all numerical values.  In the
-remaining section, we evaluated our tool based on the randomly abstracted tests
-of Lodash 4.
+remaining section, we evaluated our tool based on the \textit{original} tests
+and the \textit{abstracted} tests of Lodash 4.
 
-For abstracted tests, the dynamic shortcut successfully accelerates the static
-analysis.  Figure~\ref{fig:abs-analysis-time} shows the analysis time for the
-abstracted tests in a logarithmic scale.  Among \inred{269} abstracted tests,
-the base analysis (no-DS) finished \inred{82} tests within 5 minutes.  On the
-other hand, the analysis using dynamic shortcut (DS) finished \inred{219} tests.
-For \inred{82} tests analyzable by both analyses, the analyses took
-\inred{168.4} seconds and \inred{12.2} seconds on average without dynamic
-shortcut (no-DS) and with dynamic shortcut (DS), and the dynamic shortcut
-accelerates \inred{20.16}\textsf{x} the static analysis on average.
+Also for abstracted tests, the dynamic shortcut successfully accelerates the
+static analysis.  Figure~\ref{fig:abs-analysis-time} shows the analysis time for
+the abstracted tests.  Among \inred{269} abstracted tests, the base analysis
+(no-DS) finished \inred{82} tests within 5 minutes.  On the other hand, the
+analysis using dynamic shortcut (DS) finished \inred{219} tests.  For \inred{82}
+tests analyzable by both analyses, the analyses took \inred{168.4} seconds and
+\inred{12.2} seconds on average without dynamic shortcut (no-DS) and with
+dynamic shortcut (DS), and the dynamic shortcut accelerates
+\inred{20.16}\textsf{x} the static analysis on average.
 
@@
   \vspace*{-1.5em}
-  \caption{Time ratio of the finished analysis with dynamic shortcut for
-  \inred{219} Lodash 4 \textit{abstracted} tests.}
+  \caption{Analysis time ratio for \inred{219} Lodash 4 \textit{abstracted}
+  tests.}
   \label{fig:abs-analysis-ratio}
@@
 
-For \inred{219} abstracted tests successfully analyzed with the dynamic
-shortcut, communication costs between static and dynamic analysis grew
-relatively to the number of dynamic shortcuts.  To communicate with the
-dynamic analyzer, the static analysis should dump the current abstract state,
-send it to the dynamic analyzer, receive the result from the dynamic analysis,
-and apply the given update information to the abstract state.  Thus, the
-communication costs will increase dependent on the number of dynamic shortcuts.
-Figure~\ref{fig:abs-analysis-ratio} shows the time ratio of dynamic and static
-analysis parts with communication costs in total analysis time.  On average, the
-dynamic analysis occupied \inred{63.30}\%, communication \inred{9.52}\%, and
-static analysis \inred{27.17}\% in total analysis time.  If the dynamic
-shortcuts are performed less than 10 times, the ratio of communication in total
-analysis time is \inred{9.50\%} on average.  The more dynamic shortcuts
-performed, the more communication cost is required.  When the number is
-between 41 and 50, the ratio of average communication cost is rised to
-\inred{10.65\%} in the total analysis time.
+Unlike Lodash 4 original tests, \inred{xx} dynamic shortcuts are invoked during
+analysis for \inred{82} abstracted tests analyzable by both analyses.  We expect
+the analysis time with dynamic shortcuts is propositioned to the number of
+dynamic shortcuts. To communicate with the dynamic analyzer, the static analysis
+should dump the current abstract state, send it to the dynamic analyzer, receive
+the result from the dynamic analysis, and apply the given update information to
+the abstract state.  Thus, the communication costs might increase dependent on
+the number of dynamic shortcuts.  To experimentally evaluate our predictions,
+we also evaluated the relationship between the number of dynamic shortcuts and
+the communication costs between static and dynamic analysis.  For \inred{xx}
+Lodash 4 original tests, the communication cost occupied only \inred{x.xx}\% of
+total analysis.  However, for \inred{xx} abstracted tests, the communication
+cost occupied \inred{xx.xx}\% in total analysis.
+Figure~\ref{fig:abs-analysis-ratio} shows the detailed analysis time ratio for
+\inred{82} Lodash 4 original tests.  The $x$-axis denotes the number of dynamic
+shortcuts with the number of corresponding tests, and $y$-axis represents the
+time ratio normalized by the total analysis time with dynamic shortcuts.  For
+all \inred{82} tests, while it shows that the dynamic static analysis occupied
+only \inred{x.xx}\% and \inred{27.17}\% in total analysis time, the
+communication cost occupied \inred{xx.xx}\%.  If the dynamic shortcuts are
+performed less than 10 times, the ratio of communication in total analysis time
+is endurable because it occupied only \inred{xx.xx\%} on average.   However,
+when \inred{21-30} dynamic shortcuts are performed, the communication occupied
+\inred{80\%} of analysis time.  Moreover, the number of dynamic shortcuts is
+more than \inred{30}, the communication time itself (DS-Comm.) is over than the
+analysis time without dynamic shortcuts (no-DS).  Based on the evaluation, we
+believe that it is possible to leverage dynamic shortcuts by optimizing the
+communication between static and dynamic analysis.
 
@@
   \begin{subfigure}[t]{0.48\textwidth}
-    \includegraphics[width=\linewidth]{img/precision-fail}
+    \includegraphics[width=\linewidth]{img/conc-precision}
     \vspace*{-1.5em}
-    \caption{\# Failed Assertions.}
+    \caption{Reachable branches for \inred{xx} \textit{original} tests}
     \label{fig:precision-fail}
@@
   \begin{subfigure}[t]{0.48\textwidth}
-    \includegraphics[width=\linewidth]{img/precision-branch}
+    \includegraphics[width=\linewidth]{img/abs-precision}
     \vspace*{-1.5em}
-    \caption{\# Covered Branches.}
+    \caption{Reachable branches for \inred{82} \textit{abstracted} tests}
     \label{fig:precision-branch}
@@
   \caption{The comparison of analysis precision without (no-DS) and with (DS)
-  dynamic shortcut for \inred{82} \textit{abstracted} tests analyzable by both
-  analyses}
+  dynamic shortcut based on the branch coverage of analysis.}
   \label{fig:precision}
@@
 
-To evaluate the precision improvement of dynamic shortcut, we used two different
-metrics to measure the precision of the analysis results: 1) the number of false
-alarms for assertions in tests and 2) the number of branch covered by analysis.
-Figure~\ref{fig:precision} depicts the comparison of analysis precision without
-(no-DS) and with (DS) dynamic shortcut using two different metrics.
+To evaluate the precision improvement of dynamic shortcut, we used the number of
+branches covered by analysis to measure the precision of the analysis results.
+One of the most popular application of static analysis is dead code elimination
+by using the result of reachability analysis.  To acquire smaller codes, precise
+reachability analysis is required.  Thus, we decided to measure the analysis
+precision based on the number of branches covered by analysis.  The high
+branch coverage denotes the low analysis precision, and low branch coverage
+denotes the high precision.  Figure~\ref{fig:precision} depicts the comparison of
+the number of covered branches without (no-DS) and with (DS) dynamic shortcuts
+for \inred{xx} original tests and \inred{xx} abstracted tests.
 
-Lodash 4 official tests check the assertions based on
-QUnit\footnote{https://qunitjs.com/}, which is a powerful, easy-to-use
-JavaScript testing framework.  Since all assertions in each test are passed in
-the concrete execution, any assertion failures during static analysis should be
-false alarms.  Although we analyzed \textit{abstracted} Lodash 4 tests, the
-number of assertion failures during static anlysis could be a metric of
-imprecision of the analysis.  Figure~\ref{fig:precision-fail} shows the number
-of assertion failures in each test analyzable by both analysis with and
-without dynamic shortcut.  The $x$- and $y$-axis denote the analysis without
-(no-DS) and with (DS) dynamic shortcut and each $\times$ mark denotes each test.
-The top and bottom dotted lines denote the worst and best precision improvement,
-and the middle solid line denotes the average improvement.  Thus, dynamic
-shortcut reduces assertion failures to at least \inred{1.00}\textsc{x}, at most
-\inred{0.54}\textsc{x}, and \inred{0.92}x on average.
-
-Another metric to measure the precision of static analysis is the number of
-branches covered during analysis.  If the static analysis is sound, the more
-precise analysis covers the less number of branches.  In the similar way with
-the number of assertion failures, Figure~\ref{fig:precision-branch} depicts the
-the comparison of the number of branches during static analysis without (no-DS)
-and with (DS) dynamic shortcut.  In the view point of the branch coverage,
-dynamic shortcut successfully cut down the number of covered branches at least
+For \inred{xx} both analyzable original tests, Figure~\ref{fig:conc-precision}
+shows the number of branches covered by analysis.  The $x$- and $y$-axis denote
+the analysis without (no-DS) and with (DS) dynamic shortcuts and each $\times$
+mark denotes each test.  The top and bottom dotted lines denote the worst and
+best precision improvement, and the middle solid line denotes the average
+improvement.  Thus, dynamic shortcuts successfully reduced the number of
+branches at least \inred{1.00}\textsc{x}, at most \inred{0.54}\textsc{x}, and
+\inred{0.92}x on average.  For abstracted tests, we evaluated \inred{xx} tests
+analyzable by both analyses.  Figure~\ref{fig:precision-branch} depicts the
+results of experiments for abstracted tests and it shows that dynamic shortcuts
+also successfully cuts down the number of covered branches at least
 \inred{0.81}\textsc{x}, at most \inred{0.51}\textsc{x}, and
 \inred{0.68}\textsc{x} on average.
-
-\inred{TODO - Case Study.}
 
@@
 Table~\ref{table:func-replace} describes the dynamic shortcut effectively lessen
-the burden of manual modeling for JavaScript built-in functions.  Among Lodash 4
-\inred{219} abstracted tests analyzable with dynamic shortcut, we measured the
+the burden of manual modeling for JavaScript built-in functions.  For Lodash 4
+\inred{xx} original tests and \inred{xx} abstracted tests, we measured the
 number of tests using only dynamic shortcut instead of manual modeling for each
@@
 row in the left side describes that \jscode{Array.prototype.toString} is used in
-\inred{139} Lodash 4 abstracted tests and the static analysis with dynamic
-shortcut successfully analyze \inred{92} tests among them.  It means that
-\inred{66}\% of tests using \jscode{Array.prototype.toString} could be analyzed
-without the manual modeling of the built-in function.
+\inred{139} original tests and \inred{xxx} abstracted tests. Amogn them,
+\inred{44} original tests \inred{xx} abstracted tests are successfully analyzed
+by dynamic shortcuts instead of using the modeling of
+\jscode{Array.prototype.toString}.
 
-Moreover, \inred{6} functions out of \inred{49} JavaScript built-in functions
-are analyzed by only dynamic shortcut instead of manual modeling for all Lodash
-4 tests.  Each raw colored colored with \inred{yellow} describes such case in
-Table~\ref{table:func-replace}.  It means that the manual modeling of \inred{6} 
-JavaScript built-in functions is does not required to analyze all Lodash 4
-abstracted tests. \inred{TODO - Explain the detail for each case.}
+Moreover, several built-in functions are analyzed by only dynamic shortcuts in
+all tests.  Among \inred{49} JavaScript built-in functions, \inred{xx} and
+\inred{xx} functions are analyzed by only dynamic shortcut instead of manual
+modeling for all original or all abstracted tests.  Each cell colored by
+\inred{yellow} describes fully replaceable cases in
+Table~\ref{table:func-replace}.

### 2020-11-20 paper/pldi21/implementation.tex
Minor fix of Section 5

@@
 constructs an execution environment at the start of a dynamic shortcut, it
-creates revoked \jscode{Proxy} objects to represent abstract values via the
+creates \jscode{Proxy} objects to represent abstract values via the
 following \jscode{generateSymbol} function:
@@
 function generateSymbol() {
-  const r = Proxy.revocable(function() {}, {});
-  r.revoke();
-  return r.proxy;
+  function detect() { /* access detection */ }
+  return new Proxy(function() {}, {
+    getPrototypeOf: detect,
+    ...
+    construct     : detect
+  });
 }
@@
 \end{lstlisting}
-The function creates a sealed symbol \jscode{r} as a revocable proxy object with a dummy
-function object without any handlers. It then revokes the symbol by
-\jscode{r.revoke()} not to allow any accesses of the symbol.  A revoked
-object throws a \jscode{TypeError} exception when any of 13 pre-defined operations
-are applied to the object, which enables us to determine whether an
-object is sealed or not.  For example, the variable
+The function creates a sealed symbol as a proxy object with a dummy
+function object with a handler for all 13 traps using an access detection
+function \jscode{detect}.  A sealed symbol invokes the function \jscode{detect}
+when any of 13 pre-defined traps are operated to the object, which enables us to
+determine whether an object is sealed or not.  For example, the variable
 \jscode{y} successfully points to the same symbol stored in \jscode{x}, but the
-program throws \jscode{TypeError} on line 8 because \jscode{x + 1} requires
+program invokes the function \jscode{detect} on line 11 because \jscode{x + 1} requires
 the actual value of the symbol.  In addition, we instrument unary and binary
 operations in Jalangi so that we can detect all the accesses on the
-symbol beyond the 13 operations provided by \jscode{Proxy}.
+symbol beyond the 13 traps provided by \jscode{Proxy}.
 Using this idea, we successfully extended the

### 2020-11-20 paper/pldi21/eval.tex
Minor fix in Sec. 5

@@
 
-We evaluated our tool based on the following research questions:
+We evaluated our tool based on the following three research questions:
 \begin{itemize}
 \item \textbf{RQ1) Analysis Speed-up:} How much analysis time is reduced by
-    adding dynamic shortcut to static analysis?
+using dynamic shortcuts during static analysis?
 \item \textbf{RQ2) Precision Improvement:} How much analysis precision is
-    improved by replacing the manual modeling with dynamic shortcut?
+improved by using dynamic shortcuts instead of manual modeling?
 \item \textbf{RQ3) Opaque Function Coverage:} How many opaque functions are
-    covered by dynamic shortcut without using manual modeling?
+covered by dynamic shortcuts without using manual modeling?
 \end{itemize}
-We targeted the official 306 tests of Lodash 4
+We selected the official 306 tests of Lodash 4
 (v.4.17.20)\footnote{https://github.com/lodash/lodash/blob/4.17.20/test/test.js}
-used in motivating examples (Section~\ref{sec:motivation}).  The most recent
-papers for JavaScript static analysis techniques~\cite{value-refinement,
-value-partitioning} also evaluated their techniques based on them.
-Among them, we filtered out \inred{37} tests including JavaScript language
-features SAFE does not support, such as dynamic code generation using
-\jscode{Function}, getter/setter, and browser specific features
-(e.g. $\jscode{__proto__}$).  Thus, we only targeted \inred{269} out of 306
-tests for the evaluation.  We performed our experiments on an Ubuntu machine
+used in the motivating examples in Section~\ref{sec:motivation} as our evaluation target.
+The most recent papers about JavaScript static analysis techniques~\cite{value-refinement,
+value-partitioning} also used the tests to evaluate their techniques.
+Among them, we filtered out \inred{37} tests that use JavaScript language
+features SAFE does not support such as dynamic code generation using
+\jscode{Function}, getters and setters, and browser-specific features like $\jscode{__proto__}$.
+Thus, we used \inred{269} out of 306 tests for the evaluation of $\tool$.
+We performed our experiments on a Ubuntu machine
 equipped with 4.2GHz Quad-Core Intel Core i7 and 64GB of RAM.
@@
 
-To evaluate the effectiveness of the dynamic shortcut, we performed static
-analysis for \inred{269} Lodash 4 tests with and without dynamic shortcut.
+To evaluate the effectiveness of using dynamic shortcuts, we performed static
+analysis of \inred{269} Lodash 4 tests with and without dynamic shortcuts.
+%
 Figure~\ref{fig:conc-analysis-time} depicts the histogram for their analysis

### 2020-11-20 paper/pldi21/implementation.tex
Removed inred for timelimit in Section 5
Minor fix in Sec. 5

@@
 The function creates a sealed symbol as a proxy object with a dummy
-function object with a handler for all 13 traps using an access detection
+function object and a handler for all 13 traps using an access detection
 function \jscode{detect}.  A sealed symbol invokes the function \jscode{detect}
-when any of 13 pre-defined traps are operated to the object, which enables us to
+when any of 13 pre-defined traps are operated on the object, which enables us to
 determine whether an object is sealed or not.  For example, the variable
@@
 the result of the sealed symbolic execution.  In our experiments, we set the time limit as
-\inred{5 seconds} for each sealed symbolic execution.
+5 seconds for each sealed symbolic execution.
 

### 2020-11-20 paper/pldi21/eval.tex
Revising Sec. 6

@@
   \caption{Analysis time for Lodash 4 \textit{original} tests without (no-DS)
-  and with (DS) the dynamic shortcut within 5 minutes.}
+  and with (DS) dynamic shortcuts within 5 minutes}
   \label{fig:conc-analysis-time}
@@
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
   \caption{Analysis time for Lodash 4 \textit{abstracted} tests without (no-DS)
-  and with (DS) the dynamic shortcut within 5 minutes.}
+  and with (DS) dynamic shortcuts within 5 minutes}
   \label{fig:abs-analysis-time}
@@
 analysis of \inred{269} Lodash 4 tests with and without dynamic shortcuts.
-%
-Figure~\ref{fig:conc-analysis-time} depicts the histogram for their analysis
-time and the box plot for speed up after applying the dynamic shortcut.  While
-the base analysis (no-DS) finished \inred{199} out of \inred{269} tests within 5
-minutes, our tool finished all tests with the dynamic shortcut (DS).  For
-\inred{199} tests analyzable by both analyses, the analysis took \inred{168.4}
-seconds and \inred{12.2} seconds on average without dynamic shortcut (no-DS) and
-with dynamic shortcut (DS), and the dynamic shortcut accelerates
-\inred{20.16}\textsf{x} the static analysis on average.  Only for one test using
-$\jscode{_.sample}$ (a Lodash 4 library that randomly samples a value from a
-given array), the static analysis using dynamic shortcut had
-\inred{0.81}\textsf{x} speed of the base analysis because of the frequent use of
-dynamic shortcut (\inred{24} times).
+Figure~\ref{fig:conc-analysis-time} depicts histograms for their analysis
+time and a box plot for speed up after applying dynamic shortcuts.
+While the baseline analysis (no-DS) finished analysis of \inred{199} out of \inred{269} tests within 5
+minutes, our tool (DS) finished analysis of all tests using dynamic shortcuts.
+For \inred{199} tests analyzable by both analyzers, on average, the analysis took \inred{168.4}
+seconds for no-DS and \inred{12.2} seconds for DS, which shows that
+using dynamic shortcuts outperforms the baseline analyzer \inred{20.16}\textsf{x} on average.
+Only for one test using $\jscode{_.sample}$, a Lodash 4 library
+function that randomly samples a value from a given array, DS showed
+\inred{0.81}\textsf{x} speed of no-DS due to frequent use of
+dynamic shortcuts, that is \inred{24} times.
 
-Unfortunately, since most of Lodash 4 tests use concrete values instead of
-non-deterministic user inputs, they could be analyzed via a few number of
-dynamic shortcut.  In fact, among \inred{269} tests, \inred{262} tests analyzed
-via a single usage of dynamic shortcut without using abstract semantics.
-However, the arguments of library functions might include non-deterministic user
-inputs in the real-world JavaScript programs.  Thus, we modified Lodash 4
-official tests with abstract values to mimic the use patterns of library
-functions.  We randomly selected literals and replace one of them to their
-corresponding typed abstract values.  For example, if we pick a numerical
-literal \jscode{42}, we modified it to the abstract numeric value
-$\top_{\code{num}}$, which represents the all numerical values.  In the
-remaining section, we evaluated our tool based on the \textit{original} tests
+Note that since most Lodash 4 tests use concrete values instead of
+non-deterministic user inputs, they can be analyzed by a few number of dynamic shortcuts.
+In fact, among \inred{269} tests, \inred{262} tests are analyzed
+by a single dynamic shortcut without using abstract semantics.
+However, in real-world JavaScript programs, arguments of library
+functions may include non-deterministic user inputs.
+To evaluate our approach in a real-world setting,
+we modified Lodash 4 official tests with abstract values to simulate actual use patterns of library functions.
+We mad abstract values by randomly selecting literals and replacing
+one of them with its corresponding abstract value.
+For example, if we select a numeric literal \jscode{42}, we modified it to the abstract numeric value
+$\top_{\code{num}}$, which represents all the numeric values.
+In the remaining section, we evaluated $\tool$ using the \textit{original} tests
 and the \textit{abstracted} tests of Lodash 4.
 
-Also for abstracted tests, the dynamic shortcut successfully accelerates the
-static analysis.  Figure~\ref{fig:abs-analysis-time} shows the analysis time for
-the abstracted tests.  Among \inred{269} abstracted tests, the base analysis
-(no-DS) finished \inred{82} tests within 5 minutes.  On the other hand, the
-analysis using dynamic shortcut (DS) finished \inred{219} tests.  For \inred{82}
-tests analyzable by both analyses, the analyses took \inred{168.4} seconds and
-\inred{12.2} seconds on average without dynamic shortcut (no-DS) and with
-dynamic shortcut (DS), and the dynamic shortcut accelerates
-\inred{20.16}\textsf{x} the static analysis on average.
+For abstracted tests as well, dynamic shortcuts successfully accelerated the static analysis.
+Figure~\ref{fig:abs-analysis-time} shows the analysis time of the abstracted tests.
+Among \inred{269} abstracted tests, no-DS finished analysis of \inred{82} tests within 5 minutes,
+but DS finished analysis of \inred{219} tests.  For \inred{82} tests analyzable by both analyzers,
+on average, the analyses took \inred{168.4} seconds for no-DS and \inred{12.2} seconds for DS,
+which shows that dynamic shortcuts outperforms the baseline analyzer
+\inred{20.16}\textsf{x} on average.
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
   \vspace*{-1.5em}
-  \caption{Analysis time ratio for \inred{219} Lodash 4 \textit{abstracted}
-  tests.}
+  \caption{Analysis time ratio for \inred{219} \textit{abstracted} tests}
   \label{fig:abs-analysis-ratio}
@@
 
-Unlike Lodash 4 original tests, \inred{xx} dynamic shortcuts are invoked during
-analysis for \inred{82} abstracted tests analyzable by both analyses.  We expect
-the analysis time with dynamic shortcuts is propositioned to the number of
-dynamic shortcuts. To communicate with the dynamic analyzer, the static analysis
-should dump the current abstract state, send it to the dynamic analyzer, receive
-the result from the dynamic analysis, and apply the given update information to
-the abstract state.  Thus, the communication costs might increase dependent on
-the number of dynamic shortcuts.  To experimentally evaluate our predictions,
-we also evaluated the relationship between the number of dynamic shortcuts and
-the communication costs between static and dynamic analysis.  For \inred{xx}
-Lodash 4 original tests, the communication cost occupied only \inred{x.xx}\% of
-total analysis.  However, for \inred{xx} abstracted tests, the communication
-cost occupied \inred{xx.xx}\% in total analysis.
-Figure~\ref{fig:abs-analysis-ratio} shows the detailed analysis time ratio for
-\inred{82} Lodash 4 original tests.  The $x$-axis denotes the number of dynamic
-shortcuts with the number of corresponding tests, and $y$-axis represents the
-time ratio normalized by the total analysis time with dynamic shortcuts.  For
-all \inred{82} tests, while it shows that the dynamic static analysis occupied
-only \inred{x.xx}\% and \inred{27.17}\% in total analysis time, the
-communication cost occupied \inred{xx.xx}\%.  If the dynamic shortcuts are
-performed less than 10 times, the ratio of communication in total analysis time
-is endurable because it occupied only \inred{xx.xx\%} on average.   However,
-when \inred{21-30} dynamic shortcuts are performed, the communication occupied
-\inred{80\%} of analysis time.  Moreover, the number of dynamic shortcuts is
-more than \inred{30}, the communication time itself (DS-Comm.) is over than the
-analysis time without dynamic shortcuts (no-DS).  Based on the evaluation, we
-believe that it is possible to leverage dynamic shortcuts by optimizing the
-communication between static and dynamic analysis.
+Unlike for the original tests, analysis of \inred{82}
+abstracted tests that are analyzable by both analyzers invoked
+\inred{xx} dynamic shortcuts.  Because taking a dynamic shortcut
+requires converting between abstract states and sealed symbolic values
+and exchanging them between the static analyzer and the dynamic analyzer,
+using dynamic shortcuts multiple times may incur more performance
+overhead than performance benefits by using sealed symbolic execution.
+One may conjecture that the communication cost between the static
+analyzer and the dynamic analyzer may be proportional to the number of
+dynamic shortcuts.
 
-\subsection{Precision Improvement}
+To experimentally evaluate the conjecture, we investigated the relationship between
+the communication cost between analyzers and the number of dynamic shortcuts.
+For \inred{xx} original tests, the communication cost was only
+\inred{x.xx}\% of the total analysis time.  However, for \inred{xx}
+abstracted tests, the communication cost was \inred{xx.xx}\% of the
+total analysis time.  Figure~\ref{fig:abs-analysis-ratio} presents the
+analysis time ratio for \inred{82} abstracted tests.
+The $x$-axis represents the time ratio normalized by the total analysis time with dynamic shortcuts
+and the $y$-axis denotes the number of dynamic shortcuts and the number of corresponding tests.
+For all \inred{82} tests, the communication cost (DS-Comm.) is larger than
+both the static analysis time (DS-Static) and the dynamic analysis
+time (DS-Dynamic).  When dynamic shortcuts are performed less than 10 times,
+the communication cost is modest compared with the baseline static
+analysis time (no-DS).  However, the more dynamic shortcuts are performed,
+the less the performance benefits by using sealed symbolic execution.
+Specifically, when dynamic shortcuts are performed more than
+\inred{30} times, DS-Comm. is even larger than no-DS.
+Based on this evaluation result, we believe that we can leverage
+dynamic shortcuts by optimizing the communication between static and dynamic analyzers.
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
   \vspace*{-1em}
-  \caption{The comparison of analysis precision without (no-DS) and with (DS)
-  dynamic shortcut based on the branch coverage of analysis.}
+  \caption{Branch coverage of analysis without (no-DS) and with (DS) dynamic shortcuts}
   \label{fig:precision}
@@
 
-\begin{table*}
+\begin{table*}[t]
   \centering
   \caption{The number of \textit{abstracted} tests using dynamic shortcut
-  instead of manual modeling for each JavaScript built-in library.}
+  instead of manual modeling for each JavaScript built-in library}
   \label{table:func-replace}
@@
 
-To evaluate the precision improvement of dynamic shortcut, we used the number of
-branches covered by analysis to measure the precision of the analysis results.
-One of the most popular application of static analysis is dead code elimination
-by using the result of reachability analysis.  To acquire smaller codes, precise
-reachability analysis is required.  Thus, we decided to measure the analysis
-precision based on the number of branches covered by analysis.  The high
-branch coverage denotes the low analysis precision, and low branch coverage
-denotes the high precision.  Figure~\ref{fig:precision} depicts the comparison of
-the number of covered branches without (no-DS) and with (DS) dynamic shortcuts
-for \inred{xx} original tests and \inred{xx} abstracted tests.
+\subsection{Precision Improvement}
 
-For \inred{xx} both analyzable original tests, Figure~\ref{fig:conc-precision}
-shows the number of branches covered by analysis.  The $x$- and $y$-axis denote
-the analysis without (no-DS) and with (DS) dynamic shortcuts and each $\times$
-mark denotes each test.  The top and bottom dotted lines denote the worst and
-best precision improvement, and the middle solid line denotes the average
-improvement.  Thus, dynamic shortcuts successfully reduced the number of
-branches at least \inred{1.00}\textsc{x}, at most \inred{0.54}\textsc{x}, and
-\inred{0.92}x on average.  For abstracted tests, we evaluated \inred{xx} tests
-analyzable by both analyses.  Figure~\ref{fig:precision-branch} depicts the
-results of experiments for abstracted tests and it shows that dynamic shortcuts
-also successfully cuts down the number of covered branches at least
-\inred{0.81}\textsc{x}, at most \inred{0.51}\textsc{x}, and
-\inred{0.68}\textsc{x} on average.
+To evaluate the analysis precision improvement of dynamic shortcuts,
+we measured the number of branches covered by no-DS and DS.
+Because both no-DS and DS are designed to be sound,
+high (low) branch coverage denotes low (high) analysis precision.
+
+Figure~\ref{fig:precision} depicts the comparison of the analysis
+precision between no-DS and DS.  The $x$-axis and the $y$-axis denote
+the number of branches covered by no-DS and DS, respectively;
+each $\times$ mark denotes each test.  The top and bottom dotted lines
+denote the worst and the best precision improvement, respectively, and
+the middle solid line denotes the average improvement.
+For \inred{xx} original tests that are analyzable by both analyzers,
+Figure~\ref{fig:precision}(a) shows that dynamic shortcuts
+successfully reduced the number of covered branches at least
+\inred{1.00}\textsc{x}, at most \inred{0.54}\textsc{x}, and \inred{0.92}x on average.
+For \inred{xx} abstracted tests that are analyzable by both analyzers,
+Figure~\ref{fig:precision}(b) shows that dynamic shortcuts
+also successfully cut down the number of covered branches at least
+\inred{0.81}\textsc{x}, at most \inred{0.51}\textsc{x}, and \inred{0.68}\textsc{x} on average.
 
 \subsection{Opaque Function Coverage}
-
-The dynamic shortcut does not only improve performance or precision of analysis
-but also reduce the effort to model the behavior of opaque functions.
-JavaScript programs often use JavaScript built-in libraries or host-dependent
-functions but they are opaque codes; it means that they are executable but
-written in a different programming languages.  A typical solution is to
-manually model their behaviors to statically analyze for JavaScript programs
-using such functions.  The dynamic shortcut can reduce such efforts if some
-opaque functions are analyzed by only dynamic analysis instead of static
-analysis.
-
-Table~\ref{table:func-replace} describes the dynamic shortcut effectively lessen
-the burden of manual modeling for JavaScript built-in functions.  For Lodash 4
-\inred{xx} original tests and \inred{xx} abstracted tests, we measured the
-number of tests using only dynamic shortcut instead of manual modeling for each
-JavaScript built-in library.  For each raw, \textbf{Object} column denotes the
-built-in object, \textbf{Function} function name, \textbf{\# Replaced} the
-number of tests successfully replacing the modeling via dynamic shortcut with
-the total number of tests using the target function.  For example, the fourth
-row in the left side describes that \jscode{Array.prototype.toString} is used in
-\inred{139} original tests and \inred{xxx} abstracted tests. Amogn them,
-\inred{44} original tests \inred{xx} abstracted tests are successfully analyzed
+To evaluate how much manual modeling efforts of opaque functions
+are reduced by dynamic shortcuts, we measured the number of tests where
+opaque functions that are analyzed only by dynamic analysis not by
+static analysis.  Table~\ref{table:func-replace} summarizes the result.
+For \inred{xx} original tests and \inred{xx} abstracted tests, we measured the
+number of tests that use only dynamic shortcuts instead of manual modeling
+for each JavaScript built-in library function.  For each row,
+\textbf{Object} column denotes a built-in object,
+\textbf{Function} a function name, and
+\inred{\textbf{\# Replaced} the number of tests successfully replacing manual
+modeling via dynamic shortcuts with the total number of tests using the target function.
+For example, the fourth row in the left side describes that \jscode{Array.prototype.toString} is used in
+\inred{139} original tests and \inred{xxx} abstracted tests.
+ Among them, \inred{44} original tests \inred{xx} abstracted tests are successfully analyzed
 by dynamic shortcuts instead of using the modeling of
 \jscode{Array.prototype.toString}.
-
 Moreover, several built-in functions are analyzed by only dynamic shortcuts in
@@
 \inred{xx} functions are analyzed by only dynamic shortcut instead of manual
-modeling for all original or all abstracted tests.  Each cell colored by
-\inred{yellow} describes fully replaceable cases in
-Table~\ref{table:func-replace}.
+modeling for all original and all abstracted tests, respectively.  Each filled cell
+describes fully replaceable cases in Table~\ref{table:func-replace}.
+Therefore, dynamic shortcuts effectively lessen
+the burden of manual modeling for JavaScript built-in functions.
+}

### 2020-11-20 paper/pldi21/ds.tex
Section 3

@@
-\subsection{Dynamic Shortcut}
+\subsection{Combined Domain}
 
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=\linewidth]{img/dynamic-shortcut}
-  \vspace*{-2em}
-  \caption{The diagram for the extended view transition for dynamic shortcut.}
-  \vspace*{-1em}
-  \label{fig:dynamic-shortcut}
-\end{figure}
+In this part, we define a \textit{combined domain} of a given sensitive abstract
+domain with the sealed symbolic domain and its one-step execution.
+\begin{definition}[Combined Domain]
+  A \textit{combined domain} is $\combdom = \sabsdom \times \symbdom$ and its
+  concretization function $\combgamma: \combdom \rightarrow \dom$ and join
+  operator defined as
+  \begin{align}
+    \combgamma((\sabselem, \symbelem)) &= \sgamma(\sabselem) \cup
+      \symbgamma(\symbelem)\\
+    (\sabselem, \symbelem) \join ({\sabselem}', \symbelem') &= (\sabselem \join
+      {\sabselem}', \symbelem \cup \symbelem')
+  \end{align}
+\end{definition}
+
+Before defining the one-step execution for the combined domain, we introduce
+\textit{analysis elements} to easily configure different types of abstract
+states in sensitive abstract domain and sealed symbolic domain.
+\begin{definition}[Analysis Elements]\label{def:aelem}
+  An \textit{analysis element} $\aelem \in \aelemset = (\viewset \times \absdom)
+  \uplus (\absimapset \times \symbstset)$ is either 1) a pair of a view and an
+  abstract state in sensitive abstract domain $\sabsdom$, or 2) a pair of an
+  abstract instantiation map and a sealed symbolic state in sealed symbolic
+  domain $\symbdom$.  Its concretization function $\aelemgamma:
+  \aelemset \rightarrow \dom$ is defined as
+  \[
+    \aelemgamma(\aelem) = \left\{
+      \begin{array}{ll}
+        \viewmap(\view) \cap \gamma(\abselem) & \text{if} \; (\view, \abselem) = \aelem\\
+        \instant{\symbst}{\absimap} & \text{if} \; (\absimap, \symbst) = \aelem\\
+      \end{array}
+    \right.
+  \]
+\end{definition}
 
@@
   \centering
-
-  \fbox{$\st \trans \st$}
-  \begin{mathpar}
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \refer = \expr\\
-      \referrule{\st}{\refer}{\loc}\\
-      \exprrule{\st}{\expr}{\val}\\
-    }
-    {
-      \st = (\lab, \mem, \ctxt, \addr)
-      \trans
-      (\labnext(\lab), \mem[\loc \mapsto \val], \ctxt, \addr)
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \refer = \kwobj\\
-      \referrule{\st}{\refer}{\loc}\\
-      \addr' = \text{(a fresh object address)}
-    }
-    {
-      \st = (\lab, \mem, \ctxt, \addr)
-      \trans
-      (\labnext(\lab), \mem[\loc \mapsto \addr'], \ctxt, \addr)
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \refer = \expr_f ( \expr_a )\\
-      \referrule{\st}{\refer}{\loc}\\
-      \exprrule{\st}{\expr_f}{\fval{x}{\lab_b}}\\
-      \exprrule{\st}{\expr_a}{\val_a}\\
-      \addr' = \text{(a fresh environment address)}
-    }
-    {
-      \st = (\lab, \mem, \ctxt, \addr)
-      \trans
-      (\lab_b, \mem[(\addr', x) \mapsto \val_a], \ctxt[\addr' \mapsto (\addr,
-      \labnext(\lab), \loc)], \addr')
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \kwret \; \expr\\
-      \exprrule{\st}{\expr}{\val}\\
-      \ctxt(\addr) = (\addr', \lab', \loc)
-    }
-    {
-      \st = (\lab, \mem, \ctxt, \addr)
-      \trans
-      (\lab', \mem[\loc \mapsto \val], \ctxt, \addr')
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \kwif \; \expr \; \lab'\\
-      \exprrule{\st}{\expr}{\kwtrue}\\
-    }
-    {
-      \st = (\lab, \mem, \ctxt, \addr)
-      \trans
-      (\lab', \mem, \ctxt, \addr)
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \kwif \; \expr \; \lab'\\
-      \exprrule{\st}{\expr}{\kwfalse}\\
-    }
-    {
-      \st = (\lab, \mem, \ctxt, \addr)
-      \trans
-      (\labnext(\lab), \mem, \ctxt, \addr)
-    }
-  \end{mathpar}
-
-  \fbox{$\referrule{\st}{\refer}{\loc}$}
-  \begin{mathpar}
-    \inferrule*[width=0.48\textwidth]
-    {}
-    {
-      \referrule{\st = (\lab, \mem, \ctxt, \addr)}{x}{(\addr, x)}\\
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \exprrule{\st}{\expr_0}{\addr_0}\\
-      \exprrule{\st}{\expr_1}{\val_1}\\
-      \val_1 \in \strset\\
-    }
-    {
-      \referrule{\st = (\lab, \mem, \ctxt, \addr)}{\expr_0 [ \expr_1
-      ]}{(\addr_0, \val_1)}
-    }
-  \end{mathpar}
-
-  \fbox{$\exprrule{\st}{\expr}{\val}$}
-  \begin{mathpar}
-    \inferrule*[width=0.48\textwidth]
-    {}
-    {
-      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}{\pval}{\pval}
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {}
-    {
-      \exprrule{\st = (\lab, \mem, \ctxt,
-      \addr)}{\fval{x}{\lab'}}{\fval{x}{\lab'}}
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \referrule{\st}{\refer}{\loc}\\
-      \loc \in \Dom(\mem)
-    }
-    {
-      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}{\refer}{\mem(\loc)}
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \exprrule{\st}{\expr_1}{\val_1}\\
-      \cdots\\
-      \exprrule{\st}{\expr_n}{\val_n}
-    }
-    {
-      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}
-      {\op(\expr_1, \cdots, \expr_n)}{\op(\val_1, \cdots, \val_n)}
-    }
-  \end{mathpar}
-
-  \caption{The transition relation for the core language of JavaScript}
-  \label{fig:core-trans-rel}
+  \begin{subfigure}[t]{0.15\textwidth}
+    \includegraphics[height=3.2cm]{img/listing}
+    \caption{Notations}
+    \label{fig:ds-example1}
+  \end{subfigure}
+  \quad
+  \begin{subfigure}[t]{0.23\textwidth}
+    \includegraphics[height=3.2cm]{img/path-1}
+    \caption{$\varx = 0$}
+    \label{fig:ds-example2}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.28\textwidth}
+    \includegraphics[height=3.2cm]{img/path-2}
+    \caption{$\varx > 0$}
+    \label{fig:ds-example3}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.28\textwidth}
+    \includegraphics[height=3.2cm]{img/path-3}
+    \caption{$\varx \in \mathbb{N}$}
+    \label{fig:ds-example4}
+  \end{subfigure}
+  \caption{Three abstract interpretation using combined domain for the running
+  example with different initial values for $\varx$.}
+  \label{fig:ds-examples}
 \end{figure*}
 
-We define the the abstract interpretation with \textit{dynamic shortcut}, which
-is a concrete semantics on sealed symbolic execution.  With dynamic shortcut,
-we use the powerset of symbolic states as the domain $\combdom =
-\powerset{\symbstset}$, and extend the view transition as follows:
+Moreover, to freely convert types of analysis elements, we define two converters:
+\begin{align}
+  \asconverter & : (\viewset \times \absdom) \hookrightarrow
+    (\absimapset \times \symbstset)\\
+  \saconverter & : (\viewset \times
+    \absdom) \leftarrow (\absimapset \times \symbstset)
+\end{align}
+While the converter $\saconverter$ is total, the other one $\asconverter$ is
+\textit{partial}. Thus, it is possible to convert an analysis element
+$(\view, \abselem)$ in sensitive abstract domain to another analysis element in
+sealed symbolic domain only if the convert $\asconverter$ is defined: $(\view,
+\abselem) \in \Dom(\asconverter)$.  In addition, they should convert given
+elements without loss of information for all $\aelem \in \aelemset$:
 \[
+  \asconverter(\aelem) = \aelem' \Rightarrow \left\{
   \begin{array}{l}
-    \combviewtrans{\view}{\view'}(\combelem) =\\
-    \qquad \{
-      \symbst' \mid \symbst \in S \wedge
-      \symbst \symbtrans \symbst' \wedge
-      \saconverter(\symbst') = (\view', \_)
-    \}\\
-    \qquad \cup \left\{
-    \begin{array}{ll}
-      \{ \asconverter \circ \viewtrans{\view}{\view'}(\bigjoin D) \}
-      & \text{if} \; D \neq \varnothing\\
-      \varnothing & \text{otherwise}\\
+    \aelem = \saconverter(\aelem')\\
+    \aelemgamma(\aelem) = \aelemgamma(\aelem')\\
   \end{array}
   \right.
+\]
+
+Now, we define the \textit{combined one-step execution} $\combstep: \combdom
+\rightarrow \combdom$ with two converters $\asconverter$ and $\saconverter$ and
+it consists of two steps; 1) the \textit{triage} step prepares the execution of
+analysis elements by converting their types via two converters according to
+their status, and 2) the \textit{execution} step performs execution of each
+analysis element using abstract one-step execution $\absstep$ in sensitive
+abstract domain and sealed symbolic one-step execution $\symbstep$ in sealed
+symbolic execution.
+\begin{definition}[Combined One-Step Execution]
+  A \textit{combined one-step execution} $\combstep: \combdom \rightarrow
+  \combdom$ is define as
+  \[
+    \combstep(\combelem) = (\sabsstep(\sabselem), \symbstep(\symbelem))
+  \]
+  where $(\sabselem, \symbelem) = \triage(\combelem)$.
+\end{definition}
+
+The $\triage$ function decides whether a new sealed symbolic execution is
+\textit{introduced} or an existing one is \textit{terminated}.  When an analysis
+element $(\view, \abselem)$ in the sensitive abstract domain is defined in the
+converter $\asconverter$, a new sealed symbolic execution is introduced by
+converting the analysis element to the corresponding one $(\absimap, \symbst) =
+\asconverter((\view, \abselem))$ in the sealed symbolic domain.  In the other
+hand, assume that if there is no more other sealed symbolic states having
+symbolic transitions with $\symbst$ for an analysis element $(\absimap,
+\symbst)$ in the sealed symbolic domain; $\symbst \symbtrans \excst$.  Then, the
+sealed symbolic execution for $(\absimap, \symbst)$ is terminated by 1)
+converting it to another analysis element $(\view, \abselem) =
+\saconverter((\absimap, \symbst))$ in the sensitive abstract domain and 2)
+merging with the current abstract state stored in the view $\view$ with
+$\abselem$.
+
+To formally define the $\triage$ function, we first define a $\atriage$ function
+for analysis elements using two converters and then define the $\triage$ function.
+\begin{definition}[$\atriage$]\label{def:atriage}
+  The function $\atriage: \aelemset \rightarrow \aelemset$ for analysis elements
+  is defined as
+  \[
+    \atriage(\aelem) = \left\{
+      \begin{array}{ll}
+        \asconverter(\aelem)
+        & \text{if} \; \aelem = (\view, \abselem) \wedge \aelem \in
+        \Dom(\asconverter)\\
+        \saconverter(\aelem)
+        & \text{if} \; \aelem = (\absimap, \symbst) \wedge \symbst \symbtrans
+        \bot\\
+        \aelem
+        & \text{Otherwise}
       \end{array}
+    \right.
   \]
-where $S = \combelem\mid_{\checker}$ and $D =
-\dot{\saconverter}(\combelem\mid_{\neg\checker})$.  The dot notation $\dot{f}$
-denotes the element-wise extended function of a function $f$.  The abstract
-interpretation with dynamic shortcut performs one-step symbolic transition for
-each symbolic state that passes the filter $\checker$. On the other hand, it
-converts remaining symbolic states to the corresponding abstract states, merges
-them into a single abstract state, and performs the abstract one-step execution
-for the abstract state.
+\end{definition}
+\begin{definition}[$\triage$]\label{def:triage}
+  The triage function $\triage: \combdom \rightarrow \combdom$ for combined
+  states is defined as
+  \[
+    \triage((\sabselem, \symbelem)) = \left(
+      \lambda \view. \bigjoin \{ \abselem \!\mid\! (\view, \abselem) \in E \},
+      E \cap (\absimapset \times \symbstset)
+    \right)
+  \]
+  where
+  \[
+    E = \dot{\atriage}(\{ (\view, \sabselem(\view)) \mid \view \in \viewset \} \cup \symbelem)
+  \]
+  (The dot notation $\dot{f}$ denotes the element-wise extended function of a
+  function $f$.)
+\end{definition}
 
-For example, Figure~\ref{fig:dynamic-shortcut} depicts the
-diagram of the extended view transition from $\view$ to $\view'$ for dynamic
-shortcut.  The element $\combelem$ in $\view$ consists of five symbolic states
-from $\nsymbst{1}$ to $\nsymbst{5}$.  The solid box denotes that the corresponding
-symbolic state passes the filter $\checker$ and the dotted box denotes that it
-does not.  For each symbolic state that passes the filter ($\nsymbst{1}$,
-$\nsymbst{2}$, and $\nsymbst{4}$), it applies the symbolic transition $\symbtrans$.
-For failed symbolic states ($\nsymbst{3}$ and $\nsymbst{5}$), it applies the
-converter $\saconverter$ to convert each of them to the corresponding abstract
-state and merges results using the join operator ($\join$).  Then, it utilizes
-the abstract semantics via the original view transition
-$\viewtrans{\view}{\view'}$ and the converter $\asconverter$ to convert the
-result to the corresponding symbolic state.
+\subsection{Examples}
 
-We could configure when the sealed symbolic execution or the abstract
-interpretation is performed based on the definition of the $\checker$ function
-and its negation $\neg\checker$.  For example, we could define the $\checker$
-that passes only function entry, call, and exit points to perform conversions in
-a function level.  However, for the soundness and the termination of the
-the abstract interpretation with dynamic shortcut, it should satisfy the
-following condition:
-\begin{theorem}\label{theorem:shortcut}
-  The abstract interpretation with dynamic shortcut is sound and terminates in a
-  finite time if its abstract semantics is sound and $\checker$ satisfies the
-  following condition:
+For examples of the abstract interpretation with the combined domain,
+Figure~\ref{fig:ds-examples} depicts the flow of analysis for the running
+example in Figure~\ref{fig:running-example} with three different initial set of
+values for the variable $\varx$.  In this example, we use the abstract domain
+$\{ -, 0, + \}$ for integers stored in $\varx$ introduced in
+Section~\ref{sec:ai}, and the \textit{flow sensitivity} which utilizes the
+labels of states as their views introduced in Section~\ref{sec:sens}.  For
+brevity, we use the concatenated form to represent the abstract values such as
+$-0$ denotes the set $\{ -, 0 \}$.
+
+Figure~\ref{fig:ds-examples}(a) explains notations used in each graph. A solid
+box denotes an analysis element, which is a pair of label $\lab$ and abstract
+state $\abselem$.  A pair wrapped with angle brackets denotes an analysis
+element, which is a pair of abstract instantiation map $\absimap$ and sealed
+symbolic state $\symbst$.  In fact, the sealed symbolic state part (right) of
+each pair in graphs contains only the value of the variable of $\varx$ without
+the current label.  For brevity, we represents its label by locating them in the
+next to the corresponding label.  A solid line is a view transition
+$\viewtrans{\lab}{\lab'}$ from a label $\lab$ to another one $\lab'$.  A dotted
+line is a sealed symbolic transition $\symbtrans$.  Three solid lines with
+circled labels denote two converters $\saconverter$, $\asconverter$ and the join
+operator $\join$.
+
+Figure~\ref{fig:ds-examples}(b) shows the analysis with the combined domain when
+the initial value of $\varx$ is $0$.  First, in the triage step,
+the converter $\asconverter$ converts the analysis element $(\lab_0, 0)$ to
+another analysis element $\langle \varnothing, 0 \rangle$ with the label
+$\lab_0$.  Moreover, it does not introduce any sealed symbolic values because
+the value represents only a single value.  Until the end of the program, the
+sealed symbolic execution from $\langle \varnothing, 0 \rangle$ is successfully
+continues.  However, there is no more possible symbolic transition for the
+symbolic state $\langle \varnothing, 0 \rangle$ with the label $\lab_4$.  Thus,
+it is converted to $(\lab_4, 0)$ via the converter $\saconverter$.
+
+Instead of a single value, assume that the initial value of $\varx$ is one of
+any positive integers.  Figure~\ref{fig:ds-examples}(c) describes the analysis
+flow for such case.  Then, the initial abstract value at the label $\lab_0$ is
+$+$ and it is impossible to convert to any sealed symbolic values because the
+next program statement requires the actual value stored in the variable $\varx$
+for the branch condition $\varx \geq 0$.  Thus, it performs view transition
+$\viewtrans{\lab_0}{\lab_1}$ from the label $\lab_0$ to another one $\lab_1$ for
+the abstract value $+$ and the result is also $+$.  Now, the analysis element
+$(\lab_1, +)$ could be converted to $\langle \symb \mapsto +, \symb \rangle$
+with the label $\lab_1$.  This sealed symbolic execution step terminates in the
+label $\lab_3$ because the next statement is $\varx = -\varx$ and the negation
+operator requires the actual value of $\varx$.  Finally, it performs the view
+transition and the result is $(\lab_4, -)$.
+
+For the last case, we assume that all integers are possible for the initial
+value of the variable $\varx$ as described in Figure~\ref{fig:ds-examples}(d).
+While it reaches the false branch in the label $\lab_2$ unlike previous cases,
+it also cannot perform dynamic shortcuts because the statement in the false
+branch is $\varx = -\varx$.  At the label $\lab_3$, there is two analysis
+elements: 1) $(\lab_3, +)$ introduced by view transition from the label $\lab_2$
+with $-$, and 2) $\langle \symb \mapsto 0+, \symb \rangle$ with $\lab_2$
+introduced by sealed symbolic execution started at $\lab_1$.  However, since it
+is not possible to perform sealed symbolic execution for both elements, the
+second one is converted to $(\lab, 0+)$ and merged with $+$ at $\lab_3$ via the
+join operator $\join$.  Finally, the view transition
+$\viewtrans{\lab_3}{\lab_4}$ from $\lab_3$ to $\lab_4$ is performed to the
+merged abstract state $0+$ and the result is $-0$.
+
+\subsection{Soundness and Termination}
+
+The converter $\asconverter$ and the sealed symbol transition $\symbtrans$ are
+keys to configure the introduction and termination of sealed symbolic
+executions.  To ensure the \textit{soundness} and \textit{termination} of the
+abstract interpretation defined with the combined domain of sensitive abstract
+domain and sealed symbolic domain, the following conditions should be hold.
+
+\begin{theorem}[Soundness and Termination]\label{theorem:shortcut}
+  The abstract interpretation with dynamic shortcut is \textbf{sound} and
+  \textbf{terminates} in a finite time if
+  \begin{itemize}
+    \item The abstract transfer $\abstransfer$ is sound
+    \item The sensitive abstract domain $\sabsdom$ has finite height
+    \item The sealed symbolic transition $\symbtrans$ is valid
+    \item There exists $N < \infty$ such that
       \[
-    \checker(\symbst) \Rightarrow \symbst \symbtrans^k \excst \wedge
-    1 < k \leq N
+        \forall \aelem \in \aelemset. \; \asconverter(\aelem) = (\absimap,
+        \symbst) \Rightarrow \symbst
+        \symbtrans^k \excst \wedge 1 < k \leq N
       \]
-  where $N$ is a pre-defined maximum length of the sealed symbolic execution.
+  \end{itemize}
 \end{theorem}
-\inred{We proved Theorem~\ref{theorem:shortcut} using the Kleene's fixed-point
-theorem~\cite{kleene} with the finite height of abstract domains. Because of the
-page limitation, we omit the proof in this paper and include it in a companion
-report~\cite{report}.}
+
+To prove the termination of the abstract interpretation with the combined
+domain, the condition provides an upper bound of the number of sealed symbolic
+states after the sensitive abstract states are reached the fixed point.  Thus,
+the termination of the analysis is guaranteed.  For the proof of Soundness, two
+properties (\ref{equ:sound-join}) for join operator $\join$ and
+(\ref{equ:sound-step}) for combined one-step execution are required to be
+proved.  The core idea of the proof is to prove the following lemmas for
+$\triage$ function and utilize them.
+\begin{lemma}\label{lemma:step-symb}
+  Assume that the following condition is hold
+  \[
+    \forall (\absimap, \symbst) \in \symbelem. \; \exists \symbst' \in
+    \symbstset. \; \text{s.t.} \; \symbst \symbtrans \symbst'
+  \]
+  then the following property holds:
+  \[
+    \step \circ \symbgamma(\symbelem) \subseteq
+    \symbgamma \circ \symbstep(\symbelem)\\
+  \]
+\end{lemma}
+\begin{lemma}\label{lemma:triage}
+  For a given combined state $\combelem \in \combdom$, the $\triage$ function
+  satisfies the following two properties:
+  \begin{itemize}
+    \item $\combgamma(\combelem) \subseteq \combgamma \circ \triage(\combelem)$
+    \item $\forall (\absimap, \symbst) \in \symbelem. \; \exists \symbst' \in
+      \symbstset.  \; \text{s.t.} \; \symbst \symbtrans \symbst'$
+  \end{itemize}
+  where $(\sabselem, \symbelem) = \triage(\combelem)$
+\end{lemma}

### 2020-11-20 paper/pldi21/motivation.tex
Section 3

@@
 It is the homepage of Zoom, which is a videotelephony software program developed by Zoom
-Video Communications and it is ranked as the \inred{16th} popular web site according
+Video Communications and it is ranked as the 16th popular web site according
 to Alexa\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.

### 2020-11-20 paper/pldi21/shortcut.tex
Section 3

@@
 
-In this section, we formally define the dynamic shortcut with sealed symbolic
-execution.  We extend the formalization of abstract interpretation of
-\citet{abs-interp-1977, abs-interp-1992} and views-based analysis sensitivity of
-\citet{sens-toplas}.
+In this section, we formally define dynamic shortcuts during static analysis by
+combining abstract interpretation with sealed symbolic execution.  We extend the
+formalization of abstract interpretation of \citet{abs-interp-1977,
+abs-interp-1992} and views-based analysis sensitivity of \citet{sens-toplas}.
+For dynamic shortcuts, we define a sealed symbolic execution and extend it to a
+sealed symbolic domain with abstract instantiation maps.  To combine the
+sensitive abstract interpretation with the sealed symbolic execution, we define
+the combined domain of sensitive abstract domain and sealed symbolic domain and
+explain it with a simple example. Finally, We prove the soundness and
+termination property of abstract interpretation using the combined domain.
 
@@
   \[
-    \begin{array}{l}
-      \enspace \labdot{0} \; \varx = \;? \; ;  \; \labdot{1}\\
-      \enspace \kwif \; (\; \varx \geq 0 \;) \; \labdot{2} \; \varx = \varx ;\\
-      \enspace \kwelse \; \labdot{3} \; \varx = -\varx ;  \; \labdot{4}\\
+    \begin{array}{r@{~}l@{~}c@{~}l}
+      \labdot{0} & \kwif \; (\; \varx \geq 0 \;) & \labdot{1} & \varx = \varx ;\\
+                 & \kwelse & \labdot{2} & \varx = -\varx ;\\
+      \labdot{3} & \varx = -\varx ; & \labdot{4} \\
     \end{array}
@@
   \vspace*{-1em}
-  \caption{Conditional branch}
+  \caption{The negation of the absolute value of $\varx$}
   \label{fig:running-example}
@@
 For example, the code in Figure~\ref{fig:running-example} is a simple program
-that applies the mathematical absolute value function to the variable $\varx$.
-The question mark $?$ denotes a user input that returns an integer.  States
-are pairs of labels and integers $\varx$: $\stset = \labset \times \mathbb{N}$.
-The initial states are $\istset = \{ (\lab_0, 0) \}$ which means the program
-starts with the variable $\varx$ that stores 0 at $\lab_0$.  If the user input is
-$-42$, the program is executed with the following trace:
+that calculates the negation of the absolute value of the variable $\varx$.
+States are pairs of labels and integers stored in $\varx$: $\stset = \labset
+\times \mathbb{N}$.  Assume that the initial states are $\istset = \{ (\lab_0,
+-42) \}$ which means the program starts with the variable $\varx$ that stores
+$-42$ at $\lab_0$.  Then, the program is executed with the following trace:
 \[
-  (\lab_0, 0) \trans (\lab_1, -42) \trans (\lab_3, -42) \trans (\lab_4, 42)
+  (\lab_0, -42) \trans (\lab_2, -42) \trans (\lab_3, 42) \trans (\lab_4, -42)
 \]
 
-\subsection{Abstract Interpretation}
+\subsection{Abstract Interpretation}\label{sec:ai}
+
 The abstract interpretation~\cite{abs-interp-1977, abs-interp-1992}
@@
 conditions:
-\begin{itemize}
-  \item $\forall \abselem_0, \abselem_1 \in \absdom. \; \gamma(\abselem_0) \cup
-    \gamma(\abselem_1) \subseteq \gamma(\abselem_0 \join \abselem_1)$
-  \item $\forall \abselem \in \absdom. \; \absstep \circ \gamma(\abselem) \subseteq
-    \gamma \circ \absstep(\abselem)$
-\end{itemize}
+\begin{align}
+  \forall \abselem_0, \abselem_1 \in \absdom & . \; \gamma(\abselem_0) \cup
+  \gamma(\abselem_1) \subseteq \gamma(\abselem_0 \join
+  \abselem_1) \label{equ:sound-join}\\
+  \forall \abselem \in \absdom & . \; \absstep \circ \gamma(\abselem) \subseteq
+  \gamma \circ \absstep(\abselem) \label{equ:sound-step}
+\end{align}
 
@@
 set operators as domain operators; $-$ denotes negative integers, $+$ positive
-integers, and $0$ zero.  If we use it for the code in
-Figure~\ref{fig:running-example}, the analysis result becomes $\{ -, +, 0 \}$
-because $\varx$ can have any integers at $\lab_1$.
+integers, and $0$ zero.  Assume that we use it for the code in
+Figure~\ref{fig:running-example} and the initial abstract state is $\iabselem =
+\{ - \}$. Then, the analysis result becomes $\{ -, + \}$ because $\varx$ can
+have positive values by executing $\varx = -\varx$ but there is no way to get
+the value $0$ in this program.
 
-\subsection{Analysis Sensitivity}
+\subsection{Analysis Sensitivity}\label{sec:sens}
 
@@
 of views $\viewset$ to sets of states $\dom$. Each view $\view \in \viewset$
-represents a set of states $\viewmap(\view)$.
-A \textit{sensitive state abstraction} $\dom
-\galois{\alpha_\viewmap}{\gamma_\viewmap} \sabsdom$ is a Galois connection between
-the concrete domain $\dom$ and the sensitive abstract domain $\sabsdom$ with the
-following concretization function:
+represents a set of states $\viewmap(\view)$ and also a state is always included
+in a unique view: $\forall \st \in \stset. \; \exists! \view \in
+\viewset.$ s.t. $\st \in \viewmap(\view)$.  A \textit{sensitive state
+abstraction} $\dom \galois{\alpha_\viewmap}{\gamma_\viewmap} \sabsdom$ is a
+Galois connection between the concrete domain $\dom$ and the sensitive abstract
+domain $\sabsdom$ with the following concretization function:
 \[
-  \gamma_\viewmap(\sabselem) = \{ \st \in \stset \mid \forall \view \in \viewset.
-  \; \st \in \viewmap(\view) \Rightarrow \st \in \gamma \circ \sabselem(\view) \}
+  \sgamma(\sabselem) = \underset{\view \in \viewset}{\bigcup}
+  {\viewmap(\view) \cap \gamma \circ \sabselem(\view)}
 \]
@@
 \]
-If we apply the flow sensitivity for the above example, the analysis result
-becomes as follows:
+If we apply the flow sensitivity for the above example with the initial abstract
+state $[ \lab_0 \mapsto \{ -, 0, + \} ]$, the analysis result becomes as follows:
 \[
@@
     \labset & \lab_0 & \lab_1 & \lab_2 & \lab_3 & \lab_4\\\hline
-    \absdom_\pm & 0 & -, +, 0 & +, 0 & - & +, 0\\\hline
+    \absdom_\pm & -, 0, + & 0, + & - & 0, + & -, 0\\\hline
   \end{array}
@@
 
-To handle abstract values in concrete semantics, we define \textit{sealed
-symbolic execution} by extending the transition relation $\trans$ as a symbolic
-transition relation $\symbtrans$ on symbolic states.  First, we extend the
-concrete states $\stset$ to symbolic states with \textit{sealed symbolic values}
-$\symbset$.  A symbolic transition relation $\symbtrans \subseteq \symbstset
-\times (\symbstset \uplus \{ \excst \})$ is exactly the same with the original
-transition relation $\trans$ except when the relation requires the exact value
-of sealed symbolic values.  In this case, the symbolic state has the relation a
-special exception state $\excst$ to represent that it is impossible to interpret
-in a concrete way.  Thus, a symbolic state \textit{always} has a symbolic
-transition relation with a single symbolic state, and the sealed symbolic
-execution is linear until being terminated or reaching the exception state
-$\excst$.
+We define \textit{sealed symbolic execution} by extending the transition
+relation $\trans$ as a symbolic transition relation $\symbtrans$ on symbolic
+states.  First, we augment concrete states $\stset$ to symbolic states
+$\symbstset$ by extending values $\valset$ with \textit{sealed symbolic values}
+$\symbset$.  We also define the symbolic transition relation $\symbtrans
+\subseteq \symbstset \times \symbstset$. We use the notation $\symbtrans^k$
+for $k$ repetition of $\symbtrans$, and  $\symbst \symbtrans \excst$ when
+$\symbst$ does not have symbolic transitions with any other sealed symbolic
+states.  We define the validity of sealed symbolic execution as follows:
+\begin{definition}[Validity]\label{def:valid-symbtrans}
+  The symbolic transition relation is \textit{valid} when the following
+  condition is satisfied for any sealed symbolic states $\symbst$ and
+  $\symbst'$:
+  \[
+    \symbst \symbtrans \symbst' \Leftrightarrow
+    \forall \imap \in \imapset. \;
+    \{ \st' \mid \instant{\symbst}{\imap} \trans \st' \}
+    = \{ \instant{\symbst'}{\imap} \}
+  \]
+  where $\imapset: \symbset \rightarrow \valset$ represent \textit{instantiation
+  maps} from symblic values to concrete values, and $\instant{\symbst}{\imap}$
+  denotes a state produced by replacing each symbolic value $\symb$ to the
+  corresponding value $\imap(\symb)$ using the instantiation map $\imap \in
+  \imapset$.
+\end{definition}
 
-The main difference of sealed symbolic execution with the traditional symbolic
-execution~\cite{symbolic} is that it only supports sealed symbolic values
-instead of symbolic expressions and path constraints.  For example, the
+Note that The main difference of sealed symbolic execution with the traditional
+symbolic execution~\cite{symbolic} is that it only supports sealed symbolic
+values instead of symbolic expressions and path constraints.  For example, the
 following trace represents the traditional symbolic execution of the running
 example in Figure~\ref{fig:running-example}:
+{
+\small
 \[
-  \begin{array}{r@{~}c@{~}l}
-    &&(\lab_2, \symb)[\symb \geq 0] \trans (\lab_4, \symb)[\symb \geq 0]
+  \begin{array}{r@{~}c@{~}c@{~}c@{~}r@{~}c@{~}r}
+    &&(\lab_1, \symb)[\symb \!\geq\! 0]
+    &\trans& (\lab_3, \phantom{-}\symb)[\symb \!\geq\! 0]
+    &\trans& (\lab_4, -\symb)[\symb \!\geq\! 0]
     \vspace*{-0.5em}\\
@@
     \vspace*{-0.5em}\\
-    (\lab_0, 0)[] \trans (\lab_1, \symb)[]&&
+    (\lab_0, \symb)[\varnothing]
     \vspace*{-0.5em}\\
@@
     \vspace*{-0.5em}\\
-    &&(\lab_3, \symb)[\symb < 0] \trans (\lab_4, -\symb)[\symb < 0]\\
+    &&(\lab_2, \symb)[\symb \!<\! 0]
+    &\trans& (\lab_3, -\symb)[\symb \!<\! 0]
+    &\trans& (\lab_4, \phantom{-}\symb)[\symb \!<\! 0]\\
   \end{array}
 \]
-It first assigns a symbolic value $\symb$ to the variable $\varx$ at $\lab_1$.
+}
+It first assigns a symbolic value $\symb$ to the variable $\varx$ at $\lab_0$.
 For the conditional branch, it is forked by creating two symbolic states with
@@
 branches, respectively.  After executing statements $\varx = \varx$ and $\varx =
--\varx$, the variable $\varx$ stores symbolic expressions $\symb$ and $-\symb$ at
-$\lab_4$.  However, the sealed symbolic execution stops at $\lab_1$ as follows:
+-\varx$, the variable $\varx$ stores symbolic expressions $\symb$ and $-\symb$
+at $\lab_3$. Similarly, $\varx$  stores $-\symb$ and $\symb$ at $\lab_3$.
+However, the sealed symbolic execution stops at $\lab_0$ as follows:
 \[
-  (\lab_0, 0) \; \symbtrans \; (\lab_1, \symb) \; \symbtrans \; \excst
+  (\lab_0, 0) \; \symbtrans \; \excst
 \]
@@
 
-To freely convert a pair of view and an abstract state to its corresponding
-symbolic state and vice versa, we define two domain converters $\symbstset
-\galois{\saconverter}{\asconverter} (\viewset \times \absdom)$.  In the
-converter $\asconverter$ from abstract states to symbolic states, if an abstract
-value $\absval$ represents a singleton value, the function transforms the
-abstract value to the corresponding concrete value.  Otherwise, it converts the
-abstract value as a symbolic value in a result symbolic state.  Two converters
-convert given elements without loss of information:
+To define an abstract domain consists of sealed symbolic states, we define
+\textit{abstract instantiation maps} $\absimapset: \symbset \rightarrow
+\absvalset$ from symbolic values to abstract values.  Its concretization
+function $\imapgamma: \absimapset \rightarrow \powerset{\imapset}$ is defined
+with the concretization function $\valgamma: \absvalset \rightarrow
+\powerset{\valset}$ for values as follows:
 \[
-  \saconverter \circ \asconverter = \asconverter \circ \saconverter = \identity
+  \imapgamma(\absimap) = \{
+    \imap \mid \forall \symb \in \symbset. \;
+    \imap(\symb) \in \gamma \circ \absimap(\symb)
+  \}
 \]
-where $\identity$ denotes the identity function.
+The instantiation of a given sealed symbolic state $\symbst \in \symbstset$ with
+an abstract instantiation map $\absimap \in \absimapset$ is defined as follows:
+\[
+  \instant{\symbst}{\absimap} = \{ \instant{\symbst}{\imap} \mid \imap \in
+  \imapgamma(\absimap) \}
+\]
+Now, we define the \textit{sealed symbolic domain} as follows:
+
+\begin{definition}[Sealed Symbolic Domain]\label{def:symbdom}
+  A \textit{sealed symbolic domain} $\symbdom: \powerset{\absimapset \times
+  \symbstset}$ is defined with the following concretization function
+  $\symbgamma: \symbdom \rightarrow \dom$ and sealed symbolic one-step execution
+  $\symbstep: \symbdom \rightarrow \symbdom$ such that
+  \begin{align}
+    \symbgamma(\symbelem) &=
+    \bigcup \{ \instant{\symbst}{\absimap} \mid (\absimap, \symbst) \in
+    \symbelem\}\\
+    \symbstep(\symbelem) &= \{ (\absimap, \symbst') \mid (\absimap, \symbst)
+    \in \symbelem \wedge \symbst \symbtrans \symbst' \}
+  \end{align}
+\end{definition}

### 2020-11-20 paper/pldi21/ds.tex
ds.tex

@@
 (\ref{equ:sound-step}) for combined one-step execution are required to be
-proved.  The core idea of the proof is to prove the following lemmas for
-$\triage$ function and utilize them.
+proved.  The core idea of the proof is to use Lemma~\ref{lemma:step-symb} and
+Lemma~\ref{ref:lemma:trage} for the sealed symbolic one-step execution
+$\symbstep$ and the $\triage$ function. Because of the page limitation, we omit
+the proof in this paper and include it in a companion report~\cite{report}.
 \begin{lemma}\label{lemma:step-symb}

### 2020-11-20 paper/pldi21/ds.tex
Minore typos

@@
 proved.  The core idea of the proof is to use Lemma~\ref{lemma:step-symb} and
-Lemma~\ref{ref:lemma:trage} for the sealed symbolic one-step execution
+Lemma~\ref{ref:lemma:triage} for the sealed symbolic one-step execution
 $\symbstep$ and the $\triage$ function. Because of the page limitation, we omit

### 2020-11-20 paper/pldi21/shortcut.tex
Minore typos

@@
   where $\imapset: \symbset \rightarrow \valset$ represent \textit{instantiation
-  maps} from symblic values to concrete values, and $\instant{\symbst}{\imap}$
+  maps} from symbolic values to concrete values, and $\instant{\symbst}{\imap}$
   denotes a state produced by replacing each symbolic value $\symb$ to the

### 2020-11-20 paper/pldi21/javascript.tex
Little writing for Evaluation
Move Figure 6 to the right position
Section 3
Section 4

@@
 \subsection{Core Language of JavaScript}
-
-\begin{figure*}[t]
-  \centering
-
-  \fbox{$\st \trans \st$}
-  \begin{mathpar}
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \refer = \expr\\
-      \referrule{\st}{\refer}{\loc}\\
-      \exprrule{\st}{\expr}{\val}\\
-    }
-    {
-      \st = (\lab, \mem, \ctxt, \addr)
-      \trans
-      (\labnext(\lab), \mem[\loc \mapsto \val], \ctxt, \addr)
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \refer = \kwobj\\
-      \referrule{\st}{\refer}{\loc}\\
-      \addr' = \text{(a fresh object address)}
-    }
-    {
-      \st = (\lab, \mem, \ctxt, \addr)
-      \trans
-      (\labnext(\lab), \mem[\loc \mapsto \addr'], \ctxt, \addr)
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \refer = \expr_f ( \expr_a )\\
-      \referrule{\st}{\refer}{\loc}\\
-      \exprrule{\st}{\expr_f}{\fval{x}{\lab_b}}\\
-      \exprrule{\st}{\expr_a}{\val_a}\\
-      \addr' = \text{(a fresh environment address)}
-    }
-    {
-      \st = (\lab, \mem, \ctxt, \addr)
-      \trans
-      (\lab_b, \mem[(\addr', x) \mapsto \val_a], \ctxt[\addr' \mapsto (\addr,
-      \labnext(\lab), \loc)], \addr')
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \kwret \; \expr\\
-      \exprrule{\st}{\expr}{\val}\\
-      \ctxt(\addr) = (\addr', \lab', \loc)
-    }
-    {
-      \st = (\lab, \mem, \ctxt, \addr)
-      \trans
-      (\lab', \mem[\loc \mapsto \val], \ctxt, \addr')
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \kwif \; \expr \; \lab'\\
-      \exprrule{\st}{\expr}{\kwtrue}\\
-    }
-    {
-      \st = (\lab, \mem, \ctxt, \addr)
-      \trans
-      (\lab', \mem, \ctxt, \addr)
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \kwif \; \expr \; \lab'\\
-      \exprrule{\st}{\expr}{\kwfalse}\\
-    }
-    {
-      \st = (\lab, \mem, \ctxt, \addr)
-      \trans
-      (\labnext(\lab), \mem, \ctxt, \addr)
-    }
-  \end{mathpar}
-
-  \fbox{$\referrule{\st}{\refer}{\loc}$}
-  \begin{mathpar}
-    \inferrule*[width=0.48\textwidth]
-    {}
-    {
-      \referrule{\st = (\lab, \mem, \ctxt, \addr)}{x}{(\addr, x)}\\
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \exprrule{\st}{\expr_0}{\addr_0}\\
-      \exprrule{\st}{\expr_1}{\val_1}\\
-      \val_1 \in \strset\\
-    }
-    {
-      \referrule{\st = (\lab, \mem, \ctxt, \addr)}{\expr_0 [ \expr_1
-      ]}{(\addr_0, \val_1)}
-    }
-  \end{mathpar}
-
-  \fbox{$\exprrule{\st}{\expr}{\val}$}
-  \begin{mathpar}
-    \inferrule*[width=0.48\textwidth]
-    {}
-    {
-      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}{\pval}{\pval}
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {}
-    {
-      \exprrule{\st = (\lab, \mem, \ctxt,
-      \addr)}{\fval{x}{\lab'}}{\fval{x}{\lab'}}
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \referrule{\st}{\refer}{\loc}\\
-      \loc \in \Dom(\mem)
-    }
-    {
-      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}{\refer}{\mem(\loc)}
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \exprrule{\st}{\expr_1}{\val_1}\\
-      \cdots\\
-      \exprrule{\st}{\expr_n}{\val_n}
-    }
-    {
-      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}
-      {\op(\expr_1, \cdots, \expr_n)}{\op(\val_1, \cdots, \val_n)}
-    }
-  \end{mathpar}
-
-  \caption{The transition relation for the core language of JavaScript}
-  \label{fig:core-trans-rel}
-\end{figure*}
 
@@
 
-We formulate the concrete semantics of the core language as described in
-Figure~\ref{fig:core-trans-rel}.  The transition relation between concrete
-states is defined with the semantics of references and expressions using two
-different forms \fbox{$\referrule{\st}{\refer}{\loc}$} and
+We formulate the concrete semantics of the core language.  The transition
+relation between concrete states is defined with the semantics of references and
+expressions using two different forms \fbox{$\referrule{\st}{\refer}{\loc}$} and
 \fbox{$\exprrule{\st}{\expr}{\val}$}, respectively.  The initial states are
 $\istset = \{ (\ilab, \varnothing, \epsilon, \tladdr) \}$ where $\ilab$ denotes
-the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level
-environment address.  The function $\labnext$ returns the next label of a
-given label in the current program $\prog$.
+the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level environment
+address.  The function $\labnext$ returns the next label of a given label in the
+current program $\prog$.
 
 \subsection{Abstract Semantics}
-
-\begin{figure*}[t]
-  \centering
-
-  \fbox{$\viewtrans{\view}{\view'}: \absdom \rightarrow \absdom$}
-  \begin{mathpar}
-    \inferrule*[width=0.48\textwidth]
-    {
-      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
-      \prog(\lab) = \refer = \expr\\
-      \referabssem{\refer}(\abselem) = L\\
-      \exprabssem{\expr}(\abselem) = \absval
-    }
-    {
-      \viewtrans{\lab}{\labnext(\lab)}(\abselem) =
-      (\absmem[L \mapstos \absval], \absctxt, \absaddr, \abscount)
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
-      \prog(\lab) = \refer = \kwobj\\
-      \referabssem{\refer}(\abselem) = L\\
-      \oabsaddr = \lab
-    }
-    {
-      \viewtrans{\lab}{\labnext(\lab)}(\abselem) = (\absmem[L \mapstos \{
-      \oabsaddr \}], \absctxt, \absaddr, \inc(\abscount, \oabsaddr))
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
-      \prog(\lab) = \refer = \expr_f ( \expr_a )\\
-      \referabssem{\refer}(\abselem) = L\\
-      \fval{x}{\lab_b} \in \exprabssem{\expr_f}(\abselem)\\
-      \exprabssem{\expr_a}(\abselem) = \absval_a\\
-      \eabsaddr = \lab_b\\
-      \eabsctxt = \absctxt[\eabsaddr \mapsto \absctxt(\eabsaddr) \cup \{
-      (\absaddr, \labnext(\lab), L) \} ]
-    }
-    {
-      \viewtrans{\lab}{\lab_b}(\abselem) = (\absmem[(\eabsaddr, x) \mapsto
-      \absval_a], \eabsctxt, \eabsaddr, \inc(\abscount, \eabsaddr))
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
-      \prog(\lab) = \kwret \; \expr\\
-      \exprabssem{\expr}(\abselem) = \absval\\
-      (\rabsaddr, \lab', L) \in \absctxt(\absaddr)
-    }
-    {
-      \viewtrans{\lab}{\lab'}(\abselem) = (\absmem[L \mapstos \absval],
-      \absctxt, \rabsaddr, \abscount)
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \kwif \; \expr \; \lab'\\
-      \kwtrue \in \exprabssem{\expr}(\abselem)
-    }
-    {
-      \viewtrans{\lab}{\lab'}(\abselem) = \abselem
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \prog(\lab) = \kwif \; \expr \; \lab'\\
-      \kwfalse \in \exprabssem{\expr}(\abselem)
-    }
-    {
-      \viewtrans{\lab}{\labnext(\lab)}(\abselem) = \abselem
-    }
-  \end{mathpar}
-
-  \fbox{$\referabssem{\refer}: \absdom \rightarrow \powerset{\abslocset}$}
-  \begin{mathpar}
-    \inferrule*[width=0.48\textwidth]
-    {
-      \abselem = (\absmem, \absctxt, \absaddr, \abscount)
-    }
-    {
-      \referabssem{x}(\abselem) = \{ (\absaddr, x) \}
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
-      A = \exprabssem{\expr_0}(\abselem) \cap \absaddrset\\
-      S = \exprabssem{\expr_1}(\abselem) \cap \strset\\
-    }
-    {
-      \referabssem{\expr_0 [ \expr_1 ]}(\abselem) = A \times S
-    }
-  \end{mathpar}
-
-  \fbox{$\exprabssem{\expr}: \absdom \rightarrow \absvalset$}
-  \begin{mathpar}
-    \inferrule*[width=0.48\textwidth]
-    {}
-    {
-      \exprabssem{\pval}(\abselem) = \{ \pval \}
-    }
-
-    {}
-    {
-      \exprabssem{\fval{x}{\lab}}(\abselem) = \{ \fval{x}{\lab} \}
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
-      \absval = \bigjoin \{ \absmem(\absloc) \mid \absloc \in
-      \referabssem{\refer}(\abselem) \}
-    }
-    {
-      \exprabssem{\refer}(\abselem) = \absval
-    }
-
-    \inferrule*[width=0.48\textwidth]
-    {
-      \exprabssem{\expr_1}(\abselem) = \absval_1\\
-      \cdots\\
-      \exprabssem{\expr_n}(\abselem) = \absval_n
-    }
-    {
-      \exprabssem{\op(\expr_1, \cdots, \expr_n)}(\abselem) = \ops(\absval_1,
-      \cdots, \absval_n)
-    }
-  \end{mathpar}
-
-  \caption{The semantics of view transition for the core language of JavaScript}
-  \label{fig:core-view-trans}
-\end{figure*}
 
@@
 
-We define the semantics of view transition for the core language in
-Figure~\ref{fig:core-view-trans}.  For abstract memories, we use the notation
-$\absmem[L \mapstos \absval]$ to represent the update of multiple abstract
-locations in $L$ with the abstract value $\absval$.  It performs the strong
-update if the abstract address for an abstract location $(\absaddr, \_) \in L$
-is singleton: $\abscount(\absaddr) = \absone$.  Otherwise, it performs the weak
-update for the soundness.  Moreover, we define the increment function $\inc:
-\abscountset \times \absaddrset \rightarrow \abscountset$ of the abstract counter
-defined as follows:
+We define the semantics of view transition for the core language.  For abstract
+memories, we use the notation $\absmem[L \mapstos \absval]$ to represent the
+update of multiple abstract locations in $L$ with the abstract value $\absval$.
+It performs the strong update if the abstract address for an abstract location
+$(\absaddr, \_) \in L$ is singleton: $\abscount(\absaddr) = \absone$.
+Otherwise, it performs the weak update for the soundness.  Moreover, we define
+the increment function $\inc: \abscountset \times \absaddrset \rightarrow
+\abscountset$ of the abstract counter defined as follows:
 \[
@@
 We define the converter $\asconverter: (\viewset \times \absdom) \rightarrow
-\symbstset$ from abstract states to corresponding symbolic states as follows:
-\[
-  \asconverter((\lab, (\absmem, \absctxt, \absaddr, \abscount))) = (\lab,
-  \asconverter^\memset(\absmem), \asconverter^\ctxtset(\absctxt),
-  \asconverter^\addrset(\absaddr), \abscount)\\
-\]
-The converter for memories $\asconverter^\memset$ is defined with the converter
-for values $\asconverter^\valset$ where:
-\[
-  \asconverter^\valset(\absval) = \left\{
-    \begin{array}{ll}
-      \val & \text{if} \; \absval = \{ \val \}\\
-      \absval & \text{otherwise}\\
-    \end{array}
-  \right.
-\]
-In a similar way, the converter for contexts $\asconverter^\ctxtset$ is defined
-as follows:
-\[
-  \asconverter^\ctxtset(\absctxt)(\absaddr) = \left\{
-    \begin{array}{ll}
-      (\absaddr, \lab, \loc) & \text{if} \; \absctxt(\absaddr) = \{ (\absaddr,
-      \lab, \{ \loc \}) \}\\
-      \absctxt(\absaddr) & \text{otherwise}\\
-    \end{array}
-  \right.
-\]
-The opposite converter $\saconverter: \symbstset \rightarrow (\viewset \times
-\absdom)$ from symbolic states to abstract states is defined as the inverse
-function of $\asconverter$: $\saconverter = \asconverter^{-1}$.
-The symbolic transition relation $\symbtrans$ is an extension of the original
-concrete transition relation $\trans$.  When the exact values of symbolic values
-are required, symbolic states have the symbolic transition relation with the
-exception state $\excst$.  For example, we add the following rule for $\kwret$
-statements:
+(\absimapset \times \symbstset)$ from pairs of views and abstract states to the
+corresponding pairs of abstract instantiation maps and sealed symbolic states.
+The algorithm is to traverse the averall structure, to remain a single value,
+but changes to each abstract value represents multiple values to a new symbol
+and adds the mapping from the new symbol to the original abstract value.  In a
+reverse way, the opposite converter $\saconverter: (\absimapset \times
+\symbstset)  \rightarrow (\viewset \times \absdom)$ recovers the abstract values
+based on the given abstract instantiation map.  The symbolic transition relation
+$\symbtrans$ is an extension of the original concrete transition relation
+$\trans$.  When the exact values of symbolic values are required, symbolic
+states have the symbolic transition relation with the exception state $\excst$.
+For example, we add the following rule for $\kwret$ statements:
 \begin{mathpar}

### 2020-11-21 paper/pldi21/shortcut.tex
Till Sec. 3.4

--- 2020-11-20 paper/pldi21/shortcut.tex
@@
-\section{Dynamic Shortcut}\label{sec:formal}
-
-In this section, we formally define dynamic shortcuts during static analysis by
-combining abstract interpretation with sealed symbolic execution.  We extend the
-formalization of abstract interpretation of \citet{abs-interp-1977,
+\section{Dynamic Shortcuts}\label{sec:formal}
+In this section, we formally define static analysis using dynamic shortcuts by
+introducing sealed symbolic execution in the abstract interpretation framework.
+We extend the formalization of abstract interpretation of \citet{abs-interp-1977,
 abs-interp-1992} and views-based analysis sensitivity of \citet{sens-toplas}.
-For dynamic shortcuts, we define a sealed symbolic execution and extend it to a
-sealed symbolic domain with abstract instantiation maps.  To combine the
-sensitive abstract interpretation with the sealed symbolic execution, we define
-the combined domain of sensitive abstract domain and sealed symbolic domain and
+For dynamic shortcuts, we define sealed symbolic execution and \inred{extend it to} a
+sealed symbolic domain with abstract instantiation maps.  To combine
+sensitive abstract interpretation and sealed symbolic execution, we define
+a combined domain of sensitive abstract domain and sealed symbolic domain and
 explain it with a simple example. Finally, We prove the soundness and
@@
 are transformed to other states.  A \textit{collecting semantics} $\sem{\prog} =
-\{ \st \in \stset \mid \ist \in \istset \wedge \ist \trans^* \st \}$ consists of
-reachable states from initial states of the program $\prog$.  We could calculate
-it using the \textit{transfer function} $\transfer: \dom \rightarrow \dom$ as
+\{ \st \in \stset \mid \ist~\in~\istset \wedge \ist \trans^* \st \}$ consists of
+reachable states from initial states of the program $\prog$.  We can compute
+it using a \textit{transfer function} $\transfer: \dom \rightarrow \dom$ as
 follows:
@@
 \]
-The \textit{concrete domain} $\dom = \powerset{\stset}$ is a complete lattice
+where the \textit{concrete domain} $\dom = \powerset{\stset}$ is a complete lattice
 with $\cup$, $\cap$, and $\subseteq$ as its join($\join$), meet($\meet$), and
@@
 
-\begin{figure}[H]
+\begin{figure}[t]
   \[
@@
   \vspace*{-1em}
-  \caption{The negation of the absolute value of $\varx$}
+  \caption{Negation of the absolute value of $\varx$}
   \label{fig:running-example}
@@
 \times \mathbb{N}$.  Assume that the initial states are $\istset = \{ (\lab_0,
--42) \}$ which means the program starts with the variable $\varx$ that stores
-$-42$ at $\lab_0$.  Then, the program is executed with the following trace:
+-42) \}$, which denotes that the program starts at $\lab_0$
+with the variable $\varx$ of value $-42$.
+Then, it executes with the following trace:
 \[
@@
 \subsection{Abstract Interpretation}\label{sec:ai}
-
-The abstract interpretation~\cite{abs-interp-1977, abs-interp-1992}
-over-approximates the transfer $\transfer$ to the \textit{abstract transfer
-function} $\abstransfer: \absdom \rightarrow \absdom$ to get the
+Abstract interpretation~\cite{abs-interp-1977, abs-interp-1992}
+over-approximates the transfer function $\transfer$ as an \textit{abstract transfer
+function} $\abstransfer: \absdom \rightarrow \absdom$ to get an
 \textit{abstract semantics} $\abssem{\prog}$ in finite iterations as follows:
@@
 \textit{abstraction function} $\alpha$.  The initial abstract state $\iabselem
-\in \absdom$ represents an abstraction of the initial state set; $\ielem
+\in \absdom$ represents an abstraction of the initial state set: $\ielem
 \subseteq \gamma(\iabselem)$.  The abstract transfer function $\abstransfer:
@@
 \join \absstep(\abselem)$ with an \textit{abstract one-step execution}
-$\absstep: \absdom \rightarrow \absdom$.  For the sound state abstraction, the
+$\absstep: \absdom \rightarrow \absdom$.  For a sound state abstraction, the
 join operator and the abstract one-step execution should satisfy the following
@@
 set operators as domain operators; $-$ denotes negative integers, $+$ positive
-integers, and $0$ zero.  Assume that we use it for the code in
-Figure~\ref{fig:running-example} and the initial abstract state is $\iabselem =
-\{ - \}$. Then, the analysis result becomes $\{ -, + \}$ because $\varx$ can
-have positive values by executing $\varx = -\varx$ but there is no way to get
-the value $0$ in this program.
+integers, and $0$ zero.  Assume that we analyze the code in
+Figure~\ref{fig:running-example} with the abstract domain and the initial abstract state $\iabselem =
+\{ - \}$. Then, the analysis result is $\{ -, + \}$ because $\varx$ can
+have a positive value by executing $\varx = -\varx$ but there is no
+way for $\varx$ to have $0$ in this program.
 
@@
 of views $\viewset$ to sets of states $\dom$. Each view $\view \in \viewset$
-represents a set of states $\viewmap(\view)$ and also a state is always included
-in a unique view: $\forall \st \in \stset. \; \exists! \view \in
-\viewset.$ s.t. $\st \in \viewmap(\view)$.  A \textit{sensitive state
+represents a set of states $\viewmap(\view)$ and each state is included
+in a unique view: $\forall \st \in \stset. \; \st \in \viewmap(\view)
+\Rightarrow \not\exists \view' \in \viewset.$ s.t. $\st \in \viewmap(\view')$.
+A \textit{sensitive state
 abstraction} $\dom \galois{\alpha_\viewmap}{\gamma_\viewmap} \sabsdom$ is a
@@
 \]
-where $\viewtrans{\view'}{\view}: \absdom \rightarrow \absdom$ is the abstract
+where $\viewtrans{\view'}{\view}: \absdom \rightarrow \absdom$ is an abstract
 semantics of a \textit{view transition} from a view $\view'$ to another view
@@
 One of the most widely-used analysis sensitivity is \textit{flow sensitivity}
-defined with the flow-sensitive view abstraction $\fsviewmap: \labset
+defined with a flow-sensitive view abstraction $\fsviewmap: \labset
 \rightarrow \dom$ where:
@@
 If we apply the flow sensitivity for the above example with the initial abstract
-state $[ \lab_0 \mapsto \{ -, 0, + \} ]$, the analysis result becomes as follows:
+state $[ \lab_0 \mapsto \{ -, 0, + \} ]$, the analysis result is as follows:
 \[
@@
 relation $\trans$ as a symbolic transition relation $\symbtrans$ on symbolic
-states.  First, we augment concrete states $\stset$ to symbolic states
+states.  First, we extend concrete states $\stset$ to symbolic states
 $\symbstset$ by extending values $\valset$ with \textit{sealed symbolic values}
@@
 \subseteq \symbstset \times \symbstset$. We use the notation $\symbtrans^k$
-for $k$ repetition of $\symbtrans$, and  $\symbst \symbtrans \excst$ when
-$\symbst$ does not have symbolic transitions with any other sealed symbolic
+for $k$ repetition of $\symbtrans$, and write $\symbst \symbtrans \excst$ when
+$\symbst$ does not have any symbolic transitions to other sealed symbolic
 states.  We define the validity of sealed symbolic execution as follows:
@@
   where $\imapset: \symbset \rightarrow \valset$ represent \textit{instantiation
-  maps} from symblic values to concrete values, and $\instant{\symbst}{\imap}$
-  denotes a state produced by replacing each symbolic value $\symb$ to the
+  maps} from symbolic values to concrete values, and $\instant{\symbst}{\imap}$
+  denotes a state produced by replacing each symbolic value $\symb$ in
+  $\symbst$ with its
   corresponding value $\imap(\symb)$ using the instantiation map $\imap \in
@@
 
-Note that The main difference of sealed symbolic execution with the traditional
-symbolic execution~\cite{symbolic} is that it only supports sealed symbolic
+Sealed symbolic execution is different from traditional
+symbolic execution~\cite{symbolic} in that it supports only sealed symbolic
 values instead of symbolic expressions and path constraints.  For example, the
-following trace represents the traditional symbolic execution of the running
+following trace represents traditional symbolic execution of the running
 example in Figure~\ref{fig:running-example}:
@@
 It first assigns a symbolic value $\symb$ to the variable $\varx$ at $\lab_0$.
-For the conditional branch, it is forked by creating two symbolic states with
+For the conditional branch, it creates two symbolic states with
 different path conditions $\symb \geq 0$ and $\symb < 0$ for true and false
@@
 -\varx$, the variable $\varx$ stores symbolic expressions $\symb$ and $-\symb$
-at $\lab_3$. Similarly, $\varx$  stores $-\symb$ and $\symb$ at $\lab_3$.
-However, the sealed symbolic execution stops at $\lab_0$ as follows:
+at $\lab_3$, respectively. Similarly, $\varx$  stores $-\symb$ and $\symb$ at $\lab_4$.
+However, sealed symbolic execution stops at $\lab_0$ as follows:
 \[
-  (\lab_0, 0) \; \symbtrans \; \excst
+  (\lab_0, \symb) \; \symbtrans \; \excst
 \]
@@
 
-To define an abstract domain consists of sealed symbolic states, we define
+To define an abstract domain that contains sealed symbolic states, we define
 \textit{abstract instantiation maps} $\absimapset: \symbset \rightarrow
@@
 \]
-Now, we define the \textit{sealed symbolic domain} as follows:
+Now, we define a \textit{sealed symbolic domain} as follows:
 
@@
   A \textit{sealed symbolic domain} $\symbdom: \powerset{\absimapset \times
-  \symbstset}$ is defined with the following concretization function
-  $\symbgamma: \symbdom \rightarrow \dom$ and sealed symbolic one-step execution
+  \symbstset}$ is defined with the concretization function
+  $\symbgamma: \symbdom \rightarrow \dom$ and the sealed symbolic one-step execution
   $\symbstep: \symbdom \rightarrow \symbdom$ such that

### 2020-11-21 paper/pldi21/ds.tex
Till Sec. 3.5

@@
 \subsection{Combined Domain}
-
-In this part, we define a \textit{combined domain} of a given sensitive abstract
+We now define a \textit{combined domain} of a given sensitive abstract
 domain with the sealed symbolic domain and its one-step execution.
@@
   concretization function $\combgamma: \combdom \rightarrow \dom$ and join
-  operator defined as
+  operator are defined as follows:
   \begin{align}
@@
 \textit{analysis elements} to easily configure different types of abstract
-states in sensitive abstract domain and sealed symbolic domain.
+states in the sensitive abstract domain and the sealed symbolic domain.
 \begin{definition}[Analysis Elements]\label{def:aelem}
@@
   \uplus (\absimapset \times \symbstset)$ is either 1) a pair of a view and an
-  abstract state in sensitive abstract domain $\sabsdom$, or 2) a pair of an
-  abstract instantiation map and a sealed symbolic state in sealed symbolic
+  abstract state in a sensitive abstract domain $\sabsdom$, or 2) a pair of an
+  abstract instantiation map and a sealed symbolic state in a sealed symbolic
   domain $\symbdom$.  Its concretization function $\aelemgamma:
-  \aelemset \rightarrow \dom$ is defined as
+  \aelemset \rightarrow \dom$ is defined as follows:
   \[
@@
 
-Moreover, to freely convert types of analysis elements, we define two converters:
+Moreover, to freely convert between different kinds of analysis elements, we define two converters:
 \begin{align}
@@
 \textit{partial}. Thus, it is possible to convert an analysis element
-$(\view, \abselem)$ in sensitive abstract domain to another analysis element in
-sealed symbolic domain only if the convert $\asconverter$ is defined: $(\view,
+$(\view, \abselem)$ in a sensitive abstract domain to another analysis element in
+a sealed symbolic domain only if the convert $\asconverter$ is defined: $(\view,
 \abselem) \in \Dom(\asconverter)$.  In addition, they should convert given
-elements without loss of information for all $\aelem \in \aelemset$:
+analysis elements without loss of information for all $\aelem \in \aelemset$:
 \[
@@
 Now, we define the \textit{combined one-step execution} $\combstep: \combdom
-\rightarrow \combdom$ with two converters $\asconverter$ and $\saconverter$ and
-it consists of two steps; 1) the \textit{triage} step prepares the execution of
-analysis elements by converting their types via two converters according to
-their status, and 2) the \textit{execution} step performs execution of each
-analysis element using abstract one-step execution $\absstep$ in sensitive
-abstract domain and sealed symbolic one-step execution $\symbstep$ in sealed
+\rightarrow \combdom$ with two converters $\asconverter$ and $\saconverter$.
+It consists of two steps: 1) the \textit{\triagename} step converts
+analysis elements if a new sealed symbolic execution starts or an
+existing one stops, and 2) the \textit{execution} step performs execution of each
+analysis element using the abstract one-step execution $\absstep$ in the sensitive
+abstract domain and the sealed symbolic one-step execution $\symbstep$ in the sealed
 symbolic execution.
@@
 A \textit{combined one-step execution} $\combstep: \combdom \rightarrow
-  \combdom$ is define as
+\combdom$ is define as follows:
   \[
@@
 
-The $\triage$ function decides whether a new sealed symbolic execution is
-\textit{introduced} or an existing one is \textit{terminated}.  When an analysis
-element $(\view, \abselem)$ in the sensitive abstract domain is defined in the
-converter $\asconverter$, a new sealed symbolic execution is introduced by
-converting the analysis element to the corresponding one $(\absimap, \symbst) =
-\asconverter((\view, \abselem))$ in the sealed symbolic domain.  In the other
-hand, assume that if there is no more other sealed symbolic states having
-symbolic transitions with $\symbst$ for an analysis element $(\absimap,
-\symbst)$ in the sealed symbolic domain; $\symbst \symbtrans \excst$.  Then, the
-sealed symbolic execution for $(\absimap, \symbst)$ is terminated by 1)
-converting it to another analysis element $(\view, \abselem) =
-\saconverter((\absimap, \symbst))$ in the sensitive abstract domain and 2)
-merging with the current abstract state stored in the view $\view$ with
-$\abselem$.
+From a given $\combelem$, the $\triage$ function makes analysis elements
+and converts them if a new sealed symbolic execution
+begins or an existing sealed symbolic execution terminates.
+Specifically, for an analysis element $(\view, \abselem)$ in the sensitive abstract domain,
+if the converter $\asconverter$ is defined for it, $\triage$ introduces a new sealed symbolic execution
+by converting the analysis element to its corresponding one $(\absimap, \symbst) =
+\asconverter((\view, \abselem))$ in the sealed symbolic domain.
+On the other hand, for an analysis element $(\absimap, \symbst)$ in the sealed symbolic domain,
+if it does not have any sealed symbolic states to transit to, $\symbst \symbtrans \excst$,
+the sealed symbolic execution for $(\absimap, \symbst)$ terminates;
+It converts the analysis element to its corresponding one $(\view, \abselem) =
+\saconverter((\absimap, \symbst))$ in the sensitive abstract domain and
+merges the current abstract state stored in the view $\view$ with $\abselem$.
 
 To formally define the $\triage$ function, we first define a $\atriage$ function
-for analysis elements using two converters and then define the $\triage$ function.
+for analysis elements using two converters.
 \begin{definition}[$\atriage$]\label{def:atriage}
   The function $\atriage: \aelemset \rightarrow \aelemset$ for analysis elements
-  is defined as
+  is defined as follows:
   \[
@@
 \begin{definition}[$\triage$]\label{def:triage}
-  The triage function $\triage: \combdom \rightarrow \combdom$ for combined
-  states is defined as
+  The \triagename function $\triage: \combdom \rightarrow \combdom$ for combined
+  states is defined as follows:
   \[
@@
   \]
-  (The dot notation $\dot{f}$ denotes the element-wise extended function of a
-  function $f$.)
+and the dot notation $\dot{f}$ denotes the element-wise extended function of a
+function $f$.
 \end{definition}
@@
 Figure~\ref{fig:ds-examples}(b) shows the analysis with the combined domain when
-the initial value of $\varx$ is $0$.  First, in the triage step,
+the initial value of $\varx$ is $0$.  First, in the \triagename step,
 the converter $\asconverter$ converts the analysis element $(\lab_0, 0)$ to

### 2020-11-21 paper/pldi21/ds.tex
Minor revision in Section 3

@@
 existing one stops, and 2) the \textit{execution} step performs execution of each
-analysis element using the abstract one-step execution $\absstep$ in the sensitive
+analysis element using the abstract one-step execution $\sabsstep$ in the sensitive
 abstract domain and the sealed symbolic one-step execution $\symbstep$ in the sealed
-symbolic execution.
+symbolic domain.
 \begin{definition}[Combined One-Step Execution]

### 2020-11-21 paper/pldi21/ds.tex
Till Sec. 3.6

@@
   \end{subfigure}
-  \caption{Three abstract interpretation using combined domain for the running
+  \caption{Abstract interpretation using a combined domain for the running
   example with different initial values for $\varx$.}
@@
 \subsection{Examples}
-
-For examples of the abstract interpretation with the combined domain,
+Now, we show examples of abstract interpretation with a combined domain.
 Figure~\ref{fig:ds-examples} depicts the flow of analysis for the running
-example in Figure~\ref{fig:running-example} with three different initial set of
+example in Figure~\ref{fig:running-example} with three different initial sets of
 values for the variable $\varx$.  In this example, we use the abstract domain
-$\{ -, 0, + \}$ for integers stored in $\varx$ introduced in
-Section~\ref{sec:ai}, and the \textit{flow sensitivity} which utilizes the
-labels of states as their views introduced in Section~\ref{sec:sens}.  For
-brevity, we use the concatenated form to represent the abstract values such as
+$\{ -, 0, + \}$ for integers stored in $\varx$ as introduced in
+Section~\ref{sec:ai}, and the \textit{flow sensitivity} that utilizes the
+labels of states as their views as introduced in Section~\ref{sec:sens}.
+For brevity, we use concatenation of abstract values so that
 $-0$ denotes the set $\{ -, 0 \}$.
 
-Figure~\ref{fig:ds-examples}(a) explains notations used in each graph. A solid
-box denotes an analysis element, which is a pair of label $\lab$ and abstract
-state $\abselem$.  A pair wrapped with angle brackets denotes an analysis
-element, which is a pair of abstract instantiation map $\absimap$ and sealed
+Figure~\ref{fig:ds-examples}(a) presents notations used in each graph. A solid
+box denotes an analysis element that is a pair of a label $\lab$ and an abstract
+state $\abselem$.  A pair enclosed by angle brackets denotes an analysis
+element that is a pair of an abstract instantiation map $\absimap$ and a sealed
 symbolic state $\symbst$.  In fact, the sealed symbolic state part (right) of
 each pair in graphs contains only the value of the variable of $\varx$ without
-the current label.  For brevity, we represents its label by locating them in the
-next to the corresponding label.  A solid line is a view transition
+its label.  For brevity, we represent its label by locating it next to
+a node with its label.  A solid line is a view transition
 $\viewtrans{\lab}{\lab'}$ from a label $\lab$ to another one $\lab'$.  A dotted
@@
 another analysis element $\langle \varnothing, 0 \rangle$ with the label
-$\lab_0$.  Moreover, it does not introduce any sealed symbolic values because
+$\lab_0$.  It does not introduce any sealed symbolic values because
 the value represents only a single value.  Until the end of the program, the
-sealed symbolic execution from $\langle \varnothing, 0 \rangle$ is successfully
-continues.  However, there is no more possible symbolic transition for the
-symbolic state $\langle \varnothing, 0 \rangle$ with the label $\lab_4$.  Thus,
+sealed symbolic execution from $\langle \varnothing, 0 \rangle$ successfully
+continues.  Because there is no more possible symbolic transition for the
+symbolic state $\langle \varnothing, 0 \rangle$ with the label $\lab_4$,
 it is converted to $(\lab_4, 0)$ via the converter $\saconverter$.
@@
 any positive integers.  Figure~\ref{fig:ds-examples}(c) describes the analysis
-flow for such case.  Then, the initial abstract value at the label $\lab_0$ is
-$+$ and it is impossible to convert to any sealed symbolic values because the
+flow for the case.  The initial abstract value at the label $\lab_0$ is
+$+$ and it is impossible to convert it to any sealed symbolic values because the
 next program statement requires the actual value stored in the variable $\varx$
@@
 the abstract value $+$ and the result is also $+$.  Now, the analysis element
-$(\lab_1, +)$ could be converted to $\langle \symb \mapsto +, \symb \rangle$
+$(\lab_1, +)$ can be converted to $\langle \symb \mapsto +, \symb \rangle$
 with the label $\lab_1$.  This sealed symbolic execution step terminates in the
 label $\lab_3$ because the next statement is $\varx = -\varx$ and the negation
-operator requires the actual value of $\varx$.  Finally, it performs the view
-transition and the result is $(\lab_4, -)$.
+operator requires the actual value of $\varx$.  It is converted to $(\lab_3, +)$ via $\saconverter$,
+performs the view transition, and results in $(\lab_4, -)$.
 
@@
 While it reaches the false branch in the label $\lab_2$ unlike previous cases,
-it also cannot perform dynamic shortcuts because the statement in the false
-branch is $\varx = -\varx$.  At the label $\lab_3$, there is two analysis
-elements: 1) $(\lab_3, +)$ introduced by view transition from the label $\lab_2$
-with $-$, and 2) $\langle \symb \mapsto 0+, \symb \rangle$ with $\lab_2$
-introduced by sealed symbolic execution started at $\lab_1$.  However, since it
+it cannot perform dynamic shortcuts because the statement in the false
+branch is $\varx = -\varx$, which requires the actual value of $\varx$.
+At the label $\lab_3$, there are two analysis
+elements: 1) $(\lab_3, +)$ introduced by the view transition from the label $\lab_2$
+with $-$, and 2) $\langle \symb \mapsto 0+, \symb \rangle$ with $\lab_3$
+introduced by sealed symbolic execution started at $\lab_1$.  Since it
 is not possible to perform sealed symbolic execution for both elements, the
-second one is converted to $(\lab, 0+)$ and merged with $+$ at $\lab_3$ via the
+second one is converted to $(\lab_3, 0+)$ and merged with $+$ at $\lab_3$ via the
 join operator $\join$.  Finally, the view transition

### 2020-11-21 paper/pldi21/ds.tex
Till Sec. 3.7

@@
 
-From a given $\combelem$, the $\triage$ function makes analysis elements
+From a given combined state $\combelem$, the $\triage$ function makes analysis elements
 and converts them if a new sealed symbolic execution
@@
 \subsection{Soundness and Termination}
-
-The converter $\asconverter$ and the sealed symbol transition $\symbtrans$ are
+The converter $\asconverter$ and the sealed symbolic transition $\symbtrans$ are
 keys to configure the introduction and termination of sealed symbolic
-executions.  To ensure the \textit{soundness} and \textit{termination} of the
-abstract interpretation defined with the combined domain of sensitive abstract
-domain and sealed symbolic domain, the following conditions should be hold.
+execution.  To ensure the \textit{soundness} and \textit{termination} of an
+abstract interpretation defined with a combined domain of a sensitive abstract
+domain and a sealed symbolic domain, the following conditions should hold.
 
 \begin{theorem}[Soundness and Termination]\label{theorem:shortcut}
-  The abstract interpretation with dynamic shortcut is \textbf{sound} and
-  \textbf{terminates} in a finite time if
+An abstract interpretation with dynamic shortcuts is \textbf{sound} and
+\textbf{terminates} in a finite time if:
   \begin{itemize}
-    \item The abstract transfer $\abstransfer$ is sound
-    \item The sensitive abstract domain $\sabsdom$ has finite height
-    \item The sealed symbolic transition $\symbtrans$ is valid
-    \item There exists $N < \infty$ such that
+    \item the abstract transfer function $\abstransfer$ is sound,
+    \item the sensitive abstract domain $\sabsdom$ has a finite height,
+    \item the sealed symbolic transition $\symbtrans$ is valid, and
+    \item there exists $N < \infty$ such that
       \[
@@
 
-To prove the termination of the abstract interpretation with the combined
-domain, the condition provides an upper bound of the number of sealed symbolic
-states after the sensitive abstract states are reached the fixed point.  Thus,
-the termination of the analysis is guaranteed.  For the proof of Soundness, two
-properties (\ref{equ:sound-join}) for join operator $\join$ and
-(\ref{equ:sound-step}) for combined one-step execution are required to be
-proved.  The core idea of the proof is to use Lemma~\ref{lemma:step-symb} and
-Lemma~\ref{ref:lemma:triage} for the sealed symbolic one-step execution
-$\symbstep$ and the $\triage$ function. Because of the page limitation, we omit
-the proof in this paper and include it in a companion report~\cite{report}.
+The second and the fourth conditions provide upper bounds of
+the number of sensitive abstract states and
+the number of sealed symbolic states, respectively.
+Thus, it guarantees the termination of the analysis.
+
+For soundness proof, we should prove 
+two conditions presented in Section~\ref{sec:ai}:
+(\ref{equ:sound-join}) for the join operator $\join$ and
+(\ref{equ:sound-step}) for the combined one-step execution.
+The core idea of the proof is to use Lemma~\ref{lemma:step-symb} and
+Lemma~\ref{lemma:triage} for the sealed symbolic one-step execution
+$\symbstep$ and the $\triage$ function, respectively. Due to the page limitation, we omit
+the proof in this paper and present it in a companion report~\cite{report}.
 \begin{lemma}\label{lemma:step-symb}
-  Assume that the following condition is hold
+  Assume that the following condition holds:
   \[
     \forall (\absimap, \symbst) \in \symbelem. \; \exists \symbst' \in
-    \symbstset. \; \text{s.t.} \; \symbst \symbtrans \symbst'
+    \symbstset. \; \symbst \symbtrans \symbst'
   \]
@@
     \item $\forall (\absimap, \symbst) \in \symbelem. \; \exists \symbst' \in
-      \symbstset.  \; \text{s.t.} \; \symbst \symbtrans \symbst'$
+      \symbstset.  \; \symbst \symbtrans \symbst'$
   \end{itemize}

### 2020-11-21 paper/pldi21/eval.tex
Section 6.1 ing...

@@
 value-partitioning} also used the tests to evaluate their techniques.
-Among them, we filtered out \inred{37} tests that use JavaScript language
+Among them, we filtered out 37 tests that use JavaScript language
 features SAFE does not support such as dynamic code generation using
 \jscode{Function}, getters and setters, and browser-specific features like $\jscode{__proto__}$.
-Thus, we used \inred{269} out of 306 tests for the evaluation of $\tool$.
+Thus, we used 269 out of 306 tests for the evaluation of $\tool$.
 We performed our experiments on a Ubuntu machine
@@
 To evaluate the effectiveness of using dynamic shortcuts, we performed static
-analysis of \inred{269} Lodash 4 tests with and without dynamic shortcuts.
-Figure~\ref{fig:conc-analysis-time} depicts histograms for their analysis
-time and a box plot for speed up after applying dynamic shortcuts.
-While the baseline analysis (no-DS) finished analysis of \inred{199} out of \inred{269} tests within 5
-minutes, our tool (DS) finished analysis of all tests using dynamic shortcuts.
-For \inred{199} tests analyzable by both analyzers, on average, the analysis took \inred{168.4}
-seconds for no-DS and \inred{12.2} seconds for DS, which shows that
-using dynamic shortcuts outperforms the baseline analyzer \inred{20.16}\textsf{x} on average.
-Only for one test using $\jscode{_.sample}$, a Lodash 4 library
+analysis of 269 Lodash 4 tests with and without dynamic shortcuts.
+Figure~\ref{fig:conc-analysis-time} depicts cumulative distribution charts for
+their analysis time and a box plot in a logarithmic scale for speed up after
+applying dynamic shortcuts.  In the upper chart, the $x$-axis is time and the
+$y$-axis shows the number of tests until the time.  While the baseline analysis
+(no-DS) finished analysis of 200 out of 269 tests within 5 minutes, our tool
+(DS) finished analysis of 263 tests using dynamic shortcuts.  For finished
+tests, the average analysis time is 49.57 seconds for no-DS and 2.78 seconds for
+DS.  Since only few tests analyzed in 2 to 5 minutes (8 tests for no-DS
+and no tests for DS), we only show the results until 2 minutes on the
+cumulative distribution charts to show the difference between their results more
+clearly.  Among 200 tests analyzed by no-DS, two tests are timeout in DS thus
+198 tests are analyzable by both analyzers. For them, we depicts the box plot for
+analysis speed up by applying dynamic shortcuts.  It shows that tsing dynamic
+shortcuts outperforms the baseline analyzer at most 54.98$\x$ and 19.96$\x$ on
+average.  Only for one test using $\jscode{_.sample}$, a Lodash 4 library
 function that randomly samples a value from a given array, DS showed
-\inred{0.81}\textsf{x} speed of no-DS due to frequent use of
-dynamic shortcuts, that is \inred{24} times.
+0.90$\x$ speed of no-DS due to frequent use of dynamic shortcuts, that is 24
+times.
 
@@
 non-deterministic user inputs, they can be analyzed by a few number of dynamic shortcuts.
-In fact, among \inred{269} tests, \inred{262} tests are analyzed
+In fact, among 269 tests, 262 tests are analyzed
 by a single dynamic shortcut without using abstract semantics.
@@
 Figure~\ref{fig:abs-analysis-time} shows the analysis time of the abstracted tests.
-Among \inred{269} abstracted tests, no-DS finished analysis of \inred{82} tests within 5 minutes,
-but DS finished analysis of \inred{219} tests.  For \inred{82} tests analyzable by both analyzers,
-on average, the analyses took \inred{168.4} seconds for no-DS and \inred{12.2} seconds for DS,
-which shows that dynamic shortcuts outperforms the baseline analyzer
-\inred{20.16}\textsf{x} on average.
+Only 4 tests for no-DS and 9 tests for DS are finished between 2 to 5 minutes.
+Among 269 abstracted tests, no-DS finished analysis of 158 tests within 5 minutes,
+but DS finished analysis of 168 tests.  For finished tests, the average analysis
+time is 44.88 seconds for no-DS and 42.28 seconds for DS. Among 158 tests analyzed by no-DS, DS
+fails to analysis 15 tests in the time limit thus 143 tests are analyzable by
+both analyzers.  For them, the dynamic shortcuts outperforms the baseline
+analyzer at most 50.60$\x$ and 20.16$\x$ on average.
 

### 2020-11-21 paper/pldi21/javascript.tex
Till Sec. 4.2

@@
-\section{Dynamic Shortcut for JavaScript}\label{sec:javascript}
-
+\section{Dynamic Shortcuts for JavaScript}\label{sec:javascript}
 In this section, we introduce the core language of JavaScript that supports
 first-class functions, open objects, and first-class property names, and define
-sealed symbolic execution of the core language for dynamic shortcut.
+sealed symbolic execution of the core language for dynamic shortcuts.
+Due to the space limitation, we present the main design of the
+language in this paper and refer the interested readers to a companion report~\cite{report}.
 
@@
 address or an object address.  A function value $\fval{x}{\lab} \in \fvalset$
-consists of a parameter and a body label.  In the core language, the closed
-scoping is used for functions for brevity thus only parameters and local
-variables are accessible in the function body.
+consists of a parameter name and a body label.  In the core language, the closed
+scoping is used for functions for brevity, thus only parameters and local
+variables are accessible in a function body.
 
@@
 $\istset = \{ (\ilab, \varnothing, \epsilon, \tladdr) \}$ where $\ilab$ denotes
-the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level environment
-address.  The function $\labnext$ returns the next label of a given label in the
-current program $\prog$.
+the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level environment address.
 
 \subsection{Abstract Semantics}
-
-In abstract semantics of the core language, we use the flow sensitivity with a
+In the abstract semantics of the core language, we use the flow sensitivity with a
 flow sensitive view abstraction $\fsviewmap: \labset \rightarrow \dom$ that
@@
 \absdom$.  We define an abstract state $\abselem \in \absdom$ as a tuple of an
-abstract memory, an abstract context, an abstract address, and set of singleton
-abstract addresses as follows:
+abstract memory, an abstract context, an abstract address, and an
+abstract counter as follows:
 
 \[
-  \begin{array}{lr@{~}c@{~}l@{~}c@{~}l}
-    \text{Abstract States} & \abselem &\in& \absdom &=& \absmemset \times \absctxtset
+  \begin{array}{l@{~}r@{~}c@{~}l@{~}c@{~}l}
+\text{Abstract states} & \abselem &\in& \absdom &=& \absmemset \times \absctxtset
 \times \absaddrset \times \abscountset\\
-    \text{Abstract Memories} & \absmem &\in& \absmemset &=& \abslocset \finmap
+\text{Abstract memories} & \absmem &\in& \absmemset &=& \abslocset \finmap
 \absvalset\\
-    \text{Abstract Contexts} & \absctxt &\in& \absctxtset &=& \absaddrset \finmap
+\text{Abstract locations} & \absloc &\in& \abslocset &=& (\absaddrset \times
+\varset) \uplus (\absaddrset \times \strset)\\
+\text{Abstract addresses} & \absaddr &\in& \absaddrset &=& \labset\\
+\text{Abstract contexts} & \absctxt &\in& \absctxtset &=& \absaddrset \finmap
 \powerset{\absaddrset \times \viewset \times \powerset{\abslocset}}\\
-    \text{Abstract Locations} & \absloc &\in& \abslocset &=& (\absaddrset \times
-    \varset) \uplus (\absaddrset \times \strset)\\
-    \text{Abstract Values} & \absval &\in& \absvalset &=& \powerset{\pvalset
+\text{Abstract counters} & \abscount &\in& \abscountset &=& \absaddrset
+\rightarrow \{ \abszero, \absone, \absmany \}\\
+\text{Abstract values} & \absval &\in& \absvalset &=& \powerset{\pvalset
 \uplus \absaddrset \uplus \fvalset}\\
-    \text{Abstract Addresses} & \absaddr &\in& \absaddrset &=& \labset\\
-    \text{Abstract Counters} & \abscount &\in& \abscountset &=& \absaddrset
-    \rightarrow \{ \abszero, \absone, \absmany \}\\
   \end{array}
@@
 counting~\cite{abstract-gc-counting, revisit-recency} in static analysis, we
-define abstract counters $\abscountset$ that maps from abstract addresses to
+define abstract counters $\abscountset$ that are mappings from abstract addresses to
 their abstract counts representing how many times each abstract address has been
 allocated; $\abszero$ denotes that it has never been allocated, $\absone$ once,
-and $\absmany$ more than or equals to twice.
+and $\absmany$ more than or equal to twice.
 
-We define the semantics of view transition for the core language.  For abstract
+We define the semantics of the view transition for the core language.  For abstract
 memories, we use the notation $\absmem[L \mapstos \absval]$ to represent the
@@
 $(\absaddr, \_) \in L$ is singleton: $\abscount(\absaddr) = \absone$.
-Otherwise, it performs the weak update for the soundness.  Moreover, we define
+Otherwise, it performs the weak update for the analysis soundness.  We use
 the increment function $\inc: \abscountset \times \absaddrset \rightarrow

### 2020-11-21 paper/pldi21/javascript.tex
Updated javascript.tex

@@
 
-We define the symbolic states with the extended concrete values and the abstract
-counters for addresses as follows:
+We define the sealed symbolic states by not only extending the concrete values
+$\valset$ with symbolic values $\symbset$ but also adding the abstract counters
+$\abscountset$ as follows:
 \[
@@
 \]
-We define the converter $\asconverter: (\viewset \times \absdom) \rightarrow
-(\absimapset \times \symbstset)$ from pairs of views and abstract states to the
-corresponding pairs of abstract instantiation maps and sealed symbolic states.
-The algorithm is to traverse the averall structure, to remain a single value,
-but changes to each abstract value represents multiple values to a new symbol
-and adds the mapping from the new symbol to the original abstract value.  In a
-reverse way, the opposite converter $\saconverter: (\absimapset \times
-\symbstset)  \rightarrow (\viewset \times \absdom)$ recovers the abstract values
-based on the given abstract instantiation map.  The symbolic transition relation
-$\symbtrans$ is an extension of the original concrete transition relation
-$\trans$.  When the exact values of symbolic values are required, symbolic
-states have the symbolic transition relation with the exception state $\excst$.
-For example, we add the following rule for $\kwret$ statements:
+The objects in JavaScript are open thus their properties can be dynamically
+added or deleted.  Moreover, the object properties are accessible via string
+values thus it is difficult to decide whether the strong udpates are possible or
+not in static analysis.  To check the possibility of strong updates during
+sealed symbolic execution, we augmented its states with the abstract counters
+$\abscountset$.  Then, we define the converter $\asconverter: (\viewset \times
+\absdom) \rightarrow (\absimapset \times \symbstset)$ by traversing the averall
+structure of given abstract states to keep singleton values but to change each
+abstract value to a unique symbolic value.  During the traverse, we also keep
+the mapping from symbolic values to the corresponding abstract values to
+construct an abstract instantiation map.  For the opposite converter
+$\saconverter: (\absimapset \times \symbstset)  \rightarrow (\viewset \times
+\absdom)$, we just recovers the abstract values using the given abstract
+instantiation map.  We only define the sealed symbolic transition relation
+$\symbtrans$ when the next step does not require actual values of any symbolic
+values.  If not, a given sealed symbolic state does not have sealed symbolic
+transitions with any other ones.  For example, we add the following rule for
+$\kwret$ statements:
 \begin{mathpar}

### 2020-11-21 paper/pldi21/javascript.tex
Till Sec. 4.3

--- 2020-11-21 paper/pldi21/javascript.tex
@@
 \]
-We define the converter $\asconverter: (\viewset \times \absdom) \rightarrow
-(\absimapset \times \symbstset)$ from pairs of views and abstract states to the
-corresponding pairs of abstract instantiation maps and sealed symbolic states.
-The algorithm is to traverse the averall structure, to remain a single value,
-but changes to each abstract value represents multiple values to a new symbol
-and adds the mapping from the new symbol to the original abstract value.  In a
-reverse way, the opposite converter $\saconverter: (\absimapset \times
-\symbstset)  \rightarrow (\viewset \times \absdom)$ recovers the abstract values
-based on the given abstract instantiation map.  The symbolic transition relation
-$\symbtrans$ is an extension of the original concrete transition relation
-$\trans$.  When the exact values of symbolic values are required, symbolic
-states have the symbolic transition relation with the exception state $\excst$.
-For example, we add the following rule for $\kwret$ statements:
+Because JavaScript provides open objects, the properties of objects can be dynamically added or deleted.
+Moreover, since object properties are string values that can be constructed at run time,
+it is difficult for static analysis to know whether strong udpates are possible or not.
+To check the possibility of strong updates during sealed symbolic execution,
+we augment its states with the abstract counters $\abscountset$.
+
+For each abstract value in a given abstract state,
+if the abstract value denotes a single concrete value,
+the converter $\asconverter: (\viewset \times
+\absdom) \rightarrow (\absimapset \times \symbstset)$
+keeps it as it is; otherwise, $\asconverter$ replaces the abstract
+value with its unique identifier and maintains the mapping from the
+unique identifier to the abstract value to construct an abstract instantiation map.
+The opposite converter $\saconverter: (\absimapset \times
+  \symbstset)  \rightarrow (\viewset \times \absdom)$
+recovers abstract values from their unique identifiers using the abstract instantiation map.
+We define the sealed symbolic transition relation $\symbtrans$
+only if the next step does not require actual values of any symbolic values.
+Otherwise, a given sealed symbolic state does not have any sealed symbolic
+transitions to apply.  For example, we add the following rule for the $\kwret$ statement:
 \begin{mathpar}
@@
     \prog(\lab) = \kwret \; \expr\\
-    \exprrule{\st}{\expr}{\val}\\
+    \exprrule{\symbst}{\expr}{\val}\\
     \ctxt(\addr) \in \symbset
@@
   {
-    \st = (\lab, \mem, \ctxt, \addr)
-    \trans \excst
+    \symbst = (\lab, \mem, \ctxt, \addr, \abscount)\
+    \symbtrans \excst
   }
 \end{mathpar}
-We extend each rule of concrete semantics to support such behaviors of symbolic
+We extend each rule of the concrete semantics to support such behaviors of symbolic
 values.

### 2020-11-21 paper/pldi21/intro.tex
Added figure 8. Removed inred in intro and motivation.

@@
   \vspace*{-2em}
-  \caption{Performance of a dynamic analyzer and a static analyzer for V8
-  benchmarks version 7}
+  \caption{Performance of a dynamic analyzer and a static analyzer for a subset
+  of the SunSpider benchmark}
   \label{fig:performance}
@@
 static analyzers.  Figure~\ref{fig:performance} shows that the dynamic analyzer
-Jalangi is \inred{X.X}x faster than the static analyzer SAFE for V8 benchmarks
-version 7.  Using high performance dynamic analysis, researchers have
+Jalangi is 34.8x faster than the static analyzer SAFE for a subset of the
+SunSpider benchmark.  Using high performance dynamic analysis, researchers have
 reduced the scope of static analysis~\cite{determinacy, blendedJS} and constructed
@@
 To evaluate our technique, we implemented $\tool$ using both SAFE
-and Jalangi and analyzed \inred{77} official tests of Lodash 4 library.
+and Jalangi and analyzed 269 official tests of Lodash 4 library.
 
@@
 extended combination of SAFE and Jalangi.
-\item For empirical evaluation, we analyzed \inred{77} official tests of
-\inred{Lodash 4} library.  The experiment shows that $\tool$ outperforms
+\item For empirical evaluation, we analyzed 269 official tests of
+Lodash 4 library.  The experiment shows that $\tool$ outperforms
 SAFE \inred{X.X}x on average.  Moreover, by using dynamic shortcuts
 instead of manual modeling for \inred{XX.X} opaque functions,
-$\tool$ improves \inred{XX.XX}\% of the analysis precision on average.
+$\tool$ improves the analysis precision to detect 5.97 more dead branches on
+average.
 \end{itemize}

### 2020-11-21 paper/pldi21/motivation.tex
Added figure 8. Removed inred in intro and motivation.

@@
 the most popular npm package\footnote{https://www.npmjs.com/browse/depended}
-and \inred{124,562} npm packages have a dependency on it.
+and 124,287 npm packages have a dependency on it.
 The \jscode{concat} function creates a new array concatenating given arrays or values.

### 2020-11-21 paper/pldi21/intro.tex
Fixed overflow in the contribution bullet.

@@
 instead of manual modeling for \inred{XX.X} opaque functions,
-$\tool$ improves the analysis precision to detect 5.97 more dead branches on
+$\tool$ improves the analysis precision to detect 6 more dead branches on
 average.

### 2020-11-21 paper/pldi21/eval.tex
Temporal dump

@@
   \vspace*{-1.5em}
-  \caption{Analysis time ratio for \inred{219} \textit{abstracted} tests}
+  \caption{Analysis time ratio for 143 \textit{abstracted} tests}
   \label{fig:abs-analysis-ratio}
@@
 
-Unlike for the original tests, analysis of \inred{82}
+\begin{table*}[t]
+  \centering
+  \caption{The number of \textit{abstracted} tests using dynamic shortcut
+  instead of manual modeling for each JavaScript built-in library}
+  \label{table:func-replace}
+  \vspace*{-1em}
+  \scriptsize
+  \[
+    \begin{array}{c|l|c|c?c|l|c|c?c|l|c|c}
+
+      \myhead{Object}       {Function}        {\# Replaced}
+
+      \mydata{1}{}          {Array    }  {214 / 214}{214 / 214} & \mydata{1}{}             {String     }  {214 / 214}{214 / 214} & \mydata{1}{}       {Object        }  {214 / 214}{214 / 214} \mylinefff
+      \mydata{1}{}          {new Array}  {214 / 214}{214 / 214} & \mydata{1}{}             {toString   }  {214 / 214}{214 / 214} & \mydata{1}{}       {new Object    }  {214 / 214}{214 / 214} \mylinefff
+      \mydata{1}{}          {isArray  }  {214 / 214}{214 / 214} & \mydata{1}{}             {valueOf    }  {214 / 214}{214 / 214} & \mydata{1}{}       {getPrototypeOf}  {214 / 214}{214 / 214} \mylinetff
+      \mydata{1}{}          {concat   }  { 92 /  92}{139 /  92} & \mysucc{1}{}             {charAt     }  {214 /  92}{214 /  92} & \mydata{1}{}       {create        }  {214 /  92}{214 /  92} \mylinetff
+      \mydata{1}{}          {join     }  {193 / 193}{214 / 193} & \mydata{1}{}             {charCodeAt }  {214 / 193}{214 / 193} & \mydata{1}{Object} {defineProperty}  {214 / 193}{214 / 193} \mylinefff
+      \mydata{1}{}          {pop      }  {214 / 214}{214 / 214} & \mydata{1}{}             {indexOf    }  {214 / 214}{214 / 214} & \mydata{1}{}       {freeze        }  {214 / 214}{214 / 214} \mylinefft
+      \mydata{2}{Array}     {push     }  {214 / 214}{214 / 214} & \mydata{1}{String}       {match      }  {214 / 214}{214 / 214} & \mydata{1}{}       {keys          }  {214 / 214}{214 / 214} \mylineftf
+      \mysucc{1}{}          {reverse  }  {214 / 214}{214 / 214} & \mydata{1}{}             {replace    }  {214 / 214}{214 / 214} & \mydata{1}{}       {toString      }  {214 / 214}{214 / 214} \mylinefff
+      \mydata{1}{}          {shift    }  {214 / 214}{214 / 214} & \mydata{1}{}             {slice      }  {214 / 214}{214 / 214} & \mydata{1}{}       {hasOwnProperty}  {214 / 214}{214 / 214} \mylineftf
+      \mydata{1}{}          {slice    }  {214 / 214}{214 / 214} & \mydata{1}{}             {split      }  {214 / 214}{214 / 214} & \mysucc{1}{}       {parseInt}        {214 / 214}{214 / 214} \mylinefff
+      \mydata{1}{}          {sort     }  {214 / 214}{214 / 214} & \mydata{1}{}             {substring  }  {214 / 214}{214 / 214} & \mydata{1}{Global} {isNaN   }        {214 / 214}{214 / 214} \mylinefff
+      \mydata{1}{}          {splice   }  {214 / 214}{214 / 214} & \mydata{1}{}             {toLowerCase}  {214 / 214}{214 / 214} & \mydata{1}{}       {isFinite}        {214 / 214}{214 / 214} \mylinefff
+      \mydata{1}{}          {unshift  }  {214 / 214}{214 / 214} & \mydata{1}{}             {toUpperCase}  {214 / 214}{214 / 214} & \mydata{1}{}       {RegExp    }      {214 / 214}{214 / 214} \mylinetff
+      \mysucc{1}{}          {indexOf  }  {214 / 214}{214 / 214} & \mydata{2}{Boolean}      {Boolean}      {214 / 214}{214 / 214} & \mysucc{2}{RegExp} {new RegExp}      {214 / 214}{214 / 214} \mylinetff
+      \mydata{1}{}          {every    }  {214 / 214}{214 / 214} & \mydata{1}{}             {valueOf}      {214 / 214}{214 / 214} & \mydata{1}{}       {exec      }      {214 / 214}{214 / 214} \mylinefff
+      \mydata{1}{}          {ceil }      {214 / 214}{214 / 214} & \mydata{2}{Number}       {Number }      {214 / 214}{214 / 214} & \mydata{1}{}       {test      }      {214 / 214}{214 / 214} \mylinefff
+      \mydata{1}{}          {floor}      {214 / 214}{214 / 214} & \mydata{1}{}             {valueOf}      {214 / 214}{214 / 214} & \mydata{1}{}       {Error         }  {214 / 214}{214 / 214} \mylinefff
+      \mydata{1}{Math}      {max  }      {214 / 214}{214 / 214} & \mydata{1}{}             {toString}     {214 / 214}{214 / 214} & \mydata{2}{Error}  {new Error     }  {214 / 214}{214 / 214} \mylinefff
+      \mydata{1}{}          {min  }      {214 / 214}{214 / 214} & \mydata{1}{Function}     {apply   }     {214 / 214}{214 / 214} & \mydata{1}{}       {new RangeError}  {214 / 214}{214 / 214} \mylinefff
+      \mydata{1}{}          {pow  }      {214 / 214}{214 / 214} & \mydata{1}{}             {call    }     {214 / 214}{214 / 214} & \mydata{1}{}       {new TypeError }  {214 / 214}{214 / 214}
+    \end{array}
+  \]
+  \vspace*{-1em}
+\end{table*}
+
+Unlike for the original tests, analysis of 143
 abstracted tests that are analyzable by both analyzers invoked
-\inred{xx} dynamic shortcuts.  Because taking a dynamic shortcut
+16.05 dynamic shortcuts.  Because taking a dynamic shortcut
 requires converting between abstract states and sealed symbolic values
@@
 
+\todo
 To experimentally evaluate the conjecture, we investigated the relationship between
 the communication cost between analyzers and the number of dynamic shortcuts.
-For \inred{xx} original tests, the communication cost was only
-\inred{x.xx}\% of the total analysis time.  However, for \inred{xx}
+For 198 original tests, the communication cost was only
+\inred{x.xx}\% of the total analysis time.  However, for 143
 abstracted tests, the communication cost was \inred{xx.xx}\% of the
 total analysis time.  Figure~\ref{fig:abs-analysis-ratio} presents the
-analysis time ratio for \inred{82} abstracted tests.
+analysis time ratio for 143 abstracted tests.
 The $x$-axis represents the time ratio normalized by the total analysis time with dynamic shortcuts
 and the $y$-axis denotes the number of dynamic shortcuts and the number of corresponding tests.
-For all \inred{82} tests, the communication cost (DS-Comm.) is larger than
+For all 143 tests, the communication cost (DS-Comm.) is larger than
 both the static analysis time (DS-Static) and the dynamic analysis
@@
     \vspace*{-1.5em}
-    \caption{Reachable branches for \inred{xx} \textit{original} tests}
+    \caption{Reachable branches for 198 \textit{original} tests}
     \label{fig:precision-fail}
@@
     \vspace*{-1.5em}
-    \caption{Reachable branches for \inred{82} \textit{abstracted} tests}
+    \caption{Reachable branches for 143 \textit{abstracted} tests}
     \label{fig:precision-branch}
@@
 \end{figure}
-
-\begin{table*}[t]
-  \centering
-  \caption{The number of \textit{abstracted} tests using dynamic shortcut
-  instead of manual modeling for each JavaScript built-in library}
-  \label{table:func-replace}
-  \vspace*{-1em}
-  \scriptsize
-  \[
-    \begin{array}{c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}}
-
-      \myhead{Object}       {Function}        {\# Replaced}
-
-      \mysucc{2}{Boolean}   {Boolean}         {214}{214}{100} & \mydata{1}{}            {new Object}        {214}{214}{100} & \mymult{2}{Number}      {valueOf}       {214}{214}{100} \mylineff
-      \mydata{1}{}          {new Boolean}     {214}{214}{100} & \mydata{1}{}            {getPrototypeOf}    {214}{214}{100} & \myname{1}{.prototype}                                  \mylinetft
-      \mydata{1}{Array}     {isArray}         {214}{214}{100} & \mydata{1}{}            {create}            {214}{214}{100} & \mymult{2}{RegExp}      {toString}      {214}{214}{100} \mylinetf
-      \mydata{1}{}          {toString}        { 92}{139}{ 66} & \mydata{1}{Object}      {preventExtensions} {214}{214}{100} & \myname{1}{.prototype}                                  \mylinefft
-      \mydata{1}{}          {toLocaleString}  {193}{214}{ 90} & \mydata{1}{}            {isFrozen}          {214}{214}{100} & \mydata{2}{String}      {String}        {214}{214}{100} \mylinefff
-      \mydata{1}{}          {concat}          {214}{214}{100} & \mydata{1}{}            {isExtensible}      {214}{214}{100} & \mydata{1}{}            {fromCharCode}  {214}{214}{100} \mylinefft
-      \mydata{1}{}          {join}            {214}{214}{100} & \mydata{1}{}            {keys}              {214}{214}{100} & \mydata{1}{}            {charAt}        {214}{214}{100} \mylineftf
-      \mysucc{1}{Array}     {pop}             {214}{214}{100} & \mydata{1}{Object}      {valueOf}           {214}{214}{100} & \mydata{1}{}            {charCodeAt}    {214}{214}{100} \mylinefff
-      \mydata{1}{.prototype}{push}            {214}{214}{100} & \mydata{1}{.prototype}  {isPrototypeOf}     {214}{214}{100} & \mydata{1}{}            {indexOf}       {214}{214}{100} \mylineftf
-      \mydata{1}{}          {slice}           {214}{214}{100} & \mydata{1}{}            {acos}              {214}{214}{100} & \mysucc{1}{}            {match}         {214}{214}{100} \mylinefff
-      \mydata{1}{}          {splice}          {214}{214}{100} & \mysucc{1}{}            {atan2}             {214}{214}{100} & \mydata{1}{String}      {replace}       {214}{214}{100} \mylinefff
-      \mydata{1}{}          {map}             {214}{214}{100} & \mydata{1}{}            {cos}               {214}{214}{100} & \mydata{1}{.prototype}  {splice}        {214}{214}{100} \mylinefff
-      \mydata{1}{}          {reduce}          {214}{214}{100} & \mydata{1}{Math}        {exp}               {214}{214}{100} & \mydata{1}{}            {split}         {214}{214}{100} \mylinetff
-      \mysucc{1}{global}    {eval}            {214}{214}{100} & \mydata{1}{}            {floor}             {214}{214}{100} & \mysucc{1}{}            {substring}     {214}{214}{100} \mylinetff
-      \mydata{1}{}          {new Date}        {214}{214}{100} & \mydata{1}{}            {max}               {214}{214}{100} & \mydata{1}{}            {toLowerCase}   {214}{214}{100} \mylinefff
-      \mydata{1}{Date}      {parse}           {214}{214}{100} & \mydata{1}{}            {min}               {214}{214}{100} & \mydata{1}{}            {toUpperCase}   {214}{214}{100} \mylinef
-      \mydata{1}{}          {now}             {214}{214}{100}
-    \end{array}
-  \]
-  \vspace*{-1em}
-\end{table*}
 
@@
 the middle solid line denotes the average improvement.
-For \inred{xx} original tests that are analyzable by both analyzers,
+For 198 original tests that are analyzable by both analyzers,
 Figure~\ref{fig:precision}(a) shows that dynamic shortcuts
-successfully reduced the number of covered branches at least
-\inred{1.00}\textsc{x}, at most \inred{0.54}\textsc{x}, and \inred{0.92}x on average.
-For \inred{xx} abstracted tests that are analyzable by both analyzers,
-Figure~\ref{fig:precision}(b) shows that dynamic shortcuts
-also successfully cut down the number of covered branches at least
-\inred{0.81}\textsc{x}, at most \inred{0.51}\textsc{x}, and \inred{0.68}\textsc{x} on average.
+reduced the number of covered branches at most 13.13\%. However, it reduced
+the number of branches 0.46\% on average because the most of original tests
+use concrete values without any non-determinism. Unlike original tets, for 143
+abstracted tests that are analyzable by both analyzers,
+Figure~\ref{fig:precision}(b) shows that dynamic shortcuts successfully cut down
+the number of covered branches at most 13.65\% and 1.89\% on average.  In other
+words, the dynamic shortcuts prevent to analyze 1.44 and 5.97 spurious branches
+for original and abstracted tests on average.
 

### 2020-11-21 paper/pldi21/abstract.tex
Revising inreds.

@@
 dynamic analyzer, respectively.  We evaluated $\tool$ using
-\inred{77} official tests of Lodash 4 library.
-Our experiment shows that $\tool$ is \inred{X.X}x faster than the
-baseline static analyzer on average, and it improves \inred{XX.XX}\%
-of the analysis precision on average by using sealed symbolic
-execution for \inred{XX.X} opaque functions.
+269 official tests of Lodash 4 library.
+Our experiment shows that $\tool$ is \inred{6.30}x faster than the
+baseline static analyzer, and it improves the precision to
+detect 6 more dead branches on average by using sealed symbolic execution for
+\inred{12} opaque functions.
 \end{abstract}

### 2020-11-21 paper/pldi21/conclusion.tex
Revising inreds.

@@
 analyzers SAFE and Jalangi.  Our tool accelerates the speed
-of static analysis \inred{X.X}x for original tests and \inred{X.X}x for
-abstracted tests of Lodash 4 library.  Moreover, it improves \inred{XX.XX}\% of
-the analysis precision by using sealed symbolic execution instead of
-manual modeling for \inred{XX.X} opaque functions on average.
+of static analysis \inred{19.96}x for original tests and \inred{6.30}x for
+abstracted tests of Lodash 4 library.  Moreover, it detect \inred{6} more of
+dead branches by using sealed symbolic execution instead of
+manual modeling for \inred{12} opaque functions on average.

### 2020-11-21 paper/pldi21/intro.tex
Revising inreds.

@@
 Lodash 4 library.  The experiment shows that $\tool$ outperforms
-SAFE \inred{X.X}x on average.  Moreover, by using dynamic shortcuts
-instead of manual modeling for \inred{XX.X} opaque functions,
+SAFE \inred{6.30}x on average.  Moreover, by using dynamic shortcuts
+instead of manual modeling for \inred{12} opaque functions,
 $\tool$ improves the analysis precision to detect 6 more dead branches on

### 2020-11-21 paper/pldi21/eval.tex
Fixed typo in RQ1.
Another dump

@@
 both analyzers.  For them, the dynamic shortcuts outperforms the baseline
-analyzer at most 50.60$\x$ and 20.16$\x$ on average.
+analyzer at most 50.60$\x$ and 6.30$\x$ on average.
 
@@
 
-      \mydata{1}{}          {Array    }  {214 / 214}{214 / 214} & \mydata{1}{}             {String     }  {214 / 214}{214 / 214} & \mydata{1}{}       {Object        }  {214 / 214}{214 / 214} \mylinefff
-      \mydata{1}{}          {new Array}  {214 / 214}{214 / 214} & \mydata{1}{}             {toString   }  {214 / 214}{214 / 214} & \mydata{1}{}       {new Object    }  {214 / 214}{214 / 214} \mylinefff
-      \mydata{1}{}          {isArray  }  {214 / 214}{214 / 214} & \mydata{1}{}             {valueOf    }  {214 / 214}{214 / 214} & \mydata{1}{}       {getPrototypeOf}  {214 / 214}{214 / 214} \mylinetff
-      \mydata{1}{}          {concat   }  { 92 /  92}{139 /  92} & \mysucc{1}{}             {charAt     }  {214 /  92}{214 /  92} & \mydata{1}{}       {create        }  {214 /  92}{214 /  92} \mylinetff
-      \mydata{1}{}          {join     }  {193 / 193}{214 / 193} & \mydata{1}{}             {charCodeAt }  {214 / 193}{214 / 193} & \mydata{1}{Object} {defineProperty}  {214 / 193}{214 / 193} \mylinefff
-      \mydata{1}{}          {pop      }  {214 / 214}{214 / 214} & \mydata{1}{}             {indexOf    }  {214 / 214}{214 / 214} & \mydata{1}{}       {freeze        }  {214 / 214}{214 / 214} \mylinefft
-      \mydata{2}{Array}     {push     }  {214 / 214}{214 / 214} & \mydata{1}{String}       {match      }  {214 / 214}{214 / 214} & \mydata{1}{}       {keys          }  {214 / 214}{214 / 214} \mylineftf
-      \mysucc{1}{}          {reverse  }  {214 / 214}{214 / 214} & \mydata{1}{}             {replace    }  {214 / 214}{214 / 214} & \mydata{1}{}       {toString      }  {214 / 214}{214 / 214} \mylinefff
-      \mydata{1}{}          {shift    }  {214 / 214}{214 / 214} & \mydata{1}{}             {slice      }  {214 / 214}{214 / 214} & \mydata{1}{}       {hasOwnProperty}  {214 / 214}{214 / 214} \mylineftf
-      \mydata{1}{}          {slice    }  {214 / 214}{214 / 214} & \mydata{1}{}             {split      }  {214 / 214}{214 / 214} & \mysucc{1}{}       {parseInt}        {214 / 214}{214 / 214} \mylinefff
-      \mydata{1}{}          {sort     }  {214 / 214}{214 / 214} & \mydata{1}{}             {substring  }  {214 / 214}{214 / 214} & \mydata{1}{Global} {isNaN   }        {214 / 214}{214 / 214} \mylinefff
-      \mydata{1}{}          {splice   }  {214 / 214}{214 / 214} & \mydata{1}{}             {toLowerCase}  {214 / 214}{214 / 214} & \mydata{1}{}       {isFinite}        {214 / 214}{214 / 214} \mylinefff
-      \mydata{1}{}          {unshift  }  {214 / 214}{214 / 214} & \mydata{1}{}             {toUpperCase}  {214 / 214}{214 / 214} & \mydata{1}{}       {RegExp    }      {214 / 214}{214 / 214} \mylinetff
-      \mysucc{1}{}          {indexOf  }  {214 / 214}{214 / 214} & \mydata{2}{Boolean}      {Boolean}      {214 / 214}{214 / 214} & \mysucc{2}{RegExp} {new RegExp}      {214 / 214}{214 / 214} \mylinetff
-      \mydata{1}{}          {every    }  {214 / 214}{214 / 214} & \mydata{1}{}             {valueOf}      {214 / 214}{214 / 214} & \mydata{1}{}       {exec      }      {214 / 214}{214 / 214} \mylinefff
-      \mydata{1}{}          {ceil }      {214 / 214}{214 / 214} & \mydata{2}{Number}       {Number }      {214 / 214}{214 / 214} & \mydata{1}{}       {test      }      {214 / 214}{214 / 214} \mylinefff
-      \mydata{1}{}          {floor}      {214 / 214}{214 / 214} & \mydata{1}{}             {valueOf}      {214 / 214}{214 / 214} & \mydata{1}{}       {Error         }  {214 / 214}{214 / 214} \mylinefff
-      \mydata{1}{Math}      {max  }      {214 / 214}{214 / 214} & \mydata{1}{}             {toString}     {214 / 214}{214 / 214} & \mydata{2}{Error}  {new Error     }  {214 / 214}{214 / 214} \mylinefff
-      \mydata{1}{}          {min  }      {214 / 214}{214 / 214} & \mydata{1}{Function}     {apply   }     {214 / 214}{214 / 214} & \mydata{1}{}       {new RangeError}  {214 / 214}{214 / 214} \mylinefff
-      \mydata{1}{}          {pow  }      {214 / 214}{214 / 214} & \mydata{1}{}             {call    }     {214 / 214}{214 / 214} & \mydata{1}{}       {new TypeError }  {214 / 214}{214 / 214}
+      \mysutf{1}{}          {Array    }  {203 / 203}{ 90 / 116} & \mysutf{1}{}             {String     }  { 20 /  20}{  9 /  10} & \mysutf{1}{}       {Object        }  {263 / 263}{151 / 167} \mylinefff
+      \mysutf{1}{}          {new Array}  {  0 /   0}{  0 /  10} & \mysutf{1}{}             {toString   }  {  0 /   0}{  0 /  33} & \mysutf{1}{}       {new Object    }  {  0 /   0}{  0 /   3} \mylinefff
+      \mysutf{1}{}          {isArray  }  {263 / 263}{144 / 167} & \mysutf{1}{}             {valueOf    }  {  0 /   0}{  0 /  12} & \mysutf{1}{}       {getPrototypeOf}  { 56 /  56}{ 24 /  29} \mylinefff
+      \mysutf{1}{}          {concat   }  {263 / 263}{163 / 167} & \mysutt{1}{}             {charAt     }  {  7 /   7}{  5 /   5} & \mysutf{1}{}       {create        }  {263 / 263}{164 / 167} \mylinefff
+      \mysutf{1}{}          {join     }  {263 / 263}{166 / 167} & \mysutf{1}{}             {charCodeAt }  { 15 /  15}{  3 /   4} & \mysutf{1}{Object} {defineProperty}  {263 / 263}{160 / 167} \mylinefff
+      \mysutf{1}{}          {pop      }  { 25 /  25}{  9 /  13} & \mysutt{1}{}             {indexOf    }  {  2 /   2}{  1 /   1} & \mysbtt{1}{}       {freeze        }  {  1 /   1}{  1 /   1} \mylinefff
+      \mysutf{2}{Array}     {push     }  {263 / 263}{150 / 167} & \mysutf{1}{String}       {match      }  { 25 /  25}{ 11 /  13} & \mysutf{1}{}       {keys          }  {263 / 263}{161 / 167} \mylinefff
+      \mysutt{1}{}          {reverse  }  { 10 /  10}{  3 /   3} & \mysutf{1}{}             {replace    }  { 55 /  55}{ 19 /  26} & \mysutf{1}{}       {toString      }  {263 / 263}{129 / 167} \mylinefff
+      \mysutf{1}{}          {shift    }  {  2 /   2}{  0 /   1} & \mysutf{1}{}             {slice      }  {263 / 263}{165 / 167} & \mysutf{1}{}       {hasOwnProperty}  {263 / 263}{161 / 167} \mylinefft
+      \mysutf{1}{}          {slice    }  {263 / 263}{164 / 167} & \mysutf{1}{}             {split      }  {  5 /   5}{  0 /   1} & \mysutf{1}{}       {parseInt}        {  1 /   1}{  0 /   1} \mylinefff
+      \mysutf{1}{}          {sort     }  { 69 /  69}{ 26 /  28} & \mysutf{1}{}             {substring  }  {214 / 214}{ 91 / 121} & \mysutf{1}{Global} {isNaN   }        { 15 /  15}{  9 /  25} \mylinefff
+      \mysutf{1}{}          {splice   }  { 25 /  25}{  6 /  11} & \mysutf{1}{}             {toLowerCase}  {214 / 214}{ 90 / 121} & \mysbtt{1}{}       {isFinite}        {  3 /   3}{  1 /   1} \mylinefft
+      \mysutt{1}{}          {unshift  }  {  2 /   2}{  1 /   1} & \mysutf{1}{}             {toUpperCase}  { 10 /  10}{  4 /   6} & \mysbtt{1}{}       {RegExp    }      {263 / 263}{167 / 167} \mylineftf
+      \mysutf{1}{}          {indexOf  }  { 94 /  94}{ 22 /  47} & \mysutt{2}{Boolean}      {Boolean}      {  3 /   3}{  2 /   2} & \mysutf{2}{RegExp} {new RegExp}      {  0 /   0}{  0 /   1} \mylinefff
+      \mysutf{1}{}          {every    }  { 92 /  92}{ 23 /  32} & \mysutf{1}{}             {valueOf}      {  0 /   0}{  0 /   6} & \mysbtt{1}{}       {exec      }      {263 / 263}{167 / 167} \mylinettf
+      \mysutt{1}{}          {ceil }      { 36 /  36}{  8 /   8} & \mysutf{2}{Number}       {Number }      {  2 /   2}{  1 /   2} & \mysutf{1}{}       {test      }      {263 / 263}{158 / 167} \mylinefft
+      \mysuff{1}{}          {floor}      { 16 /  17}{  4 /   5} & \mysutf{1}{}             {valueOf}      {  0 /   0}{  0 /  16} & \mysutf{1}{}       {Error         }  {  1 /   1}{  0 /   1} \mylineftf
+      \mysutf{1}{Math}      {max  }      {263 / 263}{134 / 167} & \mysutt{1}{}             {toString}     {263 / 263}{167 / 167} & \mysutf{2}{Error}  {new Error     }  {  0 /   0}{  0 /   8} \mylinefff
+      \mysutf{1}{}          {min  }      { 64 /  64}{ 15 /  48} & \mysutf{1}{Function}     {apply   }     {263 / 263}{124 / 167} & \mysutf{1}{}       {new RangeError}  {  0 /   0}{  0 /   3} \mylinefff
+      \mysutt{1}{}          {pow  }      { 11 /  11}{  5 /   5} & \mysuff{1}{}             {call    }     {262 / 263}{ 50 / 167} & \mysutf{1}{}       {new TypeError }  {  0 /   0}{  0 /   9}
     \end{array}

### 2020-11-21 paper/pldi21/conclusion.tex
Fixed typos.

@@
 of static analysis \inred{19.96}x for original tests and \inred{6.30}x for
-abstracted tests of Lodash 4 library.  Moreover, it detect \inred{6} more of
+abstracted tests of Lodash 4 library.  Moreover, it detects \inred{6} more
 dead branches by using sealed symbolic execution instead of

### 2020-11-21 paper/pldi21/eval.tex
Another dump

@@
 
-\todo
 To experimentally evaluate the conjecture, we investigated the relationship between
@@
 \inred{x.xx}\% of the total analysis time.  However, for 143
-abstracted tests, the communication cost was \inred{xx.xx}\% of the
+abstracted tests, the communication cost was 82.49\% of the
 total analysis time.  Figure~\ref{fig:abs-analysis-ratio} presents the
 analysis time ratio for 143 abstracted tests.
-The $x$-axis represents the time ratio normalized by the total analysis time with dynamic shortcuts
-and the $y$-axis denotes the number of dynamic shortcuts and the number of corresponding tests.
-For all 143 tests, the communication cost (DS-Comm.) is larger than
-both the static analysis time (DS-Static) and the dynamic analysis
-time (DS-Dynamic).  When dynamic shortcuts are performed less than 10 times,
+The $x$-axis represents the time ratio normalized by the total analysis time of
+the baseline analysis (no-DS) and the $y$-axis denotes the number of dynamic
+shortcuts and the number of corresponding tests.
+For all 143 tests, the communication cost (Comm. Cost) is larger than
+both the static analysis time (Static) and the dynamic analysis
+time (Dynamic).  When dynamic shortcuts are performed less than 10 times,
 the communication cost is modest compared with the baseline static
-analysis time (no-DS).  However, the more dynamic shortcuts are performed,
+analysis time.  However, the more dynamic shortcuts are performed,
 the less the performance benefits by using sealed symbolic execution.
 Specifically, when dynamic shortcuts are performed more than
-\inred{30} times, DS-Comm. is even larger than no-DS.
+20 times, DS-Comm. is even larger than no-DS.
 Based on this evaluation result, we believe that we can leverage

### 2020-11-21 paper/pldi21/eval-opaque.tex
Split

--- 2020-11-21 paper/pldi21/eval.tex
@@
-\section{Evaluation}\label{sec:eval}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{img/conc-analysis-time}
-  \vspace*{-1.5em}
-  \caption{Analysis time for Lodash 4 \textit{original} tests without (no-DS)
-  and with (DS) dynamic shortcuts within 5 minutes}
-  \label{fig:conc-analysis-time}
-  \vspace*{-1.5em}
-\end{figure}
-
-We evaluated our tool based on the following three research questions:
-\begin{itemize}
-\item \textbf{RQ1) Analysis Speed-up:} How much analysis time is reduced by
-using dynamic shortcuts during static analysis?
-\item \textbf{RQ2) Precision Improvement:} How much analysis precision is
-improved by using dynamic shortcuts instead of manual modeling?
-\item \textbf{RQ3) Opaque Function Coverage:} How many opaque functions are
-covered by dynamic shortcuts without using manual modeling?
-\end{itemize}
-We selected the official 306 tests of Lodash 4
-(v.4.17.20)\footnote{https://github.com/lodash/lodash/blob/4.17.20/test/test.js}
-used in the motivating examples in Section~\ref{sec:motivation} as our evaluation target.
-The most recent papers about JavaScript static analysis techniques~\cite{value-refinement,
-value-partitioning} also used the tests to evaluate their techniques.
-Among them, we filtered out 37 tests that use JavaScript language
-features SAFE does not support such as dynamic code generation using
-\jscode{Function}, getters and setters, and browser-specific features like $\jscode{__proto__}$.
-Thus, we used 269 out of 306 tests for the evaluation of $\tool$.
-We performed our experiments on a Ubuntu machine
-equipped with 4.2GHz Quad-Core Intel Core i7 and 64GB of RAM.
-
-\subsection{Analysis Speed-up}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=\linewidth]{img/abs-analysis-time}
-  \vspace*{-1.5em}
-  \caption{Analysis time for Lodash 4 \textit{abstracted} tests without (no-DS)
-  and with (DS) dynamic shortcuts within 5 minutes}
-  \label{fig:abs-analysis-time}
-  \vspace*{-1.5em}
-\end{figure}
-
-To evaluate the effectiveness of using dynamic shortcuts, we performed static
-analysis of 269 Lodash 4 tests with and without dynamic shortcuts.
-Figure~\ref{fig:conc-analysis-time} depicts cumulative distribution charts for
-their analysis time and a box plot in a logarithmic scale for speed up after
-applying dynamic shortcuts.  In the upper chart, the $x$-axis is time and the
-$y$-axis shows the number of tests until the time.  While the baseline analysis
-(no-DS) finished analysis of 200 out of 269 tests within 5 minutes, our tool
-(DS) finished analysis of 263 tests using dynamic shortcuts.  For finished
-tests, the average analysis time is 49.57 seconds for no-DS and 2.78 seconds for
-DS.  Since only few tests analyzed in 2 to 5 minutes (8 tests for no-DS
-and no tests for DS), we only show the results until 2 minutes on the
-cumulative distribution charts to show the difference between their results more
-clearly.  Among 200 tests analyzed by no-DS, two tests are timeout in DS thus
-198 tests are analyzable by both analyzers. For them, we depicts the box plot for
-analysis speed up by applying dynamic shortcuts.  It shows that tsing dynamic
-shortcuts outperforms the baseline analyzer at most 54.98$\x$ and 19.96$\x$ on
-average.  Only for one test using $\jscode{_.sample}$, a Lodash 4 library
-function that randomly samples a value from a given array, DS showed
-0.90$\x$ speed of no-DS due to frequent use of dynamic shortcuts, that is 24
-times.
-
-Note that since most Lodash 4 tests use concrete values instead of
-non-deterministic user inputs, they can be analyzed by a few number of dynamic shortcuts.
-In fact, among 269 tests, 262 tests are analyzed
-by a single dynamic shortcut without using abstract semantics.
-However, in real-world JavaScript programs, arguments of library
-functions may include non-deterministic user inputs.
-To evaluate our approach in a real-world setting,
-we modified Lodash 4 official tests with abstract values to simulate actual use patterns of library functions.
-We mad abstract values by randomly selecting literals and replacing
-one of them with its corresponding abstract value.
-For example, if we select a numeric literal \jscode{42}, we modified it to the abstract numeric value
-$\top_{\code{num}}$, which represents all the numeric values.
-In the remaining section, we evaluated $\tool$ using the \textit{original} tests
-and the \textit{abstracted} tests of Lodash 4.
-
-For abstracted tests as well, dynamic shortcuts successfully accelerated the static analysis.
-Figure~\ref{fig:abs-analysis-time} shows the analysis time of the abstracted tests.
-Only 4 tests for no-DS and 9 tests for DS are finished between 2 to 5 minutes.
-Among 269 abstracted tests, no-DS finished analysis of 158 tests within 5 minutes,
-but DS finished analysis of 168 tests.  For finished tests, the average analysis
-time is 44.88 seconds for no-DS and 42.28 seconds for DS. Among 158 tests analyzed by no-DS, DS
-fails to analysis 15 tests in the time limit thus 143 tests are analyzable by
-both analyzers.  For them, the dynamic shortcuts outperforms the baseline
-analyzer at most 50.60$\x$ and 6.30$\x$ on average.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=\linewidth]{img/abs-analysis-ratio}
-  \vspace*{-1.5em}
-  \caption{Analysis time ratio for 143 \textit{abstracted} tests}
-  \label{fig:abs-analysis-ratio}
-  \vspace*{-1.5em}
-\end{figure}
-
-\begin{table*}[t]
-  \centering
-  \caption{The number of \textit{abstracted} tests using dynamic shortcut
-  instead of manual modeling for each JavaScript built-in library}
-  \label{table:func-replace}
-  \vspace*{-1em}
-  \scriptsize
-  \[
-    \begin{array}{c|l|c|c?c|l|c|c?c|l|c|c}
-
-      \myhead{Object}       {Function}        {\# Replaced}
-
-      \mysutf{1}{}          {Array    }  {203 / 203}{ 90 / 116} & \mysutf{1}{}             {String     }  { 20 /  20}{  9 /  10} & \mysutf{1}{}       {Object        }  {263 / 263}{151 / 167} \mylinefff
-      \mysutf{1}{}          {new Array}  {  0 /   0}{  0 /  10} & \mysutf{1}{}             {toString   }  {  0 /   0}{  0 /  33} & \mysutf{1}{}       {new Object    }  {  0 /   0}{  0 /   3} \mylinefff
-      \mysutf{1}{}          {isArray  }  {263 / 263}{144 / 167} & \mysutf{1}{}             {valueOf    }  {  0 /   0}{  0 /  12} & \mysutf{1}{}       {getPrototypeOf}  { 56 /  56}{ 24 /  29} \mylinefff
-      \mysutf{1}{}          {concat   }  {263 / 263}{163 / 167} & \mysutt{1}{}             {charAt     }  {  7 /   7}{  5 /   5} & \mysutf{1}{}       {create        }  {263 / 263}{164 / 167} \mylinefff
-      \mysutf{1}{}          {join     }  {263 / 263}{166 / 167} & \mysutf{1}{}             {charCodeAt }  { 15 /  15}{  3 /   4} & \mysutf{1}{Object} {defineProperty}  {263 / 263}{160 / 167} \mylinefff
-      \mysutf{1}{}          {pop      }  { 25 /  25}{  9 /  13} & \mysutt{1}{}             {indexOf    }  {  2 /   2}{  1 /   1} & \mysbtt{1}{}       {freeze        }  {  1 /   1}{  1 /   1} \mylinefff
-      \mysutf{2}{Array}     {push     }  {263 / 263}{150 / 167} & \mysutf{1}{String}       {match      }  { 25 /  25}{ 11 /  13} & \mysutf{1}{}       {keys          }  {263 / 263}{161 / 167} \mylinefff
-      \mysutt{1}{}          {reverse  }  { 10 /  10}{  3 /   3} & \mysutf{1}{}             {replace    }  { 55 /  55}{ 19 /  26} & \mysutf{1}{}       {toString      }  {263 / 263}{129 / 167} \mylinefff
-      \mysutf{1}{}          {shift    }  {  2 /   2}{  0 /   1} & \mysutf{1}{}             {slice      }  {263 / 263}{165 / 167} & \mysutf{1}{}       {hasOwnProperty}  {263 / 263}{161 / 167} \mylinefft
-      \mysutf{1}{}          {slice    }  {263 / 263}{164 / 167} & \mysutf{1}{}             {split      }  {  5 /   5}{  0 /   1} & \mysutf{1}{}       {parseInt}        {  1 /   1}{  0 /   1} \mylinefff
-      \mysutf{1}{}          {sort     }  { 69 /  69}{ 26 /  28} & \mysutf{1}{}             {substring  }  {214 / 214}{ 91 / 121} & \mysutf{1}{Global} {isNaN   }        { 15 /  15}{  9 /  25} \mylinefff
-      \mysutf{1}{}          {splice   }  { 25 /  25}{  6 /  11} & \mysutf{1}{}             {toLowerCase}  {214 / 214}{ 90 / 121} & \mysbtt{1}{}       {isFinite}        {  3 /   3}{  1 /   1} \mylinefft
-      \mysutt{1}{}          {unshift  }  {  2 /   2}{  1 /   1} & \mysutf{1}{}             {toUpperCase}  { 10 /  10}{  4 /   6} & \mysbtt{1}{}       {RegExp    }      {263 / 263}{167 / 167} \mylineftf
-      \mysutf{1}{}          {indexOf  }  { 94 /  94}{ 22 /  47} & \mysutt{2}{Boolean}      {Boolean}      {  3 /   3}{  2 /   2} & \mysutf{2}{RegExp} {new RegExp}      {  0 /   0}{  0 /   1} \mylinefff
-      \mysutf{1}{}          {every    }  { 92 /  92}{ 23 /  32} & \mysutf{1}{}             {valueOf}      {  0 /   0}{  0 /   6} & \mysbtt{1}{}       {exec      }      {263 / 263}{167 / 167} \mylinettf
-      \mysutt{1}{}          {ceil }      { 36 /  36}{  8 /   8} & \mysutf{2}{Number}       {Number }      {  2 /   2}{  1 /   2} & \mysutf{1}{}       {test      }      {263 / 263}{158 / 167} \mylinefft
-      \mysuff{1}{}          {floor}      { 16 /  17}{  4 /   5} & \mysutf{1}{}             {valueOf}      {  0 /   0}{  0 /  16} & \mysutf{1}{}       {Error         }  {  1 /   1}{  0 /   1} \mylineftf
-      \mysutf{1}{Math}      {max  }      {263 / 263}{134 / 167} & \mysutt{1}{}             {toString}     {263 / 263}{167 / 167} & \mysutf{2}{Error}  {new Error     }  {  0 /   0}{  0 /   8} \mylinefff
-      \mysutf{1}{}          {min  }      { 64 /  64}{ 15 /  48} & \mysutf{1}{Function}     {apply   }     {263 / 263}{124 / 167} & \mysutf{1}{}       {new RangeError}  {  0 /   0}{  0 /   3} \mylinefff
-      \mysutt{1}{}          {pow  }      { 11 /  11}{  5 /   5} & \mysuff{1}{}             {call    }     {262 / 263}{ 50 / 167} & \mysutf{1}{}       {new TypeError }  {  0 /   0}{  0 /   9}
-    \end{array}
-  \]
-  \vspace*{-1em}
-\end{table*}
-
-Unlike for the original tests, analysis of 143
-abstracted tests that are analyzable by both analyzers invoked
-16.05 dynamic shortcuts.  Because taking a dynamic shortcut
-requires converting between abstract states and sealed symbolic values
-and exchanging them between the static analyzer and the dynamic analyzer,
-using dynamic shortcuts multiple times may incur more performance
-overhead than performance benefits by using sealed symbolic execution.
-One may conjecture that the communication cost between the static
-analyzer and the dynamic analyzer may be proportional to the number of
-dynamic shortcuts.
-
-To experimentally evaluate the conjecture, we investigated the relationship between
-the communication cost between analyzers and the number of dynamic shortcuts.
-For 198 original tests, the communication cost was only
-\inred{x.xx}\% of the total analysis time.  However, for 143
-abstracted tests, the communication cost was 82.49\% of the
-total analysis time.  Figure~\ref{fig:abs-analysis-ratio} presents the
-analysis time ratio for 143 abstracted tests.
-The $x$-axis represents the time ratio normalized by the total analysis time of
-the baseline analysis (no-DS) and the $y$-axis denotes the number of dynamic
-shortcuts and the number of corresponding tests.
-For all 143 tests, the communication cost (Comm. Cost) is larger than
-both the static analysis time (Static) and the dynamic analysis
-time (Dynamic).  When dynamic shortcuts are performed less than 10 times,
-the communication cost is modest compared with the baseline static
-analysis time.  However, the more dynamic shortcuts are performed,
-the less the performance benefits by using sealed symbolic execution.
-Specifically, when dynamic shortcuts are performed more than
-20 times, DS-Comm. is even larger than no-DS.
-Based on this evaluation result, we believe that we can leverage
-dynamic shortcuts by optimizing the communication between static and dynamic analyzers.
-
-\begin{figure}[t]
-  \centering
-  \begin{subfigure}[t]{0.48\textwidth}
-    \includegraphics[width=\linewidth]{img/conc-precision}
-    \vspace*{-1.5em}
-    \caption{Reachable branches for 198 \textit{original} tests}
-    \label{fig:precision-fail}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.48\textwidth}
-    \includegraphics[width=\linewidth]{img/abs-precision}
-    \vspace*{-1.5em}
-    \caption{Reachable branches for 143 \textit{abstracted} tests}
-    \label{fig:precision-branch}
-  \end{subfigure}
-  \vspace*{-1em}
-  \caption{Branch coverage of analysis without (no-DS) and with (DS) dynamic shortcuts}
-  \label{fig:precision}
-  \vspace*{-1.5em}
-\end{figure}
-
-\subsection{Precision Improvement}
-
-To evaluate the analysis precision improvement of dynamic shortcuts,
-we measured the number of branches covered by no-DS and DS.
-Because both no-DS and DS are designed to be sound,
-high (low) branch coverage denotes low (high) analysis precision.
-
-Figure~\ref{fig:precision} depicts the comparison of the analysis
-precision between no-DS and DS.  The $x$-axis and the $y$-axis denote
-the number of branches covered by no-DS and DS, respectively;
-each $\times$ mark denotes each test.  The top and bottom dotted lines
-denote the worst and the best precision improvement, respectively, and
-the middle solid line denotes the average improvement.
-For 198 original tests that are analyzable by both analyzers,
-Figure~\ref{fig:precision}(a) shows that dynamic shortcuts
-reduced the number of covered branches at most 13.13\%. However, it reduced
-the number of branches 0.46\% on average because the most of original tests
-use concrete values without any non-determinism. Unlike original tets, for 143
-abstracted tests that are analyzable by both analyzers,
-Figure~\ref{fig:precision}(b) shows that dynamic shortcuts successfully cut down
-the number of covered branches at most 13.65\% and 1.89\% on average.  In other
-words, the dynamic shortcuts prevent to analyze 1.44 and 5.97 spurious branches
-for original and abstracted tests on average.
-
 \subsection{Opaque Function Coverage}

### 2020-11-21 paper/pldi21/eval.tex
Split

@@
 for original and abstracted tests on average.
-
-\subsection{Opaque Function Coverage}
-To evaluate how much manual modeling efforts of opaque functions
-are reduced by dynamic shortcuts, we measured the number of tests where
-opaque functions that are analyzed only by dynamic analysis not by
-static analysis.  Table~\ref{table:func-replace} summarizes the result.
-For \inred{xx} original tests and \inred{xx} abstracted tests, we measured the
-number of tests that use only dynamic shortcuts instead of manual modeling
-for each JavaScript built-in library function.  For each row,
-\textbf{Object} column denotes a built-in object,
-\textbf{Function} a function name, and
-\inred{\textbf{\# Replaced} the number of tests successfully replacing manual
-modeling via dynamic shortcuts with the total number of tests using the target function.
-For example, the fourth row in the left side describes that \jscode{Array.prototype.toString} is used in
-\inred{139} original tests and \inred{xxx} abstracted tests.
- Among them, \inred{44} original tests \inred{xx} abstracted tests are successfully analyzed
-by dynamic shortcuts instead of using the modeling of
-\jscode{Array.prototype.toString}.
-Moreover, several built-in functions are analyzed by only dynamic shortcuts in
-all tests.  Among \inred{49} JavaScript built-in functions, \inred{xx} and
-\inred{xx} functions are analyzed by only dynamic shortcut instead of manual
-modeling for all original and all abstracted tests, respectively.  Each filled cell
-describes fully replaceable cases in Table~\ref{table:func-replace}.
-Therefore, dynamic shortcuts effectively lessen
-the burden of manual modeling for JavaScript built-in functions.
-}

### 2020-11-21 paper/pldi21/eval.tex
Minor fix

@@
 For 198 original tests, the communication cost was only
-\inred{x.xx}\% of the total analysis time.  However, for 143
-abstracted tests, the communication cost was 82.49\% of the
-total analysis time.  Figure~\ref{fig:abs-analysis-ratio} presents the
+3.51\% compared to the analysis time without dynamic shortcuts (no-DS).  However, for 143
+abstracted tests, the communication cost was 82.49\% compared to the analysis
+time of no-DS.  Figure~\ref{fig:abs-analysis-ratio} presents the
 analysis time ratio for 143 abstracted tests.

### 2020-11-21 paper/pldi21/eval-opaque.tex
eval-opaque.tex

@@
 static analysis.  Table~\ref{table:func-replace} summarizes the result.
-For \inred{xx} original tests and \inred{xx} abstracted tests, we measured the
+For 198 original tests and 143 abstracted tests, we measured the
 number of tests that use only dynamic shortcuts instead of manual modeling
 for each JavaScript built-in library function.  For each row,
-\textbf{Object} column denotes a built-in object,
-\textbf{Function} a function name, and
-\inred{\textbf{\# Replaced} the number of tests successfully replacing manual
+\textbf{Object} column denotes a built-in object, \textbf{Function} a function
+name, and \inred{\textbf{\# Replaced} the number of tests successfully replacing manual
 modeling via dynamic shortcuts with the total number of tests using the target function.
-For example, the fourth row in the left side describes that \jscode{Array.prototype.toString} is used in
-\inred{139} original tests and \inred{xxx} abstracted tests.
- Among them, \inred{44} original tests \inred{xx} abstracted tests are successfully analyzed
-by dynamic shortcuts instead of using the modeling of
-\jscode{Array.prototype.toString}.
-Moreover, several built-in functions are analyzed by only dynamic shortcuts in
-all tests.  Among \inred{49} JavaScript built-in functions, \inred{xx} and
-\inred{xx} functions are analyzed by only dynamic shortcut instead of manual
-modeling for all original and all abstracted tests, respectively.  Each filled cell
-describes fully replaceable cases in Table~\ref{table:func-replace}.
-Therefore, dynamic shortcuts effectively lessen
-the burden of manual modeling for JavaScript built-in functions.
-}
+For example, the first row in the left side describes that \jscode{Array} is used in
+203 original tests and 116 abstracted tests.  Among them, 203 original
+tests 90 abstracted tests are successfully analyzed by dynamic shortcuts
+instead of using the modeling of \jscode{Array}.  Each filled cell describes
+fully replaceable cases in Table~\ref{table:func-replace}.  Therefore, dynamic
+shortcuts effectively lessen the burden of manual modeling for JavaScript
+built-in functions.  Again, since all the original Lodash 4 tests except one
+test is finisehd with a single dynamic shortcut, all the built-in fuctions
+except \jscode{Math.floor} and \jscode{Function.prototype.call} are replaceable
+for original tests.  For abstracted tests, 12 functions out of 60 built-in
+functions are analyzed by only dynamic shortcut instead of manual modeling.

### 2020-11-21 paper/pldi21/eval-opaque.tex
Fixed error

@@
 \textbf{Object} column denotes a built-in object, \textbf{Function} a function
-name, and \inred{\textbf{\# Replaced} the number of tests successfully replacing manual
+name, and \textbf{\# Replaced} the number of tests successfully replacing manual
 modeling via dynamic shortcuts with the total number of tests using the target function.

### 2020-11-21 paper/pldi21/conclusion.tex
Revising Sec. 6

@@
 We presented a novel technique for JavaScript static analysis using \textit{dynamic shortcuts}.
-It can significantly accelerate the JavaScript static
+It can significantly accelerate static
 analysis by freely leveraging high performance of dynamic analysis for
-concretely executable program parts.  To maximally use dynamic analysis during static analysis,
+concretely executable program parts.  To maximize such benefits,
 we proposed \textit{sealed symbolic execution}, which performs

### 2020-11-21 paper/pldi21/eval.tex
Revising Sec. 6

@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{img/conc-analysis-time}
-  \vspace*{-1.5em}
-  \caption{Analysis time for Lodash 4 \textit{original} tests without (no-DS)
-  and with (DS) dynamic shortcuts within 5 minutes}
-  \label{fig:conc-analysis-time}
-  \vspace*{-1.5em}
-\end{figure}
-
-We evaluated our tool based on the following three research questions:
+We evaluate $\tool$ using the following research questions:
 \begin{itemize}
 \item \textbf{RQ1) Analysis Speed-up:} How much analysis time is reduced by
-using dynamic shortcuts during static analysis?
+using dynamic shortcuts?
 \item \textbf{RQ2) Precision Improvement:} How much analysis precision is
-improved by using dynamic shortcuts instead of manual modeling?
+improved by using dynamic shortcuts?
+% instead of manual modeling?
 \item \textbf{RQ3) Opaque Function Coverage:} How many opaque functions are
-covered by dynamic shortcuts without using manual modeling?
+covered only by dynamic shortcuts?
+% without using manual modeling?
 \end{itemize}
@@
 (v.4.17.20)\footnote{https://github.com/lodash/lodash/blob/4.17.20/test/test.js}
-used in the motivating examples in Section~\ref{sec:motivation} as our evaluation target.
-The most recent papers about JavaScript static analysis techniques~\cite{value-refinement,
+used in the examples in Section~\ref{sec:motivation} as our evaluation target.
+Recent work~\cite{value-refinement,
 value-partitioning} also used the tests to evaluate their techniques.
@@
 \subsection{Analysis Speed-up}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\linewidth]{img/conc-analysis-time}
+  \vspace*{-1.5em}
+  \caption{Analysis time for Lodash 4 \textit{original} tests without (no-DS)
+  and with (DS) dynamic shortcuts within 5 minutes}
+  \label{fig:conc-analysis-time}
+  \vspace*{-1.5em}
+\end{figure}
 
@@
 applying dynamic shortcuts.  In the upper chart, the $x$-axis is time and the
-$y$-axis shows the number of tests until the time.  While the baseline analysis
+$y$-axis shows the number of tests within the time.  While the baseline analysis
 (no-DS) finished analysis of 200 out of 269 tests within 5 minutes, our tool
@@
 DS.  Since only few tests analyzed in 2 to 5 minutes (8 tests for no-DS
-and no tests for DS), we only show the results until 2 minutes on the
+and no tests for DS), we only show the results within 2 minutes on the
 cumulative distribution charts to show the difference between their results more
-clearly.  Among 200 tests analyzed by no-DS, two tests are timeout in DS thus
-198 tests are analyzable by both analyzers. For them, we depicts the box plot for
-analysis speed up by applying dynamic shortcuts.  It shows that tsing dynamic
-shortcuts outperforms the baseline analyzer at most 54.98$\x$ and 19.96$\x$ on
-average.  Only for one test using $\jscode{_.sample}$, a Lodash 4 library
-function that randomly samples a value from a given array, DS showed
-0.90$\x$ speed of no-DS due to frequent use of dynamic shortcuts, that is 24
-times.
+clearly.  Among 200 tests analyzed by no-DS, two tests are timeout in DS, thus
+198 tests are analyzable by both analyzers. For them, we depict the box plot for
+analysis speed up by dynamic shortcuts.  It shows that DS
+outperforms no-DS up to 54.98$\x$ and 19.96$\x$ on
+average.  Only for one test using $\jscode{_.sample}$, which
+randomly samples a value from a given array, DS showed
+0.90$\x$ speed of no-DS due to 24 times uses of dynamic shortcuts.
 
-Note that since most Lodash 4 tests use concrete values instead of
-non-deterministic user inputs, they can be analyzed by a few number of dynamic shortcuts.
+Note that since most tests use concrete values instead of
+non-deterministic inputs, they can be analyzed by a few number of dynamic shortcuts.
 In fact, among 269 tests, 262 tests are analyzed
@@
 However, in real-world JavaScript programs, arguments of library
-functions may include non-deterministic user inputs.
-To evaluate our approach in a real-world setting,
-we modified Lodash 4 official tests with abstract values to simulate actual use patterns of library functions.
-We mad abstract values by randomly selecting literals and replacing
+functions may include non-deterministic inputs.
+To evaluate $\tool$ in a real-world setting,
+we modified the tests to use abstract values.
+We made abstract values by randomly selecting literals and replacing
 one of them with its corresponding abstract value.
@@
 In the remaining section, we evaluated $\tool$ using the \textit{original} tests
-and the \textit{abstracted} tests of Lodash 4.
+and the \textit{abstracted} tests.
 
-For abstracted tests as well, dynamic shortcuts successfully accelerated the static analysis.
+For abstracted tests as well, DS outperformed no-DS.
 Figure~\ref{fig:abs-analysis-time} shows the analysis time of the abstracted tests.
-Only 4 tests for no-DS and 9 tests for DS are finished between 2 to 5 minutes.
+Only four tests for no-DS and nine tests for DS are finished between 2 to 5 minutes.
 Among 269 abstracted tests, no-DS finished analysis of 158 tests within 5 minutes,

### 2020-11-21 paper/pldi21/implementation.tex
Revising Sec. 6

@@
   return new Proxy(function() {}, {
-    getPrototypeOf: detect,
-    ...
+    getPrototypeOf: detect,  ...
     construct     : detect
-  });
-}
+  }); }
 var x = generateSymbol();
@@
 \jscode{y} successfully points to the same symbol stored in \jscode{x}, but the
-program invokes the function \jscode{detect} on line 11 because \jscode{x + 1} requires
+program invokes the function \jscode{detect} on line 9 because \jscode{x + 1} requires
 the actual value of the symbol.  In addition, we instrument unary and binary
@@
 For seamless interaction between static analysis and sealed symbolic execution,
-synchronization of control points in both worlds is a prerequisite.
+synchronization of control points in both worlds is necessary.
 The SAFE static analyzer parses a JavaScript program to an Abstract
@@
 builds a Control Flow Graph (CFG).  It produces annotations for
-control points on the CFG including functions, call sites, and object allocation sites.
+control points on CFGs including functions, call sites, and object allocation sites.
 On the contrary, the Jalangi dynamic analyzer instruments a JavaScript program 
@@
 we simply perform sealed symbolic execution with a pre-determined time limit.  When it runs
-over the time limit, we treat it as a failure to pass $\checker$; otherwise, we utilize
-the result of the sealed symbolic execution.  In our experiments, we set the time limit as
-5 seconds for each sealed symbolic execution.
+over the time limit, we treat it as a failure to pass $\checker$; otherwise, we use
+the result of sealed symbolic execution.  Our experiments used 5 seconds 
+as the time limit for each sealed symbolic execution.
 

### 2020-11-21 paper/pldi21/javascript.tex
Revising Sec. 6

@@
 \absdom) \rightarrow (\absimapset \times \symbstset)$
-keeps it as it is; otherwise, $\asconverter$ replaces the abstract
+keeps it; otherwise, $\asconverter$ replaces the abstract
 value with its unique identifier and maintains the mapping from the

### 2020-11-21 paper/pldi21/related.tex
Revising Sec. 6

@@
 \section{Related Work}\label{sec:related}
-Researchers have introduced various analysis technique to utilize dynamic
+Researchers have introduced various technique to utilize dynamic
 analysis for static analysis in three ways: combined analysis,

### 2020-11-21 paper/pldi21/eval.tex
Revising Sec. 6

@@
 time is 44.88 seconds for no-DS and 42.28 seconds for DS. Among 158 tests analyzed by no-DS, DS
-fails to analysis 15 tests in the time limit thus 143 tests are analyzable by
-both analyzers.  For them, the dynamic shortcuts outperforms the baseline
-analyzer at most 50.60$\x$ and 6.30$\x$ on average.
+timed-out for 15 tests.  For 143 tests analyzable by both analyzers,
+DS outperformed no-DS up to 50.60$\x$ and 6.30$\x$ on average.
 
@@
 
-Unlike for the original tests, analysis of 143
-abstracted tests that are analyzable by both analyzers invoked
+Unlike for the original tests, analysis of 143 abstracted tests invoked
 16.05 dynamic shortcuts.  Because taking a dynamic shortcut
-requires converting between abstract states and sealed symbolic values
+requires conversion between abstract states and sealed symbolic values
 and exchanging them between the static analyzer and the dynamic analyzer,

### 2020-11-21 paper/pldi21/eval.tex
Cetering Table 1.
Till Sec. 6.2

@@
 \begin{table*}[t]
-  \centering
-  \caption{The number of \textit{abstracted} tests using dynamic shortcut
+  \caption{Number of \textit{abstracted} tests using dynamic shortcuts
   instead of manual modeling for each JavaScript built-in library}
@@
   \vspace*{-1em}
+  \centering
   \scriptsize
   \[
+\quad
     \begin{array}{c|l|c|c?c|l|c|c?c|l|c|c}
@@
 requires conversion between abstract states and sealed symbolic values
-and exchanging them between the static analyzer and the dynamic analyzer,
+and their exchanges between the static analyzer and the dynamic analyzer,
 using dynamic shortcuts multiple times may incur more performance
 overhead than performance benefits by using sealed symbolic execution.
-One may conjecture that the communication cost between the static
+One conjecture is that the communication cost between the static
 analyzer and the dynamic analyzer may be proportional to the number of
@@
 For 198 original tests, the communication cost was only
-3.51\% compared to the analysis time without dynamic shortcuts (no-DS).  However, for 143
+3.51\% compared to the analysis time of no-DS.  However, for 143
 abstracted tests, the communication cost was 82.49\% compared to the analysis
@@
 The $x$-axis represents the time ratio normalized by the total analysis time of
-the baseline analysis (no-DS) and the $y$-axis denotes the number of dynamic
+no-DS and the $y$-axis denotes the number of dynamic
 shortcuts and the number of corresponding tests.
@@
 analysis time.  However, the more dynamic shortcuts are performed,
-the less the performance benefits by using sealed symbolic execution.
+the less the performance benefits by using dynamic shortcuts.
 Specifically, when dynamic shortcuts are performed more than
-20 times, DS-Comm. is even larger than no-DS.
+20 times, Comm. Cost is even larger than no-DS.
 Based on this evaluation result, we believe that we can leverage
-dynamic shortcuts by optimizing the communication between static and dynamic analyzers.
+dynamic shortcuts by optimizing the communication cost between
+the static analyzer and the dynamic analyzer.
 
@@
 we measured the number of branches covered by no-DS and DS.
-Because both no-DS and DS are designed to be sound,
+Because both no-DS and DS are sound,
 high (low) branch coverage denotes low (high) analysis precision.
@@
 Figure~\ref{fig:precision}(a) shows that dynamic shortcuts
-reduced the number of covered branches at most 13.13\%. However, it reduced
-the number of branches 0.46\% on average because the most of original tests
-use concrete values without any non-determinism. Unlike original tets, for 143
+reduced the number of covered branches up to 13.13\%. However, it reduced
+the number of branches 0.46\% on average because most original tests
+do not use non-determinism. Unlike original tests, for 143
 abstracted tests that are analyzable by both analyzers,
 Figure~\ref{fig:precision}(b) shows that dynamic shortcuts successfully cut down
-the number of covered branches at most 13.65\% and 1.89\% on average.  In other
-words, the dynamic shortcuts prevent to analyze 1.44 and 5.97 spurious branches
-for original and abstracted tests on average.
+the number of covered branches up to 13.65\% and 1.89\% on average.
+Thus, on average, dynamic shortcuts removed analysis of 1.44 and 5.97 spurious branches
+for original and abstracted tests, respectively.

### 2020-11-21 paper/pldi21/abstract.tex
Removed inred

@@
 269 official tests of Lodash 4 library.
-Our experiment shows that $\tool$ is \inred{6.30}x faster than the
+Our experiment shows that $\tool$ is 6.30$\x$ faster than the
 baseline static analyzer, and it improves the precision to
 detect 6 more dead branches on average by using sealed symbolic execution for
-\inred{12} opaque functions.
+12 opaque functions.
 \end{abstract}

### 2020-11-21 paper/pldi21/conclusion.tex
Removed inred

@@
 analyzers SAFE and Jalangi.  Our tool accelerates the speed
-of static analysis \inred{19.96}x for original tests and \inred{6.30}x for
-abstracted tests of Lodash 4 library.  Moreover, it detects \inred{6} more
+of static analysis 19.96$\x$ for original tests and 6.30$\x$ for
+abstracted tests of Lodash 4 library.  Moreover, it detects 6 more
 dead branches by using sealed symbolic execution instead of
-manual modeling for \inred{12} opaque functions on average.
+manual modeling for 12 opaque functions on average.

### 2020-11-21 paper/pldi21/eval-opaque.tex
No highlighting for Function

@@
 test is finisehd with a single dynamic shortcut, all the built-in fuctions
-except \jscode{Math.floor} and \jscode{Function.prototype.call} are replaceable
+except \jscode{Math.floor} and \njscode{Function.prototype.call} are replaceable
 for original tests.  For abstracted tests, 12 functions out of 60 built-in

### 2020-11-21 paper/pldi21/eval-opaque.tex
Work in progress

--- 2020-11-21 paper/pldi21/eval-opaque.tex
@@
 static analysis.  Table~\ref{table:func-replace} summarizes the result.
-For 198 original tests and 143 abstracted tests, we measured the
+For 263 original tests and 167 abstracted tests, we measured the
 number of tests that use only dynamic shortcuts instead of manual modeling
@@
 \textbf{Object} column denotes a built-in object, \textbf{Function} a function
-name, and \textbf{\# Replaced} the number of tests successfully replacing manual
-modeling via dynamic shortcuts with the total number of tests using the target function.
+name, and \textbf{\#~Replaced} the number of tests successfully replacing manual
+modeling via dynamic shortcuts over the total number of tests using the target function.
 For example, the first row in the left side describes that \jscode{Array} is used in
 203 original tests and 116 abstracted tests.  Among them, 203 original
-tests 90 abstracted tests are successfully analyzed by dynamic shortcuts
-instead of using the modeling of \jscode{Array}.  Each filled cell describes
-fully replaceable cases in Table~\ref{table:func-replace}.  Therefore, dynamic
+tests and 90 abstracted tests are successfully analyzed by using dynamic shortcuts
+instead of manual modeling of \jscode{Array}.  Each filled cell describes
+a fully replaceable case.  Therefore, dynamic
 shortcuts effectively lessen the burden of manual modeling for JavaScript
 built-in functions.  Again, since all the original Lodash 4 tests except one
-test is finisehd with a single dynamic shortcut, all the built-in fuctions
-except \jscode{Math.floor} and \jscode{Function.prototype.call} are replaceable
+is finisehd with a single dynamic shortcut, all the built-in fuctions
+except \jscode{Math.floor} and \njscode{Function.prototype.call} are replaceable
 for original tests.  For abstracted tests, 12 functions out of 60 built-in

### 2020-11-21 paper/pldi21/eval.tex
No highlighting for Function
Work in progress

@@
 features SAFE does not support such as dynamic code generation using
-\jscode{Function}, getters and setters, and browser-specific features like $\jscode{__proto__}$.
+\njscode{Function}, getters and setters, and browser-specific features like $\jscode{__proto__}$.
 Thus, we used 269 out of 306 tests for the evaluation of $\tool$.
@@
 Among 269 abstracted tests, no-DS finished analysis of 158 tests within 5 minutes,
-but DS finished analysis of 168 tests.  For finished tests, the average analysis
+but DS finished analysis of 167 tests.  For finished tests, the average analysis
 time is 44.88 seconds for no-DS and 42.28 seconds for DS. Among 158 tests analyzed by no-DS, DS
@@
 \begin{table*}[t]
-  \caption{Number of \textit{abstracted} tests using dynamic shortcuts
-  instead of manual modeling for each JavaScript built-in library}
+  \caption{Number of original and abstracted tests using dynamic shortcuts
+only for each JavaScript built-in library}
   \label{table:func-replace}
@@
       \mysutf{1}{Math}      {max  }      {263 / 263}{134 / 167} & \mysutt{1}{}             {toString}     {263 / 263}{167 / 167} & \mysutf{2}{Error}  {new Error     }  {  0 /   0}{  0 /   8} \mylinefff
-      \mysutf{1}{}          {min  }      { 64 /  64}{ 15 /  48} & \mysutf{1}{Function}     {apply   }     {263 / 263}{124 / 167} & \mysutf{1}{}       {new RangeError}  {  0 /   0}{  0 /   3} \mylinefff
+      \mysutf{1}{}          {min  }      { 64 /  64}{ 15 /  48} & \mnsutf{1}{Function}     {apply   }     {263 / 263}{124 / 167} & \mysutf{1}{}       {new RangeError}  {  0 /   0}{  0 /   3} \mylinefff
       \mysutt{1}{}          {pow  }      { 11 /  11}{  5 /   5} & \mysuff{1}{}             {call    }     {262 / 263}{ 50 / 167} & \mysutf{1}{}       {new TypeError }  {  0 /   0}{  0 /   9}

### 2020-11-21 paper/pldi21/eval-opaque.tex
Till Sec.6

@@
 To evaluate how much manual modeling efforts of opaque functions
-are reduced by dynamic shortcuts, we measured the number of tests where
-opaque functions that are analyzed only by dynamic analysis not by
+are reduced by dynamic shortcuts, we measured the number of tests for which
+opaque functions are analyzed only by dynamic analysis not by
 static analysis.  Table~\ref{table:func-replace} summarizes the result.
-For 263 original tests and 167 abstracted tests, we measured the
+For 263 original tests and 167 abstracted tests that DS finished analysis, we measured the
 number of tests that use only dynamic shortcuts instead of manual modeling
@@
 modeling via dynamic shortcuts over the total number of tests using the target function.
-For example, the first row in the left side describes that \jscode{Array} is used in
+For example, the first row in the leftmost side describes that \jscode{Array} is used in
 203 original tests and 116 abstracted tests.  Among them, 203 original
@@
 shortcuts effectively lessen the burden of manual modeling for JavaScript
-built-in functions.  Again, since all the original Lodash 4 tests except one
-is finisehd with a single dynamic shortcut, all the built-in fuctions
+built-in functions.  Again, since analysis of all the original Lodash 4 tests except one
+finishes with a single dynamic shortcut, all the built-in fuctions
 except \jscode{Math.floor} and \njscode{Function.prototype.call} are replaceable
-for original tests.  For abstracted tests, 12 functions out of 60 built-in
-functions are analyzed by only dynamic shortcut instead of manual modeling.
+for original tests.  For abstracted tests, 12 out of 60 built-in
+functions are analyzed by only dynamic shortcuts.

### 2020-11-21 paper/pldi21/eval-opaque.tex
Fixed a typo.

@@
 built-in functions.  Again, since analysis of all the original Lodash 4 tests except one
-finishes with a single dynamic shortcut, all the built-in fuctions
+finishes with a single dynamic shortcut, all the built-in functions
 except \jscode{Math.floor} and \njscode{Function.prototype.call} are replaceable

### 2020-11-21 paper/pldi21/javascript.tex
Fixed minor typo

@@
 Moreover, since object properties are string values that can be constructed at run time,
-it is difficult for static analysis to know whether strong udpates are possible or not.
+it is difficult for static analysis to know whether strong updates are possible or not.
 To check the possibility of strong updates during sealed symbolic execution,

### 2020-11-21 paper/pldi21/implementation.tex
Removed inred
New one

@@
 To guarantee the termination of static analysis using dynamic shortcuts, the
-filter $\checker$ should pass a state $\symbst$ only when it terminates in a
-bound time $N$.  Since statically checking the termination property is a difficult task,
-we simply perform sealed symbolic execution with a pre-determined time limit.  When it runs
-over the time limit, we treat it as a failure to pass $\checker$; otherwise, we use
-the result of sealed symbolic execution.  Our experiments used 5 seconds 
-as the time limit for each sealed symbolic execution.
+converter $\asconverter$ should pass an analysis element $(\view, \abselem)$
+only when it terminates in a bound time $N$.  Since statically checking the
+termination property is a difficult task, we simply perform sealed symbolic
+execution with a pre-determined time limit.  When it runs over the time limit,
+we treat it as a failure to convert the analysis element via $\asconverter$;
+otherwise, we use the result of sealed symbolic execution.  Our experiments used
+5 seconds as the time limit for each sealed symbolic execution.
 
@@
 % Since it is difficult to staticaly check its termination, we just performs the
-% sealed symbolic exeuction with a time limit and we use \inred{5} minutes time
+% sealed symbolic exeuction with a time limit and we use 5 minutes time
 % limit for experiments.  Thus, a sealed symbolic execution introduced by a

### 2020-11-21 paper/pldi21/implementation.tex
Minor edits

@@
 symbolic execution on an existing JavaScript engine.  To represent an abstract
-value, we leverage the \jscode{Proxy} object introduced in ECMAScript 6
+value, we use the \jscode{Proxy} object introduced in ECMAScript 6
 (2015, ES6)~\cite{es6}, which allows developers to handle internal behaviors
@@
 converter $\asconverter$ should pass an analysis element $(\view, \abselem)$
-only when it terminates in a bound time $N$.  Since statically checking the
+only when it terminates in a time bound $N$.  Since statically checking the
 termination property is a difficult task, we simply perform sealed symbolic
-execution with a pre-determined time limit.  When it runs over the time limit,
-we treat it as a failure to convert the analysis element via $\asconverter$;
+execution with a pre-determined time limit.  When it times out,
+we treat it as a failure in conversion;
 otherwise, we use the result of sealed symbolic execution.  Our experiments used

### 2020-11-21 paper/pldi21/motivation.tex

@@
 It is the homepage of Zoom, which is a videotelephony software program developed by Zoom
-Video Communications and it is ranked as the 16th popular web site according
+Video Communications and it is ranked as the 14th popular web site according
 to Alexa\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.

### 2020-11-23 paper/pldi21/report/def.tex
Almost complete termination proof

@@
 
-We define a $\atriage$ function using two converters between analysis elements
+We define a $\areform$ function using two converters between analysis elements
 as follows:
-\begin{definition}[$\atriage$]\label{def:atriage}
-  The triage function $\atriage: \aelemset \rightarrow \aelemset$ for analysis
+\begin{definition}[$\areform$]\label{def:areform}
+  The reform function $\areform: \aelemset \rightarrow \aelemset$ for analysis
   elements is defined as
   \[
-    \atriage(\aelem) = \left\{
+    \areform(\aelem) = \left\{
       \begin{array}{ll}
@@
 \end{definition}
-Using the $\atriage$ function for analysis elements, we defined the $\triage$
+Using the $\areform$ function for analysis elements, we defined the $\reform$
 function for combined states:
-\begin{definition}[$\triage$]\label{def:triage}
-  The triage function $\triage: \combdom \rightarrow \combdom$ for combined
+\begin{definition}[$\reform$]\label{def:reform}
+  The reform function $\reform: \combdom \rightarrow \combdom$ for combined
   states is defined as
   \[
-    \triage((\sabselem, \symbelem)) = \left(
+    \reform((\sabselem, \symbelem)) = \left(
       \lambda \view. \bigjoin \{ \abselem \!\mid\! (\view, \abselem) \in E \},
@@
   \[
-    E = \dot{\atriage}(\{ (\view, \sabselem(\view)) \mid \view \in \viewset \} \cup \symbelem)
+    E = \dot{\areform}(\{ (\view, \sabselem(\view)) \mid \view \in \viewset \} \cup \symbelem)
   \]
@@
   \]
-  where $(\sabselem, \symbelem) = \triage(\combelem)$.
+  where $(\sabselem, \symbelem) = \reform(\combelem)$.
 \end{definition}

### 2020-11-26 paper/pldi21/report/ds.tex
Extendend Section 3 in report

\subsection{Combined Domain}
We now define a \textit{combined domain} of a given sensitive abstract
domain with the sealed symbolic domain and its one-step execution.
\begin{definition}[Combined Domain]
  A \textit{combined domain} is $\combdom = \sabsdom \times \symbdom$ and its
  concretization function $\combgamma: \combdom \rightarrow \dom$ and join
  operator are defined as follows:
  \begin{align}
    \combgamma((\sabselem, \symbelem)) &= \sgamma(\sabselem) \cup
      \symbgamma(\symbelem)\\
    (\sabselem, \symbelem) \join ({\sabselem}', \symbelem') &= (\sabselem \join
      {\sabselem}', \symbelem \cup \symbelem')
  \end{align}
\end{definition}

Before defining the one-step execution for the combined domain, we introduce
\textit{analysis elements} to easily configure different types of abstract
states in the sensitive abstract domain and the sealed symbolic domain.
\begin{definition}[Analysis Elements]\label{def:aelem}
  An \textit{analysis element} $\aelem \in \aelemset = (\viewset \times \absdom)
  \uplus (\absimapset \times \symbstset)$ is either 1) a pair of a view and an
  abstract state in a sensitive abstract domain $\sabsdom$, or 2) a pair of an
  abstract instantiation map and a sealed symbolic state in a sealed symbolic
  domain $\symbdom$.  Its concretization function $\aelemgamma:
  \aelemset \rightarrow \dom$ is defined as follows:
  \[
    \aelemgamma(\aelem) = \left\{
      \begin{array}{ll}
        \viewmap(\view) \cap \gamma(\abselem) & \text{if} \; (\view, \abselem) = \aelem\\
        \instant{\symbst}{\absimap} & \text{if} \; (\absimap, \symbst) = \aelem\\
      \end{array}
    \right.
  \]
\end{definition}

\begin{figure*}[t]
  \centering
  \begin{subfigure}[t]{0.15\textwidth}
    \includegraphics[height=3.2cm]{../img/listing}
    \caption{Notations}
    \label{fig:ds-example1}
  \end{subfigure}
  \quad
  \begin{subfigure}[t]{0.23\textwidth}
    \includegraphics[height=3.2cm]{../img/path-1}
    \caption{$\varx = 0$}
    \label{fig:ds-example2}
  \end{subfigure}
  \begin{subfigure}[t]{0.28\textwidth}
    \includegraphics[height=3.2cm]{../img/path-2}
    \caption{$\varx > 0$}
    \label{fig:ds-example3}
  \end{subfigure}
  \begin{subfigure}[t]{0.28\textwidth}
    \includegraphics[height=3.2cm]{../img/path-3}
    \caption{$\varx \in \mathbb{N}$}
    \label{fig:ds-example4}
  \end{subfigure}
  \caption{Abstract interpretation using a combined domain for the running
  example with different initial values for $\varx$.}
  \label{fig:ds-examples}
\end{figure*}

Moreover, to freely convert between different kinds of analysis elements, we define two converters:
\begin{align}
  \asconverter & : (\viewset \times \absdom) \hookrightarrow
    (\absimapset \times \symbstset)\\
  \saconverter & : (\viewset \times
    \absdom) \leftarrow (\absimapset \times \symbstset)
\end{align}
While the converter $\saconverter$ is total, the other one $\asconverter$ is
\textit{partial}. Thus, it is possible to convert an analysis element
$(\view, \abselem)$ in a sensitive abstract domain to another analysis element in
a sealed symbolic domain only if the convert $\asconverter$ is defined: $(\view,
\abselem) \in \Dom(\asconverter)$.  In addition, they should convert given
analysis elements without loss of information for all $\aelem \in \aelemset$:
\[
  \asconverter(\aelem) = \aelem' \Rightarrow \left\{
  \begin{array}{l}
    \aelem = \saconverter(\aelem')\\
    \aelemgamma(\aelem) = \aelemgamma(\aelem')\\
  \end{array}
  \right.
\]

Now, we define the \textit{combined one-step execution} $\combstep: \combdom
\rightarrow \combdom$ with two converters $\asconverter$ and $\saconverter$.
It consists of two steps: 1) the \textit{\reformname} step converts
analysis elements if a new sealed symbolic execution starts or an
existing one stops, and 2) the \textit{execution} step performs execution of each
analysis element using the abstract one-step execution $\sabsstep$ in the sensitive
abstract domain and the sealed symbolic one-step execution $\symbstep$ in the sealed
symbolic domain.
\begin{definition}[Combined One-Step Execution]
A \textit{combined one-step execution} $\combstep: \combdom \rightarrow
\combdom$ is define as follows:
  \[
    \combstep(\combelem) = (\sabsstep(\sabselem), \symbstep(\symbelem))
  \]
where $(\sabselem, \symbelem) = \reform(\combelem)$.
\end{definition}

From a given combined state $\combelem$, the $\reform$ function makes analysis elements
and converts them if a new sealed symbolic execution
begins or an existing sealed symbolic execution terminates.
Specifically, for an analysis element $(\view, \abselem)$ in the sensitive abstract domain,
if the converter $\asconverter$ is defined for it, $\reform$ introduces a new sealed symbolic execution
by converting the analysis element to its corresponding one $(\absimap, \symbst) =
\asconverter((\view, \abselem))$ in the sealed symbolic domain.
On the other hand, for an analysis element $(\absimap, \symbst)$ in the sealed symbolic domain,
if it does not have any sealed symbolic states to transit to, $\symbst \symbtrans \excst$,
the sealed symbolic execution for $(\absimap, \symbst)$ terminates;
It converts the analysis element to its corresponding one $(\view, \abselem) =
\saconverter((\absimap, \symbst))$ in the sensitive abstract domain and
merges the current abstract state stored in the view $\view$ with $\abselem$.

To formally define the $\reform$ function, we first define a $\areform$ function
for analysis elements using two converters.
\begin{definition}[$\areform$]\label{def:areform}
  The function $\areform: \aelemset \rightarrow \aelemset$ for analysis elements
  is defined as follows:
  \[
    \areform(\aelem) = \left\{
      \begin{array}{ll}
        \asconverter(\aelem)
        & \text{if} \; \aelem = (\view, \abselem) \wedge \aelem \in
        \Dom(\asconverter)\\
        \saconverter(\aelem)
        & \text{if} \; \aelem = (\absimap, \symbst) \wedge \symbst \symbtrans
        \bot\\
        \aelem
        & \text{Otherwise}
      \end{array}
    \right.
  \]
\end{definition}
\begin{definition}[$\reform$]\label{def:reform}
  The \reformname function $\reform: \combdom \rightarrow \combdom$ for combined
  states is defined as follows:
  \[
    \reform((\sabselem, \symbelem)) = \left(
      \lambda \view. \bigjoin \{ \abselem \!\mid\! (\view, \abselem) \in E \},
      E \cap (\absimapset \times \symbstset)
    \right)
  \]
  where
  \[
    E = \dot{\areform}(\{ (\view, \sabselem(\view)) \mid \view \in \viewset \} \cup \symbelem)
  \]
and the dot notation $\dot{f}$ denotes the element-wise extended function of a
function $f$.
\end{definition}

\subsection{Examples}
Now, we show examples of abstract interpretation with a combined domain.
Figure~\ref{fig:ds-examples} depicts the flow of analysis for the running
example in Figure~\ref{fig:running-example} with three different initial sets of
values for the variable $\varx$.  In this example, we use the abstract domain
$\{ -, 0, + \}$ for integers stored in $\varx$ as introduced in
Section~\ref{sec:ai}, and the \textit{flow sensitivity} that utilizes the
labels of states as their views as introduced in Section~\ref{sec:sens}.
For brevity, we use concatenation of abstract values so that
$-0$ denotes the set $\{ -, 0 \}$.

Figure~\ref{fig:ds-examples}(a) presents notations used in each graph. A solid
box denotes an analysis element that is a pair of a label $\lab$ and an abstract
state $\abselem$.  A pair enclosed by angle brackets denotes an analysis
element that is a pair of an abstract instantiation map $\absimap$ and a sealed
symbolic state $\symbst$.  In fact, the sealed symbolic state part (right) of
each pair in graphs contains only the value of the variable of $\varx$ without
its label.  For brevity, we represent its label by locating it next to
a node with its label.  A solid line is a view transition
$\viewtrans{\lab}{\lab'}$ from a label $\lab$ to another one $\lab'$.  A dotted
line is a sealed symbolic transition $\symbtrans$.  Three solid lines with
circled labels denote two converters $\saconverter$, $\asconverter$ and the join
operator $\join$.

Figure~\ref{fig:ds-examples}(b) shows the analysis with the combined domain when
the initial value of $\varx$ is $0$.  First, in the \reformname step,
the converter $\asconverter$ converts the analysis element $(\lab_0, 0)$ to
another analysis element $\langle \varnothing, 0 \rangle$ with the label
$\lab_0$.  It does not introduce any sealed symbolic values because
the value represents only a single value.  Until the end of the program, the
sealed symbolic execution from $\langle \varnothing, 0 \rangle$ successfully
continues.  Because there is no more possible symbolic transition for the
symbolic state $\langle \varnothing, 0 \rangle$ with the label $\lab_4$,
it is converted to $(\lab_4, 0)$ via the converter $\saconverter$.

Instead of a single value, assume that the initial value of $\varx$ is one of
any positive integers.  Figure~\ref{fig:ds-examples}(c) describes the analysis
flow for the case.  The initial abstract value at the label $\lab_0$ is
$+$ and it is impossible to convert it to any sealed symbolic values because the
next program statement requires the actual value stored in the variable $\varx$
for the branch condition $\varx \geq 0$.  Thus, it performs view transition
$\viewtrans{\lab_0}{\lab_1}$ from the label $\lab_0$ to another one $\lab_1$ for
the abstract value $+$ and the result is also $+$.  Now, the analysis element
$(\lab_1, +)$ can be converted to $\langle \symb \mapsto +, \symb \rangle$
with the label $\lab_1$.  This sealed symbolic execution step terminates in the
label $\lab_3$ because the next statement is $\varx = -\varx$ and the negation
operator requires the actual value of $\varx$.  It is converted to $(\lab_3, +)$ via $\saconverter$,
performs the view transition, and results in $(\lab_4, -)$.

For the last case, we assume that all integers are possible for the initial
value of the variable $\varx$ as described in Figure~\ref{fig:ds-examples}(d).
While it reaches the false branch in the label $\lab_2$ unlike previous cases,
it cannot perform dynamic shortcuts because the statement in the false
branch is $\varx = -\varx$, which requires the actual value of $\varx$.
At the label $\lab_3$, there are two analysis
elements: 1) $(\lab_3, +)$ introduced by the view transition from the label $\lab_2$
with $-$, and 2) $\langle \symb \mapsto 0+, \symb \rangle$ with $\lab_3$
introduced by sealed symbolic execution started at $\lab_1$.  Since it
is not possible to perform sealed symbolic execution for both elements, the
second one is converted to $(\lab_3, 0+)$ and merged with $+$ at $\lab_3$ via the
join operator $\join$.  Finally, the view transition
$\viewtrans{\lab_3}{\lab_4}$ from $\lab_3$ to $\lab_4$ is performed to the
merged abstract state $0+$ and the result is $-0$.

\subsection{Soundness and Termination}
The converter $\asconverter$ and the sealed symbolic transition $\symbtrans$ are
keys to configure the introduction and termination of sealed symbolic
execution.  To ensure the \textit{soundness} and \textit{termination} of an
abstract interpretation defined with a combined domain of a sensitive abstract
domain and a sealed symbolic domain, the following conditions should hold.

\begin{theorem}[Soundness and Termination]\label{theorem:shortcut}
An abstract interpretation with dynamic shortcuts is \textbf{sound} and
\textbf{terminates} in a finite time if:
  \begin{itemize}
    \item the abstract transfer function $\abstransfer$ is sound,
    \item the sensitive abstract domain $\sabsdom$ has a finite height,
    \item the sealed symbolic transition $\symbtrans$ is valid, and
    \item there exists $N < \infty$ such that
      \[
        \forall \aelem \in \aelemset. \; \asconverter(\aelem) = (\absimap,
        \symbst) \Rightarrow \symbst
        \symbtrans^k \excst \wedge 1 < k \leq N
      \]
  \end{itemize}
\end{theorem}

To formally prove Theorem~\ref{theorem:shortcut}, we assume that its all
conditions are hold and rephrase the \textit{soundness} as
Theorem~\ref{theorem:soundness} and \textit{termination} as
Theorem~\ref{theorem:termination}.

\subsubsection{Soundness}

\begin{theorem}[Soundness]\label{theorem:soundness}
  The abstract interpretation using the combined domain $\combdom$ is
  \textbf{sound} if
  \begin{equation}\label{equ:sound-join}
    \forall \combelem_0, \combelem_1 \in \combdom. \; \combgamma(\combelem_0) \cup
    \combgamma(\combelem_1) \subseteq \combgamma(\combelem_0 \join \combelem_1)
  \end{equation}
  \begin{equation}\label{equ:sound-combstep}
    \forall \combelem \in \combdom. \; \step \circ \combgamma(\combelem) \subseteq
    \combgamma \circ \combstep(\combelem)\\
  \end{equation}
\end{theorem}
\begin{proof}
  First, we prove that the abstract transfer function $\combtransfer: \combdom
  \rightarrow \combdom$ defined as $\combtransfer(\combelem) = \combelem \join
  \combstep(\combelem)$ is sound
  \[
    \begin{array}{rcll}
      \transfer \circ \combgamma(\combelem)
      &=& \combgamma(\combelem) \cup \step \circ \combgamma(\combelem)\\
      &\subseteq& \combgamma(\combelem) \cup \combgamma \circ \combstep(\combelem)
      & (\because \; \text{condition~(\ref{equ:sound-combstep})})\\
      &\subseteq& \combgamma(\combelem \join \combstep(\combelem))
      & (\because \; \text{condition~(\ref{equ:sound-join})})\\
      &=& \combgamma \circ \combtransfer(\combelem)\\
    \end{array}
  \]
  Then, the abstract semantics $\combsem{\prog} = \underset{n \rightarrow
  \infty}{\lim}{(\combtransfer)^n(\icombelem)} $ is also sound because it is
  defined with a sound abstract transfer function $\combtransfer$ using the
  combined one-step execution $\combstep$.
\end{proof}

Now, we should show that two conditions about the soundness of the join
operator (\ref{equ:sound-join}) and the soundness of the combined one-step
execution (\ref{equ:sound-combstep}) in Theorem~\ref{theorem:soundness} hold.

First, we prove the soundness of the join operator (\ref{equ:sound-join}) in
Lemma~\ref{lemma:sound-join}.
\begin{lemma}[Soundness of $\join$]\label{lemma:sound-join}
  \[
    \forall \combelem_0, \combelem_1 \in \combdom. \; \combgamma(\combelem_0) \cup
    \combgamma(\combelem_1) \subseteq \combgamma(\combelem_0 \join \combelem_1)
  \]
\end{lemma}
\begin{proof}
  \[
    \begin{array}{cl}
      \multicolumn{2}{l}{
        \combgamma((\sabselem, \symbelem)) \cup \combgamma((\sabselem', \symbelem'))
      }\\
      =& \sgamma(\sabselem) \cup \symbgamma(\symbelem)
      \cup \sgamma(\sabselem') \cup \symbgamma(\symbelem')\\
      =& (\sgamma(\sabselem)\cup \sgamma(\sabselem'))
      \cup (\symbgamma(\symbelem) \cup \symbgamma(\symbelem'))\\
      \subseteq& \sgamma(\sabselem \join \sabselem')
      \cup (\symbgamma(\symbelem) \cup \symbgamma(\symbelem'))\\
      & \multicolumn{1}{r}{(\because \; \sabsdom \; \text{is sound})}\\
      =& \sgamma(\sabselem \join \sabselem')
      \cup \symbgamma(\symbelem \cup \symbelem')\\
      =& \combgamma((\sabselem \join \sabselem', \symbelem \cup \symbelem'))\\
      =& \combgamma((\sabselem, \symbelem) \join (\sabselem', \symbelem'))\\
    \end{array}
  \]
\end{proof}

For the condition (\ref{equ:sound-combstep}), we first prove two properties of the
$\reform$ function in Lemma~\ref{lemma:reform}.  Using the properties, we prove
the soundness of the sealed symbolic one-step execution in
Lemma~\ref{lemma:sound-symbstep}.  Finally, we prove the soundness of the
combined one-step execution (\ref{equ:sound-combstep}) in
Lemma~\ref{lemma:sound-combstep}.

\begin{lemma}[Properties of $\reform$]\label{lemma:reform}
  For a given combined state $\combelem \in \combdom$, the $\reform$ function
  satisfies the following two properties:
  \begin{itemize}
    \item $\combgamma(\combelem) \subseteq \combgamma \circ \reform(\combelem)$
    \item $\forall (\absimap, \symbst) \in \symbelem. \; \exists \symbst' \in
      \symbstset.  \; \text{s.t.} \; \symbst \symbtrans \symbst'$
  \end{itemize}
  where $(\sabselem, \symbelem) = \reform(\combelem)$
\end{lemma}
\begin{proof}
  \[
    \fbox{$\combgamma(\combelem) \subseteq \combgamma \circ \reform(\combelem)$}
  \]
  \[
    \begin{array}{cl}
      \multicolumn{2}{l}{\combgamma((\sabselem, \symbelem))}\\
      =& \sgamma(\sabselem) \cup \symbgamma(\symbelem)\\

      =& \left( \underset{\view \in \viewset}{\bigcup} {\viewmap(\view) \cap
      \gamma \circ \sabselem(\view)} \right) \cup \left( \underset{(\absimap,
      \symbst) \in \symbelem}{\bigcup} \instant{\symbst}{\absimap} \right) \\

      =& \left( \underset{\view \in \viewset}{\bigcup} \aelemgamma((\view,
      \sabselem(\view))) \right) \cup \left( \underset{(\absimap, \symbst) \in
      \symbelem}{\bigcup} \aelemgamma((\absimap, \symbst)) \right) \\

      =& \dot\aelemgamma(\{ (\view, \sabselem(\view)) \mid \view \in \viewset \}
      \cup \symbelem)\\

      =& \dot\aelemgamma(\dot{\areform}(\{ (\view, \sabselem(\view)) \mid \view
      \in \viewset \} \cup \symbelem))\\

       & \multicolumn{1}{r}{\because \; (\text{Trivially,} \; \forall \aelem \in
       \aelemset.  \; \aelemgamma(\aelem) = \aelemgamma \circ \areform(\aelem))}\\

      =& \dot\aelemgamma(E)\\
       & \multicolumn{1}{r}{\because \; (\text{See the definition of $E$ in
       Definition~\ref{def:reform}})}\\
    \end{array}
  \]
  \[
    \begin{array}{cl}
      =& \left( \underset{(\view, \abselem) \in E}{\bigcup} \aelemgamma((\view,
      \abselem)) \right) \cup \left( \underset{(\absimap, \symbst) \in
      E}{\bigcup} \aelemgamma((\absimap, \symbst)) \right)\\

      =& \left( \underset{(\view, \abselem) \in E}{\bigcup} \viewmap(\view) \cap
      \gamma(\abselem) \right) \cup \left( \underset{(\absimap, \symbst) \in
      E}{\bigcup} \instant{\symbst}{\absimap} \right)\\

      =& \left( \underset{\view \in \viewset}{\bigcup} { \underset{(\view,
      \abselem) \in E}{\bigcup} \viewmap(\view) \cap \gamma(\abselem) } \right)
      \cup \left( \underset{(\absimap, \symbst) \in E}{\bigcup}
      \instant{\symbst}{\absimap} \right)\\

      =& \left( \underset{\view \in \viewset}{\bigcup} {\viewmap(\view) \cap
        \left(\underset{(\view, \abselem) \in
      E}{\bigcup}{\gamma(\abselem)}\right)} \right) \cup \left(
      \underset{(\absimap, \symbst) \in E}{\bigcup} \instant{\symbst}{\absimap}
      \right)\\

      \subseteq& \left( \underset{\view \in \viewset}{\bigcup} {\viewmap(\view)
        \cap \gamma\left( \underset{(\view, \abselem) \in E}{\bigjoin}\abselem
      \right)} \right) \cup \left( \underset{(\absimap, \symbst) \in E}{\bigcup}
      \instant{\symbst}{\absimap} \right)\\

      =& \sgamma\left( \lambda \view. \underset{(\view, \abselem) \in
      E}{\bigjoin}\abselem \right) \cup \symbgamma(E \cap (\absimapset \times
      \symbstset))\\

      =& \combgamma\left( \lambda \view. \underset{(\view, \abselem) \in
      E}{\bigjoin}\abselem, E \cap (\absimapset \times \symbstset) \right)\\

      =& \combgamma \circ \reform((\sabselem, \symbelem))
    \end{array}
  \]
  \[\]
  \[
    \fbox{$\forall (\absimap, \symbst) \in \symbelem. \; \exists \symbst' \in
    \symbstset.  \; \text{s.t.} \; \symbst \symbtrans \symbst'$}
  \]

  For a given $(\absimap, \symbst) \in \symbelem$, there exists an analysis
  element $\aelem \in \aelemset$ such that $\areform(\aelem) = (\absimap,
  \symbst)$.  According to the definition of $\areform$ in
  Definition~\ref{def:areform}, there are two possible cases: $\aelem =
  (\absimap, \symbst) \wedge \exists \symbst' \in \symbstset. \; \text{s.t} \;
  \symbst \symbtrans \symbst'$ or $\aelem = (\view, \abselem) \wedge \aelem \in
  \Dom(\asconverter)$. We separately consider those two cases:
  \begin{itemize}
    \item $\aelem = (\absimap, \symbst) \wedge \exists \symbst' \in \symbstset.
      \; \text{s.t} \; \symbst \symbtrans \symbst'$\\
        By definition, $\exists \symbst' \in \symbstset.  \; \text{s.t} \;
        \symbst \symbtrans \symbst'$
    \item $\aelem = (\view, \abselem) \wedge \aelem \in \Dom(\asconverter)$\\
      By the condition~\ref{equ:asc-cond} in the Theorem~\ref{theorem:shortcut},\\
      $\exists k > 1. \symbst \symbtrans^k \excst$.  Thus, $\exists \symbst' \in
      \symbstset.  \; \text{s.t} \; \symbst \symbtrans \symbst'$
  \end{itemize}
\end{proof}

\begin{lemma}[Soundness of $\symbstep$]\label{lemma:sound-symbstep}
  The sealed symbolic one-step execution $\symbstep$ is sound:
  \[
    \step \circ \symbgamma(\symbelem) \subseteq
    \symbgamma \circ \symbstep(\symbelem)\\
  \]
\end{lemma}
\begin{proof}
  \[
    \begin{array}{cl}
      \multicolumn{2}{l}{\step \circ \symbgamma(\symbelem)}\\
      =& \step(\bigcup \{ \instant{\symbst}{\absimap} \mid (\absimap, \symbst) \in
      \symbelem\})\\
      =& \{ \st' \mid (\absimap, \symbst) \in \symbelem \wedge \st \in
      \instant{\symbst}{\absimap} \wedge \st \trans \st'\})\\
      =& \{ \st' \mid (\absimap, \symbst) \in \symbelem \wedge \imap \in
      \imapgamma(\absimap) \wedge \instant{\symbst}{\imap} \trans \st'\})\\
      =& \{ \st' \mid (\absimap, \symbst) \in \symbelem \wedge \imap \in
      \imapgamma(\absimap) \wedge \instant{\symbst}{\imap} \trans \st'\\
       & \phantom{\{ \st' \mid (\absimap, \symbst) \in \symbelem \wedge \imap \in
      \imapgamma(\absimap)} \wedge \symbst \symbtrans \symbst' \})\\
       & \multicolumn{1}{r}{(\because \; \text{Second property in
       Lemma~ref{lemma:reform}})}\\
      =& \{ \instant{\symbst'}{\imap} \mid (\absimap, \symbst)
      \in \symbelem \wedge \imap \in \imapgamma(\absimap) \wedge \symbst
      \symbtrans \symbst'\}\\
      & \multicolumn{1}{r}{(\because \; \text{Validity of} \; \symbtrans)}\\
      =& \bigcup \{ \instant{\symbst'}{\absimap} \mid (\absimap, \symbst)
      \in \symbelem \wedge \symbst \symbtrans \symbst' \}\\
      =& \symbgamma(\{ (\absimap, \symbst') \mid (\absimap, \symbst)
      \in \symbelem \wedge \symbst \symbtrans \symbst' \})\\
      =& \symbgamma \circ \symbstep(\symbelem)\\
    \end{array}
  \]
\end{proof}

\begin{lemma}[Soundness of $\combstep$]\label{lemma:sound-combstep}
  The combined one-step execution $\combstep$ is sound:
  \[
    \forall \combelem \in \combdom. \; \step \circ \combgamma(\combelem) \subseteq
    \combgamma \circ \combstep(\combelem)\\
  \]
\end{lemma}
\begin{proof}
  \[
    \begin{array}{cl}
      \multicolumn{2}{l}{
        \step \circ \combgamma(\combelem)
      }\\
      \subseteq& \step \circ \combgamma((\sabselem, \symbelem))\\
       & \multicolumn{1}{r}{(\because \; \text{First property in
       Lemma~\ref{lemma:reform}}}\\
       & \multicolumn{1}{r}{\text{where} \; (\sabselem, \symbelem)
       = \reform(\combelem).)}\\

      =& \step(\sgamma(\sabselem) \cup \symbgamma(\symbelem))\\
      =& \step(\sgamma(\sabselem)) \cup \step(\symbgamma(\symbelem))\\
      \subseteq& \sgamma \circ \sabsstep(\sabselem) \cup \step(\symbgamma(\symbelem))\\
      & \multicolumn{1}{r}{(\because \; \sabsstep \; \text{is sound.})}\\
      \subseteq& \sgamma \circ \sabsstep(\sabselem) \cup \symbgamma \circ
      \symbstep((\symbelem))\\
               & \multicolumn{1}{r}{(\because \; \text{and
               Lemma~\ref{lemma:sound-symbstep}})}\\
      =& \combgamma((\sabsstep(\sabselem), \symbstep(\symbelem)))\\
      =& \combgamma \circ \combstep(\combelem)\\
    \end{array}
  \]
\end{proof}

\subsection{Termination}

Before proving the termination of the abstract interpretation using the combined
domain $\combdom$, we define several notations. The initial abstract state
$\icombelem = (\isabselem, \varnothing)$ is pair of the initial abstract state of
the sensitive abstract domain $\sabsdom$ and an empty set. For each iteration $i
\geq 0$, we define the $i$-th result of abstract interpretation
$\combtransfer^i(\icombelem) = \combelem^i = (\sabselem^i, \symbelem^i)$ and the
\textit{difference set} $\diffset_i = \symbelem^{i+1} \setminus \symbelem^i$.
For simplicity, we define $\diffset_i$ as $\varnothing$ for $i < 0$.  Moreover, we
define a lifted version of sealed symbolic relation $\liftsymbtrans \subseteq
(\absimapset \times \symbstset) \times (\absimapset \times \symbstset)$ as
follows:
\[
  (\absimap, \symbst) \liftsymbtrans (\absimap, \symbst') \Leftrightarrow
  \symbst \symbtrans \symbst'
\]
Using the lifted relation, we define the \textit{time to live (TTL)} function of
symbolic states $\ttl_i: \diffset_i \rightarrow \numset$ for each iteration $i
\geq 0$ as follows:
\begin{definition}[TTL Function]
  \[
    \begin{array}{c}
      \ttl_i(\symbaelem) = \left \{
      \begin{array}{l}
        N - 1 \;\; ( \text{if} \; D = \varnothing)\\
        \text{min}(\dot\ttl_{i-1}(D)) - 1
        \;\; ( \text{otherwise})
      \end{array}
      \right. \\
      \\
      \text{where} \; D =
      \{\symbaelem' \in \diffset_{i-1} \mid \symbaelem' \liftsymbtrans \symbaelem\}
    \end{array}
  \]
\end{definition}

Based on the notations, we formally prove the termination property as folows:
\begin{theorem}[Termination]\label{theorem:termination}
  The abstract interpretation using the combined domain $\combdom$
  \textbf{terminates} in a finite time if
  \begin{equation}\label{equ:termination-sai}
    \exists n. \; \forall m \geq n. \; \sabselem^m = \sabselem^n
  \end{equation}
  \begin{equation}\label{equ:bounded-ttl}
    \forall i \geq 0. \; \forall \symbaelem \in \diffset_i. \;
    0 < \ttl_i(\symbaelem) < N
  \end{equation}
  \begin{equation}\label{equ:dec-ttl}
    \begin{array}{c}
      \forall i > 0. \; \sabselem^{i-1} = \sabselem^i \Rightarrow\\
      \sup(\dot \ttl_i(\diffset_i)) \leq \sup(\dot \ttl_{i-1}(\diffset_{i-1})) - 1
    \end{array}
  \end{equation}
\end{theorem}

\begin{proof}
  By the condition (\ref{equ:termination-sai}), there exists $n \in \numset$
  such that $\sabselem^m = \sabselem^n$ for all $m \geq n$.  By the condition
  (\ref{equ:bounded-ttl}), the TTL of each symbolic state in $\diffset_n$ is
  bounded by $N$:
  \[
    \sup(\dot \ttl_n(\diffset_n)) < N
  \].
  Then, the upper bound of TTL for symbolic states in each difference set after
  the $n-$th iteration is decreased by the condition (\ref{equ:dec-ttl}):
  \[
    \forall i > 0. \; \sup(\dot \ttl_{n+i}(\diffset_{n+i})) \leq \sup(\dot
    \ttl_{n+i-1}(\diffset_{n+i-1})) - 1
  \].
  which implies that
  \[
    \sup(\dot \ttl_{n+i}(\diffset_{n+i})) \leq \sup(\dot \ttl_n(\diffset_n)) - i < N - i
  \]
  Therefore, for $j \geq N$,
  \[
    \sup(\dot \ttl_{n+j}(\diffset_{n+j})) < N - j \leq 0
  \]
  Notice that again by the condition (\ref{equ:bounded-ttl}),
  \[
    inf(\dot \ttl_{n+j}(\diffset_{n+j})) > 0
  \]
  meaning that
  \[
    inf(\dot \ttl_{n+j}(\diffset_{n+j})) > \sup(\dot \ttl_{n+j}(\diffset_{n+j}))
  \]
  which implies $\diffset_{n+j} = \varnothing$ and $\symbelem^{n+j+1} =
  \symbelem^{n+j}$.
  Therefore, for all $m \geq n + N$,
  \[
    \sabselem^m = \sabselem^{n+N} \wedge \symbelem^m = \symbelem^{n+N}
  \]
  and
  \[
    \combelem^m = \combelem^{n+N}
  \]
  which means the abstract interpretation using the combined domain
  $\combdom$ terminates in $n+N$ iterations.
\end{proof}

Now, we should show that three conditions about the termination of the sensitive
abstract interpretation (\ref{equ:termination-sai}), the bound of TTL for
symbolic states in difference sets (\ref{equ:bounded-ttl}), and the decrease of
their upper bounds (\ref{equ:dec-ttl}) in Theorem~\ref{theorem:termination}
hold.

First, we prove the termination of the sensitive abstract interpretation
(\ref{equ:termination-sai}) in Lemma~\ref{lemma:termination-sai}.

\begin{lemma}[Termination of Sensitive Abstract Interpretation]\label{lemma:sabs-term}
\label{lemma:termination-sai}
  \[
    \exists n. \; \forall m \geq n. \;
    \sabselem^m = \sabselem^n
  \]
\end{lemma}

\begin{proof}
Note that for all $\sabselem, \sabselem' \in \sabsdom$ that satisfies
$\combtransfer((\sabselem, \_)) = (\sabselem', \_)$,
\[
  \begin{array}{rcl}
  \combtransfer((\sabselem, \_))
  &=& (\sabselem, \_) \join \combstep((\sabselem, \_))\\
  &=& (\sabselem, \_) \join (\_, \_) = (\sabselem \join \_, \_)\\
  &=& (\sabselem', \_)
  \end{array}
\]
which implies $\sabselem \order \sabselem'$.  Since
$\combtransfer((\sabselem^i, \_)) = (\sabselem^{i+1}, \_), \sabselem^i \order
\sabselem^{i+1}$ holds for all $i \geq 0$.  Then, $\sabselem^0 \order \sabselem^1
\order \sabselem^2 \cdots$ is an ascending chain.  Since the height of the
sensitive abstract domain $\sabsdom$ is finite, the ascending chain condition is
also hold. Therefore, there exists n such that for all $m \geq n, \sabselem^m =
\sabselem^n$.
\end{proof}

Then, we prove two remaining conditions (\ref{equ:bounded-ttl}) and
(\ref{equ:dec-ttl}).  We first prove two properties of difference sets in
Lemma~\ref{lemma:diffset_prop} and Corollary~\ref{corollary:only-from-diffset},
and a property of TTL in Lemma~\ref{lemma:prop-ttl}.  Using them, we prove the
bound of TTL for symbolic states in difference sets (\ref{equ:bounded-ttl}) in
Corollary~\ref{corollary:bounded-ttl} and the decrease of their upper bounds
(\ref{equ:dec-ttl}) in Lemma~\ref{lemma:dec-ttl}.

\begin{lemma}\label{lemma:diffset_prop}
  \[
    \begin{array}{c}
      \forall i \geq 0. \; \forall \symbaelem \in \diffset_i. \\
      \exists \view. \; \asconverter((\view,\sabselem^i(\view))) \liftsymbtrans \symbaelem 
      \lor \exists \symbaelem' \in \diffset_{i-1} . \; \symbaelem' \liftsymbtrans \symbaelem
    \end{array}
  \]
\end{lemma}
\begin{proof}
  Let $i \in \numset$ and $\symbaelem \in \diffset_i = \symbelem^{i+1} \setminus \symbelem^i$ given.
  By definition,
  \[
    \symbelem^{i+1} = \symbelem^i \cup \symbstep({\symbelem^i}')
  \]
  where
  \[
    (\_, {\symbelem^i}') = \reform(\sabselem^i, \symbelem^i)
  \]
  Note that $\symbaelem \in \symbstep({\symbelem^i}')$,
  and by definition of $\symbstep$, there exists some
  $\symbaelem' \in {\symbelem^i}'$ that satisfies $\symbaelem' \liftsymbtrans \symbaelem$.
  Now, by definition of $\reform$,
  \[
    {\symbelem^i}' =
    \dot{\areform}(\{ (\view, \sabselem^i(\view)) \mid \view \in \viewset \} \cup \symbelem^i)
    \cap (\absimapset \times \symbstset)
  \]
  This means there exists
  $\aelem \in \{ (\view, \sabselem^i(\view)) \mid \view \in \viewset \} \cup \symbelem^i$
  that satisfies $\areform(\aelem) = \symbaelem'$. We have two possible cases for $\aelem$.
  \begin{itemize}

  \item $\aelem \in \{ (\view, \sabselem^i(\view)) \mid \view \in \viewset \}$

  In this case, $\areform(\aelem) = \asconverter(\aelem) = \symbaelem'$
  and the left condition for conclusion is satisfied.

  \item $\aelem \in \symbelem^i$

  In this case, $\areform(\aelem) = \aelem = \symbaelem'$.
  Now, let's assume that $\aelem \in \symbelem^{i-1}$.
  In that case, $\aelem$ would be preserved after reform step, that is,
  $\aelem \in {\symbelem^{i-1}}'$. Then, by definition of $\symbstep$,
  $\symbaelem \in \symbstep({\symbelem^{i-1}}') \subseteq \symbelem^i$
  whcih contradicts to the fact that $\symbaelem \in \diffset_i$.
  Therefore, $\aelem \notin \symbelem^{i-1}$, that is,
  $\aelem \in \symbelem^i \setminus \symbelem^{i-1} = \diffset_i$,
  and the right condition for conclusion is satisfied.
  \end{itemize}
\end{proof}

\begin{corollary}\label{corollary:only-from-diffset}
  \[
    \begin{array}{c}
      \forall i > 0. \; \sabselem^{i-1} = \sabselem^i \Rightarrow
      \forall \symbaelem \in \diffset_i. \\
      \exists \symbaelem' \in \diffset_{i-1} . \; \symbaelem' \liftsymbtrans \symbaelem
    \end{array}
  \]
\end{corollary}
\begin{proof}
  The proof goes same as the previous lemma, until the point where we divide
  the case for $\aelem$. Let's assume that the first case holds, that is,
  \[
    \aelem \in \{ (\view, \sabselem^i(\view)) \mid \view \in \viewset \}
  \]
  Since $\sabselem^{i-1} = \sabselem^i$,
  \[
    \aelem \in \{ (\view, \sabselem^{i-1}(\view)) \mid \view \in \viewset \}
  \]
  In that case, $\aelem$ would be transformed after reform step, that is,
  $\asconverter(\aelem) = \symbaelem' \in {\symbelem^{i-1}}'$.
  Then, by definition of $\symbstep$,
  $\symbaelem \in \symbstep({\symbelem^{i-1}}') \subseteq \symbelem^i$
  whcih contradicts to the fact that $\symbaelem \in \diffset_i$.
  Therefore, only second case holds and the right conclusion in previus lemma is satisfied.
\end{proof}

\begin{lemma}[Property of TTL]\label{lemma:prop-ttl}
  \[
    \begin{array}{c}
      \forall i \geq 0. \; \forall \symbaelem \in \diffset_i.
      \ttl_i(\symbaelem) = k \Rightarrow \\
      k < N \wedge
      \exists (\view, \abselem). \; (\asconverter((\view,\abselem))
      \liftsymbtrans^{(N - k)} \symbaelem) \\
    \end{array}
  \]
\end{lemma}
\begin{proof}
  We prove by induction on $i$.
  Let $\symbaelem \in \diffset_i$.
  \begin{itemize}
  \item If $i = 0$, $\ttl_0(\symbaelem) = N - 1 < N$
  and since only left conclusion of lemma~\ref{lemma:diffset_prop} can hold,
  there eixsts view $\view$ s.t.
  $\asconverter(\view, \sabselem^0(\view)) \liftsymbtrans^1 \symbaelem$.
  \item If $i > 0$, we have two cases for $D = 
    \{\symbaelem' \in \diffset_{i-1} \mid \symbaelem' \liftsymbtrans \symbaelem\}$.
  If $D = \varnothing$, the argument is similar as $i = 0$ case.
  Otherwise, let $\symbaelem' = \underset{\x \in D}{argmin}{\ttl_{i-1}(x)}$.

  By induction hypothesis, we have
  \[
    k' = \ttl_{i-1}(\symbaelem') < N
  \]
  and there eixsts $(\view, \abselem)$ such that
  \[
    \symbaelem'' = \asconverter((\view,\abselem)) \liftsymbtrans^{(N - k')} \symbaelem'.
  \]
  By definition of $\ttl_i$,
  $\ttl_i(\symbaelem) = \ttl_i(\symbaelem') - 1$, and $k = k' - 1$.
  Then,
  \[
    k = k' - 1 < N - 1 < N
  \]
  and
  $\symbaelem'' \liftsymbtrans^{(N - k - 1)} \symbaelem'$ with
  $\symbaelem' \liftsymbtrans \symbaelem$ implies that
  \[
    \symbaelem'' \liftsymbtrans^{(N - k)} \symbaelem.
  \]
  \end{itemize}
\end{proof}
\begin{corollary}\label{corollary:bounded-ttl}
  \[
    \forall i \geq 0. \; \forall \symbaelem \in \diffset_i. \;
    0 < \ttl_i(\symbaelem) < N
  \]
\end{corollary}
\begin{proof}
We already proved $k = \ttl_i(\symbaelem) < N$.
Now, let's assume that $k \leq 0$.
By previous lemma, there exists $(\view, \abselem)$ such that
\[
  (\asconverter((\view,\abselem)) \liftsymbtrans^{(N - k)} \symbaelem)
\]
Since $N - k \geq N$, this implies that there exists $\symbaelem'$ such that
\[
  (\asconverter((\view,\abselem)) \liftsymbtrans^N \symbaelem')
\]
However, this contradicts to the condition~(\ref{equ:asc-cond}) of $\asconverter$ that says
if $(\view,\abselem)$ is in domain of $\asconverter$,
the number of possible $\symbtrans$ from state of $\asconverter((\view,\abselem))$
is at most $N - 1$.
Therefore, $k > 0$.
\end{proof}

\begin{lemma}\label{lemma:dec-ttl}
  \[
    \begin{array}{c}
      \forall i > 0. \; \sabselem^{i-1} = \sabselem^i \Rightarrow \\
      \sup(\dot \ttl_i(\diffset_i)) \leq \sup(\dot \ttl_{i-1}(\diffset_{i-1})) - 1
    \end{array}
  \]
\end{lemma}
\begin{proof}
  Let $\symbaelem \in \diffset_i$.
  By Corollary~\ref{corollary:only-from-diffset}, the set
  \[
    D = \{\symbaelem' \in \diffset_{i-1} \mid \symbaelem' \liftsymbtrans \symbaelem\}
  \]
  is non-empty, and for some $\symbaelem' \in \diffset_{i-1}$,
  \[
    \ttl_i(\symbaelem) = \ttl_{i-1}(\symbaelem') - 1 \leq \sup(\dot \ttl_{i-1}(\diffset_{i-1})) - 1
  \]
  Since it holds for every $\symbaelem \in \diffset_i$,
  \[
    \sup(\dot \ttl_i(\diffset_i)) \leq \sup(\dot \ttl_{i-1}(\diffset_{i-1})) - 1
  \]
\end{proof}

### 2020-11-26 paper/pldi21/report/intro.tex
Extendend Section 3 in report

--- 2020-11-21 paper/pldi21/intro.tex
@@
   \centering
-  \includegraphics[width=\linewidth]{img/performance_v8v7}
+  \includegraphics[width=\linewidth]{../img/performance_v8v7}
   \vspace*{-2em}
@@
 Lodash 4 library.  The experiment shows that $\tool$ outperforms
-SAFE \inred{6.30}x on average.  Moreover, by using dynamic shortcuts
-instead of manual modeling for \inred{12} opaque functions,
+SAFE 6.30$\x$ on average.  Moreover, by using dynamic shortcuts
+instead of manual modeling for 12 opaque functions,
 $\tool$ improves the analysis precision to detect 6 more dead branches on

### 2020-11-26 paper/pldi21/report/javascript.tex
Extendend Section 3 in report

--- 2020-11-21 paper/pldi21/javascript.tex
@@
 Moreover, since object properties are string values that can be constructed at run time,
-it is difficult for static analysis to know whether strong updates are possible or not.
+it is difficult to perform sound strong updates in static analysis.
 To check the possibility of strong updates during sealed symbolic execution,

### 2020-11-26 paper/pldi21/report/ds.tex
Finished to revise the report

@@
 
-Based on the notations, we formally prove the termination property as folows:
+Based on the notations, we formally prove the termination property as follows:
 \begin{theorem}[Termination]\label{theorem:termination}
@@
   $\symbaelem \in \symbstep({\symbelem^{i-1}}') \subseteq \symbelem^i$
-  whcih contradicts to the fact that $\symbaelem \in \diffset_i$.
+  which contradicts to the fact that $\symbaelem \in \diffset_i$.
   Therefore, $\aelem \notin \symbelem^{i-1}$, that is,
@@
   $\symbaelem \in \symbstep({\symbelem^{i-1}}') \subseteq \symbelem^i$
-  whcih contradicts to the fact that $\symbaelem \in \diffset_i$.
-  Therefore, only second case holds and the right conclusion in previus lemma is satisfied.
+  which contradicts to the fact that $\symbaelem \in \diffset_i$.
+  Therefore, only second case holds and the right conclusion in previous lemma is satisfied.
 \end{proof}
@@
   and since only left conclusion of lemma~\ref{lemma:diffset_prop} can hold,
-  there eixsts view $\view$ s.t.
+  there exists view $\view$ s.t.
   $\asconverter(\view, \sabselem^0(\view)) \liftsymbtrans^1 \symbaelem$.
@@
   \]
-  and there eixsts $(\view, \abselem)$ such that
+  and there exists $(\view, \abselem)$ such that
   \[

### 2020-11-26 paper/pldi21/report/javascript.tex

@@
 sealed symbolic execution of the core language for dynamic shortcuts.
-Due to the space limitation, we present the main design of the
-language in this paper and refer the interested readers to a companion report~\cite{report}.
 
 \subsection{Core Language of JavaScript}
+\begin{figure*}[t]
+  \centering
+
+  \fbox{$\st \trans \st$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \refer = \expr\\
+      \referrule{\st}{\refer}{\loc}\\
+      \exprrule{\st}{\expr}{\val}\\
+    }
+    {
+      \st = (\lab, \mem, \ctxt, \addr)
+      \trans
+      (\labnext(\lab), \mem[\loc \mapsto \val], \ctxt, \addr)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \refer = \kwobj\\
+      \referrule{\st}{\refer}{\loc}\\
+      \addr' = \text{(a fresh object address)}
+    }
+    {
+      \st = (\lab, \mem, \ctxt, \addr)
+      \trans
+      (\labnext(\lab), \mem[\loc \mapsto \addr'], \ctxt, \addr)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \refer = \expr_f ( \expr_a )\\
+      \referrule{\st}{\refer}{\loc}\\
+      \exprrule{\st}{\expr_f}{\fval{x}{\lab_b}}\\
+      \exprrule{\st}{\expr_a}{\val_a}\\
+      \addr' = \text{(a fresh environment address)}
+    }
+    {
+      \st = (\lab, \mem, \ctxt, \addr)
+      \trans
+      (\lab_b, \mem[(\addr', x) \mapsto \val_a], \ctxt[\addr' \mapsto (\addr,
+      \labnext(\lab), \loc)], \addr')
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwret \; \expr\\
+      \exprrule{\st}{\expr}{\val}\\
+      \ctxt(\addr) = (\addr', \lab', \loc)
+    }
+    {
+      \st = (\lab, \mem, \ctxt, \addr)
+      \trans
+      (\lab', \mem[\loc \mapsto \val], \ctxt, \addr')
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwif \; \expr \; \lab'\\
+      \exprrule{\st}{\expr}{\kwtrue}\\
+    }
+    {
+      \st = (\lab, \mem, \ctxt, \addr)
+      \trans
+      (\lab', \mem, \ctxt, \addr)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwif \; \expr \; \lab'\\
+      \exprrule{\st}{\expr}{\kwfalse}\\
+    }
+    {
+      \st = (\lab, \mem, \ctxt, \addr)
+      \trans
+      (\labnext(\lab), \mem, \ctxt, \addr)
+    }
+  \end{mathpar}
+
+  \fbox{$\referrule{\st}{\refer}{\loc}$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {}
+    {
+      \referrule{\st = (\lab, \mem, \ctxt, \addr)}{x}{(\addr, x)}\\
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \exprrule{\st}{\expr_0}{\addr_0}\\
+      \exprrule{\st}{\expr_1}{\val_1}\\
+      \val_1 \in \strset\\
+    }
+    {
+      \referrule{\st = (\lab, \mem, \ctxt, \addr)}{\expr_0 [ \expr_1
+      ]}{(\addr_0, \val_1)}
+    }
+  \end{mathpar}
+
+  \fbox{$\exprrule{\st}{\expr}{\val}$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {}
+    {
+      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}{\pval}{\pval}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {}
+    {
+      \exprrule{\st = (\lab, \mem, \ctxt,
+      \addr)}{\fval{x}{\lab'}}{\fval{x}{\lab'}}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \referrule{\st}{\refer}{\loc}\\
+      \loc \in \Dom(\mem)
+    }
+    {
+      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}{\refer}{\mem(\loc)}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \exprrule{\st}{\expr_1}{\val_1}\\
+      \cdots\\
+      \exprrule{\st}{\expr_n}{\val_n}
+    }
+    {
+      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}
+      {\op(\expr_1, \cdots, \expr_n)}{\op(\val_1, \cdots, \val_n)}
+    }
+  \end{mathpar}
+
+  \caption{The transition relation for the core language of JavaScript}
+  \label{fig:core-trans-rel}
+\end{figure*}
+
+\begin{figure*}[t]
+  \centering
+
+  \fbox{$\viewtrans{\view}{\view'}: \absdom \rightarrow \absdom$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
+      \prog(\lab) = \refer = \expr\\
+      \referabssem{\refer}(\abselem) = L\\
+      \exprabssem{\expr}(\abselem) = \absval
+    }
+    {
+      \viewtrans{\lab}{\labnext(\lab)}(\abselem) =
+      (\absmem[L \mapstos \absval], \absctxt, \absaddr, \abscount)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
+      \prog(\lab) = \refer = \kwobj\\
+      \referabssem{\refer}(\abselem) = L\\
+      \oabsaddr = \lab
+    }
+    {
+      \viewtrans{\lab}{\labnext(\lab)}(\abselem) = (\absmem[L \mapstos \{
+      \oabsaddr \}], \absctxt, \absaddr, \inc(\abscount, \oabsaddr))
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
+      \prog(\lab) = \refer = \expr_f ( \expr_a )\\
+      \referabssem{\refer}(\abselem) = L\\
+      \fval{x}{\lab_b} \in \exprabssem{\expr_f}(\abselem)\\
+      \exprabssem{\expr_a}(\abselem) = \absval_a\\
+      \eabsaddr = \lab_b\\
+      \eabsctxt = \absctxt[\eabsaddr \mapsto \absctxt(\eabsaddr) \cup \{
+      (\absaddr, \labnext(\lab), L) \} ]
+    }
+    {
+      \viewtrans{\lab}{\lab_b}(\abselem) = (\absmem[(\eabsaddr, x) \mapsto
+      \absval_a], \eabsctxt, \eabsaddr, \inc(\abscount, \eabsaddr))
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
+      \prog(\lab) = \kwret \; \expr\\
+      \exprabssem{\expr}(\abselem) = \absval\\
+      (\rabsaddr, \lab', L) \in \absctxt(\absaddr)
+    }
+    {
+      \viewtrans{\lab}{\lab'}(\abselem) = (\absmem[L \mapstos \absval],
+      \absctxt, \rabsaddr, \abscount)
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwif \; \expr \; \lab'\\
+      \kwtrue \in \exprabssem{\expr}(\abselem)
+    }
+    {
+      \viewtrans{\lab}{\lab'}(\abselem) = \abselem
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \prog(\lab) = \kwif \; \expr \; \lab'\\
+      \kwfalse \in \exprabssem{\expr}(\abselem)
+    }
+    {
+      \viewtrans{\lab}{\labnext(\lab)}(\abselem) = \abselem
+    }
+  \end{mathpar}
+
+  \fbox{$\referabssem{\refer}: \absdom \rightarrow \powerset{\abslocset}$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)
+    }
+    {
+      \referabssem{x}(\abselem) = \{ (\absaddr, x) \}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
+      A = \exprabssem{\expr_0}(\abselem) \cap \absaddrset\\
+      S = \exprabssem{\expr_1}(\abselem) \cap \strset\\
+    }
+    {
+      \referabssem{\expr_0 [ \expr_1 ]}(\abselem) = A \times S
+    }
+  \end{mathpar}
+
+  \fbox{$\exprabssem{\expr}: \absdom \rightarrow \absvalset$}
+  \begin{mathpar}
+    \inferrule*[width=0.48\textwidth]
+    {}
+    {
+      \exprabssem{\pval}(\abselem) = \{ \pval \}
+    }
+
+    {}
+    {
+      \exprabssem{\fval{x}{\lab}}(\abselem) = \{ \fval{x}{\lab} \}
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
+      \absval = \bigjoin \{ \absmem(\absloc) \mid \absloc \in
+      \referabssem{\refer}(\abselem) \}
+    }
+    {
+      \exprabssem{\refer}(\abselem) = \absval
+    }
+
+    \inferrule*[width=0.48\textwidth]
+    {
+      \exprabssem{\expr_1}(\abselem) = \absval_1\\
+      \cdots\\
+      \exprabssem{\expr_n}(\abselem) = \absval_n
+    }
+    {
+      \exprabssem{\op(\expr_1, \cdots, \expr_n)}(\abselem) = \ops(\absval_1,
+      \cdots, \absval_n)
+    }
+  \end{mathpar}
+
+  \caption{The semantics of view transition for the core language of JavaScript}
+  \label{fig:core-view-trans}
+\end{figure*}
 
@@
 
-We formulate the concrete semantics of the core language.  The transition
-relation between concrete states is defined with the semantics of references and
-expressions using two different forms \fbox{$\referrule{\st}{\refer}{\loc}$} and
+We formulate the concrete semantics of the core language as described in
+Figure~\ref{fig:core-trans-rel}.  The transition relation between concrete
+states is defined with the semantics of references and expressions using two
+different forms \fbox{$\referrule{\st}{\refer}{\loc}$} and
 \fbox{$\exprrule{\st}{\expr}{\val}$}, respectively.  The initial states are
 $\istset = \{ (\ilab, \varnothing, \epsilon, \tladdr) \}$ where $\ilab$ denotes
-the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level environment address.
+the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level
+environment address.  The function $\labnext$ returns the next label of a
+given label in the current program $\prog$.
 
@@
 
-We define the semantics of the view transition for the core language.  For abstract
-memories, we use the notation $\absmem[L \mapstos \absval]$ to represent the
-update of multiple abstract locations in $L$ with the abstract value $\absval$.
-It performs the strong update if the abstract address for an abstract location
-$(\absaddr, \_) \in L$ is singleton: $\abscount(\absaddr) = \absone$.
-Otherwise, it performs the weak update for the analysis soundness.  We use
-the increment function $\inc: \abscountset \times \absaddrset \rightarrow
-\abscountset$ of the abstract counter defined as follows:
+We define the semantics of the view transition for the core language in
+Figure~\ref{fig:core-view-trans}.  For abstract memories, we use the notation
+$\absmem[L \mapstos \absval]$ to represent the update of multiple abstract
+locations in $L$ with the abstract value $\absval$.  It performs the strong
+update if the abstract address for an abstract location $(\absaddr, \_) \in L$
+is singleton: $\abscount(\absaddr) = \absone$.  Otherwise, it performs the weak
+update for the analysis soundness.  We use the increment function $\inc:
+\abscountset \times \absaddrset \rightarrow \abscountset$ of the abstract
+counter defined as follows:
 \[

### 2020-11-26 paper/pldi21/report/report.tex
Minor changed in report
Changed the formal definition
Modified definition
Remove duplicated package from report.tex

@@
-\documentclass[11pt]{article}
-\usepackage[a4paper,left=20mm,right=20mm,top=30mm,bottom=25mm]{geometry}
+\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
 
+\usepackage{float}
+%\usepackage{amssymb}
+\usepackage{amsmath,amsfonts}
+\usepackage[ruled, vlined]{algorithm2e}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\usepackage{listings}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{multirow}
+\usepackage{booktabs}
+\usepackage{makecell}
+\usepackage{galois}
+\usepackage{mathpartir}
+\usepackage{bussproofs}
 \usepackage{mathtools}
-\usepackage[T1]{fontenc}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{mathpartir}
-\usepackage{verbatim}
-\usepackage{hyperref}
-\usepackage{xspace}
+\usepackage{colortbl}
+\usepackage{hhline}
 \usepackage{stmaryrd}
-\usepackage{tikz}
-\usepackage{dirtree}
-\usepackage{multicol}
-\usepackage{array}
-\usepackage{galois}
-\usepackage{amsthm}
 
-\usetikzlibrary{arrows}
-\tikzset{
-  treenode/.style = {align=center, inner sep=0pt, text centered},
-  arn_n/.style = {treenode, circle, black, draw=black, text width=1.5em},
-}
+\EnableBpAbbreviations
+
+\setcopyright{acmcopyright}
+\copyrightyear{2018}
+\acmYear{2018}
+\acmDOI{10.1145/1122445.1122456}
+\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
+  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
+\acmPrice{15.00}
+\acmISBN{978-1-4503-XXXX-X/18/06}
+
+\input{../macros}
 
@@
 
-\input{macros}
+\title
+[Accelerating JavaScript Static Analysis via Dynamic Shortcuts]
+{Accelerating JavaScript Static Analysis\\ via Dynamic Shortcuts}
 
-\title{Dynamic Shortcut Soundness Proof}
+\author{Joonyoung Park}
+\affiliation{%
+  \institution{Korea Advanced Institute of Science and Technology}
+  \state{Daejeon}
+  \country{South Korea}
+}
+\email{gmb55@kaist.ac.kr}
 
-\author{Dongjun Youn$^*$ \and Jihyeok Park$^*$ \and Sukyoung Ryu$^*$}
+\author{Jihyeok Park}
+\affiliation{%
+  \institution{Korea Advanced Institute of Science and Technology}
+  \state{Daejeon}
+  \country{South Korea}
+}
+\email{jhpark0223@kaist.ac.kr}
 
-\date{$^*$KAIST, South Korea}
+\author{Dongjun Youn}
+\affiliation{%
+  \institution{Korea Advanced Institute of Science and Technology}
+  \state{Daejeon}
+  \country{South Korea}
+}
+\email{f52985@kaist.ac.kr}
+
+\author{Sukyoung Ryu}
+\affiliation{%
+  \institution{Korea Advanced Institute of Science and Technology}
+  \state{Daejeon}
+  \country{South Korea}
+}
+\email{sryu.cs@kaist.ac.kr}
+
+\renewcommand{\shortauthors}{Park and Park, et al.}
+
+\input{../abstract}
+
+\begin{CCSXML}
+<ccs2012>
+ <concept>
+  <concept_id>10010520.10010553.10010562</concept_id>
+  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+  <concept_significance>500</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10010520.10010575.10010755</concept_id>
+  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+  <concept_significance>300</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10010520.10010553.10010554</concept_id>
+  <concept_desc>Computer systems organization~Robotics</concept_desc>
+  <concept_significance>100</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10003033.10003083.10003095</concept_id>
+  <concept_desc>Networks~Network reliability</concept_desc>
+  <concept_significance>100</concept_significance>
+ </concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Computer systems organization~Embedded systems}
+\ccsdesc[300]{Computer systems organization~Redundancy}
+\ccsdesc{Computer systems organization~Robotics}
+\ccsdesc[100]{Networks~Network reliability}
+
+\keywords{JavaScript, static analysis, dynamic analysis, dynamic shortcut, sealed symbolic execution}
+
 \maketitle
 
-\input{proof}
+\input{intro}
+\input{../motivation}
+\input{../shortcut}
+\input{ds}
+\input{javascript}
+\input{../implementation}
+\input{eval}
+\input{../eval-opaque}
+\input{../related}
+\input{../conclusion}
+
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{../ref}
 
 \end{document}
+\endinput

### 2021-02-23 paper/fse21/ds.tex

--- 2020-11-26 paper/pldi21/report/ds.tex
@@
   \begin{subfigure}[t]{0.15\textwidth}
-    \includegraphics[height=3.2cm]{../img/listing}
+    \includegraphics[height=3.2cm]{img/listing}
     \caption{Notations}
@@
   \begin{subfigure}[t]{0.23\textwidth}
-    \includegraphics[height=3.2cm]{../img/path-1}
+    \includegraphics[height=3.2cm]{img/path-1}
     \caption{$\varx = 0$}
@@
   \begin{subfigure}[t]{0.28\textwidth}
-    \includegraphics[height=3.2cm]{../img/path-2}
+    \includegraphics[height=3.2cm]{img/path-2}
     \caption{$\varx > 0$}
@@
   \begin{subfigure}[t]{0.28\textwidth}
-    \includegraphics[height=3.2cm]{../img/path-3}
+    \includegraphics[height=3.2cm]{img/path-3}
     \caption{$\varx \in \mathbb{N}$}
@@
 
-To formally prove Theorem~\ref{theorem:shortcut}, we assume that its all
-conditions are hold and rephrase the \textit{soundness} as
-Theorem~\ref{theorem:soundness} and \textit{termination} as
-Theorem~\ref{theorem:termination}.
+The second and the fourth conditions provide upper bounds of
+the number of sensitive abstract states and
+the number of sealed symbolic states, respectively.
+Thus, it guarantees the termination of the analysis.
 
-\subsubsection{Soundness}
-
-\begin{theorem}[Soundness]\label{theorem:soundness}
-  The abstract interpretation using the combined domain $\combdom$ is
-  \textbf{sound} if
-  \begin{equation}\label{equ:sound-join}
-    \forall \combelem_0, \combelem_1 \in \combdom. \; \combgamma(\combelem_0) \cup
-    \combgamma(\combelem_1) \subseteq \combgamma(\combelem_0 \join \combelem_1)
-  \end{equation}
-  \begin{equation}\label{equ:sound-combstep}
-    \forall \combelem \in \combdom. \; \step \circ \combgamma(\combelem) \subseteq
-    \combgamma \circ \combstep(\combelem)\\
-  \end{equation}
-\end{theorem}
-\begin{proof}
-  First, we prove that the abstract transfer function $\combtransfer: \combdom
-  \rightarrow \combdom$ defined as $\combtransfer(\combelem) = \combelem \join
-  \combstep(\combelem)$ is sound
+For soundness proof, we should prove 
+two conditions presented in Section~\ref{sec:ai}:
+(\ref{equ:sound-join}) for the join operator $\join$ and
+(\ref{equ:sound-step}) for the combined one-step execution.
+The core idea of the proof is to use Lemma~\ref{lemma:step-symb} and
+Lemma~\ref{lemma:reform} for the sealed symbolic one-step execution
+$\symbstep$ and the $\reform$ function, respectively. Due to the page limitation, we omit
+the proof in this paper and present it in a companion report~\cite{report}.
+\begin{lemma}\label{lemma:step-symb}
+  Assume that the following condition holds:
   \[
-    \begin{array}{rcll}
-      \transfer \circ \combgamma(\combelem)
-      &=& \combgamma(\combelem) \cup \step \circ \combgamma(\combelem)\\
-      &\subseteq& \combgamma(\combelem) \cup \combgamma \circ \combstep(\combelem)
-      & (\because \; \text{condition~(\ref{equ:sound-combstep})})\\
-      &\subseteq& \combgamma(\combelem \join \combstep(\combelem))
-      & (\because \; \text{condition~(\ref{equ:sound-join})})\\
-      &=& \combgamma \circ \combtransfer(\combelem)\\
-    \end{array}
+    \forall (\absimap, \symbst) \in \symbelem. \; \exists \symbst' \in
+    \symbstset. \; \symbst \symbtrans \symbst'
   \]
-  Then, the abstract semantics $\combsem{\prog} = \underset{n \rightarrow
-  \infty}{\lim}{(\combtransfer)^n(\icombelem)} $ is also sound because it is
-  defined with a sound abstract transfer function $\combtransfer$ using the
-  combined one-step execution $\combstep$.
-\end{proof}
-
-Now, we should show that two conditions about the soundness of the join
-operator (\ref{equ:sound-join}) and the soundness of the combined one-step
-execution (\ref{equ:sound-combstep}) in Theorem~\ref{theorem:soundness} hold.
-
-First, we prove the soundness of the join operator (\ref{equ:sound-join}) in
-Lemma~\ref{lemma:sound-join}.
-\begin{lemma}[Soundness of $\join$]\label{lemma:sound-join}
+  then the following property holds:
   \[
-    \forall \combelem_0, \combelem_1 \in \combdom. \; \combgamma(\combelem_0) \cup
-    \combgamma(\combelem_1) \subseteq \combgamma(\combelem_0 \join \combelem_1)
+    \step \circ \symbgamma(\symbelem) \subseteq
+    \symbgamma \circ \symbstep(\symbelem)\\
   \]
 \end{lemma}
-\begin{proof}
-  \[
-    \begin{array}{cl}
-      \multicolumn{2}{l}{
-        \combgamma((\sabselem, \symbelem)) \cup \combgamma((\sabselem', \symbelem'))
-      }\\
-      =& \sgamma(\sabselem) \cup \symbgamma(\symbelem)
-      \cup \sgamma(\sabselem') \cup \symbgamma(\symbelem')\\
-      =& (\sgamma(\sabselem)\cup \sgamma(\sabselem'))
-      \cup (\symbgamma(\symbelem) \cup \symbgamma(\symbelem'))\\
-      \subseteq& \sgamma(\sabselem \join \sabselem')
-      \cup (\symbgamma(\symbelem) \cup \symbgamma(\symbelem'))\\
-      & \multicolumn{1}{r}{(\because \; \sabsdom \; \text{is sound})}\\
-      =& \sgamma(\sabselem \join \sabselem')
-      \cup \symbgamma(\symbelem \cup \symbelem')\\
-      =& \combgamma((\sabselem \join \sabselem', \symbelem \cup \symbelem'))\\
-      =& \combgamma((\sabselem, \symbelem) \join (\sabselem', \symbelem'))\\
-    \end{array}
-  \]
-\end{proof}
-
-For the condition (\ref{equ:sound-combstep}), we first prove two properties of the
-$\reform$ function in Lemma~\ref{lemma:reform}.  Using the properties, we prove
-the soundness of the sealed symbolic one-step execution in
-Lemma~\ref{lemma:sound-symbstep}.  Finally, we prove the soundness of the
-combined one-step execution (\ref{equ:sound-combstep}) in
-Lemma~\ref{lemma:sound-combstep}.
-
-\begin{lemma}[Properties of $\reform$]\label{lemma:reform}
+\begin{lemma}\label{lemma:reform}
   For a given combined state $\combelem \in \combdom$, the $\reform$ function
@@
 \end{lemma}
-\begin{proof}
-  \[
-    \fbox{$\combgamma(\combelem) \subseteq \combgamma \circ \reform(\combelem)$}
-  \]
-  \[
-    \begin{array}{cl}
-      \multicolumn{2}{l}{\combgamma((\sabselem, \symbelem))}\\
-      =& \sgamma(\sabselem) \cup \symbgamma(\symbelem)\\
-
-      =& \left( \underset{\view \in \viewset}{\bigcup} {\viewmap(\view) \cap
-      \gamma \circ \sabselem(\view)} \right) \cup \left( \underset{(\absimap,
-      \symbst) \in \symbelem}{\bigcup} \instant{\symbst}{\absimap} \right) \\
-
-      =& \left( \underset{\view \in \viewset}{\bigcup} \aelemgamma((\view,
-      \sabselem(\view))) \right) \cup \left( \underset{(\absimap, \symbst) \in
-      \symbelem}{\bigcup} \aelemgamma((\absimap, \symbst)) \right) \\
-
-      =& \dot\aelemgamma(\{ (\view, \sabselem(\view)) \mid \view \in \viewset \}
-      \cup \symbelem)\\
-
-      =& \dot\aelemgamma(\dot{\areform}(\{ (\view, \sabselem(\view)) \mid \view
-      \in \viewset \} \cup \symbelem))\\
-
-       & \multicolumn{1}{r}{\because \; (\text{Trivially,} \; \forall \aelem \in
-       \aelemset.  \; \aelemgamma(\aelem) = \aelemgamma \circ \areform(\aelem))}\\
-
-      =& \dot\aelemgamma(E)\\
-       & \multicolumn{1}{r}{\because \; (\text{See the definition of $E$ in
-       Definition~\ref{def:reform}})}\\
-    \end{array}
-  \]
-  \[
-    \begin{array}{cl}
-      =& \left( \underset{(\view, \abselem) \in E}{\bigcup} \aelemgamma((\view,
-      \abselem)) \right) \cup \left( \underset{(\absimap, \symbst) \in
-      E}{\bigcup} \aelemgamma((\absimap, \symbst)) \right)\\
-
-      =& \left( \underset{(\view, \abselem) \in E}{\bigcup} \viewmap(\view) \cap
-      \gamma(\abselem) \right) \cup \left( \underset{(\absimap, \symbst) \in
-      E}{\bigcup} \instant{\symbst}{\absimap} \right)\\
-
-      =& \left( \underset{\view \in \viewset}{\bigcup} { \underset{(\view,
-      \abselem) \in E}{\bigcup} \viewmap(\view) \cap \gamma(\abselem) } \right)
-      \cup \left( \underset{(\absimap, \symbst) \in E}{\bigcup}
-      \instant{\symbst}{\absimap} \right)\\
-
-      =& \left( \underset{\view \in \viewset}{\bigcup} {\viewmap(\view) \cap
-        \left(\underset{(\view, \abselem) \in
-      E}{\bigcup}{\gamma(\abselem)}\right)} \right) \cup \left(
-      \underset{(\absimap, \symbst) \in E}{\bigcup} \instant{\symbst}{\absimap}
-      \right)\\
-
-      \subseteq& \left( \underset{\view \in \viewset}{\bigcup} {\viewmap(\view)
-        \cap \gamma\left( \underset{(\view, \abselem) \in E}{\bigjoin}\abselem
-      \right)} \right) \cup \left( \underset{(\absimap, \symbst) \in E}{\bigcup}
-      \instant{\symbst}{\absimap} \right)\\
-
-      =& \sgamma\left( \lambda \view. \underset{(\view, \abselem) \in
-      E}{\bigjoin}\abselem \right) \cup \symbgamma(E \cap (\absimapset \times
-      \symbstset))\\
-
-      =& \combgamma\left( \lambda \view. \underset{(\view, \abselem) \in
-      E}{\bigjoin}\abselem, E \cap (\absimapset \times \symbstset) \right)\\
-
-      =& \combgamma \circ \reform((\sabselem, \symbelem))
-    \end{array}
-  \]
-  \[\]
-  \[
-    \fbox{$\forall (\absimap, \symbst) \in \symbelem. \; \exists \symbst' \in
-    \symbstset.  \; \text{s.t.} \; \symbst \symbtrans \symbst'$}
-  \]
-
-  For a given $(\absimap, \symbst) \in \symbelem$, there exists an analysis
-  element $\aelem \in \aelemset$ such that $\areform(\aelem) = (\absimap,
-  \symbst)$.  According to the definition of $\areform$ in
-  Definition~\ref{def:areform}, there are two possible cases: $\aelem =
-  (\absimap, \symbst) \wedge \exists \symbst' \in \symbstset. \; \text{s.t} \;
-  \symbst \symbtrans \symbst'$ or $\aelem = (\view, \abselem) \wedge \aelem \in
-  \Dom(\asconverter)$. We separately consider those two cases:
-  \begin{itemize}
-    \item $\aelem = (\absimap, \symbst) \wedge \exists \symbst' \in \symbstset.
-      \; \text{s.t} \; \symbst \symbtrans \symbst'$\\
-        By definition, $\exists \symbst' \in \symbstset.  \; \text{s.t} \;
-        \symbst \symbtrans \symbst'$
-    \item $\aelem = (\view, \abselem) \wedge \aelem \in \Dom(\asconverter)$\\
-      By the condition~\ref{equ:asc-cond} in the Theorem~\ref{theorem:shortcut},\\
-      $\exists k > 1. \symbst \symbtrans^k \excst$.  Thus, $\exists \symbst' \in
-      \symbstset.  \; \text{s.t} \; \symbst \symbtrans \symbst'$
-  \end{itemize}
-\end{proof}
-
-\begin{lemma}[Soundness of $\symbstep$]\label{lemma:sound-symbstep}
-  The sealed symbolic one-step execution $\symbstep$ is sound:
-  \[
-    \step \circ \symbgamma(\symbelem) \subseteq
-    \symbgamma \circ \symbstep(\symbelem)\\
-  \]
-\end{lemma}
-\begin{proof}
-  \[
-    \begin{array}{cl}
-      \multicolumn{2}{l}{\step \circ \symbgamma(\symbelem)}\\
-      =& \step(\bigcup \{ \instant{\symbst}{\absimap} \mid (\absimap, \symbst) \in
-      \symbelem\})\\
-      =& \{ \st' \mid (\absimap, \symbst) \in \symbelem \wedge \st \in
-      \instant{\symbst}{\absimap} \wedge \st \trans \st'\})\\
-      =& \{ \st' \mid (\absimap, \symbst) \in \symbelem \wedge \imap \in
-      \imapgamma(\absimap) \wedge \instant{\symbst}{\imap} \trans \st'\})\\
-      =& \{ \st' \mid (\absimap, \symbst) \in \symbelem \wedge \imap \in
-      \imapgamma(\absimap) \wedge \instant{\symbst}{\imap} \trans \st'\\
-       & \phantom{\{ \st' \mid (\absimap, \symbst) \in \symbelem \wedge \imap \in
-      \imapgamma(\absimap)} \wedge \symbst \symbtrans \symbst' \})\\
-       & \multicolumn{1}{r}{(\because \; \text{Second property in
-       Lemma~ref{lemma:reform}})}\\
-      =& \{ \instant{\symbst'}{\imap} \mid (\absimap, \symbst)
-      \in \symbelem \wedge \imap \in \imapgamma(\absimap) \wedge \symbst
-      \symbtrans \symbst'\}\\
-      & \multicolumn{1}{r}{(\because \; \text{Validity of} \; \symbtrans)}\\
-      =& \bigcup \{ \instant{\symbst'}{\absimap} \mid (\absimap, \symbst)
-      \in \symbelem \wedge \symbst \symbtrans \symbst' \}\\
-      =& \symbgamma(\{ (\absimap, \symbst') \mid (\absimap, \symbst)
-      \in \symbelem \wedge \symbst \symbtrans \symbst' \})\\
-      =& \symbgamma \circ \symbstep(\symbelem)\\
-    \end{array}
-  \]
-\end{proof}
-
-\begin{lemma}[Soundness of $\combstep$]\label{lemma:sound-combstep}
-  The combined one-step execution $\combstep$ is sound:
-  \[
-    \forall \combelem \in \combdom. \; \step \circ \combgamma(\combelem) \subseteq
-    \combgamma \circ \combstep(\combelem)\\
-  \]
-\end{lemma}
-\begin{proof}
-  \[
-    \begin{array}{cl}
-      \multicolumn{2}{l}{
-        \step \circ \combgamma(\combelem)
-      }\\
-      \subseteq& \step \circ \combgamma((\sabselem, \symbelem))\\
-       & \multicolumn{1}{r}{(\because \; \text{First property in
-       Lemma~\ref{lemma:reform}}}\\
-       & \multicolumn{1}{r}{\text{where} \; (\sabselem, \symbelem)
-       = \reform(\combelem).)}\\
-
-      =& \step(\sgamma(\sabselem) \cup \symbgamma(\symbelem))\\
-      =& \step(\sgamma(\sabselem)) \cup \step(\symbgamma(\symbelem))\\
-      \subseteq& \sgamma \circ \sabsstep(\sabselem) \cup \step(\symbgamma(\symbelem))\\
-      & \multicolumn{1}{r}{(\because \; \sabsstep \; \text{is sound.})}\\
-      \subseteq& \sgamma \circ \sabsstep(\sabselem) \cup \symbgamma \circ
-      \symbstep((\symbelem))\\
-               & \multicolumn{1}{r}{(\because \; \text{and
-               Lemma~\ref{lemma:sound-symbstep}})}\\
-      =& \combgamma((\sabsstep(\sabselem), \symbstep(\symbelem)))\\
-      =& \combgamma \circ \combstep(\combelem)\\
-    \end{array}
-  \]
-\end{proof}
-
-\subsection{Termination}
-
-Before proving the termination of the abstract interpretation using the combined
-domain $\combdom$, we define several notations. The initial abstract state
-$\icombelem = (\isabselem, \varnothing)$ is pair of the initial abstract state of
-the sensitive abstract domain $\sabsdom$ and an empty set. For each iteration $i
-\geq 0$, we define the $i$-th result of abstract interpretation
-$\combtransfer^i(\icombelem) = \combelem^i = (\sabselem^i, \symbelem^i)$ and the
-\textit{difference set} $\diffset_i = \symbelem^{i+1} \setminus \symbelem^i$.
-For simplicity, we define $\diffset_i$ as $\varnothing$ for $i < 0$.  Moreover, we
-define a lifted version of sealed symbolic relation $\liftsymbtrans \subseteq
-(\absimapset \times \symbstset) \times (\absimapset \times \symbstset)$ as
-follows:
-\[
-  (\absimap, \symbst) \liftsymbtrans (\absimap, \symbst') \Leftrightarrow
-  \symbst \symbtrans \symbst'
-\]
-Using the lifted relation, we define the \textit{time to live (TTL)} function of
-symbolic states $\ttl_i: \diffset_i \rightarrow \numset$ for each iteration $i
-\geq 0$ as follows:
-\begin{definition}[TTL Function]
-  \[
-    \begin{array}{c}
-      \ttl_i(\symbaelem) = \left \{
-      \begin{array}{l}
-        N - 1 \;\; ( \text{if} \; D = \varnothing)\\
-        \text{min}(\dot\ttl_{i-1}(D)) - 1
-        \;\; ( \text{otherwise})
-      \end{array}
-      \right. \\
-      \\
-      \text{where} \; D =
-      \{\symbaelem' \in \diffset_{i-1} \mid \symbaelem' \liftsymbtrans \symbaelem\}
-    \end{array}
-  \]
-\end{definition}
-
-Based on the notations, we formally prove the termination property as folows:
-\begin{theorem}[Termination]\label{theorem:termination}
-  The abstract interpretation using the combined domain $\combdom$
-  \textbf{terminates} in a finite time if
-  \begin{equation}\label{equ:termination-sai}
-    \exists n. \; \forall m \geq n. \; \sabselem^m = \sabselem^n
-  \end{equation}
-  \begin{equation}\label{equ:bounded-ttl}
-    \forall i \geq 0. \; \forall \symbaelem \in \diffset_i. \;
-    0 < \ttl_i(\symbaelem) < N
-  \end{equation}
-  \begin{equation}\label{equ:dec-ttl}
-    \begin{array}{c}
-      \forall i > 0. \; \sabselem^{i-1} = \sabselem^i \Rightarrow\\
-      \sup(\dot \ttl_i(\diffset_i)) \leq \sup(\dot \ttl_{i-1}(\diffset_{i-1})) - 1
-    \end{array}
-  \end{equation}
-\end{theorem}
-
-\begin{proof}
-  By the condition (\ref{equ:termination-sai}), there exists $n \in \numset$
-  such that $\sabselem^m = \sabselem^n$ for all $m \geq n$.  By the condition
-  (\ref{equ:bounded-ttl}), the TTL of each symbolic state in $\diffset_n$ is
-  bounded by $N$:
-  \[
-    \sup(\dot \ttl_n(\diffset_n)) < N
-  \].
-  Then, the upper bound of TTL for symbolic states in each difference set after
-  the $n-$th iteration is decreased by the condition (\ref{equ:dec-ttl}):
-  \[
-    \forall i > 0. \; \sup(\dot \ttl_{n+i}(\diffset_{n+i})) \leq \sup(\dot
-    \ttl_{n+i-1}(\diffset_{n+i-1})) - 1
-  \].
-  which implies that
-  \[
-    \sup(\dot \ttl_{n+i}(\diffset_{n+i})) \leq \sup(\dot \ttl_n(\diffset_n)) - i < N - i
-  \]
-  Therefore, for $j \geq N$,
-  \[
-    \sup(\dot \ttl_{n+j}(\diffset_{n+j})) < N - j \leq 0
-  \]
-  Notice that again by the condition (\ref{equ:bounded-ttl}),
-  \[
-    inf(\dot \ttl_{n+j}(\diffset_{n+j})) > 0
-  \]
-  meaning that
-  \[
-    inf(\dot \ttl_{n+j}(\diffset_{n+j})) > \sup(\dot \ttl_{n+j}(\diffset_{n+j}))
-  \]
-  which implies $\diffset_{n+j} = \varnothing$ and $\symbelem^{n+j+1} =
-  \symbelem^{n+j}$.
-  Therefore, for all $m \geq n + N$,
-  \[
-    \sabselem^m = \sabselem^{n+N} \wedge \symbelem^m = \symbelem^{n+N}
-  \]
-  and
-  \[
-    \combelem^m = \combelem^{n+N}
-  \]
-  which means the abstract interpretation using the combined domain
-  $\combdom$ terminates in $n+N$ iterations.
-\end{proof}
-
-Now, we should show that three conditions about the termination of the sensitive
-abstract interpretation (\ref{equ:termination-sai}), the bound of TTL for
-symbolic states in difference sets (\ref{equ:bounded-ttl}), and the decrease of
-their upper bounds (\ref{equ:dec-ttl}) in Theorem~\ref{theorem:termination}
-hold.
-
-First, we prove the termination of the sensitive abstract interpretation
-(\ref{equ:termination-sai}) in Lemma~\ref{lemma:termination-sai}.
-
-\begin{lemma}[Termination of Sensitive Abstract Interpretation]\label{lemma:sabs-term}
-\label{lemma:termination-sai}
-  \[
-    \exists n. \; \forall m \geq n. \;
-    \sabselem^m = \sabselem^n
-  \]
-\end{lemma}
-
-\begin{proof}
-Note that for all $\sabselem, \sabselem' \in \sabsdom$ that satisfies
-$\combtransfer((\sabselem, \_)) = (\sabselem', \_)$,
-\[
-  \begin{array}{rcl}
-  \combtransfer((\sabselem, \_))
-  &=& (\sabselem, \_) \join \combstep((\sabselem, \_))\\
-  &=& (\sabselem, \_) \join (\_, \_) = (\sabselem \join \_, \_)\\
-  &=& (\sabselem', \_)
-  \end{array}
-\]
-which implies $\sabselem \order \sabselem'$.  Since
-$\combtransfer((\sabselem^i, \_)) = (\sabselem^{i+1}, \_), \sabselem^i \order
-\sabselem^{i+1}$ holds for all $i \geq 0$.  Then, $\sabselem^0 \order \sabselem^1
-\order \sabselem^2 \cdots$ is an ascending chain.  Since the height of the
-sensitive abstract domain $\sabsdom$ is finite, the ascending chain condition is
-also hold. Therefore, there exists n such that for all $m \geq n, \sabselem^m =
-\sabselem^n$.
-\end{proof}
-
-Then, we prove two remaining conditions (\ref{equ:bounded-ttl}) and
-(\ref{equ:dec-ttl}).  We first prove two properties of difference sets in
-Lemma~\ref{lemma:diffset_prop} and Corollary~\ref{corollary:only-from-diffset},
-and a property of TTL in Lemma~\ref{lemma:prop-ttl}.  Using them, we prove the
-bound of TTL for symbolic states in difference sets (\ref{equ:bounded-ttl}) in
-Corollary~\ref{corollary:bounded-ttl} and the decrease of their upper bounds
-(\ref{equ:dec-ttl}) in Lemma~\ref{lemma:dec-ttl}.
-
-\begin{lemma}\label{lemma:diffset_prop}
-  \[
-    \begin{array}{c}
-      \forall i \geq 0. \; \forall \symbaelem \in \diffset_i. \\
-      \exists \view. \; \asconverter((\view,\sabselem^i(\view))) \liftsymbtrans \symbaelem 
-      \lor \exists \symbaelem' \in \diffset_{i-1} . \; \symbaelem' \liftsymbtrans \symbaelem
-    \end{array}
-  \]
-\end{lemma}
-\begin{proof}
-  Let $i \in \numset$ and $\symbaelem \in \diffset_i = \symbelem^{i+1} \setminus \symbelem^i$ given.
-  By definition,
-  \[
-    \symbelem^{i+1} = \symbelem^i \cup \symbstep({\symbelem^i}')
-  \]
-  where
-  \[
-    (\_, {\symbelem^i}') = \reform(\sabselem^i, \symbelem^i)
-  \]
-  Note that $\symbaelem \in \symbstep({\symbelem^i}')$,
-  and by definition of $\symbstep$, there exists some
-  $\symbaelem' \in {\symbelem^i}'$ that satisfies $\symbaelem' \liftsymbtrans \symbaelem$.
-  Now, by definition of $\reform$,
-  \[
-    {\symbelem^i}' =
-    \dot{\areform}(\{ (\view, \sabselem^i(\view)) \mid \view \in \viewset \} \cup \symbelem^i)
-    \cap (\absimapset \times \symbstset)
-  \]
-  This means there exists
-  $\aelem \in \{ (\view, \sabselem^i(\view)) \mid \view \in \viewset \} \cup \symbelem^i$
-  that satisfies $\areform(\aelem) = \symbaelem'$. We have two possible cases for $\aelem$.
-  \begin{itemize}
-
-  \item $\aelem \in \{ (\view, \sabselem^i(\view)) \mid \view \in \viewset \}$
-
-  In this case, $\areform(\aelem) = \asconverter(\aelem) = \symbaelem'$
-  and the left condition for conclusion is satisfied.
-
-  \item $\aelem \in \symbelem^i$
-
-  In this case, $\areform(\aelem) = \aelem = \symbaelem'$.
-  Now, let's assume that $\aelem \in \symbelem^{i-1}$.
-  In that case, $\aelem$ would be preserved after reform step, that is,
-  $\aelem \in {\symbelem^{i-1}}'$. Then, by definition of $\symbstep$,
-  $\symbaelem \in \symbstep({\symbelem^{i-1}}') \subseteq \symbelem^i$
-  whcih contradicts to the fact that $\symbaelem \in \diffset_i$.
-  Therefore, $\aelem \notin \symbelem^{i-1}$, that is,
-  $\aelem \in \symbelem^i \setminus \symbelem^{i-1} = \diffset_i$,
-  and the right condition for conclusion is satisfied.
-  \end{itemize}
-\end{proof}
-
-\begin{corollary}\label{corollary:only-from-diffset}
-  \[
-    \begin{array}{c}
-      \forall i > 0. \; \sabselem^{i-1} = \sabselem^i \Rightarrow
-      \forall \symbaelem \in \diffset_i. \\
-      \exists \symbaelem' \in \diffset_{i-1} . \; \symbaelem' \liftsymbtrans \symbaelem
-    \end{array}
-  \]
-\end{corollary}
-\begin{proof}
-  The proof goes same as the previous lemma, until the point where we divide
-  the case for $\aelem$. Let's assume that the first case holds, that is,
-  \[
-    \aelem \in \{ (\view, \sabselem^i(\view)) \mid \view \in \viewset \}
-  \]
-  Since $\sabselem^{i-1} = \sabselem^i$,
-  \[
-    \aelem \in \{ (\view, \sabselem^{i-1}(\view)) \mid \view \in \viewset \}
-  \]
-  In that case, $\aelem$ would be transformed after reform step, that is,
-  $\asconverter(\aelem) = \symbaelem' \in {\symbelem^{i-1}}'$.
-  Then, by definition of $\symbstep$,
-  $\symbaelem \in \symbstep({\symbelem^{i-1}}') \subseteq \symbelem^i$
-  whcih contradicts to the fact that $\symbaelem \in \diffset_i$.
-  Therefore, only second case holds and the right conclusion in previus lemma is satisfied.
-\end{proof}
-
-\begin{lemma}[Property of TTL]\label{lemma:prop-ttl}
-  \[
-    \begin{array}{c}
-      \forall i \geq 0. \; \forall \symbaelem \in \diffset_i.
-      \ttl_i(\symbaelem) = k \Rightarrow \\
-      k < N \wedge
-      \exists (\view, \abselem). \; (\asconverter((\view,\abselem))
-      \liftsymbtrans^{(N - k)} \symbaelem) \\
-    \end{array}
-  \]
-\end{lemma}
-\begin{proof}
-  We prove by induction on $i$.
-  Let $\symbaelem \in \diffset_i$.
-  \begin{itemize}
-  \item If $i = 0$, $\ttl_0(\symbaelem) = N - 1 < N$
-  and since only left conclusion of lemma~\ref{lemma:diffset_prop} can hold,
-  there eixsts view $\view$ s.t.
-  $\asconverter(\view, \sabselem^0(\view)) \liftsymbtrans^1 \symbaelem$.
-  \item If $i > 0$, we have two cases for $D = 
-    \{\symbaelem' \in \diffset_{i-1} \mid \symbaelem' \liftsymbtrans \symbaelem\}$.
-  If $D = \varnothing$, the argument is similar as $i = 0$ case.
-  Otherwise, let $\symbaelem' = \underset{\x \in D}{argmin}{\ttl_{i-1}(x)}$.
-
-  By induction hypothesis, we have
-  \[
-    k' = \ttl_{i-1}(\symbaelem') < N
-  \]
-  and there eixsts $(\view, \abselem)$ such that
-  \[
-    \symbaelem'' = \asconverter((\view,\abselem)) \liftsymbtrans^{(N - k')} \symbaelem'.
-  \]
-  By definition of $\ttl_i$,
-  $\ttl_i(\symbaelem) = \ttl_i(\symbaelem') - 1$, and $k = k' - 1$.
-  Then,
-  \[
-    k = k' - 1 < N - 1 < N
-  \]
-  and
-  $\symbaelem'' \liftsymbtrans^{(N - k - 1)} \symbaelem'$ with
-  $\symbaelem' \liftsymbtrans \symbaelem$ implies that
-  \[
-    \symbaelem'' \liftsymbtrans^{(N - k)} \symbaelem.
-  \]
-  \end{itemize}
-\end{proof}
-\begin{corollary}\label{corollary:bounded-ttl}
-  \[
-    \forall i \geq 0. \; \forall \symbaelem \in \diffset_i. \;
-    0 < \ttl_i(\symbaelem) < N
-  \]
-\end{corollary}
-\begin{proof}
-We already proved $k = \ttl_i(\symbaelem) < N$.
-Now, let's assume that $k \leq 0$.
-By previous lemma, there exists $(\view, \abselem)$ such that
-\[
-  (\asconverter((\view,\abselem)) \liftsymbtrans^{(N - k)} \symbaelem)
-\]
-Since $N - k \geq N$, this implies that there exists $\symbaelem'$ such that
-\[
-  (\asconverter((\view,\abselem)) \liftsymbtrans^N \symbaelem')
-\]
-However, this contradicts to the condition~(\ref{equ:asc-cond}) of $\asconverter$ that says
-if $(\view,\abselem)$ is in domain of $\asconverter$,
-the number of possible $\symbtrans$ from state of $\asconverter((\view,\abselem))$
-is at most $N - 1$.
-Therefore, $k > 0$.
-\end{proof}
-
-\begin{lemma}\label{lemma:dec-ttl}
-  \[
-    \begin{array}{c}
-      \forall i > 0. \; \sabselem^{i-1} = \sabselem^i \Rightarrow \\
-      \sup(\dot \ttl_i(\diffset_i)) \leq \sup(\dot \ttl_{i-1}(\diffset_{i-1})) - 1
-    \end{array}
-  \]
-\end{lemma}
-\begin{proof}
-  Let $\symbaelem \in \diffset_i$.
-  By Corollary~\ref{corollary:only-from-diffset}, the set
-  \[
-    D = \{\symbaelem' \in \diffset_{i-1} \mid \symbaelem' \liftsymbtrans \symbaelem\}
-  \]
-  is non-empty, and for some $\symbaelem' \in \diffset_{i-1}$,
-  \[
-    \ttl_i(\symbaelem) = \ttl_{i-1}(\symbaelem') - 1 \leq \sup(\dot \ttl_{i-1}(\diffset_{i-1})) - 1
-  \]
-  Since it holds for every $\symbaelem \in \diffset_i$,
-  \[
-    \sup(\dot \ttl_i(\diffset_i)) \leq \sup(\dot \ttl_{i-1}(\diffset_{i-1})) - 1
-  \]
-\end{proof}

### 2021-02-24 paper/fse21/eval.tex
Revising the paper.

--- 2020-11-21 paper/pldi21/eval.tex
@@
 tests, the average analysis time is 49.57 seconds for no-DS and 2.78 seconds for
-DS.  Since only few tests analyzed in 2 to 5 minutes (8 tests for no-DS
-and no tests for DS), we only show the results within 2 minutes on the
-cumulative distribution charts to show the difference between their results more
-clearly.  Among 200 tests analyzed by no-DS, two tests are timeout in DS, thus
+DS.  Among 200 tests analyzed by no-DS, two tests are timeout in DS, thus
 198 tests are analyzable by both analyzers. For them, we depict the box plot for
@@
 Figure~\ref{fig:abs-analysis-time} shows the analysis time of the abstracted tests.
-Only four tests for no-DS and nine tests for DS are finished between 2 to 5 minutes.
 Among 269 abstracted tests, no-DS finished analysis of 158 tests within 5 minutes,
@@
 \begin{table*}[t]
-  \caption{Number of original and abstracted tests using dynamic shortcuts
+  \caption{Number of original (orig.) and abstracted (abs.) tests using dynamic shortcuts
 only for each JavaScript built-in library}

### 2021-02-24 paper/fse21/intro.tex
Added the latex template for FSE21..
Revising the paper.

--- 2020-11-26 paper/pldi21/report/intro.tex
@@
   \centering
-  \includegraphics[width=\linewidth]{../img/performance_v8v7}
+  \includegraphics[width=\linewidth]{img/performance_v8v7}
   \vspace*{-2em}
@@
 To alleviate these problems, researchers have leveraged
-dynamic analysis during static analysis.  Because dynamic
+dynamic analysis during static analysis.  \inred{Because dynamic
 analyzers such as Jalangi~\cite{jalangi} and DLint~\cite{dlint} run on
-highly-optimized commercial JavaScript engines, they are much faster than
-static analyzers.  Figure~\ref{fig:performance} shows that the dynamic analyzer
+highly-optimized commercial JavaScript engines while static analyzers run on
+their own interpreters, that leads to a great gap in performance.}
+Figure~\ref{fig:performance} shows that the dynamic analyzer
 Jalangi is 34.8x faster than the static analyzer SAFE for a subset of the
-SunSpider benchmark.  Using high performance dynamic analysis, researchers have
+SunSpider benchmark \inred{that is input-independent and deterministic}.
+Using high performance dynamic analysis, researchers have
 reduced the scope of static analysis~\cite{determinacy, blendedJS} and constructed

### 2021-02-24 paper/fse21/motivation.tex
Revising the paper.

--- 2020-11-21 paper/pldi21/motivation.tex
@@
 the most popular npm package\footnote{https://www.npmjs.com/browse/depended}
-and 124,287 npm packages have a dependency on it.
+and 131,517 npm packages have a dependency on it.
 The \jscode{concat} function creates a new array concatenating given arrays or values.
@@
 It is the homepage of Zoom, which is a videotelephony software program developed by Zoom
-Video Communications and it is ranked as the 14th popular web site according
-to Alexa\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.
+Video Communications and it is ranked as the 15th popular web site according
+to Alexa\footnote{https://www.alexa.com/siteinfo/zoom.us} in February 2021.
 

### 2021-02-24 paper/fse21/related.tex
Fixed typos.

--- 2020-11-21 paper/pldi21/related.tex
@@
 \section{Related Work}\label{sec:related}
-Researchers have introduced various technique to utilize dynamic
+Researchers have introduced various techniques to utilize dynamic
 analysis for static analysis in three ways: combined analysis,
@@
 to switch to static analysis to use abstract semantics for abstract values.
-Finally, \concerto preserves the soundness when a program satisfies
+Finally, \concerto\ preserves the soundness when a program satisfies
 the \textit{state separation hypothesis}.  It assumes that the states
@@
 the event handler with the abstract state.
-Unfortunately, all the above mentioned approaches do not preserve
+Unfortunately, all the above mentioned approaches except~\cite{determinacy} do not preserve
 soundness of static analysis unlike our approach using dynamic shortcuts.

### 2021-02-24 paper/fse21/shortcut.tex
Fixed typos.

--- 2020-11-21 paper/pldi21/shortcut.tex
@@
 abs-interp-1992} and views-based analysis sensitivity of \citet{sens-toplas}.
-For dynamic shortcuts, we define sealed symbolic execution and \inred{extend it to} a
-sealed symbolic domain with abstract instantiation maps.  To combine
+For dynamic shortcuts, we define sealed symbolic execution with a
+sealed symbolic domain and abstract instantiation maps.  To combine
 sensitive abstract interpretation and sealed symbolic execution, we define
 a combined domain of sensitive abstract domain and sealed symbolic domain and
-explain it with a simple example. Finally, We prove the soundness and
+explain it with a simple example. Finally, we prove the soundness and
 termination property of abstract interpretation using the combined domain.
@@
   \abselem_1) \label{equ:sound-join}\\
-  \forall \abselem \in \absdom & . \; \absstep \circ \gamma(\abselem) \subseteq
+  \forall \abselem \in \absdom & . \; \step \circ \gamma(\abselem) \subseteq
   \gamma \circ \absstep(\abselem) \label{equ:sound-step}
@@
 in a unique view: $\forall \st \in \stset. \; \st \in \viewmap(\view)
-\Rightarrow \not\exists \view' \in \viewset.$ s.t. $\st \in \viewmap(\view')$.
+\Rightarrow \forall \view' \in \viewset. \st \in \viewmap(\view') \Rightarrow \view = \view'$.
 A \textit{sensitive state

### 2021-02-24 paper/fse21/implementation.tex
Changed Optimization to Function-Level Dynamic Shortcut.

--- 2020-11-21 paper/pldi21/implementation.tex
@@
 
-\paragraph{Sealed Symbolic Values.}
+\paragraph{Sealed Values.}
 The main challenge of implementing dynamic shortcuts is to support sealed
@@
 
-\paragraph{Optimizations.}
-To use dynamic shortcuts, the static analyzer should communicate with the
-dynamic analyzer by passing abstract states and receiving results of sealed
-symbolic execution.  When abstract states are massive, sending
-abstract states and receiving sealed symbolic values as they are could
-incur large performance overhead.  Thus, we
-implemented mark-and-sweep garbage collection to remove unreachable
-information in abstract states.  In addition, because abstract values
-themselves are not used in sealed symbolic execution, we make a map
-from unique identifiers to abstract values and replace
-abstract values with their unique identifiers when we convert abstract
-values to sealed symbolic values.  Therefore, the dynamic analyzer
-receives only identifiers of abstract values and wraps them as
-\jscode{Proxy} objects.  After finishing sealed symbolic execution,
-the static analyzer recovers the abstract values in the results of
-sealed symbolic execution by replacing unique identifiers with their
-corresponding abstract values.
+\paragraph{Function-Level Dynamic Shortcut.}
+The dynamic shortcut is activated when the current abstract state passes the
+filter $\checker$.  If the filter tolerantly admits the dynamic shortcut, the
+analysis may suffer from the frequent communication between static and dynamic
+analyzers.  To adjust the burden of communication, we only activate new
+dynamic shortcut in function entries and deactivate it in the corresponding
+function exits thus $\tool$ supports only \textit{function-level} dynamic
+shortcut.
 
@@
 5 seconds as the time limit for each sealed symbolic execution.
-
-% \paragraph{Function-Level Dynamic Shortcut.}
-% The dynamic shortcut is activated when the current abstract state passes the
-% filter $\checker$.  If the filter tolerantly admits the dynamic shortcut, the
-% analysis suffers from the frequent communication between static and dynamic
-% analyzers.  To diminish the burden of communication, we only activate new
-% dynamic shortcut in function entries thus $\tool$ supports only
-% \textit{function-level} dynamic shortcut.  Moreover, the filter $\checker$
-% should pass only when the given abstract state terminates in a bound time.
-% Since it is difficult to staticaly check its termination, we just performs the
-% sealed symbolic exeuction with a time limit and we use 5 minutes time
-% limit for experiments.  Thus, a sealed symbolic execution introduced by a
-% function \jscode{f} terminates when it 1) meets the exit of the function
-% \jscode{f}, 2) accesses the inside of sealed symbolic values, or 3) runs over
-% the time limit.
 

### 2021-02-24 paper/fse21/abstract.tex
Color undefined numbers in red

--- 2020-11-21 paper/pldi21/abstract.tex
@@
 269 official tests of Lodash 4 library.
-Our experiment shows that $\tool$ is \inred{6.30}x faster than the
+Our experiment shows that $\tool$ is \inred{6.30}$\x$ faster than the
 baseline static analyzer, and it improves the precision to
-detect 6 more dead branches on average by using sealed symbolic execution for
+\inred{reduce assertion fails by 12\% on average} by using sealed symbolic execution for
 \inred{12} opaque functions.

### 2021-02-24 paper/fse21/eval-opaque.tex
Color undefined numbers in red

--- 2020-11-21 paper/pldi21/eval-opaque.tex
@@
 static analysis.  Table~\ref{table:func-replace} summarizes the result.
-For 263 original tests and 167 abstracted tests that DS finished analysis, we measured the
+For \inred{263} original tests and \inred{167} abstracted tests that DS finished analysis, we measured the
 number of tests that use only dynamic shortcuts instead of manual modeling
@@
 For example, the first row in the leftmost side describes that \jscode{Array} is used in
-203 original tests and 116 abstracted tests.  Among them, 203 original
-tests and 90 abstracted tests are successfully analyzed by using dynamic shortcuts
+\inred{203} original tests and \inred{116} abstracted tests.  Among them, \inred{203} original
+tests and \inred{90} abstracted tests are successfully analyzed by using dynamic shortcuts
 instead of manual modeling of \jscode{Array}.  Each filled cell describes
@@
 shortcuts effectively lessen the burden of manual modeling for JavaScript
-built-in functions.  Again, since analysis of all the original Lodash 4 tests except one
-finishes with a single dynamic shortcut, all the built-in fuctions
+built-in functions.  \inred{Again, since analysis of all the original Lodash 4 tests except one
+finishes with a single dynamic shortcut, all the built-in functions
 except \jscode{Math.floor} and \njscode{Function.prototype.call} are replaceable
 for original tests.  For abstracted tests, 12 out of 60 built-in
-functions are analyzed by only dynamic shortcuts.
+functions are analyzed by only dynamic shortcuts.}

### 2021-02-24 paper/fse21/eval.tex
Color undefined numbers in red

@@
 (no-DS) finished analysis of 200 out of 269 tests within 5 minutes, our tool
-(DS) finished analysis of 263 tests using dynamic shortcuts.  For finished
-tests, the average analysis time is 49.57 seconds for no-DS and 2.78 seconds for
-DS.  Among 200 tests analyzed by no-DS, two tests are timeout in DS, thus
-198 tests are analyzable by both analyzers. For them, we depict the box plot for
+(DS) finished analysis of \inred{263} tests using dynamic shortcuts.  For finished
+tests, the average analysis time is \inred{49.57} seconds for no-DS and \inred{2.78} seconds for
+DS.  Among 200 tests analyzed by no-DS, \inred{two tests} are timeout in DS, thus
+\inred{198} tests are analyzable by both analyzers. For them, we depict the box plot for
 analysis speed up by dynamic shortcuts.  It shows that DS
-outperforms no-DS up to 54.98$\x$ and 19.96$\x$ on
+outperforms no-DS up to \inred{54.98$\x$} and \inred{19.96$\x$} on
 average.  Only for one test using $\jscode{_.sample}$, which
 randomly samples a value from a given array, DS showed
-0.90$\x$ speed of no-DS due to 24 times uses of dynamic shortcuts.
+\inred{0.90$\x$ speed of no-DS due to 24 times uses} of dynamic shortcuts.
 
@@
 non-deterministic inputs, they can be analyzed by a few number of dynamic shortcuts.
-In fact, among 269 tests, 262 tests are analyzed
+In fact, among 269 tests, \inred{262} tests are analyzed
 by a single dynamic shortcut without using abstract semantics.
@@
 Among 269 abstracted tests, no-DS finished analysis of 158 tests within 5 minutes,
-but DS finished analysis of 167 tests.  For finished tests, the average analysis
-time is 44.88 seconds for no-DS and 42.28 seconds for DS. Among 158 tests analyzed by no-DS, DS
-timed-out for 15 tests.  For 143 tests analyzable by both analyzers,
-DS outperformed no-DS up to 50.60$\x$ and 6.30$\x$ on average.
+but DS finished analysis of \inred{167} tests.  For finished tests, the average analysis
+time is \inred{44.88} seconds for no-DS and \inred{42.28} seconds for DS. Among 158 tests analyzed by no-DS, DS
+timed-out for \inred{15} tests.  For \inred{143} tests analyzable by both analyzers,
+DS outperformed no-DS up to \inred{50.60$\x$} and \inred{6.30$\x$} on average.
+\inred{Except for 6 test cases, using dynamic shortcut did show speed up.}
 
@@
   \vspace*{-1.5em}
-  \caption{Analysis time ratio for 143 \textit{abstracted} tests}
+  \caption{Analysis time ratio for \inred{143} \textit{abstracted} tests}
   \label{fig:abs-analysis-ratio}
@@
 
-Unlike for the original tests, analysis of 143 abstracted tests invoked
-16.05 dynamic shortcuts.  Because taking a dynamic shortcut
+Unlike for the original tests, analysis of \inred{143} abstracted tests invoked
+\inred{16.05} dynamic shortcuts.  Because taking a dynamic shortcut
 requires conversion between abstract states and sealed symbolic values
@@
 the communication cost between analyzers and the number of dynamic shortcuts.
-For 198 original tests, the communication cost was only
-3.51\% compared to the analysis time of no-DS.  However, for 143
-abstracted tests, the communication cost was 82.49\% compared to the analysis
+For \inred{198} original tests, the communication cost was only
+\inred{3.51\%} compared to the analysis time of no-DS.  However, for \inred{143}
+abstracted tests, the communication cost was \inred{82.49\%} compared to the analysis
 time of no-DS.  Figure~\ref{fig:abs-analysis-ratio} presents the
-analysis time ratio for 143 abstracted tests.
+analysis time ratio for \inred{143} abstracted tests.
 The $x$-axis represents the time ratio normalized by the total analysis time of
@@
 shortcuts and the number of corresponding tests.
-For all 143 tests, the communication cost (Comm. Cost) is larger than
+For all \inred{143} tests, the communication cost (Comm. Cost) is larger than
 both the static analysis time (Static) and the dynamic analysis
@@
 the less the performance benefits by using dynamic shortcuts.
-Specifically, when dynamic shortcuts are performed more than
-20 times, Comm. Cost is even larger than no-DS.
+\inred{Specifically, when dynamic shortcuts are performed more than
+20 times, Comm. Cost is even larger than no-DS.}
 Based on this evaluation result, we believe that we can leverage
@@
     \vspace*{-1.5em}
-    \caption{Reachable branches for 198 \textit{original} tests}
+    \caption{Reachable branches for \inred{198} \textit{original} tests}
     \label{fig:precision-fail}
@@
     \vspace*{-1.5em}
-    \caption{Reachable branches for 143 \textit{abstracted} tests}
+    \caption{Reachable branches for \inred{143} \textit{abstracted} tests}
     \label{fig:precision-branch}
@@
 To evaluate the analysis precision improvement of dynamic shortcuts,
-we measured the number of branches covered by no-DS and DS.
+we measured the number of \inred{assertion fails invoked by} no-DS and DS.
 Because both no-DS and DS are sound,
-high (low) branch coverage denotes low (high) analysis precision.
+high (low) \inred{number of assertion fails} denotes low (high) analysis precision.
 
@@
 precision between no-DS and DS.  The $x$-axis and the $y$-axis denote
-the number of branches covered by no-DS and DS, respectively;
-each $\times$ mark denotes each test.  The top and bottom dotted lines
-denote the worst and the best precision improvement, respectively, and
-the middle solid line denotes the average improvement.
-For 198 original tests that are analyzable by both analyzers,
+the number of \inred{assertion fails invoked} by no-DS and DS, respectively;
+each \inred{circle} mark denotes each test \inred{in heatmap form. The darker the circle is, the more tests it indicates.} The top line
+denotes the y=x line, and
+the bottom solid line denotes the average improvement.
+For \inred{198} original tests that are analyzable by both analyzers,
 Figure~\ref{fig:precision}(a) shows that dynamic shortcuts
-reduced the number of covered branches up to 13.13\%. However, it reduced
-the number of branches 0.46\% on average because most original tests
-do not use non-determinism. Unlike original tests, for 143
-abstracted tests that are analyzable by both analyzers,
+\inred{completely removed the assertion fails for 24 tests, reducing the nuber of assertion fails by 93\% on average.}
+For \inred{143} abstracted tests that are analyzable by both analyzers,
 Figure~\ref{fig:precision}(b) shows that dynamic shortcuts successfully cut down
-the number of covered branches up to 13.65\% and 1.89\% on average.
-Thus, on average, dynamic shortcuts removed analysis of 1.44 and 5.97 spurious branches
+the number of \inred{covered branches 12\% on average.}
+Thus, on average, dynamic shortcuts removed analysis of \inred{93\%} and \inred{12\%} spurious alarms
 for original and abstracted tests, respectively.

### 2021-02-24 paper/fse21/intro.tex
Color undefined numbers in red

@@
 Lodash 4 library.  The experiment shows that $\tool$ outperforms
-SAFE 6.30$\x$ on average.  Moreover, by using dynamic shortcuts
-instead of manual modeling for 12 opaque functions,
-$\tool$ improves the analysis precision to detect 6 more dead branches on
+SAFE \inred{6.30$\x$} on average.  Moreover, by using dynamic shortcuts
+instead of manual modeling for \inred{12} opaque functions,
+$\tool$ improves the analysis precision to \inred{reduce assertion fails by 12\%} on
 average.

### 2021-02-24 paper/fse21/abstract.tex
Substituted "sealed symbolic" to "sealed" by using macro.

@@
 consists of three parts: 1) converting an abstract state to its corresponding
-\textit{sealed symbolic state}, 2) performing \textit{sealed symbolic execution}
-on the sealed symbolic state, and 3) converting a sealed symbolic state
+\textit{{\sealed} state}, 2) performing \textit{{\sealed} state}
+on the {\sealed} state, and 3) converting a {\sealed} state
 to its corresponding abstract state. By taking dynamic shortcuts
@@
 scalability and precision by using highly-optimized commercial JavaScript engines
-and lessen the modeling efforts by performing sealed symbolic execution for opaque code.
+and lessen the modeling efforts by performing {\sealed} execution for opaque code.
 We formally define static analysis using dynamic shortcuts in the abstract
@@
 baseline static analyzer, and it improves the precision to
-\inred{reduce assertion fails by 12\% on average} by using sealed symbolic execution for
+\inred{reduce assertion fails by 12\% on average} by using {\sealed} execution for
 \inred{12} opaque functions.

### 2021-02-24 paper/fse21/conclusion.tex
Substituted "sealed symbolic" to "sealed" by using macro.

--- 2020-11-21 paper/pldi21/conclusion.tex
@@
 concretely executable program parts.  To maximize such benefits,
-we proposed \textit{sealed symbolic execution}, which performs
-concrete execution using sealed symbolic values for abstract values.
+we proposed \textit{{\sealed} execution}, which performs
+concrete execution using {\sealed} values for abstract values.
 We formally defined static analysis using dynamic shortcuts in the
@@
 abstracted tests of Lodash 4 library.  Moreover, it detects 6 more
-dead branches by using sealed symbolic execution instead of
+dead branches by using {\sealed} execution instead of
 manual modeling for 12 opaque functions on average.

### 2021-02-24 paper/fse21/ds.tex
Substituted "sealed symbolic" to "sealed" by using macro.

@@
 We now define a \textit{combined domain} of a given sensitive abstract
-domain with the sealed symbolic domain and its one-step execution.
+domain with the {\sealed} domain and its one-step execution.
 \begin{definition}[Combined Domain]
@@
 \textit{analysis elements} to easily configure different types of abstract
-states in the sensitive abstract domain and the sealed symbolic domain.
+states in the sensitive abstract domain and the {\sealed} domain.
 \begin{definition}[Analysis Elements]\label{def:aelem}
@@
   abstract state in a sensitive abstract domain $\sabsdom$, or 2) a pair of an
-  abstract instantiation map and a sealed symbolic state in a sealed symbolic
+  abstract instantiation map and a {\sealed} state in a {\sealed}
   domain $\symbdom$.  Its concretization function $\aelemgamma:
@@
 $(\view, \abselem)$ in a sensitive abstract domain to another analysis element in
-a sealed symbolic domain only if the convert $\asconverter$ is defined: $(\view,
+a {\sealed} domain only if the convert $\asconverter$ is defined: $(\view,
 \abselem) \in \Dom(\asconverter)$.  In addition, they should convert given
@@
 It consists of two steps: 1) the \textit{\reformname} step converts
-analysis elements if a new sealed symbolic execution starts or an
+analysis elements if a new {\sealed} execution starts or an
 existing one stops, and 2) the \textit{execution} step performs execution of each
 analysis element using the abstract one-step execution $\sabsstep$ in the sensitive
-abstract domain and the sealed symbolic one-step execution $\symbstep$ in the sealed
-symbolic domain.
+abstract domain and the {\sealed} one-step execution $\symbstep$ in the {\sealed} domain.
 \begin{definition}[Combined One-Step Execution]
@@
 From a given combined state $\combelem$, the $\reform$ function makes analysis elements
-and converts them if a new sealed symbolic execution
-begins or an existing sealed symbolic execution terminates.
+and converts them if a new {\sealed} execution
+begins or an existing {\sealed} execution terminates.
 Specifically, for an analysis element $(\view, \abselem)$ in the sensitive abstract domain,
-if the converter $\asconverter$ is defined for it, $\reform$ introduces a new sealed symbolic execution
+if the converter $\asconverter$ is defined for it, $\reform$ introduces a new {\sealed} execution
 by converting the analysis element to its corresponding one $(\absimap, \symbst) =
-\asconverter((\view, \abselem))$ in the sealed symbolic domain.
-On the other hand, for an analysis element $(\absimap, \symbst)$ in the sealed symbolic domain,
-if it does not have any sealed symbolic states to transit to, $\symbst \symbtrans \excst$,
-the sealed symbolic execution for $(\absimap, \symbst)$ terminates;
+\asconverter((\view, \abselem))$ in the {\sealed} domain.
+On the other hand, for an analysis element $(\absimap, \symbst)$ in the {\sealed} domain,
+if it does not have any {\sealed} states to transit to, $\symbst \symbtrans \excst$,
+the {\sealed} execution for $(\absimap, \symbst)$ terminates;
 It converts the analysis element to its corresponding one $(\view, \abselem) =
@@
 state $\abselem$.  A pair enclosed by angle brackets denotes an analysis
-element that is a pair of an abstract instantiation map $\absimap$ and a sealed
-symbolic state $\symbst$.  In fact, the sealed symbolic state part (right) of
+element that is a pair of an abstract instantiation map $\absimap$ and a {\sealed}
+state $\symbst$.  In fact, the {\sealed} state part (right) of
 each pair in graphs contains only the value of the variable of $\varx$ without
@@
 $\viewtrans{\lab}{\lab'}$ from a label $\lab$ to another one $\lab'$.  A dotted
-line is a sealed symbolic transition $\symbtrans$.  Three solid lines with
+line is a {\sealed} transition $\symbtrans$.  Three solid lines with
 circled labels denote two converters $\saconverter$, $\asconverter$ and the join
@@
 another analysis element $\langle \varnothing, 0 \rangle$ with the label
-$\lab_0$.  It does not introduce any sealed symbolic values because
+$\lab_0$.  It does not introduce any {\sealed} values because
 the value represents only a single value.  Until the end of the program, the
-sealed symbolic execution from $\langle \varnothing, 0 \rangle$ successfully
-continues.  Because there is no more possible symbolic transition for the
-symbolic state $\langle \varnothing, 0 \rangle$ with the label $\lab_4$,
+{\sealed} execution from $\langle \varnothing, 0 \rangle$ successfully
+continues.  Because there is no more possible {\sealed} transition for the
+{\sealed} state $\langle \varnothing, 0 \rangle$ with the label $\lab_4$,
 it is converted to $(\lab_4, 0)$ via the converter $\saconverter$.
@@
 flow for the case.  The initial abstract value at the label $\lab_0$ is
-$+$ and it is impossible to convert it to any sealed symbolic values because the
+$+$ and it is impossible to convert it to any {\sealed} values because the
 next program statement requires the actual value stored in the variable $\varx$
@@
 $(\lab_1, +)$ can be converted to $\langle \symb \mapsto +, \symb \rangle$
-with the label $\lab_1$.  This sealed symbolic execution step terminates in the
+with the label $\lab_1$.  This {\sealed} execution step terminates in the
 label $\lab_3$ because the next statement is $\varx = -\varx$ and the negation
@@
 with $-$, and 2) $\langle \symb \mapsto 0+, \symb \rangle$ with $\lab_3$
-introduced by sealed symbolic execution started at $\lab_1$.  Since it
-is not possible to perform sealed symbolic execution for both elements, the
+introduced by {\sealed} execution started at $\lab_1$.  Since it
+is not possible to perform {\sealed} execution for both elements, the
 second one is converted to $(\lab_3, 0+)$ and merged with $+$ at $\lab_3$ via the
@@
 \subsection{Soundness and Termination}
-The converter $\asconverter$ and the sealed symbolic transition $\symbtrans$ are
-keys to configure the introduction and termination of sealed symbolic
+The converter $\asconverter$ and the {\sealed} transition $\symbtrans$ are
+keys to configure the introduction and termination of {\sealed}
 execution.  To ensure the \textit{soundness} and \textit{termination} of an
 abstract interpretation defined with a combined domain of a sensitive abstract
-domain and a sealed symbolic domain, the following conditions should hold.
+domain and a {\sealed} domain, the following conditions should hold.
 
@@
     \item the sensitive abstract domain $\sabsdom$ has a finite height,
-    \item the sealed symbolic transition $\symbtrans$ is valid, and
+    \item the {\sealed} transition $\symbtrans$ is valid, and
     \item there exists $N < \infty$ such that
@@
 the number of sensitive abstract states and
-the number of sealed symbolic states, respectively.
+the number of {\sealed} states, respectively.
 Thus, it guarantees the termination of the analysis.
@@
 The core idea of the proof is to use Lemma~\ref{lemma:step-symb} and
-Lemma~\ref{lemma:reform} for the sealed symbolic one-step execution
+Lemma~\ref{lemma:reform} for the {\sealed} one-step execution
 $\symbstep$ and the $\reform$ function, respectively. Due to the page limitation, we omit

### 2021-02-24 paper/fse21/eval.tex
Substituted "sealed symbolic" to "sealed" by using macro.

@@
 \inred{16.05} dynamic shortcuts.  Because taking a dynamic shortcut
-requires conversion between abstract states and sealed symbolic values
+requires conversion between abstract states and {\sealed} values
 and their exchanges between the static analyzer and the dynamic analyzer,
 using dynamic shortcuts multiple times may incur more performance
-overhead than performance benefits by using sealed symbolic execution.
+overhead than performance benefits by using {\sealed} execution.
 One conjecture is that the communication cost between the static

### 2021-02-24 paper/fse21/implementation.tex
Substituted "sealed symbolic" to "sealed" by using macro.

@@
 
-\paragraph{Sealed Values.}
-The main challenge of implementing dynamic shortcuts is to support sealed
-symbolic execution on an existing JavaScript engine.  To represent an abstract
+\paragraph{{\SealeD} Values.}
+The main challenge of implementing dynamic shortcuts is to support {\sealed} execution on an existing JavaScript engine.  To represent an abstract
 value, we use the \jscode{Proxy} object introduced in ECMAScript 6
@@
 Using this idea, we successfully extended the
-JavaScript engine to support sealed symbolic execution.
+JavaScript engine to support {\sealed} execution.
 
 \paragraph{Synchronization of Control Points.}
-For seamless interaction between static analysis and sealed symbolic execution,
+For seamless interaction between static analysis and {\sealed} execution,
 synchronization of control points in both worlds is necessary.
@@
 to keep track of necessary information at run time.  Therefore, during
-sealed symbolic execution, Jalangi requires the annotations from SAFE to compute
+{\sealed} execution, Jalangi requires the annotations from SAFE to compute
 abstract locations of newly created concrete objects and lexical environments.
@@
 
-\paragraph{Function-Level Dynamic Shortcut.}
-The dynamic shortcut is activated when the current abstract state passes the
+\paragraph{\inred{Function-Level Dynamic Shortcut.}}
+\inred{The dynamic shortcut is activated when the current abstract state passes the
 filter $\checker$.  If the filter tolerantly admits the dynamic shortcut, the
@@
 function exits thus $\tool$ supports only \textit{function-level} dynamic
-shortcut.
+shortcut.}
 
@@
 only when it terminates in a time bound $N$.  Since statically checking the
-termination property is a difficult task, we simply perform sealed symbolic
+termination property is a difficult task, we simply perform {\sealed}
 execution with a pre-determined time limit.  When it times out,
 we treat it as a failure in conversion;
-otherwise, we use the result of sealed symbolic execution.  Our experiments used
-5 seconds as the time limit for each sealed symbolic execution.
+otherwise, we use the result of {\sealed} execution.  Our experiments used
+5 seconds as the time limit for each {\sealed} execution.
 
@@
 % dynamic analyzer by passing the current abstract state and receiving the final
-% result of the sealed symbolic execution.  However, The static analyzer SAFE and
+% result of the {\sealed} execution.  However, The static analyzer SAFE and
 % the dynamic analyzer Jalangi are implemented in different languages Scala and
@@
 % the given JSON object and executes the dynamic analysis from the target program
-% points.  After finishing the sealed symbolic execution, it sends a newly
+% points.  After finishing the {\sealed} execution, it sends a newly
 % constructed JSON object to SAFE to update the abstract states in the function
@@
 %JavaScript program to annotate each object created during dynamic analysis with
-%its allocation site and context information.  After the sealed symbolic
+%its allocation site and context information.  After the {\sealed}
 %execution, the dynamic analyzer collects the objects based on their annotated

### 2021-02-24 paper/fse21/intro.tex
Substituted "sealed symbolic" to "sealed" by using macro.

@@
 consists of three parts: 1) converting the current abstract state to
-its corresponding \textit{sealed symbolic state}, 2) performing
-\textit{sealed symbolic execution} on the sealed symbolic state, and
-3) converting the result of the sealed symbolic execution to its
+its corresponding \textit{{\sealed} state}, 2) performing
+\textit{{\sealed} execution} on the {\sealed} state, and
+3) converting the result of the {\sealed} execution to its
 corresponding abstract state.  Our key observation is that we can use
@@
 we can concretely execute the code.  Based on this observation,
-we introduce sealed symbolic execution, which is concrete execution
-using \textit{sealed symbolic values}.  A sealed symbolic value is a
-representation of an abstract value in symbolic execution; it signals
-the end of the current dynamic shortcut when the sealed symbolic
+we introduce {\sealed} execution, which is concrete execution
+using \textit{{\sealed} values}.  \inred{A {\sealed} value is a symbol
+that represent an abstract value in {\sealed} execution}; it signals
+the end of the current dynamic shortcut when the {\sealed}
 execution tries to access its value.

### 2021-02-24 paper/fse21/javascript.tex
Substituted "sealed symbolic" to "sealed" by using macro.

--- 2020-11-21 paper/pldi21/javascript.tex
@@
 first-class functions, open objects, and first-class property names, and define
-sealed symbolic execution of the core language for dynamic shortcuts.
+{\sealed} execution of the core language for dynamic shortcuts.
 Due to the space limitation, we present the main design of the
@@
 
-\subsection{Sealed Symbolic Execution}
+\subsection{{\SealeD} Execution}
 
-We define the sealed symbolic states by not only extending the concrete values
-$\valset$ with symbolic values $\symbset$ but also adding the abstract counters
+We define the {\sealed} states by not only extending the concrete values
+$\valset$ with {\sealed} values $\symbset$ but also adding the abstract counters
 $\abscountset$ as follows:
@@
 Moreover, since object properties are string values that can be constructed at run time,
-it is difficult for static analysis to know whether strong updates are possible or not.
-To check the possibility of strong updates during sealed symbolic execution,
+it is difficult to perform sound strong updates in static analysis.
+To check the possibility of strong updates during {\sealed} execution,
 we augment its states with the abstract counters $\abscountset$.
@@
 recovers abstract values from their unique identifiers using the abstract instantiation map.
-We define the sealed symbolic transition relation $\symbtrans$
-only if the next step does not require actual values of any symbolic values.
-Otherwise, a given sealed symbolic state does not have any sealed symbolic
+We define the {\sealed} transition relation $\symbtrans$
+only if the next step does not require actual values of any {\sealed} values.
+Otherwise, a given {\sealed} state does not have any {\sealed}
 transitions to apply.  For example, we add the following rule for the $\kwret$ statement:
@@
 \end{mathpar}
-We extend each rule of the concrete semantics to support such behaviors of symbolic
+We extend each rule of the concrete semantics to support such behaviors of {\sealed} 
 values.

### 2021-02-24 paper/fse21/motivation.tex
Fixed typos.
Substituted "sealed symbolic" to "sealed" by using macro.

@@
 It calls the \jscode{concat} function to update the drop-down list of
-states or provinces on lines 17--18.  However, when the user selects ``United States of America,''
+states or provinces on lines 16--17.  However, when the user selects ``United States of America,''
 which is \jscode{"US"}, two arguments are pre-defined with
@@
   \vspace*{-1em}
-  \caption{Concrete objects with sealed symbolic values}
+  \caption{Concrete objects with {\sealed} values}
   \label{fig:sealed}
@@
 Even when a function is called with abstract values, we can still
-perform dynamic analysis using sealed symbolic execution.
+perform dynamic analysis using {\sealed} execution.
 For example, \jscode{getData} in Figure~\ref{fig:example}(c) is invoked
@@
 To perform dynamic analysis with abstract values, we seal abstract values
-with symbolic values as in Figure~\ref{fig:sealed}.  Two symbolic
+with {\sealed} values as in Figure~\ref{fig:sealed}.  Two {\sealed}
 values $\symbevt$ and $\symbint$ represent an event
@@
 However, dynamic analysis fails for \jscode{copyArray(array)} on line 10
-because the value of the \jscode{length} property of \jscode{array} is the symbolic value $\symbint$.
-Then, we stop the sealed symbolic execution, convert the current
-sealed symbolic state to its corresponding abstract state, and resume
-the static analysis from line 10.  Because sealed symbolic execution
+because the value of the \jscode{length} property of \jscode{array} is the {\sealed} value $\symbint$.
+Then, we stop the {\sealed} execution, convert the current
+{\sealed} state to its corresponding abstract state, and resume
+the static analysis from line 10.  Because {\sealed} execution
 leverages fast dynamic analysis as long as possible, the overall
@@
 using dynamic shortcuts, static analysis does not need to model \jscode{isArray}.
-It can perform sealed symbolic execution for \jscode{isArray}, which
+It can perform {\sealed} execution for \jscode{isArray}, which
 returns a more precise result \jscode{true} than $\top_b$.

### 2021-02-24 paper/fse21/related.tex
Substituted "sealed symbolic" to "sealed" by using macro.

@@
 introduced \textit{mostly-concrete interpretation} similar to our
-sealed symbolic execution, it supports only a special \textit{unknown}
+{\sealed} execution, it supports only a special \textit{unknown}
 value that represents any possible value.  Thus, it cannot preserve
@@
   regex, weaklySPE} frequently used in JavaScript static analysis.
-On the contrary, sealed symbolic execution automatically detects when
+On the contrary, {\sealed} execution automatically detects when
 to switch to static analysis to use abstract semantics for abstract values.

### 2021-02-24 paper/fse21/shortcut.tex
Substituted "sealed symbolic" to "sealed" by using macro.

@@
 In this section, we formally define static analysis using dynamic shortcuts by
-introducing sealed symbolic execution in the abstract interpretation framework.
+introducing {\sealed} execution in the abstract interpretation framework.
 We extend the formalization of abstract interpretation of \citet{abs-interp-1977,
 abs-interp-1992} and views-based analysis sensitivity of \citet{sens-toplas}.
-For dynamic shortcuts, we define sealed symbolic execution with a
-sealed symbolic domain and abstract instantiation maps.  To combine
-sensitive abstract interpretation and sealed symbolic execution, we define
-a combined domain of sensitive abstract domain and sealed symbolic domain and
+For dynamic shortcuts, we define {\sealed} execution with a
+{\sealed} domain and abstract instantiation maps.  To combine
+sensitive abstract interpretation and {\sealed} execution, we define
+a combined domain of sensitive abstract domain and {\sealed} domain and
 explain it with a simple example. Finally, we prove the soundness and
@@
 
-\subsection{Sealed Symbolic Execution}
+\subsection{{\SealeD} Execution}
 
-We define \textit{sealed symbolic execution} by extending the transition
-relation $\trans$ as a symbolic transition relation $\symbtrans$ on symbolic
-states.  First, we extend concrete states $\stset$ to symbolic states
-$\symbstset$ by extending values $\valset$ with \textit{sealed symbolic values}
-$\symbset$.  We also define the symbolic transition relation $\symbtrans
+We define \textit{{\sealed} execution} by extending the transition
+relation $\trans$ as a {\sealed} transition relation $\symbtrans$ on {\sealed}
+states.  First, we extend concrete states $\stset$ to {\sealed} states
+$\symbstset$ by extending values $\valset$ with \textit{{\sealed} values}
+$\symbset$.  We also define the {\sealed} transition relation $\symbtrans
 \subseteq \symbstset \times \symbstset$. We use the notation $\symbtrans^k$
 for $k$ repetition of $\symbtrans$, and write $\symbst \symbtrans \excst$ when
-$\symbst$ does not have any symbolic transitions to other sealed symbolic
-states.  We define the validity of sealed symbolic execution as follows:
+$\symbst$ does not have any {\sealed} transitions to other {\sealed}
+states.  We define the validity of {\sealed} execution as follows:
 \begin{definition}[Validity]\label{def:valid-symbtrans}
-  The symbolic transition relation is \textit{valid} when the following
-  condition is satisfied for any sealed symbolic states $\symbst$ and
+  The {\sealed} transition relation is \textit{valid} when the following
+  condition is satisfied for any {\sealed} states $\symbst$ and
   $\symbst'$:
@@
   where $\imapset: \symbset \rightarrow \valset$ represent \textit{instantiation
-  maps} from symbolic values to concrete values, and $\instant{\symbst}{\imap}$
-  denotes a state produced by replacing each symbolic value $\symb$ in
+  maps} from {\sealed} values to concrete values, and $\instant{\symbst}{\imap}$
+  denotes a state produced by replacing each {\sealed} value $\symb$ in
   $\symbst$ with its
@@
 
-Sealed symbolic execution is different from traditional
-symbolic execution~\cite{symbolic} in that it supports only sealed symbolic
+{\Sealed} execution is different from traditional
+symbolic execution~\cite{symbolic} in that it supports only {\sealed}
 values instead of symbolic expressions and path constraints.  For example, the
@@
 at $\lab_3$, respectively. Similarly, $\varx$  stores $-\symb$ and $\symb$ at $\lab_4$.
-However, sealed symbolic execution stops at $\lab_0$ as follows:
+However, {\sealed} execution stops at $\lab_0$ as follows:
 \[
@@
 \]
-because the branch requires the actual value of the symbolic value $\symb$.
+because the branch requires the actual value of the {\sealed} value $\symb$.
 
-To define an abstract domain that contains sealed symbolic states, we define
+To define an abstract domain that contains {\sealed} states, we define
 \textit{abstract instantiation maps} $\absimapset: \symbset \rightarrow
-\absvalset$ from symbolic values to abstract values.  Its concretization
+\absvalset$ from {\sealed} values to abstract values.  Its concretization
 function $\imapgamma: \absimapset \rightarrow \powerset{\imapset}$ is defined
@@
 \]
-The instantiation of a given sealed symbolic state $\symbst \in \symbstset$ with
+The instantiation of a given {\sealed} state $\symbst \in \symbstset$ with
 an abstract instantiation map $\absimap \in \absimapset$ is defined as follows:
@@
 \]
-Now, we define a \textit{sealed symbolic domain} as follows:
+Now, we define a \textit{{\sealed} domain} as follows:
 
-\begin{definition}[Sealed Symbolic Domain]\label{def:symbdom}
-  A \textit{sealed symbolic domain} $\symbdom: \powerset{\absimapset \times
+\begin{definition}[{\SealeD} Domain]\label{def:symbdom}
+  A \textit{{\sealed} domain} $\symbdom: \powerset{\absimapset \times
   \symbstset}$ is defined with the concretization function
-  $\symbgamma: \symbdom \rightarrow \dom$ and the sealed symbolic one-step execution
+  $\symbgamma: \symbdom \rightarrow \dom$ and the {\sealed} one-step execution
   $\symbstep: \symbdom \rightarrow \symbdom$ such that

### 2021-02-25 paper/fse21/eval.tex
Update figures and table

@@
 
-      \mysutf{1}{}          {Array    }  {203 / 203}{ 90 / 116} & \mysutf{1}{}             {String     }  { 20 /  20}{  9 /  10} & \mysutf{1}{}       {Object        }  {263 / 263}{151 / 167} \mylinefff
-      \mysutf{1}{}          {new Array}  {  0 /   0}{  0 /  10} & \mysutf{1}{}             {toString   }  {  0 /   0}{  0 /  33} & \mysutf{1}{}       {new Object    }  {  0 /   0}{  0 /   3} \mylinefff
-      \mysutf{1}{}          {isArray  }  {263 / 263}{144 / 167} & \mysutf{1}{}             {valueOf    }  {  0 /   0}{  0 /  12} & \mysutf{1}{}       {getPrototypeOf}  { 56 /  56}{ 24 /  29} \mylinefff
-      \mysutf{1}{}          {concat   }  {263 / 263}{163 / 167} & \mysutt{1}{}             {charAt     }  {  7 /   7}{  5 /   5} & \mysutf{1}{}       {create        }  {263 / 263}{164 / 167} \mylinefff
-      \mysutf{1}{}          {join     }  {263 / 263}{166 / 167} & \mysutf{1}{}             {charCodeAt }  { 15 /  15}{  3 /   4} & \mysutf{1}{Object} {defineProperty}  {263 / 263}{160 / 167} \mylinefff
-      \mysutf{1}{}          {pop      }  { 25 /  25}{  9 /  13} & \mysutt{1}{}             {indexOf    }  {  2 /   2}{  1 /   1} & \mysbtt{1}{}       {freeze        }  {  1 /   1}{  1 /   1} \mylinefff
-      \mysutf{2}{Array}     {push     }  {263 / 263}{150 / 167} & \mysutf{1}{String}       {match      }  { 25 /  25}{ 11 /  13} & \mysutf{1}{}       {keys          }  {263 / 263}{161 / 167} \mylinefff
-      \mysutt{1}{}          {reverse  }  { 10 /  10}{  3 /   3} & \mysutf{1}{}             {replace    }  { 55 /  55}{ 19 /  26} & \mysutf{1}{}       {toString      }  {263 / 263}{129 / 167} \mylinefff
-      \mysutf{1}{}          {shift    }  {  2 /   2}{  0 /   1} & \mysutf{1}{}             {slice      }  {263 / 263}{165 / 167} & \mysutf{1}{}       {hasOwnProperty}  {263 / 263}{161 / 167} \mylinefft
-      \mysutf{1}{}          {slice    }  {263 / 263}{164 / 167} & \mysutf{1}{}             {split      }  {  5 /   5}{  0 /   1} & \mysutf{1}{}       {parseInt}        {  1 /   1}{  0 /   1} \mylinefff
-      \mysutf{1}{}          {sort     }  { 69 /  69}{ 26 /  28} & \mysutf{1}{}             {substring  }  {214 / 214}{ 91 / 121} & \mysutf{1}{Global} {isNaN   }        { 15 /  15}{  9 /  25} \mylinefff
-      \mysutf{1}{}          {splice   }  { 25 /  25}{  6 /  11} & \mysutf{1}{}             {toLowerCase}  {214 / 214}{ 90 / 121} & \mysbtt{1}{}       {isFinite}        {  3 /   3}{  1 /   1} \mylinefft
-      \mysutt{1}{}          {unshift  }  {  2 /   2}{  1 /   1} & \mysutf{1}{}             {toUpperCase}  { 10 /  10}{  4 /   6} & \mysbtt{1}{}       {RegExp    }      {263 / 263}{167 / 167} \mylineftf
-      \mysutf{1}{}          {indexOf  }  { 94 /  94}{ 22 /  47} & \mysutt{2}{Boolean}      {Boolean}      {  3 /   3}{  2 /   2} & \mysutf{2}{RegExp} {new RegExp}      {  0 /   0}{  0 /   1} \mylinefff
-      \mysutf{1}{}          {every    }  { 92 /  92}{ 23 /  32} & \mysutf{1}{}             {valueOf}      {  0 /   0}{  0 /   6} & \mysbtt{1}{}       {exec      }      {263 / 263}{167 / 167} \mylinettf
-      \mysutt{1}{}          {ceil }      { 36 /  36}{  8 /   8} & \mysutf{2}{Number}       {Number }      {  2 /   2}{  1 /   2} & \mysutf{1}{}       {test      }      {263 / 263}{158 / 167} \mylinefft
-      \mysuff{1}{}          {floor}      { 16 /  17}{  4 /   5} & \mysutf{1}{}             {valueOf}      {  0 /   0}{  0 /  16} & \mysutf{1}{}       {Error         }  {  1 /   1}{  0 /   1} \mylineftf
-      \mysutf{1}{Math}      {max  }      {263 / 263}{134 / 167} & \mysutt{1}{}             {toString}     {263 / 263}{167 / 167} & \mysutf{2}{Error}  {new Error     }  {  0 /   0}{  0 /   8} \mylinefff
-      \mysutf{1}{}          {min  }      { 64 /  64}{ 15 /  48} & \mnsutf{1}{Function}     {apply   }     {263 / 263}{124 / 167} & \mysutf{1}{}       {new RangeError}  {  0 /   0}{  0 /   3} \mylinefff
-      \mysutt{1}{}          {pow  }      { 11 /  11}{  5 /   5} & \mysuff{1}{}             {call    }     {262 / 263}{ 50 / 167} & \mysutf{1}{}       {new TypeError }  {  0 /   0}{  0 /   9}
+      \mysuff{1}{}          {Array    }  {204 / 205}{119 / 141} 	& \mysutf{1}{}             {String     }  { 20 /  20}{ 13 /  14} 	& \mysutf{1}{}       {Object        }  {265 / 265}{181 / 193} \mylinefff
+      \mysutf{1}{}          {new Array}  {  0 /   0}{  0 /   7} 	& \mysutf{1}{}             {toString   }  {  0 /   0}{  0 /  14} 	& \mysutf{1}{}       {getPrototypeOf}  { 56 /  56}{ 34 /  35} \mylinefff
+      \mysuff{1}{}          {isArray  }  {264 / 265}{181 / 193} 	& \mysutf{1}{}             {valueOf    }  {  0 /   0}{  0 /  20} 	& \mysutt{1}{}       {create        }  {265 / 265}{193 / 193} \mylinefff
+      \mysutf{1}{}          {concat   }  {265 / 265}{189 / 193} 	& \mysutt{1}{}             {charAt     }  {  8 /   8}{  6 /   6} 	& \mysutf{2}{Object} {defineProperty}  {265 / 265}{190 / 193} \mylinefff
+      \mysutt{1}{}          {join     }  {265 / 265}{193 / 193} 	& \mysutt{1}{}             {charCodeAt }  { 15 /  15}{  8 /   8} 	& \mysbtt{1}{}       {freeze        }  {  1 /   1}{  1 /   1} \mylinefff
+      \mysutt{1}{}          {pop      }  { 25 /  25}{ 14 /  14} 	& \mysutt{1}{}             {indexOf    }  {  2 /   2}{  1 /   1} 	& \mysutf{1}{}       {keys          }  {265 / 265}{191 / 193} \mylinefff
+      \mysutf{2}{Array}     {push     }  {265 / 265}{186 / 193} 	& \mysutf{2}{String}       {match      }  { 26 /  26}{ 16 /  18} 	& \mysuff{1}{}       {toString      }  {264 / 265}{138 / 193} \mylinefff
+      \mysutt{1}{}          {reverse  }  { 10 /  10}{  6 /   6} 	& \mysutf{1}{}             {replace    }  { 56 /  56}{ 31 /  37} 	& \mysutf{1}{}       {hasOwnProperty}  {265 / 265}{190 / 193} \mylinefft
+      \mysutt{1}{}          {shift    }  {  3 /   3}{  2 /   2} 	& \mysutf{1}{}             {slice      }  {265 / 265}{191 / 193} 	& \mysutt{1}{JSON}   {stringify}       {  1 /   1}{  1 /   1} \mylinefft
+      \mysutt{1}{}          {slice    }  {265 / 265}{193 / 193} 	& \mysutt{1}{}             {split      }  {  5 /   5}{  2 /   2} 	& \mysutf{1}{}       {parseInt}        {  2 /   2}{  1 /   2} \mylinefff
+      \mysutf{1}{}          {sort     }  { 69 /  69}{ 38 /  39} 	& \mysutf{1}{}             {substring  }  {214 / 214}{136 / 145} 	& \mysutf{1}{Global} {isNaN   }        { 15 /  15}{ 11 /  40} \mylinefff
+      \mysutf{1}{}          {splice   }  { 25 /  25}{  9 /  12} 	& \mysutf{1}{}             {toLowerCase}  {215 / 215}{135 / 146} 	& \mysbtt{1}{}       {isFinite}        {  3 /   3}{  1 /   1} \mylinefft
+      \mysutt{1}{}          {unshift  }  {  2 /   2}{  2 /   2} 	& \mysutf{1}{}             {toUpperCase}  { 11 /  11}{  6 /   7} 	& \mysbtt{1}{}       {RegExp    }      {265 / 265}{193 / 193} \mylinefff
+      \mysutf{1}{}          {indexOf  }  { 94 /  94}{ 61 /  66} 	& \mysutt{1}{}             {fromCharCode} {  1 /   1}{  1 /   1}  &	\mysutf{2}{RegExp} {new RegExp}      {  0 /   0}{  0 /   1} \mylineftf
+      \mysutf{1}{}          {every    }  { 92 /  92}{ 43 /  47} 	& \mysuff{1}{Date}         {new Date}     {  0 /   1}{  0 /   1} 	& \mysbtt{1}{}       {exec      }      {265 / 265}{193 / 193} \mylinettf
+      \mysuff{1}{}          {ceil }      { 37 /  38}{ 20 /  21} 	& \mysutt{1}{}             {Number}       {  2 /   2}{  2 /   2} 	& \mysuff{1}{}       {test      }      {264 / 265}{185 / 193} \mylinefft
+      \mysuff{1}{}          {floor}      { 16 /  18}{  8 /  10} 	& \mysutt{1}{Number}       {toFixed}      {  1 /   1}{  0 /   0} 	& \mysutf{1}{}       {Error     }      {  1 /   1}{  0 /   1} \mylinefff
+      \mysuff{2}{Math}      {max  }      {264 / 265}{179 / 193} 	& \mysutf{1}{}             {valueOf}      {  0 /   0}{  0 /  28} 	& \mysutf{1}{Error}  {new RangeError}  {  0 /   0}{  0 /   2} \mylineftf
+      \mysutf{1}{}          {min  }      { 64 /  64}{ 31 /  44} 	& \mysutt{1}{}             {toString}     {265 / 265}{193 / 193} 	& \mysutf{1}{}       {new TypeError }  {  0 /   0}{  0 /   7} \mylinefft
+      \mysutt{1}{}          {pow  }      { 11 /  11}{  6 /   6} 	& \mysuff{1}{Function}     {apply   }     {263 / 265}{133 / 193} 	& \mysutt{2}{Boolean}{Boolean}         {  3 /   3}{  2 /   2} \mylinefff
+      \mysutt{1}{}          {round}      {  2 /   2}{  1 /   1} 	& \mysuff{1}{}             {call    }     {259 / 265}{ 50 / 193} 	& \mysutf{1}{}       {valueof}         {  0 /   0}{  0 /   7}
     \end{array}
@@
   \begin{subfigure}[t]{0.48\textwidth}
-    \includegraphics[width=\linewidth]{img/conc-precision}
+    \includegraphics[width=\linewidth]{img/precision}
     \vspace*{-1.5em}
-    \caption{Reachable branches for \inred{198} \textit{original} tests}
+    \caption{Reachable branches for \inred{198} \textit{original} tests and \inred{143} \textit{abstracted} tests}
     \label{fig:precision-fail}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.48\textwidth}
-    \includegraphics[width=\linewidth]{img/abs-precision}
-    \vspace*{-1.5em}
-    \caption{Reachable branches for \inred{143} \textit{abstracted} tests}
-    \label{fig:precision-branch}
   \end{subfigure}

### 2021-02-25 paper/fse21/abstract.tex
Fix typo in abstract

@@
 consists of three parts: 1) converting an abstract state to its corresponding
-\textit{{\sealed} state}, 2) performing \textit{{\sealed} state}
+\textit{{\sealed} state}, 2) performing \textit{{\sealed} execution}
 on the {\sealed} state, and 3) converting a {\sealed} state

### 2021-02-25 paper/fse21/abstract.tex
Finalize numbers in red

@@
 269 official tests of Lodash 4 library.
-Our experiment shows that $\tool$ is \inred{6.30}$\x$ faster than the
+Our experiment shows that $\tool$ is 7.81$\x$ faster than the
 baseline static analyzer, and it improves the precision to
-\inred{reduce assertion fails by 12\% on average} by using {\sealed} execution for
-\inred{12} opaque functions.
+reduce failed assertions by 12.31\% on average by using {\sealed} execution for
+22 opaque functions.
 \end{abstract}

### 2021-02-25 paper/fse21/eval-opaque.tex
Finalize numbers in red

--- 2020-11-21 paper/pldi21/eval-opaque.tex
@@
 static analysis.  Table~\ref{table:func-replace} summarizes the result.
-For 263 original tests and 167 abstracted tests that DS finished analysis, we measured the
+For 265 original tests and 193 abstracted tests that DS finished analysis, we measured the
 number of tests that use only dynamic shortcuts instead of manual modeling
@@
 For example, the first row in the leftmost side describes that \jscode{Array} is used in
-203 original tests and 116 abstracted tests.  Among them, 203 original
-tests and 90 abstracted tests are successfully analyzed by using dynamic shortcuts
+205 original tests and 141 abstracted tests.  Among them, 204 original
+tests and 119 abstracted tests are successfully analyzed by using dynamic shortcuts
 instead of manual modeling of \jscode{Array}.  Each filled cell describes
@@
 shortcuts effectively lessen the burden of manual modeling for JavaScript
-built-in functions.  Again, since analysis of all the original Lodash 4 tests except one
-finishes with a single dynamic shortcut, all the built-in fuctions
-except \jscode{Math.floor} and \njscode{Function.prototype.call} are replaceable
-for original tests.  For abstracted tests, 12 out of 60 built-in
-functions are analyzed by only dynamic shortcuts.
+built-in functions.  \inred{For original tests, 45 out of 63 built-in functinos are replaceable
+for original tests.  For abstracted tests, 22 built-in
+functions are analyzed by only dynamic shortcuts.}

### 2021-02-25 paper/fse21/eval.tex
Finalize numbers in red

@@
 We performed our experiments on a Ubuntu machine
-equipped with 4.2GHz Quad-Core Intel Core i7 and 64GB of RAM.
+equipped with 4.2GHz Quad-Core Intel Core i7 and 32GB of RAM.
 
@@
 (no-DS) finished analysis of 200 out of 269 tests within 5 minutes, our tool
-(DS) finished analysis of \inred{263} tests using dynamic shortcuts.  For finished
-tests, the average analysis time is \inred{49.57} seconds for no-DS and \inred{2.78} seconds for
-DS.  Among 200 tests analyzed by no-DS, \inred{two tests} are timeout in DS, thus
-\inred{198} tests are analyzable by both analyzers. For them, we depict the box plot for
+(DS) finished analysis of 265 tests using dynamic shortcuts.  For finished
+tests, the average analysis time is 49.46 seconds for no-DS and 3.21 seconds for
+DS.  Among 200 tests analyzed by no-DS, one test is timeout in DS, thus
+199 tests are analyzable by both analyzers. For them, we depict the box plot for
 analysis speed up by dynamic shortcuts.  It shows that DS
-outperforms no-DS up to \inred{54.98$\x$} and \inred{19.96$\x$} on
+outperforms no-DS up to 83.71$\x$ and 22.30$\x$ on
 average.  Only for one test using $\jscode{_.sample}$, which
 randomly samples a value from a given array, DS showed
-\inred{0.90$\x$ speed of no-DS due to 24 times uses} of dynamic shortcuts.
+0.36$\x$ speed of no-DS due to 24 times uses of dynamic shortcuts.
 
@@
 non-deterministic inputs, they can be analyzed by a few number of dynamic shortcuts.
-In fact, among 269 tests, \inred{262} tests are analyzed
+In fact, among 269 tests, 259 tests are analyzed
 by a single dynamic shortcut without using abstract semantics.
@@
 Among 269 abstracted tests, no-DS finished analysis of 158 tests within 5 minutes,
-but DS finished analysis of \inred{167} tests.  For finished tests, the average analysis
-time is \inred{44.88} seconds for no-DS and \inred{42.28} seconds for DS. Among 158 tests analyzed by no-DS, DS
-timed-out for \inred{15} tests.  For \inred{143} tests analyzable by both analyzers,
-DS outperformed no-DS up to \inred{50.60$\x$} and \inred{6.30$\x$} on average.
-\inred{Except for 6 test cases, using dynamic shortcut did show speed up.}
+but DS finished analysis of 193 tests.  For finished tests, the average analysis
+time is 44.88 seconds for no-DS and 19.05 seconds for DS. Among 158 tests analyzed by no-DS, DS
+timed-out for 2 tests.  For 156 tests analyzable by both analyzers,
+DS outperformed no-DS up to 78.07$\x$ and 7.81$\x$ on average.
+\inred{Except for 9 test cases, using dynamic shortcut did show speed up.}
 
@@
   \vspace*{-1.5em}
-  \caption{Analysis time ratio for \inred{143} \textit{abstracted} tests}
+  \caption{Analysis time ratio for 156 \textit{abstracted} tests}
   \label{fig:abs-analysis-ratio}
@@
       \mysuff{1}{}          {Array    }  {204 / 205}{119 / 141} 	& \mysutf{1}{}             {String     }  { 20 /  20}{ 13 /  14} 	& \mysutf{1}{}       {Object        }  {265 / 265}{181 / 193} \mylinefff
-      \mysutf{1}{}          {new Array}  {  0 /   0}{  0 /   7} 	& \mysutf{1}{}             {toString   }  {  0 /   0}{  0 /  14} 	& \mysutf{1}{}       {getPrototypeOf}  { 56 /  56}{ 34 /  35} \mylinefff
-      \mysuff{1}{}          {isArray  }  {264 / 265}{181 / 193} 	& \mysutf{1}{}             {valueOf    }  {  0 /   0}{  0 /  20} 	& \mysutt{1}{}       {create        }  {265 / 265}{193 / 193} \mylinefff
+      \mysuff{1}{}          {new Array}  {  0 /   0}{  0 /   7} 	& \mysuff{1}{}             {toString   }  {  0 /   0}{  0 /  14} 	& \mysutf{1}{}       {getPrototypeOf}  { 56 /  56}{ 34 /  35} \mylinefff
+      \mysuff{1}{}          {isArray  }  {264 / 265}{181 / 193} 	& \mysuff{1}{}             {valueOf    }  {  0 /   0}{  0 /  20} 	& \mysbtt{1}{}       {create        }  {265 / 265}{193 / 193} \mylinefff
       \mysutf{1}{}          {concat   }  {265 / 265}{189 / 193} 	& \mysutt{1}{}             {charAt     }  {  8 /   8}{  6 /   6} 	& \mysutf{2}{Object} {defineProperty}  {265 / 265}{190 / 193} \mylinefff
@@
       \mysutt{1}{}          {reverse  }  { 10 /  10}{  6 /   6} 	& \mysutf{1}{}             {replace    }  { 56 /  56}{ 31 /  37} 	& \mysutf{1}{}       {hasOwnProperty}  {265 / 265}{190 / 193} \mylinefft
-      \mysutt{1}{}          {shift    }  {  3 /   3}{  2 /   2} 	& \mysutf{1}{}             {slice      }  {265 / 265}{191 / 193} 	& \mysutt{1}{JSON}   {stringify}       {  1 /   1}{  1 /   1} \mylinefft
+      \mysutt{1}{}          {shift    }  {  3 /   3}{  2 /   2} 	& \mysutf{1}{}             {slice      }  {265 / 265}{191 / 193} 	& \mysbtt{1}{JSON}   {stringify}       {  1 /   1}{  1 /   1} \mylinefft
       \mysutt{1}{}          {slice    }  {265 / 265}{193 / 193} 	& \mysutt{1}{}             {split      }  {  5 /   5}{  2 /   2} 	& \mysutf{1}{}       {parseInt}        {  2 /   2}{  1 /   2} \mylinefff
@@
       \mysutt{1}{}          {unshift  }  {  2 /   2}{  2 /   2} 	& \mysutf{1}{}             {toUpperCase}  { 11 /  11}{  6 /   7} 	& \mysbtt{1}{}       {RegExp    }      {265 / 265}{193 / 193} \mylinefff
-      \mysutf{1}{}          {indexOf  }  { 94 /  94}{ 61 /  66} 	& \mysutt{1}{}             {fromCharCode} {  1 /   1}{  1 /   1}  &	\mysutf{2}{RegExp} {new RegExp}      {  0 /   0}{  0 /   1} \mylineftf
+      \mysutf{1}{}          {indexOf  }  { 94 /  94}{ 61 /  66} 	& \mysutt{1}{}             {fromCharCode} {  1 /   1}{  1 /   1}  &	\mysuff{2}{RegExp} {new RegExp}      {  0 /   0}{  0 /   1} \mylineftf
       \mysutf{1}{}          {every    }  { 92 /  92}{ 43 /  47} 	& \mysuff{1}{Date}         {new Date}     {  0 /   1}{  0 /   1} 	& \mysbtt{1}{}       {exec      }      {265 / 265}{193 / 193} \mylinettf
       \mysuff{1}{}          {ceil }      { 37 /  38}{ 20 /  21} 	& \mysutt{1}{}             {Number}       {  2 /   2}{  2 /   2} 	& \mysuff{1}{}       {test      }      {264 / 265}{185 / 193} \mylinefft
-      \mysuff{1}{}          {floor}      { 16 /  18}{  8 /  10} 	& \mysutt{1}{Number}       {toFixed}      {  1 /   1}{  0 /   0} 	& \mysutf{1}{}       {Error     }      {  1 /   1}{  0 /   1} \mylinefff
-      \mysuff{2}{Math}      {max  }      {264 / 265}{179 / 193} 	& \mysutf{1}{}             {valueOf}      {  0 /   0}{  0 /  28} 	& \mysutf{1}{Error}  {new RangeError}  {  0 /   0}{  0 /   2} \mylineftf
-      \mysutf{1}{}          {min  }      { 64 /  64}{ 31 /  44} 	& \mysutt{1}{}             {toString}     {265 / 265}{193 / 193} 	& \mysutf{1}{}       {new TypeError }  {  0 /   0}{  0 /   7} \mylinefft
-      \mysutt{1}{}          {pow  }      { 11 /  11}{  6 /   6} 	& \mysuff{1}{Function}     {apply   }     {263 / 265}{133 / 193} 	& \mysutt{2}{Boolean}{Boolean}         {  3 /   3}{  2 /   2} \mylinefff
-      \mysutt{1}{}          {round}      {  2 /   2}{  1 /   1} 	& \mysuff{1}{}             {call    }     {259 / 265}{ 50 / 193} 	& \mysutf{1}{}       {valueof}         {  0 /   0}{  0 /   7}
+      \mysuff{1}{}          {floor}      { 16 /  18}{  8 /  10} 	& \mysutf{1}{Number}       {toFixed}      {  1 /   1}{  0 /   0} 	& \mysutf{1}{}       {Error     }      {  1 /   1}{  0 /   1} \mylinefff
+      \mysuff{2}{Math}      {max  }      {264 / 265}{179 / 193} 	& \mysuff{1}{}             {valueOf}      {  0 /   0}{  0 /  28} 	& \mysuff{1}{Error}  {new RangeError}  {  0 /   0}{  0 /   2} \mylineftf
+      \mysutf{1}{}          {min  }      { 64 /  64}{ 31 /  44} 	& \mysutt{1}{}             {toString}     {265 / 265}{193 / 193} 	& \mysuff{1}{}       {new TypeError }  {  0 /   0}{  0 /   7} \mylinefft
+      \mysutt{1}{}          {pow  }      { 11 /  11}{  6 /   6} 	& \mysuff{1}{Function}     {apply   }     {263 / 265}{133 / 193} 	& \mysbtt{2}{Boolean}{Boolean}         {  3 /   3}{  2 /   2} \mylinefff
+      \mysutt{1}{}          {round}      {  2 /   2}{  1 /   1} 	& \mysuff{1}{}             {call    }     {259 / 265}{ 50 / 193} 	& \mysuff{1}{}       {valueof}         {  0 /   0}{  0 /   7}
     \end{array}
@@
 
-Unlike for the original tests, analysis of \inred{143} abstracted tests invoked
-\inred{16.05} dynamic shortcuts.  Because taking a dynamic shortcut
+Unlike for the original tests, analysis of 156 abstracted tests invoked
+20.35 dynamic shortcuts.  Because taking a dynamic shortcut
 requires conversion between abstract states and {\sealed} values
@@
 the communication cost between analyzers and the number of dynamic shortcuts.
-For \inred{198} original tests, the communication cost was only
-\inred{3.51\%} compared to the analysis time of no-DS.  However, for \inred{143}
-abstracted tests, the communication cost was \inred{82.49\%} compared to the analysis
+For 199 original tests, the communication cost was only
+1.58\% compared to the analysis time of no-DS.  However, for 156
+abstracted tests, the communication cost was 31.06\% compared to the analysis
 time of no-DS.  Figure~\ref{fig:abs-analysis-ratio} presents the
-analysis time ratio for \inred{143} abstracted tests.
+analysis time ratio for 156 abstracted tests.
 The $x$-axis represents the time ratio normalized by the total analysis time of
@@
 shortcuts and the number of corresponding tests.
-For all \inred{143} tests, the communication cost (Comm. Cost) is larger than
+For all 156 tests, the communication cost (Comm. Cost) is larger than
 both the static analysis time (Static) and the dynamic analysis
@@
 the less the performance benefits by using dynamic shortcuts.
-\inred{Specifically, when dynamic shortcuts are performed more than
-20 times, Comm. Cost is even larger than no-DS.}
+Specifically, when dynamic shortcuts are performed more than 20 times,
+Comm. Cost is even larger than half of cost of no-DS.
 Based on this evaluation result, we believe that we can leverage
@@
     \vspace*{-1.5em}
-    \caption{Reachable branches for \inred{198} \textit{original} tests and \inred{143} \textit{abstracted} tests}
     \label{fig:precision-fail}
@@
   \vspace*{-1em}
-  \caption{Branch coverage of analysis without (no-DS) and with (DS) dynamic shortcuts}
+  \caption{Failed assertions of analysis without (no-DS) and with (DS) dynamic shortcuts for 199 \textit{original} tests (left) and 156 \textit{abstracted} tests (right)}
   \label{fig:precision}
@@
 To evaluate the analysis precision improvement of dynamic shortcuts,
-we measured the number of \inred{assertion fails invoked by} no-DS and DS.
+we measured the number of failed assertions produced by no-DS and DS.
 Because both no-DS and DS are sound,
-high (low) \inred{number of assertion fails} denotes low (high) analysis precision.
+high (low) number of failed assertions denotes low (high) analysis precision.
 
@@
 precision between no-DS and DS.  The $x$-axis and the $y$-axis denote
-the number of \inred{assertion fails invoked} by no-DS and DS, respectively;
-each \inred{circle} mark denotes each test \inred{in heatmap form. The darker the circle is, the more tests it indicates.} The top line
-denotes the y=x line, and
-the bottom solid line denotes the average improvement.
-For \inred{198} original tests that are analyzable by both analyzers,
-Figure~\ref{fig:precision}(a) shows that dynamic shortcuts
-\inred{completely removed the assertion fails for 24 tests, reducing the nuber of assertion fails by 93\% on average.}
-For \inred{143} abstracted tests that are analyzable by both analyzers,
-Figure~\ref{fig:precision}(b) shows that dynamic shortcuts successfully cut down
-the number of \inred{covered branches 12\% on average.}
-Thus, on average, dynamic shortcuts removed analysis of \inred{93\%} and \inred{12\%} spurious alarms
+the number of failed assertions produced by no-DS and DS, respectively;
+\inred{each circle denotes each test in heatmap form. The darker the circle is, the more tests it indicates.} The top line
+denotes the y=x line, and the bottom solid line denotes the average improvement.
+For 199 original tests that are analyzable by both analyzers,
+Figure~\ref{fig:precision}(left) shows that dynamic shortcuts
+\inred{completely removed the failed assertions for 24 tests, reducing the nuber of failed assertions by 92.79\% on average}.
+For 156 abstracted tests that are analyzable by both analyzers,
+Figure~\ref{fig:precision}(right) shows that dynamic shortcuts successfully cut down
+the number of failed asserions by 12.31\% on average.
+Thus, on average, dynamic shortcuts removed analysis of 92.79\% and 12.31\% failed assertions
 for original and abstracted tests, respectively.

### 2021-02-25 paper/fse21/intro.tex
Finalize numbers in red

@@
 Lodash 4 library.  The experiment shows that $\tool$ outperforms
-SAFE \inred{6.30$\x$} on average.  Moreover, by using dynamic shortcuts
-instead of manual modeling for \inred{12} opaque functions,
-$\tool$ improves the analysis precision to \inred{reduce assertion fails by 12\%} on
+SAFE 7.81$\x$ on average.  Moreover, by using dynamic shortcuts
+instead of manual modeling for 22 opaque functions,
+$\tool$ improves the analysis precision to reduce failed assertions by 12.31\% on
 average.

### 2021-02-25 paper/fse21/eval.tex
Revised Figure 9.

@@
 \begin{figure}[t]
-  \centering
-  \begin{subfigure}[t]{0.48\textwidth}
-    \includegraphics[width=\linewidth]{img/precision}
+  \begin{subfigure}[t]{0.23\textwidth}
+    \includegraphics[width=\linewidth]{img/conc-precision}
     \vspace*{-1.5em}
-    \label{fig:precision-fail}
+    \caption{199 \textit{original} tests}
+    \label{fig:conc-precision}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.23\textwidth}
+    \includegraphics[width=\linewidth]{img/abs-precision}
+    \vspace*{-1.5em}
+    \caption{156 \textit{abstracted} tests}
+    \label{fig:abs-precision}
   \end{subfigure}
   \vspace*{-1em}
-  \caption{Failed assertions of analysis without (no-DS) and with (DS) dynamic shortcuts for 199 \textit{original} tests (left) and 156 \textit{abstracted} tests (right)}
+  \caption{Failed assertions of analysis without (no-DS) and with (DS) dynamic shortcuts}
   \label{fig:precision}
@@
 For 199 original tests that are analyzable by both analyzers,
-Figure~\ref{fig:precision}(left) shows that dynamic shortcuts
+Figure~\ref{fig:conc-precision} shows that dynamic shortcuts
 \inred{completely removed the failed assertions for 24 tests, reducing the nuber of failed assertions by 92.79\% on average}.
 For 156 abstracted tests that are analyzable by both analyzers,
-Figure~\ref{fig:precision}(right) shows that dynamic shortcuts successfully cut down
+Figure~\ref{fig:abs-precision} shows that dynamic shortcuts successfully cut down
 the number of failed asserions by 12.31\% on average.

### 2021-02-25 paper/fse21/implementation.tex
Shorten "Synchronization of Control Points." of implementation and related work.

@@
 For seamless interaction between static analysis and {\sealed} execution,
-synchronization of control points in both worlds is necessary.
-The SAFE static analyzer parses a JavaScript program to an Abstract
-Syntax Tree (AST), compiles it to its intermediate representation, and
-builds a Control Flow Graph (CFG).  It produces annotations for
-control points on CFGs including functions, call sites, and object allocation sites.
-On the contrary, the Jalangi dynamic analyzer instruments a JavaScript program 
-to keep track of necessary information at run time.  Therefore, during
-{\sealed} execution, Jalangi requires the annotations from SAFE to compute
-abstract locations of newly created concrete objects and lexical environments.
-The key to put annotations on the instrumented code is the source-code
-location of the original AST node.  While both CFG of SAFE and
-instrumented code of Jalangi maintain the source-code location information,
-because they use different parsers we found various location mismatches for corner cases.
-Therefore, we synchronize control points of two analyzers by using the closest match
-of their source-code locations rather than using their exact match.
+synchronization of control points in both sides is necessary.
+The SAFE and Jalangi have their own notations for control points that are not directly
+compatible.
+We use the source-code location of a target program as a key to synchronize.
+Even though they use different parsers and we faced numerous location mismatches for corner cases,
+we could synchronize control points of two analyzers by using the closest match
+of their source-code locations rather than using exact match of them.
 

### 2021-02-25 paper/fse21/related.tex
Shorten "Synchronization of Control Points." of implementation and related work.

@@
 \section{Related Work}\label{sec:related}
-Researchers have introduced various techniques to utilize dynamic
-analysis for static analysis in three ways: combined analysis,
-automatic modeling, and pruning analysis scope.
+%Researchers have introduced various techniques to utilize dynamic
+%analysis for static analysis in three ways: combined analysis,
+%automatic modeling, and pruning analysis scope.
 
@@
 divides a given program to \textit{applications} parts for static
-analysis and \textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
+analysis and \textit{frameworks} parts for dynamic analysis.  Thus, it cannot
 freely switch between static analysis and dynamic analysis.  It is
@@
 libraries or host-dependent functions is necessary because they are opaque code.
-Since manual modeling is error-prone, tedious, and labor-intensive,
+Since manual modeling is error-prone and labor-intensive,
 researchers~\cite{safewapi, safets} have utilized type information to
-automatically model their behaviors.  However, type information is too imprecise
-to reflect complex semantics and is difficult to represent the side-effects.
+automatically model their behaviors.  However, type is not enough
+to reflect complex semantics and side-effects.
 To alleviate the problem, \citet{mimic} introduced a technique
 to infer JavaScript code for opaque code using concrete execution.
-They captured the effects of opaque code on user objects by collecting partial
-execution traces and synthesized JavaScript code using the extracted behaviors.
-They also leveraged ES6 \jscode{Proxy} objects to capture the effects on user objects.
+They leveraged ES6 \jscode{Proxy} objects to collect partial execution traces
+from opaque code and synthesized JavaScript code using the extracted behaviors.
 Instead of synthesizing JavaScript code,
 \citet{opaque-model} presented a \textit{Sample-Run-Abstract (SRA)} approach for
-on-demand modeling focusing on the current abstract states during static analysis.
-It first \textit{samples} concrete states in a well-distributed manner,
-\textit{runs} each sampled state on a JavaScript engine, and \textit{abstracts} execution results.
+on-demand modeling focusing on the current abstract states during static analysis
+by sampling well-distributed concrete states.
 However, all the previous work sacrifice the soundness of static analysis.
-On the contrary, while dynamic shortcuts may not be applicable to some
-invocations of opaque functions, it is sound if it is applicable.
+On the contrary, while dynamic shortcuts is not always applicable to opaque
+functions, it is sound if it is applicable.
 
@@
 to prune the scope of analysis.  \citet{determinacy} proposed dynamic
-determinacy analysis, which infers determinacy facts like whether a
-variable or an expression at a given location holds the same value in
-all possible execution of a program via concrete execution.
-They specialized target source code with determinacy
-facts so that static analysis can get benefits from elimination of dynamic code
-generation such as \jscode{eval} and constant property names.
+determinacy analysis.  They specialized target source code with determinacy
+facts so that static analysis can get benefits from elimination of \jscode{eval}
+and constant property names.
 \citet{blended} introduced \textit{blended taint analysis}, which specializes JavaScript dynamic
@@
 in dynamic language features and restricts the semantics of features based on the
-collected traces during static analysis.  \citet{battles, eha} utilize three different points to reduce
+collected traces during static analysis.  \citet{battles, eha} utilize three points to reduce
 analysis scope: initial states, dynamically loaded files, and event handlers.
-They dumped the initial states from a specific web browser to focus on
-analysis of the behaviors of web applications running on the browser.
-Then, they collected paths of dynamically loaded files via concrete
-execution and utilized the path information in static analysis.
-For event handlers, they intentionally analyzed partial execution flows using concrete user events.
-They collected concrete states for each entry of an event handler
-during dynamic analysis, merged them to a single abstract state, and analyzed
-the event handler with the abstract state.
 Unfortunately, all the above mentioned approaches except~\cite{determinacy} do not preserve

### 2021-02-25 paper/fse21/implementation.tex
Marked inred.

@@
 synchronization of control points in both sides is necessary.
-The SAFE and Jalangi have their own notations for control points that are not directly
+\inred{The SAFE and Jalangi have their own notations for control points that are not directly
 compatible.
@@
 we could synchronize control points of two analyzers by using the closest match
-of their source-code locations rather than using exact match of them.
+of their source-code locations rather than using exact match of them.}
 

### 2021-02-25 paper/fse21/eval-opaque.tex
The first draft

@@
 shortcuts effectively lessen the burden of manual modeling for JavaScript
-built-in functions.  \inred{For original tests, 45 out of 63 built-in functinos are replaceable
-for original tests.  For abstracted tests, 22 built-in
-functions are analyzed by only dynamic shortcuts.}
+built-in functions. For the original tests, 45 out of 63 built-in functinos are replaceable
+for them.  For the abstracted tests, 22 built-in functions are analyzed by only dynamic shortcuts.

### 2021-02-25 paper/fse21/eval.tex
Shorten "Synchronization of Control Points." of implementation and related work.
The first draft

@@
   \label{fig:conc-analysis-time}
-  \vspace*{-1.5em}
+\vspace*{-.5em}
 \end{figure}
@@
   \label{fig:abs-analysis-time}
-  \vspace*{-1.5em}
+  \vspace*{-.5em}
 \end{figure}
 
-To evaluate the effectiveness of using dynamic shortcuts, we performed static
+We evaluated the effectiveness of dynamic shortcuts by static
 analysis of 269 Lodash 4 tests with and without dynamic shortcuts.
+%
 Figure~\ref{fig:conc-analysis-time} depicts cumulative distribution charts for
@@
 DS outperformed no-DS up to 78.07$\x$ and 7.81$\x$ on average.
-\inred{Except for 9 test cases, using dynamic shortcut did show speed up.}
+Except for 9 test cases, using dynamic shortcuts did show speed-ups.
 
@@
 
+Unlike for the original tests, analysis of 156 abstracted tests invoked
+20.35 dynamic shortcuts.  Because taking a dynamic shortcut
+requires conversion between abstract states and {\sealed} values
+and their exchanges between the static analyzer and the dynamic analyzer,
+using dynamic shortcuts multiple times may incur more performance
+overhead than performance benefits by using {\sealed} execution.
+One conjecture is that the communication cost between the static
+analyzer and the dynamic analyzer may be proportional to the number of
+dynamic shortcuts.
+
+To experimentally evaluate the conjecture, we investigated the relationship between
+the communication cost (Comm. Cost) between analyzers and the number of dynamic shortcuts.
+For 199 original tests, Comm. Cost was only
+1.58\% compared to the analysis time of no-DS.  However, for 156
+abstracted tests, Comm. Cost was 31.06\% compared to the analysis
+time of no-DS.  Figure~\ref{fig:abs-analysis-ratio} presents the
+analysis time ratio for 156 abstracted tests.
+The $x$-axis represents the time ratio normalized by the total analysis time of
+no-DS and the $y$-axis denotes the number of dynamic
+shortcuts and the number of corresponding tests.
+For all 156 tests, Comm. Cost is larger than
+both the static analysis time (Static) and the dynamic analysis
+time (Dynamic).  When dynamic shortcuts are performed less than 10 times,
+Comm. Cost is modest compared with the baseline static
+analysis time.  However, the more dynamic shortcuts are performed,
+the less the performance benefits by using dynamic shortcuts.
+Specifically, when dynamic shortcuts are performed more than 20 times,
+Comm. Cost is even larger than half of cost of no-DS.
+Based on this evaluation result, we believe that we can leverage
+dynamic shortcuts by optimizing Comm. Cost between
+the static analyzer and the dynamic analyzer.
+
+\begin{figure}[t]
+  \centering
+  \begin{subfigure}[t]{0.23\textwidth}
+    \includegraphics[height=3.2cm]{img/conc-precision}
+    \vspace*{-0.7em}
+    \caption{199 \textit{original} tests}
+    \label{fig:conc-precision}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.23\textwidth}
+    \includegraphics[height=3.2cm]{img/abs-precision}
+    \vspace*{-0.7em}
+    \caption{156 \textit{abstracted} tests}
+    \label{fig:abs-precision}
+  \end{subfigure}
+  \vspace*{-1em}
+  \caption{Failed assertions of analysis without (no-DS) and with (DS) dynamic shortcuts}
+  \label{fig:precision}
+  \vspace*{-1.5em}
+\end{figure}
+
 \begin{table*}[t]
@@
   \label{table:func-replace}
-  \vspace*{-1em}
+  \vspace*{-1.5em}
   \centering
@@
 
-Unlike for the original tests, analysis of 156 abstracted tests invoked
-20.35 dynamic shortcuts.  Because taking a dynamic shortcut
-requires conversion between abstract states and {\sealed} values
-and their exchanges between the static analyzer and the dynamic analyzer,
-using dynamic shortcuts multiple times may incur more performance
-overhead than performance benefits by using {\sealed} execution.
-One conjecture is that the communication cost between the static
-analyzer and the dynamic analyzer may be proportional to the number of
-dynamic shortcuts.
-
-To experimentally evaluate the conjecture, we investigated the relationship between
-the communication cost between analyzers and the number of dynamic shortcuts.
-For 199 original tests, the communication cost was only
-1.58\% compared to the analysis time of no-DS.  However, for 156
-abstracted tests, the communication cost was 31.06\% compared to the analysis
-time of no-DS.  Figure~\ref{fig:abs-analysis-ratio} presents the
-analysis time ratio for 156 abstracted tests.
-The $x$-axis represents the time ratio normalized by the total analysis time of
-no-DS and the $y$-axis denotes the number of dynamic
-shortcuts and the number of corresponding tests.
-For all 156 tests, the communication cost (Comm. Cost) is larger than
-both the static analysis time (Static) and the dynamic analysis
-time (Dynamic).  When dynamic shortcuts are performed less than 10 times,
-the communication cost is modest compared with the baseline static
-analysis time.  However, the more dynamic shortcuts are performed,
-the less the performance benefits by using dynamic shortcuts.
-Specifically, when dynamic shortcuts are performed more than 20 times,
-Comm. Cost is even larger than half of cost of no-DS.
-Based on this evaluation result, we believe that we can leverage
-dynamic shortcuts by optimizing the communication cost between
-the static analyzer and the dynamic analyzer.
-
-\begin{figure}[t]
-  \begin{subfigure}[t]{0.23\textwidth}
-    \includegraphics[width=\linewidth]{img/conc-precision}
-    \vspace*{-1.5em}
-    \caption{199 \textit{original} tests}
-    \label{fig:conc-precision}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.23\textwidth}
-    \includegraphics[width=\linewidth]{img/abs-precision}
-    \vspace*{-1.5em}
-    \caption{156 \textit{abstracted} tests}
-    \label{fig:abs-precision}
-  \end{subfigure}
-  \vspace*{-1em}
-  \caption{Failed assertions of analysis without (no-DS) and with (DS) dynamic shortcuts}
-  \label{fig:precision}
-  \vspace*{-1.5em}
-\end{figure}
-
 \subsection{Precision Improvement}
@@
 the number of failed assertions produced by no-DS and DS, respectively;
-\inred{each circle denotes each test in heatmap form. The darker the circle is, the more tests it indicates.} The top line
+each circle denotes each test in the heatmap form. The darker the circle is, the more tests it indicates.
+The top line
 denotes the y=x line, and the bottom solid line denotes the average improvement.
 For 199 original tests that are analyzable by both analyzers,
-Figure~\ref{fig:conc-precision} shows that dynamic shortcuts
-\inred{completely removed the failed assertions for 24 tests, reducing the nuber of failed assertions by 92.79\% on average}.
+Figure~\ref{fig:precision}(a) shows that dynamic shortcuts
+completely removed the failed assertions for 24 tests, reducing the nuber of failed assertions by 92.79\% on average.
 For 156 abstracted tests that are analyzable by both analyzers,
-Figure~\ref{fig:abs-precision} shows that dynamic shortcuts successfully cut down
+Figure~\ref{fig:precision}(b) shows that dynamic shortcuts successfully cut down
 the number of failed asserions by 12.31\% on average.

### 2021-02-25 paper/fse21/implementation.tex
The first draft

--- 2021-02-25 paper/fse21/implementation.tex
@@
 synchronization of control points in both sides is necessary.
-The SAFE and Jalangi have their own notations for control points that are not directly
+The SAFE static analyzer and the Jalangi dynamic analyzer
+have their own notations for control points that are not directly
 compatible.
@@
 we could synchronize control points of two analyzers by using the closest match
-of their source-code locations rather than using exact match of them.
+of their source-code locations rather than using their exact match.
 
-\paragraph{\inred{Function-Level Dynamic Shortcut.}}
-\inred{The dynamic shortcut is activated when the current abstract state passes the
-filter $\checker$.  If the filter tolerantly admits the dynamic shortcut, the
-analysis may suffer from the frequent communication between static and dynamic
-analyzers.  To adjust the burden of communication, we only activate new
-dynamic shortcut in function entries and deactivate it in the corresponding
-function exits thus $\tool$ supports only \textit{function-level} dynamic
-shortcut.}
+\paragraph{Function-Level Dynamic Shortcut.}
+A dynamic shortcut is activated when the current abstract state passes the
+filter $\checker$.  If the filter admits dynamic shortcuts generously, the
+analysis may suffer from frequent communications between static and dynamic
+analyzers.  To adjust such a burden, $\tool$ supports only \textit{function-level} dynamic
+shortcuts by activating dynamic shortcuts in function entries and deactivating them
+in their corresponding function exits.
 
@@
 only when it terminates in a time bound $N$.  Since statically checking the
-termination property is a difficult task, we simply perform {\sealed}
-execution with a pre-determined time limit.  When it times out,
-we treat it as a failure in conversion;
-otherwise, we use the result of {\sealed} execution.  Our experiments used
-5 seconds as the time limit for each {\sealed} execution.
+termination property is difficult, we simply perform {\sealed}
+execution with a pre-determined time limit of 5 secounds.
+When it times out, we treat it as a failure in conversion;
+otherwise, we use the result of {\sealed} execution.
 

### 2021-02-25 paper/fse21/related.tex
The first draft

@@
 analysis scope: initial states, dynamically loaded files, and event handlers.
-Unfortunately, all the above mentioned approaches except~\cite{determinacy} do not preserve
+Unfortunately, all the above approaches except~\cite{determinacy} do not preserve
 soundness of static analysis unlike our approach using dynamic shortcuts.

### 2021-02-26 paper/fse21/implementation.tex
Remove 'symbol' from implementation section

@@
 creates \jscode{Proxy} objects to represent abstract values via the
-following \jscode{generateSymbol} function:
+following \jscode{getSealedValue} function:
 \begin{lstlisting}[style=myJSstyle]
-function generateSymbol() {
+function getSealedValue() {
   function detect() { /* access detection */ }
@@
   }); }
-var x = generateSymbol();
+var x = getSealedValue();
 var y = x;
@@
 \end{lstlisting}
-The function creates a sealed symbol as a proxy object with a dummy
+The function creates a sealed value as a proxy object with a dummy
 function object and a handler for all 13 traps using an access detection
-function \jscode{detect}.  A sealed symbol invokes the function \jscode{detect}
+function \jscode{detect}.  A sealed value invokes the function \jscode{detect}
 when any of 13 pre-defined traps are operated on the object, which enables us to
 determine whether an object is sealed or not.  For example, the variable
-\jscode{y} successfully points to the same symbol stored in \jscode{x}, but the
+\jscode{y} successfully points to the same sealed stored in \jscode{x}, but the
 program invokes the function \jscode{detect} on line 9 because \jscode{x + 1} requires
-the actual value of the symbol.  In addition, we instrument unary and binary
+the actual value of the sealed value.  In addition, we instrument unary and binary
 operations in Jalangi so that we can detect all the accesses on the
-symbol beyond the 13 traps provided by \jscode{Proxy}.
+sealed value beyond the 13 traps provided by \jscode{Proxy}.
 Using this idea, we successfully extended the

### 2021-02-26 paper/fse21/implementation.tex
Fix typo

@@
 determine whether an object is sealed or not.  For example, the variable
-\jscode{y} successfully points to the same sealed stored in \jscode{x}, but the
+\jscode{y} successfully points to the same sealed value stored in \jscode{x}, but the
 program invokes the function \jscode{detect} on line 9 because \jscode{x + 1} requires

### 2021-02-26 paper/fse21/eval.tex
Fix typos
Run spell checker

@@
 time (Dynamic).  When dynamic shortcuts are performed less than 10 times,
-Comm. Cost is modest compared with the baseline static
+Comm. Cost is modest compared to the baseline static
 analysis time.  However, the more dynamic shortcuts are performed,
 the less the performance benefits by using dynamic shortcuts.
-Specifically, when dynamic shortcuts are performed more than 20 times,
+Specifically, when dynamic shortcuts are performed more than 30 times,
 Comm. Cost is even larger than half of cost of no-DS.
@@
 the number of failed assertions produced by no-DS and DS, respectively;
-each circle denotes each test in the heatmap form. The darker the circle is, the more tests it indicates.
+each circle denotes each test in the heat-map form. The darker the circle is, the more tests it indicates.
 The top line
@@
 Figure~\ref{fig:precision}(a) shows that dynamic shortcuts
-completely removed the failed assertions for 24 tests, reducing the nuber of failed assertions by 92.79\% on average.
+completely removed the failed assertions for 24 tests, reducing the number of failed assertions by 92.79\% on average.
 For 156 abstracted tests that are analyzable by both analyzers,
 Figure~\ref{fig:precision}(b) shows that dynamic shortcuts successfully cut down
-the number of failed asserions by 12.31\% on average.
+the number of failed assertions by 12.31\% on average.
 Thus, on average, dynamic shortcuts removed analysis of 92.79\% and 12.31\% failed assertions

### 2021-02-26 paper/fse21/report/ds.tex
Added report for FSE version

--- 2020-11-26 paper/pldi21/report/ds.tex
@@
 From a given combined state $\combelem$, the $\reform$ function makes analysis elements
-and converts them if a new sealed symbolic execution
-begins or an existing sealed symbolic execution terminates.
+and converts them if a new {\sealed} execution
+begins or an existing {\sealed} execution terminates.
 Specifically, for an analysis element $(\view, \abselem)$ in the sensitive abstract domain,
-if the converter $\asconverter$ is defined for it, $\reform$ introduces a new sealed symbolic execution
+if the converter $\asconverter$ is defined for it, $\reform$ introduces a new {\sealed} execution
 by converting the analysis element to its corresponding one $(\absimap, \symbst) =
-\asconverter((\view, \abselem))$ in the sealed symbolic domain.
-On the other hand, for an analysis element $(\absimap, \symbst)$ in the sealed symbolic domain,
-if it does not have any sealed symbolic states to transit to, $\symbst \symbtrans \excst$,
-the sealed symbolic execution for $(\absimap, \symbst)$ terminates;
+\asconverter((\view, \abselem))$ in the {\sealed} domain.
+On the other hand, for an analysis element $(\absimap, \symbst)$ in the {\sealed} domain,
+if it does not have any {\sealed} states to transit to, $\symbst \symbtrans \excst$,
+the {\sealed} execution for $(\absimap, \symbst)$ terminates.
 It converts the analysis element to its corresponding one $(\view, \abselem) =
 \saconverter((\absimap, \symbst))$ in the sensitive abstract domain and
-merges the current abstract state stored in the view $\view$ with $\abselem$.
+merges the current abstract state stored in $\view$ with $\abselem$.
 
@@
 another analysis element $\langle \varnothing, 0 \rangle$ with the label
-$\lab_0$.  It does not introduce any sealed symbolic values because
+$\lab_0$.  It does not introduce any {\sealed} values because
 the value represents only a single value.  Until the end of the program, the
-sealed symbolic execution from $\langle \varnothing, 0 \rangle$ successfully
-continues.  Because there is no more possible symbolic transition for the
-symbolic state $\langle \varnothing, 0 \rangle$ with the label $\lab_4$,
+{\sealed} execution from $\langle \varnothing, 0 \rangle$ successfully
+continues.  Because there is no more possible {\sealed} transition for the
+{\sealed} state $\langle \varnothing, 0 \rangle$ with $\lab_4$,
 it is converted to $(\lab_4, 0)$ via the converter $\saconverter$.
@@
 $\reform$ function in Lemma~\ref{lemma:reform}.  Using the properties, we prove
-the soundness of the sealed symbolic one-step execution in
+the soundness of the sealed one-step execution in
 Lemma~\ref{lemma:sound-symbstep}.  Finally, we prove the soundness of the
@@
 \begin{lemma}[Soundness of $\symbstep$]\label{lemma:sound-symbstep}
-  The sealed symbolic one-step execution $\symbstep$ is sound:
+  The sealed one-step execution $\symbstep$ is sound:
   \[
@@
 For simplicity, we define $\diffset_i$ as $\varnothing$ for $i < 0$.  Moreover, we
-define a lifted version of sealed symbolic relation $\liftsymbtrans \subseteq
+define a lifted version of sealed relation $\liftsymbtrans \subseteq
 (\absimapset \times \symbstset) \times (\absimapset \times \symbstset)$ as
@@
 Using the lifted relation, we define the \textit{time to live (TTL)} function of
-symbolic states $\ttl_i: \diffset_i \rightarrow \numset$ for each iteration $i
+sealed states $\ttl_i: \diffset_i \rightarrow \numset$ for each iteration $i
 \geq 0$ as follows:
@@
   such that $\sabselem^m = \sabselem^n$ for all $m \geq n$.  By the condition
-  (\ref{equ:bounded-ttl}), the TTL of each symbolic state in $\diffset_n$ is
+  (\ref{equ:bounded-ttl}), the TTL of each sealed state in $\diffset_n$ is
   bounded by $N$:
@@
   \].
-  Then, the upper bound of TTL for symbolic states in each difference set after
+  Then, the upper bound of TTL for sealed states in each difference set after
   the $n-$th iteration is decreased by the condition (\ref{equ:dec-ttl}):
@@
 abstract interpretation (\ref{equ:termination-sai}), the bound of TTL for
-symbolic states in difference sets (\ref{equ:bounded-ttl}), and the decrease of
+sealed states in difference sets (\ref{equ:bounded-ttl}), and the decrease of
 their upper bounds (\ref{equ:dec-ttl}) in Theorem~\ref{theorem:termination}
@@
 and a property of TTL in Lemma~\ref{lemma:prop-ttl}.  Using them, we prove the
-bound of TTL for symbolic states in difference sets (\ref{equ:bounded-ttl}) in
+bound of TTL for sealed states in difference sets (\ref{equ:bounded-ttl}) in
 Corollary~\ref{corollary:bounded-ttl} and the decrease of their upper bounds

### 2021-02-26 paper/fse21/report/javascript.tex
Added report for FSE version

--- 2020-11-26 paper/pldi21/report/javascript.tex
@@
 first-class functions, open objects, and first-class property names, and define
-sealed symbolic execution of the core language for dynamic shortcuts.
+{\sealed} execution of the core language for dynamic shortcuts.
 
@@
 We formulate the concrete semantics of the core language as described in
-Figure~\ref{fig:core-trans-rel}.  The transition relation between concrete
-states is defined with the semantics of references and expressions using two
-different forms \fbox{$\referrule{\st}{\refer}{\loc}$} and
+Figure~\ref{fig:core-trans-rel}.  The transition
+relation between concrete states is defined with the semantics of references and
+expressions using two different forms \fbox{$\referrule{\st}{\refer}{\loc}$} and
 \fbox{$\exprrule{\st}{\expr}{\val}$}, respectively.  The initial states are
 $\istset = \{ (\ilab, \varnothing, \epsilon, \tladdr) \}$ where $\ilab$ denotes
-the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level
-environment address.  The function $\labnext$ returns the next label of a
-given label in the current program $\prog$.
+the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level environment
+address.  The function $\labnext$ returns the next label of a given label in the
+current program $\prog$.
 
@@
 abstract counter as follows:
-
 \[
@@
 
-We define the semantics of the view transition for the core language in
-Figure~\ref{fig:core-view-trans}.  For abstract memories, we use the notation
-$\absmem[L \mapstos \absval]$ to represent the update of multiple abstract
-locations in $L$ with the abstract value $\absval$.  It performs the strong
-update if the abstract address for an abstract location $(\absaddr, \_) \in L$
-is singleton: $\abscount(\absaddr) = \absone$.  Otherwise, it performs the weak
-update for the analysis soundness.  We use the increment function $\inc:
-\abscountset \times \absaddrset \rightarrow \abscountset$ of the abstract
-counter defined as follows:
+We define the semantics of the view transition for the core language.  For abstract
+memories, we use the notation $\absmem[L \mapstos \absval]$ to represent the
+update of multiple abstract locations in $L$ with the abstract value $\absval$.
+It performs the strong update if the abstract address for an abstract location
+$(\absaddr, \_) \in L$ is singleton: $\abscount(\absaddr) = \absone$.
+Otherwise, it performs the weak update for the analysis soundness.  We use
+the increment function $\inc: \abscountset \times \absaddrset \rightarrow
+\abscountset$ of the abstract counter defined as follows:
+
 \[
@@
 
-\subsection{Sealed Symbolic Execution}
+\subsection{{\SealeD} Execution}
 
-We define the sealed symbolic states by not only extending the concrete values
-$\valset$ with symbolic values $\symbset$ but also adding the abstract counters
-$\abscountset$ as follows:
+We define {\sealed} states by not only extending the concrete values
+$\valset$ with {\sealed} values $\symbset$ but also adding the abstract counters~
+$\abscountset$:
+% as follows:
 \[
@@
 it is difficult to perform sound strong updates in static analysis.
-To check the possibility of strong updates during sealed symbolic execution,
+To check the possibility of strong updates during {\sealed} execution,
 we augment its states with the abstract counters $\abscountset$.
@@
 recovers abstract values from their unique identifiers using the abstract instantiation map.
-We define the sealed symbolic transition relation $\symbtrans$
-only if the next step does not require actual values of any symbolic values.
-Otherwise, a given sealed symbolic state does not have any sealed symbolic
-transitions to apply.  For example, we add the following rule for the $\kwret$ statement:
+We define the {\sealed} transition relation $\symbtrans$
+only if the next step does not require actual values of any {\sealed} values.
+Otherwise, a given {\sealed} state does not have any {\sealed}
+transitions to apply.  For example, we add the following rule:
 \begin{mathpar}
@@
 \end{mathpar}
-We extend each rule of the concrete semantics to support such behaviors of symbolic
-values.
+for the $\kwret$ statement. We extend each rule of the concrete semantics
+to support such behaviors of {\sealed} values.

### 2021-04-29 paper/fse21/rebuttal.md
Added rebuttal.md file

We sincerely thank the reviewers for their careful reviews and detailed
suggestions for improvement. We will reflect the suggestions in our revision,
and we answer the outstanding comments and questions from the reviewers as
follows:

- TODO

--------------------------------------------------------------------------------
# Individual Response (Optional)
--------------------------------------------------------------------------------

Review #162A
------------

### Abstract

- The abstract is too long and meandering

- "Sealed state" is a term for your new contribution (I believe), but it is not
  understood by the non-expert reader. I would avoid using jargon in the
  abstract.

- This approach could be explained more intuitively in the abstract. E.g., "We
  eliminate the need to analyze some methods by using the concrete parameters
  used to call them, and simply executing the code instead of analyzing it."
  This is probably not a totally correct characterization of your work, but it
  is much more intuitive and easy to understand.

- Microcontrollers for IoT is not a major use of Javascript… seems off topic.

- What do you mean by host environments?

- What do you mean by "high performance"? Do you mean fast? Do you mean
  accurate?

- It is difficult to make the jump from the high-level discussion (top) to the
  detailed discussion (bottom).

### Section 1 Introduction

- I don’t understand the focus on JavaScript in IoT environments… how is that
  relevant?

- "High performance" is an odd phrase to use here. I would consider speaking of
  the attribute you appreciate directly. I think you are referring to speed.

- The characterization of related work makes it difficult to determine how your
  work differs from theirs.

- I do not follow the example very well. I am not an expert on this type of
  program analysis, but I do understand program analysis generally, and I feel
  like this example is not clear. I would remove it.

- The performance gains seem very strong.

### Section 2 Motivation

- These examples are helpful for understanding your approach. I would remove
  the other example from the introduction, which was not helpful because it was
  too brief.

### Section 5 Implementation

- Good description of implementation and clever approach.

### Section 6 Evaluation

- The speedup seems remarkable.

- The communication costs section could be removed.

- Section 6.2 Precision Improvement) Can you discuss the practical implications
  of removing these failed assertions more clearly?

### Questions for authors

- Can you describe the key insight(s) of your approach, as if you were speaking
  to a non-expert, in 1-2 sentences?

--------------------------------------------------------------------------------

Review #162B
------------

### Comments for authors
- The idea of combining concrete and symbolic execution is a good one. I have
  not seen this done in Abstract Interpretation setting before. However, it is
  well established in Symbolic Execution domain. Concolic execution, especially
  as pioneered by EXE, and is currently best exemplified by KLEE, seems the
  closest to the proposed technique.

- Symbolic Execution can be seen as abstract interpretation over an abstract
  domain of expressions. From the high-level, it is identical to what is
  proposed in the paper: state is divided into concrete and abstract values,
  concrete values are executed concretely, symbolic are executed symbolically.
  Concrete values can be converted to symbolic, but not the other way around.
  There is a large body of related work on all kind of iterations of this basic
  idea.

- The paper spends a significant amount of space formalizing the semantics and
  the abstract domain. The formalism is appreciated, but it belongs to the
  appendix rather than the main body of the paper. Nothing new is communicated
  by it in addition to what is described in the motivation.

- However, what is missing is a clear identification of the limitations of the
  approach. How does the proposed scheme integrates with typical abstract
  interpretation analyses? For example, I imagine that aggressive use of joins
  and convex abstract domains will create so much abstract values that concrete
  execution will not be possible. Similar questions apply to widening,
  summary/contract computation for handling recursion, etc.

- In the current presentation, it seems that the authors consider only simple
  non-relational domains that are lifted to a powerset (i.e., join is union).
  If that is the case, the result is essentially identical to symbolic
  execution and the degree of novelty compared to concolic execution is low.

### Questions for authors

- What is the key distinguishing characteristic of the proposed approach with
  Concolic Symbolic Execution

- What are the limitations the approach places on abstract domains / algorithms
  used with it

- How the proposed technique integrates with typical static analysis: join,
  widen, efficient fixedpoint computation, etc.

--------------------------------------------------------------------------------

Review #162C
------------

### Weak Point 1 (W1)

- Sect. 4.3 is one of the most interesting sections - the paper is about
  JavaScript after all.  However, 4.3 is very short and Sects. 4.1 and 4.2
  introduce a lot of definitions which are not really needed to understand
  Sect. 4.3.  So maybe 4.1 and 4.2 could be less detailed in favor of 4.3.

- The paper could discuss why/how (not) dynamic shortcuts can be used for other
  languages.

### Weak Point 2 (W2)

- Please make explicit what the baseline analyzer is (I suppose standard
  SAFE?).

- I think that the chosen benchmark set (Lodash tests) is not a good choice,
  because even in the abstracted version, test cases are a special kind of
  software (threat to external validity).

- Moreover, the authors mention that the benchmark set was already used twice.
  But those uses are by similar authors.  So this statement is not convincing
  for the acceptance of the benchmark set in the community.

### Section 6.1 Analysis Speed-up
- Communication cost is one of your future work suggestions, so more details
  could be interesting: The authors could mention what is included in
  communication cost.  The state conversions? Or only data transfer between
  processes?  In this context it might also be interesting to know how you
  implemented the communication.  And then it can get relevant to know how
  exactly you measured it.

### Section 6.2 Precision Improvement

- How is "average improvement" (solid line) calculated?

- I do not understand where I can see the 24 failed assertions in Figure 9a.

- Also the percentages: You write "Figure 9(b) shows ... by 12.32 %" I do not
  understand how to get the numbers from the figure.  Maybe a table is more
  appropriate here?

- In general, I find the heat-map notation a bit confusing. Maybe one could
  explain an example, like "The grey circle at (0,12) means that x assertions
  failed with DS, ..."

- I also don't understand what the authors are averaging over in statements
  like "92.79 % on average".  I understand that for each of the 156 tests a
  failed assertion can be produced or not.  So it's possible to say, e.g., if
  half of the failed assertions are removed, the number is reduced by 50 %. But
  why average?

### 2021-04-29 paper/fse21/rebuttal-optional.md
Splitted rebuttal.md

--- 2021-04-29 paper/fse21/rebuttal.md
@@
-We sincerely thank the reviewers for their careful reviews and detailed
-suggestions for improvement. We will reflect the suggestions in our revision,
-and we answer the outstanding comments and questions from the reviewers as
-follows:
-
-- TODO
-
 --------------------------------------------------------------------------------
@@
 
-Review #162A
+Review A
 ------------
@@
 
-- The abstract is too long and meandering
+__A1)__ The abstract is too long and meandering
 
-- "Sealed state" is a term for your new contribution (I believe), but it is not
-  understood by the non-expert reader. I would avoid using jargon in the
+__=>__ TODO
+
+__A2)__ "Sealed state" is a term for your new contribution (I believe), but it
+is not understood by the non-expert reader. I would avoid using jargon in the
 abstract.
 
-- This approach could be explained more intuitively in the abstract. E.g., "We
-  eliminate the need to analyze some methods by using the concrete parameters
-  used to call them, and simply executing the code instead of analyzing it."
-  This is probably not a totally correct characterization of your work, but it
-  is much more intuitive and easy to understand.
+__=>__ TODO
 
-- Microcontrollers for IoT is not a major use of Javascript… seems off topic.
+__A3)__ This approach could be explained more intuitively in the abstract.
+E.g., "We eliminate the need to analyze some methods by using the concrete
+parameters used to call them, and simply executing the code instead of
+analyzing it." This is probably not a totally correct characterization of your
+work, but it is much more intuitive and easy to understand.
 
-- What do you mean by host environments?
+__=>__ TODO
 
-- What do you mean by "high performance"? Do you mean fast? Do you mean
+__A4)__ Microcontrollers for IoT is not a major use of Javascript… seems off
+topic.
+
+__=>__ TODO
+
+__A5)__ What do you mean by host environments?
+
+__=>__ TODO
+
+__A6)__ What do you mean by "high performance"? Do you mean fast? Do you mean
 accurate?
 
-- It is difficult to make the jump from the high-level discussion (top) to the
-  detailed discussion (bottom).
+__=>__ TODO
+
+__A7)__ It is difficult to make the jump from the high-level discussion (top)
+to the detailed discussion (bottom).
+
+__=>__ TODO
 
@@
 
-- I don’t understand the focus on JavaScript in IoT environments… how is that
-  relevant?
+__A8)__ I don’t understand the focus on JavaScript in IoT environments… how is
+that relevant?
 
-- "High performance" is an odd phrase to use here. I would consider speaking of
-  the attribute you appreciate directly. I think you are referring to speed.
+__=>__ TODO
 
-- The characterization of related work makes it difficult to determine how your
-  work differs from theirs.
+__A9)__ "High performance" is an odd phrase to use here. I would consider
+speaking of the attribute you appreciate directly. I think you are referring to
+speed.
 
-- I do not follow the example very well. I am not an expert on this type of
-  program analysis, but I do understand program analysis generally, and I feel
+__=>__ TODO
+
+__A10)__ The characterization of related work makes it difficult to determine
+how your work differs from theirs.
+
+__=>__ TODO
+
+__A11)__ I do not follow the example very well. I am not an expert on this type
+of program analysis, but I do understand program analysis generally, and I feel
 like this example is not clear. I would remove it.
 
-- The performance gains seem very strong.
+__=>__ TODO
 
@@
 
-- These examples are helpful for understanding your approach. I would remove
-  the other example from the introduction, which was not helpful because it was
-  too brief.
+__A12)__ These examples are helpful for understanding your approach. I would
+remove the other example from the introduction, which was not helpful because
+it was too brief.
 
-### Section 5 Implementation
-
-- Good description of implementation and clever approach.
+__=>__ TODO
 
@@
 
-- The speedup seems remarkable.
+__A13)__ The communication costs section could be removed.
 
-- The communication costs section could be removed.
+__=>__ TODO
 
-- Section 6.2 Precision Improvement) Can you discuss the practical implications
-  of removing these failed assertions more clearly?
+__A14)__ Section 6.2 Precision Improvement) Can you discuss the practical
+implications of removing these failed assertions more clearly?
+
+__=>__ TODO
 
@@
 
-- Can you describe the key insight(s) of your approach, as if you were speaking
-  to a non-expert, in 1-2 sentences?
+__A15)__ Can you describe the key insight(s) of your approach, as if you were
+speaking to a non-expert, in 1-2 sentences?
+
+__=>__ TODO
 
@@
 
-Review #162B
+Review B
 ------------
@@
 ### Comments for authors
-- The idea of combining concrete and symbolic execution is a good one. I have
-  not seen this done in Abstract Interpretation setting before. However, it is
-  well established in Symbolic Execution domain. Concolic execution, especially
-  as pioneered by EXE, and is currently best exemplified by KLEE, seems the
-  closest to the proposed technique.
 
-- Symbolic Execution can be seen as abstract interpretation over an abstract
-  domain of expressions. From the high-level, it is identical to what is
+__B1)__ The idea of combining concrete and symbolic execution is a good one. I
+have not seen this done in Abstract Interpretation setting before. However, it
+is well established in Symbolic Execution domain. Concolic execution,
+especially as pioneered by EXE, and is currently best exemplified by KLEE,
+seems the closest to the proposed technique.
+
+__=>__ TODO
+
+__B2)__ Symbolic Execution can be seen as abstract interpretation over an
+abstract domain of expressions. From the high-level, it is identical to what is
 proposed in the paper: state is divided into concrete and abstract values,
@@
 
-- The paper spends a significant amount of space formalizing the semantics and
-  the abstract domain. The formalism is appreciated, but it belongs to the
-  appendix rather than the main body of the paper. Nothing new is communicated
-  by it in addition to what is described in the motivation.
+__=>__ TODO
 
-- However, what is missing is a clear identification of the limitations of the
-  approach. How does the proposed scheme integrates with typical abstract
+__B3)__ The paper spends a significant amount of space formalizing the
+semantics and the abstract domain. The formalism is appreciated, but it belongs
+to the appendix rather than the main body of the paper. Nothing new is
+communicated by it in addition to what is described in the motivation.
+
+__=>__ TODO
+
+__B4)__ However, what is missing is a clear identification of the limitations
+of the approach. How does the proposed scheme integrates with typical abstract
 interpretation analyses? For example, I imagine that aggressive use of joins
@@
 
-- In the current presentation, it seems that the authors consider only simple
-  non-relational domains that are lifted to a powerset (i.e., join is union).
-  If that is the case, the result is essentially identical to symbolic
+__=>__ TODO
+
+__B5)__ In the current presentation, it seems that the authors consider only
+simple non-relational domains that are lifted to a powerset (i.e., join is
+union).  If that is the case, the result is essentially identical to symbolic
 execution and the degree of novelty compared to concolic execution is low.
+
+__=>__ TODO
 
@@
 
-- What is the key distinguishing characteristic of the proposed approach with
-  Concolic Symbolic Execution
+__B6)__ What is the key distinguishing characteristic of the proposed approach
+with Concolic Symbolic Execution
 
-- What are the limitations the approach places on abstract domains / algorithms
-  used with it
+__=>__ TODO
 
-- How the proposed technique integrates with typical static analysis: join,
-  widen, efficient fixedpoint computation, etc.
+__B7)__ What are the limitations the approach places on abstract domains /
+algorithms used with it
+
+__=>__ TODO
+
+__B8)__ How the proposed technique integrates with typical static analysis:
+join, widen, efficient fixedpoint computation, etc.
+
+__=>__ TODO
 
@@
 
-Review #162C
+Review C
 ------------
@@
 
-- Sect. 4.3 is one of the most interesting sections - the paper is about
+__C1)__ Sect. 4.3 is one of the most interesting sections - the paper is about
 JavaScript after all.  However, 4.3 is very short and Sects. 4.1 and 4.2
-  introduce a lot of definitions which are not really needed to understand
-  Sect. 4.3.  So maybe 4.1 and 4.2 could be less detailed in favor of 4.3.
+introduce a lot of definitions which are not really needed to understand Sect.
+4.3.  So maybe 4.1 and 4.2 could be less detailed in favor of 4.3.
 
-- The paper could discuss why/how (not) dynamic shortcuts can be used for other
-  languages.
+__=>__ TODO
+
+__C2)__ The paper could discuss why/how (not) dynamic shortcuts can be used for
+other languages.
+
+__=>__ TODO
 
@@
 
-- Please make explicit what the baseline analyzer is (I suppose standard
+__C3)__ Please make explicit what the baseline analyzer is (I suppose standard
 SAFE?).
 
-- I think that the chosen benchmark set (Lodash tests) is not a good choice,
-  because even in the abstracted version, test cases are a special kind of
-  software (threat to external validity).
+__=>__ TODO
 
-- Moreover, the authors mention that the benchmark set was already used twice.
-  But those uses are by similar authors.  So this statement is not convincing
-  for the acceptance of the benchmark set in the community.
+__C4)__ I think that the chosen benchmark set (Lodash tests) is not a good
+choice, because even in the abstracted version, test cases are a special kind
+of software (threat to external validity).
+
+__=>__ TODO
+
+__C5)__ Moreover, the authors mention that the benchmark set was already used
+twice.  But those uses are by similar authors.  So this statement is not
+convincing for the acceptance of the benchmark set in the community.
+
+__=>__ TODO
 
 ### Section 6.1 Analysis Speed-up
-- Communication cost is one of your future work suggestions, so more details
-  could be interesting: The authors could mention what is included in
+
+__C6)__ Communication cost is one of your future work suggestions, so more
+details could be interesting: The authors could mention what is included in
 communication cost.  The state conversions? Or only data transfer between
@@
 
+__=>__ TODO
+
 ### Section 6.2 Precision Improvement
 
-- How is "average improvement" (solid line) calculated?
+__C7)__ How is "average improvement" (solid line) calculated?
 
-- I do not understand where I can see the 24 failed assertions in Figure 9a.
+__=>__ TODO
 
-- Also the percentages: You write "Figure 9(b) shows ... by 12.32 %" I do not
-  understand how to get the numbers from the figure.  Maybe a table is more
+__C8)__ I do not understand where I can see the 24 failed assertions in Figure
+9a.
+
+__=>__ TODO
+
+__C9)__ Also the percentages: You write "Figure 9(b) shows ... by 12.32%" I do
+not understand how to get the numbers from the figure.  Maybe a table is more
 appropriate here?
 
-- In general, I find the heat-map notation a bit confusing. Maybe one could
-  explain an example, like "The grey circle at (0,12) means that x assertions
-  failed with DS, ..."
+__=>__ TODO
 
-- I also don't understand what the authors are averaging over in statements
-  like "92.79 % on average".  I understand that for each of the 156 tests a
-  failed assertion can be produced or not.  So it's possible to say, e.g., if
-  half of the failed assertions are removed, the number is reduced by 50 %. But
-  why average?
+__C10)__ In general, I find the heat-map notation a bit confusing. Maybe one
+could explain an example, like "The grey circle at (0,12) means that x
+assertions failed with DS, ..."
+
+__=>__ TODO
+
+__C11)__ I also don't understand what the authors are averaging over in
+statements like "92.79% on average".  I understand that for each of the 156
+tests a failed assertion can be produced or not.  So it's possible to say,
+e.g., if half of the failed assertions are removed, the number is reduced by
+50%. But why average?
+
+__=>__ TODO

### 2021-04-29 paper/fse21/rebuttal.md
Splitted rebuttal.md

@@
 - TODO
-
---------------------------------------------------------------------------------
-# Individual Response (Optional)
---------------------------------------------------------------------------------
-
-Review #162A
-------------
-
-### Abstract
-
-- The abstract is too long and meandering
-
-- "Sealed state" is a term for your new contribution (I believe), but it is not
-  understood by the non-expert reader. I would avoid using jargon in the
-  abstract.
-
-- This approach could be explained more intuitively in the abstract. E.g., "We
-  eliminate the need to analyze some methods by using the concrete parameters
-  used to call them, and simply executing the code instead of analyzing it."
-  This is probably not a totally correct characterization of your work, but it
-  is much more intuitive and easy to understand.
-
-- Microcontrollers for IoT is not a major use of Javascript… seems off topic.
-
-- What do you mean by host environments?
-
-- What do you mean by "high performance"? Do you mean fast? Do you mean
-  accurate?
-
-- It is difficult to make the jump from the high-level discussion (top) to the
-  detailed discussion (bottom).
-
-### Section 1 Introduction
-
-- I don’t understand the focus on JavaScript in IoT environments… how is that
-  relevant?
-
-- "High performance" is an odd phrase to use here. I would consider speaking of
-  the attribute you appreciate directly. I think you are referring to speed.
-
-- The characterization of related work makes it difficult to determine how your
-  work differs from theirs.
-
-- I do not follow the example very well. I am not an expert on this type of
-  program analysis, but I do understand program analysis generally, and I feel
-  like this example is not clear. I would remove it.
-
-- The performance gains seem very strong.
-
-### Section 2 Motivation
-
-- These examples are helpful for understanding your approach. I would remove
-  the other example from the introduction, which was not helpful because it was
-  too brief.
-
-### Section 5 Implementation
-
-- Good description of implementation and clever approach.
-
-### Section 6 Evaluation
-
-- The speedup seems remarkable.
-
-- The communication costs section could be removed.
-
-- Section 6.2 Precision Improvement) Can you discuss the practical implications
-  of removing these failed assertions more clearly?
-
-### Questions for authors
-
-- Can you describe the key insight(s) of your approach, as if you were speaking
-  to a non-expert, in 1-2 sentences?
-
---------------------------------------------------------------------------------
-
-Review #162B
-------------
-
-### Comments for authors
-- The idea of combining concrete and symbolic execution is a good one. I have
-  not seen this done in Abstract Interpretation setting before. However, it is
-  well established in Symbolic Execution domain. Concolic execution, especially
-  as pioneered by EXE, and is currently best exemplified by KLEE, seems the
-  closest to the proposed technique.
-
-- Symbolic Execution can be seen as abstract interpretation over an abstract
-  domain of expressions. From the high-level, it is identical to what is
-  proposed in the paper: state is divided into concrete and abstract values,
-  concrete values are executed concretely, symbolic are executed symbolically.
-  Concrete values can be converted to symbolic, but not the other way around.
-  There is a large body of related work on all kind of iterations of this basic
-  idea.
-
-- The paper spends a significant amount of space formalizing the semantics and
-  the abstract domain. The formalism is appreciated, but it belongs to the
-  appendix rather than the main body of the paper. Nothing new is communicated
-  by it in addition to what is described in the motivation.
-
-- However, what is missing is a clear identification of the limitations of the
-  approach. How does the proposed scheme integrates with typical abstract
-  interpretation analyses? For example, I imagine that aggressive use of joins
-  and convex abstract domains will create so much abstract values that concrete
-  execution will not be possible. Similar questions apply to widening,
-  summary/contract computation for handling recursion, etc.
-
-- In the current presentation, it seems that the authors consider only simple
-  non-relational domains that are lifted to a powerset (i.e., join is union).
-  If that is the case, the result is essentially identical to symbolic
-  execution and the degree of novelty compared to concolic execution is low.
-
-### Questions for authors
-
-- What is the key distinguishing characteristic of the proposed approach with
-  Concolic Symbolic Execution
-
-- What are the limitations the approach places on abstract domains / algorithms
-  used with it
-
-- How the proposed technique integrates with typical static analysis: join,
-  widen, efficient fixedpoint computation, etc.
-
---------------------------------------------------------------------------------
-
-Review #162C
-------------
-
-### Weak Point 1 (W1)
-
-- Sect. 4.3 is one of the most interesting sections - the paper is about
-  JavaScript after all.  However, 4.3 is very short and Sects. 4.1 and 4.2
-  introduce a lot of definitions which are not really needed to understand
-  Sect. 4.3.  So maybe 4.1 and 4.2 could be less detailed in favor of 4.3.
-
-- The paper could discuss why/how (not) dynamic shortcuts can be used for other
-  languages.
-
-### Weak Point 2 (W2)
-
-- Please make explicit what the baseline analyzer is (I suppose standard
-  SAFE?).
-
-- I think that the chosen benchmark set (Lodash tests) is not a good choice,
-  because even in the abstracted version, test cases are a special kind of
-  software (threat to external validity).
-
-- Moreover, the authors mention that the benchmark set was already used twice.
-  But those uses are by similar authors.  So this statement is not convincing
-  for the acceptance of the benchmark set in the community.
-
-### Section 6.1 Analysis Speed-up
-- Communication cost is one of your future work suggestions, so more details
-  could be interesting: The authors could mention what is included in
-  communication cost.  The state conversions? Or only data transfer between
-  processes?  In this context it might also be interesting to know how you
-  implemented the communication.  And then it can get relevant to know how
-  exactly you measured it.
-
-### Section 6.2 Precision Improvement
-
-- How is "average improvement" (solid line) calculated?
-
-- I do not understand where I can see the 24 failed assertions in Figure 9a.
-
-- Also the percentages: You write "Figure 9(b) shows ... by 12.32 %" I do not
-  understand how to get the numbers from the figure.  Maybe a table is more
-  appropriate here?
-
-- In general, I find the heat-map notation a bit confusing. Maybe one could
-  explain an example, like "The grey circle at (0,12) means that x assertions
-  failed with DS, ..."
-
-- I also don't understand what the authors are averaging over in statements
-  like "92.79 % on average".  I understand that for each of the 156 tests a
-  failed assertion can be produced or not.  So it's possible to say, e.g., if
-  half of the failed assertions are removed, the number is reduced by 50 %. But
-  why average?

### 2021-04-29 paper/fse21/rebuttal.md
First draft of rebuttal.md

@@
 
-- TODO
+### Novelty (Review A, B)
+
+The most important contribution of this paper is to present the __first
+formalization of _flexible_ switching between abstract and concrete execution
+for JavaScript in a sound way__.  We introduced a _dynamic shortcut_ as a
+technique to perform concrete execution with abstract values during static
+analysis to enhance analysis performance and precision.  To be aware of when the
+actual value of each abstract value is required in the concrete execution, we
+converted it to a _sealed value_, which is a symbol that signals the end of the
+current dynamic shortcut when the concrete execution tries to access its value.
+The most related previous work is Concerto
+[[POPL'19](https://dl.acm.org/doi/abs/10.1145/3290356)], a Java static analyzer
+with mostly-concrete execution described in the related work section.  Similar
+to our dynamic shortcuts, Concerto combines static analysis with extended
+concrete execution (mostly-concrete execution or symbolic execution) to improve
+analysis precision and performance.  However, Concerto has a critical limitation
+that they _syntactically_ divide programs into two different parts for static
+analysis and concrete execution.
+
+### Comparison with Concolic Execution (Review B)
+
+We agree with Review B that _concolic execution_ also has similar concept with
+dynamic shortcuts because it also leverages concrete execution not for abstract
+interpretation but for _symbolic execution_.  As Review B already mentioned,
+symbolic execution can be treated as an abstract interpretation with symbolic
+expressions and path constraints.  However, we formalized a dynamic shortcut as
+a technique to combine concrete execution with general abstract interpretation
+not symbolic execution.  Thus, dynamic shortcuts are theoretically applicable
+for any type of abstract interpretation including symbolic execution it is more
+general definition of concolic execution.  Nevertheless, we agree with concolic
+execution is also closely related with out technique.  We will supplement
+citations for symbolic and concolic execution and compare them with dynamic
+shortcuts.
+
+### Necessity of Formalization (Review B)
+
+The concept of dynamic shortcut is quite simple because it just utilizes
+concrete execution with abstract values until their actual values are required.
+However, we believe that the formalization of dynamic shortcut is necessary and
+the brief formalization idea should be explained in the paper.  Although many
+real-world static analyzers aim _soundy_ analysis by sacrificing soundness, it
+is still important to prove the _soundness_ and _termination_ of static
+analysis.  Thus, we formally defined dynamic shortcuts, found the conditions
+when the dynamic shortcut would be sound and terminate, and formally proved
+them.  We believe that this formalization could answer an important question:
+"Are the soundness and termination of the static analysis with dynamic
+shortcuts still guaranteed even though parts of abstract interpretation are
+replaced with _concrete execution_?''
+
+### Limitation of Dynamic Shortcuts (Review B)
+
+We agree with Review B that the quality of dynamic shortcuts depends on the
+shape of the abstract domain including its abstract values and join (widening)
+operator.  Although dynamic shortcuts are theoretically applicable to any
+abstract domain, its quality is not always guaranteed.  If an abstract domain
+gives less opportunities to utilize concrete execution, the effect of dynamic
+shortcuts decrease.  On the other hand, aggressively many dynamic shortcuts
+might suffer from massive communication costs.  Although we did not answer about
+a more detailed relationship between dynamic shortcuts and the shape of abstract
+domain in this paper, we experimentally showed that dynamic shortcuts can
+enhance the performance and precision of JavaScript static analysis.  We believe
+that to find more detailed relationship between them is one of good future
+research direction.
+
+### Extensibility for Other Languages (Review C)
+
+We believe that dynamic shortcuts are applicable for static analysis of other
+languages.  Although the abstract domain and sealed execution in other languages
+are totally different with those of JavaScript, the general formalization of
+dynamic shortcut is not dependent on JavaScript language characteristics.  Thus,
+it is possible to define dynamic shortcuts on any other languages and they can
+enhance the analysis precision.  However, the precision improvement might not be
+remarkable or the analysis might suffer from massive communication costs.  We
+believe that to apply dynamic shortcuts for other languages is a convincing
+future research direction for dynamic shortcuts.

### 2021-04-29 paper/fse21/rebuttal.md
Merged draft of rebuttal.md

@@
 
-### Necessity of Formalization (Review B)
+### Importance of Formalization (Review B)
 
@@
 future research direction for dynamic shortcuts.
+
+--------------------------------------------------------------------------------
+# Individual Response (Optional)
+--------------------------------------------------------------------------------
+
+Review A
+------------
+
+### Abstract
+
+__A1) The abstract is too long and meandering__
+
+__=>__ Thank you for the detailed comments. We will revise our paper with
+considering your comments in the final version. We will remove unnecessary
+details in the abstract.
+
+__A2) "Sealed state" is a term for your new contribution (I believe), but it
+is not understood by the non-expert reader. I would avoid using jargon in the
+abstract.__
+
+__=>__ We will rephrase the abstract to remove some jargon.
+
+__A3) This approach could be explained more intuitively in the abstract.
+E.g., "We eliminate the need to analyze some methods by using the concrete
+parameters used to call them, and simply executing the code instead of
+analyzing it." This is probably not a totally correct characterization of your
+work, but it is much more intuitive and easy to understand.__
+
+__=>__ As explained in __Novelty__ part, we believe that the most important
+contribution of this paper is to present the __first formalization of
+_flexible_ switching between abstract and concrete execution for JavaScript in
+a sound way__.  We will add this sentence to the abstract.
+
+__A4) Microcontrollers for IoT is not a major use of JavaScript… seems off
+topic.__
+
+__=>__ We believe that micro-controllers are emerging fields of JavaScript.
+A paper [[HOPL'19](https://dl.acm.org/doi/abs/10.1145/3386327)] about the
+history of JavaScript also says that:
+
+> In addition to server applications built using Node.js and other hosts,
+> JavaScript is being used to build desktop applications, mobile device
+> applications, fitness trackers, robots, and numerous embedded systems.
+
+__A5) What do you mean by host environments?__
+
+__=>__
+
+In ECMAScript 2020 (ES11) explains host environments as follows:
+
+> A host environment typically includes objects or functions which allow
+> obtaining input and providing output as host-defined properties of the global
+> object.
+
+For instance, a browser supplies objects that represent windows, pop-ups, text
+areas, cookies, and input/output as its host environment.
+
+__A6) What do you mean by "high performance"? Do you mean fast? Do you mean
+accurate?__
+
+__=>__ We refer to "short elapsed time" as "high performance" at all time.
+
+__A7)  It is difficult to make the jump from the high-level discussion (top)
+to the detailed discussion (bottom).__
+
+__=>__ We will reorganize the abstract in a top-down structure.
+
+### Section 1 Introduction
+
+__A8) I don’t understand the focus on JavaScript in IoT environments… how is
+that relevant?__
+
+__=>__ The same answer as A4).
+
+__A9) "High performance" is an odd phrase to use here. I would consider
+speaking of the attribute you appreciate directly. I think you are referring to
+speed.__
+
+__=>__ The same answer as A6).
+
+__A10) The characterization of related work makes it difficult to determine
+how your work differs from theirs.__
+
+__=>__ Please see __Novelty__.
+
+__A11) I do not follow the example very well. I am not an expert on this type
+of program analysis, but I do understand program analysis generally, and I feel
+like this example is not clear. I would remove it.__
+
+__=>__ We believe that this example explains the core idea of our approach.  We
+will rephrase explanations more clearly.
+
+### Section 2 Motivation
+
+__A12) These examples are helpful for understanding your approach. I would
+remove the other example from the introduction, which was not helpful because
+it was too brief.__
+
+__=>__ The same answer as A11).
+
+### Section 6 Evaluation
+
+__A13) The communication costs section could be removed.__
+
+__=>__ We believe that to reduce the communication cost is also important
+problem because the analysis might suffer from large communication cost.
+
+__A14) Section 6.2 Precision Improvement) Can you discuss the practical
+implications of removing these failed assertions more clearly?__
+
+__=>__ In static analysis, to count the number of failed assertions is a
+possible approach to measure analysis precision.  The more removing failed
+assertions, the more precise analysis.  Thus, we experimentally showed that
+dynamic shortcuts can improve precision of JavaScript static analysis.
+
+### Questions for authors
+
+__A15) Can you describe the key insight(s) of your approach, as if you were
+speaking to a non-expert, in 1-2 sentences?__
+
+__=>__ Briefly speaking, dynamic analyses on commercial engines are much faster
+than static analyzers, so we can accelerate the static analysis as much as we
+substitute some parts of the static analysis to the dynamic analysis.  We
+propose a novel technique to utilize the dynamic analysis during the static
+analysis with the most flexible form and in a sound manner.
+
+--------------------------------------------------------------------------------
+
+Review B
+------------
+
+### Comments for authors
+
+__B1) The idea of combining concrete and symbolic execution is a good one. I
+have not seen this done in Abstract Interpretation setting before. However, it
+is well established in Symbolic Execution domain. Concolic execution,
+especially as pioneered by EXE, and is currently best exemplified by KLEE,
+seems the closest to the proposed technique.__
+
+__=>__ Thank you for the constructive comments about concolic execution.
+Please see __Comparison with Concolic Execution__.
+
+__B2) Symbolic Execution can be seen as abstract interpretation over an
+abstract domain of expressions. From the high-level, it is identical to what is
+proposed in the paper: state is divided into concrete and abstract values,
+concrete values are executed concretely, symbolic are executed symbolically.
+Concrete values can be converted to symbolic, but not the other way around.
+There is a large body of related work on all kind of iterations of this basic
+idea.__
+
+__=>__ Please see __Comparison with Concolic Execution__.
+
+__B3) The paper spends a significant amount of space formalizing the
+semantics and the abstract domain. The formalism is appreciated, but it belongs
+to the appendix rather than the main body of the paper. Nothing new is
+communicated by it in addition to what is described in the motivation.__
+
+__=>__ Please see __Importance of Formalization__.
+
+__B4) However, what is missing is a clear identification of the limitations
+of the approach. How does the proposed scheme integrates with typical abstract
+interpretation analyses? For example, I imagine that aggressive use of joins
+and convex abstract domains will create so much abstract values that concrete
+execution will not be possible. Similar questions apply to widening,
+summary/contract computation for handling recursion, etc.__
+
+__=>__ Please see __Limitation of Dynamic Shortcuts__.
+
+__B5) In the current presentation, it seems that the authors consider only
+simple non-relational domains that are lifted to a powerset (i.e., join is
+union).  If that is the case, the result is essentially identical to symbolic
+execution and the degree of novelty compared to concolic execution is low.__
+
+__=>__ Please see __Limitation of Dynamic Shortcuts__.
+
+### Questions for authors
+
+__B6) What is the key distinguishing characteristic of the proposed approach
+with Concolic Symbolic Execution__
+
+__=>__ Please see __Comparison with Concolic Execution__.
+
+__B7) What are the limitations the approach places on abstract domains /
+algorithms used with it__
+
+__=>__ Please see __Limitation of Dynamic Shortcuts__.
+
+__B8) How the proposed technique integrates with typical static analysis:
+join, widen, efficient fixedpoint computation, etc.__
+
+__=>__ Please see __Limitation of Dynamic Shortcuts__.
+
+--------------------------------------------------------------------------------
+
+Review C
+------------
+
+### Weak Point 1 (W1)
+
+__C1) Sect. 4.3 is one of the most interesting sections - the paper is about
+JavaScript after all.  However, 4.3 is very short and Sects. 4.1 and 4.2
+introduce a lot of definitions which are not really needed to understand Sect.
+4.3.  So maybe 4.1 and 4.2 could be less detailed in favor of 4.3.__
+
+__=>__ Section 4.3 explains how to extend concrete execution to sealed
+execution thus it is not related to abstract semantics explains in Section 4.1
+and 4.2.
+
+__C2) The paper could discuss why/how (not) dynamic shortcuts can be used for
+other languages.__
+
+__=>__ Thank you for a good question about the extensibility of dynamic
+shortcuts for other languages.  Please see __Extensibility for Other
+Languages__.
+
+### Weak Point 2 (W2)
+
+__C3) Please make explicit what the baseline analyzer is (I suppose standard
+SAFE?).__
+
+__=>__ We used the baseline analyzer based on the standard SAFE with the
+following minor changes.
+1) We increased the call-site sensitivity from 20 to 30 and the iteration of
+loop sensitivity from 100 to 400.
+2) We modified some incomplete models for opaque functions to analyze Lodash
+tests soundly.
+
+__C4) I think that the chosen benchmark set (Lodash tests) is not a good
+choice, because even in the abstracted version, test cases are a special kind
+of software (threat to external validity).__
+
+__=>__ Most static analysis techniques for JavaScript programs have been
+evaluated with famous JavaScript libraries. Until the mid-2010s, most of the
+researchers [[ECOOP'15](https://drops.dagstuhl.de/opus/volltexte/2015/5245/),
+[DLS'16](https://dl.acm.org/doi/10.1145/2989225.2989228),
+[APLAS'17](https://link.springer.com/chapter/10.1007/978-3-319-71237-6_8)]
+focused on jQuery and its benchmarks.  However, recent techniques
+[[OOPSLA'19](https://dl.acm.org/doi/abs/10.1145/3360566),
+[ECOOP'20](https://drops.dagstuhl.de/opus/volltexte/2020/13173/)] are evaluated
+with Lodash and its official tests because of its popularity and complex field
+copy patterns (e.g. `mixin` function).   We agree that real-world benchmarks
+are more interesting and appropriate to evaluate dynamic shortcuts than
+randomly _abstracted_ Lodash 4 tests.  However, static analysis of real-world
+JavaScript applications require diverse host-dependent abstract models such as
+DOM trees/APIs and event handlers for web applications or file systems,
+networks, and module imports for Node.js applications.  Thus, we decided to
+focus on pure JavaScript applications and to randomly abstract Lodash 4 tests.
+
+__C5) Moreover, the authors mention that the benchmark set was already used
+twice.  But those uses are by similar authors.  So this statement is not
+convincing for the acceptance of the benchmark set in the community.__
+
+__=>__ The same answer as C4)
+
+### Section 6.1 Analysis Speed-up
+
+__C6) Communication cost is one of your future work suggestions, so more
+details could be interesting: The authors could mention what is included in
+communication cost.  The state conversions? Or only data transfer between
+processes?  In this context it might also be interesting to know how you
+implemented the communication.  And then it can get relevant to know how
+exactly you measured it.__
+
+__=>__ The current implementation we used the SAFE analyzer written in Scala
+and the dynamic analysis naturally runs on JavaScript engine.  They run as two
+different processes and communicate through a localhost server.  So the
+communication cost consist of both the state conversions and data transfer.  We
+measured state conversions and data transfer separately but we simply present
+the sum of them because they are almost proportional.
+
+### Section 6.2 Precision Improvement
+
+Thank you for pointing out some misleading explanation about the precision
+improvement.  We will answer all the questions and revise this section based on
+these answers.
+
+__C7) How is "average improvement" (solid line) calculated?__
+
+__=>__  For each test case except on (0, 0), we calculate the slope by ((the
+number of failed assertions from DS) / (the number of failed assertions from
+no-DS)) and calculate average of them.
+
+__C8) I do not understand where I can see the 24 failed assertions in Figure__
+9a.
+
+__=>__ We tried to say the DS did not produce any failed assertions for 24 test
+cases that the no-DS produced at least 2 failed assertions for.  The darker
+circle is, the more tests it indicates.  Thus, the sum of test cases from the
+circles on the x-axis except (0, 0) is 24.
+
+__C9) Also the percentages: You write "Figure 9(b) shows ... by 12.32%" I do
+not understand how to get the numbers from the figure.  Maybe a table is more
+appropriate here?__
+
+__=>__ The improvement of "12.31%" can be calculated by (1 - (the slope of the
+solid line)).
+
+__C10) In general, I find the heat-map notation a bit confusing. Maybe one
+could explain an example, like "The gray circle at (0,12) means that x
+assertions failed with DS, ..."__
+
+__=>__ We will add an example, as you commented.
+
+__C11) I also don't understand what the authors are averaging over in
+statements like "92.79% on average".  I understand that for each of the 156
+tests a failed assertion can be produced or not.  So it's possible to say,
+e.g., if half of the failed assertions are removed, the number is reduced by
+50%. But why average?__
+
+__=>__ We will revise the whole paragraph to explain Figure 9 more clearly.

### 2021-04-30 paper/fse21/rebuttal.md
Applied Dongjun's opinion to rebuttal.md

@@
 that they _syntactically_ divide programs into two different parts for static
-analysis and concrete execution.
+analysis and concrete execution.  Unlike their approaches, we wanted to utilize
+JavaScript engines more aggressively and flexibly by automatically detecting
+whether concrete execution is possible without any syntactic restrictions.
 
@@
 
-We agree with Review B that _concolic execution_ also has similar concept with
+We agree with Review B that _concolic execution_ also has similar concept to
 dynamic shortcuts because it also leverages concrete execution not for abstract
@@
 not symbolic execution.  Thus, dynamic shortcuts are theoretically applicable
-for any type of abstract interpretation including symbolic execution it is more
-general definition of concolic execution.  Nevertheless, we agree with concolic
-execution is also closely related with out technique.  We will supplement
-citations for symbolic and concolic execution and compare them with dynamic
-shortcuts.
+for any type of abstract interpretation including symbolic execution and it is
+more general definition of concolic execution.  Nevertheless, we agree that
+concolic execution is also closely related to our technique.  We will
+supplement citations for symbolic and concolic execution and compare them to
+dynamic shortcuts.
 
@@
 concrete execution with abstract values until their actual values are required.
-However, we believe that the formalization of dynamic shortcut is necessary and
-the brief formalization idea should be explained in the paper.  Although many
-real-world static analyzers aim _soundy_ analysis by sacrificing soundness, it
-is still important to prove the _soundness_ and _termination_ of static
-analysis.  Thus, we formally defined dynamic shortcuts, found the conditions
-when the dynamic shortcut would be sound and terminate, and formally proved
-them.  We believe that this formalization could answer an important question:
-"Are the soundness and termination of the static analysis with dynamic
-shortcuts still guaranteed even though parts of abstract interpretation are
-replaced with _concrete execution_?''
+However, we believe that the formalization of dynamic shortcut is necessary to
+prove _soundness_ and _termination_, thus we explained the brief formalization
+idea should be explained in the paper.  Although many real-world static
+analyzers aim _soundy_ analysis by sacrificing soundness for practical reasons,
+it is still important to prove the _soundness_ and _termination_ for a new
+analysis technique in theory.  Thus, we formally defined dynamic shortcuts,
+found the conditions when the dynamic shortcut would be sound and terminate,
+and formally proved them.  We believe that this formalization could answer an
+important question: "Are the soundness and termination of the static analysis
+with dynamic shortcuts still guaranteed even though parts of abstract
+interpretation are replaced with _concrete execution_?''
 
@@
 enhance the performance and precision of JavaScript static analysis.  We believe
-that to find more detailed relationship between them is one of good future
+that finding more detailed relationship between them is one of good future
 research direction.
@@
 remarkable or the analysis might suffer from massive communication costs.  We
-believe that to apply dynamic shortcuts for other languages is a convincing
+believe that applying dynamic shortcuts for other languages is a convincing
 future research direction for dynamic shortcuts.
@@
 
-__=>__ Thank you for the detailed comments. We will revise our paper with
+__=>__ Thank you for the detailed comments. We will revise our paper by
 considering your comments in the final version. We will remove unnecessary
@@
 
-__=>__
-
-In ECMAScript 2020 (ES11) explains host environments as follows:
+__=>__ In ECMAScript 2020 (ES11) explains host environments as follows:
 
@@
 
-__=>__ We believe that to reduce the communication cost is also important
+__=>__ We believe that reducing the communication cost is also important
 problem because the analysis might suffer from large communication cost.
@@
 __=>__ In static analysis, to count the number of failed assertions is a
-possible approach to measure analysis precision.  The more removing failed
-assertions, the more precise analysis.  Thus, we experimentally showed that
-dynamic shortcuts can improve precision of JavaScript static analysis.
+typical approach to measure analysis precision.  More failed assertions denote
+more precise analysis.  Thus, we experimentally showed that dynamic shortcuts
+can improve precision of JavaScript static analysis.
 
@@
 __=>__ Briefly speaking, dynamic analyses on commercial engines are much faster
-than static analyzers, so we can accelerate the static analysis as much as we
-substitute some parts of the static analysis to the dynamic analysis.  We
-propose a novel technique to utilize the dynamic analysis during the static
-analysis with the most flexible form and in a sound manner.
+than static analyzers, so we can accelerate the static analysis by substituting
+some parts of the static analysis to the dynamic analysis.  We propose a novel
+technique to utilize the dynamic analysis during the static analysis with the
+most flexible form and in a sound manner.
 
@@
 
-__=>__ Section 4.3 explains how to extend concrete execution to sealed
-execution thus it is not related to abstract semantics explains in Section 4.1
-and 4.2.
+__=>__ While Section 4.2 extends concrete execution of JavaScript explained in
+Section 4.1 to abstract execution, Section 4.3 extends it to sealed execution.
+Thus, we believe that Section 4.1 is necessary to understand the baseline of
+sealed execution. Moreover, Section 4.2 is not directly related to Section 4.3.
+but Section 4.2 itself is important to define how to abstract the concrete
+semantics of JavaScript.
 
@@
 __=>__ We used the baseline analyzer based on the standard SAFE with the
-following minor changes.
-1) We increased the call-site sensitivity from 20 to 30 and the iteration of
+following minor changes.  We will explain these configuration in the Evaluation
+section.
+
+1. We increased the call-site sensitivity from 20 to 30 and the iteration of
 loop sensitivity from 100 to 400.
-2) We modified some incomplete models for opaque functions to analyze Lodash
+2. We modified some incomplete models for opaque functions to analyze Lodash
 tests soundly.
@@
 
-__=>__  For each test case except on (0, 0), we calculate the slope by ((the
-number of failed assertions from DS) / (the number of failed assertions from
-no-DS)) and calculate average of them.
+__=>__  Each Lodash 4 test contains multiple assertions and it is represented
+as a circle in heat-map charts.  Since circles are positioned in the same point
+when their corresponding tests have same number of failed assertions, we use
+darker gray to denote larger number of tests.  For each test case except on (0,
+0), we calculate the slope by ((the number of failed assertions from DS) / (the
+number of failed assertions from no-DS)) and calculate average of them.
 
@@
 
-__=>__ We tried to say the DS did not produce any failed assertions for 24 test
-cases that the no-DS produced at least 2 failed assertions for.  The darker
-circle is, the more tests it indicates.  Thus, the sum of test cases from the
-circles on the x-axis except (0, 0) is 24.
+__=>__ We tried to say that the DS did not produce any failed assertions for 24
+test cases that the no-DS produced at least 2 failed assertions for.  The
+darker circle is, the more tests it indicates.  Thus, the sum of test cases
+from the circles on the x-axis except (0, 0) is 24.
 

### 2021-05-13 paper/fse21/rebuttal-optional.md

@@
 
-__=>__ TODO
+__=>__ Thank you for the detailed comments. We will revise our paper with considering your comments for the next version. We will modify to remove unnecessary details in the abstract.
 
@@
 
-__=>__ TODO
+__=>__ We will rephrase to remove some jargons.
 
@@
 
-__=>__ TODO
+__=>__ We will add an intuitive use case.
 
@@
 
-__=>__ TODO
+__=>__ TODO  Microcontrollers are the emerging field of JavaScript accoring to ...
 
@@
 
-__=>__ TODO
+__=>__ Each browser and server that supports ECMAScript supplies its own host environment, completing the ECMAScript execution environment.
+For instance, a browser supplies objects that represent windows, pop-ups, text areas, cookies, and input/output.
 
@@
 
-__=>__ TODO
+__=>__ We refer to "short elapsed time" as "high performance" at all time.
 
@@
 
-__=>__ TODO
+__=>__ We will reorganize high-level and detailed discussions.
 
@@
 
-__=>__ TODO
+__=>__ The same answer as A4).
 
@@
 
-__=>__ TODO
+__=>__ The same answer as A6).
 
@@
 
-__=>__ TODO
+__=>__ The key differences are 1) preserving the soundness of the static analyzer and 2) the most flexible form of utilizing the dynamic analysis.
 
@@
 
-__=>__ TODO
+__=>__ We will rephrase explanations more clearly.
 
@@
 
-__=>__ TODO
+__=>__ The same answer as A11).
 
@@
 
-__=>__ TODO
+__=>__ Briefly speaking, dynamic analyses on commercial engines are much faster than static analyzers, so we can accelerate the static analysis as much as we substitute some parts of the static analysis to the dynamic analysis.
+We propose a novel technique to utilize the dynamic analysis during the static analysis with the most flexible form and in a sound manner.
 
@@
 
-__=>__ TODO
+__=>__ COMPARISON WITH CONCOLIC TESTING
 
@@
 
-__=>__ TODO
+__=>__ IMPORTANCE OF FORMALIZATION
 
@@
 
-__=>__ TODO
+__=>__ Although our combined analysis is compatible for relational abstract domains or domain opertaions like widening, it may not have practical benefits for those cases.
+If the number of abstract values increases, the chance of concrete execution decreases.
+So overhead from failures of state conversion and concrete executions may the exceed benefits from success of concrete executions in theory.
+We need future studies about such trade-offs with various domains and programs to answer the question.
 
@@
 
-__=>__ TODO
+__=>__ The same answer as B4).
 
@@
 
-__=>__ TODO
+__=>__ We will balance texts in subsections of Section 4.
 
@@
 
-__=>__ TODO
+__=>__ Dynamic shortcuts can be applicable for other languages, in theory, however, we think the following conditions required to get practical benefits.
+- The dynamic analysis on a concrete engine should be much faster than the static analysis.
+- The target program contains deterministic parts that the dynamic analysis is going to be used.
+JavaScript that we firstly targeted satisfies the conditions and motivated us.
+But we need future studies about other languages to discuss concretely.
 
@@
 
-__=>__ TODO
+__=>__ We used the baseline analyzer based on the standard SAFE with minor changes.
+1) We increase its sensitivity options of "callsite" from 20 to 30 and "loopIter" 100 to 400 from the default options.
+2) We modified some incomplete models for opaque codes to analyze Lodash tests soundly.
 
@@
 
-__=>__ TODO
+__=>__ The same answer as C5)
 
@@
 
-__=>__ TODO
+__=>__ Most static analysis techniques for JavaScript programs have been evaluated with
+famous JavaScript libraries. Until the mid-2010s, most of the researchers
+[[ECOOP'15](https://drops.dagstuhl.de/opus/volltexte/2015/5245/),
+[DLS'16](https://dl.acm.org/doi/10.1145/2989225.2989228),
+[APLAS'17](https://link.springer.com/chapter/10.1007/978-3-319-71237-6_8)]
+focused on jQuery and its benchmarks.  However, recent techniques
+[[OOPSLA'19](https://dl.acm.org/doi/abs/10.1145/3360566),
+[ECOOP'20](https://drops.dagstuhl.de/opus/volltexte/2020/13173/)] are evaluated
+with Lodash and its official tests because of its popularity and complex field
+copy patterns (e.g. `mixin` function).   We agree that real-world benchmarks
+are more interesting and appropriate to evaluate dynamic shortcuts than
+randomly _abstracted_ Lodash 4 tests.  However, static analysis of real-world
+JavaScript applications require diverse host-dependent abstract models such as
+DOM trees/APIs and event handlers for web applications or file systems,
+networks, and module imports for Node.js applications.  Thus, we decided to
+focus on pure JavaScript applications and to randomly abstract Lodash 4 tests.
 
@@
 
-__=>__ TODO
+__=>__ The current implementation we used the SAFE analyzer written in Scala (tool) and the dynamic analysis naturally runs on JavaScript engine.
+They run as two different processes and communicate through a localhost server.
+So the communication cost consist of both the state conversions and data transfer.
+We measured state conversions and data transfer separately but we simply present the sum of them because they are almost proportional.
 
@@
 
-__=>__ TODO
+__=>__ For each test case except on (0, 0), we calcuate the slope by ((the number of failed assetions from DS) / (the number of failed assetions analyzed from no-DS)) and calcuate average of them.
 
@@
 
-__=>__ TODO
+__=>__ We tried to say the DS did not produce any failed assertions for 24 test cases that the no-DS produced at least 2 failed assertions for.
+The darker the circle is, the more tests it indicates.
+Thus, the sum of test cases from the circles on the x-axis except (0, 0) is 24.
 
@@
 
-__=>__ TODO
+__=>__ The improvement of "12.31%" can be calculated by (1 - (the slope of the solid line)).
 
@@
 
-__=>__ TODO
+__=>__ We will add an example, as you commented.
 
@@
 
-__=>__ TODO
+__=>__ We will revise the whole paragraph to explain Figure 9 more clearly.

### 2021-05-13 paper/fse21/rebuttal.md

@@
 shape of the abstract domain including its abstract values and join (widening)
-operator.  Although dynamic shortcuts are theoretically applicable to any
+operator.  Although dynamic shortcut is theoretically applicable to any
 abstract domain, its quality is not always guaranteed.  If an abstract domain
-gives less opportunities to utilize concrete execution, the effect of dynamic
+gives fewer opportunities to utilize concrete execution, the effect of dynamic
 shortcuts decrease.  On the other hand, aggressively many dynamic shortcuts
-might suffer from massive communication costs.  Although we did not answer about
+might suffer from massive communication costs.  Although we did not discuss
 a more detailed relationship between dynamic shortcuts and the shape of abstract
@@
 enhance the performance and precision of JavaScript static analysis.  We believe
-that finding more detailed relationship between them is one of good future
-research direction.
+that finding a more detailed relationship between them is one of good future
+research directions.
 
@@
 languages.  Although the abstract domain and sealed execution in other languages
-are totally different with those of JavaScript, the general formalization of
-dynamic shortcut is not dependent on JavaScript language characteristics.  Thus,
+are totally different from those of JavaScript, the general formalization of
+dynamic shortcuts is not dependent on JavaScript language characteristics.  Thus,
 it is possible to define dynamic shortcuts on any other languages and they can
@@
 remarkable or the analysis might suffer from massive communication costs.  We
-believe that applying dynamic shortcuts for other languages is a convincing
+believe that applying dynamic shortcuts for other languages is a promising
 future research direction for dynamic shortcuts.
@@
 
-__=>__ Thank you for the detailed comments. We will revise our paper by
-considering your comments in the final version. We will remove unnecessary
-details in the abstract.
+__=>__ Thank you for the comment. We will remove unnecessary
+details in the abstract in the final version of our paper.
 
@@
 
-__=>__ We will rephrase the abstract to remove some jargon.
+__=>__ We will rephrase the abstract to remove jargon uses.
 
@@
 
-__=>__ As explained in __Novelty__ part, we believe that the most important
+__=>__ As explained in the __Novelty__ part, we believe that the most important
 contribution of this paper is to present the __first formalization of
@@
 
-> In addition to server applications built using Node.js and other hosts,
-> JavaScript is being used to build desktop applications, mobile device
-> applications, fitness trackers, robots, and numerous embedded systems.
+In addition to server applications built using Node.js and other hosts,
+JavaScript is being used to build desktop applications, mobile device
+applications, fitness trackers, robots, and numerous embedded systems.
 
@@
 
-__=>__ In ECMAScript 2020 (ES11) explains host environments as follows:
+__=>__ ECMAScript 2020 (ES11) explains host environments as follows:
 
-> A host environment typically includes objects or functions which allow
-> obtaining input and providing output as host-defined properties of the global
-> object.
+A host environment typically includes objects or functions which allow
+obtaining input and providing output as host-defined properties of the global
+object.
 
@@
 
-__=>__ We refer to "short elapsed time" as "high performance" at all time.
+__=>__ We refer to "short elapsed time" as "high performance" at all times.
 
@@
 
-__=>__ We will reorganize the abstract in a top-down structure.
+__=>__ We will reorganize the abstract in a top-down manner.
 
@@
 __=>__ We believe that this example explains the core idea of our approach.  We
-will rephrase explanations more clearly.
+will revise the explanations more clearly.
 
@@
 
-__=>__ We believe that reducing the communication cost is also important
-problem because the analysis might suffer from large communication cost.
+__=>__ We believe that reducing the communication cost is also an important
+problem because the analysis might suffer from large communication costs.
 
@@
 
-__=>__ In static analysis, to count the number of failed assertions is a
-typical approach to measure analysis precision.  More failed assertions denote
-more precise analysis.  Thus, we experimentally showed that dynamic shortcuts
-can improve precision of JavaScript static analysis.
+__=>__ In static analysis, counting the number of failed assertions is a
+typical way to measure analysis precision.  More failed assertions denote
+less precise analysis.  Thus, we experimentally showed that dynamic shortcuts
+can improve the precision of JavaScript static analysis.
 
@@
 
-__=>__ Briefly speaking, dynamic analyses on commercial engines are much faster
-than static analyzers, so we can accelerate the static analysis by substituting
-some parts of the static analysis to the dynamic analysis.  We propose a novel
-technique to utilize the dynamic analysis during the static analysis with the
-most flexible form and in a sound manner.
+__=>__ Briefly speaking, because dynamic analysis on a commercial engine is much faster
+than static analysis, we can accelerate static analysis by substituting
+some parts of the static analysis with dynamic analysis.  We propose a novel
+technique to utilize dynamic analysis during static analysis with a
+flexible and sound manner.
 
@@
 Thus, we believe that Section 4.1 is necessary to understand the baseline of
-sealed execution. Moreover, Section 4.2 is not directly related to Section 4.3.
+sealed execution. Moreover, Section 4.2 is not directly related to Section 4.3
 but Section 4.2 itself is important to define how to abstract the concrete
@@
 
-__=>__ Thank you for a good question about the extensibility of dynamic
-shortcuts for other languages.  Please see __Extensibility for Other
-Languages__.
+__=>__ Thank you for a good question about the extensibility of dynamic shortcuts for other languages.  Please see __Extensibility for Other Languages__.
 
@@
 
-__=>__ We used the baseline analyzer based on the standard SAFE with the
-following minor changes.  We will explain these configuration in the Evaluation
+__=>__ The baseline analyzer is the standard SAFE with the
+following small changes.  We will explain this configuration in the Evaluation
 section.
@@
 randomly _abstracted_ Lodash 4 tests.  However, static analysis of real-world
-JavaScript applications require diverse host-dependent abstract models such as
+JavaScript applications requires diverse host-dependent abstract models such as
 DOM trees/APIs and event handlers for web applications or file systems,
@@
 
-__=>__ The current implementation we used the SAFE analyzer written in Scala
-and the dynamic analysis naturally runs on JavaScript engine.  They run as two
-different processes and communicate through a localhost server.  So the
-communication cost consist of both the state conversions and data transfer.  We
-measured state conversions and data transfer separately but we simply present
-the sum of them because they are almost proportional.
+__=>__ In the current implementation, we used the SAFE analyzer written in
+Scala, and the dynamic analysis naturally runs on a JavaScript engine. They run
+as two different processes and communicate through a localhost server.  So the
+communication cost consists of state conversions and data transfers.  We
+measured state conversions and data transfers separately, but we simply
+presented their sum because they are almost proportional.
 
@@
 
-Thank you for pointing out some misleading explanation about the precision
+Thank you for pointing out some misleading explanations about the precision
 improvement.  We will answer all the questions and revise this section based on
@@
 as a circle in heat-map charts.  Since circles are positioned in the same point
-when their corresponding tests have same number of failed assertions, we use
-darker gray to denote larger number of tests.  For each test case except on (0,
-0), we calculate the slope by ((the number of failed assertions from DS) / (the
-number of failed assertions from no-DS)) and calculate average of them.
+when their corresponding tests have the same number of failed assertions, we
+use darker gray to denote a larger number of tests.  For each test case except
+on (0, 0), we calculate the slope by ((the number of failed assertions from DS)
+/ (the number of failed assertions from no-DS)) and calculate average of them.
 
@@
 
-__=>__ We tried to say that the DS did not produce any failed assertions for 24
-test cases that the no-DS produced at least 2 failed assertions for.  The
-darker circle is, the more tests it indicates.  Thus, the sum of test cases
-from the circles on the x-axis except (0, 0) is 24.
+__=>__ We wanted to say that DS did not produce any failed assertions for 24
+test cases that no-DS produced at least 2 failed assertions for.  The darker
+circle is, the more tests it indicates.  Thus, the sum of the test cases from
+the circles on the x-axis except (0, 0) is 24.
 
@@
 
-__=>__ We will add an example, as you commented.
+__=>__ We will add an example as you suggested.
 

### 2021-05-13 paper/fse21/conclusion.tex

@@
 analyzers SAFE and Jalangi.  Our tool accelerates the speed
-of static analysis 19.96$\x$ for original tests and 6.30$\x$ for
-abstracted tests of Lodash 4 library.  Moreover, it detects 6 more
-dead branches by using {\sealed} execution instead of
-manual modeling for 12 opaque functions on average.
+of static analysis 22.30$\x$ for original tests and 7.81$\x$ for
+abstracted tests of Lodash 4 library.  Moreover, it reduces the number
+of failed assertions by 12.31\% by using {\sealed} execution instead of
+manual modeling for 22 opaque functions on average.

### 2021-05-13 paper/fse21/ds.tex

@@
 if it does not have any {\sealed} states to transit to, $\symbst \symbtrans \excst$,
-the {\sealed} execution for $(\absimap, \symbst)$ terminates;
+the {\sealed} execution for $(\absimap, \symbst)$ terminates.
 It converts the analysis element to its corresponding one $(\view, \abselem) =
 \saconverter((\absimap, \symbst))$ in the sensitive abstract domain and
-merges the current abstract state stored in the view $\view$ with $\abselem$.
+merges the current abstract state stored in $\view$ with $\abselem$.
 
@@
 continues.  Because there is no more possible {\sealed} transition for the
-{\sealed} state $\langle \varnothing, 0 \rangle$ with the label $\lab_4$,
+{\sealed} state $\langle \varnothing, 0 \rangle$ with $\lab_4$,
 it is converted to $(\lab_4, 0)$ via the converter $\saconverter$.

### 2021-05-13 paper/fse21/intro.tex

@@
 
-At the same time, various JavaScript host environments require excessive
+At the same time, JavaScript host environments require excessive
 manual modeling of their behaviors for static analysis.  Because built-in functions and
-host-dependent functions are implemented in native language like C and
+host-dependent functions are implemented in native languages like C and
 C++ instead of JavaScript, their code is \textit{opaque} during static
@@
 manually, which is error-prone, tedious, and labor-intensive.
-While several researchers have proposed automatic modeling
+While researchers have proposed automatic modeling
 techniques~\cite{safewapi, model-ts}, since they utilize only type
@@
 To alleviate these problems, researchers have leveraged
-dynamic analysis during static analysis.  \inred{Because dynamic
-analyzers such as Jalangi~\cite{jalangi} and DLint~\cite{dlint} run on
-highly-optimized commercial JavaScript engines while static analyzers run on
-their own interpreters, that leads to a great gap in performance.}
+dynamic analysis during static analysis.  Unlike static analyzers that
+run on their own interpreters, dynamic analyzers such as Jalangi~\cite{jalangi} and DLint~\cite{dlint}
+run on highly-optimized commercial JavaScript engines, which makes them
+much faster than static analyzers.
 Figure~\ref{fig:performance} shows that the dynamic analyzer
 Jalangi is 34.8x faster than the static analyzer SAFE for a subset of the
-SunSpider benchmark \inred{that is input-independent and deterministic}.
+SunSpider benchmark that is input-independent and deterministic.
 Using high performance dynamic analysis, researchers have
@@
 we introduce {\sealed} execution, which is concrete execution
-using \textit{{\sealed} values}.  \inred{A {\sealed} value is a symbol
-that represent an abstract value in {\sealed} execution}; it signals
+using \textit{{\sealed} values}.  A {\sealed} value is a symbol
+that represent an abstract value in {\sealed} execution; it signals
 the end of the current dynamic shortcut when the {\sealed}
 execution tries to access its value.
-To evaluate our technique, we implemented $\tool$ using both SAFE
+To evaluate our technique, we implemented $\tool$ using SAFE
 and Jalangi and analyzed 269 official tests of Lodash 4 library.

### 2021-05-13 paper/fse21/javascript.tex

@@
 \abscountset$ of the abstract counter defined as follows:
+
 \[
@@
 
-We define the {\sealed} states by not only extending the concrete values
-$\valset$ with {\sealed} values $\symbset$ but also adding the abstract counters
-$\abscountset$ as follows:
+We define {\sealed} states by not only extending the concrete values
+$\valset$ with {\sealed} values $\symbset$ but also adding the abstract counters~
+$\abscountset$:
+% as follows:
 \[
@@
 Otherwise, a given {\sealed} state does not have any {\sealed}
-transitions to apply.  For example, we add the following rule for the $\kwret$ statement:
+transitions to apply.  For example, we add the following rule:
 \begin{mathpar}
@@
 \end{mathpar}
-We extend each rule of the concrete semantics to support such behaviors of {\sealed} 
-values.
+for the $\kwret$ statement. We extend each rule of the concrete semantics
+to support such behaviors of {\sealed} values.

### 2021-05-13 paper/fse21/motivation.tex

@@
     \end{lstlisting}
-    \vspace*{-1em}
+    \vspace*{-1.5em}
     \caption{Call of \jscode{concat} with concrete values}
@@
     \end{lstlisting}
-    \vspace*{-1em}
+    \vspace*{-1.5em}
     \caption{Call of \jscode{concat} with abstract values}
@@
   \label{fig:example}
-  \vspace*{-1em}
+  \vspace*{-1.5em}
 \end{figure}
 
-In this section, we explain the motivation of dynamic shortcuts
-using real-world examples shown in Figure~\ref{fig:example}.
-We first describe their behaviors and then explain how we can utilize
-dynamic shortcuts during their static analysis.
+This section explains the motivation of dynamic shortcuts
+using real-world examples in Figure~\ref{fig:example}.
+We describe their behaviors and explain how we can utilize
+dynamic shortcuts during static analysis.
 
@@
 cases of the \jscode{concat} function in the \code{zoom.us}~\cite{zoom} site.
-It is the homepage of Zoom, which is a videotelephony software program developed by Zoom
+It is the homepage of Zoom, a videotelephony software by Zoom
 Video Communications and it is ranked as the 15th popular web site according
@@
 \jscode{[["Other", "Other"]]} and the second one is an array of pairs
-of abbreviations and names of the states defined as follows:
+of abbreviations and names of the states defined as follows: \\[-.5em]
 \begin{lstlisting}[style=myJSstyle,numbers=none]
@@
 \end{lstlisting}
-Moreover, \jscode{this} also has a concrete value, the Lodash top-level object \jscode{\_}.
-Thus, we can perform dynamic analysis by invoking \jscode{concat} with
-\jscode{\_} as its \jscode{this} value and the above concrete values as arguments. 
+\noindent\smallskip
+Moreover, \jscode{this} also has a concrete value, the Lodash top-level object~\jscode{\_}.
+Thus, we can perform dynamic analysis by invoking \jscode{concat} with~\jscode{\_}
+as its \jscode{this} value and the above concrete values as arguments. 
 By skipping the analysis of the function call on lines 17--18 and
